### 2023-07-22 scripts/01-qc.Rmd
init quality control script

---
title: '01 - TreehopperFitness: Data prep'
author: "Micah Fletcher"
date: '`r Sys.Date()`'
output: 
  rmdformats::robobook:
  fig_width: 9
toc_depth: 3
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 8, fig.height = 6)

library(kableExtra)   ## Needed if rendering tables
```

<!-- This file will not execute by itself. It should be called within the  -->
<!-- runfile to render the final report. You can arrange figures, add explanations, -->
<!-- and do other aesthetic tweaks here. -->

```{=html}
<style type="text/css">
  .book .book-body .page-inner {
    max-width: 1600px;
    margin-left: auto;
    margin-right: auto;
  }
details > summary {
  display: list-item;
}
</style>
```

# Data input, qc and pre-processessing for 2019 Publilia field data
```{r}
library(here)
library(tidyverse)
library(readxl)
library(lubridate)
library(stringr)

theme_set(theme_bw())
```

## 0 - Raw Data Input
Read in the data from `data_in_progress/Watershed_field_data_2019_ALL_local.xlsx`
```{r, warning = FALSE}
col_types = c("date", rep("text",8), "date", rep("text", 12))
in_filename <- here("data/Watershed_field_data_2019_ALL_local.xlsx")
in_data <- rbind(read_xlsx(in_filename, sheet = "A", col_types = col_types),
  read_xlsx(in_filename, sheet = "B", col_types = col_types),
  read_xlsx(in_filename, sheet = "C", col_types = col_types),
  read_xlsx(in_filename, sheet = "D", col_types = col_types),
  read_xlsx(in_filename, sheet = "E", col_types = col_types),
  read_xlsx(in_filename, sheet = "F", col_types = col_types),
  read_xlsx(in_filename, sheet = "G", col_types = col_types),
  read_xlsx(in_filename, sheet = "H", col_types = col_types)) %>%
  mutate(Date = as_date(Date),
         Time = hm(Time)) %>% 
  group_by(row_number()) %>% 
  mutate(Leaf = ifelse(!is.na(Female_ID) & is.na(Leaf), 
                       "S",
                       Leaf),
         Female_ID = ifelse(Female_ID %in% c("Uf", "Um", "M", "U") , # append plant and leaf to ID if female id is "unknown"
                            paste0(c(Female_ID, "_", as.character(Plant), "_", as.character(Leaf)), collapse = ""),
                            Female_ID)) %>%
  ungroup()
```

# 1 - Manually check and revise female IDs reproducibly

Create `Female_locations_on_dates` table to use for to manually check for obvious mismatched female IDs and typos in plant id or leaf id etc.

Then manually log these changes into `{dorm letter} Female_ID revisions` sheet then import these and revise the female IDs in the input data without editing the original data file.

Note that changes to things like plant id and leaf id had to be manually edited in the original data file. These are documented in the "Revisions" column in each sheet for each dorm in `Watershed_field_data_2019_ALL_local.xlsx`

## 1.1 - Flag duplicate female ID entries

Flag cases where the same female ID is used on the same day in the same dorm to aid in manual checking.

Display false negative and false positive duplicates in `Dup?` column (used in excel for field data entry).

```{r}
in_data_dupStatus <- in_data %>%
  group_by(Date, Dorm, Female_ID) %>%
    mutate(n_female_dupes = ifelse(!is.na(Female_ID) & !(Female_ID %in% c("E", "E?", "0", NA)),
                                   n(),
                                   NA),
           female_dup_order = ifelse(!is.na(Female_ID) & !(Female_ID %in% c("E", "E?", "0", NA)),
                                     row_number(),
                                     NA)) %>%
  ungroup() %>%
  mutate(dup_status = ifelse(!is.na(n_female_dupes) & !(Female_ID %in% c("E", "E?", "0", "N", NA)),
                             ifelse(n_female_dupes == 1 & !is.na(as.numeric(`Dup?`)),
                                    "Fpos", # copy-paste error or "?" ambiguity in Excel
                                    ifelse(n_female_dupes > 1 & !is.na(as.numeric(`Dup?`)),
                                           "Tpos", 
                                           ifelse(n_female_dupes > 1 & is.na(as.numeric(`Dup?`)),
                                                  "Fneg", # copy-paste error
                                                  ifelse(n_female_dupes == 1 & is.na(as.numeric(`Dup?`)),
                                                         "Tneg",
                                                         "Something went wrong!")))),
                             NA),
         Fem_IDn = ifelse(!is.na(n_female_dupes) & !(Female_ID %in% c("E", "E?", "0", "N", NA)),
                               ifelse(n_female_dupes == 1,
                                      Female_ID,
                                      paste0(Female_ID, "_d", female_dup_order)),
                               NA))

in_data_dupStatus %>%
  count(dup_status)

in_data_dupStatus %>% filter(dup_status == "Fpos") %>% distinct(Female_ID) %>% print(n=Inf)
in_data_dupStatus %>% filter(dup_status == "Tpos") %>% distinct(Female_ID) %>% print(n=Inf)
in_data_dupStatus %>% filter(dup_status == "Fneg") %>% distinct(Female_ID) %>% print(n=Inf)
in_data_dupStatus %>% filter(dup_status == "Tneg") %>% distinct(Female_ID) %>% print(n=Inf)
in_data_dupStatus %>% filter(dup_status == "Something went wrong!") %>% distinct(Female_ID) %>% print(n=Inf)
```

## 1.2 - Create `Female_locations_on_dates_dupStatus` table for manual checking.
Create female locations on dates table for manual checking.
```{r}
female_roster_days_dupStatus <- in_data_dupStatus %>%
  group_by(Date, Dorm) %>%
    distinct(Fem_IDn, .keep_all = TRUE) %>%
  ungroup() %>%
  select(Date, Dorm, Fem_IDn, Female_ID, Plant, Leaf, Eggs) %>%
  filter(!is.na(Fem_IDn), !grepl("M", Female_ID, ignore.case = TRUE))

female_roster_dupStatus <- female_roster_days_dupStatus %>%
  group_by(Dorm, Fem_IDn) %>%
    distinct(Fem_IDn) %>%
  ungroup()

# what days are each female observed on?
Female_locations_on_dates_dupStatus <- female_roster_days_dupStatus %>%
  group_by(row_number()) %>%
    mutate(location = paste0(c(Dorm, Plant, "_", Leaf), collapse = ""),
           Dorm_Fem_IDn = paste0(c(Dorm, "_", Fem_IDn), collapse = "")) %>%
  ungroup() %>%
  select(Dorm_Fem_IDn, location, Date) %>%
  spread(Date, location)

Days_observed_dupStatus <- female_roster_days_dupStatus %>% 
  group_by(Dorm, Fem_IDn) %>%
    summarize(Days_observed = n()) %>%
  ungroup() %>%
  arrange(Dorm, Days_observed)

# used 20200319 version
write_csv(Days_observed_dupStatus, here("data/manual_check/Days_observed_dupStatus.csv"))
```

## 1.3 - Revise Female_ID using `Female_ID revisions dupStatus` sheet

```{r}
# Read in revisions table
Female_ID_revisions <- read_xlsx(in_filename, sheet = "Female_ID revisions dupStatus", col_types = c("date", "text", "text", "text","text", "text", "text", "text"), na = c("", "NA")) %>%
  mutate(Date = as_date(Date),
         Female_ID_revision_notes = Notes) %>%
  select(-Notes) %>%
  mutate(Date = `year<-`(Date, 2019)) # excel's fuckery with dates means any revisions I did in 2020 in the format m/d were interpretted as 2020-%m-%d

# Check number of duplicate rows in revisions sheet (should be 0)
ID_revision_duplicates <- Female_ID_revisions %>%
  group_by(Date, Dorm, Plant, Leaf, `From ID`) %>%
    mutate(n_rows_FromID = n()) %>%
  ungroup() %>%
  group_by(Date, Dorm, Plant, Leaf, `To ID`) %>%
    mutate(n_rows_ToID = n()) %>%
  ungroup() %>%
  arrange(Dorm, Plant, Leaf, Date) %>%
  filter(n_rows_FromID > 1 | n_rows_ToID > 1)
print(paste("Number of duplicate rows in revisions sheet:", nrow(ID_revision_duplicates)))

# Implement revisions from revisions table
All_data_v1 <- in_data_dupStatus %>% 
  full_join(Female_ID_revisions, by = c("Date", "Dorm", "Plant", "Leaf", "Fem_IDn" = "From ID")) %>%
  select(-dup_status) %>%
  # check whether any revisions entries had typos in location or tried to add a female where there was none
  mutate(orphaned_revisions = ifelse(!is.na(`To ID`) & is.na(Female_ID) | `To ID` == "NA",
                TRUE,
                FALSE)) %>%
  # change Female_ID to revised ID unless there was originally no Female_ID
  mutate(Female_ID = ifelse(!orphaned_revisions & !is.na(`To ID`),
                            `To ID`,
                            # add new Female_ID where there was originally no Female_ID
                            ifelse(orphaned_revisions & !is.na(`NA To ID`),
                                   `NA To ID`,
                                   Fem_IDn))) %>%
  # create `location` value combining dorm, plant and leaf into a string
  group_by(row_number()) %>%
    mutate(location = ifelse(!is.na(Leaf),
                             paste0(c(Dorm, Plant, "_", Leaf), collapse = ""),
                             NA)) %>%
  ungroup() %>%
  select(-`NA To ID`)

print(paste("Number of new Female_IDs where original Female_ID was NA:", nrow(All_data_v1  %>%
  filter(orphaned_revisions))))

# Generate new roster so I can manually doublecheck that there are no more mismatched IDs
female_roster_days_v1 <- All_data_v1 %>%
  group_by(Date, Dorm) %>%
    distinct(Female_ID, .keep_all = TRUE) %>%
  ungroup() %>%
  select(Date, Dorm, Female_ID, Plant, Leaf, Eggs) %>%
  filter(!is.na(Female_ID), !(Female_ID %in% c("E", "E?", "N", "0")), !grepl("M", Female_ID, ignore.case = TRUE))

female_roster_v1 <- female_roster_days_v1 %>%
  group_by(Dorm, Female_ID) %>%
    distinct(Female_ID) %>%
  ungroup()

data_revised_Female_locations_on_dates_v1 <- female_roster_days_v1 %>%
  group_by(row_number()) %>%
    mutate(location = ifelse(!is.na(Leaf),
                             paste0(c(Dorm, Plant, "_", Leaf), collapse = ""),
                             NA),
           Female_ID = paste0(c(Dorm, "_", Female_ID), collapse = "")) %>%
  ungroup() %>%
  select(Female_ID, location, Date) %>%
  spread(Date, location)

print("Number of unique female IDs were in original dataset vs. manually revised dataset:")
num_females_All_data <- female_roster_dupStatus %>% nrow()
num_females_All_data_revised <- female_roster_v1 %>% nrow()
print(paste("num_females_All_data:", num_females_All_data))
print(paste("num_females_All_data_revised:", num_females_All_data_revised))
```

### Plot the number of females over time.
```{r}
Num_females_eggs_v1 <- female_roster_days_v1 %>% # Note that this is not an accurate measure of the number of eggs since there are duplicate entries for the same leaf if more than one female per leaf
  group_by(Date, Dorm) %>%
    summarize(Num_females = sum(!is.na(Female_ID)), num_eggs = sum(!is.na(Eggs))) %>%
  ungroup()

# failed to visit all dorms on these days so they would uneven sampling
omit_days_ABCE = as_date(c("2019-06-02", "2019-06-03", "2019-06-05"))

Num_females_ABCE_v1 <- Num_females_eggs_v1 %>%
  filter(Dorm %in% c("A", "B", "C", "E")) %>%
  group_by(Date) %>%
  summarize(Num_females = sum(Num_females)) %>%
  ungroup() %>%
  filter(!(Date %in% omit_days_ABCE)) %>%
  mutate(year = "2019")

ggplot(data = Num_females_eggs_v1) +
  geom_line(aes(x = Date, y = Num_females, color = Dorm), size = 2)

ggplot(data = Num_females_ABCE_v1, aes(x = Date, y = Num_females)) +
  geom_line() +
  scale_y_continuous(limits = c(0,250))
```

# 2 - Manually check and revise egg initiation and hatching times reproducibly

*Note: This section saves many `.csv` files with tables to aid manual checks. In each case, the contents of these files were copied into the `data/Watershed_field_data_2019_ALL_local.xlsx` spreadsheet as new sheet at the time of initial analysis, revised manually as needed and subsequently read back in to this analysis script and used to revise the data object in the R environment. Every effort was made to keep the original field-collected dataseets unchanged in favor of programmatically revising the loading R object. In a few cases where this was not possible, the original spreadsheet was edited (with a note in the `Revisions` column). As such, newly generated check tables using this script may differ from the originals documented in `data/Watershed_field_data_2019_ALL_local.xlsx`, which preserve the original state of the data.*

## 2.1 - Flag cases where egg status is missing or inconsistent across multiple entries
(e.g. multiple females on same eggs, but only the first row was manually entered in the field)

I'll be redoing the same check many times so here's a function:
```{r}
egg_conflict_check <- function(dataset){
  egg_status <- dataset %>%
    group_by(row_number()) %>%
    filter(!Leaf %in% c("S","A"), !substring(Leaf, nchar(Leaf)) == "A") %>%
  group_by(Date, location) %>%
    distinct(Eggs, .keep_all = TRUE) %>%
    # mult entries for location/date but some are missing egg data
    mutate(eggs_need_filling = n() > 1) %>%
    # unique text entries for location/date
    mutate(num_unique_eggs = sum(!is.na(Eggs))) %>%
    # flag cases where more than one non-NA value unique values for Eggs
    mutate(egg_text_conflict = num_unique_eggs > 1) %>%  
    # flag cases where Egg status is ambiguous
    mutate(egg_status_missing = num_unique_eggs != 0 & Eggs %in% c("E?", "***")) %>% 
  ungroup() %>%
  select(Date, location, Eggs_status = Eggs, eggs_need_filling, egg_text_conflict, egg_status_missing, num_unique_eggs)
  return(egg_status)
}
```

```{r}
egg_status_v1_tmp <- egg_conflict_check(All_data_v1) %>%
  select(Date, location, Eggs_status, eggs_need_filling, egg_text_conflict, 
         egg_status_missing, num_unique_eggs)

# Flag any egg text conflicts or missing data that needs filling
egg_status_v1 <- egg_conflict_check(All_data_v1)

# Make dataframe to take missing values from
egg_fill_source <- egg_status_v1 %>%
  # keep only the Eggs values to fill missing data with for each location-time
  filter(eggs_need_filling, !egg_text_conflict, !is.na(Eggs_status)) %>%
  select(Date, location, Eggs_status, fill_from_src = eggs_need_filling)

# Join original dataset with new values such that missing values will be filled
# (but manually check that Eggs_filled is what you expect before replacing Eggs)
All_data_v2 <- All_data_v1 %>%
  left_join(egg_fill_source, by=c("Date", "location")) %>%
  mutate(Eggs_filled = ifelse(is.na(fill_from_src),
                              Eggs,
                              Eggs_status))

# Manually check that Eggs_filled is what you expect before replacing Eggs
All_data_v2 <- All_data_v2 %>% mutate(Eggs = Eggs_filled) %>% select(-Eggs_filled, -Eggs_status)
```

## 2.2 - Create tables to use for manually checking and revising egg status text conflict or missing data
```{r}
# Create table for entries text conflict that need to be resolved
egg_text_conflict_data_v1 <- All_data_v2 %>% # egg_text_conflict: 39 on 2019/09/24
  left_join(egg_status_v1, by = c("Date", "location", "Eggs" = "Eggs_status")) %>%
  filter(egg_text_conflict) %>%
  select(Date, Dorm, Plant, Leaf, Eggs)
write_csv(egg_text_conflict_data_v1, here("data/manual_check/egg_text_conflict_data.csv"))

# Create table for entries with missing data that need to be resolved
egg_status_missing_data_v1 <- All_data_v2 %>% # egg_status_missing: 219 on 2019/09/24
  left_join(egg_status_v1, by = c("Date", "location", "Eggs" = "Eggs_status")) %>%
  filter(egg_status_missing, !grepl('NA|M', Female_ID)) %>%
  select(Date, Dorm, Plant, Leaf, Eggs)
write_csv(egg_status_missing_data_v1, here("data/manual_check/egg_status_missing_data.csv"))

print("Conflicts and missing data before implementing manual revisions:")
print(paste("egg_text_conflict_data:", nrow(egg_text_conflict_data_v1)))
print(paste("egg_status_missing_data:", nrow(egg_status_missing_data_v1)))
```

## 2.3 - Import and implement `egg status missing data` revisions
`import "egg_stats_missing_data revision" > implement revisions > `
   `standardize the L6A8 vs. L6a8 vs. 6a8 format > get summary of start of egg number over time > `
   `define a (soft?) cuttoff for settling *** ambiguities > implement cuttoff > proceed to checking clutch lifetime`

```{r}
# Read in manual revisons table
egg_status_revisions <- read_xlsx(in_filename, sheet = "egg_stats_missing_data revision", col_types = c("date", "text", "text", "text","text", "text", "text", "date")) %>%
  mutate(Date = as_date(Date)) %>%
  select(-`Date revised`)

# Check revisions table for duplicate (i.e. overwriting) entries
egg_stats_revision_duplicates <- egg_status_revisions %>%
  group_by(Date, Dorm, Plant, Leaf) %>%
    mutate(n_rows = n()) %>%
  ungroup() %>%
  arrange(Dorm, Plant, Leaf, Date) %>%
  filter(n_rows > 1)
print(paste("Number of duplicate rows in revisions sheet:", nrow(egg_stats_revision_duplicates)))

# Implement revisions from revisions table
All_data_v3 <- All_data_v2 %>% 
  rename(Eggs_v2 = Eggs) %>%
  full_join(egg_status_revisions, by = c("Date", "Dorm", "Plant", "Leaf")) %>%
  rename(Eggs_v2_xls = Eggs, Notes = Notes.x) %>%
  # need to check whether locations are properly assigned to each revision
  mutate(Eggs_v3 = ifelse(Eggs_revisions != "IGNORE" & !is.na(Eggs_revisions),
                            Eggs_revisions,
                            Eggs_v2)) %>%
  select(-Num_adults, -Description, -`Paired with`, -Time, -Notes.y, -`Dup?`, -`row_number()`,
         -fill_from_src, -Eggs_v2_xls, -Eggs_revisions, -orphaned_revisions, -Fem_IDn,
         -`To ID`, -n_female_dupes, -female_dup_order, -Female_ID_revision_notes, -Eggs_v2) %>%
  select(Date, Dorm, Plant, Leaf, location, Female_ID, Eggs = Eggs_v3,
         N1, N2, N5, New_eA, Old_eA, nymph_origin, everything())

# Check whether revisions implementation worked by rerunning inconsistency checks
# Flag any egg text conflicts or missing data that needs filling
egg_status_v2 <- egg_conflict_check(All_data_v3)

# Conflicts and missing data after implementing manual revisions
egg_text_conflict_data_v2 <- All_data_v3 %>%
  group_by(row_number()) %>%
  mutate(Female_ID = paste0(c(Dorm, "_", Female_ID), collapse = "")) %>%
  ungroup() %>%
  left_join(egg_status_v2, by = c("Date", "location", "Eggs" = "Eggs_status")) %>%
  filter(egg_text_conflict) %>%
  select(Date, Dorm, Plant, Leaf, Eggs)

egg_status_missing_data_v2 <- All_data_v3 %>%
  group_by(row_number()) %>%
  mutate(Female_ID = paste0(c(Dorm, "_", Female_ID), collapse = "")) %>%
  ungroup() %>%
  left_join(egg_status_v2, by = c("Date", "location", "Eggs" = "Eggs_status")) %>%
  filter(egg_status_missing, !grepl('NA|M', Female_ID)) %>%
  select(Date, Dorm, Plant, Leaf, Eggs) #%>% print(n=Inf)

print("Conflicts and missing data after implementing manual revisions:")
print(paste("egg_text_conflict_data_eggs_revised:", nrow(egg_text_conflict_data_v2)))
print(paste("egg_status_missing_data_eggs_revised:", nrow(egg_status_missing_data_v2)))

# 20200326 version was used
write_csv(egg_status_missing_data_eggs_revised, here("data/manual_check/egg_status_missing_data_eggs_revised.csv"))
```

## 2.4 - Import and implement `egg measures` revisions
```{r}
# Read in manual revisons table
egg_measures_revisions <- read_xlsx(in_filename, sheet = "egg_measures_revisions", col_types = c("text", "date", "text", "text","text"), na = c("", "NA")) %>%
  mutate(Date = as_date(Date)) %>%
  select(-Notes)

# Check revisions table for mismatched entries
egg_measures_revisions_mismatched <- All_data_v3 %>%
  full_join(egg_measures_revisions, by = c("location", "Date")) %>%
  semi_join(egg_measures_revisions, by = c("location", "Date")) %>%
  filter(is.na(Eggs) | Eggs != `Eggs from`) %>%
  select(Date, Dorm, Plant, Leaf, location, Female_ID, Eggs, `Eggs from`, `Eggs to`)
print(paste("egg_measures_revisions_mismatched: ", nrow(egg_measures_revisions_mismatched)))

# Implement revisions from revisions table
All_data_v4 <- All_data_v3 %>%
  full_join(egg_measures_revisions, by = c("location", "Date")) %>%
  mutate(Eggs_match_revision = ifelse(!is.na(Eggs) & !is.na(`Eggs from`) & Eggs == `Eggs from`,
                       TRUE,
                       FALSE),
         Eggs_v5 = ifelse(Eggs_match_revision,
                       `Eggs to`,
                       Eggs)) %>%
  select(-Eggs, -`Eggs from`, -`Eggs to`, -Eggs_match_revision) %>%
  select(Date, Dorm, Plant, Leaf, location, Female_ID, Eggs = Eggs_v5,
         N1, N2, N5, New_eA, Old_eA, nymph_origin, everything())

# Check whether revisions implementation worked by rerunning inconsistency checks
egg_status_v3 <- egg_conflict_check(All_data_v4)

egg_text_conflict_data_v3 <- All_data_v4 %>%
  group_by(row_number()) %>%
  mutate(Female_ID = paste0(c(Dorm, "_", Female_ID), collapse = "")) %>%
  ungroup() %>%
  left_join(egg_status_v3, by = c("Date", "location", "Eggs" = "Eggs_status")) %>%
  filter(egg_text_conflict) %>%
  select(Date, Dorm, Plant, Leaf, Eggs)

egg_status_missing_data_v3 <- All_data_v4 %>%
  group_by(row_number()) %>%
  mutate(Female_ID = paste0(c(Dorm, "_", Female_ID), collapse = "")) %>%
  ungroup() %>%
  left_join(egg_status_v3, by = c("Date", "location", "Eggs" = "Eggs_status")) %>%
  filter(egg_status_missing, !grepl('NA|M', Female_ID)) %>%
  select(Date, Dorm, Plant, Leaf, Eggs) #%>% print(n=Inf)

print(paste("egg_text_conflict_data_eggs_revised:", nrow(egg_text_conflict_data_v3)))
print(paste("egg_status_missing_data_eggs_revised:", nrow(egg_status_missing_data_v3)))

#write_csv(egg_status_missing_data_eggs_revised, "egg_status_missing_data_eggs_revised_20200326.csv")

```

### Omit inconsistent egg measures from 7/4
Luke used a much more conservative metric for number of eggs on 7/4; convert these measures to "E" for Dorms A, E, F
```{r}
egg_status_v4 <- egg_status_v3 %>%
  mutate(Eggs_status = ifelse(Date == as.Date("2019-07-04") & grepl("^(A|E|F)", location) & grepl("[0-9]e ", Eggs_status),
                              "E",
                              Eggs_status))
```

## 2.5 - Create `revised_clutch_status_on_dates` table for second round of manual checking
Create female locations on dates table for manual checking (as for Female IDs) and get a rough count of the number of clutches in this first round.
```{r}
# Only include clutches, not leaves that never had eggs and not leaves that only had nymphs
any_eggs_not_just_nymphs <- egg_status_v4 %>%
  select(location, Clutch_status = Eggs_status, Date) %>%
  group_by(location) %>%
    summarize(any_eggs_or_nymphs = any(!is.na(Clutch_status)),
              any_eggs_not_just_nymphs = any(!is.na(Clutch_status) &
                                               !(Clutch_status %in% c("N","0")))) %>%
  ungroup() %>%
  filter(any_eggs_not_just_nymphs)

revised_clutch_status_on_dates <- egg_status_v4 %>%
  left_join(any_eggs_not_just_nymphs, by = c("location")) %>%
  filter(any_eggs_not_just_nymphs) %>%
  select(location, Clutch_status = Eggs_status, Date) %>%
  spread(key = Date, Clutch_status)

# 402 clutches in revised data as of 2019/09/25
print(paste(nrow(revised_clutch_status_on_dates), "clutches in revised data"))
```

## 2.6 - Define initiation dates (v1) to help with manual checks
First pass initiation dates, before filling nymphs in duplicate entries and manual checks
```{r}
## 1: define initiation date, hatch date (taking into account "not hatched" notes)
clutch_status_v1 <- egg_status_v4 %>%
  left_join(any_eggs_not_just_nymphs, by = c("location")) %>%
  filter(any_eggs_not_just_nymphs) %>%
  select(location, Clutch_status = Eggs_status, Date) %>%
  mutate(Egg_measures = ifelse(grepl("[1234567890]e", Clutch_status),
                                Clutch_status,
                               ifelse(!is.na(as.integer(Clutch_status)),
                                      Clutch_status,
                                      NA_character_)
                               )
         ) %>%
  separate(Egg_measures, into = c("egg_num", "egg_len"), sep = "e", remove = FALSE) %>%
  mutate(egg_num = as.integer(str_trim(egg_num)), 
         egg_len = as.integer(str_trim(egg_len))) #%>%
 # filter(!is.na(Egg_measures) & is.na(egg_len)) # check this if change anything upstream

# 369 clutches had defined initiation dates as of 2019/09/25
initiation_dates_v1 <- clutch_status_v1 %>%
  filter(!is.na(Egg_measures) & Egg_measures != "0" | str_trim(Clutch_status, side = "both") == "E") %>%
  group_by(location) %>%
    filter(row_number() == 1) %>%
  ungroup() %>%
  select(location, initiation_date = Date)

print(paste(nrow(initiation_dates_v1), "clutches have defined initiation dates"))

# 33 clutches didn't have an initiation date as of 2019/09/25 because they had no days where the eggs were measured
#clutch_status_v1 %>% anti_join(initiation_dates) %>% distinct(location)
#clutch_status_v1 %>% anti_join(initiation_dates) %>% arrange(location, Date) %>% print(n=Inf)

print(paste(nrow(clutch_status_v1 %>% anti_join(initiation_dates_v1) %>% distinct(location)), 
            "clutches didn't have an initiation date because they had no days where the eggs were measured"))

```

## 2.7 - Fix cases where nymph status is missing or inconsistent across multiple entries
Similar process as with egg status above, but generalizing for differen columns in tibble. 
Default is to group by date and location, but `perPlant`=TRUE allows to group by date and plant.
```{r}
text_conflict_check <- function(tibble, N, perPlant=FALSE){
  # N = N1, N2, N5, NOr, Ants_on_leaf, Ants_on_plant (perPlant=TRUE)
  require(dplyr)
  if(perPlant == FALSE) {
    # N = Eggs, N1, N2, N5, NOr, Ants_on_leaf
    N_status <- tibble %>%
      filter(!Leaf %in% c("S","A"), !substring(Leaf, nchar(Leaf)) == "A") %>%
      group_by(Date, location) %>%
      distinct((!!as.name(N)), .keep_all = TRUE) %>%
      # mult entries for location/date but some are missing nymph data
      mutate(N_need_filling = n() > 1) %>%
      # unique text entries for location/date
      mutate(num_unique_N = sum(!is.na(!!as.name(N)))) %>%
      # flag cases where more than one non-NA value unique values for nymph
      mutate(N_text_conflict = num_unique_N > 1) %>%
      # flag cases where nymph status is ambiguous
      mutate(N_status_missing = !is.na(!!as.name(N)) & 
               is.na(suppressWarnings(as.integer(!!as.name(N))))) %>% 
      ungroup() %>%
      select(Date, location, N, N_need_filling, N_text_conflict, N_status_missing, num_unique_N)
  } else {
    # N = Ants_on_plant (perPlant=TRUE)
    N_status <- tibble %>%
      group_by(Date, Dorm, Plant) %>%
      distinct((!!as.name(N)), .keep_all = TRUE) %>%
      mutate(N_need_filling = n() > 1) %>%
      mutate(num_unique_N = sum(!is.na(!!as.name(N)))) %>%
      mutate(N_text_conflict = num_unique_N > 1) %>%
      mutate(N_status_missing = !is.na(!!as.name(N)) & 
               is.na(suppressWarnings(as.integer(!!as.name(N))))) %>% 
      ungroup() %>%
      select(Date, Dorm, Plant, N, N_need_filling, N_text_conflict, N_status_missing, num_unique_N)
  }
  return(N_status)
}
```

```{r}
N1_status <- text_conflict_check(All_data_v4, N = "N1") %>%
  select(Date, location, N1, N1_need_filling = N_need_filling, 
         N1_text_conflict = N_text_conflict, N1_status_missing = N_status_missing)

print(paste("N1_need_filling: ", nrow(N1_status %>% filter(N1_need_filling))))
print(paste("N1_text_conflict: ", nrow(N1_status %>% filter(N1_text_conflict))))
print(paste("N1_status_missing: ", nrow(N1_status %>% filter(N1_status_missing))))

N2_status <- text_conflict_check(All_data_v4, N = "N2") %>%
  select(Date, location, N2, N2_need_filling = N_need_filling, 
         N2_text_conflict = N_text_conflict, N2_status_missing = N_status_missing)

print(paste("N2_need_filling: ", nrow(N2_status %>% filter(N2_need_filling))))
print(paste("N2_text_conflict: ", nrow(N2_status %>% filter(N2_text_conflict))))
print(paste("N2_status_missing: ", nrow(N2_status %>% filter(N2_status_missing))))

N5_status <- text_conflict_check(All_data_v4, N = "N5") %>%
  select(Date, location, N5, N5_need_filling = N_need_filling, 
         N5_text_conflict = N_text_conflict, N5_status_missing = N_status_missing)

print(paste("N5_need_filling: ", nrow(N5_status %>% filter(N5_need_filling))))
print(paste("N5_text_conflict: ", nrow(N5_status %>% filter(N5_text_conflict))))
print(paste("N5_status_missing: ", nrow(N5_status %>% filter(N5_status_missing))))

# Adding nymph origin to nymph status so that I can check for ambiguous nymph origins with clutch status and better filter problematic clutches for calculating hatch success and nymph survival
NOr_status <- text_conflict_check(All_data_v4, N = "nymph_origin") %>%
  # flag cases where nymph_origin status is ambiguous
  group_by(Date, location) %>%
  mutate(NOr_ambiguous = !is.na(nymph_origin) & 
           suppressWarnings(is.na(as.integer(nymph_origin)))) %>% 
  ungroup() %>%
  select(Date, location, nymph_origin, NOr_need_filling = N_need_filling, 
         NOr_text_conflict = N_text_conflict, NOr_ambiguous)

nymph_status <- N1_status %>% 
  left_join(N2_status) %>% 
  left_join(N5_status) %>% 
  left_join(NOr_status)

nymph_status_to_resolve <- nymph_status  %>% # should only include a handful of entries with "?" ambiguous entries for N1 or N2 (because did the revions by hand on 2019/09/26)
  group_by(row_number()) %>%
    filter(any(N1_need_filling, N1_text_conflict, N1_status_missing,
               N2_need_filling, N2_text_conflict, N2_status_missing,
               N5_need_filling, N5_text_conflict, N5_status_missing)) %>%
  ungroup()
# write_csv(nymph_status_to_resolve, "nymph_status_to_resolve.csv") ## manually added this to "nymph_status revisions" sheet in "Watershed_field_data_2019_ALL_local" and manually revised raw data 2019/09/26

print(paste("nymph_status_to_resolve: ", nrow(nymph_status_to_resolve)))

# checking number of ambiguous entries that need to be resolved
nymph_text_conflict_data <- All_data_v4 %>% # nymph_text_conflict: 10 on 2019/09/24; 0 on 2019/09/26
  left_join(N1_status, by = c("Date", "location", "N1")) %>%
  left_join(N2_status, by = c("Date", "location", "N2")) %>%
  left_join(N5_status, by = c("Date", "location", "N5")) %>%
  group_by(row_number()) %>% 
    filter(any(c(N1_text_conflict, N2_text_conflict, N5_text_conflict))) %>%
  ungroup() %>%
  select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_text_conflict, N2_text_conflict, N5_text_conflict)
#write_csv(egg_text_conflict_data, "egg_text_conflict_data.csv")

nymph_status_missing_data <- All_data_v4 %>% # nymph_status_missing: 17 on 2019/09/24; 5 on 2019/09/26 (all ok to ignore)
  left_join(N1_status, by = c("Date", "location", "N1")) %>%
  left_join(N2_status, by = c("Date", "location", "N2")) %>%
  left_join(N5_status, by = c("Date", "location", "N5")) %>%
  group_by(row_number()) %>% 
  filter(any(c(N1_status_missing, N2_status_missing, N5_status_missing))) %>%
  ungroup() %>%
  select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_status_missing, N2_status_missing, N5_status_missing)
#write_csv(egg_status_missing_data, "egg_status_missing_data.csv")

print("checking number of ambiguous nymph entries that need to be resolved:")
print(paste("nymph_text_conflict_data: ", nrow(nymph_text_conflict_data)))
print(paste("nymph_status_missing_data: ", nrow(nymph_status_missing_data)))

# clutch_status_v1 should have no duplicate entries for location and date, so I can safely left_join the nymph status information
print("clutch_status_v1 should have no duplicate entries for location and date, so I can safely left_join the nymph status information")
print(paste("instances with more than one entry per location and date for in clutch_status_v1: ",
            nrow(clutch_status_v1 %>% group_by(Date, location) %>% summarize(n = n()) %>% ungroup() %>% filter(n < 1))))
```

## 2.8 - Define hatch dates (v1) to help with manual checks
Define hatch date for this dataset:
First day that n1 appear unless "not hatched" in notes -> check manually
  - roughly: filter(!is.na(N1) & !grepl("not hatched", Notes))
```{r}
clutch_nymph_status_v1 <- clutch_status_v1 %>% 
  left_join(nymph_status, by = c("Date", "location")) %>%
  select(location, Date, Clutch_status, Egg_measures, egg_num, egg_len, N1, N2, N5, nymph_origin, NOr_ambiguous) %>%
  arrange(location, Date)

hatch_dates_v1 <- clutch_nymph_status_v1 %>%
  filter(!is.na(as.integer(N1)) & N1 != 0) %>% 
  # & notes that don't mention "not hatched yet" <- manually checked below with "check_hatch_date" and revised with "check_hatch_date_revisions"
  group_by(location) %>%
    filter(row_number() == 1) %>%
  ungroup() %>%
  select(location, hatch_date = Date)

print("Hatch_dates v1 (filled in nymphs but not yet incorporating 'not hatched' notes):")
print(paste("hatch_dates: ", nrow(hatch_dates_v1)))
```

## 2.9 - Manually check hatch dates using the "not hatched" notes from field using `check_hatch_date` sheet
Use the "not hatched" notes (from original field notes; typically b/c nymphs present but they are immigrants, not hatched from the focal clutch) to inform first pass of hatch date revisions
Again these changes were specified in the `check_hatch_date` sheet and are applied here without changing the original data file.
```{r}
# Create `check_hatch_date` sheet for checking "not hatched" notes and suggesting manual revisions
check_hatch_date <- All_data_v4  %>%
  filter(grepl("not", Notes, ignore.case = TRUE), grepl("hatch", Notes, ignore.case = TRUE)) %>%
  distinct(location)
#write_csv(check_hatch_date, "check_hatch_date_tmp.csv")
```

### Revise initiation dates and hatch dates (v2) based on `check_hatch_date` manual check
```{r}
# Revise initiation dates and hatch dates based on `check_hatch_date` manual check
check_hatch_date_revisions <- read_xlsx(in_filename, sheet = "check_hatch_date", col_types = c("text", "text", "date", "date", "text", "text", "text", "text")) %>%
  select(location, revised_hatch_date_date, revised_hatch_date_text) %>%
  mutate(revised_hatch_date_date = date(revised_hatch_date_date))

hatch_dates_v2 <- hatch_dates_v1 %>% 
  left_join(check_hatch_date_revisions, by="location") %>%
  mutate(hatch_date = if_else(!is.na(revised_hatch_date_date),
                              revised_hatch_date_date,
                              if_else(revised_hatch_date_text %in% c("never hatched", "no eggs"),
                                      as.Date(NA),
                                      hatch_date))) %>%
  select(location, hatch_date)

# Just checking that all of the clutches determined to have no eggs don't have initiation dates
# (this shouldn't do anything if so)
initiation_dates_v2 <- initiation_dates_v1 %>% 
  left_join(check_hatch_date_revisions, by="location") %>%
  mutate(initiation_date = if_else(!is.na(revised_hatch_date_text) & revised_hatch_date_text == "no eggs",
                            as.Date(NA),
                            initiation_date)) %>%
  select(location, initiation_date)

print("Hatch_dates (v2) after incorporating 'not hatched' notes:")
print(paste("hatch_dates_v2: ", nrow(hatch_dates_v2)))
print("Initiation_dates (v2) after manually checking:")
print(paste("initiation_dates_v2: ", nrow(initiation_dates_v2)))
```

## 2.10 - Manually check clutches with short initiation-hatch intervals
Changes were specified in the `short_unhatched_days_check` sheet and are applied here without changing the original data file.

Criteria used to manually flag unusually short init-hatch intervals:
- outlier starting egg number (suggests I'm missing first obs)
- spurious 0 entry for Eggs
- immigration of N1 from another leaf
- mother not accounted for on previous days

## 2.11 - Use `short_unhatched_days_check` sheet to revise initiation and hatch dates (v3)
*NOTE:* I just use these revisions to adjust the female guarding duration data, rather than revising the "All_data_revised_eggs_revised". *the All_data tibble is thus not a perfect source of nymph counts*

### Implement initiation date (v3) revisions
Where it was obvious that the initiation date was overlooked in the field (based on above criteria), I specified that an "E" be entered at that location on the suspected initiation date.
```{r}
# Use "short_unhatched_days_check" sheet to further revise hatch dates
short_unhatched_check_revisions <- read_xlsx(in_filename, sheet = "short_unhatched_days_check") %>%#, col_types = c("text", "text", "date", "date", "text", "text", "text", "text")) %>%
  select(location, Egg_revisions, Hatch_revised, Initiation_revised, Female_revision_ID, Female_revision_date, Omit_for_abandon_time)

short_unhatched_check_revisions_eggs <- short_unhatched_check_revisions %>%
  filter(grepl("no eggs|initiated|hatched",Egg_revisions) | Omit_for_abandon_time == "yes", !grepl("manually|fixed", Egg_revisions)) %>% print(n=Inf)

initiation_dates_v3 <- initiation_dates_v2 %>% 
  left_join(short_unhatched_check_revisions, by="location") %>%
  mutate(initiation_date_revised = if_else(grepl("no eggs|initiated|hatched",Egg_revisions) & !grepl("manually|fixed", Egg_revisions),
                                      if_else(Egg_revisions == "no eggs",
                                              as.Date(NA),
                                              if_else(!is.na(Initiation_revised),
                                                      as.Date(Initiation_revised),
                                                      initiation_date)
                                      ),
                                      initiation_date)) %>%
  filter(is.na(Omit_for_abandon_time)) %>%
  arrange(location) %>%
  select(location, initiation_date, initiation_date_revised) %>% # check that this worked before proceeding!
  select(location, initiation_date = initiation_date_revised)

print("Initiation_dates (v3) after manually checking unusually short unhatched days:")
print(paste("initiation_dates_v3: ", nrow(initiation_dates_v3)))
```

### Implement hatch date (v3) revisions
Where it was obvious that the hatch date (v2) was incorrect (e.g. immigration of N1), I specified a new hatch date (v3). *Note that only hatch date is thus revised, and not the nymph status in `All_data`.* _So if I need to have accurate nymph status on specific dates for downstream analysis, I would need to adjust this to add a "N" or some similar nymph placeholder for those location-dates._
```{r}
hatch_dates_v3 <- hatch_dates_v2 %>% 
  left_join(short_unhatched_check_revisions, by="location") %>%
  group_by(location) %>%
  mutate(hatch_date_revised = if_else(grepl("no eggs|initiated|hatched",Egg_revisions) & !grepl("manually|fixed", Egg_revisions),
                              if_else(Egg_revisions %in% c("never hatched", "no eggs"),
                                      as.Date(NA),
                                      if_else(!is.na(Hatch_revised),
                                              as.Date(Hatch_revised),
                                              hatch_date)
                                      ),
                              hatch_date)) %>%
  ungroup() %>%
  filter(is.na(Omit_for_abandon_time)) %>%
  select(location, hatch_date, hatch_date_revised) %>% # check that this worked before proceeding!
  select(location, hatch_date = hatch_date_revised)

print("Hatch_dates (v3) after manually checking unusually short unhatched days:")
print(paste("hatch_dates_v3: ", nrow(hatch_dates_v3)))
```

### Specify which clutches should be omitted from desertion date analyses
- If we likely missed first several days of clutch, unclear how early initiated, and unclear who was present at initiation.
- Or unclear whether eggs never hatched
```{r}
omit_for_abandon_time <- short_unhatched_check_revisions %>%
  filter(!is.na(Omit_for_abandon_time)) %>%
  select(location, Omit_for_abandon_time)
print(paste("Clutches with ambiguous init/hatch dates to omit from desertion date analysis: ", nrow(omit_for_abandon_time)))
```

## 2.10 - Use `short_unhatched_days_check` sheet to revise Female IDs
Add females to `All_data` where they were not originally observed based on evidence from short init-hatch interval.
When a female was guarding shortly after initiation but neither the eggs nor the mother was observed on the revised day of initiation, it was assumed that we overlookoed that location in the field on that day, so she was added accordingly. These revisions are tracked in the `short_unhatched_days_check` sheet.
```{r}
# Add females from short_unhatched_check_revisions to `All_data` tibble
short_unhatched_check_revisions_moms <- short_unhatched_check_revisions %>% 
  filter(!is.na(Female_revision_ID) & Female_revision_ID != "?") %>%
  separate_rows(Female_revision_date, sep = ",") %>%
  mutate(Female_revision_date = as.Date(str_trim(Female_revision_date, side = "both"))) %>%
  select(Date = Female_revision_date, location, Female_revision_ID) %>%
  separate(location, c("DormPlant", "Leaf"), "_", remove = FALSE) %>%
  mutate(Dorm = substr(DormPlant, 1,1),
         Plant = substring(DormPlant, 2)) %>%
  select(Date, location_revision = location, Dorm, Plant, Leaf, Female_revision_ID)

All_data_v5 <- All_data_v4 %>% 
  full_join(short_unhatched_check_revisions_moms, by = c("Date", "Dorm", "Plant", "Leaf")) %>%
  mutate(Female_ID = ifelse(!is.na(Female_revision_ID),
                            paste0(Dorm, "_", Female_revision_ID),
                            ifelse(!is.na(Female_ID),
                                   paste0(Dorm, "_", Female_ID),
                                   NA)),
         location = ifelse(is.na(location_revision),
                           location,
                           ifelse(is.na(location),
                                  location_revision,
                                  NA)),
         Eggs = ifelse(!is.na(Female_revision_ID),
                       "E",
                       Eggs)) %>%
  select(-Female_revision_ID, -location_revision)
```

## 2.11 Update clutch_status data using revised `All_data` table
```{r}
egg_status_v5 <- egg_conflict_check(All_data_v5) %>%
  select(Date, location, Eggs_status, eggs_need_filling, egg_text_conflict, egg_status_missing) %>%
  # Luke used a much more conservative metric for number of eggs on 7/4; convert these measures to "E" for Dorms A, E, F
  mutate(Eggs_status = ifelse(Date == as.Date("2019-07-04") & grepl("^(A|E|F)", location) & grepl("[0-9]e ", Eggs_status),"E",Eggs_status))

# Only include clutches, not leaves that never had eggs and not leaves that only had nymphs
any_eggs_not_just_nymphs_v2 <- egg_status_v5 %>%
  select(location, Clutch_status = Eggs_status, Date) %>%
  group_by(location) %>%
    summarize(any_eggs_or_nymphs = any(!is.na(Clutch_status)),
              any_eggs_not_just_nymphs = any(!is.na(Clutch_status) &
                                               !(Clutch_status %in% c("N","0")))) %>%
  ungroup() %>%
  filter(any_eggs_not_just_nymphs)

# define initiation date, hatch date
clutch_status_v2 <- egg_status_v4 %>%
  left_join(any_eggs_not_just_nymphs_v2, by = c("location")) %>%
  filter(any_eggs_not_just_nymphs) %>%
  select(location, Clutch_status = Eggs_status, Date) %>%
  mutate(Egg_measures = ifelse(grepl("[1234567890]e", Clutch_status),
                                Clutch_status,
                               ifelse(!is.na(as.integer(Clutch_status)),
                                      Clutch_status,
                                      NA_character_)
                               )
         ) %>%
  separate(Egg_measures, into = c("egg_num", "egg_len"), sep = "e", remove = FALSE) %>%
  mutate(egg_num = as.integer(str_trim(egg_num)), 
         egg_len = as.integer(str_trim(egg_len))) #%>%
 # filter(!is.na(Egg_measures) & is.na(egg_len)) # check this if change anything upstream

clutch_nymph_status_v2 <- clutch_status_v2 %>% 
  left_join(nymph_status, by = c("Date", "location")) %>%
  select(location, Date, Clutch_status, Egg_measures, egg_num, egg_len, N1, N2, N5, nymph_origin, nymph_origin, NOr_ambiguous) %>%
  arrange(location, Date)
```

### 2023-07-22 scripts/Publilia-01-qc.Rmd
first full draft of Publilia-01-qc.Rmd script, deleted intermediate checks (the originals of which are all included in the `All_data` .xlsx as sheets)

--- 2023-07-22 scripts/01-qc.Rmd
@@
 ---
-title: '01 - TreehopperFitness: Data prep'
+title: '01 - TreehopperFitness: Quality control'
 author: "Micah Fletcher"
@@
 ```
-
-<!-- This file will not execute by itself. It should be called within the  -->
-<!-- runfile to render the final report. You can arrange figures, add explanations, -->
-<!-- and do other aesthetic tweaks here. -->
 
@@
 # used 20200319 version
-write_csv(Days_observed_dupStatus, here("data/manual_check/Days_observed_dupStatus.csv"))
+# write_csv(Days_observed_dupStatus, here("data/manual_check/Days_observed_dupStatus.csv"))
 ```
@@
   select(Date, Dorm, Plant, Leaf, Eggs)
-write_csv(egg_text_conflict_data_v1, here("data/manual_check/egg_text_conflict_data.csv"))
+# write_csv(egg_text_conflict_data_v1, here("data/manual_check/egg_text_conflict_data.csv"))
 
@@
   select(Date, Dorm, Plant, Leaf, Eggs)
-write_csv(egg_status_missing_data_v1, here("data/manual_check/egg_status_missing_data.csv"))
+# write_csv(egg_status_missing_data_v1, here("data/manual_check/egg_status_missing_data.csv"))
 
@@
 # 20200326 version was used
-write_csv(egg_status_missing_data_eggs_revised, here("data/manual_check/egg_status_missing_data_eggs_revised.csv"))
+# write_csv(egg_status_missing_data_eggs_revised, here("data/manual_check/egg_status_missing_data_eggs_revised.csv"))
 ```
@@
 
-#write_csv(egg_status_missing_data_eggs_revised, "egg_status_missing_data_eggs_revised_20200326.csv")
-
+# 20200326 version was used
+# write_csv(egg_status_missing_data_eggs_revised, here("data/manual_check/egg_status_missing_data_eggs_revised.csv")
 ```
@@
   ungroup()
-# write_csv(nymph_status_to_resolve, "nymph_status_to_resolve.csv") ## manually added this to "nymph_status revisions" sheet in "Watershed_field_data_2019_ALL_local" and manually revised raw data 2019/09/26
+# write_csv(nymph_status_to_resolve, here("data/manual_check/nymph_status_to_resolve.csv") ## manually added this to "nymph_status revisions" sheet in "Watershed_field_data_2019_ALL_local" and manually revised raw data 2019/09/26
 
@@
   select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_text_conflict, N2_text_conflict, N5_text_conflict)
-#write_csv(egg_text_conflict_data, "egg_text_conflict_data.csv")
+# write_csv(egg_text_conflict_data, "egg_text_conflict_data.csv")
 
@@
   select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_status_missing, N2_status_missing, N5_status_missing)
-#write_csv(egg_status_missing_data, "egg_status_missing_data.csv")
+# write_csv(egg_status_missing_data, "egg_status_missing_data.csv")
 
@@
   distinct(location)
-#write_csv(check_hatch_date, "check_hatch_date_tmp.csv")
+# write_csv(check_hatch_date, "check_hatch_date_tmp.csv")
 ```
@@
 ```
+
+# 3 - Revise ant data reproducibly
+Revised ant data and updated All_data_v5 to All_data_v6
+Note that the only changes from All_data_v5 to All_data_v6 were adding columns for ant data and all variables derived from All_data_v5 should be safe to left_join with All_data_v6
+
+## 3.1 - Fill empty entries and resolve text conflicts
+As for eggs and nymphs above
+```{r}
+## find plants where ants were not filled in for all duplicate leaf or plant entries
+## for duplicate plant entries
+plant_ants_flagged_v1 <- text_conflict_check(All_data_v5, N="Ants_on_plant", perPlant=TRUE) %>%
+  select(Date, Dorm, Plant, Ants_on_plant, 
+         plant_ants_need_filling = N_need_filling,
+         plant_ants_text_conflict = N_text_conflict,
+         num_unique_plant_ants = num_unique_N)
+
+plant_ants_fill_source_v1 <- plant_ants_flagged_v1 %>%
+  filter(plant_ants_need_filling, !plant_ants_text_conflict, !is.na(Ants_on_plant)) %>%
+  select(Date, Dorm, Plant, Ants_on_plant_fill = Ants_on_plant, plant_ants_fill_from_src = plant_ants_need_filling)
+
+All_data_v5_plant_ants_v1 <- All_data_v5 %>%
+  left_join(plant_ants_fill_source_v1, by=c("Date", "Dorm", "Plant")) %>%
+  mutate(Ants_on_plant_filled = ifelse(is.na(plant_ants_fill_from_src),
+                              Ants_on_plant,
+                              Ants_on_plant_fill))
+
+# manually check that Ants_on_plant_filled is what you expect before replacing Ants_on_plant
+All_data_v5_plant_ants_v1 <- All_data_v5_plant_ants_v1  %>% mutate(Ants_on_plant = Ants_on_plant_filled) %>% select(-Ants_on_plant_filled)
+
+## for duplicate leaf entries
+leaf_ants_flagged_v1 <- text_conflict_check(All_data_v5, N="Ants_on_leaf", perPlant=FALSE) %>%
+  select(Date, location, Ants_on_leaf,
+         leaf_ants_need_filling = N_need_filling,
+         leaf_ants_text_conflict = N_text_conflict,
+         num_unique_leaf_ants = num_unique_N)
+
+leaf_ants_fill_source_v1 <- leaf_ants_flagged_v1 %>%
+  filter(leaf_ants_need_filling, !leaf_ants_text_conflict, !is.na(Ants_on_leaf)) %>%
+  select(Date, location, Ants_on_leaf_fill = Ants_on_leaf, leaf_ants_fill_from_src = leaf_ants_need_filling)
+
+All_data_v5_plant_leaf_ants_v1 <- All_data_v5_plant_ants_v1 %>%
+  left_join(leaf_ants_fill_source_v1, by=c("Date", "location")) %>%
+  mutate(Ants_on_leaf_filled = ifelse(is.na(leaf_ants_fill_from_src),
+                                       Ants_on_leaf,
+                                       Ants_on_leaf_fill))
+
+# manually check that Ants_on_leaf_filled is what you expect before replacing Ants_on_leaf
+All_data_v5_plant_leaf_ants_v2 <- All_data_v5_plant_leaf_ants_v1 %>% mutate(Ants_on_leaf = Ants_on_leaf_filled) %>% select(-Ants_on_leaf_filled)
+```
+
+## 3.2 - Check that filled empty entries and text conflicts have been resolved
+```{r}
+# check that the automatic filling worked and address the text conflicts manually in a separate spreadsheet
+plant_ants_flagged_v2 <- text_conflict_check(All_data_v5_plant_leaf_ants_v2,
+                                             N="Ants_on_plant", perPlant=TRUE) %>%
+  select(Date, Dorm, Plant, Ants_on_plant, 
+         plant_ants_need_filling = N_need_filling,
+         plant_ants_text_conflict = N_text_conflict,
+         num_unique_plant_ants = num_unique_N)
+
+## for duplicate leaf entries
+leaf_ants_flagged_v2 <- text_conflict_check(All_data_v5_plant_leaf_ants_v2,
+                                            N="Ants_on_leaf", perPlant=FALSE) %>%
+  select(Date, location, Ants_on_leaf,
+         leaf_ants_need_filling = N_need_filling,
+         leaf_ants_text_conflict = N_text_conflict,
+         num_unique_leaf_ants = num_unique_N)
+
+ant_text_conflict_v2 <- filter(plant_ants_flagged_v2, plant_ants_text_conflict) %>%
+  bind_rows(filter(leaf_ants_flagged_v2, leaf_ants_text_conflict))
+
+# write_csv(ant_text_conflict, "ant_text_conflict.csv") # resolved 2019-10-08
+```
+
+## 3.3 - Split ant species into separate columns, check and revise ant counts per species and total
+Note: If the total number of ants on plant is less than the sum of the leaves, recalculated ants_P (i.e.
+ants on plant); ants on stem could be problematic with this, since some groups of ants are assigned to multiple females, but we tried our best to write in the totals for any plant that had such an ambiguous case, so I think I can just omit stem and apex
+```{r}
+All_data_v5_plant_leaf_ants_split_v1 <- All_data_v5_plant_leaf_ants_v2 %>% 
+  mutate(Ants_on_plant_preprocessed = str_to_lower(str_replace_all(str_trim(Ants_on_plant), pattern = " ", replacement = ""))) %>% # remove all whitespace
+  mutate(sbP = as.numeric(str_extract(str_extract(Ants_on_plant, "([0-9]+)sb"), "[0-9]+")),
+         brbP = as.numeric(str_extract(str_extract(Ants_on_plant, "([0-9]+)brb"), "[0-9]+")),
+         brrbP = as.numeric(str_extract(str_extract(Ants_on_plant, "([0-9]+)brrb"), "[0-9]+")),
+         srP = as.numeric(str_extract(str_extract(Ants_on_plant, "([0-9]+)sr"), "[0-9]+")),
+         lrP = as.numeric(str_extract(str_extract(Ants_on_plant, "([0-9]+)lr"), "[0-9]+"))) %>%
+  mutate(sbL = as.numeric(str_extract(str_extract(Ants_on_leaf, "([0-9]+)sb"), "[0-9]+")),
+         brbL = as.numeric(str_extract(str_extract(Ants_on_leaf, "([0-9]+)brb"), "[0-9]+")),
+         brrbL = as.numeric(str_extract(str_extract(Ants_on_leaf, "([0-9]+)brrb"), "[0-9]+")),
+         srL = as.numeric(str_extract(str_extract(Ants_on_leaf, "([0-9]+)sr"), "[0-9]+")),
+         lrL = as.numeric(str_extract(str_extract(Ants_on_leaf, "([0-9]+)lr"), "[0-9]+")))# %>%
+  #select(-Ants_on_plant, -Ants_on_leaf, -Ants_on_plant_preprocessed)
+
+All_data_v5_plant_leaf_ants_split_v1_revisions <- All_data_v5_plant_leaf_ants_split_v1 %>% 
+  group_by(Date, Dorm, Plant, Leaf) %>%
+    filter(row_number() == 1) %>%
+  ungroup() %>%
+  group_by(Date, Dorm, Plant) %>%
+    mutate(sbP_revise = ifelse(!grepl("_S|_A", location),
+                               ifelse(is.na(sbP) & !all(is.na(sbL)) | sbP < sum(sbL, na.rm = TRUE),
+                                      sum(sbL, na.rm = TRUE),
+                                      sbP),
+                               sbP),
+              brbP_revise = ifelse(!grepl("_S|_A", location),
+                               ifelse(is.na(brbP) & !all(is.na(brbL)) | brbP < sum(brbL, na.rm = TRUE),
+                                      sum(brbL, na.rm = TRUE),
+                                      brbP),
+                               brbP),
+              brrbP_revise = ifelse(!grepl("_S|_A", location),
+                               ifelse(is.na(brrbP) & !all(is.na(brrbL)) | brrbP < sum(brrbL, na.rm = TRUE),
+                                      sum(brrbL, na.rm = TRUE),
+                                      brrbP),
+                               brrbP),
+              lrP_revise = ifelse(!grepl("_S|_A", location),
+                               ifelse(is.na(lrP) & !all(is.na(lrL)) | lrP < sum(lrL, na.rm = TRUE),
+                                      sum(lrL, na.rm = TRUE),
+                                      lrP),
+                               lrP),
+              srP_revise = ifelse(!grepl("_S|_A", location),
+                               ifelse(is.na(srP) & !all(is.na(srL)) | srP < sum(srL, na.rm = TRUE),
+                                      sum(srL, na.rm = TRUE),
+                                      srP),
+                               srP)) %>%
+  ungroup() %>%
+  select(Date, location, sbP_revise, brbP_revise, brrbP_revise, srP_revise, lrP_revise) %>%
+  filter(!is.na(location))
+
+# Combine revised ant counts for each species with All_data to create `All_data_v6`
+All_data_v6 <- All_data_v5_plant_leaf_ants_split_v1 %>% 
+  left_join(All_data_v5_plant_leaf_ants_split_v1_revisions, by = c("Date", "location")) %>%
+  select(-sbP, -brbP, -brrbP, -srP, -lrP) %>%
+  rename(sbP = sbP_revise, brbP = brbP_revise, brrbP = brrbP_revise, srP = srP_revise, lrP = lrP_revise) %>%
+  group_by(row_number()) %>%
+    mutate(ants_L = sum(sbL, brbL, brrbL, srL, lrL, na.rm = TRUE),
+           ants_P = sum(sbP, brbP, brrbP, srP, lrP, na.rm = TRUE)) %>%
+  ungroup() %>%
+  select(-`row_number()`, -Ants_on_plant, -Ants_on_leaf, -Ants_on_plant_fill, -plant_ants_fill_from_src, -Ants_on_leaf_fill, -leaf_ants_fill_from_src, -Ants_on_plant_preprocessed)
+```
+
+# 4 - Final pass at revising clutch status
+
+## 4.1 - Calculate female visit order to help with visualizing egg guarding timelines
+```{r}
+visit_order_v1 <- All_data_v6 %>%
+  filter(!is.na(Female_ID), !grepl('NA|M|_E|_N|N (dup)', Female_ID)) %>%
+  select(Date, location, Female_ID) %>%
+  arrange(location, Date) %>%
+  group_by(location, Female_ID) %>%
+    filter(row_number() == 1) %>%
+  ungroup() %>%
+  group_by(location) %>%
+    mutate(visit_order = rank(Date, ties.method = "min")) %>%
+  ungroup() %>%
+  select(-Date)
+
+# this just helps with plotting timeline, doesn't deal with visit order ties
+visitor_rank_v1 <- All_data_v6 %>%
+  filter(!is.na(Female_ID), !grepl('NA|M|_E|_N|N (dup)', Female_ID)) %>%
+  filter(!grepl("_S", location)) %>%
+  select(Date, location, Female_ID) %>%
+  arrange(location, Date) %>%
+  group_by(location, Female_ID) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  group_by(location) %>%
+  mutate(visitor_rank = rank(Date, ties.method = "random")) %>%
+  ungroup() %>%
+  select(-Date)
+
+Female_location_visit_order_v1 <- All_data_v6 %>%
+  filter(!is.na(Female_ID), !grepl('NA|M|_E|_N|N (dup)', Female_ID)) %>%
+  filter(!grepl("_S", location)) %>%
+  select(Date, location, Female_ID) %>%
+  arrange(location, Date) %>%
+  left_join(visit_order_v1) %>%
+  left_join(visitor_rank_v1)
+```
+
+## 4.2 - Identify "clutch fate": when leaves die / go missing / are 100% eaten
+```{r}
+## I think it would be helpful to identify when leaves die / go missing / are 100% eaten
+Eggs_eaten_dates_v1 <- clutch_status_v2 %>%
+  select(location, Date, Clutch_status) %>%
+  mutate(eggs_eaten = grepl("eaten", Clutch_status, ignore.case = TRUE)) %>%
+  filter(eggs_eaten) %>%
+  group_by(location) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  select(location, eggs_eaten_date = Date)
+
+Leaf_missing_dates_v1 <- clutch_status_v2 %>%
+  select(location, Date, Clutch_status) %>%
+  mutate(leaf_missing_date = grepl("missing", Clutch_status, ignore.case = TRUE)) %>%
+  filter(leaf_missing_date) %>%
+  group_by(location) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  select(location, leaf_missing_date = Date)
+
+Leaf_dead_dates_v1 <- clutch_status_v2 %>%
+  select(location, Date, Clutch_status) %>%
+  mutate(leaf_dead_date = grepl("dead", Clutch_status, ignore.case = TRUE)) %>%
+  filter(leaf_dead_date) %>%
+  group_by(location) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  select(location, leaf_dead_date = Date)
+
+egg_fate_dates_v1 <- clutch_nymph_status_v2 %>%
+  left_join(Eggs_eaten_dates_v1) %>%
+  left_join(Leaf_missing_dates_v1) %>%
+  left_join(Leaf_dead_dates_v1) %>%
+  group_by(location) %>%
+    filter(row_number() == 1) %>%
+    mutate(egg_fate = ifelse(any(!is.na(c(eggs_eaten_date, leaf_missing_date, leaf_dead_date))),
+                               ifelse(which.min(c(eggs_eaten_date, leaf_missing_date, leaf_dead_date)) == 1, "Eaten/hatched",
+                                       ifelse(which.min(c(eggs_eaten_date, leaf_missing_date, leaf_dead_date)) == 2, "Missing",
+                                               ifelse(which.min(c(eggs_eaten_date, leaf_missing_date, leaf_dead_date)) == 3, "Dead",
+                                                       NA_character_))),NA_character_)) %>%
+  mutate(egg_fate_date = if_else(any(!is.na(c(eggs_eaten_date, leaf_missing_date, leaf_dead_date))),
+                            min(c(eggs_eaten_date, leaf_missing_date, leaf_dead_date), na.rm = TRUE),
+                            as.Date(NA))) %>%
+  select(location, egg_fate, egg_fate_date)
+```
+
+## 4.3 - Finalizing initiation and hatch dates (plus leaf fate etc) = "clutch status"
+```{r}
+clutch_status_init_hatch_v1 <- clutch_nymph_status_v2 %>%
+  left_join(initiation_dates_v3, by="location") %>%
+  left_join(hatch_dates_v3, by="location") %>%
+  left_join(egg_fate_dates_v1, by="location") %>%
+  mutate(initiation_date_binary = Date == initiation_date,
+         hatch_date_binary = Date == hatch_date,
+         egg_fate_date_binary = Date == egg_fate_date) %>%
+  left_join(Female_location_visit_order_v1, by=c("Date", "location")) %>%
+  select(location, Date, Female_ID, visit_order, Clutch_status, egg_num, egg_len, 
+         N1, N2, N5, nymph_origin, NOr_ambiguous, initiation_date, initiation_date_binary, hatch_date, hatch_date_binary, visitor_rank,
+         egg_fate, egg_fate_date, egg_fate_date_binary)
+
+clutch_status_init_hatch_v1 %>% filter(egg_len > 50)
+clutch_status_init_hatch_v1 %>% filter(location == "A61_10") %>% print(n=Inf)
+
+# dates <- as.Date((clutch_status_init_hatch_v1 %>%
+#   distinct(Date) %>% arrange(Date))$Date)
+
+clutch_status_last_date_measured_v1 <- clutch_status_init_hatch_v1 %>%
+  arrange(location, desc(Date)) %>%
+  group_by(location) %>%
+    filter(!is.na(egg_len|egg_num)) %>%
+    filter(row_number() == 1) %>%
+  ungroup()
+
+clutch_status_init_hatch_labels_v1 <- clutch_status_init_hatch_v1 %>%
+  mutate(init_label = ifelse(initiation_date_binary,
+                             "O",
+                             NA_character_),
+         hatch_label = ifelse(hatch_date_binary,
+                              "H",
+                              NA_character_),
+         fate_label = ifelse(egg_fate_date_binary,
+                              egg_fate,
+                              NA_character_)) %>%
+  group_by(location, Female_ID) %>%
+    arrange(location, Female_ID, desc(Date)) %>%
+    mutate(Female_ID_label = ifelse(Date == max(Date),
+                                    Female_ID,
+                                    NA_character_)) %>%
+  ungroup() %>%
+  group_by(location) %>%
+    mutate(unhatched_days = ifelse(hatch_date_binary, 
+                                   paste0(hatch_date-initiation_date, " days"),
+                                   NA_character_)) %>%
+  ungroup() %>%
+  arrange(location, Date)
+
+# exploring the distribution of clutch size metrics
+clutch_status_stats_v1 <- clutch_status_init_hatch_labels_v1 %>%
+  filter(egg_num > 0 | Clutch_status == "E") %>%
+  group_by(location) %>%
+    summarize(first_egg_num = first(egg_num),
+              min_egg_num = min(egg_num, na.rm = TRUE),
+              max_egg_num = max(egg_num, na.rm = TRUE),
+              first_egg_len = first(egg_len),
+              min_egg_len = min(egg_len, na.rm = TRUE),
+              max_egg_len = max(egg_len, na.rm = TRUE),
+              initiation_date = first(initiation_date),
+              hatch_date = first(hatch_date),
+              egg_fate = factor(first(egg_fate)),
+              egg_fate_date = first(egg_fate_date),
+              any_NOr_ambig_loc = any(NOr_ambiguous)) %>%
+  ungroup() %>%
+  mutate(unhatched_days = as.integer(hatch_date-initiation_date)) %>%
+  left_join(omit_for_abandon_time) %>%
+# add number of clutches per plant
+  separate(location, c("DormPlant", "Leaf"), "_", remove = FALSE) %>%
+  mutate(Dorm = substr(DormPlant, 1,1),
+         Plant = substring(DormPlant, 2)) %>%
+  group_by(Dorm, Plant) %>%
+    mutate(n_clutches_on_plant = n()) %>%
+  ungroup() %>%
+  select(-Leaf, -DormPlant, -Dorm, -Plant)
+```
+
+Note that there is a strong relationship between egg number and clutch length, but the variance increases dramatically at larger numbers of eggs
+```{r}
+## How tight is the relationship between number of eggs and egg mass length?
+ggplot(data = clutch_status_init_hatch_v1, aes(x = egg_len, y = egg_num)) +
+  geom_hex() +
+  geom_smooth()
+```
+
+### [See note] Exporting a list of all clutches with initiation date and hatch date to keep track of revisions
+*Note:* Initially I ran this after creating the clutch_status_stats table, but to avoid needing to redo all the calculations/revisions to update clutch_status_stats I moved the data input and revision steps to before I create clutch_status_stats.
+This would need to be changed if working with the fresh data where "egg_measures_revions" doesn't already exist on the spreadsheet
+```{r}
+# exporting a list of all clutches with initiation date and hatch date to keep track of revisions
+short_unhatched_days_check <- clutch_status_stats_v1 %>% 
+  filter(unhatched_days <= 16)
+
+# write_csv(short_unhatched_days_check, "short_unhatched_days_check_tmp.csv")
+
+# *** when is this used for revisions, if ever?
+never_hatched_check <- clutch_status_stats_v1 %>% 
+  filter(is.na(hatch_date))
+
+# write_csv(never_hatched_check, "never_hatched_check_tmp.csv")
+
+# write_csv(clutch_status_stats_v1, "egg_measures_check_tmp.csv")
+```

### 2023-07-22 scripts/Publilia-01-qc.Rmd
init `Publilia-02-strats.Rmd`, including new histogram figure

@@
 ```
+
+# 5 - Creating a table with relative guarding times
+This will be used for most of the downstream analyses.
+
+## 5.1 - Identify initiators, create visit/guard summaries (first pass)
+Creates `initiators`, `visit_durations_summary`, `clutch_durations_summary` and `num_clutches_initiated`
+```{r}
+initiators <- Female_location_visit_order_v1 %>%
+  arrange(Female_ID, Date) %>%
+  left_join(initiation_dates_v3, by = "location") %>%
+  left_join(hatch_dates_v3, by = "location") %>%
+  filter(!is.na(initiation_date), Date == initiation_date) %>%
+  arrange(location, Date, visit_order) %>%
+  group_by(location) %>%
+    # "first visitor initiator" means she was present at init and was the first female on the leaf
+    mutate(first_visitor_initiator = rank(visit_order, ties.method = "min") == 1) %>%
+  ungroup() %>%
+  group_by(location) %>%
+    mutate(num_at_init = n()) %>%
+  ungroup() %>%
+  select(-Date)
+
+visit_durations_summary <- Female_location_visit_order_v1 %>%
+  left_join(initiation_dates_v3, by = "location") %>%
+  left_join(hatch_dates_v3, by = "location") %>%
+  arrange(location, Date) %>%
+  group_by(Female_ID, location) %>%
+    summarize(visit_starts = first(Date),
+              visit_ends = last(Date),
+            visit_duration = last(Date) - first(Date),
+            guard_duration = last(Date) - max(first(Date, first(initiation_date))),
+            relative_desert_date = last(Date) - first(hatch_date)) %>%
+  ungroup() %>%
+  arrange(Female_ID, visit_starts) %>%
+  group_by(Female_ID) %>%
+    mutate(leaf_visit_order = rank(visit_starts, ties.method = "min")) %>%
+  ungroup()
+
+# add clutch_order (the order of the clutch a female has initiated)
+clutch_durations_summary <- visit_durations_summary %>%
+  right_join(initiators) %>%
+  group_by(location) %>% 
+    mutate(duration_rank = rank(desc(guard_duration), ties.method="min")) %>%
+  ungroup() %>%
+  group_by(Female_ID) %>%
+    arrange(visit_starts) %>%
+    # moms that were on the leaf first and were there at init are considered initiators
+    mutate(initiator = ifelse(first_visitor_initiator & num_at_init == 1, 
+                              TRUE,
+                              # break ties by assuming longest guarder was init and marked female was init
+                              ifelse(first_visitor_initiator & duration_rank == 1 & !grepl("U", Female_ID), 
+                                     TRUE,
+                                     FALSE)),
+           # if the visit ends while a clutch is present
+           clutch_visited_order = ifelse(visit_ends >= initiation_date,
+                                         # find the order of the clutch visit
+                                         rank(visit_starts, ties.method = "min"),
+                                         # otherwise, the female visited before init (rank = 0)
+                                         0) 
+    ) %>%
+  ungroup() %>%
+  group_by(Female_ID, initiator) %>%
+    # if the mom is the initiator
+    mutate(clutch_initiated_order = ifelse(initiator, 
+                                    # find the order of the clutch visit
+                                    rank(visit_starts, ties.method = "min"), 
+                                    # otherwise, this doesn't count as an initiation
+                                    NA)) %>% 
+  ungroup() %>%
+  arrange(Female_ID) %>%
+  mutate(Dorm = substr(location, 1,1)) %>%
+  mutate(females_removed = Dorm %in% c("D", "F", "G", "H"),
+         ants_removed = Dorm %in% c("C", "B", "F", "H"))
+
+num_clutches_initiated <- clutch_durations_summary %>%
+  group_by(Dorm, Female_ID) %>%
+    summarize(num_clutches_initiated = max(clutch_initiated_order),
+              females_removed = first(females_removed)) %>%
+  ungroup()
+```
+
+## 5.2 - Last date female was observed
+Last date female observed, so I have the option of filtering out females that probably died rather than leaving on their own fruition
+```{r}
+last_day_fID <- All_data_v6 %>%
+#  mutate(females_removed = Dorm %in% c("D", "F", "G", "H"),
+#         ants_removed = Dorm %in% c("C", "B", "F", "H")) %>%
+  group_by(Female_ID, Dorm) %>% #, females_removed, ants_removed) %>%
+  summarize(last_day_fID = max(Date)) %>%
+  ungroup()
+
+# ggplot(filter(last_day_fID, !females_removed)) + 
+#   geom_freqpoly(aes(x = last_day_fID, after_stat(density), color = ants_removed))
+
+# clutch_durations_summary_v2 %>% 
+#   filter(mom_at_init)
+```
+
+## 5.3 - Summary of secondary visitor behavior
+Need to differentiate visit days before eggs present from "guard" days after initiation.
+```{r}
+visit_durations_summary_v2 <- Female_location_visit_order_v1 %>%
+  left_join(initiation_dates_v3, by = "location") %>%
+  left_join(hatch_dates_v3, by = "location") %>%
+  arrange(location, Date) %>%
+  group_by(Female_ID, location) %>%
+    summarize(visit_starts = first(Date),
+              visit_ends = last(Date),
+            visit_duration = visit_ends - visit_starts,
+            # duration of visit after initiation (NA if did not visit while eggs present)
+            guard_duration = ifelse(visit_ends - max(visit_starts, first(initiation_date)) >= 0,
+                                    visit_ends - max(visit_starts, first(initiation_date)),
+                                    NA),
+            relative_desert_date = visit_ends - first(hatch_date),
+            initiation_date = first(initiation_date),
+            hatch_date = first(hatch_date)) %>%
+  ungroup() %>%
+  arrange(Female_ID, visit_starts) %>%
+  group_by(Female_ID) %>%
+    mutate(leaf_visit_order = rank(visit_starts, ties.method = "min")) %>%
+  ungroup() %>%
+  arrange(location, visit_starts)
+```
+
+## 5.4 Alternatives to determining who is the initiator
+Create `clutch_durations_summary_v2` and `clutch_status_guarding_summary_v2` after identify the "longest initiator" and `shortest initiator` for each clutch, corresponding to the mother at initiation that was there the longest prior to eggs being observed and (1) remained guarding the clutch the longest after initiation or (2) deserted the clutch the earliest after initiation, respectively.
+```{r}
+num_at_init <- initiators %>%
+  distinct(location, num_at_init)
+
+clutch_durations_summary_v2 <- visit_durations_summary_v2 %>%
+  left_join(select(initiators, -initiation_date, -hatch_date, -num_at_init)) %>%
+  left_join(num_at_init, by = "location") %>%
+  # note: includes small num of moms on a leaf before init, left before init, then returned
+  mutate(mom_at_init = ifelse(visit_starts <= initiation_date & visit_ends >= initiation_date,
+                              TRUE,
+                              FALSE)) %>%
+  group_by(location) %>% 
+    mutate(init_dur_rank = rank(desc(ifelse(mom_at_init, guard_duration, NA)),
+                                ties.method="min", na.last = "keep"),
+           init_dur_shortest = rank(ifelse(mom_at_init, guard_duration, NA),
+                                ties.method="min", na.last = "keep") == 1,
+           init_first_dur_rank = rank(desc(ifelse(first_visitor_initiator, guard_duration, NA)),
+                                ties.method="min", na.last = "keep"),
+           init_first_dur_shortest = rank(ifelse(first_visitor_initiator, guard_duration, NA),
+                                ties.method="min", na.last = "keep") == 1) %>%
+  ungroup() %>%
+  # mutate(init_long = init_dur_rank == 1,
+  #        init_short = init_dur_shortest,
+  #        init_first_long = init_first_dur_rank == 1,
+  #        init_first_short = init_first_dur_shortest) %>%
+  group_by(Female_ID) %>%
+    # if the visit ends while a clutch is present
+    mutate(clutch_visited_order = ifelse(visit_ends >= initiation_date,
+                                         # find the order of the clutch visit
+                                         rank(visit_starts, ties.method = "min"),
+                                         # otherwise, the female visited before init (rank = 0)
+                                         0),
+           clutch_initiated_order = rank(ifelse(mom_at_init, visit_starts, NA),
+                                         ties.method = "min", na.last = "keep"),
+           clutch_init_first_order = rank(ifelse(first_visitor_initiator, visit_starts, NA),
+                                          ties.method = "min", na.last = "keep")) %>%
+           # clutch_init_long_order = rank(ifelse(init_long, visit_starts, NA),
+           #                         ties.method = "min", na.last = "keep"),
+           # clutch_init_first_long_order = rank(ifelse(init_first_long, visit_starts, NA),
+           #                         ties.method = "min", na.last = "keep"),
+           # clutch_init_first_short_order = rank(ifelse(init_first_short, visit_starts, NA),
+           #                         ties.method = "min", na.last = "keep")) %>% 
+  ungroup() %>%
+  arrange(location, visit_starts) %>%
+  mutate(Dorm = substr(location,1,1),
+         females_removed = Dorm %in% c("D", "F", "G", "H"),
+         ants_removed = Dorm %in% c("C", "B", "F", "H"))
+
+clutch_status_guarding_summary_v2 <- clutch_durations_summary_v2 %>%
+  left_join(select(clutch_status_stats_v1, -initiation_date, -hatch_date), by = "location") %>%
+  left_join(select(num_clutches_initiated, -females_removed), by=c("Dorm", "Female_ID")) %>%
+  left_join(select(check_hatch_date_revisions, location, hatch_date_check = revised_hatch_date_text), by="location") %>%
+  left_join(select(short_unhatched_check_revisions, location, short_unhatched_check = Egg_revisions), by="location") %>%
+  # "never_hatched" should be used to override the automatically generated hatch date based on presence of nymphs
+  # but this work has already been done by check_hatch_date_revisions and short_unhatched_check_revisions revisions
+  # so this column isn't really useful for anything
+  mutate(never_hatched = grepl("never hatched", hatch_date_check) | grepl("never hatched", short_unhatched_check)) %>%
+  select(-hatch_date_check, -short_unhatched_check)
+```
+
+# 6 - Write data to `.rds` for further analysis in clean environment
+```{r}
+write_rds(All_data_v6, here("saved_rds/All_data_v6.rds"))
+write_rds(clutch_status_guarding_summary_v2, here("saved_rds/clutch_status_guarding_summary_v2.rds"))
+write_rds(last_day_fID, here("saved_rds/last_day_fID.rds"))
+```

### 2023-07-22 scripts/Publilia-02-strats.Rmd
init `Publilia-02-strats.Rmd`, including new histogram figure

---
title: '01 - TreehopperFitness: Defining strategies and calculating frequencies'
author: "Micah Fletcher"
date: '`r Sys.Date()`'
output: 
  rmdformats::robobook:
  fig_width: 9
toc_depth: 3
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 8, fig.height = 6)

library(kableExtra)   ## Needed if rendering tables
```

```{=html}
<style type="text/css">
  .book .book-body .page-inner {
    max-width: 1600px;
    margin-left: auto;
    margin-right: auto;
  }
details > summary {
  display: list-item;
}
</style>
```

# Publilia 2019 Chapter - Script 1: guarding strategies

## Required libraries and functions
```{r}
library(tidyverse)
library(lubridate)
library(ggpubr)
library(ggh4x)
library(rstatix)
library(emmeans)
library(effectsize)
library(gt)
library(gtsummary)
theme_gtsummary_compact()
library(flextable)
library(multcompView)
library(here)

theme_publilia <- function(){
  theme_bw() +
    theme(text = element_text(family = "Arial"),
          axis.text = element_text(size = 12), 
          axis.title = element_text(size = 14),
          axis.line.x = element_line(color="black"), 
          axis.line.y = element_line(color="black"),
          panel.border = element_blank(),
          panel.grid.major.x = element_blank(),                                          
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.y = element_blank(),  
          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
          plot.title = element_text(size = 18, vjust = 1, hjust = 0.5, face = "bold"),
          legend.text = element_text(size = 10),          
          legend.title = element_blank(),                              
          # legend.position = c(0.90, 0.90), 
          legend.key = element_blank(),
          legend.background = element_rect(color = "black", 
                                           fill = "transparent", 
                                           size = 2, linetype = "blank"))
}
```

# 0 - Data import

clutch_status_guarding_summary_v2
```{r}
All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))
clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))

strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
```

# 1 - Summary stats

We were able to track the behavior of # females over the course of the season. 
```{r}
paste(nrow(strats_data %>% distinct(Female_ID)),
      "Females were successfully identified in the 8 enclosures,")

paste("We were able to mark and recover", nrow(strats_data %>% distinct(Female_ID) %>%
             filter(!grepl("U", Female_ID))),
      "females in the 8 enclosures,")

paste("and an additional", nrow(strats_data %>% distinct(Female_ID) %>%
             filter(grepl("U", Female_ID))),
      "events where unmarked females (which we were unable to mark in situ) either initiated or visited a clutch.")

paste("We observed a total of", nrow(strats_data),
      "clutch visit events,")

paste("on a total of", nrow(strats_data %>% distinct(location)),
      "clutches.")

paste(nrow(strats_data %>% filter(mom_at_init)),
      "of which were ")

paste(nrow(strats_data),
      "Clutch-female pairs were successfully identified in the 8 enclosures,")

paste(nrow(filter(strats_data,
           !grepl("U", Female_ID))),
      "of which were of marked females, who were followed through time.")

paste("To explore the behavioral strategies of freely moving females we restricted our analysis to the",
      nrow(filter(strats_data,
           !females_removed)),
      "clutch visit events on",
      nrow(filter(strats_data,
           !females_removed) %>% distinct(location)),
      "unique clutches in the four enclosures where we did not remove females experimentally.")

paste("We observed",
      nrow(filter(strats_data,
           !grepl("U", Female_ID),
           !females_removed,
           mom_at_init,
           clutch_initiated_order == 1)),
      "of these females initiating their first clutch.")

paste(nrow(filter(strats_data,
           !grepl("U", Female_ID),
           !females_removed,
           !mom_at_init)),
      "of these observations were of females visiting an existing clutch, while",
      nrow(filter(strats_data,
           !grepl("U", Female_ID),
           !females_removed,
           mom_at_init)),
      "were of females that were present on the leaf when eggs were first observed.")

paste("We observed",
      nrow(filter(strats_data,
           !grepl("U", Female_ID),
           !females_removed,
           mom_at_init,
           clutch_initiated_order == 1)),
      "of these females initiating their first clutch.")

paste(nrow(filter(strats_data,
                  !grepl("U", Female_ID),
                  !females_removed,
                  mom_at_init,
                  clutch_initiated_order == 1,
                  visit_ends == last_day_fID)),
      "females were not observed again after leaving their first clutch, and so were excluded from the analysis because we could not rule out depredation or emigration from the study area.",
      "That leaves", nrow(filter(strats_data,
           !grepl("U", Female_ID),
           !females_removed,
           mom_at_init,
           clutch_initiated_order == 1,
           visit_ends < last_day_fID)),
      "females on their first clutches used in this analysis.")

## ****does this change anything?*****
paste("Including these missing females in the analysis reveals...")
```

# 2 - When were females visited on their first clutch?
First I need to know when females were visited on their first clutch.
I also need to estimate the hatch date for clutches that never hatched so I can still show and run stats for relative desertion date. I do this by adding 20 days to the initiation date. The mean interval from initiation to hatch is 20 days.
```{r}
visited_1st_4d_data <- strats_data %>%
  group_by(location) %>%
    mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
  ungroup() %>%
  mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
                                      "Visited", "Not visited"),
         ants = ifelse(ants_removed, "Ants removed", "Control"),
         est_hatch = as_date(ifelse(is.na(hatch_date),
                                 initiation_date + 20,
                                 hatch_date)),
         est_rel2h = visit_ends-est_hatch)

strats_data %>%
  summarize(mean_interval = mean(hatch_date-initiation_date, na.rm=T))
```

I also need to know how to pick just one initiator when two (or more) females are present on a clutch on the first day eggs are observed.
```{r}
visited_1st_4d_data_tb <- visited_1st_4d_data %>%
  # 1) Longest initiator
  mutate(initL = init_first_dur_rank == 1) %>% 
  # 2) Shortest initiator
  #  i) break ties by picking marked females over unmarked
  group_by(location, init_first_dur_shortest) %>% 
    mutate(initS_tmp = ifelse(n()>1, !grepl("Uf", Female_ID), TRUE)) %>% 
  ungroup() %>%
  #  ii) finally picking at random (only one case, identical predictor vars)
  group_by(location, init_first_dur_shortest, initS_tmp) %>%
    mutate(initS = init_first_dur_shortest & initS_tmp & row_number()==1) %>%
  ungroup()
```

# 3 - Defining exposure to ants

## 3.1 - Ant counts on plant; some ants_removed clutches were visited by ants, and vice versa
```{r}
ant_counts <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch) %>%
    summarize(ants_removed=first(ants_removed),
              females_removed=first(females_removed),
              n_antsP=sum(ants_P,na.rm=T),
              ever_antsP=n_antsP>0,
              mean_antsP=mean(ants_P,na.rm=T),
              med_antsP=median(ants_P,na.rm=T),

              n_antsP_b4h=sum(ants_P&b4h),
              ever_antsP_b4h=n_antsP_b4h>0,
              mean_antsP_b4h=mean(ifelse(b4h,ants_P,NA),na.rm=T),
              med_antsP_b4h=median(ifelse(b4h,ants_P,NA),na.rm=T),

              n_antsP_afh=sum(ants_P&afh),
              ever_antsP_afh=n_antsP_afh>0,
              mean_antsP_afh=mean(ifelse(afh,ants_P,NA),na.rm=T),
              med_antsP_afh=median(ifelse(afh,ants_P,NA),na.rm=T)) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

ggplot(data=ant_counts,aes(x=Dorm,y=n_antsP, fill=ants_treatment)) +
  geom_boxplot()

ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP, fill=ants_treatment)) +
  geom_boxplot()

ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_b4h, fill=ants_treatment)) +
  geom_boxplot()

ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_afh, fill=ants_treatment)) +
  geom_boxplot()

ant_counts %>%
  count(Dorm,ants_treatment,ever_antsP)

ant_counts %>%
  count(Dorm,ants_treatment,ever_antsP_b4h)

ant_counts %>%
  count(Dorm,ants_treatment,ever_antsP_afh)

# how many clutches ever had ants in each of the dorms?
ant_counts %>%
  ggplot(data=., aes(y=as.numeric(ever_antsP), x=Dorm, fill=ants_treatment)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
  theme_publilia()

ant_counts %>%
  ggplot(data=., aes(y=as.numeric(ever_antsP_b4h), x=Dorm, fill=ants_treatment)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
  theme_publilia()

ant_counts %>%
  ggplot(data=., aes(y=as.numeric(ever_antsP_afh), x=Dorm, fill=ants_treatment)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
  theme_publilia()

# how extreme was the break-through?
ant_counts %>%
  ggplot(data=., aes(x=mean_antsP_b4h, color=ants_treatment, linetype=females_removed, group=Dorm)) +
  geom_freqpoly(bins=100)

ant_counts %>%
  ggplot(data=., aes(x=med_antsP_b4h, color=ants_treatment, linetype=females_removed, group=Dorm)) +
  geom_freqpoly()

ant_counts %>%
  ggplot(data=., aes(x=mean_antsP_afh, color=ants_treatment, linetype=females_removed, group=Dorm)) +
  geom_freqpoly(bins=100)

ant_counts %>%
  ggplot(data=., aes(x=med_antsP_afh, color=ants_treatment, linetype=females_removed, group=Dorm)) +
  geom_freqpoly()

# how many clutches actually ever had ants vs. not?
ant_counts %>%
  ggplot(data=., aes(x=ever_antsP_b4h, fill=ants_treatment)) +
  geom_bar() +
  theme_publilia() + facet_wrap(~females_removed)

ant_counts %>%
  ggplot(data=., aes(x=ever_antsP_afh, fill=ants_treatment)) +
  geom_bar() +
  theme_publilia() + facet_wrap(~females_removed)

ant_counts %>%
  ggplot(data=., aes(x=ever_antsP_b4h|ever_antsP_afh, fill=ants_treatment)) +
  geom_bar() +
  theme_publilia() + facet_wrap(~females_removed)

```

## 3.2 - Ant arrival times
```{r}
antP_arrival_afh_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsP_afh=ants_P&afh) %>%
    filter(is_antsP_afh) %>%
    slice_head(n=1) %>% 
  mutate(antP_arrival_afh=Date-est_hatch) %>%
  select(location, antP_arrival_afh, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antP_last_b4h_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsP_bfh=ants_P&b4h) %>%
    filter(is_antsP_bfh) %>%
    slice_tail(n=1) %>% 
  mutate(antP_last_b4h=Date-est_hatch) %>%
  select(location, antP_last_b4h, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antL_arrival_afh_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsL_afh=ants_L&afh) %>%
    filter(is_antsL_afh) %>%
    slice_head(n=1) %>% 
  mutate(antL_arrival_afh=Date-est_hatch) %>%
  select(location, antL_arrival_afh, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antL_last_b4h_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsL_bfh=ants_L&b4h) %>%
    filter(is_antsL_bfh) %>%
    slice_tail(n=1) %>% 
  mutate(antL_last_b4h=Date-est_hatch) %>%
  select(location, antL_last_b4h, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

ant_data <- ant_counts %>%
  left_join(antP_last_b4h_data) %>%
  left_join(antP_arrival_afh_data) %>%
  left_join(antL_last_b4h_data) %>%
  left_join(antL_arrival_afh_data)

visited_1st_4d_data_ants <- visited_1st_4d_data %>%
  left_join(ant_data)

visited_1st_4d_data_ants %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h, y=antL_last_b4h, color=females_removed)) +
  geom_point() +
  geom_abline(slope=1)

visited_1st_4d_data_ants %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h, y=antL_arrival_afh, color=females_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  geom_abline(slope=1)

visited_1st_4d_data_ants %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h>=0, y=antL_last_b4h)) +
  geom_boxplot()

visited_1st_4d_data_ants %>%
  filter(ants=="Control") %>%
  ggplot(data=., aes(x=est_rel2h>=0, y=antL_arrival_afh)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=1, width=0.35, height=0) +
  stat_summary(fun=mean, geom="point", shape=4, size=3)

visited_1st_4d_data_ants %>%
  filter(ants=="Control", !females_removed) %>%
  ggplot(data=., aes(x=est_rel2h>=0, y=antL_arrival_afh)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=1, width=0.35, height=0) +
  stat_summary(fun=mean, geom="point", shape=4, size=3)
```

# 4 - Figure 1: Histograms of guarding tenure

## 4.1 Using observed presence of ants as ants treamment

Two proxies:

1. ants ever observed on plant before hatch `hatchever_antsP_b4h` or 
2. ants ever observed on plant after hatch `ever_antsP_afh`

### Not visited early
```{r}
## Not visited early
# ever ants b4h
ggplot(data = filter(visited_1st_4d_data_ants, 
                                 `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends<last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color = ever_antsP_b4h, fill = ever_antsP_b4h), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

# ever ants afh
ggplot(data = filter(visited_1st_4d_data_ants, 
                                 `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color=ever_antsP_afh, fill=ever_antsP_afh), 
            alpha = 0.75, stat='bin', binwidth=4, size=0, position="identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)
```

### Visited early
```{r}
# ever ants b4h
ggplot(data = filter(visited_1st_4d_data_ants,
                     `visited in 4 days` == "Visited",
                     !grepl("U", Female_ID), !females_removed, mom_at_init,
                     clutch_initiated_order == 1, visit_ends<last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color = ever_antsP_b4h, fill = ever_antsP_b4h), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

# ever ants afh
ggplot(data = filter(visited_1st_4d_data_ants,
                     `visited in 4 days` == "Visited",
                     !grepl("U", Female_ID), !females_removed, mom_at_init,
                     clutch_initiated_order == 1, visit_ends < last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color=ever_antsP_afh, fill=ever_antsP_afh), 
            alpha = 0.75, stat='bin', binwidth=4, size=0, position="identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)
```

## 4.2 - Using ant treatment (not observed presence)

#### Desertion relative to hatch
Using geom_area and density
```{r}
Fig1_v1_data <- visited_1st_4d_data %>%
  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
         clutch_initiated_order == 1, visit_ends < last_day_fID)

strat_data_table1 <- visited_1st_4d_data %>%
  mutate(`Ant exclusion` = ifelse(ants_removed, "Ants excluded", "Control"),
         `Females not removed (A)` = !females_removed,
         `Leaf hosted a clutch (B)` = !is.na(initiation_date),
         `Neither (!A&!B)` = `Females not removed (A)`&`Leaf hosted a clutch (B)`) %>%
  select(`Ant exclusion`, `Females not removed (A)`, `Leaf hosted a clutch (B)`,
         `Neither (!A&!B)`) %>%
  tbl_summary(by=`Ant exclusion`)

# strat_data_table1 %>%
#   as_flex_table() %>%
#   flextable::save_as_docx(path=here("prelim_figs/strat_data_table1.docx"))

strat_data_table2 <- visited_1st_4d_data %>%
  filter(!is.na(initiation_date), !females_removed) %>%
  mutate(`Ant exclusion` = ifelse(ants_removed, "Ants excluded", "Control"),
         `Mother at initiation (A)` = !is.na(clutch_initiated_order),
         `First clutch initiated (B)`=clutch_initiated_order==1,
         `Didn't disappear (C)`=visit_ends<last_day_fID,
         `Marked (D)`=!grepl("U", Female_ID),
         `Visited early (E)`=visited_1st_4d,
         `Figure 3A (A&B&C&D&!E)`=`Mother at initiation (A)`&`First clutch initiated (B)`&
           `Didn't disappear (C)`&`Marked (D)`&!`Visited early (E)`,
         `Figure 3B (A&B&C&D&E)`=`Mother at initiation (A)`&`First clutch initiated (B)`&
           `Didn't disappear (C)`&`Marked (D)`&`Visited early (E)`,
         `Figure S4C (!A&C)` = !`Mother at initiation (A)`&`Didn't disappear (C)`) %>%
  select(`Ant exclusion`, `Mother at initiation (A)`, `First clutch initiated (B)`,
         `Didn't disappear (C)`, `Marked (D)`,`Visited early (E)`, 
         `Figure 3A (A&B&C&D&!E)`, `Figure 3B (A&B&C&D&E)`, `Figure S4C (!A&C)`) %>%
  tbl_summary(by=`Ant exclusion`, missing="no")

# strat_data_table2 %>%
#   as_flex_table() %>%
#   flextable::save_as_docx(path=here("prelim_figs/strat_data_table2.docx"))

Fig1_v1A <- ggplot(data = filter(Fig1_v1_data, `visited in 4 days` == "Not visited")) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

Fig1_v1B <- ggplot(data = filter(Fig1_v1_data, `visited in 4 days` == "Visited")) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

(Fig1_v1AB <- ggpubr::ggarrange(Fig1_v1A +
            theme(legend.justification = c(1,1),
                  legend.position = "none") +
            xlim(-30,34),
         Fig1_v1B + 
           theme(legend.justification = c(1,1),
                 legend.position = c(0.95,0.95)) +
            xlim(-30,34),
         align = "v",
         labels = c("A", "B"),
         ncol = 1, nrow = 2))
```

#### Guarding duration instead of relative guarding duration
```{r}
Fig1_v1A.gd <- ggplot(data = filter(Fig1_v1_data, `visited in 4 days` == "Not visited")) +
  geom_area(aes(x = guard_duration, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Guarding duration") +
  ylab("Proportion\nof initiating females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = 20, linetype="dashed", 
                color = "gray", size=1)

Fig1_v1B.gd <- ggplot(data = filter(Fig1_v1_data, `visited in 4 days` == "Visited")) +
  geom_area(aes(x = guard_duration, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Guarding duration") +
  ylab("Proportion\nof initiating females") +
  scale_color_manual(values = c("black", "brown1")) +
  scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = 20, linetype="dashed", 
                color = "gray", size=1)

Fig1_v1C.gd <- ggplot(data = filter(visited_1st_4d_data,
                                 !females_removed, !mom_at_init,
                                 visit_ends >= initiation_date,
                                 visit_ends < last_day_fID)) +
  geom_area(aes(x = guard_duration, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Guarding duration") +
  ylab("Proportion\nof secondary visitors") +
  scale_color_manual(values = c("black", "brown1")) +
  scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = 20, linetype="dashed", 
                color = "gray", size=1)

(Fig1_v1ABC.gd <- ggpubr::ggarrange(Fig1_v1A.gd +
            theme(legend.justification = c(1,1),
                  legend.position = "none") +
            xlim(-4,52),
         Fig1_v1B.gd + 
           theme(legend.justification = c(1,1),
                 legend.position = "none") +
            xlim(-4,52),
         Fig1_v1C.gd + 
           theme(legend.justification = c(1,1),
                 legend.position = c(0.95,0.95)) +
            xlim(-4,52),
         align = "v",
         labels = c("A", "B", "C"),
         ncol = 1, nrow = 3))
```

## 4.3 - Dealing with non-independence of multi-initiators: Using only longest or shortest initiator
Sample sizes
```{r}
# Samples sizes for "not visited" are the same across longests and shortests
filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initL) %>% nrow()

filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initS) %>% nrow()

# Shortests have more females than longests for some reason??
filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initL) %>% nrow()

filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initS) %>% nrow()

visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1) %>% nrow() # 34
visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1) %>% nrow() # 36

visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed) %>% nrow() # 13

visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed) %>% nrow() # 12

visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1) %>% nrow() # 12

visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1) %>% nrow() # 11

visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1, visit_ends < last_day_fID) %>% nrow() # 5

visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1,
                                  !grepl("U", Female_ID), !females_removed,
                                  clutch_initiated_order == 1, visit_ends < last_day_fID) %>% nrow() # 11

# there are two possible reasons why samples sizes are not equal for tbL and tbS:
#  1) clutch_initiated_order==1: sometimes one of the initiators had already laid a clutch, so this was not her first clutch
#    - this happened once each for shortests and longests, so not the source of unevenness
#  2) visit < last_day_fID: sometimes one of the initiators was never seen again
#    - this happened 7 times for longests, 0 for shortests. *** is that biologically significant? ***
```

## 4.4 - How does including the females that were never observed again affect the results?

This will fix the unequal sample sizes for the tie-breaking but will it introduce undue spurious observations?

### No tie-breaking.
```{r}
Fig1_v2A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

Fig1_v2B <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

(Fig1_v2AB <- ggarrange(Fig1_v2A +
            theme(legend.position = "none") +
            xlim(-30,34),
         Fig1_v2B + 
           theme(legend.justification = c(1,1),
                 legend.position = c(0.95,0.95)) +
            ylab("Number of females") +
            xlim(-30,34),
         labels = c("A", "B"),
         ncol = 1, nrow = 2))
```

### Longest initiators only
```{r}
Fig1_v3A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1,
                                 initL)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

Fig1_v3B <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1,
                                 initL)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

(Fig1_v3AB <- ggarrange(Fig1_v3A +
            theme(legend.justification = c(1,1),
                  legend.position = c(0.95,0.95)) +
            xlim(-30,34),
         Fig1_v3B + 
           theme(legend.justification = c(1,1),
                 legend.position = c(0.95,0.95)) +
            ylab("Number of females") +
            xlim(-30,34),
         labels = c("A", "B"),
         ncol = 1, nrow = 2))
```

### Shortest initiators only
```{r}
Fig1_v4A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1,
                                 initS)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

Fig1_v4B <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1,
                                 initS)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

(Fig1_v4AB <- ggarrange(Fig1_v4A +
            theme(legend.justification = c(1,1),
                  legend.position = c(0.95,0.95)) +
            xlim(-30,34),
            Fig1_v4B + 
           theme(legend.justification = c(1,1),
                 legend.position = c(0.95,0.95)) +
            ylab("Number of females") +
            xlim(-30,34),
         labels = c("A", "B"),
         ncol = 1, nrow = 2))
```

## Figure 2: Are early-visited females more likely to desert early?

Note that the observations for Day 0 are not independent because they come from two (or more) females on the same clutch. Some of these are technically the initiator while the other are visitors. When (if) running stats, I can include only the "longest initiator" or "shortest initiator" to satisfy independence and then compare the results of the two options.

```{r}
first_visit_cuts <- strats_data %>%
  filter(!mom_at_init, visit_starts > initiation_date) %>%
  arrange(location, visit_starts) %>%
  group_by(location) %>%
  slice_head(n=1) %>%
  summarize(first_visit_starts = ifelse(num_at_init > 1, 0, as.numeric(visit_starts-initiation_date))) %>%
  mutate(first_visit_cut = cut(first_visit_starts, breaks=seq(0,40,4)))

visit_cuts_data_ExDis <- visited_1st_4d_data_tb %>%
  left_join(first_visit_cuts) %>%
  mutate(vis_cat = ifelse(num_at_init > 1,
                          "Day 0",
                          ifelse(is.na(first_visit_starts),
                                 "never visited",
                                 ifelse(first_visit_cut=="(0,4]", "Day 1-4",
                                        ifelse(first_visit_cut=="(4,8]", "Day 5-8",
                                               "Day 9+")))),
         vis_cat = factor(vis_cat, levels = c("Day 0","Day 1-4","Day 5-8",
                                              "Day 9+","never visited"))) %>%
  filter(!females_removed, mom_at_init, 
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID,
         # ** There was one female (E_Gkgg) which was on the eggs before and after but not ON the initiation date.
         # I suspect I missed her in the field or she may have left and come back. In any case she was never visited
         # and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
         !is.na(vis_cat))

(Fig1_v1D <- ggplot(data = visit_cuts_data_ExDis, 
       aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
  geom_boxplot() +
  #geom_jitter(width=0.2) +
  theme_publilia() +
  xlab("First day clutch was visited (Days since clutch initiated)") +
  ylab("Guarding duration of initiating female (days)") +
  theme(legend.position = "bottom"))

## Adding secondary visitors
### no tb
visitors_ExDis_notb <- visited_1st_4d_data_tb %>%
  semi_join(visit_cuts_data_ExDis, by=c("location")) %>%
  filter(!females_removed, !mom_at_init, visit_starts >= initiation_date,
         visit_ends < last_day_fID)

visitors_ExDis_notb_fig <- ggplot(data = visitors_ExDis_notb, 
       aes(y = guard_duration, x = "Secondary visitors")) +
  geom_boxplot() +
  #geom_jitter(width=0.2) + # I can't figure out why the jitter plot is doubling up on points for a given guard duration...
  theme_publilia() +
  ylab("Guarding duration of secondary visitor (days)")

(Fig1_v1CD <- ggarrange(Fig1_v1D +
            ylim(0,50), 
          visitors_ExDis_notb_fig +
            ylim(0,50) +
            theme(axis.title.x = element_blank()),
          widths = c(6,2.25),
          ncol = 2, nrow = 1, align = "h"))
```

Separating longest and shortest initiators: (uneven samples sizes!)
```{r}
first_visit_cuts <- visited_1st_4d_data_tb %>%
  filter(!mom_at_init, visit_starts > initiation_date) %>%
  arrange(location, visit_starts) %>%
  group_by(location) %>%
  slice_head(n=1) %>%
  summarize(first_visit_starts = ifelse(num_at_init > 1, 0, as.numeric(visit_starts-initiation_date))) %>%
  mutate(first_visit_cut = cut(first_visit_starts, breaks=seq(0,40,4)))

visit_cuts_data <- visited_1st_4d_data_tb %>%
  left_join(first_visit_cuts) %>%
  mutate(vis_cat = ifelse(num_at_init > 1,
                          "Day 0",
                          ifelse(is.na(first_visit_starts),
                                 "never visited",
                                 ifelse(first_visit_cut=="(0,4]", "Day 1-4",
                                        ifelse(first_visit_cut=="(4,8]", "Day 5-8",
                                               "Day 9+")))),
         vis_cat = factor(vis_cat, levels = c("Day 0","Day 1-4","Day 5-8",
                                              "Day 9+","never visited"))) %>%
  filter(!females_removed, mom_at_init, 
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID,
         # ** There was one female (E_Gkgg) which was on the eggs before and after but not ON the initiation date.
         # I suspect I missed her in the field or she may have left and come back. In any case she was never visited
         # and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
         !is.na(vis_cat))

ggplot(data = filter(visit_cuts_data, initL), 
       aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
  geom_boxplot() +
  geom_jitter(width=0.2) +
  theme_publilia() +
  xlab("First day clutch was visited (Days since clutch initiated)") +
  ylab("Guarding duration of the initiating female") +
  theme(legend.position = "bottom") +
  ggtitle("longest intitiators only")

ggplot(data = filter(visit_cuts_data, initS), 
       aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
  geom_boxplot() +
  geom_jitter(width=0.2) +
  theme_publilia() +
  xlab("First day clutch was visited (Days since clutch initiated)") +
  ylab("Guarding duration of the initiating female") +
  theme(legend.position = "bottom") +
  ggtitle("shortest intitiators only")

# ** why are there more shortest initiators than longest initiators? shouldn't they be equal?
filter(visit_cuts_data, initL, vis_cat == "Day 0")
filter(visit_cuts_data, initS, vis_cat == "Day 0")

visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1)
visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1)

filter(clutch_status_guarding_summary_v2, location == "A18_8", mom_at_init) %>%
  select(Female_ID:hatch_date, first_visitor_initiator, init_dur_rank:init_first_dur_shortest)
```

Separating longest and shortest initiators (excluding females that disappeared after first clutch):
```{r}
first_visit_cuts <- visited_1st_4d_data_tb %>%
  filter(!mom_at_init, visit_starts > initiation_date) %>%
  arrange(location, visit_starts) %>%
  group_by(location) %>%
  slice_head(n=1) %>%
  summarize(first_visit_starts = ifelse(num_at_init > 1, 0, as.numeric(visit_starts-initiation_date))) %>%
  mutate(first_visit_cut = cut(first_visit_starts, breaks=seq(0,40,4)))

visit_cuts_data <- visited_1st_4d_data_tb %>%
  left_join(first_visit_cuts) %>%
  mutate(vis_cat = ifelse(num_at_init > 1,
                          "Day 0",
                          ifelse(is.na(first_visit_starts),
                                 "never visited",
                                 ifelse(first_visit_cut=="(0,4]", "Day 1-4",
                                        ifelse(first_visit_cut=="(4,8]", "Day 5-8",
                                               "Day 9+")))),
         vis_cat = factor(vis_cat, levels = c("Day 0","Day 1-4","Day 5-8",
                                              "Day 9+","never visited"))) %>%
  filter(!females_removed, mom_at_init, 
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         #visit_ends < last_day_fID,
         # ** There was one female (E_Gkgg) which was on the eggs before and after but not ON the initiation date.
         # I suspect I missed her in the field or she may have left and come back. In any case she was never visited
         # and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
         !is.na(vis_cat))

(Fig1_v2D <- ggplot(data = visit_cuts_data, 
       aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
  geom_boxplot() +
  #geom_jitter(width=0.2) +
  theme_publilia() +
  xlab("First day clutch was visited (Days since clutch initiated)") +
  ylab("Guarding duration of the initiating female") +
  theme(legend.position = "bottom"))

(Fig1_v3D <- ggplot(data = filter(visit_cuts_data, initL), 
       aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
  geom_boxplot() +
  #geom_jitter(width=0.2) +
  theme_publilia() +
  xlab("First day clutch was visited (Days since clutch initiated)") +
  ylab("Guarding duration of the initiating female") +
  theme(legend.position = "bottom"))

(Fig1_v4D <- ggplot(data = filter(visit_cuts_data, initS), 
       aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
  geom_boxplot() +
  #geom_jitter(width=0.2) +
  theme_publilia() +
  xlab("First day clutch was visited (Days since clutch initiated)") +
  ylab("Guarding duration of the initiating female") +
  theme(legend.position = "bottom"))

## Adding secondary visitors
### no tb
visitors_InDis_notb <- visited_1st_4d_data_tb %>%
  semi_join(filter(visit_cuts_data, initL), by=c("location")) %>%
  filter(!females_removed, !mom_at_init | !initL, visit_starts >= initiation_date)

visitors_InDis_notb_fig <- ggplot(data = visitors_InDis_notb, 
       aes(y = guard_duration, x = "Secondary visitors")) +
  geom_boxplot() +
  #geom_jitter(width=0.2) + # I can't figure out why the jitter plot is doubling up on points for a given guard duration...
  theme_publilia() +
  ylab("Guarding duration of the visiting female")

(Fig1_v2CD <- ggarrange(Fig1_v2D +
            ylim(0,50), 
          visitors_InDis_notb_fig +
            ylim(0,50) +
            theme(axis.title.x = element_blank()),
          widths = c(6,2.25),
          ncol = 2, nrow = 1, align = "h"))

### initL
visitors_InDis_initL <- visited_1st_4d_data_tb %>%
  semi_join(filter(visit_cuts_data, initL), by=c("location")) %>%
  filter(!females_removed, !mom_at_init | !initL, visit_starts >= initiation_date)

visitors_InDis_initL_fig <- ggplot(data = visitors_InDis_initL, 
       aes(y = guard_duration, x = "Secondary visitors")) +
  geom_boxplot() +
  #geom_jitter(width=0.2) + # I can't figure out why the jitter plot is doubling up on points for a given guard duration...
  theme_publilia() +
  ylab("Guarding duration of the visiting female")

(Fig1_v3CD <- ggarrange(Fig1_v3D +
            ylim(0,50), 
          visitors_InDis_initL_fig +
            ylim(0,50) +
            theme(axis.title.x = element_blank()),
          widths = c(6,2.25),
          ncol = 2, nrow = 1, align = "h"))

### initS
visitors_InDis_initS <- visited_1st_4d_data_tb %>%
  semi_join(filter(visit_cuts_data, initS), by=c("location")) %>%
  filter(!females_removed, !mom_at_init | !initS, visit_starts >= initiation_date)

visitors_InDis_initS_fig <- ggplot(data = visitors_InDis_initS, 
       aes(y = guard_duration, x = "Secondary visitors")) +
  geom_boxplot() +
  #geom_jitter(width=0.2) + # I can't figure out why the jitter plot is doubling up on points for a given guard duration...
  theme_publilia() +
  ylab("Guarding duration of the visiting female")

(Fig1_v4CD <- ggarrange(Fig1_v4D +
            ylim(0,50), 
          visitors_InDis_initS_fig +
            ylim(0,50) +
            theme(axis.title.x = element_blank()),
          widths = c(6,2.25),
          ncol = 2, nrow = 1, align = "h"))

```

# 5 - Collecting plots of alternative filtering methods, try stats for v5
The key thing to note is that nothing really changes substantially in all of the histograms except that 
(1) including the disappeared females muddles the peaks and that 
(2) comparing the longest and shortest initiator tie-breaks for the 2nd figure suggests that most of these shortest initiators probably represent visitors who happened to arrive shortly after initiation. That's still a bit hard to tell though because even some of the females that were never visited still deserted early.

I think presenting the original version for the "histogram" is best, because it doesn't show the probably spurious (depredation) earlyish "desertion" events which muddle the key findings (i.e. use Fig1_v1AB). It should just be made explicit that more than one females may be included from a single clutch, so it would violate independence if we run stats on this.

An alternative would be to choose the "longest" tie-breaker, exclude females that disappeared and just be ok with the missing data (due to higher rates of depredation or emigration) relative to the "shortest" tie-breaker, the main interest is comparing relative abundance of strategies rather than comparing the tie-breaking methods per se.

That could actually double as a solution for the second figure as well, since we definitely need to avoid breaking the assumption of independence for that. Ok so, below this code block I'll do "v5" which will be "Longest initiator, exclude disappeared"
```{r}
# 1) Original - both initiators, exclude disappeared females
annotate_figure(Fig1_v1AB, top = text_grob("v1: Original - both \"initiators\", exclude disappeared females"))
# 2) Both initiators, include disappeared
annotate_figure(Fig1_v2AB, top = text_grob("v2: Both \"initiators\", include disappeared"))
# 3) Longest initiator, include disappeared
annotate_figure(Fig1_v3AB, top = text_grob("v3: Longest initiator, include disappeared"))
# 4) Shortest initiator, include disappeared
annotate_figure(Fig1_v4AB, top = text_grob("v4: Shortest initiator, include disappeared"))

# 1) Original - both initiators, exclude disappeared females
annotate_figure(Fig1_v1CD, top = text_grob("v1: Original - both \"initiators\", exclude disappeared females"))
# 2) Both initiators, include disappeared
annotate_figure(Fig1_v2CD, top = text_grob("v2: Both \"initiators\", include disappeared"))
# 3) Longest initiator, include disappeared
annotate_figure(Fig1_v3CD, top = text_grob("v3: Longest initiator, include disappeared"))
# 4) Shortest initiator, include disappeared
annotate_figure(Fig1_v4CD, top = text_grob("v4: Shortest initiator, include disappeared"))
```

## 5.1 Longest initiators only, disappeared females excluded (i.e. v5)
But is this too strong an assumption? I just need to discuss the differences between longest and shortest tie-breaks, but I can just show the longest I think.
```{r}
Fig1_v5A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initL)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

Fig1_v5B <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID,
                                 initL)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

(Fig1_v5AB <- ggarrange(Fig1_v5A +
            theme(legend.justification = c(1,1),
                  legend.position = c(0.95,0.95)) +
            xlim(-30,34),
         Fig1_v5B + 
           theme(legend.justification = c(1,1),
                 legend.position = c(0.95,0.95)) +
            xlim(-30,34),
         labels = c("A", "B"),
         ncol = 1, nrow = 2))

### initL
Fig1_v5D <- ggplot(data = filter(visit_cuts_data_ExDis, initL), 
       aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
  geom_boxplot() +
  #geom_jitter(width=0.2) +
  theme_publilia() +
  xlab("First day clutch was visited (Days since clutch initiated)") +
  ylab("Guarding duration of initiator (Days)") +
  theme(legend.position = "bottom")

visitors_ExDis_initL <- visited_1st_4d_data_tb %>%
  semi_join(filter(visit_cuts_data_ExDis, initL), by=c("location")) %>%
  filter(!females_removed, !mom_at_init | !initL, visit_starts >= initiation_date,
         visit_ends < last_day_fID)

visitors_ExDis_initL_fig <- ggplot(data = visitors_InDis_initL, 
       aes(y = guard_duration, x = "Secondary visitors")) +
  geom_boxplot() +
  #geom_jitter(width=0.2) + # I can't figure out why the jitter plot is doubling up on points for a given guard duration...
  theme_publilia() +
  ylab("Guarding duration of the visiting female")

(Fig1_v5CD <- ggarrange(Fig1_v5D +
            ylim(0,50), 
          visitors_ExDis_initL_fig +
            ylim(0,50) +
            theme(axis.title.x = element_blank()),
          widths = c(6,2.25),
          ncol = 2, nrow = 1, align = "h"))
```

## 5.2 Stats
### Check Assumptions
- SDs not equal: ranges from 16.4 to 36.6, but passes levene test for homogeneity of variance
- one extreme outlier: E18_8 E_Grrk (desert, control)
- fails the Shapiro-Wilk test of normality
```{r}
strats_cuts_v5.data <- filter(visit_cuts_data_ExDis, initL)

# Samples sizes in each group
strats_cuts_v5.data %>% count(vis_cat)

# Means and SDs
strats_cuts_v5.data %>%
  group_by(vis_cat) %>%
  summarize(mean = mean(guard_duration),
            sd = sd(guard_duration))

# Check for outliers
strats_cuts_v5.data %>%
  select(vis_cat, guard_duration, location, Female_ID) %>%
  group_by(vis_cat) %>%
  identify_outliers(guard_duration)

# Build the linear model
model  <- lm(guard_duration ~ vis_cat,
             data = strats_cuts_v5.data)

# Create a QQ plot of residuals
ggqqplot(residuals(model))

# Compute Shapiro-Wilk test of normality
shapiro_test(residuals(model))

# SW test by group
strats_cuts_v5.data %>%
  group_by(vis_cat) %>%
  shapiro_test(guard_duration)

# QQ plot per group
ggqqplot(strats_cuts_v5.data, "guard_duration", ggtheme = theme_bw()) +
  facet_wrap(vars(vis_cat))

# Homogeneity of variance
strats_cuts_v5.data %>% levene_test(guard_duration ~ vis_cat)
```

### Parametric stats v5
Desertion category was significant but not ants or interaction.
```{r}
strats_cuts_v5.aov <- strats_cuts_v5.data %>% anova_test(guard_duration ~ vis_cat)
strats_cuts_v5.aov

strats_cuts_v5.tukey <- strats_cuts_v5.data %>% tukey_hsd(guard_duration ~ vis_cat)

# Visualization: box plots with p-values
strats_cuts_v5.tukey <- strats_cuts_v5.tukey %>% add_xy_position(x = "vis_cat")
(Fig1_v5D.stats <- Fig1_v5D +
  stat_pvalue_manual(strats_cuts_v5.tukey, hide.ns=T) +
  labs(
    subtitle = get_test_label(strats_cuts_v5.aov, detailed = TRUE),
    caption = get_pwc_label(strats_cuts_v5.tukey)
    ) +
  xlab("Day first visited (Days since initiation)") +
  ylab("Guard duration of initiating female"))
```

### Parametric stats v1
```{r}
strats_cuts_v1.data <- visit_cuts_data_ExDis

strats_cuts_v1.aov <- strats_cuts_v1.data %>% anova_test(guard_duration ~ vis_cat)
strats_cuts_v1.aov

strats_cuts_v1.tukey <- strats_cuts_v1.data %>% tukey_hsd(guard_duration ~ vis_cat)

# Visualization: box plots with p-values
strats_cuts_v1.tukey <- strats_cuts_v1.tukey %>% add_xy_position(x = "vis_cat")
(Fig1_v1D.stats <- Fig1_v1D +
  stat_pvalue_manual(strats_cuts_v1.tukey, hide.ns=T, tip.length=0.01) +
  labs(
    subtitle = get_test_label(strats_cuts_v1.aov, detailed = TRUE),
    caption = get_pwc_label(strats_cuts_v1.tukey)
    ) +
  xlab("Age of clutch when first visited by secondary female (days)") +
  ylab("Guarding duration of initiating female (days)"))
```

### Parametric stats v2
```{r}
strats_cuts_v4.data <- visit_cuts_data_ExDis

strats_cuts_v4.aov <- strats_cuts_v4.data %>% anova_test(guard_duration ~ vis_cat)
strats_cuts_v4.aov

strats_cuts_v4.tukey <- strats_cuts_v4.data %>% tukey_hsd(guard_duration ~ vis_cat)

# Visualization: box plots with p-values
strats_cuts_v4.tukey <- strats_cuts_v4.tukey %>% add_xy_position(x = "vis_cat")
(Fig1_v4D.stats <- Fig1_v4D +
  stat_pvalue_manual(strats_cuts_v4.tukey, hide.ns=T) +
  labs(
    subtitle = get_test_label(strats_cuts_v4.aov, detailed = TRUE),
    caption = get_pwc_label(strats_cuts_v4.tukey)
    ) +
  xlab("Day first visited (Days since initiation)") +
  ylab("Guard duration of initiating female"))
```

### Non-parametric stats: v1
```{r}
# non-parametric: Kruskall-Wallis test followed by Dunn test or pairwise wilcox tests
vis_cat_v1.data <- visited_1st_4d_data %>%
  left_join(first_visit_cuts) %>%
  mutate(vis_cat = ifelse(num_at_init > 1,
                          "0",
                          ifelse(is.na(first_visit_starts),
                                 "never visited",
                                 ifelse(first_visit_cut=="(0,4]", "1 to 4", "5+"))),
         vis_cat = factor(vis_cat, levels = c("0","1 to 4",
                                              "5+","never visited"))) %>%
  filter(!females_removed, mom_at_init, 
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID,
         # ** There was one female (E_Gkgg) which was on the eggs before and after but not ON the initiation date.
         # I suspect I missed her in the field or she may have left and come back. In any case she was never visited
         # and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
         !is.na(vis_cat))

ggplot(vis_cat_v1.data, aes(x=first_visit_starts, y=guard_duration)) +
  geom_count() +
  geom_smooth(method=lm)

(Fig1_v1D <- ggplot(data = vis_cat_v1.data, 
       aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
  #geom_boxplot(outlier.shape = NA) +
  geom_violin(aes(fill=vis_cat%in%c("0","1 to 4")), color = NA, trim=T, size=2, alpha=0.50) +
  geom_jitter(aes(color=vis_cat%in%c("0","1 to 4")), width=0.1, size=3) +
  theme_publilia() +
  scale_color_brewer(palette="Set2") + scale_fill_brewer(palette="Set2") +
  xlab("First day clutch was visited (Days since clutch initiated)") +
  ylab("Guarding duration of initiating female (days)") +
  theme(legend.position = "none"))

strats_cuts_v1.KWtest <- vis_cat_v1.data %>% kruskal_test(guard_duration ~ vis_cat)
strats_cuts_v1.KWtest
rank_epsilon_squared(guard_duration ~ vis_cat, data = vis_cat_v1.data)

strats_cuts_v1.dunn <- vis_cat_v1.data %>% dunn_test(guard_duration ~ vis_cat)
strats_cuts_v1.dunn

strats_cuts_v1.dunn.vec <- strats_cuts_v1.dunn$p.adj.signif
names(strats_cuts_v1.dunn.vec) <- paste(strats_cuts_v1.dunn$group1,strats_cuts_v1.dunn$group2,sep="-")
strats_cuts_v1.multcompLetters <- tibble(vis_cat=names(multcompLetters(strats_cuts_v1.dunn.vec)$Letters),
                            label=unname(multcompLetters(strats_cuts_v1.dunn.vec)$Letters))

# Visualization: box plots with p-values
(Fig1_v1D.stats.nonpara <- Fig1_v1D +
    geom_text(data=strats_cuts_v1.multcompLetters, aes(x=vis_cat, y=-4, label=label, color=vis_cat%in%c("0","1 to 4")), fontface="bold", size=6) +
  labs(
    subtitle = get_test_label(strats_cuts_v1.KWtest, detailed = TRUE),
    caption = get_pwc_label(strats_cuts_v1.dunn)
    ) +
  xlab("Day first visited (Days since initiation)") +
  ylab("Guard duration of initiating female") +
    theme(legend.position = "none"))
```

### Non-parametric stats, but including females that disappeared or were unmarked
Three clutches were omitted from the analysis. Two were visited after hatching, and one had no females present at initiation.
```{r}
# non-parametric: Kruskall-Wallis test followed by Dunn test or pairwise wilcox tests
vis_cat_v2.data <- visited_1st_4d_data %>%
  left_join(first_visit_cuts) %>%
  mutate(vis_cat = ifelse(num_at_init > 1,
                          "0",
                          ifelse(is.na(first_visit_starts),
                                 "never visited",
                                 ifelse(first_visit_cut=="(0,4]", "1 to 4", "5+"))),
         vis_cat = ifelse(location=='E40_9', "never visited", vis_cat),
         vis_cat = factor(vis_cat, levels = c("0","1 to 4",
                                              "5+","never visited"))) %>%
  filter(!females_removed, mom_at_init, 
         clutch_initiated_order == 1, !is.na(vis_cat))

# # where do the NAs come from?
# vis_cat_v2.data %>% filter(is.na(vis_cat))
# visited_1st_4d_data %>% filter(location=='C41_6')
# # C41_6 was deserted immediately, then visited long after hatch
# visited_1st_4d_data %>% filter(location=='E148_6')
# # E148_6 was also visited long after hatch
# visited_1st_4d_data %>% filter(location=='E40_9')
# # There was one female (E_Gkgg: E40_9) on the eggs before and after but not ON the init date.
# # I suspect I missed her in the field or she may have left and come back. She was never visited
# # and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.

ggplot(vis_cat_v2.data, aes(x=first_visit_starts, y=guard_duration)) +
  geom_count() +
  geom_smooth(method=lm)

(vis_start.vs.guard_dur.v2.p <- ggplot(data = vis_cat_v2.data, 
       aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
  #geom_boxplot(outlier.shape = NA) +
  geom_violin(aes(fill=vis_cat%in%c("0","1 to 4")), color = NA, trim=T, size=2, alpha=0.50) +
  geom_jitter(aes(color=vis_cat%in%c("0","1 to 4")), width=0.1, size=3) +
  theme_publilia() +
  scale_color_brewer(palette="Set2") + scale_fill_brewer(palette="Set2") +
  xlab("First day clutch was visited (Days since clutch initiated)") +
  ylab("Guarding duration of initiating female (days)") +
  theme(legend.position = "none"))

strats_cuts_v2.KWtest <- vis_cat_v2.data %>% kruskal_test(guard_duration ~ vis_cat)
strats_cuts_v2.KWtest
rank_epsilon_squared(guard_duration ~ vis_cat, data = vis_cat_v2.data)

strats_cuts_v2.dunn <- vis_cat_v2.data %>% dunn_test(guard_duration ~ vis_cat)
strats_cuts_v2.dunn

strats_cuts_v2.dunn.vec <- strats_cuts_v2.dunn$p.adj.signif
names(strats_cuts_v2.dunn.vec) <- paste(strats_cuts_v2.dunn$group1,strats_cuts_v2.dunn$group2,sep="-")
strats_cuts_v2.multcompLetters <- tibble(vis_cat=names(multcompLetters(strats_cuts_v2.dunn.vec)$Letters),
                            label=unname(multcompLetters(strats_cuts_v2.dunn.vec)$Letters))

# Visualization: box plots with p-values
(vis_start.vs.guard_dur.v2.stats.nonpara.p <- vis_start.vs.guard_dur.v2.p +
    geom_text(data=strats_cuts_v2.multcompLetters, aes(x=vis_cat, y=-4, label=label, color=vis_cat%in%c("0","1 to 4")), fontface="bold", size=6) +
  labs(
    subtitle = get_test_label(strats_cuts_v2.KWtest, detailed = TRUE),
    caption = get_pwc_label(strats_cuts_v2.dunn)
    ) +
  xlab("Day first visited (Days since initiation)") +
  ylab("Guard duration of initiating female") +
    theme(legend.position = "none"))

# ggsave(here("prelim_figs/guard_dur.vs.first_visit.v2.png"),
#        vis_start.vs.guard_dur.v2.stats.nonpara.p,
#        device = "png",
#        width = 160, height = 120, units = "mm", dpi = "print")
```

# 6 Comparing early desertion by initiator vs. latest desertion of leaf by any female vs. latest desertion of the plant by any female
```{r}
visit_data.desL.desP <- visited_1st_4d_data %>%
  left_join(first_visit_cuts) %>%
  group_by(location) %>% mutate(last_visit_ends_L = max(visit_ends, na.rm=T)) %>% ungroup() %>%
  separate(location, into = c("DormPlant", "Leaf"), sep="_", remove=FALSE) %>%
  group_by(DormPlant) %>% mutate(last_visit_ends_P = max(visit_ends, na.rm=T)) %>% ungroup() %>%
  mutate(last_desL_rel2h = last_visit_ends_L-est_hatch,
         last_desP_rel2h = last_visit_ends_P-est_hatch)

# sloped
visit_data.desL.desP %>% filter(!females_removed) %>%
  filter(clutch_initiated_order==1, visit_ends<last_day_fID, !grepl("U", Female_ID)) %>%
ggplot(data = ., aes(x=est_rel2h, y=last_desL_rel2h)) +
  geom_abline(slope=1,intercept=0, color="gray") +
  geom_count(aes(color=`visited in 4 days`), alpha=0.75) +
  geom_vline(xintercept = -16, linetype="dotted", color = "gray", size=1) +
  geom_vline(xintercept = 4, linetype="dotted", color = "gray", size=1) +
  scale_color_brewer(palette="Set2") +
  facet_wrap(~ants_removed) + ylim(-30,60) + xlim(-25,32)

visit_data.desL.desP %>% filter(!females_removed) %>%
  filter(clutch_initiated_order==1, visit_ends<last_day_fID, !grepl("U", Female_ID)) %>%
ggplot(data = ., aes(x=est_rel2h, y=last_desP_rel2h)) +
  geom_abline(slope=1,intercept=0, color="gray") +
  geom_count(aes(color=`visited in 4 days`), alpha=0.75) +
  geom_vline(xintercept = -16, linetype="dotted", color = "gray", size=1) +
  geom_vline(xintercept = 4, linetype="dotted", color = "gray", size=1) +
  scale_color_brewer(palette="Set2") +
  facet_wrap(~ants_removed) + ylim(-30,60) + xlim(-25,32)

# residuals
des.vs.desL.p.facet <- visit_data.desL.desP %>% filter(!females_removed) %>%
  filter(clutch_initiated_order==1, visit_ends<last_day_fID, !grepl("U", Female_ID)) %>%
ggplot(data = .) +
  geom_rect(data=data.frame(xmin=-Inf,xmax=-16, ymin=-Inf, ymax=Inf), 
            aes(xmin=-Inf,xmax=-16, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_rect(data=data.frame(xmin=4,xmax=Inf, ymin=-Inf, ymax=Inf), 
            aes(xmin=4,xmax=Inf, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_count(aes(x=est_rel2h, y=last_desL_rel2h-est_rel2h, color=`visited in 4 days`), alpha=0.75) +
  scale_color_brewer(palette="Set2") + ylim(0,80) +
  xlab("Desertion date of initiator relative to hatch") +
  ylab("Number of days a female remained on\nleaf after initiator") +
  facet_wrap(~ants_removed)

des.vs.desP.p.facet <- visit_data.desL.desP %>% filter(!females_removed) %>%
  filter(clutch_initiated_order==1, visit_ends<last_day_fID, !grepl("U", Female_ID)) %>%
ggplot(data = .) +
  geom_rect(data=data.frame(xmin=-Inf,xmax=-16, ymin=-Inf, ymax=Inf), 
            aes(xmin=-Inf,xmax=-16, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_rect(data=data.frame(xmin=4,xmax=Inf, ymin=-Inf, ymax=Inf), 
            aes(xmin=4,xmax=Inf, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_count(aes(x=est_rel2h, y=last_desP_rel2h-est_rel2h, color=`visited in 4 days`), alpha=0.75) +
  scale_color_brewer(palette="Set2") + ylim(0,80) +
  xlab("Desertion date of initiator relative to hatch") +
  ylab("Number of days a female remained on\nplant after initiator") +
  facet_wrap(~ants_removed)

(des.vs.desL.vs.desP.p.facet <- ggpubr::ggarrange(
  des.vs.desL.p.facet +
    theme(legend.justification = c(1,1)) +
    xlim(-30,34),
  des.vs.desP.p.facet + 
    theme(legend.justification = c(1,1)) +
    xlim(-30,34),
  common.legend = T, legend = "right",
  align = "h", labels = c("A", "B"), ncol = 2, nrow = 1))

# residuals, not facetted
des.vs.desL.p <- visit_data.desL.desP %>% filter(!females_removed) %>%
  filter(clutch_initiated_order==1, visit_ends<last_day_fID, !grepl("U", Female_ID),
         !is.na(`visited in 4 days`)) %>%
ggplot(data = .) +
  geom_rect(data=data.frame(xmin=-Inf,xmax=-15, ymin=-Inf, ymax=Inf), 
            aes(xmin=-Inf,xmax=-15, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_rect(data=data.frame(xmin=5,xmax=Inf, ymin=-Inf, ymax=Inf), 
            aes(xmin=5,xmax=Inf, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_count(aes(x=est_rel2h, y=last_desL_rel2h-est_rel2h, color=`visited in 4 days`), alpha=0.75, shape=16) +
  scale_color_brewer(palette="Set2") + ylim(0,77) +
  xlab("Desertion date of initiator\nrelative to hatch") +
  ylab("Number of days a female remained on\nleaf after initiator")

des.vs.desP.p <- visit_data.desL.desP %>% filter(!females_removed) %>%
  filter(clutch_initiated_order==1, visit_ends<last_day_fID, !grepl("U", Female_ID),
         !is.na(`visited in 4 days`)) %>%
ggplot(data = .) +
  geom_rect(data=data.frame(xmin=-Inf,xmax=-15, ymin=-Inf, ymax=Inf), 
            aes(xmin=-Inf,xmax=-15, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_rect(data=data.frame(xmin=5,xmax=Inf, ymin=-Inf, ymax=Inf), 
            aes(xmin=5,xmax=Inf, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_count(aes(x=est_rel2h, y=last_desP_rel2h-est_rel2h, color=`visited in 4 days`), alpha=0.75, shape=16) +
  scale_color_brewer(palette="Set2") + ylim(0,77) +
  xlab("Desertion date of initiator\nrelative to hatch") +
  ylab("Number of days a female remained on\nplant after initiator")

(des.vs.desL.vs.desP.p <- ggpubr::ggarrange(
  des.vs.desL.p +
    theme(legend.justification = c(1,1)) +
    xlim(-23,30),
  des.vs.desP.p + 
    theme(legend.justification = c(1,1)) +
    xlim(-23,30),
  common.legend = T, legend = "right",
  align = "h", labels = c("A", "B"), ncol = 2, nrow = 1))

# ggsave(here("prelim_figs/des_vs_desL_vs_desP.png"),
#        des.vs.desL.vs.desP.p,
#        device = "png",
#        width = 240, height = 120, units = "mm", dpi = "print")

# residuals, not facetted: include females that disappeared
des.vs.desL.v2.p <- visit_data.desL.desP %>% filter(!females_removed) %>%
  filter(clutch_initiated_order==1, !is.na(`visited in 4 days`)) %>%
ggplot(data = .) +
  geom_rect(data=data.frame(xmin=-Inf,xmax=-15, ymin=-Inf, ymax=Inf), 
            aes(xmin=-Inf,xmax=-15, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_rect(data=data.frame(xmin=5,xmax=Inf, ymin=-Inf, ymax=Inf), 
            aes(xmin=5,xmax=Inf, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_count(aes(x=est_rel2h, y=last_desL_rel2h-est_rel2h, color=`visited in 4 days`), alpha=0.75, shape=16) +
  scale_color_brewer(palette="Set2") + ylim(0,77) +
  xlab("Desertion date of initiator\nrelative to hatch") +
  ylab("Number of days a female remained on\nleaf after initiator")

des.vs.desP.v2.p <- visit_data.desL.desP %>% filter(!females_removed) %>%
  filter(clutch_initiated_order==1, !is.na(`visited in 4 days`)) %>%
ggplot(data = .) +
  geom_rect(data=data.frame(xmin=-Inf,xmax=-15, ymin=-Inf, ymax=Inf), 
            aes(xmin=-Inf,xmax=-15, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_rect(data=data.frame(xmin=5,xmax=Inf, ymin=-Inf, ymax=Inf), 
            aes(xmin=5,xmax=Inf, ymin=-Inf, ymax=Inf), fill="gray", alpha=0.2) +
  geom_count(aes(x=est_rel2h, y=last_desP_rel2h-est_rel2h, color=`visited in 4 days`), alpha=0.75, shape=16) +
  scale_color_brewer(palette="Set2") + ylim(0,77) +
  xlab("Desertion date of initiator\nrelative to hatch") +
  ylab("Number of days a female remained on\nplant after initiator")

(des.vs.desL.vs.desP.v2.p <- ggpubr::ggarrange(
  des.vs.desL.v2.p +
    theme(legend.justification = c(1,1)) +
    xlim(-23,30),
  des.vs.desP.v2.p + 
    theme(legend.justification = c(1,1)) +
    xlim(-23,30),
  common.legend = T, legend = "right",
  align = "h", labels = c("A", "B"), ncol = 2, nrow = 1))

# ggsave(here("prelim_figs/des_vs_desL_vs_desP.v2.png"),
#        des.vs.desL.vs.desP.v2.p,
#        device = "png",
#        width = 240, height = 120, units = "mm", dpi = "print")
```

# 7 - Save selected figures and stats for chapter

I will use the original filtering because I feel it best represents the complexity of the data without making too stringent or tenuous assumptions. I think showing only the data from a "longest" tie break could be missing the possibility/uncertainty that some initiators may desert early when visited and some may not, even if it avoids breaking the assumption of independence for statistical tests. I should just discuss this and include the v5 figure in the supplemental/appendix.

## 7.1 Figures

### Main
```{r}
(desertion_firstclutch_hist <- Fig1_v1AB)
(guard_dur.vs.first_visit <- Fig1_v1D.stats.nonpara)

# ggsave(here("prelim_figs/desertion_firstclutch_hist.png"),
#        desertion_firstclutch_hist,
#        device = "png",
#        width = 120, height = 140, units = "mm", dpi = "print")
# 
# ggsave(here("prelim_figs/guard_dur.vs.first_visit.png"),
#        guard_dur.vs.first_visit,
#        device = "png",
#        width = 160, height = 120, units = "mm", dpi = "print")
# 
# ggsave(here("prelim_figs/desertion_firstclutch_hist_v2.png"), # include females that disappeared
#        Fig1_v2AB,
#        device = "png",
#        width = 120, height = 140, units = "mm", dpi = "print")
```

### Supplement
```{r}
(duration_firstclutch_hist <- Fig1_v1ABC.gd)
# ggsave(here("prelim_figs/duration_firstclutch_hist.png"),
#        duration_firstclutch_hist,
#        device = "png",
#        width = 120, height = 180, units = "mm", dpi = "print")
```

## 7.2 Stats for text

### Females on their first clutch

In the control treatment, where ants had free access to females and their clutches, females tended to desert their first clutch either within a few days of initiating them (mode = 0-3 days after first eggs, n = 12) or within a few days of the first nymphs hatching (mode = 0-3 days after first nymphs, n = 19). For clutches where ants were excluded, some females also deserted their eggs within the first few days of initiation (mode = 0-3 days after first eggs, n = 11) but those that remained tended to desert well after hatching (mode = 12-15 days after first nymphs, n = 11).

```{r}
# control
visited_1st_4d_data_tb %>%
  filter(!females_removed, !ants_removed,
         mom_at_init, 
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>%
  mutate(dur_cuts = cut(guard_duration, breaks = seq(-1,63,4))) %>%
  count(dur_cuts) %>%
  arrange(desc(n))

visited_1st_4d_data_tb %>%
  filter(!females_removed, !ants_removed,
         mom_at_init, 
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>%
  mutate(rel_cuts = cut(as.numeric(est_rel2h, "days"), breaks = seq(-33,33,4))) %>%
  count(rel_cuts) %>%
  arrange(desc(n))

# ant removal
visited_1st_4d_data_tb %>%
  filter(!females_removed, ants_removed,
         mom_at_init, 
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>%
  mutate(dur_cuts = cut(guard_duration, breaks = seq(-1,63,4))) %>%
  count(dur_cuts) %>%
  arrange(desc(n))

visited_1st_4d_data_tb %>%
  filter(!females_removed, ants_removed,
         mom_at_init, 
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>%
  mutate(rel_cuts = cut(as.numeric(est_rel2h, "days"), breaks = seq(-33,33,4))) %>%
  count(rel_cuts) %>%
  arrange(desc(n))
```

Of the females that guarded at least until nymphs hatched, females in the ant exclusion enclosure guarded nymphs longer than females in the control enclosure (Estimate = 10 days, W = 1061, p<0.0001; Mann-Whitney U Test).
```{r}
wilcox_data <- visited_1st_4d_data_tb %>%
  filter(!females_removed,
         mom_at_init, 
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID,
         est_rel2h >= 0)

ggplot(wilcox_data) +
  geom_histogram(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 1, size = 0, position = "identity") +
  facet_wrap(vars(ants), ncol=1)

wilcox.test(as.numeric(est_rel2h, "days") ~ ants, data = wilcox_data,
            na.rm=TRUE, paired=FALSE, exact=FALSE, conf.int=TRUE)
```

Of the 96 first clutches included in the analysis (see Methods), 13 had two or more females present on the first day eggs were observed, 24 were otherwise visited by a secondary female within the first 4 days and 14 were visited at some point later. 
```{r}
vis_cat_v1.data %>%
  summarize(n=n())

vis_cat_v1.data %>%
  group_by(vis_cat) %>%
  summarize(n=n())

vis_cat_v1.data %>%
  filter(vis_cat=="0") %>%
  group_by(location) %>% summarize(n_females_at_init = n()) %>% ungroup() %>%
  group_by(n_females_at_init) %>% summarize(n = n())

visit_cuts_data_ExDis %>%
  filter(!females_removed,
         mom_at_init, 
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>%
  distinct(location) %>% nrow()

visit_cuts_data_ExDis %>%
  filter(!females_removed,
         mom_at_init,
         num_at_init>1,
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>%
  distinct(location) %>% nrow()

visit_cuts_data_ExDis %>%
  filter(!females_removed,
         mom_at_init,
         vis_cat == "Day 1-4",
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>%
  distinct(location) %>% nrow()
```

There was no interaction between ant exclusion and clutch age at first visit in any of the following comparisons of females that were first visited at different times, so these data were combined.
```{r}
visited_1st_4d_data_tb %>%
  filter(!females_removed,
         mom_at_init,
         guard_duration <= 4,
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>%
  count(ants_removed, `visited in 4 days`)

visited_1st_4d_data_tb %>%
  filter(!females_removed,
         mom_at_init,
         `visited in 4 days`=="Visited",
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>%
  count(ants_removed, guard_duration <= 4)

# ANOVA
strats_cuts_v1.data <- visit_cuts_data_ExDis

strats_cuts_v1.aov <- strats_cuts_v1.data %>% anova_test(guard_duration ~ vis_cat * ants)
strats_cuts_v1.aov

ggplot(data = visit_cuts_data_ExDis, 
       aes(y = guard_duration, x = vis_cat, color = ants, group = interaction(vis_cat,ants))) +
  geom_boxplot() +
  #geom_jitter(width=0.2) +
  theme_publilia() +
  xlab("First day clutch was visited (Days since clutch initiated)") +
  ylab("Guarding duration of initiating female (days)") +
  theme(legend.position = "bottom")

# non-parametric: Kruskall-Wallis test followed by Dunn test or pairwise wilcox tests
strats_cuts_v1.KWtest <- strats_cuts_v1.data %>% kruskal_test(guard_duration ~ vis_cat)
strats_cuts_v1.KWtest
rank_epsilon_squared(guard_duration ~ vis_cat, data = strats_cuts_v1.data)

strats_cuts_v1.dunn <- strats_cuts_v1.data %>% dunn_test(guard_duration ~ vis_cat)
strats_cuts_v1.dunn

pairwise.wilcox.test(strats_cuts_v1.data$guard_duration,
                                             strats_cuts_v1.data$vis_cat, 
                                             p.adjust.method = "bonf")

# Visualization: box plots with p-values
strats_cuts_v1.dunn <- strats_cuts_v1.dunn %>% add_xy_position(x = "vis_cat")
(Fig1_v4D.stats.nonpara <- Fig1_v4D +
  stat_pvalue_manual(strats_cuts_v1.dunn, hide.ns=T) +
  labs(
    subtitle = get_test_label(strats_cuts_v1.KWtest, detailed = TRUE),
    caption = get_pwc_label(strats_cuts_v1.dunn)
    ) +
  xlab("Day first visited (Days since initiation)") +
  ylab("Guard duration of initiating female"))
```

Most of the females that deserted early were visited by a secondary female within the first 4 days of initiation (22/26), 
```{r}
visit_cuts_data_ExDis %>%
  filter(!females_removed,
         mom_at_init,
         guard_duration <= 4,
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>% nrow()

visited_1st_4d_data_tb %>%
  filter(!females_removed,
         mom_at_init,
         guard_duration <= 4,
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>%
  count(`visited in 4 days`)
```

but only about half (23/45) of females that were visited within the first 4 days deserted early.
```{r}
visited_1st_4d_data_tb %>%
  filter(!females_removed,
         mom_at_init,
         `visited in 4 days`=="Visited",
         clutch_initiated_order == 1, 
         !grepl("U", Female_ID),
         visit_ends < last_day_fID) %>%
  count(guard_duration <= 4)
```

The length of time a female guarded her first eggs before first being visited by a secondary female was related to her guarding duration (Figure 2; F = 8.93, p = < 0.0001; ANOVA [shouldn’t this be non-parametric?]). Females that were first visited on the day of initiation or 1-4 days after had significantly shorter guarding times than those that were visited later or never visited (p < 0.05, Tukey post-hoc test). Females that were visited either on the day of initiation or 1-4 days after did not differ significantly from each other nor did females that were visited after day 5 or never visited at all (p > 0.05, Tukey post-hoc test). 
```{r}
strats_cuts_v1.data <- visit_cuts_data_ExDis

strats_cuts_v1.aov <- strats_cuts_v1.data %>% anova_test(guard_duration ~ vis_cat)
strats_cuts_v1.aov

strats_cuts_v1.tukey <- strats_cuts_v1.data %>% tukey_hsd(guard_duration ~ vis_cat)

strats_cuts_v1.tukey <- strats_cuts_v1.tukey %>% add_xy_position(x = "vis_cat")
(Fig1_v1D.stats <- Fig1_v1D +
  stat_pvalue_manual(strats_cuts_v1.tukey, hide.ns=T, tip.length=0.01) +
  labs(
    subtitle = get_test_label(strats_cuts_v1.aov, detailed = TRUE),
    caption = get_pwc_label(strats_cuts_v1.tukey)
    ) +
  xlab("Age of clutch when first visited by secondary female (days)") +
  ylab("Guarding duration of initiating female (days)"))
```

### Visiting female behavior
Most females laid their first eggs by initiating their own clutch while some females started by visiting an existing clutch (n=115 and 36 respectively). 
```{r}
visited_1st_4d_data_tb %>%
  filter(!females_removed,
         clutch_visited_order == 1) %>%
  count(clutch_initiated_order == 1)
print(paste("% (not removed) females that started the season by visiting an existing clutch:", 36/151*100))
print(paste("% (not removed) females that started by initiating their own clutch:", 115/151*100))

visited_1st_4d_data_tb %>%
  filter(females_removed,
         clutch_visited_order == 1) %>%
  count(clutch_initiated_order == 1)
62/100

visited_1st_4d_data_tb %>%
  filter(clutch_visited_order == 1) %>%
  count(clutch_initiated_order == 1)
62/215
```

Visits by secondary females were typically short (median = X days) and only 2 visitors remained through hatching (Figure 2B). 
```{r}
visited_1st_4d_data_tb %>%
  filter(!females_removed,
         !mom_at_init,
         visit_ends < last_day_fID) %>%
  summarize(n = n(),
            n_NA = sum(is.na(guard_duration)),
            mean_gd = mean(as.numeric(guard_duration, "days"), na.rm=T),
            med_gd = median(as.numeric(guard_duration, "days"), na.rm=T))
```

### After the first clutch
No tie-breaking.
- Does the increased proportion of females that desert early after the first clutch reflect laying additional clutches on a different leaf of the same plant? And thus adding additional eggs/nymphs to the plant without risking the leaf dying before hatching? Another reason to look at plant-level survivorship.
 - Do females that their first clutch early lay additional clutches on the same or different plant? Is the pattern the same later in the season?
```{r}
Fig1sup_v2A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order > 1)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

Fig1sup_v2B <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order > 1)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

(Fig1sup_v2AB <- ggarrange(Fig1sup_v2A +
            theme(legend.justification = c(1,1),
                  legend.position = c(0.95,0.95)) +
            xlim(-30,34),
         Fig1sup_v2B + 
           theme(legend.justification = c(1,1),
                 legend.position = c(0.95,0.95)) +
            ylab("Number of females") +
            xlim(-30,34),
         labels = c("A", "B"),
         ncol = 1, nrow = 2))
```

# Figures for FPO
```{r}
ggplot(data = 
         filter(visited_1st_4d_data_tb, !grepl("U", Female_ID), !females_removed, 
                mom_at_init,
                clutch_initiated_order == 1, 
                visit_ends < last_day_fID)) +
  geom_area(aes(x = guard_duration, y=..density..), 
            alpha = 0.75, stat='bin', binwidth = 4, 
            size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Guarding duration (days)") +
  ylab("Proportion of females")

FPO_freqpoly_all <- ggplot(data = 
         filter(visited_1st_4d_data_tb, !grepl("U", Female_ID), !females_removed, 
                mom_at_init,
                clutch_initiated_order == 1, 
                visit_ends < last_day_fID)) +
  geom_area(aes(x = guard_duration, y=..density..), 
            alpha = 0.75, stat='bin', binwidth = 4, 
            size = 0, position = "identity") + 
  xlim(-4,54) +
  theme_publilia() +
  xlab("Guarding duration (days)") +
  ylab("Proportion of females")

# ggsave(here("prelim_figs/FPO_freqpoly_all.png"), FPO_freqpoly_all,
#        device = "png", width = 120, height = 80, units = "mm", dpi = "print")

FPO_freqpoly_noVis_all <- ggplot(data = 
         filter(visited_1st_4d_data_tb, !grepl("U", Female_ID), !females_removed, 
                mom_at_init,
                `visited in 4 days` == "Not visited",
                clutch_initiated_order == 1, 
                visit_ends < last_day_fID)) +
  geom_area(aes(x = guard_duration, y=..density.., fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, 
            size = 0, position = "identity") + 
  ylim(0,0.09) + xlim(-4,54) +
  theme_publilia() +
  xlab("Guarding duration (days)") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
  scale_fill_manual(values = c("black", "brown1")) +
  theme(legend.position="none")

# ggsave(here("prelim_figs/FPO_freqpoly_noVis_all.png"), FPO_freqpoly_noVis_all,
#        device = "png", width = 120, height = 80, units = "mm", dpi = "print")

FPO_freqpoly_noVis_black <- ggplot(data = 
         filter(visited_1st_4d_data_tb, !grepl("U", Female_ID), !females_removed, 
                mom_at_init,
                `visited in 4 days` == "Not visited",
                ants == "Ants removed",
                clutch_initiated_order == 1, 
                visit_ends < last_day_fID)) +
  geom_area(aes(x = guard_duration, y=..density..), fill="black",
            alpha = 0.75, stat='bin', binwidth = 4, 
            size = 0, position = "identity") + 
  ylim(0,0.09) + xlim(-4,54) +
  theme_publilia() +
  xlab("Guarding duration (days)") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))

# ggsave(here("prelim_figs/FPO_freqpoly_noVis_black.png"), FPO_freqpoly_noVis_black,
#        device = "png", width = 120, height = 80, units = "mm", dpi = "print")

ggplot(data = 
         filter(visited_1st_4d_data_tb, 
                `visited in 4 days` == "Not visited",
                !grepl("U", Female_ID), !females_removed, 
                mom_at_init,
                clutch_initiated_order == 1, 
                visit_ends < last_day_fID,
                initL)) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, 
            size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1"))
```

# 2023.07.22 - Using geom_ridgeline instead of freq_poly with alpha

## Original from chapter:
```{r}
Fig1_v1_data <- visited_1st_4d_data %>%
  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
         clutch_initiated_order == 1, visit_ends < last_day_fID)

strat_data_table1 <- visited_1st_4d_data %>%
  mutate(`Ant exclusion` = ifelse(ants_removed, "Ants excluded", "Control"),
         `Females not removed (A)` = !females_removed,
         `Leaf hosted a clutch (B)` = !is.na(initiation_date),
         `Neither (!A&!B)` = `Females not removed (A)`&`Leaf hosted a clutch (B)`) %>%
  select(`Ant exclusion`, `Females not removed (A)`, `Leaf hosted a clutch (B)`,
         `Neither (!A&!B)`) %>%
  tbl_summary(by=`Ant exclusion`)

# strat_data_table1 %>%
#   as_flex_table() %>%
#   flextable::save_as_docx(path=here("prelim_figs/strat_data_table1.docx"))

strat_data_table2 <- visited_1st_4d_data %>%
  filter(!is.na(initiation_date), !females_removed) %>%
  mutate(`Ant exclusion` = ifelse(ants_removed, "Ants excluded", "Control"),
         `Mother at initiation (A)` = !is.na(clutch_initiated_order),
         `First clutch initiated (B)`=clutch_initiated_order==1,
         `Didn't disappear (C)`=visit_ends<last_day_fID,
         `Marked (D)`=!grepl("U", Female_ID),
         `Visited early (E)`=visited_1st_4d,
         `Figure 3A (A&B&C&D&!E)`=`Mother at initiation (A)`&`First clutch initiated (B)`&
           `Didn't disappear (C)`&`Marked (D)`&!`Visited early (E)`,
         `Figure 3B (A&B&C&D&E)`=`Mother at initiation (A)`&`First clutch initiated (B)`&
           `Didn't disappear (C)`&`Marked (D)`&`Visited early (E)`,
         `Figure S4C (!A&C)` = !`Mother at initiation (A)`&`Didn't disappear (C)`) %>%
  select(`Ant exclusion`, `Mother at initiation (A)`, `First clutch initiated (B)`,
         `Didn't disappear (C)`, `Marked (D)`,`Visited early (E)`, 
         `Figure 3A (A&B&C&D&!E)`, `Figure 3B (A&B&C&D&E)`, `Figure S4C (!A&C)`) %>%
  tbl_summary(by=`Ant exclusion`, missing="no")

# strat_data_table2 %>%
#   as_flex_table() %>%
#   flextable::save_as_docx(path=here("prelim_figs/strat_data_table2.docx"))

Fig1_v1A <- ggplot(data = filter(Fig1_v1_data, `visited in 4 days` == "Not visited")) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

Fig1_v1B <- ggplot(data = filter(Fig1_v1_data, `visited in 4 days` == "Visited")) +
  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

(Fig1_v1AB <- ggpubr::ggarrange(Fig1_v1A +
            theme(legend.justification = c(1,1),
                  legend.position = "none") +
            xlim(-30,34),
         Fig1_v1B + 
           theme(legend.justification = c(1,1),
                 legend.position = c(0.95,0.95)) +
            xlim(-30,34),
         align = "v",
         labels = c("A", "B"),
         ncol = 1, nrow = 2))
```

## New version
```{r}
visit_labels <-

visit_colors <- rev(unique(ggplot_build(Fig1_v1D)$data[[1]]$fill))

hist_strips <- strip_nested(
     # Horizontal strips
     background_y = list(
       element_rect(fill = visit_colors[1]), 
       element_rect(fill = visit_colors[2]), 
       element_blank(), element_blank(), 
       element_blank(), element_blank()),
     text_y = list(
       element_text(color = c("black")), 
       element_text(color = c("black")), 
       element_blank(), element_blank(), 
       element_blank(), element_blank()),
     by_layer_y = FALSE
)

visited_1st_4d_data %>%
  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
         clutch_initiated_order == 1, visit_ends < last_day_fID) %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  mutate(`visited in 4 days` = 
           ifelse(`visited in 4 days` == "Visited", 
                  "Visited within first 4 days", 
                  "Not visited within first 4 days")) %>%
  ggplot(aes(x=est_rel2h, fill=ants)) +
  geom_histogram(binwidth = 4) +
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Number of females") +
  scale_y_continuous(breaks = c(0,4,8),
                     labels = label_number(accuracy = 1)) +
  scale_color_manual(values = c("black", "brown1")) +
  scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1) +
  ggh4x::facet_grid2(vars(`visited in 4 days`, ants), 
                     strip = hist_strips) +
  theme(strip.background = element_rect(color = NA))
```

### 2023-07-22 scripts/Publilia-02-strats.Rmd
Updated version of guarding duration figure for manuscript

@@
 ## Original from chapter:
-```{r}
+```{r, fig.width=3, fig.height=3}
 Fig1_v1_data <- visited_1st_4d_data %>%
@@
   tbl_summary(by=`Ant exclusion`)
-
-# strat_data_table1 %>%
-#   as_flex_table() %>%
-#   flextable::save_as_docx(path=here("prelim_figs/strat_data_table1.docx"))
-
-strat_data_table2 <- visited_1st_4d_data %>%
-  filter(!is.na(initiation_date), !females_removed) %>%
-  mutate(`Ant exclusion` = ifelse(ants_removed, "Ants excluded", "Control"),
-         `Mother at initiation (A)` = !is.na(clutch_initiated_order),
-         `First clutch initiated (B)`=clutch_initiated_order==1,
-         `Didn't disappear (C)`=visit_ends<last_day_fID,
-         `Marked (D)`=!grepl("U", Female_ID),
-         `Visited early (E)`=visited_1st_4d,
-         `Figure 3A (A&B&C&D&!E)`=`Mother at initiation (A)`&`First clutch initiated (B)`&
-           `Didn't disappear (C)`&`Marked (D)`&!`Visited early (E)`,
-         `Figure 3B (A&B&C&D&E)`=`Mother at initiation (A)`&`First clutch initiated (B)`&
-           `Didn't disappear (C)`&`Marked (D)`&`Visited early (E)`,
-         `Figure S4C (!A&C)` = !`Mother at initiation (A)`&`Didn't disappear (C)`) %>%
-  select(`Ant exclusion`, `Mother at initiation (A)`, `First clutch initiated (B)`,
-         `Didn't disappear (C)`, `Marked (D)`,`Visited early (E)`, 
-         `Figure 3A (A&B&C&D&!E)`, `Figure 3B (A&B&C&D&E)`, `Figure S4C (!A&C)`) %>%
-  tbl_summary(by=`Ant exclusion`, missing="no")
-
-# strat_data_table2 %>%
-#   as_flex_table() %>%
-#   flextable::save_as_docx(path=here("prelim_figs/strat_data_table2.docx"))
 
@@
 ## New version
-```{r}
-visit_labels <-
-
+### Relative desert date
+```{r, fig.width=3, fig.height=3}
 visit_colors <- rev(unique(ggplot_build(Fig1_v1D)$data[[1]]$fill))
@@
 
+base_text <- expand.grid(ants = c("Ants removed", "Control"),
+            `visited in 4 days` = c("Not visited within first 4 days", 
+                                    "Visited within first 4 days")) %>%
+  tibble()
+
+init_text <- base_text %>%
+  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited within first 4 days", 
+         "Mean init. date", 
+         ""))
+
+hatch_text <- base_text %>%
+  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited within first 4 days", 
+         "Hatch date", 
+         ""))
+
 visited_1st_4d_data %>%
@@
                      strip = hist_strips) +
-  theme(strip.background = element_rect(color = NA))
-```
+  theme(strip.background = element_rect(color = NA),
+        legend.justification = c(1,1),
+        legend.position = c(1,0.2)) +
+  geom_text(data = init_text,
+            aes(x = -20, y = 10, label = label),
+            hjust = 0, vjust = -1, color = "gray", fontface = "bold") +
+  geom_text(data = hatch_text,
+            aes(x = 0, y = 10, label = label),
+            hjust = 0, vjust = -1, color = "gray", fontface = "bold") +
+  coord_cartesian(clip = "off")
+```
+
+### Guarding duration
+```{r, fig.width=3, fig.height=3}
+visit_colors <- rev(unique(ggplot_build(Fig1_v1D)$data[[1]]$fill))
+
+hist_strips <- strip_nested(
+     # Horizontal strips
+     background_y = list(
+       element_rect(fill = visit_colors[1]), 
+       element_rect(fill = visit_colors[2]), 
+       element_blank(), element_blank(), 
+       element_blank(), element_blank()),
+     text_y = list(
+       element_text(color = c("black")), 
+       element_text(color = c("black")), 
+       element_blank(), element_blank(), 
+       element_blank(), element_blank()),
+     by_layer_y = FALSE
+)
+
+base_text <- expand.grid(ants = c("Ants removed", "Control"),
+            `visited in 4 days` = c("Not visited within first 4 days", 
+                                    "Visited within first 4 days")) %>%
+  tibble()
+
+hatch_text <- base_text %>%
+  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited within first 4 days", 
+         "Hatch date", 
+         ""))
+
+(guarding_durations_plot_2023 <- visited_1st_4d_data %>%
+  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
+         clutch_initiated_order == 1, visit_ends < last_day_fID) %>% 
+  filter(!is.na(`visited in 4 days`)) %>%
+  mutate(`visited in 4 days` = 
+           ifelse(`visited in 4 days` == "Visited", 
+                  "Visited within first 4 days", 
+                  "Not visited within first 4 days")) %>%
+  ggplot(aes(x=guard_duration, fill=ants)) +
+  geom_histogram(binwidth = 4) +
+  theme_publilia() +
+  xlab("Guarding duration") +
+  ylab("Number of females") +
+  scale_y_continuous(breaks = c(0,4,8),
+                     labels = label_number(accuracy = 1)) +
+  scale_color_manual(values = c("black", "brown1")) +
+  scale_fill_manual(values = c("black", "brown1")) +
+  geom_vline(xintercept = 20, linetype="dashed", 
+                color = "gray", size=1) +
+  ggh4x::facet_grid2(vars(`visited in 4 days`, ants), 
+                     strip = hist_strips) +
+  theme(strip.background = element_rect(color = NA),
+        legend.justification = c(1,1),
+        legend.position = c(1,0.2)) +
+  geom_text(data = hatch_text,
+            aes(x = 20, y = Inf, label = label),
+            hjust = -0.1, vjust = 0, color = "gray", fontface = "bold") +
+  coord_cartesian(clip = "off"))
+```

### 2023-07-23 scripts/Publilia-02-strats.Rmd
Updated visit vs early desertion figure for manuscript
minor changes to facet text

@@
 base_text <- expand.grid(ants = c("Ants removed", "Control"),
-            `visited in 4 days` = c("Not visited within first 4 days", 
-                                    "Visited within first 4 days")) %>%
+            `visited in 4 days` = c("Not visited\nwithin first 4 days", 
+                                    "Visited\nwithin first 4 days")) %>%
   tibble()
@@
 hatch_text <- base_text %>%
-  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited within first 4 days", 
+  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited\nwithin first 4 days", 
          "Hatch date", 
@@
            ifelse(`visited in 4 days` == "Visited", 
-                  "Visited within first 4 days", 
-                  "Not visited within first 4 days")) %>%
+                  "Visited\nwithin first 4 days", 
+                  "Not visited\nwithin first 4 days")) %>%
   ggplot(aes(x=guard_duration, fill=ants)) +
@@
   theme(strip.background = element_rect(color = NA),
+        strip.text = element_text(size = 12),
         legend.justification = c(1,1),
-        legend.position = c(1,0.2)) +
+        legend.position = c(1,0.2),
+        legend.text = element_text(size = 12)) +
   geom_text(data = hatch_text,
@@
 ```
+
+# 2023.07.22 - Using geom_ridgeline instead of freq_poly with alpha
+Sarah asked to remove the stats text
+```{r, fig.width=3, fig.height=2}
+Fig1_v1D +
+  xlab("Day first visited (days from initiation)") +
+  ylab("Guard duration of initiating female") +
+    theme(legend.position = "none")
+```

### 2023-07-23 scripts/Publilia-02-strats.Rmd
sample size upset plots

@@
 ```{r, fig.width=3, fig.height=2}
+# Visualization: box plots with p-values
 Fig1_v1D +
-  xlab("Day first visited (days from initiation)") +
+    geom_text(data=strats_cuts_v1.multcompLetters, 
+              aes(x=vis_cat, y=-4, label=label, 
+                  color=vis_cat%in%c("0","1 to 4")), 
+              fontface="bold", size=6) +
+  xlab("Day first visited (Days since initiation)") +
   ylab("Guard duration of initiating female") +
@@
 ```
+
+# 2023.07.22 - Upset plot to clarify sample sizes
+
+## The data used for the figures
+```{r}
+## Unfiltered data
+strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
+
+## Data for histogram
+visited_1st_4d_data <- strats_data %>%
+  group_by(location) %>%
+    mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
+  ungroup() %>%
+  mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
+                                      "Visited", "Not visited"),
+         ants = ifelse(ants_removed, "Ants removed", "Control"),
+         est_hatch = as_date(ifelse(is.na(hatch_date),
+                                 initiation_date + 20,
+                                 hatch_date)),
+         est_rel2h = visit_ends-est_hatch)
+
+visited_1st_4d_data %>%
+  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
+         clutch_initiated_order == 1, visit_ends < last_day_fID) %>% 
+  filter(!is.na(`visited in 4 days`)) %>%
+  mutate(`visited in 4 days` = 
+           ifelse(`visited in 4 days` == "Visited", 
+                  "Visited\nwithin first 4 days", 
+                  "Not visited\nwithin first 4 days"))
+
+## Data for visit vs init
+vis_cat_v1.data <- visited_1st_4d_data %>%
+  left_join(first_visit_cuts) %>%
+  mutate(vis_cat = ifelse(num_at_init > 1,
+                          "0",
+                          ifelse(is.na(first_visit_starts),
+                                 "never visited",
+                                 ifelse(first_visit_cut=="(0,4]", "1 to 4", "5+"))),
+         vis_cat = factor(vis_cat, levels = c("0","1 to 4",
+                                              "5+","never visited"))) %>%
+  filter(!females_removed, mom_at_init, 
+         clutch_initiated_order == 1, 
+         !grepl("U", Female_ID),
+         visit_ends < last_day_fID,
+         # ** There was one female (E_Gkgg) which was on the eggs before and after but not ON the initiation date.
+         # I suspect I missed her in the field or she may have left and come back. In any case she was never visited
+         # and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
+         !is.na(vis_cat))
+```
+
+## Upset plot
+```{r, fig.width=6, fig.height=2}
+# ** There was one female (E_Gkgg) which was on the eggs before and after but not ON the initiation date.
+         # I suspect I missed her in the field or she may have left and come back. In any case she was never visited
+         # and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
+
+sample_size_upset_data <- strats_data %>%
+  group_by(location) %>%
+    mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
+  ungroup() %>%
+  mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
+                                      "Visited", "Not visited"),
+         ants = ifelse(ants_removed, "Ants removed", "Control"),
+         est_hatch = as_date(ifelse(is.na(hatch_date),
+                                 initiation_date + 20,
+                                 hatch_date)),
+         est_rel2h = visit_ends-est_hatch) %>%
+  left_join(first_visit_cuts) %>%
+  mutate(vis_cat = ifelse(num_at_init > 1,
+                          "0",
+                          ifelse(is.na(first_visit_starts),
+                                 "never visited",
+                                 ifelse(first_visit_cut=="(0,4]", "1 to 4", "5+"))),
+         vis_cat = factor(vis_cat, levels = c("0","1 to 4",
+                                              "5+","never visited"))) %>%
+  filter(!is.na(vis_cat)) %>% #**
+  # build logicals representing inclusion in different plots
+  mutate(`Text: 4 different strats` =
+           !females_removed & 
+           clutch_visited_order == 1,
+         `Figure 4 (dur vs 1st visit)` = 
+           !females_removed & 
+           mom_at_init &
+           clutch_initiated_order == 1 & 
+           !grepl("U", Female_ID) & 
+           visit_ends < last_day_fID,
+         `Figure 3 (dur histograms)` = 
+           !females_removed & 
+           mom_at_init &
+           clutch_initiated_order == 1 &
+           !grepl("U", Female_ID) & 
+           visit_ends < last_day_fID & 
+           !is.na(`visited in 4 days`)) %>%
+  mutate(`ants excluded` = ants_removed,
+         `female removed` = females_removed,
+         `female present at intiation` = mom_at_init,
+         `her first clutch` = clutch_visited_order == 1,
+         `first clutch she initiated` = clutch_initiated_order == 1,
+         `female marked` = !grepl("U", Female_ID),
+         `female disappeared` = !(visit_ends < last_day_fID),
+         `unknown whether visited` = is.na(`visited in 4 days`)) %>%
+  select(Female_ID, location,
+         `ants excluded`, `female removed`,
+         `female present at intiation`, 
+         `first clutch she initiated`,
+         `first clutch she initiated or visited`,
+         `female marked`, `female disappeared`, `unknown whether visited`, 
+         `Figure 3 (dur histograms)`, 
+         `Figure 4 (dur vs 1st visit)`,
+         `Text: 4 different strats`) %>%
+  pivot_longer(cols = `ants excluded`:`unknown whether visited`,
+               names_to = "filter_name",
+               values_to = "filter_true") %>%
+  filter(filter_true) %>%
+  group_by(Female_ID, location, 
+           `Text: 4 different strats`,
+           `Figure 3 (dur histograms)`, `Figure 4 (dur vs 1st visit)`) %>%
+  summarize(filters = list(filter_name))
+
+sample_size_upset_data %>% ggplot(aes(x=filters, fill = `Text: 4 different strats`)) +
+    geom_bar() +
+    scale_x_upset()
+
+sample_size_upset_data %>% ggplot(aes(x=filters, fill = `Figure 3 (dur histograms)`)) +
+    geom_bar() +
+    scale_x_upset()
+
+sample_size_upset_data %>% ggplot(aes(x=filters, fill = `Figure 4 (dur vs 1st visit)`)) +
+    geom_bar() +
+    scale_x_upset()
+
+```

### 2023-07-24 manuscript/Manuscript_runfile.Rmd
init `Manuscript_runfile.Rmd` to collect all code to stats, sample sizes, figures, tables for the manuscript in a minimal reproducible script

---
title: 'TreehopperFitness: Run this file for all stats, tables, and figures'
author: "Micah Fletcher"
date: '`r Sys.Date()`'
output: 
  rmdformats::robobook:
  fig_width: 9
toc_depth: 3
---

# 0 - Data import

clutch_status_guarding_summary_v2
```{r}
All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))
clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))

strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
```

# 1 - Mothers dynamically adjust care depending on the presence of ants and conspecific females

*First, we build logical columns for each of the desired filters for different text sections and figures. This way we can keep the total universe of data in one place and ensure that we are certain which data are being left out and why.*
```{r}
strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)

strats_data_with_filters <- strats_data %>%
  # Add whether female was visited within first 4 days of initiating
  group_by(location) %>%
    mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
  ungroup() %>%
  # Add some additional metrics for human readability
  mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
                                      "Visited", "Not visited"),
         ants = ifelse(ants_removed, "Ants removed", "Control"),
         est_hatch = as_date(ifelse(is.na(hatch_date),
                                 initiation_date + 20,
                                 hatch_date)),
         est_rel2h = visit_ends-est_hatch) %>%
  # Add day of first visit bins
  left_join(first_visit_cuts) %>%
  mutate(vis_cat = ifelse(num_at_init > 1,
                          "0",
                          ifelse(is.na(first_visit_starts),
                                 "never visited",
                                 ifelse(first_visit_cut=="(0,4]", "1 to 4", "5+"))),
         vis_cat = factor(vis_cat, levels = c("0","1 to 4",
                                              "5+","never visited"))) %>%
  # Remove one female who has dubious data (See note ** below)
  filter(!is.na(vis_cat)) %>%
  # Build logicals representing inclusion in different plots
  mutate(`Text: 4 different strats` =
           !females_removed & 
           clutch_visited_order == 1,
         `Figure 4 (dur vs 1st visit)` = 
           !females_removed & 
           mom_at_init &
           clutch_initiated_order == 1 & 
           !grepl("U", Female_ID) & 
           visit_ends < last_day_fID,
         `Figure 3 (dur histograms)` = 
           !females_removed & 
           mom_at_init &
           clutch_initiated_order == 1 &
           !grepl("U", Female_ID) & 
           visit_ends < last_day_fID & 
           !is.na(`visited in 4 days`))

# ** There was one female (E_Gkgg) which was on the eggs before and after but not ON the initiation date. I suspect I missed her in the field or she may have left and come back. In any case she was never visited and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
```

*To double-check that we understand how we've filtered the data for each sub-analysis, we can represent each filtering regime as an upset plot*
```{r, fig.width=6, fig.height=2}
sample_size_upset_data <-strats_data_with_filters %>%
  mutate(`ants excluded` = ants_removed,
         `female removed` = females_removed,
         `female present at intiation` = mom_at_init,
         `her first clutch` = clutch_visited_order == 1,
         `first clutch she initiated` = clutch_initiated_order == 1,
         `female marked` = !grepl("U", Female_ID),
         `female disappeared` = !(visit_ends < last_day_fID),
         `unknown whether visited` = is.na(`visited in 4 days`)) %>%
  select(Female_ID, location,
         `ants excluded`, `female removed`,
         `female present at intiation`, 
         `first clutch she initiated`,
         `her first clutch`,
         `female marked`, `female disappeared`, `unknown whether visited`, 
         `Figure 3 (dur histograms)`, 
         `Figure 4 (dur vs 1st visit)`,
         `Text: 4 different strats`) %>%
  pivot_longer(cols = `ants excluded`:`unknown whether visited`,
               names_to = "filter_name",
               values_to = "filter_true") %>%
  filter(filter_true) %>%
  group_by(Female_ID, location, 
           `Text: 4 different strats`,
           `Figure 3 (dur histograms)`, `Figure 4 (dur vs 1st visit)`) %>%
  summarize(filters = list(filter_name))

sample_size_upset_data %>% ggplot(aes(x=filters, fill = `Text: 4 different strats`)) +
    geom_bar() +
    scale_x_upset() +
  theme_publilia()

sample_size_upset_data %>% ggplot(aes(x=filters, fill = `Figure 3 (dur histograms)`)) +
    geom_bar() +
    scale_x_upset() +
  theme_publilia()

sample_size_upset_data %>% ggplot(aes(x=filters, fill = `Figure 4 (dur vs 1st visit)`)) +
    geom_bar() +
    scale_x_upset() +
  theme_publilia()
```

## Text 
Most females laid their first eggs by initiating their own clutch while some females started by visiting an existing clutch (n=115 and 36 respectively). 
```{r}
strats_data_with_filters %>%
  filter(`Text: 4 different strats`) %>%
  count(clutch_initiated_order == 1)

visited_1st_4d_data_tb %>%
  filter(!females_removed,
         clutch_visited_order == 1) %>%
  count(clutch_initiated_order == 1)

print(paste("% (not removed) females that started the season by visiting an existing clutch:", 36/151*100))
print(paste("% (not removed) females that started by initiating their own clutch:", 115/151*100))

visited_1st_4d_data_tb %>%
  filter(females_removed,
         clutch_visited_order == 1) %>%
  count(clutch_initiated_order == 1)
62/100

visited_1st_4d_data_tb %>%
  filter(clutch_visited_order == 1) %>%
  count(clutch_initiated_order == 1)
62/215
```

Visits by secondary females were typically short (median = X days) and only 2 visitors remained through hatching (Figure 2B). 
```{r}
visited_1st_4d_data_tb %>%
  filter(!females_removed,
         !mom_at_init,
         visit_ends < last_day_fID) %>%
  summarize(n = n(),
            n_NA = sum(is.na(guard_duration)),
            mean_gd = mean(as.numeric(guard_duration, "days"), na.rm=T),
            med_gd = median(as.numeric(guard_duration, "days"), na.rm=T))
```

## Figure 3
*Figure 3. The distribution of desertion times relative to hatching* (desertion date – hatch date) for females on the first clutch they initiated in the ant exclusion (black) and control (red) enclosures, for clutches that were not visited by a secondary female within 4 days of initiation (A) and for clutch that were visited by a secondary female within 4 days of initiation (B). Desertion time = 0 (dashed) is the day nymphs were first observed, and desertion time = -20 (dotted) is the mean initiation date relative to hatching.
```{r, fig.width=3, fig.height=3}
#visit_colors <- rev(unique(ggplot_build(Fig1_v1D)$data[[1]]$fill))
visit_colors <- c("#66C2A5", "#FC8D62")

hist_strips <- strip_nested(
     # Horizontal strips
     background_y = list(
       element_rect(fill = visit_colors[1]), 
       element_rect(fill = visit_colors[2]), 
       element_blank(), element_blank(), 
       element_blank(), element_blank()),
     text_y = list(
       element_text(color = c("black")), 
       element_text(color = c("black")), 
       element_blank(), element_blank(), 
       element_blank(), element_blank()),
     by_layer_y = FALSE
)

base_text <- expand.grid(ants = c("Ants removed", "Control"),
            `visited in 4 days` = c("Not visited\nwithin first 4 days", 
                                    "Visited\nwithin first 4 days")) %>%
  tibble()

hatch_text <- base_text %>%
  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited\nwithin first 4 days", 
         "Hatch date", 
         ""))

(guarding_durations_plot_2023 <- strats_data_with_filters %>%
  filter(`Figure 3 (dur histograms)`) %>%
  mutate(`visited in 4 days` = 
           ifelse(`visited in 4 days` == "Visited", 
                  "Visited\nwithin first 4 days", 
                  "Not visited\nwithin first 4 days")) %>%
  ggplot(aes(x=guard_duration, fill=ants)) +
  geom_histogram(binwidth = 4) +
  theme_publilia() +
  xlab("Guarding duration") +
  ylab("Number of females") +
  scale_y_continuous(breaks = c(0,4,8),
                     labels = label_number(accuracy = 1)) +
  scale_color_manual(values = c("black", "brown1")) +
  scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = 20, linetype="dashed", 
                color = "gray", size=1) +
  ggh4x::facet_grid2(vars(`visited in 4 days`, ants), 
                     strip = hist_strips) +
  theme(strip.background = element_rect(color = NA),
        strip.text = element_text(size = 12),
        legend.justification = c(1,1),
        legend.position = c(1,0.2),
        legend.text = element_text(size = 12)) +
  geom_text(data = hatch_text,
            aes(x = 20, y = Inf, label = label),
            hjust = -0.1, vjust = 0, color = "gray", fontface = "bold") +
  coord_cartesian(clip = "off"))
```

# 2 - Early visits by other females lead to early desertion of clutches

## Figure 4
*Figure 4. The guarding duration (days) of initiating females who were first visited by a secondary female on different numbers of days after initiation.* Day 0 represents females that were visited on the first day eggs were observed (i.e. more than one female was on the clutch when eggs were first observed). Violin plots show the density of observations. Letters signify factor levels that are not significantly different (p-value < 0.05 from a Dunn test after multiple testing correction using the Holm-Bonferroni method). The colors indicate whether the clutch was visited (orange) or not (green) within the first 4 days after initiation.
```{r, fig.width=3, fig.height=2}
(Fig1_v1D <- strats_data_with_filters %>%
  filter(`Figure 4 (dur vs 1st visit)`) %>% 
  ggplot(aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
  geom_violin(aes(fill=vis_cat%in%c("0","1 to 4")), color = NA, trim=T, size=2, alpha=0.50) +
  geom_jitter(aes(color=vis_cat%in%c("0","1 to 4")), width=0.1, size=3) +
  scale_color_brewer(palette="Set2") + scale_fill_brewer(palette="Set2") +
  geom_text(data=strats_cuts_v1.multcompLetters, 
            aes(x=vis_cat, y=-4, label=label,
                color=vis_cat %in% c("0","1 to 4")), 
              fontface="bold", size=6) +
  xlab("Day of first visit (Days since initiation)") +
  ylab("Guard duration of initiating female") +
  theme_publilia() +
  theme(legend.position = "none"))
```

### 2023-07-28 manuscript/Manuscript_runfile.Rmd
init `Manuscript_runfile.Rmd`; see issue #2

@@
   # Remove one female who has dubious data (See note ** below)
-  filter(!is.na(vis_cat)) %>%
+  #filter(!is.na(vis_cat)) %>%
   # Build logicals representing inclusion in different plots
@@
            !females_removed & 
-           clutch_visited_order == 1,
+           clutch_visited_order == 1 &
+           !is.na(num_at_init),
          `Figure 4 (dur vs 1st visit)` = 
@@
            !grepl("U", Female_ID) & 
-           visit_ends < last_day_fID,
+           visit_ends < last_day_fID &
+           !is.na(num_at_init),
          `Figure 3 (dur histograms)` = 
@@
            visit_ends < last_day_fID & 
-           !is.na(`visited in 4 days`))
+           !is.na(`visited in 4 days`) &
+           !is.na(num_at_init))
 
@@
 In any case she was never visited and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
+
+# ** 2023.07.28: c("D_Rwyw", "E_Rgrw", "E_Gkgg", "F_Yrgw") on c("D82_12", "E148_6", "E40_9",  "F4_6") were similar. See github issue #2.
 ```
@@
 *To double-check that we understand how we've filtered the data for each sub-analysis, we can represent each filtering regime as an upset plot*
-```{r, fig.width=6, fig.height=2}
-sample_size_upset_data <-strats_data_with_filters %>%
+```{r, fig.width=10, fig.height=4}
+sample_size_upset_data <- strats_data_with_filters %>%
   mutate(`ants excluded` = ants_removed,
@@
          `female disappeared` = !(visit_ends < last_day_fID),
-         `unknown whether visited` = is.na(`visited in 4 days`)) %>%
+         `unknown whether visited` = is.na(`visited in 4 days`),
+         `initiator known` = !is.na(num_at_init)) %>%
   select(Female_ID, location,
@@
          `her first clutch`,
-         `female marked`, `female disappeared`, `unknown whether visited`, 
+         `female marked`, `female disappeared`, `unknown whether visited`, `initiator known`, 
          `Figure 3 (dur histograms)`, 
@@
          `Text: 4 different strats`) %>%
-  pivot_longer(cols = `ants excluded`:`unknown whether visited`,
+  pivot_longer(cols = `ants excluded`:`initiator known`,
                names_to = "filter_name",
@@
 
-sample_size_upset_data %>% ggplot(aes(x=filters, fill = `Text: 4 different strats`)) +
+sample_size_upset_data %>% 
+  ggplot(aes(x=filters, fill = `Text: 4 different strats`)) +
     geom_bar() +
     scale_x_upset() +
+    geom_text(stat='count', aes(label=after_stat(count)), vjust=-1) +
   theme_publilia()
 
-sample_size_upset_data %>% ggplot(aes(x=filters, fill = `Figure 3 (dur histograms)`)) +
+sample_size_upset_data %>% 
+  ggplot(aes(x=filters, fill = `Figure 3 (dur histograms)`)) +
     geom_bar() +
     scale_x_upset() +
+  geom_text(stat='count', aes(label=after_stat(count)), vjust=-1) +
   theme_publilia()
 
-sample_size_upset_data %>% ggplot(aes(x=filters, fill = `Figure 4 (dur vs 1st visit)`)) +
+sample_size_upset_data %>% 
+  ggplot(aes(x=filters, fill = `Figure 4 (dur vs 1st visit)`)) +
     geom_bar() +
     scale_x_upset() +
+  geom_text(stat='count', aes(label=after_stat(count)), vjust=-1) +
   theme_publilia()
@@
 ## Text 
-Most females laid their first eggs by initiating their own clutch while some females started by visiting an existing clutch (n=115 and 36 respectively). 
 ```{r}
-strats_data_with_filters %>%
+n_start_by_init <- strats_data_with_filters %>%
   filter(`Text: 4 different strats`) %>% 
-  count(clutch_initiated_order == 1)
+  pull(clutch_initiated_order) %>% 
+  sum(.data == 1, na.rm = TRUE)
 
-visited_1st_4d_data_tb %>%
-  filter(!females_removed,
-         clutch_visited_order == 1) %>%
-  count(clutch_initiated_order == 1)
+n_start_by_visit <- strats_data_with_filters %>%
+  filter(`Text: 4 different strats`) %>% 
+  pull(clutch_initiated_order) %>% 
+  is.na() %>% sum()
 
-print(paste("% (not removed) females that started the season by visiting an existing clutch:", 36/151*100))
-print(paste("% (not removed) females that started by initiating their own clutch:", 115/151*100))
+# visited_1st_4d_data_tb %>%
+#   filter(!females_removed,
+#          clutch_visited_order == 1) %>%
+#   count(clutch_initiated_order == 1)
 
-visited_1st_4d_data_tb %>%
-  filter(females_removed,
-         clutch_visited_order == 1) %>%
-  count(clutch_initiated_order == 1)
-62/100
-
-visited_1st_4d_data_tb %>%
-  filter(clutch_visited_order == 1) %>%
-  count(clutch_initiated_order == 1)
-62/215
+# print(paste("% (not removed) females that started the season by visiting an existing clutch:", 36/151*100))
+# print(paste("% (not removed) females that started by initiating their own clutch:", 115/151*100))
+# 
+# visited_1st_4d_data_tb %>%
+#   filter(females_removed,
+#          clutch_visited_order == 1) %>%
+#   count(clutch_initiated_order == 1)
+# 62/100
+# 
+# visited_1st_4d_data_tb %>%
+#   filter(clutch_visited_order == 1) %>%
+#   count(clutch_initiated_order == 1)
+# 62/215
 ```
+Most females laid their first eggs by initiating their own clutch while some females started by visiting an existing clutch (n=`r n_start_by_init` and `r n_start_by_visit` respectively).
 

### 2023-08-08 scripts/Publilia-01-qc.Rmd
init `Publilia-03-survivorship.Rmd` and move most of the survivorship data prep to qc Rmd.

@@
 
-# 6 - Write data to `.rds` for further analysis in clean environment
+# 6 - Write data for `Publilia-02-strats.Rmd` to `.rds` for further analysis in clean environment
+
+## `Publilia-02-strats.Rmd`
 ```{r}
@@
 ```
+
+***
+
+*Prep data for `Publilia-03-survivorship.Rmd`:*
+
+# 7 - Assigning nymph origins
+
+Nymphs migrate away from their natal leaf.
+On plants with multiple clutches, it was sometimes possible to determine the origin of nymphs later in the season because sometimes groups of nymph don't travel very far from their natal leaf and mix with other groups.
+I manually curated examples of this, so that clutch-level stats on hatching success and nymph survivorship could be determined on the plants with multiple clutches.
+Some clutches (as a rule only on multi-clutch plants) did not have a clear record of nymphs that emigrated from the natal leaf and thus could not be included in future clutch-level analyses of survivorship.
+
+## 7.1 - Adding second gen adult counts per leaf to clutch status stats
+```{r}
+# counting adults
+eA_status_v1 <- All_data_v6 %>%
+  group_by(row_number()) %>% # sum of newly exclosed adults
+  filter(any(!is.na(c(New_eA, Old_eA)))) %>%
+  mutate(n_newA = ifelse(is.na(New_eA),
+                         NA,
+                         sum(as.numeric(regmatches(New_eA, gregexpr("[0-9]+", New_eA))[[1]]))),
+         n_oldA = ifelse(is.na(Old_eA),
+                         NA,
+                         sum(as.numeric(regmatches(Old_eA, gregexpr("[0-9]+", Old_eA))[[1]]))),
+         n_A = sum(n_newA, n_oldA, na.rm = TRUE)) %>%
+  ungroup() %>%
+  select(Date, location, n_newA, n_oldA, n_A)
+
+All_data_v6_clutch_status_stats_v2 <- All_data_v6 %>%
+  # add egg measures, clutch status stats (including initiation dates, hatch dates, egg fate, etc)
+  left_join(clutch_status_v2, by = c("location", "Date")) %>%
+  left_join(clutch_status_stats_v1, by = c("location")) %>%
+  left_join(eA_status_v1, by = c("Date", "location")) %>%
+  left_join(select(clutch_status_guarding_summary_v2, location, never_hatched)) %>%
+  mutate(N1 = as.numeric(N1),
+         N2 = as.numeric(N2),
+         N5 = as.numeric(N5))
+```
+
+## 7.2 - Manually check nymph origins for revision
+First create a table of all entried from clutches that were not flagged in the field as having ambiguous origin (e.g.
+"leaf 6 or 9") in cases were more than one clutch was on the plant.
+These were revised manually to specify a leaf of origin for the nymphs, where possible.
+```{r}
+NOr_status_resolveable_all_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>% 
+  select(Date, Dorm, Plant, Leaf, location, 
+         egg_num, N1, N2, N5, n_A, nymph_origin, initiation_date, hatch_date,
+         any_NOr_ambig_loc, Omit_for_abandon_time, never_hatched,
+         n_clutches_on_plant) %>%
+  # keep only entries with some nymphs or adults on a leaf
+  # OR entries for leaves where clutches have been initiated
+  group_by(row_number()) %>%
+  filter(!is.na(Leaf) & any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) | 
+           Date >= initiation_date) %>% # nrow = 17944
+  # flag entries where the nymph origin is text (typically ambiguous, e.g. "8 or 9")
+  mutate(NOr_ambig_entry = !is.na(nymph_origin) & is.na(as.numeric(nymph_origin))) %>% 
+  ungroup() %>%
+  # get rid of duplicate rows from multiple females in the same location
+  distinct(Date, location, .keep_all = TRUE) %>% # nrow = 15674
+  group_by(Dorm, Plant) %>%
+    # filter out any plants with a clutch that was omitted for abandon time
+    filter(!any(!is.na(Omit_for_abandon_time))) %>%
+    # flag plants with any ambiguous entries (e.g. "8 or 9") skip for checking
+    mutate(NOr_ambig_plant = any(NOr_ambig_entry)) %>%
+  ungroup()
+
+NOr_status_resolveable_mult_clutches <- NOr_status_resolveable_all_unambig_clutches %>% # nrow = 15674
+  group_by(Dorm, Plant) %>%
+    # plants with mutliple clutches only
+    filter(any(n_clutches_on_plant > 1)) %>%
+  ungroup() %>%
+  group_by(row_number()) %>%
+    # flag for manual checking entries with any nymphs/adults, missing nymph origin, 
+    # but not flagged for ambiguous origin in the field.
+    # these are the most likely to be easily resolved with minimal work
+    mutate(revise_NOr = ifelse(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) &
+             !NOr_ambig_plant,
+           "MANUAL CHECK",
+           NA)) %>% 
+  ungroup()
+
+NOr_manual_check_table <- NOr_status_resolveable_mult_clutches %>%
+  group_by(Dorm, Plant) %>%
+    filter(any(revise_NOr == "MANUAL CHECK")) %>% # nrow = 2830
+  ungroup() %>%
+    group_by(row_number()) %>%
+    filter(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0)) %>%
+  ungroup() %>%
+  select(Date, Dorm, Plant, Leaf, location, egg_num, N1, N2, N5, n_A, nymph_origin,
+         initiation_date, hatch_date,
+         revise_NOr) %>%
+  arrange(Dorm, as.numeric(Plant), as.numeric(Leaf), Date)
+# 83 clutches on 34 plants to check
+
+# write_csv(NOr_manual_check_table %>% filter(revise_NOr == "MANUAL CHECK"), "NOr_manual_check_tmp.csv")
+
+NOr_manual_revisions <- read_xlsx(in_filename, sheet = "NOr_manual_check", col_types = c("date", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "logical", "text")) %>%
+  mutate(Date = as_date(Date),
+         NOr_rev_loc_manual = paste0(Dorm, Plant, "_", NOr_revised)) %>%
+  filter(!cant_resolve) %>%
+  select(Date, location, NOr_rev_loc_manual, NOr_revised_manual = NOr_revised)
+
+NOr_manual_revisions %>%
+  distinct(NOr_rev_loc_manual) # 43/83 initiated clutches (43/59 hatched) with successfully revised NOr
+```
+
+## 7.3 - Implement revisions by creating the new variables NOr_revised and NOr_rev_loc
+```{r}
+# if nymph origin was clearly resolveable, the revisions were made in NOr_manual_revisions
+# updating NOr_status with revisions so that it can be left_joined to other data and
+# counts of nymphs and adults on NOr can be calculated
+NOr_status_revised_all_unambig_clutches <- NOr_status_resolveable_all_unambig_clutches %>%
+  left_join(NOr_manual_revisions, by = c("Date", "location")) %>%
+  group_by(Dorm, Plant) %>%
+    mutate(lone_hatcher_leaf = ifelse(length(unique(Leaf[!is.na(initiation_date)])) == 1,
+                                 unique(Leaf[!is.na(initiation_date)]),
+                                 NA),
+           NOr_revised = ifelse(!is.na(NOr_revised_manual),
+                                       NOr_revised_manual,
+                                ifelse(any(!is.na(lone_hatcher_leaf)),
+                                       lone_hatcher_leaf,
+                                       # if no clutches hatched on the plant, NOr_revised = Leaf
+                                       # for leaves with eggs
+                                       ifelse(!any(!is.na(hatch_date)) & !is.na(egg_num),
+                                              Leaf,
+                                              NA)))) %>%
+  ungroup() %>%  
+  group_by(location) %>%
+    mutate(NOr_revised = ifelse(any(NOr_revised == Leaf) & is.na(NOr_revised),
+                                Leaf,#unique(NOr_revised[!is.na(NOr_revised)]),
+                                NOr_revised)) %>%
+  ungroup() %>%
+  mutate(NOr_rev_loc = ifelse(is.na(NOr_revised),
+                              NA,
+                              paste0(Dorm, Plant, "_", NOr_revised))) %>%
+  select(Date, location, NOr_revised, NOr_rev_loc) %>%
+  filter(!is.na(NOr_rev_loc))
+
+All_data_v6_N_NOr_counts_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>%
+  right_join(NOr_status_revised_all_unambig_clutches, by = c("Date", "location")) %>%
+  group_by(Date, Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
+    summarize(N1_NOr = sum(N1, na.rm= TRUE),
+              N2_NOr = sum(N2, na.rm= TRUE),
+              N5_NOr = sum(N5, na.rm= TRUE),
+              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
+              A_NOr = sum(n_A, na.rm= TRUE),
+              N5plusA_NOr = sum(N5, n_A, na.rm= TRUE)) %>%
+  ungroup() # n = 186
+
+# All_data_v6_N_NOr_counts_unambig_clutches %>% distinct(Dorm, Plant, NOr_rev_loc) # n = 186
+
+All_data_v6_N_NOr_counts_unambig_clutches_summary <- All_data_v6_N_NOr_counts_unambig_clutches %>%
+  group_by(Date) %>%
+    mutate(mean_N_NOr = mean(N_NOr, na.rm = TRUE),
+           mean_N1_NOr = mean(N1_NOr, na.rm = TRUE),
+           mean_N2_NOr = mean(N2_NOr, na.rm = TRUE),
+           mean_N5_NOr = mean(N5_NOr, na.rm = TRUE),
+           mean_A_NOr = mean(A_NOr, na.rm = TRUE),
+           mean_N5plusA_NOr = mean(N5plusA_NOr, na.rm = TRUE),
+           All_N_NOr = sum(N_NOr),
+           All_A_NOr = sum(A_NOr)) %>%
+  ungroup() %>%
+  group_by(Date, Dorm) %>%
+    mutate(All_N_NOr_Dorm = sum(N_NOr),
+           All_N1_NOr_Dorm = sum(N1_NOr),
+           All_N2_NOr_Dorm = sum(N2_NOr),
+           All_N5_NOr_Dorm = sum(N5_NOr),
+           All_A_NOr_Dorm = sum(sum(A_NOr))) %>%
+  ungroup()
+
+ggplot(data = All_data_v6_N_NOr_counts_unambig_clutches_summary) +
+  geom_boxplot(aes(x = Date, y = N_NOr, group = Date)) +
+  geom_line(aes(x = Date, y = mean_N_NOr), color = "red")
+
+ggplot(data = All_data_v6_N_NOr_counts_unambig_clutches_summary) +
+  geom_line(aes(x = Date, y = mean_N_NOr), color = "black") +
+  geom_line(aes(x = Date, y = mean_N1_NOr), color = "green") +  
+  geom_line(aes(x = Date, y = mean_N2_NOr), color = "blue") +
+  geom_line(aes(x = Date, y = mean_N5_NOr), color = "purple") +
+  geom_line(aes(x = Date, y = mean_A_NOr), color = "pink") +
+  geom_line(aes(x = Date, y = mean_N5plusA_NOr), color = "red")
+
+ggplot(data = All_data_v6_N_NOr_counts_unambig_clutches_summary) +
+  geom_line(aes(x = Date, y = All_N_NOr), color = "black")
+
+ggplot(data = All_data_v6_N_NOr_counts_unambig_clutches_summary) +
+  geom_line(aes(x = Date, y = All_N_NOr_Dorm, color = Dorm))
+
+All_data_v6_all_nymphs_unambig_clutches <- All_data_v6_N_NOr_counts_unambig_clutches %>%
+  group_by(Date) %>%
+    summarize(All_N_NOr = sum(N_NOr)) %>%
+  ungroup()
+
+ggplot(data = All_data_v6_all_nymphs_unambig_clutches) +
+  geom_line(aes(x = Date, y = All_N_NOr), color = "black")
+
+All_data_v6_max_N_NOr_counts_unambig_clutches <-
+  All_data_v6_N_NOr_counts_unambig_clutches %>%
+  group_by(Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
+    summarize(max_N_NOr = max(N_NOr)) %>%
+  ungroup()
+
+clutch_status_stats_v1_unambig_clutches_hatch_success <- clutch_status_stats_v1 %>%
+  separate(location, c("DormPlant", "Leaf"), sep = "_", remove = FALSE) %>%
+  mutate(Dorm = substr(DormPlant, 1, 1),
+         Plant = substring(DormPlant, 2)) %>%
+  left_join(distinct(clutch_status_guarding_summary_v2, location, never_hatched)) %>%
+  right_join(All_data_v6_max_N_NOr_counts_unambig_clutches, by = c("Dorm", "Plant", "Leaf" = "NOr_revised")) %>%
+  # why did I originally say to make hatch_success = NA if never_hatched == TRUE?
+  mutate(hatch_success = ifelse(!is.na(initiation_date) & is.na(hatch_date),
+                                0,
+                                max_N_NOr/max_egg_num))
+```
+
+## 7.4 - Flag and resolve ambiguous nymph origins
+
+Is 190/ really the best we can do for the sample size of clutches with known hatching success?
+```{r}
+clutch_status_guarding_summary_v2 %>%
+# add number of clutches per plant
+  separate(location, c("DormPlant", "Leaf"), "_", remove = FALSE) %>%
+  mutate(Dorm = substr(DormPlant, 1,1),
+         Plant = substring(DormPlant, 2)) %>%
+  distinct(location, n_clutches_on_plant, initiation_date, any_NOr_ambig_loc) %>%
+  group_by(n_clutches_on_plant == 1, initiation_date <= as_date("2019-06-10"), any_NOr_ambig_loc) %>%
+  summarize(N = n()) %>%
+  ungroup()
+
+# there are 319 unique clutches with known inits that have not been flagged for ambig nymph origin in the field
+clutch_status_guarding_summary_v2 %>%
+# add number of clutches per plant
+  separate(location, c("DormPlant", "Leaf"), "_", remove = FALSE) %>%
+  mutate(Dorm = substr(DormPlant, 1,1),
+         Plant = substring(DormPlant, 2)) %>%
+  distinct(location, n_clutches_on_plant, initiation_date, any_NOr_ambig_loc) %>%
+  group_by(!is.na(initiation_date), any_NOr_ambig_loc) %>%
+  summarize(N = n()) %>%
+  ungroup()
+
+NOr_status_resolveable_all_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>% 
+  select(Date, Dorm, Plant, Leaf, location, 
+         egg_num, N1, N2, N5, n_A, nymph_origin, initiation_date, hatch_date,
+         any_NOr_ambig_loc, Omit_for_abandon_time, never_hatched,
+         n_clutches_on_plant) %>%
+  # keep only entries with some nymphs or adults on a leaf
+  # OR entries for leaves where clutches have been initiated
+  group_by(row_number()) %>%
+  filter(!is.na(Leaf) & any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) | 
+           Date >= initiation_date) %>% # nrow = 17944
+  # flag entries where the nymph origin is text (typically ambiguous, e.g. "8 or 9")
+  mutate(NOr_ambig_entry = !is.na(nymph_origin) & is.na(as.numeric(nymph_origin))) %>% 
+  ungroup() %>%
+  # get rid of duplicate rows from multiple females in the same location
+  distinct(Date, location, .keep_all = TRUE) %>% # nrow = 15674
+  group_by(Dorm, Plant) %>%
+    # filter out any plants with a clutch that was omitted for abandon time
+    filter(!any(!is.na(Omit_for_abandon_time))) %>%
+    # flag plants with any ambiguous entries (e.g. "8 or 9") skip for checking
+    mutate(NOr_ambig_plant = any(NOr_ambig_entry)) %>%
+  ungroup()
+
+NOr_status_resolveable_all_unambig_clutches %>% 
+  filter(!is.na(initiation_date)) %>% 
+  distinct(location) # 314
+
+NOr_status_resolveable_mult_clutches <- NOr_status_resolveable_all_unambig_clutches %>% # nrow = 15674
+  group_by(Dorm, Plant) %>%
+    # plants with mutliple clutches only
+    filter(any(n_clutches_on_plant > 1)) %>%
+  ungroup() %>%
+  group_by(row_number()) %>%
+    # flag for manual checking entries with any nymphs/adults, missing nymph origin, 
+    # but not flagged for ambiguous origin in the field.
+    # these are the most likely to be easily resolved with minimal work
+    mutate(revise_NOr = ifelse(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) &
+             !NOr_ambig_plant,
+           "MANUAL CHECK",
+           NA)) %>% 
+  ungroup()
+
+NOr_status_resolveable_mult_clutches %>%
+  filter(!is.na(initiation_date)) %>%
+  distinct(location, revise_NOr) %>%
+  group_by(revise_NOr) %>%
+  summarize(n())
+
+############## looking at what clutches are NOT included in hatch success data
+clutch_status_stats_v1 %>%
+  separate(location, c("DormPlant", "Leaf"), sep = "_", remove = FALSE) %>%
+  mutate(Dorm = substr(DormPlant, 1, 1),
+         Plant = substring(DormPlant, 2)) %>%
+  left_join(distinct(clutch_status_guarding_summary, location, never_hatched)) %>%
+  full_join(All_data_v6_max_N_NOr_counts_unambig_clutches, by = c("Dorm", "Plant", "Leaf" = "NOr_revised")) %>%
+  # why are so many "never_hatched" NA?
+  mutate(hatch_success = ifelse(is.na(hatch_date),
+                                0,
+                                max_N_NOr/max_egg_num)) %>%
+  group_by(Dorm, Plant) %>%
+  mutate(any_NOr_ambig_loc_Plant = any(any_NOr_ambig_loc)) %>%
+  ungroup() %>%
+  filter(is.na(hatch_success), !any_NOr_ambig_loc_Plant) %>% View()
+
+hatch_success_tmp1 <- clutch_status_stats_v1 %>%
+  separate(location, c("DormPlant", "Leaf"), sep = "_", remove = FALSE) %>%
+  mutate(Dorm = substr(DormPlant, 1, 1),
+         Plant = substring(DormPlant, 2)) %>%
+  left_join(distinct(clutch_status_guarding_summary_v2, location, never_hatched)) %>%
+  full_join(All_data_v6_max_N_NOr_counts_unambig_clutches, by = c("Dorm", "Plant", "Leaf" = "NOr_revised")) %>%
+  # why are so many "never_hatched" NA?
+  mutate(hatch_success = ifelse(!is.na(initiation_date) & is.na(hatch_date),
+                                0,
+                                max_N_NOr/max_egg_num))
+
+# hatch_success_tmp1 %>%
+#   filter(!is.na(hatch_success), initiation_date <= as_date("2019-06-10")) %>% View()
+
+ggplot(data = filter(hatch_success_tmp1, initiation_date <= as_date("2019-06-10"))) +
+  geom_histogram(aes(x = hatch_success))
+
+```
+
+## 7.5 - Fixing the omission of clutches that never had first instar nymphs
+
+```{r}
+NOr_status_revised_all_unambig_clutches_v2 <- NOr_status_resolveable_all_unambig_clutches %>%
+  left_join(NOr_manual_revisions, by = c("Date", "location")) %>%
+  group_by(Dorm, Plant) %>%
+    mutate(lone_hatcher_leaf = ifelse(length(unique(Leaf[!is.na(initiation_date)])) == 1,
+                                 unique(Leaf[!is.na(initiation_date)]),
+                                 NA),
+           NOr_revised = ifelse(!is.na(NOr_revised_manual), # if I manually annotated a revised location
+                                       NOr_revised_manual, # make manual location the new nymph origin
+                                ifelse(any(!is.na(lone_hatcher_leaf)), # if only one clutch hatched on the plant
+                                       lone_hatcher_leaf, # make that clutch the new nymph origin
+                                       # if no clutches hatched on the plant, NOr_revised = Leaf
+                                       # for leaves with eggs
+                                       ifelse(!any(!is.na(hatch_date)) & !is.na(egg_num), # if no clutches hatched on the plant (but there are eggs)
+                                              Leaf, # make the given leaf the new nymph origin
+                                              NA)))) %>% # BUT THIS STILL EXCLUDES CLUTCHES THAT DIDN'T HATCH ON A PLANT WITH SOME CLUTCHES THAT DID HATCH
+  ungroup() %>%  
+  group_by(location) %>%
+    mutate(NOr_revised = ifelse(any(NOr_revised == Leaf) & is.na(NOr_revised), # DOES THIS INCLUDE UNHATCHED CLUTCHES? NO
+                                Leaf,#unique(NOr_revised[!is.na(NOr_revised)]),
+                                NOr_revised),
+           NOr_revised = ifelse(any(is.na(NOr_revised)) & # if no revised nymph origin yet
+                                                  any(!is.na(egg_num)&egg_num>0 & !any(!is.na(N1)&N1>0)), # and N1 never on clutch (not hatched or spuriously visited by N1)
+                                Leaf, # make this leaf the new nymph origin (so we include unhatched clutches)
+                                NOr_revised)) %>% 
+  ungroup() %>%
+  mutate(NOr_rev_loc = ifelse(is.na(NOr_revised),
+                              NA,
+                              paste0(Dorm, Plant, "_", NOr_revised))) %>%
+  select(Date, location, NOr_revised, NOr_rev_loc) %>%
+  filter(!is.na(NOr_rev_loc))
+
+All_data_v6_N_NOr_counts_unambig_clutches_v2 <- All_data_v6_clutch_status_stats_v2 %>%
+  right_join(NOr_status_revised_all_unambig_clutches_v2, by = c("Date", "location")) %>%
+  group_by(Date, Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
+    summarize(N1_NOr = sum(N1, na.rm= TRUE),
+              N2_NOr = sum(N2, na.rm= TRUE),
+              N5_NOr = sum(N5, na.rm= TRUE),
+              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
+              A_NOr = sum(n_A, na.rm= TRUE),
+              N5plusA_NOr = sum(N5, n_A, na.rm= TRUE)) %>%
+  ungroup() # n = 186
+
+# All_data_v6_N_NOr_counts_unambig_clutches %>% distinct(Dorm, Plant, NOr_rev_loc) # n = 186
+
+All_data_v6_N_NOr_counts_unambig_clutches_summary_v2 <- All_data_v6_N_NOr_counts_unambig_clutches_v2 %>%
+  group_by(Date) %>%
+    mutate(mean_N_NOr = mean(N_NOr, na.rm = TRUE),
+           mean_N1_NOr = mean(N1_NOr, na.rm = TRUE),
+           mean_N2_NOr = mean(N2_NOr, na.rm = TRUE),
+           mean_N5_NOr = mean(N5_NOr, na.rm = TRUE),
+           mean_A_NOr = mean(A_NOr, na.rm = TRUE),
+           mean_N5plusA_NOr = mean(N5plusA_NOr, na.rm = TRUE),
+           All_N_NOr = sum(N_NOr),
+           All_A_NOr = sum(A_NOr)) %>%
+  ungroup() %>%
+  group_by(Date, Dorm) %>%
+    mutate(All_N_NOr_Dorm = sum(N_NOr),
+           All_N1_NOr_Dorm = sum(N1_NOr),
+           All_N2_NOr_Dorm = sum(N2_NOr),
+           All_N5_NOr_Dorm = sum(N5_NOr),
+           All_A_NOr_Dorm = sum(sum(A_NOr))) %>%
+  ungroup()
+
+```
+
+# 8 - Calculate hatch success and nymph survivorship
+
+Calculate hatch success (strict sense; max N1 / max eggs) and nymph survivorship (max N5+A / max eggs AND/OR max N5+A / max N1)
+
+- Filtered out clutches with outlier numbers of N1 or N5 etc at early or late clutch ages, which were assumed to be cases of immigration that weren't caught during manual nymph origin filtering
+```{r}
+# Filter to only include curated list of clutches with unambiguous nymph counts after accounting for immigration to non-natal leaves and then sum all nymphs (including emigrants) for each clutch
+# I also added clutch_age variables to help identify clutches that were started too close to the end of sampling to be useful
+clutch_unambig_NOr_revised_ENAa_summary_v2 <- All_data_v6_clutch_status_stats_v2 %>%
+  right_join(NOr_status_revised_all_unambig_clutches_v2, by = c("Date", "location")) %>%
+  select(Date, NOr_rev_loc, location, egg_num, N1, N2, N5, n_A, ants_L) %>%
+    # remove any duplicates - I need to figure out why there are dups later but for 4th yr talk
+  distinct(Date, NOr_rev_loc, location, egg_num, N1, N2, N5, n_A, ants_L, .keep_all = TRUE) %>%
+  mutate(egg_num_NOr = ifelse(NOr_rev_loc == location, egg_num, NA)) %>%
+  group_by(Date, NOr_rev_loc) %>%
+    summarize(eggs_NOr = first(egg_num_NOr[!is.na(egg_num_NOr)]), # only use eggs from origin leaf!
+              N1_NOr = sum(N1, na.rm= TRUE),
+              N2_NOr = sum(N2, na.rm= TRUE),
+              N5_NOr = sum(N5, na.rm= TRUE),
+              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
+              A_NOr = sum(n_A, na.rm= TRUE),
+              N5toA_NOr = sum(N5, n_A, na.rm= TRUE),
+              ants_NOr = sum(ants_L, na.rm = TRUE)) %>%
+  ungroup() %>%
+  left_join(filter(clutch_status_guarding_summary_v2, mom_at_init), by = c("NOr_rev_loc" = "location")) %>%
+  mutate(clutch_age1 = Date - initiation_date,
+         clutch_age2 = ceiling((Date - initiation_date)/2)*2,
+         clutch_age4 = ceiling((Date - initiation_date)/4)*4,
+         after_hatch1 = Date - hatch_date,
+         after_hatch2 = ceiling((Date - hatch_date)/2)*2,
+         after_hatch4 = ceiling((Date - hatch_date)/4)*4) %>%
+  select(Date, NOr_rev_loc, clutch_age1, after_hatch1, eggs_NOr, 
+         N1_NOr, N2_NOr, N5_NOr, N_NOr, A_NOr, N5toA_NOr, ants_NOr,
+         init_fem = Female_ID,
+         initiation_date, hatch_date, guard_duration, relative_desert_date,
+         clutch_initiated_order, females_removed, ants_removed, 
+         clutch_age2, clutch_age4, after_hatch2, after_hatch4) #%>%
+  # filter(initiation_date <= as_date("2019-06-10"),
+  #        clutch_age4 <= 68)
+
+max_N1_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  group_by(NOr_rev_loc) %>%
+  arrange(NOr_rev_loc, desc(N1_NOr), Date) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  select(NOr_rev_loc, max_N1_date = Date, max_N1_age = clutch_age1)
+
+max_N5_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  group_by(NOr_rev_loc) %>%
+  arrange(NOr_rev_loc, desc(N5_NOr), Date) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  select(NOr_rev_loc, max_N5_date = Date, max_N5_age = clutch_age1)
+
+max_A_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  group_by(NOr_rev_loc) %>%
+  arrange(NOr_rev_loc, desc(A_NOr), Date) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  select(NOr_rev_loc, max_A_date = Date, max_A_age = clutch_age1)
+
+max_N5toA_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  group_by(NOr_rev_loc) %>%
+  arrange(NOr_rev_loc, desc(N5toA_NOr), Date) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  select(NOr_rev_loc, max_N5toA_date = Date, max_N5toA_age = clutch_age1)
+
+max_N5toA_Date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  group_by(NOr_rev_loc) %>%
+  summarize(max_N1 = max(N1_NOr),
+            max_N5toA = max(N5toA_NOr),
+            max_clutch_age = max(clutch_age1),
+            max_after_hatch = max(after_hatch1),
+            max_Date = max(Date),
+            hatched = any(!is.na(hatch_date)),
+            initiation_date = first(initiation_date)) %>%
+  ungroup() %>%
+  arrange(desc(max_N5toA)) %>%
+  full_join(max_N1_date_v2) %>%
+  full_join(max_N5_date_v2) %>%
+  full_join(max_A_date_v2) %>%
+  full_join(max_N5toA_date_v2)
+
+ggplot(data = max_N5toA_Date_v2) +
+  geom_point(aes(x = initiation_date, y = max_N5toA_age))
+
+ggplot(data = max_N5toA_Date_v2) +
+  geom_point(aes(x = initiation_date, y = max_N1_age))
+
+ggplot(data = max_N5toA_Date_v2) +
+  geom_point(aes(x = initiation_date, y = max_N5_age))
+
+ggplot(data = max_N5toA_Date_v2) +
+  geom_point(aes(x = initiation_date, y = max_A_age))
+
+ggplot(data = max_N5toA_Date_v2) +
+  geom_point(aes(x = max_clutch_age, y = max_N1, 
+                 color = initiation_date >= as_date("2019-06-10")))
+
+ggplot(data = max_N5toA_Date_v2) +
+  geom_point(aes(x = initiation_date, y = max_N1))
+
+ggplot(data = max_N5toA_Date_v2) +
+  geom_point(aes(x = max_clutch_age, y = max_N5toA, 
+                 color = initiation_date >= as_date("2019-06-10")))
+
+ggplot(data = max_N5toA_Date_v2) +
+  geom_point(aes(x = initiation_date, y = max_N5toA))
+
+clutch_unambig_NOr_revised_ENAa_summary_imfilt_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  mutate(N_imm_likely_d15 = clutch_age1 < 15 & N_NOr > 0,
+         N5_imm_likely_d40 = clutch_age1 < 40 & N5_NOr > 0,
+         A_imm_likely_d40 = clutch_age1 < 40 & A_NOr > 0) %>%
+  group_by(NOr_rev_loc) %>%
+    filter(!any(N_imm_likely_d15, N5_imm_likely_d40, A_imm_likely_d40, na.rm = TRUE)) %>% # n = 168
+  ungroup()
+
+clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_v2 <-
+  clutch_unambig_NOr_revised_ENAa_summary_imfilt_v2 %>%
+  group_by(NOr_rev_loc) %>%
+    mutate(hatch_success_N1 = max(N1_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
+           survival_rate = max(N5toA_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
+           prop_E2Ni = max(N1_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
+           prop_E2N = max(N_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
+           prop_Ni2Nv = max(N5toA_NOr, na.rm = TRUE)/max(N1_NOr, na.rm = TRUE),
+           prop_E2Nv = max(N5toA_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
+           n_eggs = max(eggs_NOr, na.rm = TRUE),
+           n_hatched = max(N1_NOr, na.rm = TRUE),
+           n_N = max(N_NOr, na.rm = TRUE),
+           n_survived = max(N5toA_NOr, na.rm = TRUE)) %>%
+  ungroup()
+
+clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2 <- clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_v2 %>%
+  distinct(NOr_rev_loc, n_eggs, n_hatched, n_survived, n_N,
+           prop_E2Ni, prop_Ni2Nv, prop_E2Nv, prop_E2N, hatch_success_N1, survival_rate,
+           initiation_date, hatch_date, females_removed, ants_removed) 
+```
+
+# 9 - Ant counts on clutch
+
+## 9.1 - Some fraction of ants_removed clutches were visited by ants, and vice versa
+```{r}
+ant_counts <- All_data_v6 %>%
+  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+  filter(!is.na(initiation_date)) %>%
+  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+  group_by(location) %>%
+    mutate(b4h=Date>=initiation_date&Date<est_hatch,
+           afh=Date>=est_hatch) %>%
+    summarize(ants_removed=first(ants_removed),
+              females_removed=first(females_removed),
+              n_antsP=sum(ants_P,na.rm=T),
+              ever_antsP=n_antsP>0,
+              mean_antsP=mean(ants_P,na.rm=T),
+              med_antsP=median(ants_P,na.rm=T),
+
+              n_antsP_b4h=sum(ants_P&b4h),
+              ever_antsP_b4h=n_antsP_b4h>0,
+              mean_antsP_b4h=mean(ifelse(b4h,ants_P,NA),na.rm=T),
+              med_antsP_b4h=median(ifelse(b4h,ants_P,NA),na.rm=T),
+
+              n_antsP_afh=sum(ants_P&afh),
+              ever_antsP_afh=n_antsP_afh>0,
+              mean_antsP_afh=mean(ifelse(afh,ants_P,NA),na.rm=T),
+              med_antsP_afh=median(ifelse(afh,ants_P,NA),na.rm=T)) %>%
+  ungroup() %>%
+  mutate(Dorm=substr(location,1,1),
+         ant_treatment=ifelse(ants_removed,"Ants removed","Control"))
+
+ggplot(data=ant_counts,aes(x=Dorm,y=n_antsP, fill=ant_treatment)) +
+  geom_boxplot()
+
+ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP, fill=ant_treatment)) +
+  geom_boxplot()
+
+ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_b4h, fill=ant_treatment)) +
+  geom_boxplot()
+
+ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_afh, fill=ant_treatment)) +
+  geom_boxplot()
+
+ant_counts %>%
+  count(Dorm,ant_treatment,ever_antsP)
+
+ant_counts %>%
+  count(Dorm,ant_treatment,ever_antsP_b4h)
+
+ant_counts %>%
+  count(Dorm,ant_treatment,ever_antsP_afh)
+
+# how many clutches ever had ants in each of the dorms?
+ant_counts %>%
+  ggplot(data=., aes(y=as.numeric(ever_antsP), x=Dorm, fill=ant_treatment)) +
+  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
+  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
+  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
+  theme_publilia()
+
+ant_counts %>%
+  ggplot(data=., aes(y=as.numeric(ever_antsP_b4h), x=Dorm, fill=ant_treatment)) +
+  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
+  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
+  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
+  theme_publilia()
+
+ant_counts %>%
+  ggplot(data=., aes(y=as.numeric(ever_antsP_afh), x=Dorm, fill=ant_treatment)) +
+  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
+  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
+  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
+  theme_publilia()
+
+# how extreme was the break-through?
+ant_counts %>%
+  ggplot(data=., aes(x=mean_antsP_b4h, color=ant_treatment, linetype=females_removed, group=Dorm)) +
+  geom_freqpoly(bins=100)
+
+ant_counts %>%
+  ggplot(data=., aes(x=med_antsP_b4h, color=ant_treatment, linetype=females_removed, group=Dorm)) +
+  geom_freqpoly()
+
+ant_counts %>%
+  ggplot(data=., aes(x=mean_antsP_afh, color=ant_treatment, linetype=females_removed, group=Dorm)) +
+  geom_freqpoly(bins=100)
+
+ant_counts %>%
+  ggplot(data=., aes(x=med_antsP_afh, color=ant_treatment, linetype=females_removed, group=Dorm)) +
+  geom_freqpoly()
+
+# how many clutches actually ever had ants vs. not?
+ant_counts %>%
+  ggplot(data=., aes(x=ever_antsP_b4h, fill=ant_treatment)) +
+  geom_bar() +
+  theme_publilia() + facet_wrap(~females_removed)
+
+ant_counts %>%
+  ggplot(data=., aes(x=ever_antsP_afh, fill=ant_treatment)) +
+  geom_bar() +
+  theme_publilia() + facet_wrap(~females_removed)
+
+ant_counts %>%
+  ggplot(data=., aes(x=ever_antsP_b4h|ever_antsP_afh, fill=ant_treatment)) +
+  geom_bar() +
+  theme_publilia() + facet_wrap(~females_removed)
+
+```
+
+Should I be more lenient with my threshold, so I can have more even sample sizes between "ants" and "no ants"?
+- ants_ever = n_days_ants>0: F = 95-12=83, T = 234-91=143
+- antsP_gt2d = n_days_ants>2: F = 156-33=123, T = 173-70=103 * most even sample size
+- antsP_gt3d = n_days_ants>3: F = 172-39=133, T = 157-64=90
+```{r}
+ant_n_days <- All_data_v6 %>%
+  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+  filter(!is.na(initiation_date)) %>%
+  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+  mutate(ant_treatment=ifelse(ants_removed,"Ants removed","Control"),
+         Dorm=substr(location,1,1)) %>%
+  group_by(Date, location) %>%
+    summarize(any_antsP_day = any(ants_P>0, na.rm=T),
+              females_removed = first(females_removed),
+              ant_treatment = first(ant_treatment),
+              Dorm = first(Dorm)) %>%
+  ungroup() %>%
+  group_by(location) %>%
+    summarize(n_days_ants = sum(as.numeric(any_antsP_day)),
+              females_removed = first(females_removed),
+              ant_treatment = first(ant_treatment),
+              Dorm = first(Dorm))%>%
+  ungroup() %>%
+  mutate(antsP_gt2d = !is.na(n_days_ants)&n_days_ants>2,
+         antsP_gt3d = !is.na(n_days_ants)&n_days_ants>3,
+         ants_everP = is.na(n_days_ants)|n_days_ants>0)
+
+ggplot(ant_n_days, aes(x=Dorm, y=n_days_ants, fill=ant_treatment)) +
+  geom_boxplot()
+
+ggplot(ant_n_days, aes(x=Dorm, y=n_days_ants, fill=ant_treatment)) +
+  geom_violin() +
+  geom_hline(yintercept=2.5)
+
+ant_n_days %>%
+  select(-location) %>%
+  tbl_summary(by=ants_everP)
+
+ant_n_days %>%
+  select(-location) %>%
+  tbl_summary(by=antsP_gt2d)
+
+ant_n_days %>%
+  select(-location) %>%
+  tbl_summary(by=antsP_gt3d)
+```
+
+# 10 - Calculate alternative measures of maternal tenure
+
+`The sum of all females’ egg-guarding durations was more predictive of final clutch size than egg guarding duration of the initiator alone (Table S1 with alternative models and their AICs), showing that females lay eggs while visiting existing clutches.`
+```{r}
+visited_1st_4d_data_tb
+visited_1st_4d_data_tb %>% filter(!is.na(initiation_date))
+visited_1st_4d_data_tb %>% filter(!is.na(initiation_date), !is.na(num_at_init))
+
+##### initiator guarding time: mDb4h
+initiator_days_b4hatch <- visited_1st_4d_data_tb %>%
+  filter(!is.na(initiation_date),
+         # exclude clutches for which the initiators are not known
+         !is.na(num_at_init),
+         mom_at_init) %>%
+  group_by(row_number()) %>%
+  # Use median init to hatch interval (20 days) to est hatch date of clutch with no hatch date
+  mutate(init_dur = ifelse(min(est_hatch, visit_ends) - 
+                                       max(initiation_date, visit_starts) >= 0,
+                           visit_ends-initiation_date+1, 
+                           NA),
+         initMb4hatch = ifelse(min(est_hatch, visit_ends) - 
+                                       max(initiation_date, visit_starts) >= 0,
+           min(est_hatch, visit_ends) - 
+           max(initiation_date, visit_starts) + 1,
+           ifelse(visit_starts > est_hatch | visit_ends < initiation_date,
+                  NA,
+                  NA)),
+         initMb4h_sc2h = initMb4hatch/as.numeric((est_hatch-initiation_date+1))) %>%
+  ungroup()
+
+initMb4h_tbL <- initiator_days_b4hatch %>%
+  filter(initL) %>%
+  select(location, desert_rel2hL=est_rel2h, init_durL=init_dur, initMb4h_tbL=initMb4hatch, initMb4h_sc2hL=initMb4h_sc2h,
+         females_removed, ants_removed, initiation_date, num_at_init,
+         initiator_tbL=Female_ID, n_clutches_on_plant)
+
+initMb4h_tbS <- initiator_days_b4hatch %>%
+  filter(initS) %>%
+  select(location, desert_rel2hS=est_rel2h, init_durS=init_dur, initMb4h_tbS=initMb4hatch, initMb4h_sc2hS=initMb4h_sc2h,
+         females_removed, ants_removed, initiation_date, num_at_init,
+         initiator_tbS=Female_ID, n_clutches_on_plant)
+
+##### proportional time: mDb4h
+focalMb4h_sc2h <- visited_1st_4d_data_tb  %>%
+  # exclude visits to leaves that never had eggs; only interested in clutches
+  filter(!is.na(initiation_date),
+         # exclude clutches for which the initiators are not known (why?)
+         !is.na(num_at_init)) %>%
+  group_by(row_number()) %>%
+  # Use median init to hatch interval (20 days) to est hatch date of clutch with no hatch date
+  mutate(mD = ifelse(min(est_hatch, visit_ends) - 
+                                       max(initiation_date, visit_starts) >= 0,
+                     visit_ends-initiation_date+1,
+                     NA),
+         days_guard_b4hatch = ifelse(min(est_hatch, visit_ends) - 
+                                       max(initiation_date, visit_starts) >= 0,
+           min(est_hatch, visit_ends) - 
+           max(initiation_date, visit_starts) + 1,
+           ifelse(visit_starts > est_hatch | visit_ends < initiation_date,
+                  NA,
+                  NA)),
+         focalMb4h_sc2h = days_guard_b4hatch/as.numeric((est_hatch-initiation_date+1))) %>%
+  ungroup()
+
+clutch_momDays_b4h <- focalMb4h_sc2h %>%
+  group_by(location) %>%
+    summarize(sum_mD = sum(mD, na.rm=T),
+              sum_vD = sum(mD*!mom_at_init, na.rm=T),
+              sum_gD = sum(mD*mom_at_init, na.rm=T),
+              vDb4h_sc2h = sum(days_guard_b4hatch*!mom_at_init, na.rm = T)/
+                # scale to init-hatch interval so clutches with different intervals are comparable 
+                as.numeric(first(est_hatch)-first(initiation_date)+1),
+              gDb4h_sc2h = sum(days_guard_b4hatch*mom_at_init, na.rm = T)/
+                as.numeric((first(est_hatch)-first(initiation_date)+1)),
+              mDb4h_sc2h = sum(days_guard_b4hatch, na.rm = T)/
+                as.numeric((first(est_hatch)-first(initiation_date)+1))) %>%
+  ungroup()
+
+clutch_status_momDays_b4h <- visited_1st_4d_data_tb %>%
+  distinct(location, initiation_date, hatch_date, num_at_init,
+           females_removed, ants_removed, egg_fate, egg_fate_date,
+           max_egg_num, max_egg_len, `visited in 4 days`) %>%
+  right_join(clutch_momDays_b4h, by=c("location")) %>%
+  left_join(top5eggs_summary)
+
+#### latest desertion
+latest_desertions <- visited_1st_4d_data %>%
+  filter(!is.na(initiation_date),
+         !(visit_ends<initiation_date), # visits that end before initiation are irrelevant
+         !(visit_starts>est_hatch+4)) %>% # there are a few cases where clutches are visited long after hatching, which wouldn't affect hatching success
+  left_join(first_visit_cuts) %>%
+  select(Female_ID:visit_ends, initiation_date, est_hatch, est_rel2h, 
+         `visited in 4 days`, mom_at_init, ants_removed, females_removed) %>%
+  group_by(location) %>%
+  filter(any(mom_at_init)) %>% # remove any clutches where there was no apparent mother at initiation
+  summarize(last_des_rel2h = max(ifelse(visit_starts<=initiation_date, est_rel2h, NA), na.rm=T),
+            first_des_rel2h_init = min(ifelse(mom_at_init, est_rel2h, NA), na.rm=T),
+            last_desert = ifelse(last_des_rel2h>=-2, "after hatch",
+                                 ifelse(last_des_rel2h<=0, "before hatch", NA)),
+            females_removed = first(females_removed),
+            ants_removed = first(ants_removed),
+            `visited in 4 days` = first(`visited in 4 days`),
+            init_desert_early = ifelse(first(first_des_rel2h_init<=-16), "deserted early", "didn't desert early"),
+            est_hatch = first(est_hatch)) %>%
+  ungroup() #%>%
+  # filter(!is.na(`visited in 4 days`)) %>% # E40_9 for some reason didn't get a valid visited in 4 days entry
+  # filter(location!="A23_8") %>% # A23_8 has two moms at init but for some reason not `visited in 4 days`?
+
+#### combine the three (but after getting more comfortable with the "latest_desertions" results I can omit the initL/S for simplicity)
+clutch_egg_num_data <- latest_desertions %>%
+  left_join(initMb4h_tbL) %>%
+  left_join(initMb4h_tbS) %>%
+  separate(location, sep = "_", into = c("DormPlant"),  remove = FALSE, extra = "drop") %>%
+  left_join(select(clutch_status_momDays_b4h, location, sum_mD, sum_vD, sum_gD,
+                   mDb4h_sc2h, gDb4h_sc2h, vDb4h_sc2h, max_egg_num, max_egg_len,
+                   `visited in 4 days`)) %>%
+  # if tbL and tbS are not the same female, add the female that lost the tie-break to the total sum of visit days
+  mutate(sum_vD_initL = ifelse(initiator_tbL!=initiator_tbS,
+                           sum_vD+init_durS, sum_vD),
+         sum_vD_initS = ifelse(initiator_tbS!=initiator_tbL,
+                           sum_vD+init_durL, sum_vD),
+         visited = vDb4h_sc2h > 0,
+         pmDvD = vDb4h_sc2h/mDb4h_sc2h) %>%
+  left_join(top5eggs_summary) %>%
+  select(location, last_des_rel2h, first_des_rel2h_init,
+         ants_removed, females_removed, initiation_date, est_hatch, `visited in 4 days`,
+         sum_mD, sum_vD, sum_gD, mDb4h_sc2h,
+         num_at_init, init_desert_early, last_desert,
+         n_eggs = max_egg_num, med_t5eggs, mean_t5eggs, max_n_eggs,
+         max_egg_len, med_l_t5eggs, mean_l_t5eggs, max_l_eggs,
+         init_durL, init_durS, desert_rel2hL, desert_rel2hS,
+         sum_vD_initL, sum_vD_initS, initMb4h_sc2hL, initMb4h_sc2hS,
+         initiator_tbL, initiator_tbS,
+         n_clutches_on_plant, visited, pmDvD, DormPlant)
+
+# add filtered and curated nymph and adult counts
+clutch_survivorship_data <- clutch_egg_num_data %>%
+  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2,
+                   -c(ants_removed, females_removed, initiation_date, n_eggs)),
+            by=c("location"="NOr_rev_loc"))
+
+# older version so I can compare
+clutch_egg_num_success_data_old <- initMb4h_tbL %>%
+  left_join(initMb4h_tbS) %>%
+  separate(location, sep = "_", into = c("DormPlant"),  remove = FALSE, extra = "drop") %>%
+  left_join(select(clutch_status_momDays_b4h, location, mDb4h_sc2h, gDb4h_sc2h, vDb4h_sc2h, max_egg_num)) %>%
+  mutate(visited = vDb4h_sc2h > 0,
+         pmDvD = vDb4h_sc2h/mDb4h_sc2h) %>%
+  # left_join(select(pDaysb4h_ants_moms, location, anyMb4h)) %>%
+  # left_join(select(clutch_status_uDur_b4h, location, uDur_norm)) %>%
+  # select(location, initMb4h_sc2hL, initMb4h_sc2hS, desert_rel2hL, desert_rel2hS, mDb4h_sc2h,
+  #        anyMb4h, uDur_norm, females_removed, ants_removed, initiation_date, num_at_init, 
+  #        n_eggs = max_egg_num, initiator_tbL, initiator_tbS, n_clutches_on_plant, 
+  #        visited, visited_early, pmDvD, DormPlant) %>%
+  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2, 
+                   -females_removed, -ants_removed, -initiation_date, -n_eggs), by=c("location"="NOr_rev_loc"))
+  # filter(initiation_date <= as_date("2019-06-10"), n_hatched/n_eggs <= 0.80)
+
+```

### 2023-08-08 scripts/Publilia-03-survivorship.Rmd
init `Publilia-03-survivorship.Rmd` and move most of the survivorship data prep to qc Rmd.

---
title: "Publilia-03-survivorship.Rmd"
author: "micah fletcher"
date: "8/4/2023"
output: html_document
---

## Required libraries and functions
```{r}
library(tidyverse)
library(lubridate)
library(ggpubr)
library(ggh4x)
library(rstatix)
library(emmeans)
library(effectsize)
library(gt)
library(gtsummary)
theme_gtsummary_compact()
library(flextable)
library(multcompView)
library(here)

theme_publilia <- function(){
  theme_bw() +
    theme(text = element_text(family = "Arial"),
          axis.text = element_text(size = 12), 
          axis.title = element_text(size = 14),
          axis.line.x = element_line(color="black"), 
          axis.line.y = element_line(color="black"),
          panel.border = element_blank(),
          panel.grid.major.x = element_blank(),                                          
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.y = element_blank(),  
          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
          plot.title = element_text(size = 18, vjust = 1, hjust = 0.5, face = "bold"),
          legend.text = element_text(size = 10),          
          legend.title = element_blank(),                              
          # legend.position = c(0.90, 0.90), 
          legend.key = element_blank(),
          legend.background = element_rect(color = "black", 
                                           fill = "transparent", 
                                           size = 2, linetype = "blank"))
}
```

# 0 - Data import

clutch_status_guarding_summary_v2
```{r}
All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))

clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
# last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))
# 
# strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
```

# Final figures and stats using functions
Use the same data for each regression
```{r}
# I originally used the ants_removed as the predictor representing ants, but I am now redoing the analysis using whether ants were ever observed at the clutch.
surv_reg_data <- clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_hatched, n_survived,
         des=last_des_rel2h, ants_removed, vis=`visited in 4 days`,
         females_removed, initiation_date, est_hatch) %>%
  mutate(n_survived = ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
                             n_hatched, n_survived), # force n_survived/n_hatched=1
         ant_treatment=ifelse(ants_removed, "Removed", "Control")) %>%
  left_join(select(ant_counts, location, 
                   ever_antsP_b4h, ever_antsP_afh, ever_antsP)) %>%
  mutate(ants_b4h=ifelse(ever_antsP_b4h," ever", " never"),
         ants_afh=ifelse(ever_antsP_afh," ever"," never"),
         ants_ever=ifelse(ever_antsP," ever"," never")) %>%
  left_join(select(ant_n_days, -ants_everP, -ant_treatment, -females_removed)) %>%
  mutate(ants_gt2d=ifelse(antsP_gt2d," ants", " no ants"),
         ants_gt3d=ifelse(antsP_gt3d," ants", " no ants")) %>% 
  separate(location, into = c("DormPlant", "Leaf"), sep="_", remove=FALSE) %>%
  left_join(dplyr::select(moms_plant_data, DormPlant, last_visit_ends_P), by="DormPlant") %>%
  mutate(last_desP_rel2h = last_visit_ends_P-est_hatch,
         desP = last_desP_rel2h) 
```

# Final (really this time) figures for the dissertation
Choosing the models strictly based on qAICc leads to some odd results that make biological interpretation too complciated.

Hatching success: All model types are within ~2 qAICc of each other, so pick whichever shows the biology best and is most consistent with Nsurv and Esurv.

Nymph survivorship: desP * ants_ever * desP^2 has the best qAICc, and the desL version has the second best. The desL version (which, for biological interpretation's sake, should be in the main figure) has very wide 95% CI on the left side, which sends off alarm bells that model fit may be a less robust to addition or subtraction of samples than the AIC suggests.

Egg survivorship: desL * ants_ever * desL^2  has best qAICc, by far. Again the left side 95% CI is huge and it just looks terrible, suggesting to me that there may be too few influential points on the right side to conclusively support the convex up shape.

One problem with the ants_ever method is that the `never ants` level has a much smaller sample size than the `ever ants` level. I'm worried that this could make conclusive inference on the difference among these treatments or even just slope and shape could be shaky. Breaking the groups into `ants >2 days` vs `ants <=2 days` solves the unequal sample sizes problem and makes the desL figure more straightforward to interpret. The qAICc is considerably worse, but I'm concerned that it is only because ants ever was overfitting with too little data.

So, I'm making `desL * ants_gt2 * desL^2` the main figure and `desP * ants_gt2 * desP^2` the supplemental figure. I will report the qAICc of these two models, but not in a table. The data summary table, regression table and results text will need to change too.

*******

After running all these new regressions, I realize that the desL * ant treatment quadratic model has the lowest qAICc and the most interpretable plot and summary stats. I will use this instead.

And since the desP models perform poorly (both in terms of AICc and a convex up Nsurv fit), I just won't even include them in the supplement. I can include the desL `ants >2 days` in the supplement, but honestly it might not even be necessary since it looks so similar to the treatment-based model. I can just mention they are similar?

# Main - `desL * ants_gt2 * desL^2`

## Tables
```{r}
(surv_reg_data.tbl_summary.desL.ants_gt2d <- surv_reg_data %>%
  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `leaf desert date rel. hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desL.ants_gt2d %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desL.ants_gt2d.docx")
```

```{r}
hatch.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

(desL.ants_gt2d.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desL.ants_gt2d.quad.qb.tbl, 
                Nsurv.desL.ants_gt2d.quad.qb.tbl, 
                Esurv.desL.ants_gt2d.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desL.ants_gt2d.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desL.ants_gt2d.quad.docx")
```

## Figures
```{r}
# hatching success
des_hatch.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_gt2d)

des_hatch.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ants_gt2d.quad.fits$mai.qb)

des_hatch.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_gt2d)

des_Nsurv.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb)

des_Nsurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# egg survivorship
des_Esurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ants_gt2d)

des_Esurv.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desL.ants_gt2d.quad.fits$mai.qb)

des_Esurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
    scale_color_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days")) +
    scale_fill_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days"))

(desL.ants_gt2d.quad.qb.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desL.ants_gt2d.quad.final.png",
       desL.ants_gt2d.quad.qb.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

# Supp 1 -`desL * ants_treatment * desL^2`
## Figures
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment)

des_hatch.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ant_treatment,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ant_treatment.quad.fits$mai.qb)

des_hatch.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ant_treatment)

des_Nsurv.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ant_treatment,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)

des_Nsurv.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# egg survivorship
des_Esurv.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment)

des_Esurv.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ant_treatment,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desL.ant_treatment.quad.fits$mai.qb)

des_Esurv.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Esurv.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
    scale_color_manual(values = c("brown1", "black"), labels = c("Control", "Ant Exclusion")) +
    scale_fill_manual(values = c("brown1", "black"), labels = c("Control", "Ant Exclusion"))

(desL.ant_treatment.quad.qb.p <- egg::ggarrange(des_hatch.desL.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desL.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desL.ant_treatment.quad.qb.p+
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desL.ant_treatment.quad.final.png",
       desL.ant_treatment.quad.qb.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

## Tables
```{r}
(surv_reg_data.tbl_summary.desL.ant_treatment <- surv_reg_data %>%
  mutate(ants = ant_treatment,
         females = ifelse(females_removed, "Females removed", "Control"),
         `leaf desert date rel. hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desL.ant_treatment %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desL.ant_treatment.docx")
```

```{r}
hatch.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

(desL.ant_treatment.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desL.ant_treatment.quad.qb.tbl, 
                Nsurv.desL.ant_treatment.quad.qb.tbl, 
                Esurv.desL.ant_treatment.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desL.ant_treatment.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desL.ants_treatment.quad.docx")
```

# Supp 2 -`desP * ants_gt2 * desP^2`
## Figures
```{r}
# hatching success
des_hatch.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=desP, treatment=ants_gt2d)

des_hatch.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ants_gt2d,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desP.ants_gt2d.quad.fits$mai.qb)

des_hatch.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=desP, treatment=ants_gt2d,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=desP, treatment=ants_gt2d)

des_Nsurv.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ants_gt2d,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desP.ants_gt2d.quad.fits$mai.qb)

des_Nsurv.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=desP, treatment=ants_gt2d,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# egg survivorship
des_Esurv.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=desP, treatment=ants_gt2d)

des_Esurv.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ants_gt2d,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desP.ants_gt2d.quad.fits$mai.qb)

des_Esurv.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=desP, treatment=ants_gt2d,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
    scale_color_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days")) +
    scale_fill_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days"))

(desP.ants_gt2d.quad.qb.p <- egg::ggarrange(des_hatch.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desP.ants_gt2d.quad.final.png",
       desP.ants_gt2d.quad.qb.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

## Tables
don't need to include the data summary in supp, since the only thing that changes is the median (IQR) for desertion
```{r}
(surv_reg_data.tbl_summary.desP.ants_gt2d <- surv_reg_data %>%
  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `plant desert date rel. hatch` = desP,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `plant desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desP.ants_gt2d %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desP.ants_gt2d.docx")
```

```{r}
hatch.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

(desP.ants_gt2d.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desP.ants_gt2d.quad.qb.tbl, 
                Nsurv.desP.ants_gt2d.quad.qb.tbl, 
                Esurv.desP.ants_gt2d.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desP.ants_gt2d.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desP.ants_gt2d.quad.docx")
```

# Supp 3 -`desP * ant_s_gt2_treatment * desP^2`
## Figures
```{r}
# hatching success
des_hatch.desP.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=desP, treatment=ant_treatment)

des_hatch.desP.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ant_treatment,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desP.ant_treatment.quad.fits$mai.qb)

des_hatch.desP.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_hatch.desP.ant_treatment.quad.qb.ci, 
                                  tenure=desP, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desP.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=desP, treatment=ant_treatment)

des_Nsurv.desP.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ant_treatment,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desP.ant_treatment.quad.fits$mai.qb)

des_Nsurv.desP.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ant_treatment.quad.qb.ci, 
                                  tenure=desP, treatment=ant_treatment,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# egg survivorship
des_Esurv.desP.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=desP, treatment=ant_treatment)

des_Esurv.desP.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ant_treatment,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desP.ant_treatment.quad.fits$mai.qb)

des_Esurv.desP.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Esurv.desP.ant_treatment.quad.qb.ci, 
                                  tenure=desP, treatment=ant_treatment,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

(desP.ant_treatment.quad.qb.p <- egg::ggarrange(des_hatch.desP.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desP.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desP.ant_treatment.quad.qb.p+
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desP.ant_treatment.quad.final.png",
       desP.ant_treatment.quad.qb.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

## Tables
don't need to include the data summary in supp, since the only thing that changes is the median (IQR) for desertion
```{r}
(surv_reg_data.tbl_summary.desP.ant_treatment <- surv_reg_data %>%
  mutate(ants = ifelse(ant_treatment==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `plant desert date rel. hatch` = desP,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `plant desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desP.ant_treatment %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desP.ant_treatment.docx")
```

```{r}
hatch.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

(desP.ant_treatment.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desP.ant_treatment.quad.qb.tbl, 
                Nsurv.desP.ant_treatment.quad.qb.tbl, 
                Esurv.desP.ant_treatment.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desP.ant_treatment.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desP.ant_treatment.quad.docx")
```

# qAICc
```{r}
# qAICc into separate tables
# qaicc
(qAICc_gt_tbl_hatch_quad <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Hatching success",4)),
  qAICc = c(
    get_qaicc(des_hatch.desL.ant_treatment.quad.fits),
    get_qaicc(des_hatch.desP.ant_treatment.quad.fits),
    get_qaicc(des_hatch.desL.ants_gt2d.quad.fits),
    get_qaicc(des_hatch.desP.ants_gt2d.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))

(qAICc_gt_tbl_Nsurv_quad <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Nymph survivorship",4)),
  qAICc = c(
    get_qaicc(des_Nsurv.desL.ant_treatment.quad.fits),
    get_qaicc(des_Nsurv.desP.ant_treatment.quad.fits),
    get_qaicc(des_Nsurv.desL.ants_gt2d.quad.fits),
    get_qaicc(des_Nsurv.desP.ants_gt2d.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))

(qAICc_gt_tbl_hatch_quad <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Egg survivorship",4)),
  qAICc = c(
    get_qaicc(des_Esurv.desL.ant_treatment.quad.fits),
    get_qaicc(des_Esurv.desP.ant_treatment.quad.fits),
    get_qaicc(des_Esurv.desL.ants_gt2d.quad.fits),
    get_qaicc(des_Esurv.desP.ants_gt2d.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))
```

## Stats interpretation
```{r}
# function to get fits and confint
ci_for_stats <- function(data_in, model){

  data <- eval(substitute(
    data_in %>%
      add_column(fit = predict(model, newdata = ., type = 'response'))
    ))

  ## grad the inverse link function
  ilink <- family(model)$linkinv

  ## add fit and se.fit on the **link** scale
  data_fit_link <- eval(substitute(
    data %>% add_column(
  setNames(as_tibble(predict(model, data, se.fit = TRUE)[1:2]),
           c('fit_link','se_link'))) %>%
## create the interval and backtransform
  mutate(fit_resp  = ilink(fit_link),
         conf_upr = ilink(fit_link + (2 * se_link)),
         conf_lwr = ilink(fit_link - (2 * se_link)))
    ))

  return(data_fit_link)
}

# function to get max fit, plus upper and lower ci
get_max_fit <- function(data_in, model){

  max_fit <- eval(substitute(ci_for_stats(data_in=data_in, 
             model) %>%
  group_by(ant_treatment) %>%
  mutate(max = max(fit)) %>% filter(fit==max) %>% 
    select(ant_treatment, des, max)))

  max_upr <- eval(substitute(ci_for_stats(data_in=data_in, 
             model) %>%
  group_by(ant_treatment) %>%
  mutate(max_upr = max(conf_upr)) %>% filter(conf_upr==max_upr) %>% 
    select(ant_treatment, des_upr=des, max_upr)))

  max_lwr <- eval(substitute(ci_for_stats(data_in=data_in, 
             model) %>%
  group_by(ant_treatment) %>%
  mutate(max_lwr = max(conf_lwr)) %>% filter(conf_lwr==max_lwr) %>% 
    select(ant_treatment, des_lwr=des, max_lwr)))

  data_out <- max_fit %>% left_join(max_upr) %>% left_join(max_lwr)
  return(data_out)
}

## Hatch
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_hatch.desL.ant_treatment.quad.fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_hatch.desL.ant_treatment.quad.fits$mai.qb)

# Nsurv
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)

# Esurv
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_Esurv.desL.ant_treatment.quad.fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_Esurv.desL.ant_treatment.quad.fits$mai.qb)
```

# Figures for FPO

## Figures
### Both colors
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment)

des_hatch.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ant_treatment,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ant_treatment.quad.fits$mai.qb)

des_hatch.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ant_treatment)

des_Nsurv.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ant_treatment,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)

des_Nsurv.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

(FPO_desL.ant_treatment_allCols <- egg::ggarrange(des_hatch.desL.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desL.ant_treatment.quad.qb.p+
                 theme(legend.position="none")))

ggsave("FPO_desL.ant_treatment_allCols.png",
       FPO_desL.ant_treatment_allCols,
       device="png", width = 150, height = 200, units = "mm", dpi = "print")
```

### Black only
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad.qb.p_blackOnly <- 
  ggplot(data = filter(des_hatch.desL.ant_treatment.quad.qb.ci,
                       ant_treatment=="Removed"), 
       aes(x = des, y = fit), 
           color = "black", fill = "black") +
    theme_publilia() +
    geom_point(aes(y = n_hatched/med_t5eggs), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.5, color = NA, key_glyph=draw_key_rect) +
      xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)")

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad.qb.p_blackOnly <- 
  ggplot(data = filter(des_Nsurv.desL.ant_treatment.quad.qb.ci,
                       ant_treatment=="Removed"), 
       aes(x = des, y = fit), 
           color = "black", fill = "black") +
    theme_publilia() +
    geom_point(aes(y = n_survived/n_hatched), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.5, color = NA, key_glyph=draw_key_rect) +
  xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)")

(FPO_desL.ant_treatment_blackOnly <- egg::ggarrange(des_hatch.desL.ant_treatment.quad.qb.p_blackOnly+
                 theme(legend.position="none"),
               des_Nsurv.desL.ant_treatment.quad.qb.p_blackOnly+
                 theme(legend.position="none")))

ggsave("FPO_desL.ant_treatment_blackOnly.png",
       FPO_desL.ant_treatment_blackOnly,
       device="png", width = 150, height = 200, units = "mm", dpi = "print")
```

hatching success
```{r}
# hatching success
des_hatch.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_gt2d)

des_hatch.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ants_gt2d.quad.fits$mai.qb)

des_hatch.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

plot_ci(ci_data=filter(des_hatch.desL.ants_gt2d.quad.qb.ci, 
                       ants_gt2d ), 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

```

nymph survivorship
```{r}
# nymph survivorship
des_Nsurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_gt2d)

des_Nsurv.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb)

des_Nsurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))
```

### 2023-08-11 scripts/Publilia-01-qc.Rmd
Moved all data prep for `Publilia-03-survivorship.Rmd` to `Publilia-01-qc.Rmd`

--- 2023-07-22 scripts/Publilia-01-qc.Rmd
@@
 ```
+
+***
+
+*Prep data for `Publilia-03-survivorship.Rmd`:*
+
+# 7 - Assigning nymph origins
+
+Nymphs migrate away from their natal leaf.
+On plants with multiple clutches, it was sometimes possible to determine the origin of nymphs later in the season because sometimes groups of nymph don't travel very far from their natal leaf and mix with other groups.
+I manually curated examples of this, so that clutch-level stats on hatching success and nymph survivorship could be determined on the plants with multiple clutches.
+Some clutches (as a rule only on multi-clutch plants) did not have a clear record of nymphs that emigrated from the natal leaf and thus could not be included in future clutch-level analyses of survivorship.
+
+## 7.1 - Adding second gen adult counts per leaf to clutch status stats
+```{r}
+# counting adults
+eA_status_v1 <- All_data_v6 %>%
+  group_by(row_number()) %>% # sum of newly exclosed adults
+  filter(any(!is.na(c(New_eA, Old_eA)))) %>%
+  mutate(n_newA = ifelse(is.na(New_eA),
+                         NA,
+                         sum(as.numeric(regmatches(New_eA, gregexpr("[0-9]+", New_eA))[[1]]))),
+         n_oldA = ifelse(is.na(Old_eA),
+                         NA,
+                         sum(as.numeric(regmatches(Old_eA, gregexpr("[0-9]+", Old_eA))[[1]]))),
+         n_A = sum(n_newA, n_oldA, na.rm = TRUE)) %>%
+  ungroup() %>%
+  select(Date, location, n_newA, n_oldA, n_A)
+
+All_data_v6_clutch_status_stats_v2 <- All_data_v6 %>%
+  # add egg measures, clutch status stats (including initiation dates, hatch dates, egg fate, etc)
+  left_join(clutch_status_v2, by = c("location", "Date")) %>%
+  left_join(clutch_status_stats_v1, by = c("location")) %>%
+  left_join(eA_status_v1, by = c("Date", "location")) %>%
+  left_join(select(clutch_status_guarding_summary_v2, location, never_hatched)) %>%
+  mutate(N1 = as.numeric(N1),
+         N2 = as.numeric(N2),
+         N5 = as.numeric(N5))
+```
+
+## 7.2 - Manually check nymph origins for revision
+First create a table of all entried from clutches that were not flagged in the field as having ambiguous origin (e.g.
+"leaf 6 or 9") in cases were more than one clutch was on the plant.
+These were revised manually to specify a leaf of origin for the nymphs, where possible.
+```{r}
+NOr_status_resolveable_all_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>% 
+  select(Date, Dorm, Plant, Leaf, location, 
+         egg_num, N1, N2, N5, n_A, nymph_origin, initiation_date, hatch_date,
+         any_NOr_ambig_loc, Omit_for_abandon_time, never_hatched,
+         n_clutches_on_plant) %>%
+  # keep only entries with some nymphs or adults on a leaf
+  # OR entries for leaves where clutches have been initiated
+  group_by(row_number()) %>%
+  filter(!is.na(Leaf) & any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) | 
+           Date >= initiation_date) %>% # nrow = 17944
+  # flag entries where the nymph origin is text (typically ambiguous, e.g. "8 or 9")
+  mutate(NOr_ambig_entry = !is.na(nymph_origin) & is.na(as.numeric(nymph_origin))) %>% 
+  ungroup() %>%
+  # get rid of duplicate rows from multiple females in the same location
+  distinct(Date, location, .keep_all = TRUE) %>% # nrow = 15674
+  group_by(Dorm, Plant) %>%
+    # filter out any plants with a clutch that was omitted for abandon time
+    filter(!any(!is.na(Omit_for_abandon_time))) %>%
+    # flag plants with any ambiguous entries (e.g. "8 or 9") skip for checking
+    mutate(NOr_ambig_plant = any(NOr_ambig_entry)) %>%
+  ungroup()
+
+NOr_status_resolveable_mult_clutches <- NOr_status_resolveable_all_unambig_clutches %>% # nrow = 15674
+  group_by(Dorm, Plant) %>%
+    # plants with mutliple clutches only
+    filter(any(n_clutches_on_plant > 1)) %>%
+  ungroup() %>%
+  group_by(row_number()) %>%
+    # flag for manual checking entries with any nymphs/adults, missing nymph origin, 
+    # but not flagged for ambiguous origin in the field.
+    # these are the most likely to be easily resolved with minimal work
+    mutate(revise_NOr = ifelse(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) &
+             !NOr_ambig_plant,
+           "MANUAL CHECK",
+           NA)) %>% 
+  ungroup()
+
+NOr_manual_check_table <- NOr_status_resolveable_mult_clutches %>%
+  group_by(Dorm, Plant) %>%
+    filter(any(revise_NOr == "MANUAL CHECK")) %>% # nrow = 2830
+  ungroup() %>%
+    group_by(row_number()) %>%
+    filter(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0)) %>%
+  ungroup() %>%
+  select(Date, Dorm, Plant, Leaf, location, egg_num, N1, N2, N5, n_A, nymph_origin,
+         initiation_date, hatch_date,
+         revise_NOr) %>%
+  arrange(Dorm, as.numeric(Plant), as.numeric(Leaf), Date)
+# 83 clutches on 34 plants to check
+
+# write_csv(NOr_manual_check_table %>% filter(revise_NOr == "MANUAL CHECK"), "NOr_manual_check_tmp.csv")
+
+NOr_manual_revisions <- read_xlsx(in_filename, sheet = "NOr_manual_check", col_types = c("date", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "logical", "text")) %>%
+  mutate(Date = as_date(Date),
+         NOr_rev_loc_manual = paste0(Dorm, Plant, "_", NOr_revised)) %>%
+  filter(!cant_resolve) %>%
+  select(Date, location, NOr_rev_loc_manual, NOr_revised_manual = NOr_revised)
+
+NOr_manual_revisions %>%
+  distinct(NOr_rev_loc_manual) # 43/83 initiated clutches (43/59 hatched) with successfully revised NOr
+```
+
+## 7.3 - Implement revisions by creating the new variables NOr_revised and NOr_rev_loc
+```{r}
+# if nymph origin was clearly resolveable, the revisions were made in NOr_manual_revisions
+# updating NOr_status with revisions so that it can be left_joined to other data and
+# counts of nymphs and adults on NOr can be calculated
+NOr_status_revised_all_unambig_clutches <- NOr_status_resolveable_all_unambig_clutches %>%
+  left_join(NOr_manual_revisions, by = c("Date", "location")) %>%
+  group_by(Dorm, Plant) %>%
+    mutate(lone_hatcher_leaf = ifelse(length(unique(Leaf[!is.na(initiation_date)])) == 1,
+                                 unique(Leaf[!is.na(initiation_date)]),
+                                 NA),
+           NOr_revised = ifelse(!is.na(NOr_revised_manual),
+                                       NOr_revised_manual,
+                                ifelse(any(!is.na(lone_hatcher_leaf)),
+                                       lone_hatcher_leaf,
+                                       # if no clutches hatched on the plant, NOr_revised = Leaf
+                                       # for leaves with eggs
+                                       ifelse(!any(!is.na(hatch_date)) & !is.na(egg_num),
+                                              Leaf,
+                                              NA)))) %>%
+  ungroup() %>%  
+  group_by(location) %>%
+    mutate(NOr_revised = ifelse(any(NOr_revised == Leaf) & is.na(NOr_revised),
+                                Leaf,#unique(NOr_revised[!is.na(NOr_revised)]),
+                                NOr_revised)) %>%
+  ungroup() %>%
+  mutate(NOr_rev_loc = ifelse(is.na(NOr_revised),
+                              NA,
+                              paste0(Dorm, Plant, "_", NOr_revised))) %>%
+  select(Date, location, NOr_revised, NOr_rev_loc) %>%
+  filter(!is.na(NOr_rev_loc))
+
+All_data_v6_N_NOr_counts_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>%
+  right_join(NOr_status_revised_all_unambig_clutches, by = c("Date", "location")) %>%
+  group_by(Date, Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
+    summarize(N1_NOr = sum(N1, na.rm= TRUE),
+              N2_NOr = sum(N2, na.rm= TRUE),
+              N5_NOr = sum(N5, na.rm= TRUE),
+              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
+              A_NOr = sum(n_A, na.rm= TRUE),
+              N5plusA_NOr = sum(N5, n_A, na.rm= TRUE)) %>%
+  ungroup() # n = 186
+
+All_data_v6_N_NOr_counts_unambig_clutches_summary <- All_data_v6_N_NOr_counts_unambig_clutches %>%
+  group_by(Date) %>%
+    mutate(mean_N_NOr = mean(N_NOr, na.rm = TRUE),
+           mean_N1_NOr = mean(N1_NOr, na.rm = TRUE),
+           mean_N2_NOr = mean(N2_NOr, na.rm = TRUE),
+           mean_N5_NOr = mean(N5_NOr, na.rm = TRUE),
+           mean_A_NOr = mean(A_NOr, na.rm = TRUE),
+           mean_N5plusA_NOr = mean(N5plusA_NOr, na.rm = TRUE),
+           All_N_NOr = sum(N_NOr),
+           All_A_NOr = sum(A_NOr)) %>%
+  ungroup() %>%
+  group_by(Date, Dorm) %>%
+    mutate(All_N_NOr_Dorm = sum(N_NOr),
+           All_N1_NOr_Dorm = sum(N1_NOr),
+           All_N2_NOr_Dorm = sum(N2_NOr),
+           All_N5_NOr_Dorm = sum(N5_NOr),
+           All_A_NOr_Dorm = sum(sum(A_NOr))) %>%
+  ungroup()
+
+All_data_v6_all_nymphs_unambig_clutches <- All_data_v6_N_NOr_counts_unambig_clutches %>%
+  group_by(Date) %>%
+    summarize(All_N_NOr = sum(N_NOr)) %>%
+  ungroup()
+
+All_data_v6_max_N_NOr_counts_unambig_clutches <-
+  All_data_v6_N_NOr_counts_unambig_clutches %>%
+  group_by(Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
+    summarize(max_N_NOr = max(N_NOr)) %>%
+  ungroup()
+
+clutch_status_stats_v1_unambig_clutches_hatch_success <- clutch_status_stats_v1 %>%
+  separate(location, c("DormPlant", "Leaf"), sep = "_", remove = FALSE) %>%
+  mutate(Dorm = substr(DormPlant, 1, 1),
+         Plant = substring(DormPlant, 2)) %>%
+  left_join(distinct(clutch_status_guarding_summary_v2, location, never_hatched)) %>%
+  right_join(All_data_v6_max_N_NOr_counts_unambig_clutches, by = c("Dorm", "Plant", "Leaf" = "NOr_revised")) %>%
+  # why did I originally say to make hatch_success = NA if never_hatched == TRUE?
+  mutate(hatch_success = ifelse(!is.na(initiation_date) & is.na(hatch_date),
+                                0,
+                                max_N_NOr/max_egg_num))
+```
+
+## 7.4 - Flag and resolve ambiguous nymph origins
+
+```{r}
+NOr_status_resolveable_all_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>% 
+  select(Date, Dorm, Plant, Leaf, location, 
+         egg_num, N1, N2, N5, n_A, nymph_origin, initiation_date, hatch_date,
+         any_NOr_ambig_loc, Omit_for_abandon_time, never_hatched,
+         n_clutches_on_plant) %>%
+  # keep only entries with some nymphs or adults on a leaf
+  # OR entries for leaves where clutches have been initiated
+  group_by(row_number()) %>%
+  filter(!is.na(Leaf) & any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) | 
+           Date >= initiation_date) %>% # nrow = 17944
+  # flag entries where the nymph origin is text (typically ambiguous, e.g. "8 or 9")
+  mutate(NOr_ambig_entry = !is.na(nymph_origin) & is.na(as.numeric(nymph_origin))) %>% 
+  ungroup() %>%
+  # get rid of duplicate rows from multiple females in the same location
+  distinct(Date, location, .keep_all = TRUE) %>% # nrow = 15674
+  group_by(Dorm, Plant) %>%
+    # filter out any plants with a clutch that was omitted for abandon time
+    filter(!any(!is.na(Omit_for_abandon_time))) %>%
+    # flag plants with any ambiguous entries (e.g. "8 or 9") skip for checking
+    mutate(NOr_ambig_plant = any(NOr_ambig_entry)) %>%
+  ungroup()
+
+NOr_status_resolveable_mult_clutches <- NOr_status_resolveable_all_unambig_clutches %>%
+  group_by(Dorm, Plant) %>%
+    # plants with mutliple clutches only
+    filter(any(n_clutches_on_plant > 1)) %>%
+  ungroup() %>%
+  group_by(row_number()) %>%
+    # flag for manual checking entries with any nymphs/adults, missing nymph origin, 
+    # but not flagged for ambiguous origin in the field.
+    # these are the most likely to be easily resolved with minimal work
+    mutate(revise_NOr = ifelse(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) &
+             !NOr_ambig_plant,
+           "MANUAL CHECK",
+           NA)) %>% 
+  ungroup()
+```
+
+## 7.5 - Fixing the omission of clutches that never had first instar nymphs
+
+```{r}
+NOr_status_revised_all_unambig_clutches_v2 <- NOr_status_resolveable_all_unambig_clutches %>%
+  left_join(NOr_manual_revisions, by = c("Date", "location")) %>%
+  group_by(Dorm, Plant) %>%
+    mutate(lone_hatcher_leaf = ifelse(length(unique(Leaf[!is.na(initiation_date)])) == 1,
+                                 unique(Leaf[!is.na(initiation_date)]),
+                                 NA),
+           NOr_revised = ifelse(!is.na(NOr_revised_manual), # if I manually annotated a revised location
+                                       NOr_revised_manual, # make manual location the new nymph origin
+                                ifelse(any(!is.na(lone_hatcher_leaf)), # if only one clutch hatched on the plant
+                                       lone_hatcher_leaf, # make that clutch the new nymph origin
+                                       # if no clutches hatched on the plant, NOr_revised = Leaf
+                                       # for leaves with eggs
+                                       ifelse(!any(!is.na(hatch_date)) & !is.na(egg_num), # if no clutches hatched on the plant (but there are eggs)
+                                              Leaf, # make the given leaf the new nymph origin
+                                              NA)))) %>% # BUT THIS STILL EXCLUDES CLUTCHES THAT DIDN'T HATCH ON A PLANT WITH SOME CLUTCHES THAT DID HATCH
+  ungroup() %>%  
+  group_by(location) %>%
+    mutate(NOr_revised = ifelse(any(NOr_revised == Leaf) & is.na(NOr_revised), # DOES THIS INCLUDE UNHATCHED CLUTCHES? NO
+                                Leaf,#unique(NOr_revised[!is.na(NOr_revised)]),
+                                NOr_revised),
+           NOr_revised = ifelse(any(is.na(NOr_revised)) & # if no revised nymph origin yet
+                                                  any(!is.na(egg_num)&egg_num>0 & !any(!is.na(N1)&N1>0)), # and N1 never on clutch (not hatched or spuriously visited by N1)
+                                Leaf, # make this leaf the new nymph origin (so we include unhatched clutches)
+                                NOr_revised)) %>% 
+  ungroup() %>%
+  mutate(NOr_rev_loc = ifelse(is.na(NOr_revised),
+                              NA,
+                              paste0(Dorm, Plant, "_", NOr_revised))) %>%
+  select(Date, location, NOr_revised, NOr_rev_loc) %>%
+  filter(!is.na(NOr_rev_loc))
+
+All_data_v6_N_NOr_counts_unambig_clutches_v2 <- All_data_v6_clutch_status_stats_v2 %>%
+  right_join(NOr_status_revised_all_unambig_clutches_v2, by = c("Date", "location")) %>%
+  group_by(Date, Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
+    summarize(N1_NOr = sum(N1, na.rm= TRUE),
+              N2_NOr = sum(N2, na.rm= TRUE),
+              N5_NOr = sum(N5, na.rm= TRUE),
+              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
+              A_NOr = sum(n_A, na.rm= TRUE),
+              N5plusA_NOr = sum(N5, n_A, na.rm= TRUE)) %>%
+  ungroup()
+
+All_data_v6_N_NOr_counts_unambig_clutches_summary_v2 <- All_data_v6_N_NOr_counts_unambig_clutches_v2 %>%
+  group_by(Date) %>%
+    mutate(mean_N_NOr = mean(N_NOr, na.rm = TRUE),
+           mean_N1_NOr = mean(N1_NOr, na.rm = TRUE),
+           mean_N2_NOr = mean(N2_NOr, na.rm = TRUE),
+           mean_N5_NOr = mean(N5_NOr, na.rm = TRUE),
+           mean_A_NOr = mean(A_NOr, na.rm = TRUE),
+           mean_N5plusA_NOr = mean(N5plusA_NOr, na.rm = TRUE),
+           All_N_NOr = sum(N_NOr),
+           All_A_NOr = sum(A_NOr)) %>%
+  ungroup() %>%
+  group_by(Date, Dorm) %>%
+    mutate(All_N_NOr_Dorm = sum(N_NOr),
+           All_N1_NOr_Dorm = sum(N1_NOr),
+           All_N2_NOr_Dorm = sum(N2_NOr),
+           All_N5_NOr_Dorm = sum(N5_NOr),
+           All_A_NOr_Dorm = sum(sum(A_NOr))) %>%
+  ungroup()
+```
+
+# 8 - Calculate hatch success and nymph survivorship
+
+Calculate hatch success (strict sense; max N1 / max eggs) and nymph survivorship (max N5+A / max eggs AND/OR max N5+A / max N1)
+
+- Filtered out clutches with outlier numbers of N1 or N5 etc at early or late clutch ages, which were assumed to be cases of immigration that weren't caught during manual nymph origin filtering
+```{r}
+# Filter to only include curated list of clutches with unambiguous nymph counts after accounting for immigration to non-natal leaves and then sum all nymphs (including emigrants) for each clutch
+# I also added clutch_age variables to help identify clutches that were started too close to the end of sampling to be useful
+clutch_unambig_NOr_revised_ENAa_summary_v2 <- All_data_v6_clutch_status_stats_v2 %>%
+  right_join(NOr_status_revised_all_unambig_clutches_v2, by = c("Date", "location")) %>%
+  select(Date, NOr_rev_loc, location, egg_num, N1, N2, N5, n_A, ants_L) %>%
+    # remove any duplicates - I need to figure out why there are dups later but for 4th yr talk
+  distinct(Date, NOr_rev_loc, location, egg_num, N1, N2, N5, n_A, ants_L, .keep_all = TRUE) %>%
+  mutate(egg_num_NOr = ifelse(NOr_rev_loc == location, egg_num, NA)) %>%
+  group_by(Date, NOr_rev_loc) %>%
+    summarize(eggs_NOr = first(egg_num_NOr[!is.na(egg_num_NOr)]), # only use eggs from origin leaf!
+              N1_NOr = sum(N1, na.rm= TRUE),
+              N2_NOr = sum(N2, na.rm= TRUE),
+              N5_NOr = sum(N5, na.rm= TRUE),
+              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
+              A_NOr = sum(n_A, na.rm= TRUE),
+              N5toA_NOr = sum(N5, n_A, na.rm= TRUE),
+              ants_NOr = sum(ants_L, na.rm = TRUE)) %>%
+  ungroup() %>%
+  left_join(filter(clutch_status_guarding_summary_v2, mom_at_init), by = c("NOr_rev_loc" = "location")) %>%
+  mutate(clutch_age1 = Date - initiation_date,
+         clutch_age2 = ceiling((Date - initiation_date)/2)*2,
+         clutch_age4 = ceiling((Date - initiation_date)/4)*4,
+         after_hatch1 = Date - hatch_date,
+         after_hatch2 = ceiling((Date - hatch_date)/2)*2,
+         after_hatch4 = ceiling((Date - hatch_date)/4)*4) %>%
+  select(Date, NOr_rev_loc, clutch_age1, after_hatch1, eggs_NOr, 
+         N1_NOr, N2_NOr, N5_NOr, N_NOr, A_NOr, N5toA_NOr, ants_NOr,
+         init_fem = Female_ID,
+         initiation_date, hatch_date, guard_duration, relative_desert_date,
+         clutch_initiated_order, females_removed, ants_removed, 
+         clutch_age2, clutch_age4, after_hatch2, after_hatch4) #%>%
+  # filter(initiation_date <= as_date("2019-06-10"),
+  #        clutch_age4 <= 68)
+
+max_N1_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  group_by(NOr_rev_loc) %>%
+  arrange(NOr_rev_loc, desc(N1_NOr), Date) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  select(NOr_rev_loc, max_N1_date = Date, max_N1_age = clutch_age1)
+
+max_N5_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  group_by(NOr_rev_loc) %>%
+  arrange(NOr_rev_loc, desc(N5_NOr), Date) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  select(NOr_rev_loc, max_N5_date = Date, max_N5_age = clutch_age1)
+
+max_A_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  group_by(NOr_rev_loc) %>%
+  arrange(NOr_rev_loc, desc(A_NOr), Date) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  select(NOr_rev_loc, max_A_date = Date, max_A_age = clutch_age1)
+
+max_N5toA_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  group_by(NOr_rev_loc) %>%
+  arrange(NOr_rev_loc, desc(N5toA_NOr), Date) %>%
+  filter(row_number() == 1) %>%
+  ungroup() %>%
+  select(NOr_rev_loc, max_N5toA_date = Date, max_N5toA_age = clutch_age1)
+
+max_N5toA_Date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  group_by(NOr_rev_loc) %>%
+  summarize(max_N1 = max(N1_NOr),
+            max_N5toA = max(N5toA_NOr),
+            max_clutch_age = max(clutch_age1),
+            max_after_hatch = max(after_hatch1),
+            max_Date = max(Date),
+            hatched = any(!is.na(hatch_date)),
+            initiation_date = first(initiation_date)) %>%
+  ungroup() %>%
+  arrange(desc(max_N5toA)) %>%
+  full_join(max_N1_date_v2) %>%
+  full_join(max_N5_date_v2) %>%
+  full_join(max_A_date_v2) %>%
+  full_join(max_N5toA_date_v2)
+
+clutch_unambig_NOr_revised_ENAa_summary_imfilt_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
+  mutate(N_imm_likely_d15 = clutch_age1 < 15 & N_NOr > 0,
+         N5_imm_likely_d40 = clutch_age1 < 40 & N5_NOr > 0,
+         A_imm_likely_d40 = clutch_age1 < 40 & A_NOr > 0) %>%
+  group_by(NOr_rev_loc) %>%
+    filter(!any(N_imm_likely_d15, N5_imm_likely_d40, A_imm_likely_d40, na.rm = TRUE)) %>% # n = 168
+  ungroup()
+
+clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_v2 <-
+  clutch_unambig_NOr_revised_ENAa_summary_imfilt_v2 %>%
+  group_by(NOr_rev_loc) %>%
+    mutate(hatch_success_N1 = max(N1_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
+           survival_rate = max(N5toA_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
+           prop_E2Ni = max(N1_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
+           prop_E2N = max(N_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
+           prop_Ni2Nv = max(N5toA_NOr, na.rm = TRUE)/max(N1_NOr, na.rm = TRUE),
+           prop_E2Nv = max(N5toA_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
+           n_eggs = max(eggs_NOr, na.rm = TRUE),
+           n_hatched = max(N1_NOr, na.rm = TRUE),
+           n_N = max(N_NOr, na.rm = TRUE),
+           n_survived = max(N5toA_NOr, na.rm = TRUE)) %>%
+  ungroup()
+
+clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2 <- clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_v2 %>%
+  distinct(NOr_rev_loc, n_eggs, n_hatched, n_survived, n_N,
+           prop_E2Ni, prop_Ni2Nv, prop_E2Nv, prop_E2N, hatch_success_N1, survival_rate,
+           initiation_date, hatch_date, females_removed, ants_removed) 
+```
+
+# 9 - Ant counts on clutch
+
+```{r}
+theme_publilia <- function(){
+  theme_bw() +
+    theme(text = element_text(family = "Arial"),
+          axis.text = element_text(size = 12), 
+          axis.title = element_text(size = 14),
+          axis.line.x = element_line(color="black"), 
+          axis.line.y = element_line(color="black"),
+          panel.border = element_blank(),
+          panel.grid.major.x = element_blank(),                                          
+          panel.grid.minor.x = element_blank(),
+          panel.grid.minor.y = element_blank(),
+          panel.grid.major.y = element_blank(),  
+          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
+          plot.title = element_text(size = 18, vjust = 1, hjust = 0.5, face = "bold"),
+          legend.text = element_text(size = 10),          
+          legend.title = element_blank(),                              
+          # legend.position = c(0.90, 0.90), 
+          legend.key = element_blank(),
+          legend.background = element_rect(color = "black", 
+                                           fill = "transparent", 
+                                           size = 2, linetype = "blank"))
+}
+```
+
+## 9.0 - Get visited_1st_4d_data
+
+```{r}
+strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
+
+visited_1st_4d_data <- strats_data %>%
+  group_by(location) %>%
+    mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
+  ungroup() %>%
+  mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
+                                      "Visited", "Not visited"),
+         ants = ifelse(ants_removed, "Ants removed", "Control"),
+         est_hatch = as_date(ifelse(is.na(hatch_date),
+                                 initiation_date + 20,
+                                 hatch_date)),
+         est_rel2h = visit_ends-est_hatch)
+```
+
+```{r}
+visited_1st_4d_data_tb <- visited_1st_4d_data %>%
+  # 1) Longest initiator
+  mutate(initL = init_first_dur_rank == 1) %>% 
+  # 2) Shortest initiator
+  #  i) break ties by picking marked females over unmarked
+  group_by(location, init_first_dur_shortest) %>% 
+    mutate(initS_tmp = ifelse(n()>1, !grepl("Uf", Female_ID), TRUE)) %>% 
+  ungroup() %>%
+  #  ii) finally picking at random (only one case, identical predictor vars)
+  group_by(location, init_first_dur_shortest, initS_tmp) %>%
+    mutate(initS = init_first_dur_shortest & initS_tmp & row_number()==1) %>%
+  ungroup()
+```
+
+## 9.1 - A small fraction of ants_removed clutches were visited by ants, and vice versa
+```{r}
+ant_counts <- All_data_v6 %>%
+  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+  filter(!is.na(initiation_date)) %>%
+  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+  group_by(location) %>%
+    mutate(b4h=Date>=initiation_date&Date<est_hatch,
+           afh=Date>=est_hatch) %>%
+    summarize(ants_removed=first(ants_removed),
+              females_removed=first(females_removed),
+              n_antsP=sum(ants_P,na.rm=T),
+              ever_antsP=n_antsP>0,
+              mean_antsP=mean(ants_P,na.rm=T),
+              med_antsP=median(ants_P,na.rm=T),
+
+              n_antsP_b4h=sum(ants_P&b4h),
+              ever_antsP_b4h=n_antsP_b4h>0,
+              mean_antsP_b4h=mean(ifelse(b4h,ants_P,NA),na.rm=T),
+              med_antsP_b4h=median(ifelse(b4h,ants_P,NA),na.rm=T),
+
+              n_antsP_afh=sum(ants_P&afh),
+              ever_antsP_afh=n_antsP_afh>0,
+              mean_antsP_afh=mean(ifelse(afh,ants_P,NA),na.rm=T),
+              med_antsP_afh=median(ifelse(afh,ants_P,NA),na.rm=T)) %>%
+  ungroup() %>%
+  mutate(Dorm=substr(location,1,1),
+         ant_treatment=ifelse(ants_removed,"Ants removed","Control"))
+
+ggplot(data=ant_counts,aes(x=Dorm,y=n_antsP, fill=ant_treatment)) +
+  geom_boxplot()
+
+ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP, fill=ant_treatment)) +
+  geom_boxplot()
+
+ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_b4h, fill=ant_treatment)) +
+  geom_boxplot()
+
+ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_afh, fill=ant_treatment)) +
+  geom_boxplot()
+
+```
+
+# 9.2 - Threshold for number of days ants were on the plant
+Should I be more lenient with my threshold, so I can have more even sample sizes between "ants" and "no ants"?
+- ants_ever = n_days_ants>0: F = 83, T = 143
+- antsP_gt2d = n_days_ants>2: F = 123, T = 103 * most even sample size
+- antsP_gt3d = n_days_ants>3: F = 133, T = 90
+```{r}
+ant_n_days <- All_data_v6 %>%
+  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+  filter(!is.na(initiation_date)) %>%
+  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+  mutate(ant_treatment=ifelse(ants_removed,"Ants removed","Control"),
+         Dorm=substr(location,1,1)) %>%
+  group_by(Date, location) %>%
+    summarize(any_antsP_day = any(ants_P>0, na.rm=T),
+              females_removed = first(females_removed),
+              ant_treatment = first(ant_treatment),
+              Dorm = first(Dorm)) %>%
+  ungroup() %>%
+  group_by(location) %>%
+    summarize(n_days_ants = sum(as.numeric(any_antsP_day)),
+              females_removed = first(females_removed),
+              ant_treatment = first(ant_treatment),
+              Dorm = first(Dorm))%>%
+  ungroup() %>%
+  mutate(antsP_gt2d = !is.na(n_days_ants)&n_days_ants>2,
+         antsP_gt3d = !is.na(n_days_ants)&n_days_ants>3,
+         ants_everP = is.na(n_days_ants)|n_days_ants>0)
+
+ant_n_days %>%
+  count(females_removed, ants_everP)
+
+ant_n_days %>%
+  count(females_removed, antsP_gt2d)
+
+ant_n_days %>%
+  count(females_removed, antsP_gt3d)
+```
+
+# 10 - Estimate clutch size more robust to outliers: median top 5 egg counts
+
+## 10.1 - Generate data for fecundity modeling
+
+```{r}
+fec_model_data <- visited_1st_4d_data_tb %>%
+  filter(!is.na(guard_duration)) %>%
+  group_by(location) %>%
+  mutate(eggs_ever_visited = any(!mom_at_init & visit_ends <= est_hatch)) %>%
+  ungroup() %>%
+  select(Female_ID, location, guard_duration, est_rel2h, initiation_date, est_hatch,
+         mom_at_init, clutch_initiated_order, initL, initS,
+         visit_starts, visit_ends, last_day_fID,
+         num_at_init, n_clutches_on_plant, `visited in 4 days`, eggs_ever_visited, ants,
+         females_removed, ants_removed, 
+         max_egg_num, egg_fate, egg_fate_date)
+```
+
+## 10.2 - Calculate median of top 5 egg counts in lieu of max egg counts
+Taking the median (or mean) of the top 5 egg_num counts yields an estimate of max egg num that is more robust to outliers/miscounts
+```{r}
+tmp_t5eggs_data <- clutch_status_init_hatch_labels_v1 %>%
+  mutate(est_hatch = as_date(ifelse(is.na(hatch_date),
+                                 initiation_date + 20,
+                                 hatch_date)),
+         clutch_age = as.numeric(Date-initiation_date)) %>%
+  # remove duplicate egg counts due to multiple females at a location on a day
+  distinct(location, Date, initiation_date, est_hatch, clutch_age,
+           egg_num, egg_len) %>%
+  group_by(location) %>%
+    arrange(desc(egg_num)) %>%
+    mutate(top5egg_counts = rank(desc(egg_num), ties.method = "first") <= 5,
+           top5egg_lens = rank(desc(egg_len), ties.method = "first") <= 5) %>%
+    #filter(location == "A13_11") %>%
+    select(location, Date, initiation_date, est_hatch, clutch_age,
+           egg_num, egg_len, top5egg_counts, top5egg_lens) %>%
+    mutate(med_t5eggs = median(ifelse(top5egg_counts,egg_num,NA), na.rm=T),
+           mean_t5eggs = mean(ifelse(top5egg_counts,egg_num,NA), na.rm=T),
+           max_n_eggs = max(ifelse(top5egg_counts,egg_num,NA), na.rm=T),
+           med_l_t5eggs = median(ifelse(top5egg_lens,egg_len,NA), na.rm=T),
+           mean_l_t5eggs = mean(ifelse(top5egg_lens,egg_len,NA), na.rm=T),
+           max_l_eggs = max(ifelse(top5egg_lens,egg_len,NA), na.rm=T)) %>%
+  ungroup()
+
+top5eggs_summary <- tmp_t5eggs_data %>%
+  group_by(location) %>%
+    summarize(med_t5eggs = first(med_t5eggs),
+              mean_t5eggs = first(mean_t5eggs),
+              max_n_eggs = first(max_n_eggs),
+              med_l_t5eggs = first(med_l_t5eggs),
+              mean_l_t5eggs = first(mean_l_t5eggs),
+              max_l_eggs = first(max_l_eggs)) %>%
+  ungroup()
+```
+
+# 11 - Calculate alternative measures of maternal tenure
+
+`The sum of all females’ egg-guarding durations was more predictive of final clutch size than egg guarding duration of the initiator alone (Table S1 with alternative models and their AICs), showing that females lay eggs while visiting existing clutches.`
+
+## 11.1 - Initiator guarding time: initMb4h
+```{r}
+initiator_days_b4hatch <- visited_1st_4d_data_tb %>%
+  filter(!is.na(initiation_date),
+         # exclude clutches for which the initiators are not known
+         !is.na(num_at_init),
+         mom_at_init) %>%
+  group_by(row_number()) %>%
+  # Use median init to hatch interval (20 days) to est hatch date of clutch with no hatch date
+  mutate(init_dur = ifelse(min(est_hatch, visit_ends) - 
+                                       max(initiation_date, visit_starts) >= 0,
+                           visit_ends-initiation_date+1, 
+                           NA),
+         initMb4hatch = ifelse(min(est_hatch, visit_ends) - 
+                                       max(initiation_date, visit_starts) >= 0,
+           min(est_hatch, visit_ends) - 
+           max(initiation_date, visit_starts) + 1,
+           ifelse(visit_starts > est_hatch | visit_ends < initiation_date,
+                  NA,
+                  NA)),
+         initMb4h_sc2h = initMb4hatch/as.numeric((est_hatch-initiation_date+1))) %>%
+  ungroup()
+
+initMb4h_tbL <- initiator_days_b4hatch %>%
+  filter(initL) %>%
+  select(location, desert_rel2hL=est_rel2h, init_durL=init_dur, initMb4h_tbL=initMb4hatch, initMb4h_sc2hL=initMb4h_sc2h,
+         females_removed, ants_removed, initiation_date, num_at_init,
+         initiator_tbL=Female_ID, n_clutches_on_plant)
+
+initMb4h_tbS <- initiator_days_b4hatch %>%
+  filter(initS) %>%
+  select(location, desert_rel2hS=est_rel2h, init_durS=init_dur, initMb4h_tbS=initMb4hatch, initMb4h_sc2hS=initMb4h_sc2h,
+         females_removed, ants_removed, initiation_date, num_at_init,
+         initiator_tbS=Female_ID, n_clutches_on_plant)
+```
+
+## 11.2 - proportional time: mDb4h
+```{r}
+focalMb4h_sc2h <- visited_1st_4d_data_tb  %>%
+  # exclude visits to leaves that never had eggs; only interested in clutches
+  filter(!is.na(initiation_date),
+         # exclude clutches for which the initiators are not known (why?)
+         !is.na(num_at_init)) %>%
+  group_by(row_number()) %>%
+  # Use median init to hatch interval (20 days) to est hatch date of clutch with no hatch date
+  mutate(mD = ifelse(min(est_hatch, visit_ends) - 
+                                       max(initiation_date, visit_starts) >= 0,
+                     visit_ends-initiation_date+1,
+                     NA),
+         days_guard_b4hatch = ifelse(min(est_hatch, visit_ends) - 
+                                       max(initiation_date, visit_starts) >= 0,
+           min(est_hatch, visit_ends) - 
+           max(initiation_date, visit_starts) + 1,
+           ifelse(visit_starts > est_hatch | visit_ends < initiation_date,
+                  NA,
+                  NA)),
+         focalMb4h_sc2h = days_guard_b4hatch/as.numeric((est_hatch-initiation_date+1))) %>%
+  ungroup()
+
+clutch_momDays_b4h <- focalMb4h_sc2h %>%
+  group_by(location) %>%
+    summarize(sum_mD = sum(mD, na.rm=T),
+              sum_vD = sum(mD*!mom_at_init, na.rm=T),
+              sum_gD = sum(mD*mom_at_init, na.rm=T),
+              vDb4h_sc2h = sum(days_guard_b4hatch*!mom_at_init, na.rm = T)/
+                # scale to init-hatch interval so clutches with different intervals are comparable 
+                as.numeric(first(est_hatch)-first(initiation_date)+1),
+              gDb4h_sc2h = sum(days_guard_b4hatch*mom_at_init, na.rm = T)/
+                as.numeric((first(est_hatch)-first(initiation_date)+1)),
+              mDb4h_sc2h = sum(days_guard_b4hatch, na.rm = T)/
+                as.numeric((first(est_hatch)-first(initiation_date)+1))) %>%
+  ungroup()
+
+clutch_status_momDays_b4h <- visited_1st_4d_data_tb %>%
+  distinct(location, initiation_date, hatch_date, num_at_init,
+           females_removed, ants_removed, egg_fate, egg_fate_date,
+           max_egg_num, max_egg_len, `visited in 4 days`) %>%
+  right_join(clutch_momDays_b4h, by=c("location")) %>%
+  left_join(top5eggs_summary)
+```
+
+## 11.3 - Latest desertion
+```{r}
+first_visit_cuts <- visited_1st_4d_data_tb %>%
+  filter(!mom_at_init, visit_starts > initiation_date) %>%
+  arrange(location, visit_starts) %>%
+  group_by(location) %>%
+  slice_head(n=1) %>%
+  summarize(first_visit_starts = ifelse(num_at_init > 1, 0, as.numeric(visit_starts-initiation_date))) %>%
+  mutate(first_visit_cut = cut(first_visit_starts, breaks=seq(0,40,4)))
+
+moms_plant_data <- visited_1st_4d_data %>%
+  filter(!is.na(initiation_date)) %>%
+  separate(location, "_", into=c("DormPlant","Leaf")) %>%
+  group_by(DormPlant) %>%
+  summarize(n_moms_alltime = n(),
+            n_moms_leaf_H = sum(est_rel2h>=0, na.rm=T),
+            any_moms_leaf_H = any(est_rel2h>=0, na.rm=T),
+            last_visit_ends_P = max(visit_ends, na.rm=T),
+            n_moms_P_H = sum((last_visit_ends_P-est_hatch)>=0, na.rm=T),
+            any_moms_P_H = any((last_visit_ends_P-est_hatch)>=0, na.rm=T),
+            n_moms_P_8afterH = sum((last_visit_ends_P-est_hatch+8)>=0, na.rm=T),
+            any_moms_P_8afterH = sum((last_visit_ends_P-est_hatch+8)>=0, na.rm=T),
+            n_clutches_on_plant = first(n_clutches_on_plant)) %>%
+  ungroup()
+
+latest_desertions <- visited_1st_4d_data %>%
+  filter(!is.na(initiation_date),
+         !(visit_ends<initiation_date), # visits that end before initiation are irrelevant
+         !(visit_starts>est_hatch+4)) %>% # there are a few cases where clutches are visited long after hatching, which wouldn't affect hatching success
+  left_join(first_visit_cuts) %>%
+  select(Female_ID:visit_ends, initiation_date, est_hatch, est_rel2h, 
+         `visited in 4 days`, mom_at_init, ants_removed, females_removed) %>%
+  group_by(location) %>%
+  filter(any(mom_at_init)) %>% # remove any clutches where there was no apparent mother at initiation
+  summarize(last_des_rel2h = max(ifelse(visit_starts<=initiation_date, est_rel2h, NA), na.rm=T),
+            first_des_rel2h_init = min(ifelse(mom_at_init, est_rel2h, NA), na.rm=T),
+            last_desert = ifelse(last_des_rel2h>=-2, "after hatch",
+                                 ifelse(last_des_rel2h<=0, "before hatch", NA)),
+            females_removed = first(females_removed),
+            ants_removed = first(ants_removed),
+            `visited in 4 days` = first(`visited in 4 days`),
+            init_desert_early = ifelse(first(first_des_rel2h_init<=-16), "deserted early", "didn't desert early"),
+            est_hatch = first(est_hatch)) %>%
+  ungroup() #%>%
+  # filter(!is.na(`visited in 4 days`)) %>% # E40_9 for some reason didn't get a valid visited in 4 days entry
+  # filter(location!="A23_8") %>% # A23_8 has two moms at init but for some reason not `visited in 4 days`?
+```
+
+## 11.4 - Combined table of guarding tenures and offspring counts
+```{r}
+#### combine the three (but after getting more comfortable with the "latest_desertions" results I can omit the initL/S for simplicity)
+clutch_egg_num_data <- latest_desertions %>%
+  left_join(initMb4h_tbL) %>%
+  left_join(initMb4h_tbS) %>%
+  separate(location, sep = "_", into = c("DormPlant"),  remove = FALSE, extra = "drop") %>%
+  left_join(select(clutch_status_momDays_b4h, location, sum_mD, sum_vD, sum_gD,
+                   mDb4h_sc2h, gDb4h_sc2h, vDb4h_sc2h, max_egg_num, max_egg_len,
+                   `visited in 4 days`)) %>%
+  # if tbL and tbS are not the same female, add the female that lost the tie-break to the total sum of visit days
+  mutate(sum_vD_initL = ifelse(initiator_tbL!=initiator_tbS,
+                           sum_vD+init_durS, sum_vD),
+         sum_vD_initS = ifelse(initiator_tbS!=initiator_tbL,
+                           sum_vD+init_durL, sum_vD),
+         visited = vDb4h_sc2h > 0,
+         pmDvD = vDb4h_sc2h/mDb4h_sc2h) %>%
+  left_join(top5eggs_summary) %>%
+  select(location, last_des_rel2h, first_des_rel2h_init,
+         ants_removed, females_removed, initiation_date, est_hatch, `visited in 4 days`,
+         sum_mD, sum_vD, sum_gD, mDb4h_sc2h,
+         num_at_init, init_desert_early, last_desert,
+         n_eggs = max_egg_num, med_t5eggs, mean_t5eggs, max_n_eggs,
+         max_egg_len, med_l_t5eggs, mean_l_t5eggs, max_l_eggs,
+         init_durL, init_durS, desert_rel2hL, desert_rel2hS,
+         sum_vD_initL, sum_vD_initS, initMb4h_sc2hL, initMb4h_sc2hS,
+         initiator_tbL, initiator_tbS,
+         n_clutches_on_plant, visited, pmDvD, DormPlant)
+
+# add filtered and curated nymph and adult counts
+clutch_survivorship_data <- clutch_egg_num_data %>%
+  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2,
+                   -c(ants_removed, females_removed, initiation_date, n_eggs)),
+            by=c("location"="NOr_rev_loc"))
+```
+
+# 12 - Write data for `Publilia-03-survivorship.Rmd` to `.rds` for further analysis in clean environment
+
+## 12.0 - Combine all data for regressions
+```{r}
+surv_reg_data <- clutch_survivorship_data %>% 
+  filter(!is.na(`visited in 4 days`)) %>%
+  select(location, med_t5eggs, n_hatched, n_survived,
+         des=last_des_rel2h, ants_removed, vis=`visited in 4 days`,
+         females_removed, initiation_date, est_hatch) %>%
+  mutate(n_survived = ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
+                             n_hatched, n_survived), # force n_survived/n_hatched=1
+         ant_treatment=ifelse(ants_removed, "Removed", "Control")) %>%
+  left_join(select(ant_counts, location, 
+                   ever_antsP_b4h, ever_antsP_afh, ever_antsP)) %>%
+  mutate(ants_b4h=ifelse(ever_antsP_b4h," ever", " never"),
+         ants_afh=ifelse(ever_antsP_afh," ever"," never"),
+         ants_ever=ifelse(ever_antsP," ever"," never")) %>%
+  left_join(select(ant_n_days, -ants_everP, -ant_treatment, -females_removed)) %>%
+  mutate(ants_gt2d=ifelse(antsP_gt2d," ants", " no ants"),
+         ants_gt3d=ifelse(antsP_gt3d," ants", " no ants")) %>% 
+  separate(location, into = c("DormPlant", "Leaf"), sep="_", remove=FALSE) %>%
+  left_join(dplyr::select(moms_plant_data, DormPlant, last_visit_ends_P), by="DormPlant") %>%
+  mutate(last_desP_rel2h = last_visit_ends_P-est_hatch,
+         desP = last_desP_rel2h) 
+```
+
+## `Publilia-03-survivorship.Rmd`
+```{r}
+write_rds(surv_reg_data, here("saved_rds/surv_reg_data.rds"))
+```

### 2023-08-11 scripts/Publilia-03-survivorship.Rmd
Moved all data prep for `Publilia-03-survivorship.Rmd` to `Publilia-01-qc.Rmd`

@@
 
-# 0 - Data import
+# 0 - Data import and custom functions
 
-clutch_status_guarding_summary_v2
+## Data for regressions
 ```{r}
-All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))
-
-clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
-# last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))
-# 
-# strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
+surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
 ```
 
-# Final figures and stats using functions
-Use the same data for each regression
+## Custom functions
+
+### Model fitting and confidence intervals and plotting functions
 ```{r}
-# I originally used the ants_removed as the predictor representing ants, but I am now redoing the analysis using whether ants were ever observed at the clutch.
-surv_reg_data <- clutch_survivorship_data %>% 
-  filter(!is.na(`visited in 4 days`)) %>%
-  select(location, med_t5eggs, n_hatched, n_survived,
-         des=last_des_rel2h, ants_removed, vis=`visited in 4 days`,
-         females_removed, initiation_date, est_hatch) %>%
-  mutate(n_survived = ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
-                             n_hatched, n_survived), # force n_survived/n_hatched=1
-         ant_treatment=ifelse(ants_removed, "Removed", "Control")) %>%
-  left_join(select(ant_counts, location, 
-                   ever_antsP_b4h, ever_antsP_afh, ever_antsP)) %>%
-  mutate(ants_b4h=ifelse(ever_antsP_b4h," ever", " never"),
-         ants_afh=ifelse(ever_antsP_afh," ever"," never"),
-         ants_ever=ifelse(ever_antsP," ever"," never")) %>%
-  left_join(select(ant_n_days, -ants_everP, -ant_treatment, -females_removed)) %>%
-  mutate(ants_gt2d=ifelse(antsP_gt2d," ants", " no ants"),
-         ants_gt3d=ifelse(antsP_gt3d," ants", " no ants")) %>% 
-  separate(location, into = c("DormPlant", "Leaf"), sep="_", remove=FALSE) %>%
-  left_join(dplyr::select(moms_plant_data, DormPlant, last_visit_ends_P), by="DormPlant") %>%
-  mutate(last_desP_rel2h = last_visit_ends_P-est_hatch,
-         desP = last_desP_rel2h) 
-```
+### fit survivorship model
+fit_surv <- function(data_in, survNom, survDen, tenure, 
+                     treatment, vis, interaction=c("full","pw")){
+  data <- eval(substitute(data_in %>% filter(!is.na(tenure))))
 
-# Final (really this time) figures for the dissertation
-Choosing the models strictly based on qAICc leads to some odd results that make biological interpretation too complciated.
+  mai.b <- eval(substitute(glm(survNom/survDen ~ 
+            tenure*treatment,
+          data = data, weights = survDen, family = binomial)))
+  print("Interaction, Binomial: ")
+  print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])
 
-Hatching success: All model types are within ~2 qAICc of each other, so pick whichever shows the biology best and is most consistent with Nsurv and Esurv.
+  mai.qb <- eval(substitute(glm(survNom/survDen ~ 
+            tenure*treatment,
+          data = data, weights = survDen, family = quasibinomial)))
+  print("Interaction, Quasibinomial: ")
+  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])
 
-Nymph survivorship: desP * ants_ever * desP^2 has the best qAICc, and the desL version has the second best.
-The desL version (which, for biological interpretation's sake, should be in the main figure) has very wide 95% CI on the left side, which sends off alarm bells that model fit may be a less robust to addition or subtraction of samples than the AIC suggests.
+  ma.qb <- eval(substitute(glm(survNom/survDen ~ 
+            tenure+treatment,
+          data = data, weights = survDen, family = quasibinomial)))
+  print("No Interaction, Quasibinomial: ")
+  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])
 
-Egg survivorship: desL * ants_ever * desL^2  has best qAICc, by far.
-Again the left side 95% CI is huge and it just looks terrible, suggesting to me that there may be too few influential points on the right side to conclusively support the convex up shape.
+  mai.models <- list(mai.b = mai.b, mai.qb = mai.qb, ma.qb = ma.qb)
+  return(mai.models)
+}
 
-One problem with the ants_ever method is that the `never ants` level has a much smaller sample size than the `ever ants` level.
-I'm worried that this could make conclusive inference on the difference among these treatments or even just slope and shape could be shaky.
-Breaking the groups into `ants >2 days` vs `ants <=2 days` solves the unequal sample sizes problem and makes the desL figure more straightforward to interpret.
-The qAICc is considerably worse, but I'm concerned that it is only because ants ever was overfitting with too little data.
+# Example
+# test_fits <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants,
+#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)
 
-So, I'm making `desL * ants_gt2 * desL^2` the main figure and `desP * ants_gt2 * desP^2` the supplemental figure.
-I will report the qAICc of these two models, but not in a table.
-The data summary table, regression table and results text will need to change too.
+### fit survivorship model
+fit_surv_quad <- function(data_in, survNom, survDen, tenure, 
+                     treatment){
+  data <- eval(substitute(data_in %>% filter(!is.na(tenure))))
 
-*******
+  mai.b <- eval(substitute(glm(survNom/survDen ~
+            tenure*treatment + (I(as.numeric(tenure)^2))*treatment,
+          data = data, weights = survDen, family = binomial)))
+  print("Interaction, Binomial: ")
+  print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])
 
-After running all these new regressions, I realize that the desL * ant treatment quadratic model has the lowest qAICc and the most interpretable plot and summary stats. I will use this instead.
+  mai.qb <- eval(substitute(glm(survNom/survDen ~
+            tenure*treatment + (I(as.numeric(tenure)^2))*treatment,
+          data = data, weights = survDen, family = quasibinomial)))
+  print("Interaction, Quasibinomial: ")
+  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])
 
-And since the desP models perform poorly (both in terms of AICc and a convex up Nsurv fit), I just won't even include them in the supplement.
-I can include the desL `ants >2 days` in the supplement, but honestly it might not even be necessary since it looks so similar to the treatment-based model.
-I can just mention they are similar?
+  ma.qb <- eval(substitute(glm(survNom/survDen ~
+            tenure+treatment + (I(as.numeric(tenure)^2))*treatment,
+          data = data, weights = survDen, family = quasibinomial)))
+  print("No Interaction, Quasibinomial: ")
+  print(capture.output(summary(ma.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(ma.qb))))-1)])
 
-# Main - `desL * ants_gt2 * desL^2`
+    mai.models <- list(mai.b = mai.b, mai.qb = mai.qb, ma.qb = ma.qb)
+  return(mai.models)
+}
 
-## Tables
-```{r}
-(surv_reg_data.tbl_summary.desL.ants_gt2d <- surv_reg_data %>%
-  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
-         females = ifelse(females_removed, "Females removed", "Control"),
-         `leaf desert date rel. hatch` = des,
-         `visited early` = vis,
-         `n eggs` = med_t5eggs,
-         `n hatched` = n_hatched,
-         `n survived` = n_survived) %>%
-  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
-         `n eggs`, `n hatched`, `n survived`) %>%
-  group_by(females, ants) %>%
-  tbl_summary(by = ants) %>%
-  bold_labels() %>% italicize_levels() %>%
-  add_n())
+# Example
+# test_fits <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants,
+#                  survNom=n_hatched, survDen=med_t5eggs)
 
-surv_reg_data.tbl_summary.desL.ants_gt2d %>%
-  as_flex_table() %>%
-  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desL.ants_gt2d.docx")
-```
+### Create confidence intervals in the link scale for plotting, and backtransform for plot
+# Based on: https://fromthebottomoftheheap.net/2018/12/10/confidence-intervals-for-glms/
+ci_for_plot <- function(data_in, survNom, survDen, 
+                        tenure, treatment, model){
 
-```{r}
-hatch.desL.ants_gt2d.quad.qb.tbl <- 
-  tbl_regression(des_hatch.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
-                 label=list(des ~ "Leaf desert date",
-                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
-                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
-Nsurv.desL.ants_gt2d.quad.qb.tbl <- 
-  tbl_regression(des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
-                 label=list(des ~ "Leaf desert date",
-                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
-                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
-Esurv.desL.ants_gt2d.quad.qb.tbl <- 
-  tbl_regression(des_Esurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
-                 label=list(des ~ "Leaf desert date",
-                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
-                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
+  data <- eval(substitute(
+    data_in %>% filter(!is.na(tenure)) %>%
+      select(location, tenure, treatment, survDen, survNom) %>%
+      add_column(fit = predict(model, newdata = ., type = 'response'))
+    ))
 
-(desL.ants_gt2d.quad.qb.tbl.merge <- 
-  tbl_merge(
-    tbls = list(hatch.desL.ants_gt2d.quad.qb.tbl, 
-                Nsurv.desL.ants_gt2d.quad.qb.tbl, 
-                Esurv.desL.ants_gt2d.quad.qb.tbl),
-    tab_spanner = c("**Hatching success**", 
-                    "**Survivorship of nymphs**", 
-                    "**Survivorship of eggs**")
-  ) %>%
-  modify_header(label = "**Variable**") %>%
-  bold_labels() %>% italicize_levels())
+  ## grad the inverse link function
+  ilink <- family(model)$linkinv
 
-desL.ants_gt2d.quad.qb.tbl.merge %>%
-  as_flex_table() %>%
-  flextable::save_as_docx(path="surv.reg_summary.desL.ants_gt2d.quad.docx")
-```
+  ## add fit and se.fit on the **link** scale
+  data_fit_link <- eval(substitute(
+    data %>% add_column(
+  setNames(as_tibble(predict(model, data, se.fit = TRUE)[1:2]),
+           c('fit_link','se_link'))) %>%
+## create the interval and backtransform
+  mutate(fit_resp  = ilink(fit_link),
+         conf_upr = ilink(fit_link + (2 * se_link)),
+         conf_lwr = ilink(fit_link - (2 * se_link)))
+    ))
 
-## Figures
-```{r}
-# hatching success
-des_hatch.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_hatched, survDen=med_t5eggs,
-                              tenure=des, treatment=ants_gt2d)
+  return(data_fit_link)
+}
 
-des_hatch.desL.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
-              tenure=des, treatment=ants_gt2d,
-              survNom=n_hatched, survDen=med_t5eggs,
-              model = des_hatch.desL.ants_gt2d.quad.fits$mai.qb)
+# Example
+# test_fits.pw <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants, 
+#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)
+# 
+# test_ci_data <- ci_for_plot(data_in=hatch.data, tenure=des, treatment=ants, 
+#                  survNom=n_hatched, survDen=med_t5eggs,
+#                  model = test_fits.pw$mai.qb)
 
-des_hatch.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ants_gt2d.quad.qb.ci, 
-                                  tenure=des, treatment=ants_gt2d,
-             survNom = n_hatched, survDen = med_t5eggs) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Hatching success\n(nymphs/eggs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
+### Plot model results with confidence intervals
+plot_ci <- function(ci_data, survNom, survDen, treatment, tenure){
+  (eval(substitute(plot <- ggplot(data = ci_data, 
+       aes(x = tenure, y = fit, 
+           color = treatment, fill = treatment)) +
+    theme_publilia() +
+    geom_point(aes(y = survNom/survDen), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
+    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
+    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
+                    alpha = 0.5, color = NA, key_glyph=draw_key_rect))))
+#
+}
 
-# nymph survivorship
-des_Nsurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=n_hatched,
-                              tenure=des, treatment=ants_gt2d)
-
-des_Nsurv.desL.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
-              tenure=des, treatment=ants_gt2d,
-              survNom=n_survived, survDen=n_hatched,
-              model = des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb)
-
-des_Nsurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ants_gt2d.quad.qb.ci, 
-                                  tenure=des, treatment=ants_gt2d,
-             survNom = n_survived, survDen = n_hatched) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
-# egg survivorship
-des_Esurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=med_t5eggs,
-                              tenure=des, treatment=ants_gt2d)
-
-des_Esurv.desL.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
-              tenure=des, treatment=ants_gt2d,
-              survNom=n_survived, survDen=med_t5eggs,
-              model = des_Esurv.desL.ants_gt2d.quad.fits$mai.qb)
-
-des_Esurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desL.ants_gt2d.quad.qb.ci, 
-                                  tenure=des, treatment=ants_gt2d,
-             survNom = n_survived, survDen = med_t5eggs) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
-    scale_color_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days")) +
-    scale_fill_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days"))
-
-(desL.ants_gt2d.quad.qb.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad.qb.p+
-                 theme(legend.position="none"),
-               des_Nsurv.desL.ants_gt2d.quad.qb.p+
-                 theme(legend.position="none"),
-               des_Esurv.desL.ants_gt2d.quad.qb.p+
-                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
-               labels=c("A","B","C"),
-               ncol=3))
-
-ggsave("desL.ants_gt2d.quad.final.png",
-       desL.ants_gt2d.quad.qb.p,
-       device="png", width = 300, height = 110, units = "mm", dpi = "print")
+# Example
+# test_fits.pw <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants,
+#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)
+# 
+# test_ci_data <- ci_for_plot(data_in=hatch.data, tenure=des, treatment=ants,
+#                  survNom=n_hatched, survDen=med_t5eggs,
+#                  model = test_fits.pw$mai.qb)
+# 
+# (p <- plot_ci(ci_data = test_ci_data, tenure = des, treatment=ants,
+#              survNom = n_hatched, survDen = med_t5eggs) +
+#     xlab("Latest desertion date relative to hatch") +
+#     ylab("Hatching success") +
+#     scale_color_manual(values = c("brown1", "black")) +
+#     scale_fill_manual(values = c("brown1", "black")))
+# summary(test_fits.pw$mai.qb)
 ```
@@
 des_hatch.desL.ant_treatment.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
+  ci_for_plot(data_in=surv_reg_data, 
               tenure=des, treatment=ant_treatment,
@@
 des_Nsurv.desL.ant_treatment.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
+  ci_for_plot(data_in=surv_reg_data, 
               tenure=des, treatment=ant_treatment,
@@
 des_Esurv.desL.ant_treatment.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
+  ci_for_plot(data_in=surv_reg_data, 
               tenure=des, treatment=ant_treatment,
@@
   flextable::save_as_docx(path="surv.reg_summary.desL.ants_treatment.quad.docx")
+```
+
+# Main - `desL * ants_gt2 * desL^2`
+
+## Tables
+```{r}
+(surv_reg_data.tbl_summary.desL.ants_gt2d <- surv_reg_data %>%
+  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
+         females = ifelse(females_removed, "Females removed", "Control"),
+         `leaf desert date rel. hatch` = des,
+         `visited early` = vis,
+         `n eggs` = med_t5eggs,
+         `n hatched` = n_hatched,
+         `n survived` = n_survived) %>%
+  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
+         `n eggs`, `n hatched`, `n survived`) %>%
+  group_by(females, ants) %>%
+  tbl_summary(by = ants) %>%
+  bold_labels() %>% italicize_levels() %>%
+  add_n())
+
+surv_reg_data.tbl_summary.desL.ants_gt2d %>%
+  as_flex_table() %>%
+  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desL.ants_gt2d.docx")
+```
+
+```{r}
+hatch.desL.ants_gt2d.quad.qb.tbl <- 
+  tbl_regression(des_hatch.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
+                 label=list(des ~ "Leaf desert date",
+                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
+                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
+Nsurv.desL.ants_gt2d.quad.qb.tbl <- 
+  tbl_regression(des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
+                 label=list(des ~ "Leaf desert date",
+                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
+                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
+Esurv.desL.ants_gt2d.quad.qb.tbl <- 
+  tbl_regression(des_Esurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
+                 label=list(des ~ "Leaf desert date",
+                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
+                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
+
+(desL.ants_gt2d.quad.qb.tbl.merge <- 
+  tbl_merge(
+    tbls = list(hatch.desL.ants_gt2d.quad.qb.tbl, 
+                Nsurv.desL.ants_gt2d.quad.qb.tbl, 
+                Esurv.desL.ants_gt2d.quad.qb.tbl),
+    tab_spanner = c("**Hatching success**", 
+                    "**Survivorship of nymphs**", 
+                    "**Survivorship of eggs**")
+  ) %>%
+  modify_header(label = "**Variable**") %>%
+  bold_labels() %>% italicize_levels())
+
+desL.ants_gt2d.quad.qb.tbl.merge %>%
+  as_flex_table() %>%
+  flextable::save_as_docx(path="surv.reg_summary.desL.ants_gt2d.quad.docx")
+```
+
+## Figures
+```{r}
+# hatching success
+des_hatch.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
+                              survNom=n_hatched, survDen=med_t5eggs,
+                              tenure=des, treatment=ants_gt2d)
+
+des_hatch.desL.ants_gt2d.quad.qb.ci <- 
+  ci_for_plot(data_in=surv_reg_data, 
+              tenure=des, treatment=ants_gt2d,
+              survNom=n_hatched, survDen=med_t5eggs,
+              model = des_hatch.desL.ants_gt2d.quad.fits$mai.qb)
+
+des_hatch.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ants_gt2d.quad.qb.ci, 
+                                  tenure=des, treatment=ants_gt2d,
+             survNom = n_hatched, survDen = med_t5eggs) +
+    xlab("Latest desertion date from leaf\nrelative to hatch") +
+    ylab("Hatching success\n(nymphs/eggs)") + 
+    scale_color_manual(values = c("brown1", "black")) +
+    scale_fill_manual(values = c("brown1", "black"))
+
+# nymph survivorship
+des_Nsurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
+                              survNom=n_survived, survDen=n_hatched,
+                              tenure=des, treatment=ants_gt2d)
+
+des_Nsurv.desL.ants_gt2d.quad.qb.ci <- 
+  ci_for_plot(data_in=surv_reg_data, 
+              tenure=des, treatment=ants_gt2d,
+              survNom=n_survived, survDen=n_hatched,
+              model = des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb)
+
+des_Nsurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ants_gt2d.quad.qb.ci, 
+                                  tenure=des, treatment=ants_gt2d,
+             survNom = n_survived, survDen = n_hatched) +
+    xlab("Latest desertion date from leaf\nrelative to hatch") +
+    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
+    scale_color_manual(values = c("brown1", "black")) +
+    scale_fill_manual(values = c("brown1", "black"))
+
+# egg survivorship
+des_Esurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
+                              survNom=n_survived, survDen=med_t5eggs,
+                              tenure=des, treatment=ants_gt2d)
+
+des_Esurv.desL.ants_gt2d.quad.qb.ci <- 
+  ci_for_plot(data_in=surv_reg_data, 
+              tenure=des, treatment=ants_gt2d,
+              survNom=n_survived, survDen=med_t5eggs,
+              model = des_Esurv.desL.ants_gt2d.quad.fits$mai.qb)
+
+des_Esurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desL.ants_gt2d.quad.qb.ci, 
+                                  tenure=des, treatment=ants_gt2d,
+             survNom = n_survived, survDen = med_t5eggs) +
+    xlab("Latest desertion date from leaf\nrelative to hatch") +
+    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
+    scale_color_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days")) +
+    scale_fill_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days"))
+
+(desL.ants_gt2d.quad.qb.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad.qb.p+
+                 theme(legend.position="none"),
+               des_Nsurv.desL.ants_gt2d.quad.qb.p+
+                 theme(legend.position="none"),
+               des_Esurv.desL.ants_gt2d.quad.qb.p+
+                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
+               labels=c("A","B","C"),
+               ncol=3))
+
+ggsave("desL.ants_gt2d.quad.final.png",
+       desL.ants_gt2d.quad.qb.p,
+       device="png", width = 300, height = 110, units = "mm", dpi = "print")
 ```
@@
 des_hatch.desL.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
+  ci_for_plot(data_in=surv_reg_data, 
               tenure=des, treatment=ants_gt2d,
@@
 des_Nsurv.desL.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
+  ci_for_plot(data_in=surv_reg_data, 
               tenure=des, treatment=ants_gt2d,

### 2023-08-11 scripts/Publilia-03-survivorship.Rmd
converted offspring survivorship modeling workflow to functions

@@
 ### fit survivorship model
-fit_surv <- function(data_in, survNom, survDen, tenure, 
-                     treatment, vis, interaction=c("full","pw")){
-  data <- eval(substitute(data_in %>% filter(!is.na(tenure))))
+fit_surv <- function(data_in, survNom, survDen, tenure, treatment, quad){
+  data <- data_in %>% filter(!is.na(.[[tenure]]))
 
-  mai.b <- eval(substitute(glm(survNom/survDen ~ 
-            tenure*treatment,
-          data = data, weights = survDen, family = binomial)))
+  if (!quad) {
+    formula.mai <- paste0(survNom,"/",survDen,"~",tenure,"*",treatment) %>% as.formula()
+    formula.ma <- paste0(survNom,"/",survDen,"~",tenure,"+",treatment) %>% as.formula()
+  } else if (quad) {
+    formula.mai <- paste0(
+      survNom,"/",survDen,"~",
+      tenure,"*",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
+      ) %>% as.formula()
+    formula.ma <- paste0(
+      survNom,"/",survDen,"~",
+      tenure,"+",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
+    ) %>% as.formula()
+  }
+
+  mai.b <- glm(formula = formula.mai, data = data, weights = data[[survDen]], family = binomial)
   print("Interaction, Binomial: ")
@@
 
-  mai.qb <- eval(substitute(glm(survNom/survDen ~ 
-            tenure*treatment,
-          data = data, weights = survDen, family = quasibinomial)))
+  mai.qb <- glm(formula = formula.mai, data = data, weights = data[[survDen]], family = quasibinomial)
   print("Interaction, Quasibinomial: ")
@@
 
-  ma.qb <- eval(substitute(glm(survNom/survDen ~ 
-            tenure+treatment,
-          data = data, weights = survDen, family = quasibinomial)))
+  ma.qb <- glm(formula = formula.ma, data = data, weights = data[[survDen]], family = binomial)
   print("No Interaction, Quasibinomial: ")
@@
 
-# Example
-# test_fits <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants,
-#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)
-
-### fit survivorship model
-fit_surv_quad <- function(data_in, survNom, survDen, tenure, 
-                     treatment){
-  data <- eval(substitute(data_in %>% filter(!is.na(tenure))))
-
-  mai.b <- eval(substitute(glm(survNom/survDen ~
-            tenure*treatment + (I(as.numeric(tenure)^2))*treatment,
-          data = data, weights = survDen, family = binomial)))
-  print("Interaction, Binomial: ")
-  print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])
-
-  mai.qb <- eval(substitute(glm(survNom/survDen ~
-            tenure*treatment + (I(as.numeric(tenure)^2))*treatment,
-          data = data, weights = survDen, family = quasibinomial)))
-  print("Interaction, Quasibinomial: ")
-  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])
-
-  ma.qb <- eval(substitute(glm(survNom/survDen ~
-            tenure+treatment + (I(as.numeric(tenure)^2))*treatment,
-          data = data, weights = survDen, family = quasibinomial)))
-  print("No Interaction, Quasibinomial: ")
-  print(capture.output(summary(ma.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(ma.qb))))-1)])
-
-    mai.models <- list(mai.b = mai.b, mai.qb = mai.qb, ma.qb = ma.qb)
-  return(mai.models)
-}
-
-# Example
-# test_fits <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants,
-#                  survNom=n_hatched, survDen=med_t5eggs)
-
 ### Create confidence intervals in the link scale for plotting, and backtransform for plot
@@
 
-  data <- eval(substitute(
-    data_in %>% filter(!is.na(tenure)) %>%
-      select(location, tenure, treatment, survDen, survNom) %>%
+  data <- data_in %>%
+    filter(!is.na(.data[[tenure]])) %>%
+    select(location, all_of(tenure), all_of(treatment), all_of(survDen), all_of(survNom)) %>%
     add_column(fit = predict(model, newdata = ., type = 'response'))
-    ))
 
@@
   ## add fit and se.fit on the **link** scale
-  data_fit_link <- eval(substitute(
-    data %>% add_column(
-  setNames(as_tibble(predict(model, data, se.fit = TRUE)[1:2]),
-           c('fit_link','se_link'))) %>%
+  data_fit_link <- data %>% 
+    add_column(
+      predict(model, data, se.fit = TRUE)[1:2] %>% 
+        as_tibble() %>%
+        setNames(c('fit_link','se_link'))) %>%
     ## create the interval and backtransform
-  mutate(fit_resp  = ilink(fit_link),
-         conf_upr = ilink(fit_link + (2 * se_link)),
-         conf_lwr = ilink(fit_link - (2 * se_link)))
-    ))
+    mutate(fit_resp  = ilink(.data$fit_link),
+           conf_upr = ilink(.data$fit_link + (2 * .data$se_link)),
+           conf_lwr = ilink(.data$fit_link - (2 * .data$se_link)))
 
@@
 # Example
-# test_fits.pw <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants, 
-#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)
+# test_fits <- fit_surv(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
+#                  survNom="n_hatched", survDen="med_t5eggs", quad=TRUE)
 # 
-# test_ci_data <- ci_for_plot(data_in=hatch.data, tenure=des, treatment=ants, 
-#                  survNom=n_hatched, survDen=med_t5eggs,
-#                  model = test_fits.pw$mai.qb)
+# test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
+#                  survNom="n_hatched", survDen="med_t5eggs",
+#                  model = test_fits$mai.qb)
 
@@
 plot_ci <- function(ci_data, survNom, survDen, treatment, tenure){
-  (eval(substitute(plot <- ggplot(data = ci_data, 
-       aes(x = tenure, y = fit, 
-           color = treatment, fill = treatment)) +
+  plot <- ggplot(data = ci_data, 
+       aes(x = .data[[tenure]], y = fit, 
+           color = .data[[treatment]], fill = .data[[treatment]])) +
     theme_publilia() +
-    geom_point(aes(y = survNom/survDen), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
+    geom_point(aes(y = .data[[survNom]]/.data[[survDen]]), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
     geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
     geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
-                    alpha = 0.5, color = NA, key_glyph=draw_key_rect))))
-#
+                    alpha = 0.5, color = NA, key_glyph=draw_key_rect)
 }
@@
 # Example
-# test_fits.pw <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants,
-#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)
+# test_fits <- fit_surv(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
+#                  survNom="n_hatched", survDen="med_t5eggs", quad=TRUE)
 # 
-# test_ci_data <- ci_for_plot(data_in=hatch.data, tenure=des, treatment=ants,
-#                  survNom=n_hatched, survDen=med_t5eggs,
-#                  model = test_fits.pw$mai.qb)
+# test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
+#                  survNom="n_hatched", survDen="med_t5eggs",
+#                  model = test_fits$mai.qb)
 # 
-# (p <- plot_ci(ci_data = test_ci_data, tenure = des, treatment=ants,
-#              survNom = n_hatched, survDen = med_t5eggs) +
+# (p <- plot_ci(ci_data = test_ci_data, tenure="des", treatment="ant_treatment",
+#                  survNom="n_hatched", survDen="med_t5eggs") +
 #     xlab("Latest desertion date relative to hatch") +
@@
 #     scale_fill_manual(values = c("brown1", "black")))
-# summary(test_fits.pw$mai.qb)
+# summary(test_fits$mai.qb)
+```
+
+### Wrapper functions
+```{r}
+runTenureXOffspringModel <- function(surv_reg_data, survNom, survDen, tenure, treatment, quad = TRUE) {
+
+  if (quad) {
+    test_fits <- surv_reg_data %>%
+      fit_surv(data_in=., tenure=tenure, treatment=treatment, 
+               survNom=survNom, survDen=survDen, quad = TRUE)
+  } else if (!quad) {
+    test_fits <- surv_reg_data %>%
+      fit_surv(data_in=., tenure=tenure, treatment=treatment, 
+               survNom=survNom, survDen=survDen, quad = FALSE)
+  }
+
+  test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure=tenure, treatment=treatment,
+                              survNom=survNom, survDen=survDen,
+                              model = test_fits$mai.qb)
+
+  p <- plot_ci(ci_data = test_ci_data, tenure = tenure, treatment=treatment,
+                survNom = survNom, survDen = survDen) +
+      xlab("Latest desertion date relative to hatch") +
+      ylab("Hatching success") +
+      scale_color_manual(values = c("brown1", "black")) +
+      scale_fill_manual(values = c("brown1", "black"))
+  stat_summary <- summary(test_fits$mai.qb)
+
+  obj_out <- list(
+    fits = test_fits,
+    ci = test_ci_data,
+    p = p,
+    summary = stat_summary
+  )
+  return(obj_out)
+}
+
+# Example
+# des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
+#   runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
+#                            tenure="des", treatment="ant_treatment")
 ```
@@
 # hatching success
-des_hatch.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_hatched, survDen=med_t5eggs,
+des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                            tenure=des, treatment=ant_treatment)
 
-des_hatch.desL.ant_treatment.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=des, treatment=ant_treatment,
-              survNom=n_hatched, survDen=med_t5eggs,
-              model = des_hatch.desL.ant_treatment.quad.fits$mai.qb)
-
-des_hatch.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ant_treatment.quad.qb.ci, 
-                                  tenure=des, treatment=ant_treatment,
-             survNom = n_hatched, survDen = med_t5eggs) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Hatching success\n(nymphs/eggs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
 # nymph survivorship
-des_Nsurv.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=n_hatched,
+des_Nsurv.desL.ant_treatment.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                            tenure=des, treatment=ant_treatment)
 
-des_Nsurv.desL.ant_treatment.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=des, treatment=ant_treatment,
-              survNom=n_survived, survDen=n_hatched,
-              model = des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)
-
-des_Nsurv.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ant_treatment.quad.qb.ci, 
-                                  tenure=des, treatment=ant_treatment,
-             survNom = n_survived, survDen = n_hatched) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
 # egg survivorship
-des_Esurv.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=med_t5eggs,
+des_Esurv.desL.ant_treatment.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                            tenure=des, treatment=ant_treatment)
 
-des_Esurv.desL.ant_treatment.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=des, treatment=ant_treatment,
-              survNom=n_survived, survDen=med_t5eggs,
-              model = des_Esurv.desL.ant_treatment.quad.fits$mai.qb)
-
-des_Esurv.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Esurv.desL.ant_treatment.quad.qb.ci, 
-                                  tenure=des, treatment=ant_treatment,
-             survNom = n_survived, survDen = med_t5eggs) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
-    scale_color_manual(values = c("brown1", "black"), labels = c("Control", "Ant Exclusion")) +
-    scale_fill_manual(values = c("brown1", "black"), labels = c("Control", "Ant Exclusion"))
-
-(desL.ant_treatment.quad.qb.p <- egg::ggarrange(des_hatch.desL.ant_treatment.quad.qb.p+
+(desL.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desL.ant_treatment.quad$p +
                  theme(legend.position="none"),
-               des_Nsurv.desL.ant_treatment.quad.qb.p+
+               des_Nsurv.desL.ant_treatment.quad$p +
                  theme(legend.position="none"),
-               des_Esurv.desL.ant_treatment.quad.qb.p+
-                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
+               des_Esurv.desL.ant_treatment.quad$p +
+                 theme(legend.position = c(0.8,0.95)) + 
+                 ylim(0,1),
                labels=c("A","B","C"),
@@
 ggsave("desL.ant_treatment.quad.final.png",
-       desL.ant_treatment.quad.qb.p,
+       desL.ant_treatment.quad.p,
        device="png", width = 300, height = 110, units = "mm", dpi = "print")
@@
 hatch.desL.ant_treatment.quad.qb.tbl <- 
-  tbl_regression(des_hatch.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_hatch.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                  label=list(des ~ "Leaf desert date",
@@
 Nsurv.desL.ant_treatment.quad.qb.tbl <- 
-  tbl_regression(des_Nsurv.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_Nsurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                  label=list(des ~ "Leaf desert date",
@@
 Esurv.desL.ant_treatment.quad.qb.tbl <- 
-  tbl_regression(des_Esurv.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_Esurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                  label=list(des ~ "Leaf desert date",
@@
 hatch.desL.ants_gt2d.quad.qb.tbl <- 
-  tbl_regression(des_hatch.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_hatch.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                  label=list(des ~ "Leaf desert date",
@@
 Nsurv.desL.ants_gt2d.quad.qb.tbl <- 
-  tbl_regression(des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_Nsurv.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                  label=list(des ~ "Leaf desert date",
@@
 Esurv.desL.ants_gt2d.quad.qb.tbl <- 
-  tbl_regression(des_Esurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_Esurv.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                  label=list(des ~ "Leaf desert date",
@@
 # hatching success
-des_hatch.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_hatched, survDen=med_t5eggs,
+des_hatch.desL.ants_gt2d.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                            tenure=des, treatment=ants_gt2d)
 
-des_hatch.desL.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=des, treatment=ants_gt2d,
-              survNom=n_hatched, survDen=med_t5eggs,
-              model = des_hatch.desL.ants_gt2d.quad.fits$mai.qb)
-
-des_hatch.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ants_gt2d.quad.qb.ci, 
-                                  tenure=des, treatment=ants_gt2d,
-             survNom = n_hatched, survDen = med_t5eggs) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Hatching success\n(nymphs/eggs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
 # nymph survivorship
-des_Nsurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=n_hatched,
+des_Nsurv.desL.ants_gt2d.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                            tenure=des, treatment=ants_gt2d)
 
-des_Nsurv.desL.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=des, treatment=ants_gt2d,
-              survNom=n_survived, survDen=n_hatched,
-              model = des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb)
-
-des_Nsurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ants_gt2d.quad.qb.ci, 
-                                  tenure=des, treatment=ants_gt2d,
-             survNom = n_survived, survDen = n_hatched) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
 # egg survivorship
-des_Esurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=med_t5eggs,
+des_Esurv.desL.ants_gt2d.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                            tenure=des, treatment=ants_gt2d)
 
-des_Esurv.desL.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=des, treatment=ants_gt2d,
-              survNom=n_survived, survDen=med_t5eggs,
-              model = des_Esurv.desL.ants_gt2d.quad.fits$mai.qb)
-
-des_Esurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desL.ants_gt2d.quad.qb.ci, 
-                                  tenure=des, treatment=ants_gt2d,
-             survNom = n_survived, survDen = med_t5eggs) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
-    scale_color_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days")) +
-    scale_fill_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days"))
-
-(desL.ants_gt2d.quad.qb.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad.qb.p+
+(desL.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad$p +
                  theme(legend.position="none"),
-               des_Nsurv.desL.ants_gt2d.quad.qb.p+
+               des_Nsurv.desL.ants_gt2d.quad$p +
                  theme(legend.position="none"),
-               des_Esurv.desL.ants_gt2d.quad.qb.p+
+               des_Esurv.desL.ants_gt2d.quad$p +
                  theme(legend.position=c(0.8,0.95))+ylim(0,1),
@@
 ggsave("desL.ants_gt2d.quad.final.png",
-       desL.ants_gt2d.quad.qb.p,
+       desL.ants_gt2d.quad.p,
        device="png", width = 300, height = 110, units = "mm", dpi = "print")
@@
 # hatching success
-des_hatch.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_hatched, survDen=med_t5eggs,
+des_hatch.desP.ants_gt2d.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                            tenure=desP, treatment=ants_gt2d)
 
-des_hatch.desP.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=desP, treatment=ants_gt2d,
-              survNom=n_hatched, survDen=med_t5eggs,
-              model = des_hatch.desP.ants_gt2d.quad.fits$mai.qb)
-
-des_hatch.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desP.ants_gt2d.quad.qb.ci, 
-                                  tenure=desP, treatment=ants_gt2d,
-             survNom = n_hatched, survDen = med_t5eggs) +
-    xlab("Latest desertion date from plant\nrelative to hatch") +
-    ylab("Hatching success\n(nymphs/eggs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
 # nymph survivorship
-des_Nsurv.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=n_hatched,
+des_Nsurv.desP.ants_gt2d.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                            tenure=desP, treatment=ants_gt2d)
 
-des_Nsurv.desP.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=desP, treatment=ants_gt2d,
-              survNom=n_survived, survDen=n_hatched,
-              model = des_Nsurv.desP.ants_gt2d.quad.fits$mai.qb)
-
-des_Nsurv.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ants_gt2d.quad.qb.ci, 
-                                  tenure=desP, treatment=ants_gt2d,
-             survNom = n_survived, survDen = n_hatched) +
-    xlab("Latest desertion date from plant\nrelative to hatch") +
-    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
 # egg survivorship
-des_Esurv.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=med_t5eggs,
+des_Esurv.desP.ants_gt2d.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                            tenure=desP, treatment=ants_gt2d)
 
-des_Esurv.desP.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=desP, treatment=ants_gt2d,
-              survNom=n_survived, survDen=med_t5eggs,
-              model = des_Esurv.desP.ants_gt2d.quad.fits$mai.qb)
-
-des_Esurv.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desP.ants_gt2d.quad.qb.ci, 
-                                  tenure=desP, treatment=ants_gt2d,
-             survNom = n_survived, survDen = med_t5eggs) +
-    xlab("Latest desertion date from plant\nrelative to hatch") +
-    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
-    scale_color_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days")) +
-    scale_fill_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days"))
-
-(desP.ants_gt2d.quad.qb.p <- egg::ggarrange(des_hatch.desP.ants_gt2d.quad.qb.p+
+(desP.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desP.ants_gt2d.quad$p +
                  theme(legend.position="none"),
-               des_Nsurv.desP.ants_gt2d.quad.qb.p+
+               des_Nsurv.desP.ants_gt2d.quad$p +
                  theme(legend.position="none"),
-               des_Esurv.desP.ants_gt2d.quad.qb.p+
+               des_Esurv.desP.ants_gt2d.quad$p +
                  theme(legend.position=c(0.8,0.95))+ylim(0,1),
@@
 ggsave("desP.ants_gt2d.quad.final.png",
-       desP.ants_gt2d.quad.qb.p,
+       desP.ants_gt2d.quad.p,
        device="png", width = 300, height = 110, units = "mm", dpi = "print")
@@
 hatch.desP.ants_gt2d.quad.qb.tbl <- 
-  tbl_regression(des_hatch.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_hatch.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                  label=list(desP ~ "Leaf desert date",
@@
 Nsurv.desP.ants_gt2d.quad.qb.tbl <- 
-  tbl_regression(des_Nsurv.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_Nsurv.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                  label=list(desP ~ "Leaf desert date",
@@
 Esurv.desP.ants_gt2d.quad.qb.tbl <- 
-  tbl_regression(des_Esurv.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_Esurv.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                  label=list(desP ~ "Leaf desert date",
@@
 # hatching success
-des_hatch.desP.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_hatched, survDen=med_t5eggs,
+des_hatch.desP.ant_treatment.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                            tenure=desP, treatment=ant_treatment)
 
-des_hatch.desP.ant_treatment.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=desP, treatment=ant_treatment,
-              survNom=n_hatched, survDen=med_t5eggs,
-              model = des_hatch.desP.ant_treatment.quad.fits$mai.qb)
-
-des_hatch.desP.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_hatch.desP.ant_treatment.quad.qb.ci, 
-                                  tenure=desP, treatment=ant_treatment,
-             survNom = n_hatched, survDen = med_t5eggs) +
-    xlab("Latest desertion date from plant\nrelative to hatch") +
-    ylab("Hatching success\n(nymphs/eggs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
 # nymph survivorship
-des_Nsurv.desP.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=n_hatched,
+des_Nsurv.desP.ant_treatment.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                            tenure=desP, treatment=ant_treatment)
 
-des_Nsurv.desP.ant_treatment.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=desP, treatment=ant_treatment,
-              survNom=n_survived, survDen=n_hatched,
-              model = des_Nsurv.desP.ant_treatment.quad.fits$mai.qb)
-
-des_Nsurv.desP.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ant_treatment.quad.qb.ci, 
-                                  tenure=desP, treatment=ant_treatment,
-             survNom = n_survived, survDen = n_hatched) +
-    xlab("Latest desertion date from plant\nrelative to hatch") +
-    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
 # egg survivorship
-des_Esurv.desP.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=med_t5eggs,
+des_Esurv.desP.ant_treatment.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                            tenure=desP, treatment=ant_treatment)
 
-des_Esurv.desP.ant_treatment.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=desP, treatment=ant_treatment,
-              survNom=n_survived, survDen=med_t5eggs,
-              model = des_Esurv.desP.ant_treatment.quad.fits$mai.qb)
-
-des_Esurv.desP.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Esurv.desP.ant_treatment.quad.qb.ci, 
-                                  tenure=desP, treatment=ant_treatment,
-             survNom = n_survived, survDen = med_t5eggs) +
-    xlab("Latest desertion date from plant\nrelative to hatch") +
-    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
-(desP.ant_treatment.quad.qb.p <- egg::ggarrange(des_hatch.desP.ant_treatment.quad.qb.p+
+(desP.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desP.ant_treatment.quad$p +
                  theme(legend.position="none"),
-               des_Nsurv.desP.ant_treatment.quad.qb.p+
+               des_Nsurv.desP.ant_treatment.quad$p +
                  theme(legend.position="none"),
-               des_Esurv.desP.ant_treatment.quad.qb.p+
+               des_Esurv.desP.ant_treatment.quad$p +
                  theme(legend.position=c(0.8,0.95))+ylim(0,1),
@@
 ggsave("desP.ant_treatment.quad.final.png",
-       desP.ant_treatment.quad.qb.p,
+       desP.ant_treatment.quad.p,
        device="png", width = 300, height = 110, units = "mm", dpi = "print")
@@
 hatch.desP.ant_treatment.quad.qb.tbl <- 
-  tbl_regression(des_hatch.desP.ant_treatment.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_hatch.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                  label=list(desP ~ "Leaf desert date",
@@
 Nsurv.desP.ant_treatment.quad.qb.tbl <- 
-  tbl_regression(des_Nsurv.desP.ant_treatment.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_Nsurv.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                  label=list(desP ~ "Leaf desert date",
@@
 Esurv.desP.ant_treatment.quad.qb.tbl <- 
-  tbl_regression(des_Esurv.desP.ant_treatment.quad.fits$mai.qb, exponentiate=T,
+  tbl_regression(des_Esurv.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                  label=list(desP ~ "Leaf desert date",
@@
                       des=rep(c(-20,10,0,10,20),2)), 
-             des_hatch.desL.ant_treatment.quad.fits$mai.qb)
+             des_hatch.desL.ant_treatment.quad$fits$mai.qb)
 
@@
                            des=rep(seq(-20,20,length.out=10000),2)),
-            model=des_hatch.desL.ant_treatment.quad.fits$mai.qb)
+            model=des_hatch.desL.ant_treatment.quad$fits$mai.qb)
 
@@
                       des=rep(c(-20,10,0,10,20),2)), 
-             des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)
+             des_Nsurv.desL.ant_treatment.quad$fits$mai.qb)
 
@@
                            des=rep(seq(-20,20,length.out=10000),2)),
-            model=des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)
+            model=des_Nsurv.desL.ant_treatment.quad$fits$mai.qb)
 
@@
                       des=rep(c(-20,10,0,10,20),2)), 
-             des_Esurv.desL.ant_treatment.quad.fits$mai.qb)
+             des_Esurv.desL.ant_treatment.quad$fits$mai.qb)
 
@@
                            des=rep(seq(-20,20,length.out=10000),2)),
-            model=des_Esurv.desL.ant_treatment.quad.fits$mai.qb)
+            model=des_Esurv.desL.ant_treatment.quad$fits$mai.qb)
 ```
@@
               survNom=n_hatched, survDen=med_t5eggs,
-              model = des_hatch.desL.ant_treatment.quad.fits$mai.qb)
+              model = des_hatch.desL.ant_treatment.quad$fits$mai.qb)
 
@@
               survNom=n_survived, survDen=n_hatched,
-              model = des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)
+              model = des_Nsurv.desL.ant_treatment.quad$fits$mai.qb)
 
@@
               survNom=n_hatched, survDen=med_t5eggs,
-              model = des_hatch.desL.ants_gt2d.quad.fits$mai.qb)
+              model = des_hatch.desL.ants_gt2d.quad$fits$mai.qb)
 
@@
               survNom=n_survived, survDen=n_hatched,
-              model = des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb)
+              model = des_Nsurv.desL.ants_gt2d.quad$fits$mai.qb)
 

### 2023-08-12 scripts/Publilia-03-survivorship.Rmd
moved custom funcs in report Publilia-03 to R/custom_functions.R

@@
 
-## Required libraries and functions
+# Required libraries and functions
 ```{r}
@@
 library(here)
+library(bbmle)
 
-theme_publilia <- function(){
-  theme_bw() +
-    theme(text = element_text(family = "Arial"),
-          axis.text = element_text(size = 12), 
-          axis.title = element_text(size = 14),
-          axis.line.x = element_line(color="black"), 
-          axis.line.y = element_line(color="black"),
-          panel.border = element_blank(),
-          panel.grid.major.x = element_blank(),                                          
-          panel.grid.minor.x = element_blank(),
-          panel.grid.minor.y = element_blank(),
-          panel.grid.major.y = element_blank(),  
-          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
-          plot.title = element_text(size = 18, vjust = 1, hjust = 0.5, face = "bold"),
-          legend.text = element_text(size = 10),          
-          legend.title = element_blank(),                              
-          # legend.position = c(0.90, 0.90), 
-          legend.key = element_blank(),
-          legend.background = element_rect(color = "black", 
-                                           fill = "transparent", 
-                                           size = 2, linetype = "blank"))
-}
+source(here("R/custom_functions.R"))
 ```
 
-# 0 - Data import and custom functions
+# 0 - Data import
 
@@
 
-## Custom functions
+# 1 - Model fitting and plotting figures
 
-### Model fitting and confidence intervals and plotting functions
-```{r}
-### fit survivorship model
-fit_surv <- function(data_in, survNom, survDen, tenure, treatment, quad){
-  data <- data_in %>% filter(!is.na(.[[tenure]]))
+## Main -`desL * ants_treatment * desL^2`
 
-  if (!quad) {
-    formula.mai <- paste0(survNom,"/",survDen,"~",tenure,"*",treatment) %>% as.formula()
-    formula.ma <- paste0(survNom,"/",survDen,"~",tenure,"+",treatment) %>% as.formula()
-  } else if (quad) {
-    formula.mai <- paste0(
-      survNom,"/",survDen,"~",
-      tenure,"*",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
-      ) %>% as.formula()
-    formula.ma <- paste0(
-      survNom,"/",survDen,"~",
-      tenure,"+",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
-    ) %>% as.formula()
-  }
-
-  mai.b <- glm(formula = formula.mai, data = data, weights = data[[survDen]], family = binomial)
-  print("Interaction, Binomial: ")
-  print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])
-
-  mai.qb <- glm(formula = formula.mai, data = data, weights = data[[survDen]], family = quasibinomial)
-  print("Interaction, Quasibinomial: ")
-  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])
-
-  ma.qb <- glm(formula = formula.ma, data = data, weights = data[[survDen]], family = binomial)
-  print("No Interaction, Quasibinomial: ")
-  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])
-
-  mai.models <- list(mai.b = mai.b, mai.qb = mai.qb, ma.qb = ma.qb)
-  return(mai.models)
-}
-
-### Create confidence intervals in the link scale for plotting, and backtransform for plot
-# Based on: https://fromthebottomoftheheap.net/2018/12/10/confidence-intervals-for-glms/
-ci_for_plot <- function(data_in, survNom, survDen, 
-                        tenure, treatment, model){
-
-  data <- data_in %>%
-    filter(!is.na(.data[[tenure]])) %>%
-    select(location, all_of(tenure), all_of(treatment), all_of(survDen), all_of(survNom)) %>%
-    add_column(fit = predict(model, newdata = ., type = 'response'))
-
-  ## grad the inverse link function
-  ilink <- family(model)$linkinv
-
-  ## add fit and se.fit on the **link** scale
-  data_fit_link <- data %>% 
-    add_column(
-      predict(model, data, se.fit = TRUE)[1:2] %>% 
-        as_tibble() %>%
-        setNames(c('fit_link','se_link'))) %>%
-    ## create the interval and backtransform
-    mutate(fit_resp  = ilink(.data$fit_link),
-           conf_upr = ilink(.data$fit_link + (2 * .data$se_link)),
-           conf_lwr = ilink(.data$fit_link - (2 * .data$se_link)))
-
-  return(data_fit_link)
-}
-
-# Example
-# test_fits <- fit_surv(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
-#                  survNom="n_hatched", survDen="med_t5eggs", quad=TRUE)
-# 
-# test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
-#                  survNom="n_hatched", survDen="med_t5eggs",
-#                  model = test_fits$mai.qb)
-
-### Plot model results with confidence intervals
-plot_ci <- function(ci_data, survNom, survDen, treatment, tenure){
-  plot <- ggplot(data = ci_data, 
-       aes(x = .data[[tenure]], y = fit, 
-           color = .data[[treatment]], fill = .data[[treatment]])) +
-    theme_publilia() +
-    geom_point(aes(y = .data[[survNom]]/.data[[survDen]]), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
-    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
-    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
-                    alpha = 0.5, color = NA, key_glyph=draw_key_rect)
-}
-
-# Example
-# test_fits <- fit_surv(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
-#                  survNom="n_hatched", survDen="med_t5eggs", quad=TRUE)
-# 
-# test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
-#                  survNom="n_hatched", survDen="med_t5eggs",
-#                  model = test_fits$mai.qb)
-# 
-# (p <- plot_ci(ci_data = test_ci_data, tenure="des", treatment="ant_treatment",
-#                  survNom="n_hatched", survDen="med_t5eggs") +
-#     xlab("Latest desertion date relative to hatch") +
-#     ylab("Hatching success") +
-#     scale_color_manual(values = c("brown1", "black")) +
-#     scale_fill_manual(values = c("brown1", "black")))
-# summary(test_fits$mai.qb)
-```
-
-### Wrapper functions
-```{r}
-runTenureXOffspringModel <- function(surv_reg_data, survNom, survDen, tenure, treatment, quad = TRUE) {
-
-  if (quad) {
-    test_fits <- surv_reg_data %>%
-      fit_surv(data_in=., tenure=tenure, treatment=treatment, 
-               survNom=survNom, survDen=survDen, quad = TRUE)
-  } else if (!quad) {
-    test_fits <- surv_reg_data %>%
-      fit_surv(data_in=., tenure=tenure, treatment=treatment, 
-               survNom=survNom, survDen=survDen, quad = FALSE)
-  }
-
-  test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure=tenure, treatment=treatment,
-                              survNom=survNom, survDen=survDen,
-                              model = test_fits$mai.qb)
-
-  p <- plot_ci(ci_data = test_ci_data, tenure = tenure, treatment=treatment,
-                survNom = survNom, survDen = survDen) +
-      xlab("Latest desertion date relative to hatch") +
-      ylab("Hatching success") +
-      scale_color_manual(values = c("brown1", "black")) +
-      scale_fill_manual(values = c("brown1", "black"))
-  stat_summary <- summary(test_fits$mai.qb)
-
-  obj_out <- list(
-    fits = test_fits,
-    ci = test_ci_data,
-    p = p,
-    summary = stat_summary
-  )
-  return(obj_out)
-}
-
-# Example
-# des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
-#   runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
-#                            tenure="des", treatment="ant_treatment")
-```
-
-# Supp 1 -`desL * ants_treatment * desL^2`
-## Figures
+### Fit models
 ```{r}
@@
 des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
-                           tenure=des, treatment=ant_treatment)
+  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
+                           tenure="des", treatment="ant_treatment")
 
@@
 des_Nsurv.desL.ant_treatment.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
-                           tenure=des, treatment=ant_treatment)
+  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
+                           tenure="des", treatment="ant_treatment")
 
@@
 des_Esurv.desL.ant_treatment.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
-                           tenure=des, treatment=ant_treatment)
+  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
+                           tenure="des", treatment="ant_treatment")
 
+models_output <- list(
+  hatch = des_hatch.desL.ant_treatment.quad$fits,
+  Nsurv = des_Nsurv.desL.ant_treatment.quad$fits,
+  Esurv = des_Esurv.desL.ant_treatment.quad$fits
+)
+```
+
+### Plot figures
+```{r}
 (desL.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desL.ant_treatment.quad$p +
@@
 
-## Tables
+### Print model outputs
+#### Hatch
+```{r}
+print_glm_stats(models_output$hatch)
+```
+
+#### Nsurv
+```{r}
+print_glm_stats(models_output$Nsurv)
+```
+
+#### Esurv
+```{r}
+print_glm_stats(models_output$Esurv)
+```
+
+### Tables
+
+#### Sample sizes
 ```{r}
@@
 
+#### Parameter fit tables
 ```{r}
@@
 
-# Main - `desL * ants_gt2 * desL^2`
+## Supp 1 - `desL * ants_gt2 * desL^2`
 
-## Tables
+### Fit models
+```{r}
+# hatching success
+des_hatch.desL.ants_gt2d.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
+                           tenure="des", treatment="ants_gt2d")
+
+# nymph survivorship
+des_Nsurv.desL.ants_gt2d.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
+                           tenure="des", treatment="ants_gt2d")
+
+# egg survivorship
+des_Esurv.desL.ants_gt2d.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
+                           tenure="des", treatment="ants_gt2d")
+```
+
+### Plot figures
+```{r}
+(desL.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad$p +
+                 theme(legend.position="none"),
+               des_Nsurv.desL.ants_gt2d.quad$p +
+                 theme(legend.position="none"),
+               des_Esurv.desL.ants_gt2d.quad$p +
+                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
+               labels=c("A","B","C"),
+               ncol=3))
+
+ggsave("desL.ants_gt2d.quad.final.png",
+       desL.ants_gt2d.quad.p,
+       device="png", width = 300, height = 110, units = "mm", dpi = "print")
+```
+
+### Tables
+
+#### Sample sizes
 ```{r}
@@
 
-## Figures
-```{r}
-# hatching success
-des_hatch.desL.ants_gt2d.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
-                           tenure=des, treatment=ants_gt2d)
+## Supp 2 -`desP * ants_gt2 * desP^2`
 
-# nymph survivorship
-des_Nsurv.desL.ants_gt2d.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
-                           tenure=des, treatment=ants_gt2d)
-
-# egg survivorship
-des_Esurv.desL.ants_gt2d.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
-                           tenure=des, treatment=ants_gt2d)
-
-(desL.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad$p +
-                 theme(legend.position="none"),
-               des_Nsurv.desL.ants_gt2d.quad$p +
-                 theme(legend.position="none"),
-               des_Esurv.desL.ants_gt2d.quad$p +
-                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
-               labels=c("A","B","C"),
-               ncol=3))
-
-ggsave("desL.ants_gt2d.quad.final.png",
-       desL.ants_gt2d.quad.p,
-       device="png", width = 300, height = 110, units = "mm", dpi = "print")
-```
-
-# Supp 2 -`desP * ants_gt2 * desP^2`
-## Figures
+### Fit models
 ```{r}
@@
 des_hatch.desP.ants_gt2d.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
-                           tenure=desP, treatment=ants_gt2d)
+  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
+                           tenure="desP", treatment="ants_gt2d")
 
@@
 des_Nsurv.desP.ants_gt2d.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
-                           tenure=desP, treatment=ants_gt2d)
+  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
+                           tenure="desP", treatment="ants_gt2d")
 
@@
 des_Esurv.desP.ants_gt2d.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
-                           tenure=desP, treatment=ants_gt2d)
+  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
+                           tenure="desP", treatment="ants_gt2d")
+```
 
+### Plot figures
+```{r}
 (desP.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desP.ants_gt2d.quad$p +
@@
 
-## Tables
+### Tables
+
+#### Sample sizes
 don't need to include the data summary in supp, since the only thing that changes is the median (IQR) for desertion
@@
 
+#### Parameter fits table
 ```{r}
@@
 
-# Supp 3 -`desP * ant_s_gt2_treatment * desP^2`
-## Figures
+## Supp 3 -`desP * ant_s_gt2_treatment * desP^2`
+
+### Fit models
 ```{r}
@@
 des_hatch.desP.ant_treatment.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
-                           tenure=desP, treatment=ant_treatment)
+  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
+                           tenure="desP", treatment="ant_treatment")
 
@@
 des_Nsurv.desP.ant_treatment.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
-                           tenure=desP, treatment=ant_treatment)
+  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
+                           tenure="desP", treatment="ant_treatment")
 
@@
 des_Esurv.desP.ant_treatment.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
-                           tenure=desP, treatment=ant_treatment)
+  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
+                           tenure="desP", treatment="ant_treatment")
+```
 
+### Plot figures
+```{r}
 (desP.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desP.ant_treatment.quad$p +
@@
 
-# qAICc
+# 2 - qAICc across all models
 ```{r}
@@
   qAICc = c(
-    get_qaicc(des_hatch.desL.ant_treatment.quad.fits),
-    get_qaicc(des_hatch.desP.ant_treatment.quad.fits),
-    get_qaicc(des_hatch.desL.ants_gt2d.quad.fits),
-    get_qaicc(des_hatch.desP.ants_gt2d.quad.fits))
+    get_qaicc(des_hatch.desL.ant_treatment.quad$fits),
+    get_qaicc(des_hatch.desP.ant_treatment.quad$fits),
+    get_qaicc(des_hatch.desL.ants_gt2d.quad$fits),
+    get_qaicc(des_hatch.desP.ants_gt2d.quad$fits))
   ) %>% 
@@
   qAICc = c(
-    get_qaicc(des_Nsurv.desL.ant_treatment.quad.fits),
-    get_qaicc(des_Nsurv.desP.ant_treatment.quad.fits),
-    get_qaicc(des_Nsurv.desL.ants_gt2d.quad.fits),
-    get_qaicc(des_Nsurv.desP.ants_gt2d.quad.fits))
+    get_qaicc(des_Nsurv.desL.ant_treatment.quad$fits),
+    get_qaicc(des_Nsurv.desP.ant_treatment.quad$fits),
+    get_qaicc(des_Nsurv.desL.ants_gt2d.quad$fits),
+    get_qaicc(des_Nsurv.desP.ants_gt2d.quad$fits))
   ) %>% 
@@
 
-(qAICc_gt_tbl_hatch_quad <- tibble(
+(qAICc_gt_tbl_Esurv_quad <- tibble(
   Model = c("desert leaf + ant treatment + desert leaf*ant treatment + 
@@
   qAICc = c(
-    get_qaicc(des_Esurv.desL.ant_treatment.quad.fits),
-    get_qaicc(des_Esurv.desP.ant_treatment.quad.fits),
-    get_qaicc(des_Esurv.desL.ants_gt2d.quad.fits),
-    get_qaicc(des_Esurv.desP.ants_gt2d.quad.fits))
+    get_qaicc(des_Esurv.desL.ant_treatment.quad$fits),
+    get_qaicc(des_Esurv.desP.ant_treatment.quad$fits),
+    get_qaicc(des_Esurv.desL.ants_gt2d.quad$fits),
+    get_qaicc(des_Esurv.desP.ants_gt2d.quad$fits))
   ) %>% 
@@
 
-## Stats interpretation
+# 3 - Stats interpretation
 ```{r}
-# function to get fits and confint
-ci_for_stats <- function(data_in, model){
-
-  data <- eval(substitute(
-    data_in %>%
-      add_column(fit = predict(model, newdata = ., type = 'response'))
-    ))
-
-  ## grad the inverse link function
-  ilink <- family(model)$linkinv
-
-  ## add fit and se.fit on the **link** scale
-  data_fit_link <- eval(substitute(
-    data %>% add_column(
-  setNames(as_tibble(predict(model, data, se.fit = TRUE)[1:2]),
-           c('fit_link','se_link'))) %>%
-## create the interval and backtransform
-  mutate(fit_resp  = ilink(fit_link),
-         conf_upr = ilink(fit_link + (2 * se_link)),
-         conf_lwr = ilink(fit_link - (2 * se_link)))
-    ))
-
-  return(data_fit_link)
-}
-
-# function to get max fit, plus upper and lower ci
-get_max_fit <- function(data_in, model){
-
-  max_fit <- eval(substitute(ci_for_stats(data_in=data_in, 
-             model) %>%
-  group_by(ant_treatment) %>%
-  mutate(max = max(fit)) %>% filter(fit==max) %>% 
-    select(ant_treatment, des, max)))
-
-  max_upr <- eval(substitute(ci_for_stats(data_in=data_in, 
-             model) %>%
-  group_by(ant_treatment) %>%
-  mutate(max_upr = max(conf_upr)) %>% filter(conf_upr==max_upr) %>% 
-    select(ant_treatment, des_upr=des, max_upr)))
-
-  max_lwr <- eval(substitute(ci_for_stats(data_in=data_in, 
-             model) %>%
-  group_by(ant_treatment) %>%
-  mutate(max_lwr = max(conf_lwr)) %>% filter(conf_lwr==max_lwr) %>% 
-    select(ant_treatment, des_lwr=des, max_lwr)))
-
-  data_out <- max_fit %>% left_join(max_upr) %>% left_join(max_lwr)
-  return(data_out)
-}
-
 ## Hatch
@@
 ```
-
-# Figures for FPO
-
-## Figures
-### Both colors
-```{r}
-# hatching success
-des_hatch.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_hatched, survDen=med_t5eggs,
-                              tenure=des, treatment=ant_treatment)
-
-des_hatch.desL.ant_treatment.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=des, treatment=ant_treatment,
-              survNom=n_hatched, survDen=med_t5eggs,
-              model = des_hatch.desL.ant_treatment.quad$fits$mai.qb)
-
-des_hatch.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ant_treatment.quad.qb.ci, 
-                                  tenure=des, treatment=ant_treatment,
-             survNom = n_hatched, survDen = med_t5eggs) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Hatching success\n(nymphs/eggs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
-# nymph survivorship
-des_Nsurv.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=n_hatched,
-                              tenure=des, treatment=ant_treatment)
-
-des_Nsurv.desL.ant_treatment.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=des, treatment=ant_treatment,
-              survNom=n_survived, survDen=n_hatched,
-              model = des_Nsurv.desL.ant_treatment.quad$fits$mai.qb)
-
-des_Nsurv.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ant_treatment.quad.qb.ci, 
-                                  tenure=des, treatment=ant_treatment,
-             survNom = n_survived, survDen = n_hatched) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
-(FPO_desL.ant_treatment_allCols <- egg::ggarrange(des_hatch.desL.ant_treatment.quad.qb.p+
-                 theme(legend.position="none"),
-               des_Nsurv.desL.ant_treatment.quad.qb.p+
-                 theme(legend.position="none")))
-
-ggsave("FPO_desL.ant_treatment_allCols.png",
-       FPO_desL.ant_treatment_allCols,
-       device="png", width = 150, height = 200, units = "mm", dpi = "print")
-```
-
-### Black only
-```{r}
-# hatching success
-des_hatch.desL.ant_treatment.quad.qb.p_blackOnly <- 
-  ggplot(data = filter(des_hatch.desL.ant_treatment.quad.qb.ci,
-                       ant_treatment=="Removed"), 
-       aes(x = des, y = fit), 
-           color = "black", fill = "black") +
-    theme_publilia() +
-    geom_point(aes(y = n_hatched/med_t5eggs), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
-    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
-    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
-                    alpha = 0.5, color = NA, key_glyph=draw_key_rect) +
-      xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Hatching success\n(nymphs/eggs)")
-
-# nymph survivorship
-des_Nsurv.desL.ant_treatment.quad.qb.p_blackOnly <- 
-  ggplot(data = filter(des_Nsurv.desL.ant_treatment.quad.qb.ci,
-                       ant_treatment=="Removed"), 
-       aes(x = des, y = fit), 
-           color = "black", fill = "black") +
-    theme_publilia() +
-    geom_point(aes(y = n_survived/n_hatched), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
-    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
-    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
-                    alpha = 0.5, color = NA, key_glyph=draw_key_rect) +
-  xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Survivorship of nymphs\n(5th instars/nymphs)")
-
-(FPO_desL.ant_treatment_blackOnly <- egg::ggarrange(des_hatch.desL.ant_treatment.quad.qb.p_blackOnly+
-                 theme(legend.position="none"),
-               des_Nsurv.desL.ant_treatment.quad.qb.p_blackOnly+
-                 theme(legend.position="none")))
-
-ggsave("FPO_desL.ant_treatment_blackOnly.png",
-       FPO_desL.ant_treatment_blackOnly,
-       device="png", width = 150, height = 200, units = "mm", dpi = "print")
-```
-
-hatching success
-```{r}
-# hatching success
-des_hatch.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_hatched, survDen=med_t5eggs,
-                              tenure=des, treatment=ants_gt2d)
-
-des_hatch.desL.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=des, treatment=ants_gt2d,
-              survNom=n_hatched, survDen=med_t5eggs,
-              model = des_hatch.desL.ants_gt2d.quad$fits$mai.qb)
-
-des_hatch.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ants_gt2d.quad.qb.ci, 
-                                  tenure=des, treatment=ants_gt2d,
-             survNom = n_hatched, survDen = med_t5eggs) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Hatching success\n(nymphs/eggs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
-plot_ci(ci_data=filter(des_hatch.desL.ants_gt2d.quad.qb.ci, 
-                       ants_gt2d ), 
-                                  tenure=des, treatment=ants_gt2d,
-             survNom = n_hatched, survDen = med_t5eggs) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Hatching success\n(nymphs/eggs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-
-```
-
-nymph survivorship
-```{r}
-# nymph survivorship
-des_Nsurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
-                              survNom=n_survived, survDen=n_hatched,
-                              tenure=des, treatment=ants_gt2d)
-
-des_Nsurv.desL.ants_gt2d.quad.qb.ci <- 
-  ci_for_plot(data_in=surv_reg_data, 
-              tenure=des, treatment=ants_gt2d,
-              survNom=n_survived, survDen=n_hatched,
-              model = des_Nsurv.desL.ants_gt2d.quad$fits$mai.qb)
-
-des_Nsurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ants_gt2d.quad.qb.ci, 
-                                  tenure=des, treatment=ants_gt2d,
-             survNom = n_survived, survDen = n_hatched) +
-    xlab("Latest desertion date from leaf\nrelative to hatch") +
-    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
-```

### 2023-08-12 R/custom_functions.R

@@ -1,0 +1,227 @@
+## Plotting theme
+theme_publilia <- function(){
+  theme_bw() +
+    theme(text = element_text(family = "Arial"),
+          axis.text = element_text(size = 12), 
+          axis.title = element_text(size = 14),
+          axis.line.x = element_line(color="black"), 
+          axis.line.y = element_line(color="black"),
+          panel.border = element_blank(),
+          panel.grid.major.x = element_blank(),                                          
+          panel.grid.minor.x = element_blank(),
+          panel.grid.minor.y = element_blank(),
+          panel.grid.major.y = element_blank(),  
+          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
+          plot.title = element_text(size = 18, vjust = 1, hjust = 0.5, face = "bold"),
+          legend.text = element_text(size = 10),          
+          legend.title = element_blank(),                              
+          # legend.position = c(0.90, 0.90), 
+          legend.key = element_blank(),
+          legend.background = element_rect(color = "black", 
+                                           fill = "transparent", 
+                                           size = 2, linetype = "blank"))
+}
+
+
+
+## Publilia-03-survivorship: regression functions
+
+### fit survivorship model
+fit_surv <- function(data_in, survNom, survDen, tenure, treatment, quad){
+  data <- data_in %>% filter(!is.na(.data[[tenure]]))
+  
+  if (!quad) {
+    formula.mai <- paste0(survNom,"/",survDen,"~",tenure,"*",treatment) %>% as.formula()
+    formula.ma <- paste0(survNom,"/",survDen,"~",tenure,"+",treatment) %>% as.formula()
+  } else if (quad) {
+    formula.mai <- paste0(
+      survNom,"/",survDen,"~",
+      tenure,"*",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
+    ) %>% as.formula()
+    formula.ma <- paste0(
+      survNom,"/",survDen,"~",
+      tenure,"+",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
+    ) %>% as.formula()
+  }
+  
+  mai.b <- glm(formula = formula.mai, data = data, weights = data[[survDen]], family = binomial)
[…]

### 2023-08-12 scripts/Publilia-03-survivorship.Rmd
fixed prelim fig saving paths for publilia-03

@@
 
-ggsave("desL.ant_treatment.quad.final.png",
+ggsave(here("prelim_figs/Publilia-03-survivorship/",
+            "desL.ant_treatment.quad.final.png"),
        desL.ant_treatment.quad.p,
@@
   as_flex_table() %>%
-  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desL.ant_treatment.docx")
+  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
+                                    "surv_reg_data.tbl_summary.desL.ant_treatment.docx"))
 ```
@@
   as_flex_table() %>%
-  flextable::save_as_docx(path="surv.reg_summary.desL.ants_treatment.quad.docx")
+  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
+                                    "surv.reg_summary.desL.ants_treatment.quad.docx"))
 ```
@@
 
-ggsave("desL.ants_gt2d.quad.final.png",
+ggsave(here("prelim_figs/Publilia-03-survivorship/",
+            "desL.ants_gt2d.quad.final.png"),
        desL.ants_gt2d.quad.p,
@@
   as_flex_table() %>%
-  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desL.ants_gt2d.docx")
+  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
+                                    "surv_reg_data.tbl_summary.desL.ants_gt2d.docx"))
 ```
@@
   as_flex_table() %>%
-  flextable::save_as_docx(path="surv.reg_summary.desL.ants_gt2d.quad.docx")
+  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
+                                    "surv.reg_summary.desL.ants_gt2d.quad.docx"))
 ```
@@
 
-ggsave("desP.ants_gt2d.quad.final.png",
+ggsave(here("prelim_figs/Publilia-03-survivorship/",
+            "desP.ants_gt2d.quad.final.png"),
        desP.ants_gt2d.quad.p,
@@
   as_flex_table() %>%
-  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desP.ants_gt2d.docx")
+  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
+                                    "surv_reg_data.tbl_summary.desP.ants_gt2d.docx"))
 ```
@@
   as_flex_table() %>%
-  flextable::save_as_docx(path="surv.reg_summary.desP.ants_gt2d.quad.docx")
+  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
+                                    "surv.reg_summary.desP.ants_gt2d.quad.docx"))
 ```
@@
 
-ggsave("desP.ant_treatment.quad.final.png",
+ggsave(here("prelim_figs/Publilia-03-survivorship/",
+            "desP.ant_treatment.quad.final.png"),
        desP.ant_treatment.quad.p,
@@
   as_flex_table() %>%
-  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desP.ant_treatment.docx")
+  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
+                                    "surv_reg_data.tbl_summary.desP.ant_treatment.docx"))
 ```
@@
   as_flex_table() %>%
-  flextable::save_as_docx(path="surv.reg_summary.desP.ant_treatment.quad.docx")
+  flextable::save_as_docx(path=here("prelim_figs/Publilia-03-survivorship/",
+                                    "surv.reg_summary.desP.ant_treatment.quad.docx"))
 ```

### 2023-08-23 scripts/Publilia-01-qc.Rmd
update manual check csv writing to use `here()` and new dir structure. Resolves https://github.com/micahpf/PubliliaFitness/issues/4#issue-1864036908

@@
   select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_text_conflict, N2_text_conflict, N5_text_conflict)
-# write_csv(egg_text_conflict_data, "egg_text_conflict_data.csv")
+# write_csv(egg_text_conflict_data, here("data/manual_check/egg_text_conflict_data.csv"))
 
@@
   select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_status_missing, N2_status_missing, N5_status_missing)
-# write_csv(egg_status_missing_data, "egg_status_missing_data.csv")
+# write_csv(egg_status_missing_data, here("data/manual_check/egg_status_missing_data.csv")
 
@@
   distinct(location)
-# write_csv(check_hatch_date, "check_hatch_date_tmp.csv")
+# write_csv(check_hatch_date, here("data/manual_check/check_hatch_date_tmp.csv")
 ```
@@
 
-# write_csv(ant_text_conflict, "ant_text_conflict.csv") # resolved 2019-10-08
+# write_csv(ant_text_conflict, here("data/manual_check/ant_text_conflict.csv") # resolved 2019-10-08
 ```
@@
 
-# write_csv(short_unhatched_days_check, "short_unhatched_days_check_tmp.csv")
+# write_csv(short_unhatched_days_check, here("data/manual_check/short_unhatched_days_check_tmp.csv")
 
@@
 
-# write_csv(never_hatched_check, "never_hatched_check_tmp.csv")
-
-# write_csv(clutch_status_stats_v1, "egg_measures_check_tmp.csv")
+# write_csv(never_hatched_check, here("data/manual_check/never_hatched_check_tmp.csv")
+
+# write_csv(clutch_status_stats_v1, here("data/manual_check/egg_measures_check_tmp.csv")
 ```
@@
 
-# write_csv(NOr_manual_check_table %>% filter(revise_NOr == "MANUAL CHECK"), "NOr_manual_check_tmp.csv")
+# write_csv(NOr_manual_check_table %>% filter(revise_NOr == "MANUAL CHECK"), here("data/manual_check/NOr_manual_check_tmp.csv")
 

### 2023-08-23 manuscript/Manuscript_runfile.Rmd
Consolidated construction of `strats_data` for `Publilia-02-strats.Rmd` and moved that code to `Publilia-02-qc.Rmd`. Resolves https://github.com/micahpf/PubliliaFitness/issues/3#issuecomment-1676152818

@@
 
+```{=html}
+<style type="text/css">
+  .book .book-body .page-inner {
+    max-width: 1600px;
+    margin-left: auto;
+    margin-right: auto;
+  }
+details > summary {
+  display: list-item;
+}
+</style>
+```
+
+```{r, include=FALSE}
+knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
+                      fig.width = 8, fig.height = 6)
+
+library(kableExtra)   ## Needed if rendering tables
+```
+
 # 0 - Data import
+
+```{r}
+library(here)
+library(tidyverse)
+library(readxl)
+library(lubridate)
+library(stringr)
+
+theme_set(theme_bw())
+```
 
@@
 All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))
-clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
-last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))
-
-strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
+strats_data <- read_rds(here("saved_rds/strats_data.rds"))
 ```
@@
 ```{r}
-strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
-
 strats_data_with_filters <- strats_data %>%
-  # Add whether female was visited within first 4 days of initiating
-  group_by(location) %>%
-    mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
-  ungroup() %>%
-  # Add some additional metrics for human readability
-  mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
-                                      "Visited", "Not visited"),
-         ants = ifelse(ants_removed, "Ants removed", "Control"),
-         est_hatch = as_date(ifelse(is.na(hatch_date),
-                                 initiation_date + 20,
-                                 hatch_date)),
-         est_rel2h = visit_ends-est_hatch) %>%
-  # Add day of first visit bins
-  left_join(first_visit_cuts) %>%
-  mutate(vis_cat = ifelse(num_at_init > 1,
-                          "0",
-                          ifelse(is.na(first_visit_starts),
-                                 "never visited",
-                                 ifelse(first_visit_cut=="(0,4]", "1 to 4", "5+"))),
-         vis_cat = factor(vis_cat, levels = c("0","1 to 4",
-                                              "5+","never visited"))) %>%
   # Remove one female who has dubious data (See note ** below)
@@
 ```{r}
-visited_1st_4d_data_tb %>%
+strats_data_with_filters %>%
   filter(!females_removed,
@@
             med_gd = median(as.numeric(guard_duration, "days"), na.rm=T))
+
+# visited_1st_4d_data_tb %>%
+#   filter(!females_removed,
+#          !mom_at_init,
+#          visit_ends < last_day_fID) %>%
+#   summarize(n = n(),
+#             n_NA = sum(is.na(guard_duration)),
+#             mean_gd = mean(as.numeric(guard_duration, "days"), na.rm=T),
+#             med_gd = median(as.numeric(guard_duration, "days"), na.rm=T))
 ```

### 2023-08-23 scripts/Publilia-02-strats.Rmd
init `Manuscript_runfile.Rmd` to collect all code to stats, sample sizes, figures, tables for the manuscript in a minimal reproducible script
Consolidated construction of `strats_data` for `Publilia-02-strats.Rmd` and moved that code to `Publilia-02-qc.Rmd`. Resolves https://github.com/micahpf/PubliliaFitness/issues/3#issuecomment-1676152818

@@
 All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))
-clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
-last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))
-
-strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
+# clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
+# last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))
+
+strats_data <- read_rds(here("saved_rds/strats_data.rds"))
 ```
@@
 ```{r}
-visited_1st_4d_data <- strats_data %>%
-  group_by(location) %>%
-    mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
-  ungroup() %>%
-  mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
-                                      "Visited", "Not visited"),
-         ants = ifelse(ants_removed, "Ants removed", "Control"),
-         est_hatch = as_date(ifelse(is.na(hatch_date),
-                                 initiation_date + 20,
-                                 hatch_date)),
-         est_rel2h = visit_ends-est_hatch)
+## Moved to Publilia-01-qc.Rmd
+# visited_1st_4d_data <- strats_data %>%
+#   group_by(location) %>%
+#     mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
+#   ungroup() %>%
+#   mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
+#                                       "Visited", "Not visited"),
+#          ants = ifelse(ants_removed, "Ants removed", "Control"),
+#          est_hatch = as_date(ifelse(is.na(hatch_date),
+#                                  initiation_date + 20,
+#                                  hatch_date)),
+#          est_rel2h = visit_ends-est_hatch)
 
@@
 ```{r}
-visited_1st_4d_data_tb <- visited_1st_4d_data %>%
-  # 1) Longest initiator
-  mutate(initL = init_first_dur_rank == 1) %>% 
-  # 2) Shortest initiator
-  #  i) break ties by picking marked females over unmarked
-  group_by(location, init_first_dur_shortest) %>% 
-    mutate(initS_tmp = ifelse(n()>1, !grepl("Uf", Female_ID), TRUE)) %>% 
-  ungroup() %>%
-  #  ii) finally picking at random (only one case, identical predictor vars)
-  group_by(location, init_first_dur_shortest, initS_tmp) %>%
-    mutate(initS = init_first_dur_shortest & initS_tmp & row_number()==1) %>%
-  ungroup()
+## Moved to Publilia-01-qc.Rmd
+# visited_1st_4d_data_tb <- visited_1st_4d_data %>%
+#   # 1) Longest initiator
+#   mutate(initL = init_first_dur_rank == 1) %>% 
+#   # 2) Shortest initiator
+#   #  i) break ties by picking marked females over unmarked
+#   group_by(location, init_first_dur_shortest) %>% 
+#     mutate(initS_tmp = ifelse(n()>1, !grepl("Uf", Female_ID), TRUE)) %>% 
+#   ungroup() %>%
+#   #  ii) finally picking at random (only one case, identical predictor vars)
+#   group_by(location, init_first_dur_shortest, initS_tmp) %>%
+#     mutate(initS = init_first_dur_shortest & initS_tmp & row_number()==1) %>%
+#   ungroup()
 ```
@@
 ```{r}
-ant_counts <- All_data_v6 %>%
-  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-  filter(!is.na(initiation_date)) %>%
-  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-  group_by(location) %>%
-    mutate(b4h=Date>=initiation_date&Date<est_hatch,
-           afh=Date>=est_hatch) %>%
-    summarize(ants_removed=first(ants_removed),
-              females_removed=first(females_removed),
-              n_antsP=sum(ants_P,na.rm=T),
-              ever_antsP=n_antsP>0,
-              mean_antsP=mean(ants_P,na.rm=T),
-              med_antsP=median(ants_P,na.rm=T),
-
-              n_antsP_b4h=sum(ants_P&b4h),
-              ever_antsP_b4h=n_antsP_b4h>0,
-              mean_antsP_b4h=mean(ifelse(b4h,ants_P,NA),na.rm=T),
-              med_antsP_b4h=median(ifelse(b4h,ants_P,NA),na.rm=T),
-
-              n_antsP_afh=sum(ants_P&afh),
-              ever_antsP_afh=n_antsP_afh>0,
-              mean_antsP_afh=mean(ifelse(afh,ants_P,NA),na.rm=T),
-              med_antsP_afh=median(ifelse(afh,ants_P,NA),na.rm=T)) %>%
-  ungroup() %>%
-  mutate(Dorm=substr(location,1,1),
-         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
+## Moved to Publilia-01-qc.Rmd
+# ant_counts <- All_data_v6 %>%
+#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+#   filter(!is.na(initiation_date)) %>%
+#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+#   group_by(location) %>%
+#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
+#            afh=Date>=est_hatch) %>%
+#     summarize(ants_removed=first(ants_removed),
+#               females_removed=first(females_removed),
+#               n_antsP=sum(ants_P,na.rm=T),
+#               ever_antsP=n_antsP>0,
+#               mean_antsP=mean(ants_P,na.rm=T),
+#               med_antsP=median(ants_P,na.rm=T),
+#               
+#               n_antsP_b4h=sum(ants_P&b4h),
+#               ever_antsP_b4h=n_antsP_b4h>0,
+#               mean_antsP_b4h=mean(ifelse(b4h,ants_P,NA),na.rm=T),
+#               med_antsP_b4h=median(ifelse(b4h,ants_P,NA),na.rm=T),
+#               
+#               n_antsP_afh=sum(ants_P&afh),
+#               ever_antsP_afh=n_antsP_afh>0,
+#               mean_antsP_afh=mean(ifelse(afh,ants_P,NA),na.rm=T),
+#               med_antsP_afh=median(ifelse(afh,ants_P,NA),na.rm=T)) %>%
+#   ungroup() %>%
+#   mutate(Dorm=substr(location,1,1),
+#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
 
@@
 ```{r}
-antP_arrival_afh_data <- All_data_v6 %>%
-  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-  filter(!is.na(initiation_date)) %>%
-  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-  group_by(location) %>%
-    mutate(b4h=Date>=initiation_date&Date<est_hatch,
-           afh=Date>=est_hatch,
-           is_antsP_afh=ants_P&afh) %>%
-    filter(is_antsP_afh) %>%
-    slice_head(n=1) %>% 
-  mutate(antP_arrival_afh=Date-est_hatch) %>%
-  select(location, antP_arrival_afh, ants_removed, females_removed,
-         initiation_date, est_hatch) %>%
-  ungroup() %>%
-  mutate(Dorm=substr(location,1,1),
-         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
-
-antP_last_b4h_data <- All_data_v6 %>%
-  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-  filter(!is.na(initiation_date)) %>%
-  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-  group_by(location) %>%
-    mutate(b4h=Date>=initiation_date&Date<est_hatch,
-           afh=Date>=est_hatch,
-           is_antsP_bfh=ants_P&b4h) %>%
-    filter(is_antsP_bfh) %>%
-    slice_tail(n=1) %>% 
-  mutate(antP_last_b4h=Date-est_hatch) %>%
-  select(location, antP_last_b4h, ants_removed, females_removed,
-         initiation_date, est_hatch) %>%
-  ungroup() %>%
-  mutate(Dorm=substr(location,1,1),
-         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
-
-antL_arrival_afh_data <- All_data_v6 %>%
-  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-  filter(!is.na(initiation_date)) %>%
-  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-  group_by(location) %>%
-    mutate(b4h=Date>=initiation_date&Date<est_hatch,
-           afh=Date>=est_hatch,
-           is_antsL_afh=ants_L&afh) %>%
-    filter(is_antsL_afh) %>%
-    slice_head(n=1) %>% 
-  mutate(antL_arrival_afh=Date-est_hatch) %>%
-  select(location, antL_arrival_afh, ants_removed, females_removed,
-         initiation_date, est_hatch) %>%
-  ungroup() %>%
-  mutate(Dorm=substr(location,1,1),
-         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
-
-antL_last_b4h_data <- All_data_v6 %>%
-  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-  filter(!is.na(initiation_date)) %>%
-  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-  group_by(location) %>%
-    mutate(b4h=Date>=initiation_date&Date<est_hatch,
-           afh=Date>=est_hatch,
-           is_antsL_bfh=ants_L&b4h) %>%
-    filter(is_antsL_bfh) %>%
-    slice_tail(n=1) %>% 
-  mutate(antL_last_b4h=Date-est_hatch) %>%
-  select(location, antL_last_b4h, ants_removed, females_removed,
-         initiation_date, est_hatch) %>%
-  ungroup() %>%
-  mutate(Dorm=substr(location,1,1),
-         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
-
-ant_data <- ant_counts %>%
-  left_join(antP_last_b4h_data) %>%
-  left_join(antP_arrival_afh_data) %>%
-  left_join(antL_last_b4h_data) %>%
-  left_join(antL_arrival_afh_data)
-
-visited_1st_4d_data_ants <- visited_1st_4d_data %>%
-  left_join(ant_data)
-
-visited_1st_4d_data_ants %>%
+## Moved to Publilia-01-qc.Rmd
+# antP_arrival_afh_data <- All_data_v6 %>%
+#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+#   filter(!is.na(initiation_date)) %>%
+#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+#   group_by(location) %>%
+#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
+#            afh=Date>=est_hatch,
+#            is_antsP_afh=ants_P&afh) %>%
+#     filter(is_antsP_afh) %>%
+#     slice_head(n=1) %>% 
+#   mutate(antP_arrival_afh=Date-est_hatch) %>%
+#   select(location, antP_arrival_afh, ants_removed, females_removed,
+#          initiation_date, est_hatch) %>%
+#   ungroup() %>%
+#   mutate(Dorm=substr(location,1,1),
+#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
+# 
+# antP_last_b4h_data <- All_data_v6 %>%
+#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+#   filter(!is.na(initiation_date)) %>%
+#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+#   group_by(location) %>%
+#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
+#            afh=Date>=est_hatch,
+#            is_antsP_bfh=ants_P&b4h) %>%
+#     filter(is_antsP_bfh) %>%
+#     slice_tail(n=1) %>% 
+#   mutate(antP_last_b4h=Date-est_hatch) %>%
+#   select(location, antP_last_b4h, ants_removed, females_removed,
+#          initiation_date, est_hatch) %>%
+#   ungroup() %>%
+#   mutate(Dorm=substr(location,1,1),
+#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
+# 
+# antL_arrival_afh_data <- All_data_v6 %>%
+#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+#   filter(!is.na(initiation_date)) %>%
+#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+#   group_by(location) %>%
+#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
+#            afh=Date>=est_hatch,
+#            is_antsL_afh=ants_L&afh) %>%
+#     filter(is_antsL_afh) %>%
+#     slice_head(n=1) %>% 
+#   mutate(antL_arrival_afh=Date-est_hatch) %>%
+#   select(location, antL_arrival_afh, ants_removed, females_removed,
+#          initiation_date, est_hatch) %>%
+#   ungroup() %>%
+#   mutate(Dorm=substr(location,1,1),
+#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
+# 
+# antL_last_b4h_data <- All_data_v6 %>%
+#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+#   filter(!is.na(initiation_date)) %>%
+#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+#   group_by(location) %>%
+#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
+#            afh=Date>=est_hatch,
+#            is_antsL_bfh=ants_L&b4h) %>%
+#     filter(is_antsL_bfh) %>%
+#     slice_tail(n=1) %>% 
+#   mutate(antL_last_b4h=Date-est_hatch) %>%
+#   select(location, antL_last_b4h, ants_removed, females_removed,
+#          initiation_date, est_hatch) %>%
+#   ungroup() %>%
+#   mutate(Dorm=substr(location,1,1),
+#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
+# 
+# ant_data <- ant_counts %>%
+#   left_join(antP_last_b4h_data) %>%
+#   left_join(antP_arrival_afh_data) %>%
+#   left_join(antL_last_b4h_data) %>%
+#   left_join(antL_arrival_afh_data)
+# 
+# visited_1st_4d_data_ants <- visited_1st_4d_data %>%
+#   left_join(ant_data)
+
+strats_data %>%
   filter(ever_antsP) %>%
@@
 
-visited_1st_4d_data_ants %>%
+strats_data %>%
   filter(ever_antsP) %>%
@@
 
-visited_1st_4d_data_ants %>%
+strats_data %>%
   filter(ants=="Control") %>%
@@
 
-visited_1st_4d_data_ants %>%
+strats_data %>%
   filter(ants=="Control", !females_removed) %>%
@@
 # ever ants b4h
-ggplot(data = filter(visited_1st_4d_data_ants, 
+ggplot(data = filter(strats_data, 
                                  `visited in 4 days` == "Not visited",
@@
 # ever ants afh
-ggplot(data = filter(visited_1st_4d_data_ants, 
+ggplot(data = filter(strats_data, 
                                  `visited in 4 days` == "Not visited",
@@
 # ever ants b4h
-ggplot(data = filter(visited_1st_4d_data_ants,
+ggplot(data = filter(strats_data,
                      `visited in 4 days` == "Visited",
@@
 # ever ants afh
-ggplot(data = filter(visited_1st_4d_data_ants,
+ggplot(data = filter(strats_data,
                      `visited in 4 days` == "Visited",
@@
 # Samples sizes for "not visited" are the same across longests and shortests
-filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
+filter(strats_data, `visited in 4 days` == "Not visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
+filter(strats_data, `visited in 4 days` == "Not visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 # Shortests have more females than longests for some reason??
-filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
+filter(strats_data, `visited in 4 days` == "Visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
+filter(strats_data, `visited in 4 days` == "Visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1) %>% nrow() # 34
-visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1) %>% nrow() # 36
-
-visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1,
+strats_data %>% filter(initL, mom_at_init, num_at_init>1) %>% nrow() # 34
+strats_data %>% filter(initS, mom_at_init, num_at_init>1) %>% nrow() # 36
+
+strats_data %>% filter(initL, mom_at_init, num_at_init>1,
                                   !grepl("U", Female_ID), !females_removed) %>% nrow() # 13
 
-visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1,
+strats_data %>% filter(initS, mom_at_init, num_at_init>1,
                                   !grepl("U", Female_ID), !females_removed) %>% nrow() # 12
 
-visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1,
+strats_data %>% filter(initL, mom_at_init, num_at_init>1,
                                   !grepl("U", Female_ID), !females_removed,
@@
 
-visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1,
+strats_data %>% filter(initS, mom_at_init, num_at_init>1,
                                   !grepl("U", Female_ID), !females_removed,
@@
 
-visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1,
+strats_data %>% filter(initL, mom_at_init, num_at_init>1,
                                   !grepl("U", Female_ID), !females_removed,
@@
 ```{r}
-Fig1_v2A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
+Fig1_v2A <- ggplot(data = filter(strats_data, `visited in 4 days` == "Not visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-Fig1_v2B <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
+Fig1_v2B <- ggplot(data = filter(strats_data, `visited in 4 days` == "Visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 ```{r}
-Fig1_v3A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
+Fig1_v3A <- ggplot(data = filter(strats_data, `visited in 4 days` == "Not visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-Fig1_v3B <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
+Fig1_v3B <- ggplot(data = filter(strats_data, `visited in 4 days` == "Visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 ```{r}
-Fig1_v4A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
+Fig1_v4A <- ggplot(data = filter(strats_data, `visited in 4 days` == "Not visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-Fig1_v4B <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
+Fig1_v4B <- ggplot(data = filter(strats_data, `visited in 4 days` == "Visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-visit_cuts_data_ExDis <- visited_1st_4d_data_tb %>%
+visit_cuts_data_ExDis <- strats_data %>%
   left_join(first_visit_cuts) %>%
@@
 ### no tb
-visitors_ExDis_notb <- visited_1st_4d_data_tb %>%
+visitors_ExDis_notb <- strats_data %>%
   semi_join(visit_cuts_data_ExDis, by=c("location")) %>%
@@
 ```{r}
-first_visit_cuts <- visited_1st_4d_data_tb %>%
+first_visit_cuts <- strats_data %>%
   filter(!mom_at_init, visit_starts > initiation_date) %>%
@@
 
-visit_cuts_data <- visited_1st_4d_data_tb %>%
+visit_cuts_data <- strats_data %>%
   left_join(first_visit_cuts) %>%
@@
 
-visited_1st_4d_data_tb %>% filter(initL, mom_at_init, num_at_init>1)
-visited_1st_4d_data_tb %>% filter(initS, mom_at_init, num_at_init>1)
+strats_data %>% filter(initL, mom_at_init, num_at_init>1)
+strats_data %>% filter(initS, mom_at_init, num_at_init>1)
 
@@
 ### no tb
-visitors_InDis_notb <- visited_1st_4d_data_tb %>%
+visitors_InDis_notb <- strats_data %>%
   semi_join(filter(visit_cuts_data, initL), by=c("location")) %>%
@@
 ### initL
-visitors_InDis_initL <- visited_1st_4d_data_tb %>%
+visitors_InDis_initL <- strats_data %>%
   semi_join(filter(visit_cuts_data, initL), by=c("location")) %>%
@@
 ### initS
-visitors_InDis_initS <- visited_1st_4d_data_tb %>%
+visitors_InDis_initS <- strats_data %>%
   semi_join(filter(visit_cuts_data, initS), by=c("location")) %>%
@@
 ```{r}
-Fig1_v5A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
+Fig1_v5A <- ggplot(data = filter(strats_data, `visited in 4 days` == "Not visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-Fig1_v5B <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
+Fig1_v5B <- ggplot(data = filter(strats_data, `visited in 4 days` == "Visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-visitors_ExDis_initL <- visited_1st_4d_data_tb %>%
+visitors_ExDis_initL <- strats_data %>%
   semi_join(filter(visit_cuts_data_ExDis, initL), by=c("location")) %>%
@@
 # control
-visited_1st_4d_data_tb %>%
+strats_data %>%
   filter(!females_removed, !ants_removed,
@@
 
-visited_1st_4d_data_tb %>%
+strats_data %>%
   filter(!females_removed, !ants_removed,
@@
 # ant removal
-visited_1st_4d_data_tb %>%
+strats_data %>%
   filter(!females_removed, ants_removed,
@@
 
-visited_1st_4d_data_tb %>%
+strats_data %>%
   filter(!females_removed, ants_removed,
@@
 ```{r}
-wilcox_data <- visited_1st_4d_data_tb %>%
+wilcox_data <- strats_data %>%
   filter(!females_removed,
@@
 ```{r}
-visited_1st_4d_data_tb %>%
+strats_data %>%
   filter(!females_removed,
@@
 
-visited_1st_4d_data_tb %>%
+strats_data %>%
   filter(!females_removed,
@@
 
-visited_1st_4d_data_tb %>%
+strats_data %>%
   filter(females_removed,
@@
 
-visited_1st_4d_data_tb %>%
+strats_data %>%
   filter(clutch_visited_order == 1) %>%
@@
 ```{r}
-Fig1sup_v2A <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Not visited",
+Fig1sup_v2A <- ggplot(data = filter(strats_data, `visited in 4 days` == "Not visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-Fig1sup_v2B <- ggplot(data = filter(visited_1st_4d_data_tb, `visited in 4 days` == "Visited",
+Fig1sup_v2B <- ggplot(data = filter(strats_data, `visited in 4 days` == "Visited",
                                  !grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 ggplot(data = 
-         filter(visited_1st_4d_data_tb, !grepl("U", Female_ID), !females_removed, 
+         filter(strats_data, !grepl("U", Female_ID), !females_removed, 
                 mom_at_init,
@@
 FPO_freqpoly_all <- ggplot(data = 
-         filter(visited_1st_4d_data_tb, !grepl("U", Female_ID), !females_removed, 
+         filter(strats_data, !grepl("U", Female_ID), !females_removed, 
                 mom_at_init,
@@
 FPO_freqpoly_noVis_all <- ggplot(data = 
-         filter(visited_1st_4d_data_tb, !grepl("U", Female_ID), !females_removed, 
+         filter(strats_data, !grepl("U", Female_ID), !females_removed, 
                 mom_at_init,
@@
 FPO_freqpoly_noVis_black <- ggplot(data = 
-         filter(visited_1st_4d_data_tb, !grepl("U", Female_ID), !females_removed, 
+         filter(strats_data, !grepl("U", Female_ID), !females_removed, 
                 mom_at_init,
@@
 ggplot(data = 
-         filter(visited_1st_4d_data_tb, 
+         filter(strats_data, 
                 `visited in 4 days` == "Not visited",
@@
 ```{r, fig.width=6, fig.height=2}
-# ** There was one female (E_Gkgg) which was on the eggs before and after but not ON the initiation date.
-         # I suspect I missed her in the field or she may have left and come back. In any case she was never visited
-         # and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
+library(ggupset)
 

### 2023-08-24 scripts/Publilia-01-qc.Rmd

@@
 
-# 6 - Write data for `Publilia-02-strats.Rmd` to `.rds` for further analysis in clean environment
-
-## `Publilia-02-strats.Rmd`
-```{r}
-write_rds(All_data_v6, here("saved_rds/All_data_v6.rds"))
-write_rds(clutch_status_guarding_summary_v2, here("saved_rds/clutch_status_guarding_summary_v2.rds"))
-write_rds(last_day_fID, here("saved_rds/last_day_fID.rds"))
-```
-
 ***
@@
 ```{r}
-strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
-
-visited_1st_4d_data <- strats_data %>%
+visited_1st_4d_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID) %>%
   group_by(location) %>%
@@
 
-# 9.2 - Threshold for number of days ants were on the plant
+## 9.2 - Threshold for number of days ants were on the plant
 Should I be more lenient with my threshold, so I can have more even sample sizes between "ants" and "no ants"?
@@
   count(females_removed, antsP_gt3d)
+```
+
+## 9.3 - Ant arrival times
+
+```{r}
+antP_arrival_afh_data <- All_data_v6 %>%
+  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+  filter(!is.na(initiation_date)) %>%
+  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+  group_by(location) %>%
+    mutate(b4h=Date>=initiation_date&Date<est_hatch,
+           afh=Date>=est_hatch,
+           is_antsP_afh=ants_P&afh) %>%
+    filter(is_antsP_afh) %>%
+    slice_head(n=1) %>% 
+  mutate(antP_arrival_afh=Date-est_hatch) %>%
+  select(location, antP_arrival_afh, ants_removed, females_removed,
+         initiation_date, est_hatch) %>%
+  ungroup() %>%
+  mutate(Dorm=substr(location,1,1),
+         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
+
+antP_last_b4h_data <- All_data_v6 %>%
+  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+  filter(!is.na(initiation_date)) %>%
+  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+  group_by(location) %>%
+    mutate(b4h=Date>=initiation_date&Date<est_hatch,
+           afh=Date>=est_hatch,
+           is_antsP_bfh=ants_P&b4h) %>%
+    filter(is_antsP_bfh) %>%
+    slice_tail(n=1) %>% 
+  mutate(antP_last_b4h=Date-est_hatch) %>%
+  select(location, antP_last_b4h, ants_removed, females_removed,
+         initiation_date, est_hatch) %>%
+  ungroup() %>%
+  mutate(Dorm=substr(location,1,1),
+         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
+
+antL_arrival_afh_data <- All_data_v6 %>%
+  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+  filter(!is.na(initiation_date)) %>%
+  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+  group_by(location) %>%
+    mutate(b4h=Date>=initiation_date&Date<est_hatch,
+           afh=Date>=est_hatch,
+           is_antsL_afh=ants_L&afh) %>%
+    filter(is_antsL_afh) %>%
+    slice_head(n=1) %>% 
+  mutate(antL_arrival_afh=Date-est_hatch) %>%
+  select(location, antL_arrival_afh, ants_removed, females_removed,
+         initiation_date, est_hatch) %>%
+  ungroup() %>%
+  mutate(Dorm=substr(location,1,1),
+         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
+
+antL_last_b4h_data <- All_data_v6 %>%
+  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
+  filter(!is.na(initiation_date)) %>%
+  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
+  group_by(location) %>%
+    mutate(b4h=Date>=initiation_date&Date<est_hatch,
+           afh=Date>=est_hatch,
+           is_antsL_bfh=ants_L&b4h) %>%
+    filter(is_antsL_bfh) %>%
+    slice_tail(n=1) %>% 
+  mutate(antL_last_b4h=Date-est_hatch) %>%
+  select(location, antL_last_b4h, ants_removed, females_removed,
+         initiation_date, est_hatch) %>%
+  ungroup() %>%
+  mutate(Dorm=substr(location,1,1),
+         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
+
+ant_data <- ant_counts %>%
+  left_join(antP_last_b4h_data) %>%
+  left_join(antP_arrival_afh_data) %>%
+  left_join(antL_last_b4h_data) %>%
+  left_join(antL_arrival_afh_data)
 ```
@@
 
+# 6 - Write data for `Publilia-02-strats.Rmd` to `.rds` for further analysis in clean environment
+
+## `Publilia-02-strats.Rmd`
+```{r}
+strats_data <- visited_1st_4d_data_tb  %>%
+  # Add ant arrival data
+  left_join(ant_data) %>%
+  # Add day of first visit bins
+  left_join(first_visit_cuts) %>%
+  mutate(vis_cat = ifelse(num_at_init > 1,
+                          "0",
+                          ifelse(is.na(first_visit_starts),
+                                 "never visited",
+                                 ifelse(first_visit_cut=="(0,4]", "1 to 4", "5+"))),
+         vis_cat = factor(vis_cat, levels = c("0","1 to 4",
+                                              "5+","never visited"))) %>%
+  # Accommodate different tie-breaking procedures (wrt choosing a single female as initiator if multiple present at hatch)
+  # 1) Longest initiator
+  mutate(initL = init_first_dur_rank == 1) %>% 
+  # 2) Shortest initiator
+  #  i) break ties by picking marked females over unmarked
+  group_by(location, init_first_dur_shortest) %>% 
+    mutate(initS_tmp = ifelse(n()>1, !grepl("Uf", Female_ID), TRUE)) %>% 
+  ungroup() %>%
+  #  ii) finally picking at random (only one case, identical predictor vars)
+  group_by(location, init_first_dur_shortest, initS_tmp) %>%
+    mutate(initS = init_first_dur_shortest & initS_tmp & row_number()==1) %>%
+  ungroup()
+
+```
+
+## `Publilia-02-strats.Rmd`
+```{r}
+write_rds(All_data_v6, here("saved_rds/All_data_v6.rds"))
+# write_rds(clutch_status_guarding_summary_v2, here("saved_rds/clutch_status_guarding_summary_v2.rds"))
+# write_rds(last_day_fID, here("saved_rds/last_day_fID.rds"))
+write_rds(strats_data, here("saved_rds/strats_data.rds"))
+```
+
 # 12 - Write data for `Publilia-03-survivorship.Rmd` to `.rds` for further analysis in clean environment

### 2023-08-24 scripts/old/Publilia_2019_CHAPTER-0-prep.Rmd
added old scripts to `scripts/old/` for reference

--- 2023-08-11 scripts/Publilia-01-qc.Rmd
@@
 ---
-title: '01 - TreehopperFitness: Quality control'
-author: "Micah Fletcher"
-date: '`r Sys.Date()`'
-output: 
-  rmdformats::robobook:
-  fig_width: 9
-toc_depth: 3
+title: "Publilia_2019_CHAPTER-0-prep"
+author: "micah fletcher"
+date: "1/18/2022"
+output: html_document
 ---
 
-```{r, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
-                      fig.width = 8, fig.height = 6)
-
-library(kableExtra)   ## Needed if rendering tables
-```
-
-```{=html}
-<style type="text/css">
-  .book .book-body .page-inner {
-    max-width: 1600px;
-    margin-left: auto;
-    margin-right: auto;
-  }
-details > summary {
-  display: list-item;
-}
-</style>
-```
+# Publilia 2019 Chapter - Script 0: data prep
+This is meant to consolidate previous scripts and provide a readable and reproducible record of the analyses for the Publilia Chapter.
+
+The outline for the chapter and the corresponding scripts are as follows:
+
+0) *Data pre-processing:* 
+Preprocessing necessary for all the following analyses, including various automated and manual checking procedures (Female IDs, numbers of eggs, nymphs, ants etc.).
+
+1) *Guarding strategies:* Three distinct strategies for maternal care emerge from ant-dependent and secondary visitor-dependent plasticity
+  - *Dataset A* requirements:
+    - Guarding durations (relative to [estimated] hatching) are accurate.
+      - The sample of clutches is representative of the full factorial of ants / no ants and visited early / not visited early
+    - Able to compare 
+      - initiated vs. visited
+      - first vs. later [initiated] clutches
+        -however, if plotting "all clutches" I can include unmarked females
+      - disappeared vs. deserted (based on last day a female was observed)
+    - Deciding on who is the "true" initiator is necessary for assumptions of independence for statistics. 
+      - Ultimately, comparing the two most obvious options (first and longest guarding mom at initiation, vs first and shortest guarding mom at initiation) will need to suffice.
+Missing data is clearly represented; Compare the "original" unfiltered data to the final data and report why (and how many) data were excluded.
+
+2) *Fecundity:* No support for trade-off between current care and future fecundity
+  - *Dataset B [supp: modeling fecundity ~ guarding]* requirements:
+    - Guarding durations of ALL females that visited a clutch are accurate.
+      - Cannot exclude any females, including unmarked or ambiguously marked females, because I need them for the sum of guarding time.
+    - Maximum number of eggs per clutch is accurate.
+    - Can partition 
+      - early clutches vs. later clutches
+      - single-mother clutches vs. multiple-mother clutches
+      - ants vs. no ants
+  - *Dataset C [estimating fecundity]* requirements:
+    - Guarding durations of ALL females that visited a clutch are accurate.
+      - Cannot exclude any females, including unmarked or ambiguously marked females, because I need them for the sum of guarding time.
+    - Maximum number of eggs per clutch is accurate.
+    - Numbers of clutches per female (and guarding duration and eggs for each) are accurate.
+      - Cannot exclude any clutches, including those with ambiguous initiators, or unknown hatch dates
+    - Models/heuristics of focal female contribution to clutch are clearly defined and sensible.
+      1) simple equal proportion of days
+      2) equal proportion of days with "intercept" given to the initiator
+      3) unequal proportion of days for initiator(s) vs visitors, with intercept also given to the initiator
+      4) Reproducing Zink's fecundity
+
+3) *Clutch-level survivorship regressions:* The impact of care on offspring survivorship depends on ants and offspring stage
+  - *Dataset D [survivorship ~ guarding duration]* requirements:
+    - Guarding durations (relative to [estimated] hatching) are accurate.
+    - (Clutch-level) Hatching success is accurate.
+    - Number of eggs is accurate.
+    - Must exclude clutches where migration to/from other leaves obscured nymph count.
+      - This biases the results toward only including clutches alone on a plant, while clearly it is common to have multiple clutches on a plant.
+One way to address this is to compare to plant-level analysis, so I may reuse parts of this pipeline for the plant-level analysis.
+    - (Clutch-level) Nymph survivorship is accurate.
+    - Must exclude clutches where migration to/from other leaves obscured nymph count. This biases the results in the same way as above.
+    - Main analysis on first clutches laid before June 10. 
+    - But also report on [] in the supplement.
+      - the full dataset
+      - single-female clutches only
+      - female-removal included vs. excluded
+    - Missing data is clearly represented; Compare the "original" unfiltered data to the final data and report why (and how many) data were excluded.
+  - *Dataset E [clutch survivorship ~ ants]* requirements:
+    - Same as Dataset B but also need a representative measure of ant attendance intensity/persistence, e.g.:
+      - percent days attended before hatch
+      - mean/median number of ants before hatch
+      - number of days it took for ants to appear at clutch after hatch
+      - Note: these would ideally be comparable to plant-level metrics
+
+4) *Plant-level survivorship:* Do nymph migration and ant availability at a plant-level make plant-level dynamics more informative to survivorship than clutch-level?
+  - Dataset F [survivorship ~ female presence + ant presence + number of clutches on plant]
+most of the same metrics as for datasets D and E but with relaxed filtering of clutches with ambiguous nymph origins
+
+5) *Ovary development:* If I have time (Narrator: He won't)
+
+## Notes on previous versions.
+Started quality checking in Fall 2019 in `female_ID_qc.R`.
+Started rewriting code in Rmd format on 3/11/2020 in `Watershed_2019_Analysis_IP.Rmd`.
+Started reformatting code into multiple scripts, separating data prep from analysis for better readability, reproducibility, and modularity on 4/13/2021.
+This final version was started 1/18/2022.
 
@@
 ```{r}
-library(here)
 library(tidyverse)
@@
 theme_set(theme_bw())
+
+setwd("/Users/micah/Documents/Princeton/Kocher_Lab/Publilia/PubliliaBehavEcol/Watershed_2019/Watershed_2019_analysis/CHAPTER")
 ```
@@
 col_types = c("date", rep("text",8), "date", rep("text", 12))
-in_filename <- here("data/Watershed_field_data_2019_ALL_local.xlsx")
+in_filename <- "../data_in_progress/Watershed_field_data_2019_ALL_local.xlsx"
 in_data <- rbind(read_xlsx(in_filename, sheet = "A", col_types = col_types),
@@
   ungroup()
+
 ```
@@
 # 1 - Manually check and revise female IDs reproducibly
-
 Create `Female_locations_on_dates` table to use for to manually check for obvious mismatched female IDs and typos in plant id or leaf id etc.
-
 Then manually log these changes into `{dorm letter} Female_ID revisions` sheet then import these and revise the female IDs in the input data without editing the original data file.
-
 Note that changes to things like plant id and leaf id had to be manually edited in the original data file.
@@
 ## 1.1 - Flag duplicate female ID entries
-
 Flag cases where the same female ID is used on the same day in the same dorm to aid in manual checking.
-
 Display false negative and false positive duplicates in `Dup?` column (used in excel for field data entry).
-
 ```{r}
@@
 
-in_data_dupStatus %>%
-  count(dup_status)
-
 in_data_dupStatus %>% filter(dup_status == "Fpos") %>% distinct(Female_ID) %>% print(n=Inf)
@@
   arrange(Dorm, Days_observed)
-
-# used 20200319 version
-# write_csv(Days_observed_dupStatus, here("data/manual_check/Days_observed_dupStatus.csv"))
+#write_csv(Days_observed_dupStatus, "Days_observed_dupStatus_20200319.csv")
 ```
@@
 ## 1.3 - Revise Female_ID using `Female_ID revisions dupStatus` sheet
-
+- ~~check that each "From ID" is actually in the same location in the data as on the revisions table, flag where not the case~~ *[DONE]*
+- ~~check that all duplicates have been resolved~~ *[DONE]*
+- ~~manually doublecheck the location on date table (especially the entry for E_Rgr?_d1)~~ *[DONE]*
+- *****manually check that `short_unhatched_days_check` female revisions remain appropriate and make these revisions reversible -> Check this after running the "short_unhatched_days_check" code chunk*****
+-  ~~old method of replacing a NA (in `From ID`) with a Female_ID (in `To ID`) doesn't work; I will make a new `NA to ID` column that can add a Female ID where there was an NA before~~ *[DONE]*
 ```{r}
@@
 
-*Note: This section saves many `.csv` files with tables to aid manual checks.
-In each case, the contents of these files were copied into the `data/Watershed_field_data_2019_ALL_local.xlsx` spreadsheet as new sheet at the time of initial analysis, revised manually as needed and subsequently read back in to this analysis script and used to revise the data object in the R environment.
-Every effort was made to keep the original field-collected dataseets unchanged in favor of programmatically revising the loading R object.
-In a few cases where this was not possible, the original spreadsheet was edited (with a note in the `Revisions` column).
-As such, newly generated check tables using this script may differ from the originals documented in `data/Watershed_field_data_2019_ALL_local.xlsx`, which preserve the original state of the data.*
-
 ## 2.1 - Flag cases where egg status is missing or inconsistent across multiple entries
@@
   select(Date, Dorm, Plant, Leaf, Eggs)
-# write_csv(egg_text_conflict_data_v1, here("data/manual_check/egg_text_conflict_data.csv"))
+#write_csv(egg_text_conflict_data, "egg_text_conflict_data.csv")
 
@@
   select(Date, Dorm, Plant, Leaf, Eggs)
-# write_csv(egg_status_missing_data_v1, here("data/manual_check/egg_status_missing_data.csv"))
+#write_csv(egg_status_missing_data, "egg_status_missing_data.csv")
 
@@
 
-# 20200326 version was used
-# write_csv(egg_status_missing_data_eggs_revised, here("data/manual_check/egg_status_missing_data_eggs_revised.csv"))
+#write_csv(egg_status_missing_data_eggs_revised, "egg_status_missing_data_eggs_revised_20200326.csv")
 ```
@@
 
-# 20200326 version was used
-# write_csv(egg_status_missing_data_eggs_revised, here("data/manual_check/egg_status_missing_data_eggs_revised.csv")
+#write_csv(egg_status_missing_data_eggs_revised, "egg_status_missing_data_eggs_revised_20200326.csv")
+
 ```
@@
   ungroup()
-# write_csv(nymph_status_to_resolve, here("data/manual_check/nymph_status_to_resolve.csv") ## manually added this to "nymph_status revisions" sheet in "Watershed_field_data_2019_ALL_local" and manually revised raw data 2019/09/26
+# write_csv(nymph_status_to_resolve, "nymph_status_to_resolve.csv") ## manually added this to "nymph_status revisions" sheet in "Watershed_field_data_2019_ALL_local" and manually revised raw data 2019/09/26
 
@@
   select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_text_conflict, N2_text_conflict, N5_text_conflict)
-# write_csv(egg_text_conflict_data, "egg_text_conflict_data.csv")
+#write_csv(egg_text_conflict_data, "egg_text_conflict_data.csv")
 
@@
   select(Date, Dorm, Plant, Leaf, Female_ID, Eggs, N1, N2, N5, nymph_origin, Notes, N1_status_missing, N2_status_missing, N5_status_missing)
-# write_csv(egg_status_missing_data, "egg_status_missing_data.csv")
+#write_csv(egg_status_missing_data, "egg_status_missing_data.csv")
 
@@
   distinct(location)
-# write_csv(check_hatch_date, "check_hatch_date_tmp.csv")
+#write_csv(check_hatch_date, "check_hatch_date_tmp.csv")
 ```
@@
 
-# write_csv(ant_text_conflict, "ant_text_conflict.csv") # resolved 2019-10-08
+#write_csv(ant_text_conflict, "ant_text_conflict.csv") # resolved 2019-10-08
+
 ```
@@
 
-# write_csv(short_unhatched_days_check, "short_unhatched_days_check_tmp.csv")
+#write_csv(short_unhatched_days_check, "short_unhatched_days_check_tmp.csv")
 
@@
 
-# write_csv(never_hatched_check, "never_hatched_check_tmp.csv")
-
-# write_csv(clutch_status_stats_v1, "egg_measures_check_tmp.csv")
+#write_csv(never_hatched_check, "never_hatched_check_tmp.csv")
+
+#write_csv(clutch_status_stats_v1, "egg_measures_check_tmp.csv")
 ```
@@
 
-# 6 - Write data for `Publilia-02-strats.Rmd` to `.rds` for further analysis in clean environment
-
-## `Publilia-02-strats.Rmd`
-```{r}
-write_rds(All_data_v6, here("saved_rds/All_data_v6.rds"))
-write_rds(clutch_status_guarding_summary_v2, here("saved_rds/clutch_status_guarding_summary_v2.rds"))
-write_rds(last_day_fID, here("saved_rds/last_day_fID.rds"))
-```
-
-***
-
-*Prep data for `Publilia-03-survivorship.Rmd`:*
-
-# 7 - Assigning nymph origins
-
-Nymphs migrate away from their natal leaf.
-On plants with multiple clutches, it was sometimes possible to determine the origin of nymphs later in the season because sometimes groups of nymph don't travel very far from their natal leaf and mix with other groups.
-I manually curated examples of this, so that clutch-level stats on hatching success and nymph survivorship could be determined on the plants with multiple clutches.
-Some clutches (as a rule only on multi-clutch plants) did not have a clear record of nymphs that emigrated from the natal leaf and thus could not be included in future clutch-level analyses of survivorship.
-
-## 7.1 - Adding second gen adult counts per leaf to clutch status stats
-```{r}
-# counting adults
-eA_status_v1 <- All_data_v6 %>%
-  group_by(row_number()) %>% # sum of newly exclosed adults
-  filter(any(!is.na(c(New_eA, Old_eA)))) %>%
-  mutate(n_newA = ifelse(is.na(New_eA),
-                         NA,
-                         sum(as.numeric(regmatches(New_eA, gregexpr("[0-9]+", New_eA))[[1]]))),
-         n_oldA = ifelse(is.na(Old_eA),
-                         NA,
-                         sum(as.numeric(regmatches(Old_eA, gregexpr("[0-9]+", Old_eA))[[1]]))),
-         n_A = sum(n_newA, n_oldA, na.rm = TRUE)) %>%
-  ungroup() %>%
-  select(Date, location, n_newA, n_oldA, n_A)
-
-All_data_v6_clutch_status_stats_v2 <- All_data_v6 %>%
-  # add egg measures, clutch status stats (including initiation dates, hatch dates, egg fate, etc)
-  left_join(clutch_status_v2, by = c("location", "Date")) %>%
-  left_join(clutch_status_stats_v1, by = c("location")) %>%
-  left_join(eA_status_v1, by = c("Date", "location")) %>%
-  left_join(select(clutch_status_guarding_summary_v2, location, never_hatched)) %>%
-  mutate(N1 = as.numeric(N1),
-         N2 = as.numeric(N2),
-         N5 = as.numeric(N5))
-```
-
-## 7.2 - Manually check nymph origins for revision
-First create a table of all entried from clutches that were not flagged in the field as having ambiguous origin (e.g.
-"leaf 6 or 9") in cases were more than one clutch was on the plant.
-These were revised manually to specify a leaf of origin for the nymphs, where possible.
-```{r}
-NOr_status_resolveable_all_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>% 
-  select(Date, Dorm, Plant, Leaf, location, 
-         egg_num, N1, N2, N5, n_A, nymph_origin, initiation_date, hatch_date,
-         any_NOr_ambig_loc, Omit_for_abandon_time, never_hatched,
-         n_clutches_on_plant) %>%
-  # keep only entries with some nymphs or adults on a leaf
-  # OR entries for leaves where clutches have been initiated
-  group_by(row_number()) %>%
-  filter(!is.na(Leaf) & any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) | 
-           Date >= initiation_date) %>% # nrow = 17944
-  # flag entries where the nymph origin is text (typically ambiguous, e.g. "8 or 9")
-  mutate(NOr_ambig_entry = !is.na(nymph_origin) & is.na(as.numeric(nymph_origin))) %>% 
-  ungroup() %>%
-  # get rid of duplicate rows from multiple females in the same location
-  distinct(Date, location, .keep_all = TRUE) %>% # nrow = 15674
-  group_by(Dorm, Plant) %>%
-    # filter out any plants with a clutch that was omitted for abandon time
-    filter(!any(!is.na(Omit_for_abandon_time))) %>%
-    # flag plants with any ambiguous entries (e.g. "8 or 9") skip for checking
-    mutate(NOr_ambig_plant = any(NOr_ambig_entry)) %>%
-  ungroup()
-
-NOr_status_resolveable_mult_clutches <- NOr_status_resolveable_all_unambig_clutches %>% # nrow = 15674
-  group_by(Dorm, Plant) %>%
-    # plants with mutliple clutches only
-    filter(any(n_clutches_on_plant > 1)) %>%
-  ungroup() %>%
-  group_by(row_number()) %>%
-    # flag for manual checking entries with any nymphs/adults, missing nymph origin, 
-    # but not flagged for ambiguous origin in the field.
-    # these are the most likely to be easily resolved with minimal work
-    mutate(revise_NOr = ifelse(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) &
-             !NOr_ambig_plant,
-           "MANUAL CHECK",
-           NA)) %>% 
-  ungroup()
-
-NOr_manual_check_table <- NOr_status_resolveable_mult_clutches %>%
-  group_by(Dorm, Plant) %>%
-    filter(any(revise_NOr == "MANUAL CHECK")) %>% # nrow = 2830
-  ungroup() %>%
-    group_by(row_number()) %>%
-    filter(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0)) %>%
-  ungroup() %>%
-  select(Date, Dorm, Plant, Leaf, location, egg_num, N1, N2, N5, n_A, nymph_origin,
-         initiation_date, hatch_date,
-         revise_NOr) %>%
-  arrange(Dorm, as.numeric(Plant), as.numeric(Leaf), Date)
-# 83 clutches on 34 plants to check
-
-# write_csv(NOr_manual_check_table %>% filter(revise_NOr == "MANUAL CHECK"), "NOr_manual_check_tmp.csv")
-
-NOr_manual_revisions <- read_xlsx(in_filename, sheet = "NOr_manual_check", col_types = c("date", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "logical", "text")) %>%
-  mutate(Date = as_date(Date),
-         NOr_rev_loc_manual = paste0(Dorm, Plant, "_", NOr_revised)) %>%
-  filter(!cant_resolve) %>%
-  select(Date, location, NOr_rev_loc_manual, NOr_revised_manual = NOr_revised)
-
-NOr_manual_revisions %>%
-  distinct(NOr_rev_loc_manual) # 43/83 initiated clutches (43/59 hatched) with successfully revised NOr
-```
-
-## 7.3 - Implement revisions by creating the new variables NOr_revised and NOr_rev_loc
-```{r}
-# if nymph origin was clearly resolveable, the revisions were made in NOr_manual_revisions
-# updating NOr_status with revisions so that it can be left_joined to other data and
-# counts of nymphs and adults on NOr can be calculated
-NOr_status_revised_all_unambig_clutches <- NOr_status_resolveable_all_unambig_clutches %>%
-  left_join(NOr_manual_revisions, by = c("Date", "location")) %>%
-  group_by(Dorm, Plant) %>%
-    mutate(lone_hatcher_leaf = ifelse(length(unique(Leaf[!is.na(initiation_date)])) == 1,
-                                 unique(Leaf[!is.na(initiation_date)]),
-                                 NA),
-           NOr_revised = ifelse(!is.na(NOr_revised_manual),
-                                       NOr_revised_manual,
-                                ifelse(any(!is.na(lone_hatcher_leaf)),
-                                       lone_hatcher_leaf,
-                                       # if no clutches hatched on the plant, NOr_revised = Leaf
-                                       # for leaves with eggs
-                                       ifelse(!any(!is.na(hatch_date)) & !is.na(egg_num),
-                                              Leaf,
-                                              NA)))) %>%
-  ungroup() %>%  
-  group_by(location) %>%
-    mutate(NOr_revised = ifelse(any(NOr_revised == Leaf) & is.na(NOr_revised),
-                                Leaf,#unique(NOr_revised[!is.na(NOr_revised)]),
-                                NOr_revised)) %>%
-  ungroup() %>%
-  mutate(NOr_rev_loc = ifelse(is.na(NOr_revised),
-                              NA,
-                              paste0(Dorm, Plant, "_", NOr_revised))) %>%
-  select(Date, location, NOr_revised, NOr_rev_loc) %>%
-  filter(!is.na(NOr_rev_loc))
-
-All_data_v6_N_NOr_counts_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>%
-  right_join(NOr_status_revised_all_unambig_clutches, by = c("Date", "location")) %>%
-  group_by(Date, Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
-    summarize(N1_NOr = sum(N1, na.rm= TRUE),
-              N2_NOr = sum(N2, na.rm= TRUE),
-              N5_NOr = sum(N5, na.rm= TRUE),
-              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
-              A_NOr = sum(n_A, na.rm= TRUE),
-              N5plusA_NOr = sum(N5, n_A, na.rm= TRUE)) %>%
-  ungroup() # n = 186
-
-All_data_v6_N_NOr_counts_unambig_clutches_summary <- All_data_v6_N_NOr_counts_unambig_clutches %>%
-  group_by(Date) %>%
-    mutate(mean_N_NOr = mean(N_NOr, na.rm = TRUE),
-           mean_N1_NOr = mean(N1_NOr, na.rm = TRUE),
-           mean_N2_NOr = mean(N2_NOr, na.rm = TRUE),
-           mean_N5_NOr = mean(N5_NOr, na.rm = TRUE),
-           mean_A_NOr = mean(A_NOr, na.rm = TRUE),
-           mean_N5plusA_NOr = mean(N5plusA_NOr, na.rm = TRUE),
-           All_N_NOr = sum(N_NOr),
-           All_A_NOr = sum(A_NOr)) %>%
-  ungroup() %>%
-  group_by(Date, Dorm) %>%
-    mutate(All_N_NOr_Dorm = sum(N_NOr),
-           All_N1_NOr_Dorm = sum(N1_NOr),
-           All_N2_NOr_Dorm = sum(N2_NOr),
-           All_N5_NOr_Dorm = sum(N5_NOr),
-           All_A_NOr_Dorm = sum(sum(A_NOr))) %>%
-  ungroup()
-
-All_data_v6_all_nymphs_unambig_clutches <- All_data_v6_N_NOr_counts_unambig_clutches %>%
-  group_by(Date) %>%
-    summarize(All_N_NOr = sum(N_NOr)) %>%
-  ungroup()
-
-All_data_v6_max_N_NOr_counts_unambig_clutches <-
-  All_data_v6_N_NOr_counts_unambig_clutches %>%
-  group_by(Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
-    summarize(max_N_NOr = max(N_NOr)) %>%
-  ungroup()
-
-clutch_status_stats_v1_unambig_clutches_hatch_success <- clutch_status_stats_v1 %>%
-  separate(location, c("DormPlant", "Leaf"), sep = "_", remove = FALSE) %>%
-  mutate(Dorm = substr(DormPlant, 1, 1),
-         Plant = substring(DormPlant, 2)) %>%
-  left_join(distinct(clutch_status_guarding_summary_v2, location, never_hatched)) %>%
-  right_join(All_data_v6_max_N_NOr_counts_unambig_clutches, by = c("Dorm", "Plant", "Leaf" = "NOr_revised")) %>%
-  # why did I originally say to make hatch_success = NA if never_hatched == TRUE?
-  mutate(hatch_success = ifelse(!is.na(initiation_date) & is.na(hatch_date),
-                                0,
-                                max_N_NOr/max_egg_num))
-```
-
-## 7.4 - Flag and resolve ambiguous nymph origins
-
-```{r}
-NOr_status_resolveable_all_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>% 
-  select(Date, Dorm, Plant, Leaf, location, 
-         egg_num, N1, N2, N5, n_A, nymph_origin, initiation_date, hatch_date,
-         any_NOr_ambig_loc, Omit_for_abandon_time, never_hatched,
-         n_clutches_on_plant) %>%
-  # keep only entries with some nymphs or adults on a leaf
-  # OR entries for leaves where clutches have been initiated
-  group_by(row_number()) %>%
-  filter(!is.na(Leaf) & any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) | 
-           Date >= initiation_date) %>% # nrow = 17944
-  # flag entries where the nymph origin is text (typically ambiguous, e.g. "8 or 9")
-  mutate(NOr_ambig_entry = !is.na(nymph_origin) & is.na(as.numeric(nymph_origin))) %>% 
-  ungroup() %>%
-  # get rid of duplicate rows from multiple females in the same location
-  distinct(Date, location, .keep_all = TRUE) %>% # nrow = 15674
-  group_by(Dorm, Plant) %>%
-    # filter out any plants with a clutch that was omitted for abandon time
-    filter(!any(!is.na(Omit_for_abandon_time))) %>%
-    # flag plants with any ambiguous entries (e.g. "8 or 9") skip for checking
-    mutate(NOr_ambig_plant = any(NOr_ambig_entry)) %>%
-  ungroup()
-
-NOr_status_resolveable_mult_clutches <- NOr_status_resolveable_all_unambig_clutches %>%
-  group_by(Dorm, Plant) %>%
-    # plants with mutliple clutches only
-    filter(any(n_clutches_on_plant > 1)) %>%
-  ungroup() %>%
-  group_by(row_number()) %>%
-    # flag for manual checking entries with any nymphs/adults, missing nymph origin, 
-    # but not flagged for ambiguous origin in the field.
-    # these are the most likely to be easily resolved with minimal work
-    mutate(revise_NOr = ifelse(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) &
-             !NOr_ambig_plant,
-           "MANUAL CHECK",
-           NA)) %>% 
-  ungroup()
-```
-
-## 7.5 - Fixing the omission of clutches that never had first instar nymphs
-
-```{r}
-NOr_status_revised_all_unambig_clutches_v2 <- NOr_status_resolveable_all_unambig_clutches %>%
-  left_join(NOr_manual_revisions, by = c("Date", "location")) %>%
-  group_by(Dorm, Plant) %>%
-    mutate(lone_hatcher_leaf = ifelse(length(unique(Leaf[!is.na(initiation_date)])) == 1,
-                                 unique(Leaf[!is.na(initiation_date)]),
-                                 NA),
-           NOr_revised = ifelse(!is.na(NOr_revised_manual), # if I manually annotated a revised location
-                                       NOr_revised_manual, # make manual location the new nymph origin
-                                ifelse(any(!is.na(lone_hatcher_leaf)), # if only one clutch hatched on the plant
-                                       lone_hatcher_leaf, # make that clutch the new nymph origin
-                                       # if no clutches hatched on the plant, NOr_revised = Leaf
-                                       # for leaves with eggs
-                                       ifelse(!any(!is.na(hatch_date)) & !is.na(egg_num), # if no clutches hatched on the plant (but there are eggs)
-                                              Leaf, # make the given leaf the new nymph origin
-                                              NA)))) %>% # BUT THIS STILL EXCLUDES CLUTCHES THAT DIDN'T HATCH ON A PLANT WITH SOME CLUTCHES THAT DID HATCH
-  ungroup() %>%  
-  group_by(location) %>%
-    mutate(NOr_revised = ifelse(any(NOr_revised == Leaf) & is.na(NOr_revised), # DOES THIS INCLUDE UNHATCHED CLUTCHES? NO
-                                Leaf,#unique(NOr_revised[!is.na(NOr_revised)]),
-                                NOr_revised),
-           NOr_revised = ifelse(any(is.na(NOr_revised)) & # if no revised nymph origin yet
-                                                  any(!is.na(egg_num)&egg_num>0 & !any(!is.na(N1)&N1>0)), # and N1 never on clutch (not hatched or spuriously visited by N1)
-                                Leaf, # make this leaf the new nymph origin (so we include unhatched clutches)
-                                NOr_revised)) %>% 
-  ungroup() %>%
-  mutate(NOr_rev_loc = ifelse(is.na(NOr_revised),
-                              NA,
-                              paste0(Dorm, Plant, "_", NOr_revised))) %>%
-  select(Date, location, NOr_revised, NOr_rev_loc) %>%
-  filter(!is.na(NOr_rev_loc))
-
-All_data_v6_N_NOr_counts_unambig_clutches_v2 <- All_data_v6_clutch_status_stats_v2 %>%
-  right_join(NOr_status_revised_all_unambig_clutches_v2, by = c("Date", "location")) %>%
-  group_by(Date, Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
-    summarize(N1_NOr = sum(N1, na.rm= TRUE),
-              N2_NOr = sum(N2, na.rm= TRUE),
-              N5_NOr = sum(N5, na.rm= TRUE),
-              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
-              A_NOr = sum(n_A, na.rm= TRUE),
-              N5plusA_NOr = sum(N5, n_A, na.rm= TRUE)) %>%
-  ungroup()
-
-All_data_v6_N_NOr_counts_unambig_clutches_summary_v2 <- All_data_v6_N_NOr_counts_unambig_clutches_v2 %>%
-  group_by(Date) %>%
-    mutate(mean_N_NOr = mean(N_NOr, na.rm = TRUE),
-           mean_N1_NOr = mean(N1_NOr, na.rm = TRUE),
-           mean_N2_NOr = mean(N2_NOr, na.rm = TRUE),
-           mean_N5_NOr = mean(N5_NOr, na.rm = TRUE),
-           mean_A_NOr = mean(A_NOr, na.rm = TRUE),
-           mean_N5plusA_NOr = mean(N5plusA_NOr, na.rm = TRUE),
-           All_N_NOr = sum(N_NOr),
-           All_A_NOr = sum(A_NOr)) %>%
-  ungroup() %>%
-  group_by(Date, Dorm) %>%
-    mutate(All_N_NOr_Dorm = sum(N_NOr),
-           All_N1_NOr_Dorm = sum(N1_NOr),
-           All_N2_NOr_Dorm = sum(N2_NOr),
-           All_N5_NOr_Dorm = sum(N5_NOr),
-           All_A_NOr_Dorm = sum(sum(A_NOr))) %>%
-  ungroup()
-```
-
-# 8 - Calculate hatch success and nymph survivorship
-
-Calculate hatch success (strict sense; max N1 / max eggs) and nymph survivorship (max N5+A / max eggs AND/OR max N5+A / max N1)
-
-- Filtered out clutches with outlier numbers of N1 or N5 etc at early or late clutch ages, which were assumed to be cases of immigration that weren't caught during manual nymph origin filtering
-```{r}
-# Filter to only include curated list of clutches with unambiguous nymph counts after accounting for immigration to non-natal leaves and then sum all nymphs (including emigrants) for each clutch
-# I also added clutch_age variables to help identify clutches that were started too close to the end of sampling to be useful
-clutch_unambig_NOr_revised_ENAa_summary_v2 <- All_data_v6_clutch_status_stats_v2 %>%
-  right_join(NOr_status_revised_all_unambig_clutches_v2, by = c("Date", "location")) %>%
-  select(Date, NOr_rev_loc, location, egg_num, N1, N2, N5, n_A, ants_L) %>%
-    # remove any duplicates - I need to figure out why there are dups later but for 4th yr talk
-  distinct(Date, NOr_rev_loc, location, egg_num, N1, N2, N5, n_A, ants_L, .keep_all = TRUE) %>%
-  mutate(egg_num_NOr = ifelse(NOr_rev_loc == location, egg_num, NA)) %>%
-  group_by(Date, NOr_rev_loc) %>%
-    summarize(eggs_NOr = first(egg_num_NOr[!is.na(egg_num_NOr)]), # only use eggs from origin leaf!
-              N1_NOr = sum(N1, na.rm= TRUE),
-              N2_NOr = sum(N2, na.rm= TRUE),
-              N5_NOr = sum(N5, na.rm= TRUE),
-              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
-              A_NOr = sum(n_A, na.rm= TRUE),
-              N5toA_NOr = sum(N5, n_A, na.rm= TRUE),
-              ants_NOr = sum(ants_L, na.rm = TRUE)) %>%
-  ungroup() %>%
-  left_join(filter(clutch_status_guarding_summary_v2, mom_at_init), by = c("NOr_rev_loc" = "location")) %>%
-  mutate(clutch_age1 = Date - initiation_date,
-         clutch_age2 = ceiling((Date - initiation_date)/2)*2,
-         clutch_age4 = ceiling((Date - initiation_date)/4)*4,
-         after_hatch1 = Date - hatch_date,
-         after_hatch2 = ceiling((Date - hatch_date)/2)*2,
-         after_hatch4 = ceiling((Date - hatch_date)/4)*4) %>%
-  select(Date, NOr_rev_loc, clutch_age1, after_hatch1, eggs_NOr, 
-         N1_NOr, N2_NOr, N5_NOr, N_NOr, A_NOr, N5toA_NOr, ants_NOr,
-         init_fem = Female_ID,
-         initiation_date, hatch_date, guard_duration, relative_desert_date,
-         clutch_initiated_order, females_removed, ants_removed, 
-         clutch_age2, clutch_age4, after_hatch2, after_hatch4) #%>%
-  # filter(initiation_date <= as_date("2019-06-10"),
-  #        clutch_age4 <= 68)
-
-max_N1_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
-  group_by(NOr_rev_loc) %>%
-  arrange(NOr_rev_loc, desc(N1_NOr), Date) %>%
-  filter(row_number() == 1) %>%
-  ungroup() %>%
-  select(NOr_rev_loc, max_N1_date = Date, max_N1_age = clutch_age1)
-
-max_N5_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
-  group_by(NOr_rev_loc) %>%
-  arrange(NOr_rev_loc, desc(N5_NOr), Date) %>%
-  filter(row_number() == 1) %>%
-  ungroup() %>%
-  select(NOr_rev_loc, max_N5_date = Date, max_N5_age = clutch_age1)
-
-max_A_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
-  group_by(NOr_rev_loc) %>%
-  arrange(NOr_rev_loc, desc(A_NOr), Date) %>%
-  filter(row_number() == 1) %>%
-  ungroup() %>%
-  select(NOr_rev_loc, max_A_date = Date, max_A_age = clutch_age1)
-
-max_N5toA_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
-  group_by(NOr_rev_loc) %>%
-  arrange(NOr_rev_loc, desc(N5toA_NOr), Date) %>%
-  filter(row_number() == 1) %>%
-  ungroup() %>%
-  select(NOr_rev_loc, max_N5toA_date = Date, max_N5toA_age = clutch_age1)
-
-max_N5toA_Date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
-  group_by(NOr_rev_loc) %>%
-  summarize(max_N1 = max(N1_NOr),
-            max_N5toA = max(N5toA_NOr),
-            max_clutch_age = max(clutch_age1),
-            max_after_hatch = max(after_hatch1),
-            max_Date = max(Date),
-            hatched = any(!is.na(hatch_date)),
-            initiation_date = first(initiation_date)) %>%
-  ungroup() %>%
-  arrange(desc(max_N5toA)) %>%
-  full_join(max_N1_date_v2) %>%
-  full_join(max_N5_date_v2) %>%
-  full_join(max_A_date_v2) %>%
-  full_join(max_N5toA_date_v2)
-
-clutch_unambig_NOr_revised_ENAa_summary_imfilt_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
-  mutate(N_imm_likely_d15 = clutch_age1 < 15 & N_NOr > 0,
-         N5_imm_likely_d40 = clutch_age1 < 40 & N5_NOr > 0,
-         A_imm_likely_d40 = clutch_age1 < 40 & A_NOr > 0) %>%
-  group_by(NOr_rev_loc) %>%
-    filter(!any(N_imm_likely_d15, N5_imm_likely_d40, A_imm_likely_d40, na.rm = TRUE)) %>% # n = 168
-  ungroup()
-
-clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_v2 <-
-  clutch_unambig_NOr_revised_ENAa_summary_imfilt_v2 %>%
-  group_by(NOr_rev_loc) %>%
-    mutate(hatch_success_N1 = max(N1_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
-           survival_rate = max(N5toA_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
-           prop_E2Ni = max(N1_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
-           prop_E2N = max(N_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
-           prop_Ni2Nv = max(N5toA_NOr, na.rm = TRUE)/max(N1_NOr, na.rm = TRUE),
-           prop_E2Nv = max(N5toA_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
-           n_eggs = max(eggs_NOr, na.rm = TRUE),
-           n_hatched = max(N1_NOr, na.rm = TRUE),
-           n_N = max(N_NOr, na.rm = TRUE),
-           n_survived = max(N5toA_NOr, na.rm = TRUE)) %>%
-  ungroup()
-
-clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2 <- clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_v2 %>%
-  distinct(NOr_rev_loc, n_eggs, n_hatched, n_survived, n_N,
-           prop_E2Ni, prop_Ni2Nv, prop_E2Nv, prop_E2N, hatch_success_N1, survival_rate,
-           initiation_date, hatch_date, females_removed, ants_removed) 
-```
-
-# 9 - Ant counts on clutch
-
-```{r}
-theme_publilia <- function(){
-  theme_bw() +
-    theme(text = element_text(family = "Arial"),
-          axis.text = element_text(size = 12), 
-          axis.title = element_text(size = 14),
-          axis.line.x = element_line(color="black"), 
-          axis.line.y = element_line(color="black"),
-          panel.border = element_blank(),
-          panel.grid.major.x = element_blank(),                                          
-          panel.grid.minor.x = element_blank(),
-          panel.grid.minor.y = element_blank(),
-          panel.grid.major.y = element_blank(),  
-          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
-          plot.title = element_text(size = 18, vjust = 1, hjust = 0.5, face = "bold"),
-          legend.text = element_text(size = 10),          
-          legend.title = element_blank(),                              
-          # legend.position = c(0.90, 0.90), 
-          legend.key = element_blank(),
-          legend.background = element_rect(color = "black", 
-                                           fill = "transparent", 
-                                           size = 2, linetype = "blank"))
-}
-```
-
-## 9.0 - Get visited_1st_4d_data
-
-```{r}
-strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
-
-visited_1st_4d_data <- strats_data %>%
-  group_by(location) %>%
-    mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
-  ungroup() %>%
-  mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
-                                      "Visited", "Not visited"),
-         ants = ifelse(ants_removed, "Ants removed", "Control"),
-         est_hatch = as_date(ifelse(is.na(hatch_date),
-                                 initiation_date + 20,
-                                 hatch_date)),
-         est_rel2h = visit_ends-est_hatch)
-```
-
-```{r}
-visited_1st_4d_data_tb <- visited_1st_4d_data %>%
-  # 1) Longest initiator
-  mutate(initL = init_first_dur_rank == 1) %>% 
-  # 2) Shortest initiator
-  #  i) break ties by picking marked females over unmarked
-  group_by(location, init_first_dur_shortest) %>% 
-    mutate(initS_tmp = ifelse(n()>1, !grepl("Uf", Female_ID), TRUE)) %>% 
-  ungroup() %>%
-  #  ii) finally picking at random (only one case, identical predictor vars)
-  group_by(location, init_first_dur_shortest, initS_tmp) %>%
-    mutate(initS = init_first_dur_shortest & initS_tmp & row_number()==1) %>%
-  ungroup()
-```
-
-## 9.1 - A small fraction of ants_removed clutches were visited by ants, and vice versa
-```{r}
-ant_counts <- All_data_v6 %>%
-  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-  filter(!is.na(initiation_date)) %>%
-  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-  group_by(location) %>%
-    mutate(b4h=Date>=initiation_date&Date<est_hatch,
-           afh=Date>=est_hatch) %>%
-    summarize(ants_removed=first(ants_removed),
-              females_removed=first(females_removed),
-              n_antsP=sum(ants_P,na.rm=T),
-              ever_antsP=n_antsP>0,
-              mean_antsP=mean(ants_P,na.rm=T),
-              med_antsP=median(ants_P,na.rm=T),
-
-              n_antsP_b4h=sum(ants_P&b4h),
-              ever_antsP_b4h=n_antsP_b4h>0,
-              mean_antsP_b4h=mean(ifelse(b4h,ants_P,NA),na.rm=T),
-              med_antsP_b4h=median(ifelse(b4h,ants_P,NA),na.rm=T),
-
-              n_antsP_afh=sum(ants_P&afh),
-              ever_antsP_afh=n_antsP_afh>0,
-              mean_antsP_afh=mean(ifelse(afh,ants_P,NA),na.rm=T),
-              med_antsP_afh=median(ifelse(afh,ants_P,NA),na.rm=T)) %>%
-  ungroup() %>%
-  mutate(Dorm=substr(location,1,1),
-         ant_treatment=ifelse(ants_removed,"Ants removed","Control"))
-
-ggplot(data=ant_counts,aes(x=Dorm,y=n_antsP, fill=ant_treatment)) +
-  geom_boxplot()
-
-ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP, fill=ant_treatment)) +
-  geom_boxplot()
-
-ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_b4h, fill=ant_treatment)) +
-  geom_boxplot()
-
-ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_afh, fill=ant_treatment)) +
-  geom_boxplot()
-
-```
-
-# 9.2 - Threshold for number of days ants were on the plant
-Should I be more lenient with my threshold, so I can have more even sample sizes between "ants" and "no ants"?
-- ants_ever = n_days_ants>0: F = 83, T = 143
-- antsP_gt2d = n_days_ants>2: F = 123, T = 103 * most even sample size
-- antsP_gt3d = n_days_ants>3: F = 133, T = 90
-```{r}
-ant_n_days <- All_data_v6 %>%
-  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-  filter(!is.na(initiation_date)) %>%
-  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-  mutate(ant_treatment=ifelse(ants_removed,"Ants removed","Control"),
-         Dorm=substr(location,1,1)) %>%
-  group_by(Date, location) %>%
-    summarize(any_antsP_day = any(ants_P>0, na.rm=T),
-              females_removed = first(females_removed),
-              ant_treatment = first(ant_treatment),
-              Dorm = first(Dorm)) %>%
-  ungroup() %>%
-  group_by(location) %>%
-    summarize(n_days_ants = sum(as.numeric(any_antsP_day)),
-              females_removed = first(females_removed),
-              ant_treatment = first(ant_treatment),
-              Dorm = first(Dorm))%>%
-  ungroup() %>%
-  mutate(antsP_gt2d = !is.na(n_days_ants)&n_days_ants>2,
-         antsP_gt3d = !is.na(n_days_ants)&n_days_ants>3,
-         ants_everP = is.na(n_days_ants)|n_days_ants>0)
-
-ant_n_days %>%
-  count(females_removed, ants_everP)
-
-ant_n_days %>%
-  count(females_removed, antsP_gt2d)
-
-ant_n_days %>%
-  count(females_removed, antsP_gt3d)
-```
-
-# 10 - Estimate clutch size more robust to outliers: median top 5 egg counts
-
-## 10.1 - Generate data for fecundity modeling
-
-```{r}
-fec_model_data <- visited_1st_4d_data_tb %>%
-  filter(!is.na(guard_duration)) %>%
-  group_by(location) %>%
-  mutate(eggs_ever_visited = any(!mom_at_init & visit_ends <= est_hatch)) %>%
-  ungroup() %>%
-  select(Female_ID, location, guard_duration, est_rel2h, initiation_date, est_hatch,
-         mom_at_init, clutch_initiated_order, initL, initS,
-         visit_starts, visit_ends, last_day_fID,
-         num_at_init, n_clutches_on_plant, `visited in 4 days`, eggs_ever_visited, ants,
-         females_removed, ants_removed, 
-         max_egg_num, egg_fate, egg_fate_date)
-```
-
-## 10.2 - Calculate median of top 5 egg counts in lieu of max egg counts
-Taking the median (or mean) of the top 5 egg_num counts yields an estimate of max egg num that is more robust to outliers/miscounts
-```{r}
-tmp_t5eggs_data <- clutch_status_init_hatch_labels_v1 %>%
-  mutate(est_hatch = as_date(ifelse(is.na(hatch_date),
-                                 initiation_date + 20,
-                                 hatch_date)),
-         clutch_age = as.numeric(Date-initiation_date)) %>%
-  # remove duplicate egg counts due to multiple females at a location on a day
-  distinct(location, Date, initiation_date, est_hatch, clutch_age,
-           egg_num, egg_len) %>%
-  group_by(location) %>%
-    arrange(desc(egg_num)) %>%
-    mutate(top5egg_counts = rank(desc(egg_num), ties.method = "first") <= 5,
-           top5egg_lens = rank(desc(egg_len), ties.method = "first") <= 5) %>%
-    #filter(location == "A13_11") %>%
-    select(location, Date, initiation_date, est_hatch, clutch_age,
-           egg_num, egg_len, top5egg_counts, top5egg_lens) %>%
-    mutate(med_t5eggs = median(ifelse(top5egg_counts,egg_num,NA), na.rm=T),
-           mean_t5eggs = mean(ifelse(top5egg_counts,egg_num,NA), na.rm=T),
-           max_n_eggs = max(ifelse(top5egg_counts,egg_num,NA), na.rm=T),
-           med_l_t5eggs = median(ifelse(top5egg_lens,egg_len,NA), na.rm=T),
-           mean_l_t5eggs = mean(ifelse(top5egg_lens,egg_len,NA), na.rm=T),
-           max_l_eggs = max(ifelse(top5egg_lens,egg_len,NA), na.rm=T)) %>%
-  ungroup()
-
-top5eggs_summary <- tmp_t5eggs_data %>%
-  group_by(location) %>%
-    summarize(med_t5eggs = first(med_t5eggs),
-              mean_t5eggs = first(mean_t5eggs),
-              max_n_eggs = first(max_n_eggs),
-              med_l_t5eggs = first(med_l_t5eggs),
-              mean_l_t5eggs = first(mean_l_t5eggs),
-              max_l_eggs = first(max_l_eggs)) %>%
-  ungroup()
-```
-
-# 11 - Calculate alternative measures of maternal tenure
-
-`The sum of all females’ egg-guarding durations was more predictive of final clutch size than egg guarding duration of the initiator alone (Table S1 with alternative models and their AICs), showing that females lay eggs while visiting existing clutches.`
-
-## 11.1 - Initiator guarding time: initMb4h
-```{r}
-initiator_days_b4hatch <- visited_1st_4d_data_tb %>%
-  filter(!is.na(initiation_date),
-         # exclude clutches for which the initiators are not known
-         !is.na(num_at_init),
-         mom_at_init) %>%
-  group_by(row_number()) %>%
-  # Use median init to hatch interval (20 days) to est hatch date of clutch with no hatch date
-  mutate(init_dur = ifelse(min(est_hatch, visit_ends) - 
-                                       max(initiation_date, visit_starts) >= 0,
-                           visit_ends-initiation_date+1, 
-                           NA),
-         initMb4hatch = ifelse(min(est_hatch, visit_ends) - 
-                                       max(initiation_date, visit_starts) >= 0,
-           min(est_hatch, visit_ends) - 
-           max(initiation_date, visit_starts) + 1,
-           ifelse(visit_starts > est_hatch | visit_ends < initiation_date,
-                  NA,
-                  NA)),
-         initMb4h_sc2h = initMb4hatch/as.numeric((est_hatch-initiation_date+1))) %>%
-  ungroup()
-
-initMb4h_tbL <- initiator_days_b4hatch %>%
-  filter(initL) %>%
-  select(location, desert_rel2hL=est_rel2h, init_durL=init_dur, initMb4h_tbL=initMb4hatch, initMb4h_sc2hL=initMb4h_sc2h,
-         females_removed, ants_removed, initiation_date, num_at_init,
-         initiator_tbL=Female_ID, n_clutches_on_plant)
-
-initMb4h_tbS <- initiator_days_b4hatch %>%
-  filter(initS) %>%
-  select(location, desert_rel2hS=est_rel2h, init_durS=init_dur, initMb4h_tbS=initMb4hatch, initMb4h_sc2hS=initMb4h_sc2h,
-         females_removed, ants_removed, initiation_date, num_at_init,
-         initiator_tbS=Female_ID, n_clutches_on_plant)
-```
-
-## 11.2 - proportional time: mDb4h
-```{r}
-focalMb4h_sc2h <- visited_1st_4d_data_tb  %>%
-  # exclude visits to leaves that never had eggs; only interested in clutches
-  filter(!is.na(initiation_date),
-         # exclude clutches for which the initiators are not known (why?)
-         !is.na(num_at_init)) %>%
-  group_by(row_number()) %>%
-  # Use median init to hatch interval (20 days) to est hatch date of clutch with no hatch date
-  mutate(mD = ifelse(min(est_hatch, visit_ends) - 
-                                       max(initiation_date, visit_starts) >= 0,
-                     visit_ends-initiation_date+1,
-                     NA),
-         days_guard_b4hatch = ifelse(min(est_hatch, visit_ends) - 
-                                       max(initiation_date, visit_starts) >= 0,
-           min(est_hatch, visit_ends) - 
-           max(initiation_date, visit_starts) + 1,
-           ifelse(visit_starts > est_hatch | visit_ends < initiation_date,
-                  NA,
-                  NA)),
-         focalMb4h_sc2h = days_guard_b4hatch/as.numeric((est_hatch-initiation_date+1))) %>%
-  ungroup()
-
-clutch_momDays_b4h <- focalMb4h_sc2h %>%
-  group_by(location) %>%
-    summarize(sum_mD = sum(mD, na.rm=T),
-              sum_vD = sum(mD*!mom_at_init, na.rm=T),
-              sum_gD = sum(mD*mom_at_init, na.rm=T),
-              vDb4h_sc2h = sum(days_guard_b4hatch*!mom_at_init, na.rm = T)/
-                # scale to init-hatch interval so clutches with different intervals are comparable 
-                as.numeric(first(est_hatch)-first(initiation_date)+1),
-              gDb4h_sc2h = sum(days_guard_b4hatch*mom_at_init, na.rm = T)/
-                as.numeric((first(est_hatch)-first(initiation_date)+1)),
-              mDb4h_sc2h = sum(days_guard_b4hatch, na.rm = T)/
-                as.numeric((first(est_hatch)-first(initiation_date)+1))) %>%
-  ungroup()
-
-clutch_status_momDays_b4h <- visited_1st_4d_data_tb %>%
-  distinct(location, initiation_date, hatch_date, num_at_init,
-           females_removed, ants_removed, egg_fate, egg_fate_date,
-           max_egg_num, max_egg_len, `visited in 4 days`) %>%
-  right_join(clutch_momDays_b4h, by=c("location")) %>%
-  left_join(top5eggs_summary)
-```
-
-## 11.3 - Latest desertion
-```{r}
-first_visit_cuts <- visited_1st_4d_data_tb %>%
-  filter(!mom_at_init, visit_starts > initiation_date) %>%
-  arrange(location, visit_starts) %>%
-  group_by(location) %>%
-  slice_head(n=1) %>%
-  summarize(first_visit_starts = ifelse(num_at_init > 1, 0, as.numeric(visit_starts-initiation_date))) %>%
-  mutate(first_visit_cut = cut(first_visit_starts, breaks=seq(0,40,4)))
-
-moms_plant_data <- visited_1st_4d_data %>%
-  filter(!is.na(initiation_date)) %>%
-  separate(location, "_", into=c("DormPlant","Leaf")) %>%
-  group_by(DormPlant) %>%
-  summarize(n_moms_alltime = n(),
-            n_moms_leaf_H = sum(est_rel2h>=0, na.rm=T),
-            any_moms_leaf_H = any(est_rel2h>=0, na.rm=T),
-            last_visit_ends_P = max(visit_ends, na.rm=T),
-            n_moms_P_H = sum((last_visit_ends_P-est_hatch)>=0, na.rm=T),
-            any_moms_P_H = any((last_visit_ends_P-est_hatch)>=0, na.rm=T),
-            n_moms_P_8afterH = sum((last_visit_ends_P-est_hatch+8)>=0, na.rm=T),
-            any_moms_P_8afterH = sum((last_visit_ends_P-est_hatch+8)>=0, na.rm=T),
-            n_clutches_on_plant = first(n_clutches_on_plant)) %>%
-  ungroup()
-
-latest_desertions <- visited_1st_4d_data %>%
-  filter(!is.na(initiation_date),
-         !(visit_ends<initiation_date), # visits that end before initiation are irrelevant
-         !(visit_starts>est_hatch+4)) %>% # there are a few cases where clutches are visited long after hatching, which wouldn't affect hatching success
-  left_join(first_visit_cuts) %>%
-  select(Female_ID:visit_ends, initiation_date, est_hatch, est_rel2h, 
-         `visited in 4 days`, mom_at_init, ants_removed, females_removed) %>%
-  group_by(location) %>%
-  filter(any(mom_at_init)) %>% # remove any clutches where there was no apparent mother at initiation
-  summarize(last_des_rel2h = max(ifelse(visit_starts<=initiation_date, est_rel2h, NA), na.rm=T),
-            first_des_rel2h_init = min(ifelse(mom_at_init, est_rel2h, NA), na.rm=T),
-            last_desert = ifelse(last_des_rel2h>=-2, "after hatch",
-                                 ifelse(last_des_rel2h<=0, "before hatch", NA)),
-            females_removed = first(females_removed),
-            ants_removed = first(ants_removed),
-            `visited in 4 days` = first(`visited in 4 days`),
-            init_desert_early = ifelse(first(first_des_rel2h_init<=-16), "deserted early", "didn't desert early"),
-            est_hatch = first(est_hatch)) %>%
-  ungroup() #%>%
-  # filter(!is.na(`visited in 4 days`)) %>% # E40_9 for some reason didn't get a valid visited in 4 days entry
-  # filter(location!="A23_8") %>% # A23_8 has two moms at init but for some reason not `visited in 4 days`?
-```
-
-## 11.4 - Combined table of guarding tenures and offspring counts
-```{r}
-#### combine the three (but after getting more comfortable with the "latest_desertions" results I can omit the initL/S for simplicity)
-clutch_egg_num_data <- latest_desertions %>%
-  left_join(initMb4h_tbL) %>%
-  left_join(initMb4h_tbS) %>%
-  separate(location, sep = "_", into = c("DormPlant"),  remove = FALSE, extra = "drop") %>%
-  left_join(select(clutch_status_momDays_b4h, location, sum_mD, sum_vD, sum_gD,
-                   mDb4h_sc2h, gDb4h_sc2h, vDb4h_sc2h, max_egg_num, max_egg_len,
-                   `visited in 4 days`)) %>%
-  # if tbL and tbS are not the same female, add the female that lost the tie-break to the total sum of visit days
-  mutate(sum_vD_initL = ifelse(initiator_tbL!=initiator_tbS,
-                           sum_vD+init_durS, sum_vD),
-         sum_vD_initS = ifelse(initiator_tbS!=initiator_tbL,
-                           sum_vD+init_durL, sum_vD),
-         visited = vDb4h_sc2h > 0,
-         pmDvD = vDb4h_sc2h/mDb4h_sc2h) %>%
-  left_join(top5eggs_summary) %>%
-  select(location, last_des_rel2h, first_des_rel2h_init,
-         ants_removed, females_removed, initiation_date, est_hatch, `visited in 4 days`,
-         sum_mD, sum_vD, sum_gD, mDb4h_sc2h,
-         num_at_init, init_desert_early, last_desert,
-         n_eggs = max_egg_num, med_t5eggs, mean_t5eggs, max_n_eggs,
-         max_egg_len, med_l_t5eggs, mean_l_t5eggs, max_l_eggs,
-         init_durL, init_durS, desert_rel2hL, desert_rel2hS,
-         sum_vD_initL, sum_vD_initS, initMb4h_sc2hL, initMb4h_sc2hS,
-         initiator_tbL, initiator_tbS,
-         n_clutches_on_plant, visited, pmDvD, DormPlant)
-
-# add filtered and curated nymph and adult counts
-clutch_survivorship_data <- clutch_egg_num_data %>%
-  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2,
-                   -c(ants_removed, females_removed, initiation_date, n_eggs)),
-            by=c("location"="NOr_rev_loc"))
-```
-
-# 12 - Write data for `Publilia-03-survivorship.Rmd` to `.rds` for further analysis in clean environment
-
-## 12.0 - Combine all data for regressions
-```{r}
-surv_reg_data <- clutch_survivorship_data %>% 
-  filter(!is.na(`visited in 4 days`)) %>%
-  select(location, med_t5eggs, n_hatched, n_survived,
-         des=last_des_rel2h, ants_removed, vis=`visited in 4 days`,
-         females_removed, initiation_date, est_hatch) %>%
-  mutate(n_survived = ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
-                             n_hatched, n_survived), # force n_survived/n_hatched=1
-         ant_treatment=ifelse(ants_removed, "Removed", "Control")) %>%
-  left_join(select(ant_counts, location, 
-                   ever_antsP_b4h, ever_antsP_afh, ever_antsP)) %>%
-  mutate(ants_b4h=ifelse(ever_antsP_b4h," ever", " never"),
-         ants_afh=ifelse(ever_antsP_afh," ever"," never"),
-         ants_ever=ifelse(ever_antsP," ever"," never")) %>%
-  left_join(select(ant_n_days, -ants_everP, -ant_treatment, -females_removed)) %>%
-  mutate(ants_gt2d=ifelse(antsP_gt2d," ants", " no ants"),
-         ants_gt3d=ifelse(antsP_gt3d," ants", " no ants")) %>% 
-  separate(location, into = c("DormPlant", "Leaf"), sep="_", remove=FALSE) %>%
-  left_join(dplyr::select(moms_plant_data, DormPlant, last_visit_ends_P), by="DormPlant") %>%
-  mutate(last_desP_rel2h = last_visit_ends_P-est_hatch,
-         desP = last_desP_rel2h) 
-```
-
-## `Publilia-03-survivorship.Rmd`
-```{r}
-write_rds(surv_reg_data, here("saved_rds/surv_reg_data.rds"))
-```
+# 6 - Saving data for downstream analysis

### 2023-08-24 scripts/old/Publilia_2019_CHAPTER-1-strategies.Rmd
added old scripts to `scripts/old/` for reference

--- 2023-07-23 scripts/Publilia-02-strats.Rmd
@@
 ---
-title: '01 - TreehopperFitness: Defining strategies and calculating frequencies'
-author: "Micah Fletcher"
-date: '`r Sys.Date()`'
-output: 
-  rmdformats::robobook:
-  fig_width: 9
-toc_depth: 3
+title: "Publilia_2019_CHAPTER-1-strategies"
+author: "micah fletcher"
+date: "1/18/2022"
+output: html_document
 ---
 
-```{r, include=FALSE}
-knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
-                      fig.width = 8, fig.height = 6)
-
-library(kableExtra)   ## Needed if rendering tables
-```
-
-```{=html}
-<style type="text/css">
-  .book .book-body .page-inner {
-    max-width: 1600px;
-    margin-left: auto;
-    margin-right: auto;
-  }
-details > summary {
-  display: list-item;
-}
-</style>
+```{r setup, include=FALSE}
+knitr::opts_chunk$set(echo = TRUE)
 ```
@@
 # Publilia 2019 Chapter - Script 1: guarding strategies
+This is meant to consolidate previous scripts and provide a readable and reproducible record of the analyses for the Publilia Chapter.
+
+(See `Publilia_2019_CHAPTER-0-prep.Rmd` for the full outline of the chapter)
+1) *Guarding strategies:* Three distinct strategies for maternal care emerge from ant-dependent and secondary visitor-dependent plasticity
+  - *Dataset A* requirements:
+    - Guarding durations (relative to [estimated] hatching) are accurate.
+      - The sample of clutches is representative of the full factorial of ants / no ants and visited early / not visited early
+    - Able to compare 
+      - initiated vs. visited
+      - first vs. later [initiated] clutches
+        -however, if plotting "all clutches" I can include unmarked females
+      - disappeared vs. deserted (based on last day a female was observed)
+    - Deciding on who is the "true" initiator is necessary for assumptions of independence for statistics. 
+      - Ultimately, comparing the two most obvious options (first and longest guarding mom at initiation, vs first and shortest guarding mom at initiation) will need to suffice.
+Missing data is clearly represented; Compare the "original" unfiltered data to the final data and report why (and how many) data were excluded.
 
@@
 library(tidyverse)
-library(lubridate)
 library(ggpubr)
-library(ggh4x)
 library(rstatix)
@@
 library(effectsize)
+
 library(gt)
 library(gtsummary)
+library(flextable)
 theme_gtsummary_compact()
-library(flextable)
+
 library(multcompView)
-library(here)
 
@@
 # 0 - Data import
-
 clutch_status_guarding_summary_v2
 ```{r}
-All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))
-clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
-last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))
+setwd("/Users/micah/Documents/Princeton/Kocher_Lab/Publilia/PubliliaBehavEcol/Watershed_2019/Watershed_2019_analysis/CHAPTER")
+
+# clutch_status_guarding_summary_v2 <- read_csv("../Publilia_2019_ABS_talk_analysis_data/clutch_status_guarding_summary_v2")
+# last_day_fID <- read_csv("../Publilia_2019_ABS_talk_analysis_data/last_day_fID")
 
@@
 paste("Including these missing females in the analysis reveals...")
-```
-
-# 2 - When were females visited on their first clutch?
+
+```
+
+# 2 - Histograms and related stats
 First I need to know when females were visited on their first clutch.
@@
 
-# 3 - Defining exposure to ants
-
-## 3.1 - Ant counts on plant; some ants_removed clutches were visited by ants, and vice versa
+# Ant counts on plant; some ants_removed clutches were visited by ants, and vice versa
 ```{r}
@@
 
-## 3.2 - Ant arrival times
+ant arrival times
 ```{r}
@@
   stat_summary(fun=mean, geom="point", shape=4, size=3)
-```
-
-# 4 - Figure 1: Histograms of guarding tenure
-
-## 4.1 Using observed presence of ants as ants treamment
-
-Two proxies:
-
-1. ants ever observed on plant before hatch `hatchever_antsP_b4h` or 
-2. ants ever observed on plant after hatch `ever_antsP_afh`
-
-### Not visited early
+
+```
+
 ```{r}
@@
                 color = "gray", size=1)
-```
-
-### Visited early
-```{r}
+
+## Visited early
 # ever ants b4h
@@
 
-## 4.2 - Using ant treatment (not observed presence)
-
-#### Desertion relative to hatch
+## Figure 1:
 Using geom_area and density
@@
 
-# strat_data_table1 %>%
-#   as_flex_table() %>%
-#   flextable::save_as_docx(path=here("prelim_figs/strat_data_table1.docx"))
+strat_data_table1 %>%
+  as_flex_table() %>%
+  flextable::save_as_docx(path="strat_data_table1.docx")
 
@@
 
-# strat_data_table2 %>%
-#   as_flex_table() %>%
-#   flextable::save_as_docx(path=here("prelim_figs/strat_data_table2.docx"))
+strat_data_table2 %>%
+  as_flex_table() %>%
+  flextable::save_as_docx(path="strat_data_table2.docx")
 
@@
 
-#### Guarding duration instead of relative guarding duration
+Guarding duration instead of relative guarding duration
 ```{r}
@@
 
-## 4.3 - Dealing with non-independence of multi-initiators: Using only longest or shortest initiator
+*Dealing with non-independence of multi-initiators: Using only longest or shortest initiator*
 Sample sizes
@@
 
-## 4.4 - How does including the females that were never observed again affect the results?
-
+### How does including the females that were never observed again affect the results? 
 This will fix the unequal sample sizes for the tie-breaking but will it introduce undue spurious observations?
 
-### No tie-breaking.
+No tie-breaking.
 ```{r}
@@
 ```
-
-### Longest initiators only
+Longest initiators only
 ```{r}
@@
 ```
-
-### Shortest initiators only
+Shortest initiators only
 ```{r}
@@
 
-## Figure 2: Are early-visited females more likely to desert early?
-
+## Figure 2
+*Are early-visited females more likely to desert early?*
 Note that the observations for Day 0 are not independent because they come from two (or more) females on the same clutch.
@@
 When (if) running stats, I can include only the "longest initiator" or "shortest initiator" to satisfy independence and then compare the results of the two options.
-
 ```{r}
@@
 
-# 5 - Collecting plots of alternative filtering methods, try stats for v5
+*Collecting combined plots*
 The key thing to note is that nothing really changes substantially in all of the histograms except that 
@@
 
-## 5.1 Longest initiators only, disappeared females excluded (i.e. v5)
+*Longest initiators only, disappeared females excluded*
 But is this too strong an assumption? I just need to discuss the differences between longest and shortest tie-breaks, but I can just show the longest I think.
@@
 ```
-
-## 5.2 Stats
-### Check Assumptions
+# Stats
+#### Check Assumptions
 - SDs not equal: ranges from 16.4 to 36.6, but passes levene test for homogeneity of variance
@@
 
-### Parametric stats v5
+#### Computation
 Desertion category was significant but not ants or interaction.
@@
 
-### Parametric stats v1
+#### Computation
+v1
 ```{r}
@@
 
-### Parametric stats v2
+#### Computation
+v2
 ```{r}
@@
 
-### Non-parametric stats: v1
+#### Non-parametric version
 ```{r}
@@
 
-### Non-parametric stats, but including females that disappeared or were unmarked
+#### Non-parametric version, but including females that disappeared or were unmarked
 Three clutches were omitted from the analysis. Two were visited after hatching, and one had no females present at initiation.
@@
 
-# ggsave(here("prelim_figs/guard_dur.vs.first_visit.v2.png"),
-#        vis_start.vs.guard_dur.v2.stats.nonpara.p,
-#        device = "png",
-#        width = 160, height = 120, units = "mm", dpi = "print")
-```
-
-# 6 Comparing early desertion by initiator vs. latest desertion of leaf by any female vs. latest desertion of the plant by any female
+ggsave("guard_dur.vs.first_visit.v2.png",
+       vis_start.vs.guard_dur.v2.stats.nonpara.p,
+       device = "png",
+       width = 160, height = 120, units = "mm", dpi = "print")
+```
+
+### Comparing early desertion by initiator vs. latest desertion of leaf by any female vs. latest desertion of the plant by any female
 ```{r}
@@
 
-# ggsave(here("prelim_figs/des_vs_desL_vs_desP.png"),
-#        des.vs.desL.vs.desP.p,
-#        device = "png",
-#        width = 240, height = 120, units = "mm", dpi = "print")
+ggsave("des_vs_desL_vs_desP.png",
+       des.vs.desL.vs.desP.p,
+       device = "png",
+       width = 240, height = 120, units = "mm", dpi = "print")
 
@@
 
-# ggsave(here("prelim_figs/des_vs_desL_vs_desP.v2.png"),
-#        des.vs.desL.vs.desP.v2.p,
-#        device = "png",
-#        width = 240, height = 120, units = "mm", dpi = "print")
-```
-
-# 7 - Save selected figures and stats for chapter
-
+ggsave("des_vs_desL_vs_desP.v2.png",
+       des.vs.desL.vs.desP.v2.p,
+       device = "png",
+       width = 240, height = 120, units = "mm", dpi = "print")
+```
+
+### Save selected figures for chapter
 I will use the original filtering because I feel it best represents the complexity of the data without making too stringent or tenuous assumptions.
@@
 
-## 7.1 Figures
-
-### Main
-```{r}
-(desertion_firstclutch_hist <- Fig1_v1AB)
-(guard_dur.vs.first_visit <- Fig1_v1D.stats.nonpara)
-
-# ggsave(here("prelim_figs/desertion_firstclutch_hist.png"),
-#        desertion_firstclutch_hist,
-#        device = "png",
-#        width = 120, height = 140, units = "mm", dpi = "print")
-# 
-# ggsave(here("prelim_figs/guard_dur.vs.first_visit.png"),
-#        guard_dur.vs.first_visit,
-#        device = "png",
-#        width = 160, height = 120, units = "mm", dpi = "print")
-# 
-# ggsave(here("prelim_figs/desertion_firstclutch_hist_v2.png"), # include females that disappeared
-#        Fig1_v2AB,
-#        device = "png",
-#        width = 120, height = 140, units = "mm", dpi = "print")
-```
-
-### Supplement
-```{r}
-(duration_firstclutch_hist <- Fig1_v1ABC.gd)
-# ggsave(here("prelim_figs/duration_firstclutch_hist.png"),
-#        duration_firstclutch_hist,
-#        device = "png",
-#        width = 120, height = 180, units = "mm", dpi = "print")
-```
-
-## 7.2 Stats for text
-
-### Females on their first clutch
-
+Main
+```{r}
+desertion_firstclutch_hist <- Fig1_v1AB
+guard_dur.vs.first_visit <- Fig1_v1D.stats.nonpara
+
+ggsave("desertion_firstclutch_hist.png",
+       desertion_firstclutch_hist,
+       device = "png",
+       width = 120, height = 140, units = "mm", dpi = "print")
+
+ggsave("guard_dur.vs.first_visit.png",
+       guard_dur.vs.first_visit,
+       device = "png",
+       width = 160, height = 120, units = "mm", dpi = "print")
+
+ggsave("desertion_firstclutch_hist_v2.png", # include females that disappeared
+       Fig1_v2AB,
+       device = "png",
+       width = 120, height = 140, units = "mm", dpi = "print")
+```
+
+Supplement
+```{r}
+duration_firstclutch_hist <- Fig1_v1ABC.gd
+ggsave("duration_firstclutch_hist.png",
+       duration_firstclutch_hist,
+       device = "png",
+       width = 120, height = 180, units = "mm", dpi = "print")
+```
+
+### Stats for text
 In the control treatment, where ants had free access to females and their clutches, females tended to desert their first clutch either within a few days of initiating them (mode = 0-3 days after first eggs, n = 12) or within a few days of the first nymphs hatching (mode = 0-3 days after first nymphs, n = 19).
 For clutches where ants were excluded, some females also deserted their eggs within the first few days of initiation (mode = 0-3 days after first eggs, n = 11) but those that remained tended to desert well after hatching (mode = 12-15 days after first nymphs, n = 11).
-
 ```{r}
@@
   count(clutch_initiated_order == 1)
-print(paste("% (not removed) females that started the season by visiting an existing clutch:", 36/151*100))
-print(paste("% (not removed) females that started by initiating their own clutch:", 115/151*100))
+36/115
 
@@
 
-### After the first clutch
+#### After the first clutch
 No tie-breaking.
@@
 
-# Figures for FPO
+### Figures for FPO
 ```{r}
@@
 
-# ggsave(here("prelim_figs/FPO_freqpoly_all.png"), FPO_freqpoly_all,
-#        device = "png", width = 120, height = 80, units = "mm", dpi = "print")
+ggsave("FPO_freqpoly_all.png", FPO_freqpoly_all,
+       device = "png", width = 120, height = 80, units = "mm", dpi = "print")
 
@@
 
-# ggsave(here("prelim_figs/FPO_freqpoly_noVis_all.png"), FPO_freqpoly_noVis_all,
-#        device = "png", width = 120, height = 80, units = "mm", dpi = "print")
+ggsave("FPO_freqpoly_noVis_all.png", FPO_freqpoly_noVis_all,
+       device = "png", width = 120, height = 80, units = "mm", dpi = "print")
 
@@
 
-# ggsave(here("prelim_figs/FPO_freqpoly_noVis_black.png"), FPO_freqpoly_noVis_black,
-#        device = "png", width = 120, height = 80, units = "mm", dpi = "print")
+ggsave("FPO_freqpoly_noVis_black.png", FPO_freqpoly_noVis_black,
+       device = "png", width = 120, height = 80, units = "mm", dpi = "print")
 
@@
 ```
-
-# 2023.07.22 - Using geom_ridgeline instead of freq_poly with alpha
-
-## Original from chapter:
-```{r, fig.width=3, fig.height=3}
-Fig1_v1_data <- visited_1st_4d_data %>%
-  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
-         clutch_initiated_order == 1, visit_ends < last_day_fID)
-
-strat_data_table1 <- visited_1st_4d_data %>%
-  mutate(`Ant exclusion` = ifelse(ants_removed, "Ants excluded", "Control"),
-         `Females not removed (A)` = !females_removed,
-         `Leaf hosted a clutch (B)` = !is.na(initiation_date),
-         `Neither (!A&!B)` = `Females not removed (A)`&`Leaf hosted a clutch (B)`) %>%
-  select(`Ant exclusion`, `Females not removed (A)`, `Leaf hosted a clutch (B)`,
-         `Neither (!A&!B)`) %>%
-  tbl_summary(by=`Ant exclusion`)
-
-Fig1_v1A <- ggplot(data = filter(Fig1_v1_data, `visited in 4 days` == "Not visited")) +
-  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
-            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
-  theme_publilia() +
-  xlab("Desert date relative to hatching") +
-  ylab("Proportion of females") +
-  scale_color_manual(values = c("black", "brown1")) +
- scale_fill_manual(values = c("black", "brown1")) +
-  geom_vline(xintercept = -20, linetype="dotted", 
-                color = "gray", size=1) +
-  geom_vline(xintercept = 0, linetype="dashed", 
-                color = "gray", size=1)
-
-Fig1_v1B <- ggplot(data = filter(Fig1_v1_data, `visited in 4 days` == "Visited")) +
-  geom_area(aes(x = est_rel2h, y=..density.., color = ants, fill = ants), 
-            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
-  theme_publilia() +
-  xlab("Desert date relative to hatching") +
-  ylab("Proportion of females") +
-  scale_color_manual(values = c("black", "brown1")) +
- scale_fill_manual(values = c("black", "brown1")) +
-  geom_vline(xintercept = -20, linetype="dotted", 
-                color = "gray", size=1) +
-  geom_vline(xintercept = 0, linetype="dashed", 
-                color = "gray", size=1)
-
-(Fig1_v1AB <- ggpubr::ggarrange(Fig1_v1A +
-            theme(legend.justification = c(1,1),
-                  legend.position = "none") +
-            xlim(-30,34),
-         Fig1_v1B + 
-           theme(legend.justification = c(1,1),
-                 legend.position = c(0.95,0.95)) +
-            xlim(-30,34),
-         align = "v",
-         labels = c("A", "B"),
-         ncol = 1, nrow = 2))
-```
-
-## New version
-### Relative desert date
-```{r, fig.width=3, fig.height=3}
-visit_colors <- rev(unique(ggplot_build(Fig1_v1D)$data[[1]]$fill))
-
-hist_strips <- strip_nested(
-     # Horizontal strips
-     background_y = list(
-       element_rect(fill = visit_colors[1]), 
-       element_rect(fill = visit_colors[2]), 
-       element_blank(), element_blank(), 
-       element_blank(), element_blank()),
-     text_y = list(
-       element_text(color = c("black")), 
-       element_text(color = c("black")), 
-       element_blank(), element_blank(), 
-       element_blank(), element_blank()),
-     by_layer_y = FALSE
-)
-
-base_text <- expand.grid(ants = c("Ants removed", "Control"),
-            `visited in 4 days` = c("Not visited within first 4 days", 
-                                    "Visited within first 4 days")) %>%
-  tibble()
-
-init_text <- base_text %>%
-  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited within first 4 days", 
-         "Mean init. date", 
-         ""))
-
-hatch_text <- base_text %>%
-  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited within first 4 days", 
-         "Hatch date", 
-         ""))
-
-visited_1st_4d_data %>%
-  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
-         clutch_initiated_order == 1, visit_ends < last_day_fID) %>% 
-  filter(!is.na(`visited in 4 days`)) %>%
-  mutate(`visited in 4 days` = 
-           ifelse(`visited in 4 days` == "Visited", 
-                  "Visited within first 4 days", 
-                  "Not visited within first 4 days")) %>%
-  ggplot(aes(x=est_rel2h, fill=ants)) +
-  geom_histogram(binwidth = 4) +
-  theme_publilia() +
-  xlab("Desert date relative to hatching") +
-  ylab("Number of females") +
-  scale_y_continuous(breaks = c(0,4,8),
-                     labels = label_number(accuracy = 1)) +
-  scale_color_manual(values = c("black", "brown1")) +
-  scale_fill_manual(values = c("black", "brown1")) +
-  geom_vline(xintercept = -20, linetype="dotted", 
-                color = "gray", size=1) +
-  geom_vline(xintercept = 0, linetype="dashed", 
-                color = "gray", size=1) +
-  ggh4x::facet_grid2(vars(`visited in 4 days`, ants), 
-                     strip = hist_strips) +
-  theme(strip.background = element_rect(color = NA),
-        legend.justification = c(1,1),
-        legend.position = c(1,0.2)) +
-  geom_text(data = init_text,
-            aes(x = -20, y = 10, label = label),
-            hjust = 0, vjust = -1, color = "gray", fontface = "bold") +
-  geom_text(data = hatch_text,
-            aes(x = 0, y = 10, label = label),
-            hjust = 0, vjust = -1, color = "gray", fontface = "bold") +
-  coord_cartesian(clip = "off")
-```
-
-### Guarding duration
-```{r, fig.width=3, fig.height=3}
-visit_colors <- rev(unique(ggplot_build(Fig1_v1D)$data[[1]]$fill))
-
-hist_strips <- strip_nested(
-     # Horizontal strips
-     background_y = list(
-       element_rect(fill = visit_colors[1]), 
-       element_rect(fill = visit_colors[2]), 
-       element_blank(), element_blank(), 
-       element_blank(), element_blank()),
-     text_y = list(
-       element_text(color = c("black")), 
-       element_text(color = c("black")), 
-       element_blank(), element_blank(), 
-       element_blank(), element_blank()),
-     by_layer_y = FALSE
-)
-
-base_text <- expand.grid(ants = c("Ants removed", "Control"),
-            `visited in 4 days` = c("Not visited\nwithin first 4 days", 
-                                    "Visited\nwithin first 4 days")) %>%
-  tibble()
-
-hatch_text <- base_text %>%
-  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited\nwithin first 4 days", 
-         "Hatch date", 
-         ""))
-
-(guarding_durations_plot_2023 <- visited_1st_4d_data %>%
-  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
-         clutch_initiated_order == 1, visit_ends < last_day_fID) %>% 
-  filter(!is.na(`visited in 4 days`)) %>%
-  mutate(`visited in 4 days` = 
-           ifelse(`visited in 4 days` == "Visited", 
-                  "Visited\nwithin first 4 days", 
-                  "Not visited\nwithin first 4 days")) %>%
-  ggplot(aes(x=guard_duration, fill=ants)) +
-  geom_histogram(binwidth = 4) +
-  theme_publilia() +
-  xlab("Guarding duration") +
-  ylab("Number of females") +
-  scale_y_continuous(breaks = c(0,4,8),
-                     labels = label_number(accuracy = 1)) +
-  scale_color_manual(values = c("black", "brown1")) +
-  scale_fill_manual(values = c("black", "brown1")) +
-  geom_vline(xintercept = 20, linetype="dashed", 
-                color = "gray", size=1) +
-  ggh4x::facet_grid2(vars(`visited in 4 days`, ants), 
-                     strip = hist_strips) +
-  theme(strip.background = element_rect(color = NA),
-        strip.text = element_text(size = 12),
-        legend.justification = c(1,1),
-        legend.position = c(1,0.2),
-        legend.text = element_text(size = 12)) +
-  geom_text(data = hatch_text,
-            aes(x = 20, y = Inf, label = label),
-            hjust = -0.1, vjust = 0, color = "gray", fontface = "bold") +
-  coord_cartesian(clip = "off"))
-```
-
-# 2023.07.22 - Using geom_ridgeline instead of freq_poly with alpha
-Sarah asked to remove the stats text
-```{r, fig.width=3, fig.height=2}
-Fig1_v1D +
-  xlab("Day first visited (days from initiation)") +
-  ylab("Guard duration of initiating female") +
-    theme(legend.position = "none")
-```

### 2023-08-24 scripts/old/Publilia_2019_CHAPTER-2A-fecundity-modeling.Rmd
added old scripts to `scripts/old/` for reference

---
title: "Publilia_2019_CHAPTER-2A-fecundity-model"
author: "micah fletcher"
date: "1/18/2022"
output: html_document
---

# Publilia 2019 Chapter - Script 2A: modeling fecundity
This is meant to consolidate previous scripts and provide a readable and reproducible record of the analyses for the Publilia Chapter.

2) *Fecundity:* No support for trade-off between current care and future fecundity
  - *Dataset B [supp: modeling fecundity ~ guarding]* requirements:
    - Guarding durations of ALL females that visited a clutch are accurate.
      - Cannot exclude any females, including unmarked or ambiguously marked females, because I need them for the sum of guarding time.
    - Maximum number of eggs per clutch is accurate.
    - Can partition 
      - early clutches vs. later clutches
      - single-mother clutches vs. multiple-mother clutches
      - ants vs. no ants
  - *Dataset C [estimating fecundity]* requirements:
    - Guarding durations of ALL females that visited a clutch are accurate.
      - Cannot exclude any females, including unmarked or ambiguously marked females, because I need them for the sum of guarding time.
    - Maximum number of eggs per clutch is accurate.
    - Numbers of clutches per female (and guarding duration and eggs for each) are accurate.
      - Cannot exclude any clutches, including those with ambiguous initiators, or unknown hatch dates
    - Models/heuristics of focal female contribution to clutch are clearly defined and sensible.
      1) simple equal proportion of days
      2) equal proportion of days with "intercept" given to the initiator
      3) unequal proportion of days for initiator(s) vs visitors, with intercept also given to the initiator
      4) Reproducing Zink's fecundity

# 0 - Data import
```{r}
library(MASS)
library(tidyverse)
library(mgcv)
select <- dplyr::select
```

# 1 - Data prep
```{r}
clutch_status_guarding_summary_v2

fec_model_data <- visited_1st_4d_data_tb %>%
  filter(!is.na(guard_duration)) %>%
  group_by(location) %>%
  mutate(eggs_ever_visited = any(!mom_at_init & visit_ends <= est_hatch)) %>%
  ungroup() %>%
  select(Female_ID, location, guard_duration, est_rel2h, initiation_date, est_hatch,
         mom_at_init, clutch_initiated_order, initL, initS,
         visit_starts, visit_ends, last_day_fID,
         num_at_init, n_clutches_on_plant, `visited in 4 days`, eggs_ever_visited, ants,
         females_removed, ants_removed, 
         max_egg_num, egg_fate, egg_fate_date)

fec_model_data %>% filter(females_removed, mom_at_init) %>% nrow()
fec_model_data %>% filter(females_removed, mom_at_init) %>% count(eggs_ever_visited)
fec_model_data %>% filter(females_removed, mom_at_init) %>% count(eggs_ever_visited, visit_ends==last_day_fID)

ggplot(data=filter(fec_model_data, females_removed, mom_at_init, visit_ends==last_day_fID), 
       aes(x=guard_duration, y=max_egg_num)) +
  geom_point(aes(color=eggs_ever_visited | num_at_init>1), size = 4, alpha = 0.50) +
  theme(legend.position = "bottom")

ggplot(data=filter(fec_model_data, mom_at_init, visit_ends==last_day_fID), 
       aes(x=guard_duration, y=max_egg_num, color=eggs_ever_visited | num_at_init>1)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth() +
  theme(legend.position = "bottom")

ggplot(data=filter(fec_model_data, mom_at_init, visit_ends==last_day_fID, 
                   initiation_date<as_date("2019-06-15")), 
       aes(x=guard_duration, y=max_egg_num, color=eggs_ever_visited | num_at_init>1)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth() +
  theme(legend.position = "bottom")

ggplot(data=filter(fec_model_data, mom_at_init, visit_ends==last_day_fID,
                   initiation_date<as_date("2019-06-15")), 
       aes(x=guard_duration, y=max_egg_num, 
           color=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1,
           fill=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth() +
  theme(legend.position = "bottom")

ggplot(data=filter(fec_model_data, females_removed, mom_at_init, visit_ends==last_day_fID,
                   initiation_date<as_date("2019-06-15")), 
       aes(x=guard_duration, y=max_egg_num, 
           color=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1,
           fill=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth() +
  theme(legend.position = "bottom")

ggplot(data=filter(fec_model_data, females_removed, mom_at_init, visit_ends==last_day_fID,), 
       aes(x=guard_duration, y=max_egg_num, 
           color=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1,
           fill=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=lm) +
  theme(legend.position = "bottom")

ggplot(data=filter(fec_model_data, females_removed, mom_at_init, visit_ends==last_day_fID,
                   !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)), 
       aes(x=guard_duration, y=max_egg_num, 
           color=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1,
           fill=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=lm) +
  theme(legend.position = "bottom")
```

```{r}
# plotting the actual number of eggs over time to look for outliers
fec_model_data %>% filter(females_removed, mom_at_init, visit_ends==last_day_fID,
                   !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
         filter(guard_duration<7, max_egg_num>60)

clutch_status_init_hatch_labels_v1 %>% filter(location == "D77_11") %>% print(n=Inf) # this is definitely an outlier!
ggplot(clutch_status_init_hatch_labels_v1 %>% filter(location == "D77_11", !is.na(egg_num)),
       aes(x=Date,y=egg_num)) +
  geom_point() +
  geom_smooth()

clutch_status_init_hatch_labels_v1 %>% filter(location == "G32_8") %>% print(n=Inf) # this is definitely an outlier!
ggplot(clutch_status_init_hatch_labels_v1 %>% filter(location == "G32_8", !is.na(egg_num)),
       aes(x=Date,y=egg_num)) +
  geom_point() +
  geom_smooth()

clutch_status_init_hatch_labels_v1 %>% filter(location == "G55_9") %>% print(n=Inf) # this is definitely an outlier!
ggplot(clutch_status_init_hatch_labels_v1 %>% filter(location == "G55_9", !is.na(egg_num)),
       aes(x=Date,y=egg_num)) +
  geom_point() +
  geom_smooth()

clutch_status_init_hatch_labels_v1 %>% filter(location == "G67_10") %>% print(n=Inf) # this is definitely an outlier!
ggplot(clutch_status_init_hatch_labels_v1 %>% filter(location == "G67_10", !is.na(egg_num)),
       aes(x=Date,y=egg_num)) +
  geom_point() +
  geom_smooth()

clutch_status_init_hatch_labels_v1 %>% filter(location == "H19_8") %>% print(n=Inf) # this is definitely an outlier!
ggplot(clutch_status_init_hatch_labels_v1 %>% filter(location == "H19_8", !is.na(egg_num)),
       aes(x=Date,y=egg_num)) +
  geom_point() +
  geom_smooth()

# This stuff takes too long to run
# clutch_status_init_hatch_labels_v1 %>%
#   filter(grepl("H",location), !is.na(egg_num)) %>%
#   ggplot(aes(x=Date,y=egg_num)) +
#   geom_point() +
#   geom_smooth() +
#   facet_wrap(vars(location))
#   
# clutch_status_init_hatch_labels_v1 %>%
#   filter(grepl("G",location), !is.na(egg_num)) %>%
#   ggplot(aes(x=Date,y=egg_num)) +
#   geom_point() +
#   geom_smooth() +
#   facet_wrap(vars(location))
# 
# clutch_status_init_hatch_labels_v1 %>%
#   filter(grepl("A",location), !is.na(egg_num)) %>%
#   ggplot(aes(x=Date,y=egg_num)) +
#   geom_point() +
#   geom_smooth() +
#   facet_wrap(vars(location))
# 
# clutch_status_init_hatch_labels_v1 %>%
#   filter(grepl("B",location), !is.na(egg_num)) %>%
#   ggplot(aes(x=Date,y=egg_num)) +
#   geom_point() +
#   geom_smooth() +
#   facet_wrap(vars(location))
# 
# clutch_status_init_hatch_labels_v1 %>%
#   left_join(fec_model_data) %>%
#   filter(females_removed, mom_at_init, visit_ends==last_day_fID,
#          !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1), 
#          !is.na(egg_num)) %>%
#   ggplot(aes(x=Date,y=egg_num)) +
#   geom_point() +
#   geom_smooth() +
#   facet_wrap(vars(location))
# 
# clutch_status_init_hatch_labels_v1 %>%
#   left_join(fec_model_data) %>%
#   filter(mom_at_init, visit_ends==last_day_fID,
#          !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1), 
#          !is.na(egg_num)) %>%
#   ggplot(aes(x=Date-initiation_date,y=egg_num)) +
#   geom_point() +
#   geom_smooth(color="black",se=F) +
#   facet_wrap(vars(location)) +
#   theme(legend.position="bottom")
# 
# clutch_status_init_hatch_labels_v1 %>%
#   left_join(fec_model_data) %>%
#   filter(mom_at_init, visit_ends==last_day_fID,
#          eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1, 
#          !is.na(egg_num)) %>%
#   ggplot(aes(x=Date-initiation_date,y=egg_num)) +
#   geom_point() +
#   geom_smooth(color="purple",se=F) +
#   facet_wrap(vars(location)) +
#   theme(legend.position="bottom")

```

taking the median (or mean) of the top 4 egg_num counts yields an estimate of max egg num that is more robust to outliers/miscounts
```{r}
# can I deal with outliers by taking the median of the max 3 points for each clutch?
tmp_t5eggs_data <- clutch_status_init_hatch_labels_v1 %>%
  mutate(est_hatch = as_date(ifelse(is.na(hatch_date),
                                 initiation_date + 20,
                                 hatch_date)),
         clutch_age = as.numeric(Date-initiation_date)) %>%
  # remove duplicate egg counts due to multiple females at a location on a day
  distinct(location, Date, initiation_date, est_hatch, clutch_age,
           egg_num, egg_len) %>%
  group_by(location) %>%
    arrange(desc(egg_num)) %>%
    mutate(top5egg_counts = rank(desc(egg_num), ties.method = "first") <= 5,
           top5egg_lens = rank(desc(egg_len), ties.method = "first") <= 5) %>%
    #filter(location == "A13_11") %>%
    select(location, Date, initiation_date, est_hatch, clutch_age,
           egg_num, egg_len, top5egg_counts, top5egg_lens) %>%
    mutate(med_t5eggs = median(ifelse(top5egg_counts,egg_num,NA), na.rm=T),
           mean_t5eggs = mean(ifelse(top5egg_counts,egg_num,NA), na.rm=T),
           max_n_eggs = max(ifelse(top5egg_counts,egg_num,NA), na.rm=T),
           med_l_t5eggs = median(ifelse(top5egg_lens,egg_len,NA), na.rm=T),
           mean_l_t5eggs = mean(ifelse(top5egg_lens,egg_len,NA), na.rm=T),
           max_l_eggs = max(ifelse(top5egg_lens,egg_len,NA), na.rm=T)) %>%
  ungroup()

tmp_t5eggs_data %>% 
  filter(grepl("B",location), !is.na(egg_num)) %>%
ggplot(data=., 
       aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  geom_hline(aes(yintercept = max_n_eggs), color = "blue") +
  geom_hline(aes(yintercept = med_t5eggs), color = "green") +
  geom_hline(aes(yintercept = mean_t5eggs), color = "red") +
  geom_vline(aes(xintercept = est_hatch-initiation_date), color = "gray", linetype="dotted") +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

top5eggs_summary <- tmp_t5eggs_data %>%
  group_by(location) %>%
    summarize(med_t5eggs = first(med_t5eggs),
              mean_t5eggs = first(mean_t5eggs),
              max_n_eggs = first(max_n_eggs),
              med_l_t5eggs = first(med_l_t5eggs),
              mean_l_t5eggs = first(mean_l_t5eggs),
              max_l_eggs = first(max_l_eggs)) %>%
  ungroup()

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(females_removed, mom_at_init, visit_ends==last_day_fID,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=max_n_eggs, 
           color=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1,
           fill=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) +
  geom_point(size = 4, alpha = 0.50, color="red") +
  geom_smooth(method=lm, color="red", fill="red") +
  geom_point(aes(y=med_t5eggs), size = 4, alpha = 0.50, color="blue") +
  geom_smooth(aes(y=med_t5eggs), method=lm, color="blue", fill="blue") +
  geom_point(aes(y=mean_t5eggs), size = 4, alpha = 0.50, color="green") +
  geom_smooth(aes(y=mean_t5eggs), method=lm, color="green", fill="green") +
  theme(legend.position = "bottom")

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init, visit_ends==last_day_fID,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=max_n_eggs, 
           color=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1,
           fill=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) +
  geom_point(size = 4, alpha = 0.50, color="red") +
  geom_smooth(method=loess, color="red", fill="red") +
  geom_point(aes(y=med_t5eggs), size = 4, alpha = 0.50, color="blue") +
  geom_smooth(aes(y=med_t5eggs), method=loess, color="blue", fill="blue") +
  geom_point(aes(y=mean_t5eggs), size = 4, alpha = 0.50, color="green") +
  geom_smooth(aes(y=mean_t5eggs), method=loess, color="green", fill="green") +
  theme(legend.position = "bottom")

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=max_n_eggs, 
           color=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1,
           fill=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) +
  geom_point(size = 4, alpha = 0.50, color="red") +
  geom_smooth(method=loess, color="red", fill="red") +
  geom_point(aes(y=med_t5eggs), size = 4, alpha = 0.50, color="blue") +
  geom_smooth(aes(y=med_t5eggs), method=loess, color="blue", fill="blue") +
  geom_point(aes(y=mean_t5eggs), size = 4, alpha = 0.50, color="green") +
  geom_smooth(aes(y=mean_t5eggs), method=loess, color="green", fill="green") +
  theme(legend.position = "bottom")

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=max_n_eggs, 
           color=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1,
           fill=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) +
  geom_point(size = 4, alpha = 0.50, color="red") +
  geom_smooth(method=loess, color="red", fill="red") +
  geom_point(aes(y=med_t5eggs), size = 4, alpha = 0.50, color="blue") +
  geom_smooth(aes(y=med_t5eggs), method=loess, color="blue", fill="blue") +
  theme(legend.position = "bottom")

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init, !is.na(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1,
           fill=eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=loess) +
  theme(legend.position = "bottom")
```

basic gam
```{r}
tmp4gam <- fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1))

plot(x=tmp4gam$guard_duration, y=tmp4gam$med_t5eggs)

tmp4gam_mod <- fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
  gam(med_t5eggs ~ s(guard_duration), data=.)

plot(tmp4gam_mod)
```

can I take the slope of each 2-day segment of a loess regression of the egg counts and assign those to the females that were present at the time? that would be more faithful to the estimating I'm trying to do.

it feels elegant, but it also puts too much faith in the individual counts of eggs, especially when you consider the fact that many counts increase even after all females have been removed. how would you account for that? I think that is too presumptuous to pursue with this data full of measurement error
```{r}
tmp_t5eggs_data_loess <- tmp_t5eggs_data %>% 
  filter(grepl("G",location)|grepl("F",location), !is.na(egg_num)) %>%
  #filter(location=="G5_6", !is.na(egg_num)) %>%
  mutate(clutch_age = as.numeric(Date-initiation_date)) %>%
  group_by(location) %>%
  filter(n()>1) %>% # loess cannot be run on a single value of x
  #do(model=loess(egg_num ~ clutch_age, data=.)) %>%
  do(modelr::add_predictions(model=loess(egg_num ~ clutch_age, data=.),
                             data=.)) %>%
  arrange(location,clutch_age) %>%
  mutate(loess_step = pred - lag(pred, order_by=clutch_age))

ggplot(data=tmp_t5eggs_data %>% filter(location=="G69_10", !is.na(egg_num)), 
       aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  geom_hline(aes(yintercept = max_n_eggs), color = "blue") +
  geom_hline(aes(yintercept = med_t5eggs), color = "green") +
  geom_hline(aes(yintercept = mean_t5eggs), color = "red") +
  geom_vline(aes(xintercept = est_hatch-initiation_date), color = "gray", linetype="dotted") +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

ggplot(data=tmp_t5eggs_data_loess %>% filter(location=="G69_10", !is.na(egg_num)), 
       aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  geom_line(aes(x = clutch_age, y = pred), color = "blue") +
  geom_hline(aes(yintercept = med_t5eggs), color = "green") +
  geom_hline(aes(yintercept = mean_t5eggs), color = "red") +
  geom_vline(aes(xintercept = est_hatch-initiation_date), color = "gray", linetype="dotted") +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

#View(tmp_t5eggs_data_loess)

clutch_status_init_hatch_labels_v1 %>%
  left_join(tmp_t5eggs_data_loess)

#plot_clutch_num("G13_6")

```

can I faithfully estimate the egg laying rate of lone females with `mean_t5eggs / visit_ends-initiation_date` and a y-intercept of 0 and initiation_date-1?
```{r}
est_ov_rates <- fec_model_data %>% 
  filter(females_removed, mom_at_init, visit_ends==last_day_fID,
         !(eggs_ever_visited|num_at_init>1)) %>%
  filter(grepl("G",location)|grepl("F",location)) %>%
  left_join(tmp_t5eggs_data_loess) %>%
  distinct(Female_ID, location, mean_t5eggs, visit_ends, initiation_date) %>%
  group_by(location) %>%
  # +1 because this is the number of days the female was present, not the interval
  mutate(est_ov_rate = mean_t5eggs/as.numeric(visit_ends-initiation_date))

fec_model_data %>% 
  filter(females_removed, mom_at_init, visit_ends==last_day_fID,
         !(eggs_ever_visited|num_at_init>1)) %>%
  filter(grepl("G",location)|grepl("F",location)) %>%
  left_join(tmp_t5eggs_data_loess) %>%
ggplot(data=., aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  geom_line(aes(x = clutch_age, y = pred), color = "blue") +
  geom_hline(aes(yintercept = med_t5eggs), color = "green") +
  geom_hline(aes(yintercept = mean_t5eggs), color = "red") +
  geom_vline(aes(xintercept = est_hatch-initiation_date), color = "gray", linetype="dotted") +
  geom_abline(data=est_ov_rates, aes(slope=est_ov_rate,intercept=-1)) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

fec_model_data %>% 
  filter(females_removed, mom_at_init, visit_ends==last_day_fID) %>%
  left_join(tmp_t5eggs_data) %>%
  distinct(Female_ID, location, mean_t5eggs, visit_ends, initiation_date, .keep_all=T) %>%
  group_by(location) %>%
  # +1 because this is the number of days the female was present, not the interval
  mutate(est_ov_rate = mean_t5eggs/as.numeric(visit_ends-initiation_date)) %>%
  ggplot() +
  geom_jitter(aes(y=est_ov_rate, x=eggs_ever_visited|num_at_init>1, group=eggs_ever_visited|num_at_init>1,
    color=eggs_ever_visited|num_at_init>1)) +
  theme(legend.position = "bottom")

```

quickly looking at ovary data
```{r}
# fec_model_data %>% 
#   left_join(tmp_t5eggs_data) %>%
#   distinct(Female_ID, location, mean_t5eggs, visit_ends, initiation_date, .keep_all=T) %>%
#   group_by(location) %>%
#   # +1 because this is the number of days the female was present, not the interval
#   mutate(est_ov_rate = mean_t5eggs/as.numeric(visit_ends-initiation_date)) %>%
#   full_join(ovary_data_w_counts, by = c("Female_ID")) %>%
#   filter(females_removed, mom_at_init, visit_ends==last_day_fID,
#          eggs_ever_visited|num_at_init>1,
#          est_ov_rate<=20) %>%
#   ggplot(data=., 
#          aes(x=n_ovarioles/pronotum_len, y=est_ov_rate)) +
#   geom_point() +
#   geom_smooth(method=lm)
# 
# fec_model_data %>% 
#   left_join(tmp_t5eggs_data) %>%
#   distinct(Female_ID, location, mean_t5eggs, visit_ends, initiation_date, .keep_all=T) %>%
#   group_by(location) %>%
#   # +1 because this is the number of days the female was present, not the interval
#   mutate(est_ov_rate = mean_t5eggs/as.numeric(visit_ends-initiation_date)) %>%
#   full_join(ovary_data_w_counts, by = c("Female_ID")) %>%
#   filter(females_removed, mom_at_init,
#          eggs_ever_visited|num_at_init>1,
#          est_ov_rate<=20) %>%
#   ggplot(data=., 
#          aes(x=n_ovarioles/pronotum_len, y=est_ov_rate)) +
#   geom_point() +
#   geom_smooth(method=lm)

```

# 2 - Dataset B: modeling fecundity ~ guarding (supp)
From draft of text:
The final number of eggs in a clutch was highly correlated with the duration a female guarded them prior to hatching (Figure S2), indicating that females continue to lay eggs over time as they guard them. This pattern holds when females were forcibly removed (Figure S2), confirming that females are not depositing a lump sum of eggs at initiation and staying longer with larger clutches as suggested in other treehoppers (Olmstead and Wood 198X). The sum of all females’ egg-guarding durations was more predictive of final clutch size than egg guarding duration of the initiator alone (Table S1 with alternative models and their AICs), showing that females lay eggs while visiting existing clutches. Many females that started the season by laying in existing clutches went on to initiate their own clutches later in the season (Figure S3).

`The final number of eggs in a clutch was highly correlated with the duration a female guarded them prior to hatching (Figure S2), indicating that females continue to lay eggs over time as they guard them.`

For this I want a model and R^2 value, plus a supplemental figure showing the data with the fitted model. 
 - I want to look at single females with no other visitors interfering or adding eggs of their own. Thus, I use only the females on clutches that were (1) never observed being visited (including multiple initiators), and (2) were alone on the plant (reducing the chance of including undetected visitors). 
 - Clutches from both the control and female removal treatments are included so that we can include more intermediate durations that are rare under control conditions. 
 - Show/mention in some way that ants have no significant effect on these relationships.
```{r}
fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=n_clutches_on_plant>1,fill=n_clutches_on_plant>1)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=loess) +
  theme(legend.position = "bottom")

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=loess) +
  theme(legend.position = "bottom")

t5eggs_gdur_loneFs.data <- fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1))

ggplot(data=t5eggs_gdur_loneFs.data, 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(size = 4, alpha = 0.50) +
  theme(legend.position = "bottom")

t5eggs_gdur_loneFs.lm <- gam(med_t5eggs ~ guard_duration,
                             data = t5eggs_gdur_loneFs.data)
summary(t5eggs_gdur_loneFs.lm)
#visreg(t5eggs_gdur_loneFs.lm, "guard_duration", gg=TRUE)

t5eggs_gdur_loneFs.glm_pois <- glm(med_t5eggs ~ guard_duration, family = poisson,
                             data = t5eggs_gdur_loneFs.data)
summary(t5eggs_gdur_loneFs.glm_pois)
#visreg(t5eggs_gdur_loneFs.glm_pois, "guard_duration", gg=TRUE)

t5eggs_gdur_loneFs.gam_pois <- gam(med_t5eggs ~ s(guard_duration, bs="cr"), family = poisson,
                             data = t5eggs_gdur_loneFs.data)
summary(t5eggs_gdur_loneFs.gam_pois)
plot(t5eggs_gdur_loneFs.gam_pois)
#visreg(t5eggs_gdur_loneFs.gam_pois, "guard_duration", gg=TRUE)
```

`This pattern holds when including only females that were forcibly removed from their clutches (Figure S2), confirming that females are not depositing a lump sum of eggs at initiation and staying longer with larger clutches as suggested in other treehoppers (Olmstead and Wood 198X).`
I'm not certain this is necessary. If I want to demonstrate convincingly that they are depositing eggs over time, I could simply show the plots of different lone females on clutches with egg numbers growing over time?
```{r}
fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init, females_removed, visit_ends==last_day_fID,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=lm) +
  theme(legend.position = "bottom")

# without the potential outliers potentially representing undetected visits
fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init, females_removed, visit_ends==last_day_fID,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1),
         !(guard_duration<7&med_t5eggs>50)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=lm) +
  theme(legend.position = "bottom")

```

`The sum of all females’ egg-guarding durations was more predictive of final clutch size than egg guarding duration of the initiator alone (Table S1 with alternative models and their AICs), showing that females lay eggs while visiting existing clutches.`
```{r}
visited_1st_4d_data_tb
visited_1st_4d_data_tb %>% filter(!is.na(initiation_date))
visited_1st_4d_data_tb %>% filter(!is.na(initiation_date), !is.na(num_at_init))

##### initiator guarding time: mDb4h
initiator_days_b4hatch <- visited_1st_4d_data_tb %>%
  filter(!is.na(initiation_date),
         # exclude clutches for which the initiators are not known
         !is.na(num_at_init),
         mom_at_init) %>%
  group_by(row_number()) %>%
  # Use median init to hatch interval (20 days) to est hatch date of clutch with no hatch date
  mutate(init_dur = ifelse(min(est_hatch, visit_ends) - 
                                       max(initiation_date, visit_starts) >= 0,
                           visit_ends-initiation_date+1, 
                           NA),
         initMb4hatch = ifelse(min(est_hatch, visit_ends) - 
                                       max(initiation_date, visit_starts) >= 0,
           min(est_hatch, visit_ends) - 
           max(initiation_date, visit_starts) + 1,
           ifelse(visit_starts > est_hatch | visit_ends < initiation_date,
                  NA,
                  NA)),
         initMb4h_sc2h = initMb4hatch/as.numeric((est_hatch-initiation_date+1))) %>%
  ungroup()

initMb4h_tbL <- initiator_days_b4hatch %>%
  filter(initL) %>%
  select(location, desert_rel2hL=est_rel2h, init_durL=init_dur, initMb4h_tbL=initMb4hatch, initMb4h_sc2hL=initMb4h_sc2h,
         females_removed, ants_removed, initiation_date, num_at_init,
         initiator_tbL=Female_ID, n_clutches_on_plant)

initMb4h_tbS <- initiator_days_b4hatch %>%
  filter(initS) %>%
  select(location, desert_rel2hS=est_rel2h, init_durS=init_dur, initMb4h_tbS=initMb4hatch, initMb4h_sc2hS=initMb4h_sc2h,
         females_removed, ants_removed, initiation_date, num_at_init,
         initiator_tbS=Female_ID, n_clutches_on_plant)

##### proportional time: mDb4h
clutch_momDays_b4h <- visited_1st_4d_data_tb  %>%
  # exclude visits to leaves that never had eggs; only interested in clutches
  filter(!is.na(initiation_date),
         # exclude clutches for which the initiators are not known (why?)
         !is.na(num_at_init)) %>%
  group_by(row_number()) %>%
  # Use median init to hatch interval (20 days) to est hatch date of clutch with no hatch date
  mutate(mD = ifelse(min(est_hatch, visit_ends) - 
                                       max(initiation_date, visit_starts) >= 0,
                     visit_ends-initiation_date+1,
                     NA),
         days_guard_b4hatch = ifelse(min(est_hatch, visit_ends) - 
                                       max(initiation_date, visit_starts) >= 0,
           min(est_hatch, visit_ends) - 
           max(initiation_date, visit_starts) + 1,
           ifelse(visit_starts > est_hatch | visit_ends < initiation_date,
                  NA,
                  NA))) %>%
  ungroup() %>%
  group_by(location) %>%
    summarize(sum_mD = sum(mD, na.rm=T),
              sum_vD = sum(mD*!mom_at_init, na.rm=T),
              sum_gD = sum(mD*mom_at_init, na.rm=T),
              vDb4h_sc2h = sum(days_guard_b4hatch*!mom_at_init, na.rm = T)/
                # scale to init-hatch interval so clutches with different intervals are comparable 
                as.numeric(first(est_hatch)-first(initiation_date)+1),
              gDb4h_sc2h = sum(days_guard_b4hatch*mom_at_init, na.rm = T)/
                as.numeric((first(est_hatch)-first(initiation_date)+1)),
              mDb4h_sc2h = sum(days_guard_b4hatch, na.rm = T)/
                as.numeric((first(est_hatch)-first(initiation_date)+1))) %>%
  ungroup()

clutch_status_momDays_b4h <- visited_1st_4d_data_tb %>%
  distinct(location, initiation_date, hatch_date, num_at_init,
           females_removed, ants_removed, egg_fate, egg_fate_date,
           max_egg_num, max_egg_len, `visited in 4 days`) %>%
  right_join(clutch_momDays_b4h, by=c("location")) %>%
  left_join(top5eggs_summary)

#### combine the two
clutch_egg_num_data <- initMb4h_tbL %>%
  left_join(initMb4h_tbS) %>%
  separate(location, sep = "_", into = c("DormPlant"),  remove = FALSE, extra = "drop") %>%
  left_join(select(clutch_status_momDays_b4h, location, sum_mD, sum_vD, sum_gD,
                   mDb4h_sc2h, gDb4h_sc2h, vDb4h_sc2h, max_egg_num, max_egg_len,
                   `visited in 4 days`)) %>%
  # if tbL and tbS are not the same female, add the female that lost the tie-break to the total sum of visit days
  mutate(sum_vD_initL = ifelse(initiator_tbL!=initiator_tbS,
                           sum_vD+init_durS, sum_vD),
         sum_vD_initS = ifelse(initiator_tbS!=initiator_tbL,
                           sum_vD+init_durL, sum_vD),
         visited = vDb4h_sc2h > 0,
         pmDvD = vDb4h_sc2h/mDb4h_sc2h) %>%
  left_join(top5eggs_summary) %>%
  select(location, init_durL, init_durS, desert_rel2hL, desert_rel2hS,
         sum_mD, sum_vD, sum_gD, sum_vD_initL, sum_vD_initS, 
         initMb4h_sc2hL, initMb4h_sc2hS, mDb4h_sc2h,
         females_removed, ants_removed, initiation_date, num_at_init, 
         `visited in 4 days`,
         n_eggs = max_egg_num, med_t5eggs, mean_t5eggs, max_n_eggs,
         max_egg_len, med_l_t5eggs, mean_l_t5eggs, max_l_eggs,
         initiator_tbL, initiator_tbS, n_clutches_on_plant, 
         visited, pmDvD, DormPlant)
```

```{r}
clutch_egg_num_data %>%
  filter(!is.na(initMb4h_sc2hL)) %>%
  ggplot(data=., aes(y=med_t5eggs, x=initMb4h_sc2hL)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=loess) +
  theme(legend.position = "bottom")

clutch_egg_num_data %>%
  filter(!is.na(initMb4h_sc2hL)) %>%
  ggplot(data=., aes(y=med_t5eggs, x=init_durL)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=lm) +
  theme(legend.position = "bottom")

clutch_egg_num_data %>%
  filter(!is.na(init_durL)) %>%
  ggplot(data=., aes(y=med_t5eggs, x=init_durL, color=sum_vD_initL>0)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=loess) +
  theme(legend.position = "bottom")

clutch_egg_num_data %>%
  filter(!is.na(mDb4h_sc2h)) %>%
  ggplot(data=., aes(y=med_t5eggs, x=mDb4h_sc2h, color=visited)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=loess) +
  theme(legend.position = "bottom")

clutch_egg_num_data %>%
  filter(!is.na(sum_mD)) %>%
  ggplot(data=., aes(y=med_t5eggs, x=sum_mD, color=visited)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=loess) +
  theme(legend.position = "bottom")

clutch_egg_num_data %>%
  filter(!is.na(sum_mD)) %>%
  ggplot(data=., aes(y=med_t5eggs, x=sum_mD, color=sum_vD)) +
  geom_point(size = 4, alpha = 0.75) +
  geom_smooth(method=loess) +
  theme(legend.position = "bottom") + 
    scale_colour_gradientn(colours=rainbow(4))

clutch_egg_num_data %>%
  filter(!is.na(sum_mD)) %>%
  ggplot(data=., aes(y=med_t5eggs, x=sum_gD, color=sum_vD)) +
  geom_point(size = 4, alpha = 0.75) +
  geom_smooth(method=loess) +
  theme(legend.position = "bottom") + 
    scale_colour_gradientn(colours=rainbow(4))

# The palette with grey:
Palette <- c("red", "orange", "yellow", "green", "blue", "purple")

clutch_egg_num_data %>%
  filter(!is.na(init_durL)) %>%
  mutate(visit_cuts = cut(sum_vD, breaks=c(0,4,8,12,16,20,80))) %>%
  ggplot(data=., aes(y=med_t5eggs, x=init_durL, color=visit_cuts)) +
  geom_point(size = 4, alpha = 0.75) +
  geom_smooth(method=lm, se=F) +
  theme(legend.position = "bottom") + 
    scale_colour_manual(values=Palette)

# with corrected sum_vD(_initL)
clutch_egg_num_data %>%
  filter(!is.na(init_durL)) %>%
  mutate(visit_cuts = cut(sum_vD_initL, breaks=c(0,4,8,12,16,20,80))) %>%
  ggplot(data=., aes(y=med_t5eggs, x=init_durL, color=visit_cuts)) +
  geom_point(size = 4, alpha = 0.75) +
  geom_smooth(method=lm, se=F) +
  theme(legend.position = "bottom") + 
    scale_colour_manual(values=Palette)
```

### Next steps:
 - run model fits for initL (and initS) and mD and compare in figures and tables (perhaps gam better than glm?)
 - decide on which model params to include and what data filtering to do
 - decide whether to refine the way we calculate visit days when dealing with tie-breaks
 - move on the estimates
 - how well can we approximate the data using simple regressions and simple heuristics for estimating fecundity?
  - can I plot the estimated egg contributions per female-clutch (old vs. any new versions) against the duration-eggs relationship of known (lone female) duration-egg measurements?

### run model fits for initL (and initS) and mD and compare in figures and tables (perhaps gam better than glm?)

```{r}
library(dplyr)
```

*Assumption 1: Poisson response*
The number of eggs appears to be appropriately modeled as coming from a poisson distribution by looking at the full pooled dataset, or grouping by levels of the main explanatory variable, the proportion of days before hatch any females was present.
```{r}
ggplot(data = clutch_egg_num_data) +
  geom_histogram(aes(x = med_t5eggs))

clutch_egg_num_data %>%
  mutate(init_durL_cuts = cut(init_durL, breaks=c(0,4,8,16,24,32,60))) %>%
ggplot(data=.) +
  geom_histogram(aes(x = med_t5eggs, fill = init_durL_cuts), binwidth = 10) +
  facet_wrap(vars(init_durL_cuts))

clutch_egg_num_data %>%
  mutate(sum_mD_cuts = cut(sum_mD, breaks=c(0,4,8,16,24,32,80))) %>%
ggplot(data=.) +
  geom_histogram(aes(x = med_t5eggs, fill = sum_mD_cuts), binwidth = 10) +
  facet_wrap(vars(sum_mD_cuts))
```

*Assumption 2: Mean = Var*
*initL:* There is extreme overdispersion (var = ~7-26 * mean) and there isn't even an monotonic increase in var with increasing mean. This might be an indication that using initiator days guarded to predict number of eggs isn't even approximately appropriate.

*sum_mD:*  There is less extreme overdispersion (var = ~6.8-10.4 * mean) and but there is a nearly monotonic increase in var with increasing mean.
```{r}
clutch_egg_num_data %>%
  mutate(init_durL_cuts = cut(init_durL, breaks=c(0,4,8,16,24,32,60))) %>%
  group_by(init_durL_cuts) %>%
  summarise(mean=mean(med_t5eggs),var=var(med_t5eggs),ratio=var/mean,n=n())

clutch_egg_num_data %>%
  mutate(sum_mD_cuts = cut(sum_mD, breaks=c(0,4,8,16,24,32,80))) %>%
  group_by(sum_mD_cuts) %>%
  summarise(mean=mean(med_t5eggs),var=var(med_t5eggs),ratio=var/mean,n=n())
```

*Assumption 3: Linearity*
```{r}
# initL
ggplot(data = clutch_egg_num_data, aes(x = init_durL, y = log(med_t5eggs))) +
  geom_point() +
  geom_smooth()

ggplot(data = clutch_egg_num_data, aes(x = init_durL, y = med_t5eggs)) +
  geom_point() +
  geom_smooth()

ggplot(data = clutch_egg_num_data, aes(x = init_durL, y = med_t5eggs, color = sum_vD_initL>0)) +
  geom_point() +
  geom_smooth(se=F) +
  theme(legend.position = "bottom")

ggplot(data = clutch_egg_num_data, aes(x = init_durL, y = med_t5eggs, color = initiation_date)) +
  geom_point() +
  geom_smooth(se=F) +
  theme(legend.position = "bottom") + 
    scale_colour_gradientn(colours=rainbow(4))

ggplot(data = clutch_egg_num_data, 
       aes(x = init_durL, y = med_t5eggs, color = interaction(ants_removed, sum_vD_initL>0))) +
  geom_point() +
  geom_smooth(se=F) +
  theme(legend.position = "bottom")

clutch_egg_num_data %>%
  semi_join(fec_model_data %>% 
              left_join(top5eggs_summary) %>% 
              filter(mom_at_init,
                     !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1))) %>%
ggplot(data=., 
       aes(x = init_durL, y = med_t5eggs, color = ants_removed)) +
  geom_point() +
  geom_smooth(se=F) +
  theme(legend.position = "bottom")

# sum_mD
ggplot(data = clutch_egg_num_data, aes(x = sum_mD, y = log(med_t5eggs))) +
  geom_point() +
  geom_smooth()

ggplot(data = clutch_egg_num_data, aes(x = sum_mD, y = med_t5eggs)) +
  geom_point() +
  geom_smooth()

ggplot(data = clutch_egg_num_data, aes(x = sum_mD, y = med_t5eggs, color = visited)) +
  geom_point() +
  geom_smooth(se=F) +
  theme(legend.position = "bottom")

ggplot(data = clutch_egg_num_data, aes(x = sum_mD, y = med_t5eggs, color = initiation_date)) +
  geom_point() +
  geom_smooth(se=F) +
  theme(legend.position = "bottom") + 
    scale_colour_gradientn(colours=rainbow(4))

ggplot(data = clutch_egg_num_data, 
       aes(x = sum_mD, y = med_t5eggs, color = interaction(ants_removed, visited))) +
  geom_point() +
  geom_smooth(se=F) +
  theme(legend.position = "bottom")

clutch_egg_num_data %>%
  semi_join(fec_model_data %>% 
              left_join(top5eggs_summary) %>% 
              filter(mom_at_init,
                     !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1))) %>%
ggplot(data=., 
       aes(x = sum_mD, y = med_t5eggs, color = ants_removed)) +
  geom_point() +
  geom_smooth(se=F) +
  theme(legend.position = "bottom")
```

*Assumption 3: Independence*
*initL*: This all looks ok as far as the relationships between med_t5eggs, init_durL, sum_vD_initL,ants_removed goes. Same for when you look only at whether clutches were visited or not.
*sum_mD*: sum_mD and sum_vD are clearly (obviously) collinear. I'm not sure there is a way to include the number or proportion of days that a clutch was occupied by a visitor without introducing this collinearity with sum_mD.
```{r}
#install.packages("GGally")
library("GGally")

ggpairs(data = select(clutch_egg_num_data, med_t5eggs, init_durL, sum_vD_initL,ants_removed))
ggpairs(data = select(clutch_egg_num_data %>% mutate(visited_initL=sum_vD_initL>0), 
                      med_t5eggs, init_durL, visited_initL,ants_removed))

ggpairs(data = select(clutch_egg_num_data, med_t5eggs, sum_mD, sum_vD,ants_removed))
ggpairs(data = select(clutch_egg_num_data, med_t5eggs, sum_mD, visited,ants_removed))

ggpairs(data = select(clutch_egg_num_data, med_t5eggs, sum_gD, sum_vD,ants_removed))
```

models
```{r}
t5eggs_initL_dur.glm_pois.ai <- 
  clutch_egg_num_data %>%
  filter(!is.na(init_durL)) %>%
  mutate(med_t5eggs=round(med_t5eggs)) %>%
glm(med_t5eggs ~ init_durL*sum_vD_initL, family = poisson,
                             data=.)
summary(t5eggs_initL_dur.glm_pois.ai)

# library(MASS)
# t5eggs_initL_dur.glm_nb.ai <- 
#   clutch_egg_num_data %>%
#   filter(!is.na(init_durL)) %>%
#   mutate(med_t5eggs=round(med_t5eggs)) %>%
# glm.nb(med_t5eggs ~ init_durL*sum_vD_initL,
#                              data=.)
# summary(t5eggs_initL_dur.glm_nb.ai)
# detach("package:MASS", unload=TRUE)

# t5eggs_initL_dur.gam.ai <- 
#   clutch_egg_num_data %>%
#   filter(!is.na(init_durL)) %>%
#   mutate(med_t5eggs=round(med_t5eggs)) %>%
# gam(med_t5eggs ~ s(init_durL, bs="cr")*s(sum_vD_initL, bs="cr"),
#                              data=.)
# summary(t5eggs_initL_dur.gam.ai)
# 
# gam.check(t5eggs_initL_dur.gam.ai)
# plot(t5eggs_initL_dur.gam.ai, residuals=T, pages = 1)
# 
# 
# 
# t5eggs_mD.gam <- 
#   clutch_egg_num_data %>%
#   filter(!is.na(sum_mD)) %>%
#   mutate(med_t5eggs=round(med_t5eggs)) %>%
# gam(med_t5eggs ~ s(sum_mD, bs="cr"), data=.)
# summary(t5eggs_mD.gam)
# 
# gam.check(t5eggs_mD_dur.gam)
# plot(t5eggs_mD.gam, residuals=T, pages = 1)
# 
# t5eggs_mD.lm <- 
#   clutch_egg_num_data %>%
#   filter(!is.na(sum_mD)) %>%
#   mutate(med_t5eggs=round(med_t5eggs)) %>%
# lm(med_t5eggs ~ sum_mD, data=.)
# summary(t5eggs_mD.lm)
# plot(t5eggs_mD.lm)
# visreg(t5eggs_mD.lm)
# 
# 
# gam.check(t5eggs_mD_dur.gam)
# plot(t5eggs_mD.gam, residuals=T, pages = 1)
# 
# t5eggs_gdur_loneFs.lm <- gam(med_t5eggs ~ guard_duration,
#                              data = t5eggs_gdur_loneFs.data)
# summary(t5eggs_gdur_loneFs.lm)
# visreg(t5eggs_gdur_loneFs.lm, "guard_duration", gg=TRUE)
# 
# t5eggs_gdur_loneFs.glm_pois <- glm(med_t5eggs ~ guard_duration, family = poisson,
#                              data = t5eggs_gdur_loneFs.data)
# summary(t5eggs_gdur_loneFs.glm_pois)
# visreg(t5eggs_gdur_loneFs.glm_pois, "guard_duration", gg=TRUE)
# 
# t5eggs_gdur_loneFs.gam_pois <- gam(med_t5eggs ~ s(guard_duration, bs="cr"), family = poisson,
#                              data = t5eggs_gdur_loneFs.data)
# summary(t5eggs_gdur_loneFs.gam_pois)
# plot(t5eggs_gdur_loneFs.gam_pois)
# visreg(t5eggs_gdur_loneFs.gam_pois, "guard_duration", gg=TRUE)
```

Many females that started the season by laying in existing clutches went on to initiate their own clutches later in the season (Figure S3).
```{r}

```

# 3 - Dataset C: estimating fecundity

eye-balling a square root function model for the decreasing rate of oviposition over time
- this doesn't make any sense!!!! there doesn't appear to be any real evidence that oviposition occurs along this pattern, it only arises from looking at the effect of guarding duration on the total number of eggs in the clutch
```{r}
sqrt.fun <- function(x) sqrt(x*180+400)

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=loess) +
  stat_function(fun=sqrt.fun) +
  theme(legend.position = "bottom")

sqrt(0*180+400)
sqrt(4*180+400)
sqrt(20*180+400)
sqrt(40*180+400)

sqrt(20*180+400)+sqrt(8*180+400)

clutch_egg_num_data %>%
  mutate(init_durL_cuts = cut(init_durL, breaks=c(0,4,8,12,16,20,24,28,32,60)),
         sum_vD_initL_cuts = cut(sum_vD_initL, breaks=c(-4,0,4,8,12,20,28,60))) %>%
  group_by(init_durL_cuts,sum_vD_initL_cuts) %>%
  summarize(mean = mean(med_t5eggs), 
            sqrt_est = mean(sqrt(init_durL*180+400) + sqrt(sum_vD_initL*180+400)-20),
            n=n())

clutch_egg_num_data %>%
  mutate(sqrt_est = sqrt(init_durL*180+400) + sqrt(sum_vD_initL*180+400)-20) %>%
  ggplot(data=., aes(y=med_t5eggs, x=sqrt_est, color=sum_vD_initL>0)) +
  geom_point() +
  geom_abline(slope=1) +
  ylim(0,200) + xlim(0,200)

clutch_egg_num_data %>%
  mutate(sqrt_est = (sqrt(init_durL*180+400) + sqrt(sum_vD_initL*180+400)-20)-10) %>%
  ggplot(data=., aes(y=med_t5eggs, x=sqrt_est, color=sum_vD_initL>0)) +
  geom_point() +
  geom_abline(slope=1) +
  ylim(0,200) + xlim(0,200)

ggplot(data = clutch_egg_num_data, 
       aes(x = sum_mD, y = med_t5eggs, color = interaction(ants_removed, visited))) +
  geom_point() +
  geom_smooth(se=F) +
  theme(legend.position = "bottom")
```

### using this sqrt heuristic to estimate fecundity, then compare results to the old way
```{r}
visited_1st_4d_data_tb %>%
  left_join(clutch_egg_num_data) %>%
  mutate(eggs_sqrt_est_v1 = ifelse(mom_at_init,
                                   sqrt(guard_duration*180+400),
                                   ifelse(!mom_at_init,
                                          sqrt(sum_vD*180+400)-20,
                                          NA)),
         eggs_sqrt_est_v2 = ifelse(initL,
                                   sqrt(guard_duration*180+400),
                                   ifelse(!initL,
                                          sqrt(sum_vD_initL*180+400)-20,
                                          NA))) %>%
  group_by(location) %>%
    mutate(eggs_sqrt_est_clutch_allF_v1 = sum(eggs_sqrt_est_v1),
           eggs_sqrt_est_clutch_allF_v2 = sum(eggs_sqrt_est_v2)) %>%
  ungroup() %>%
  group_by(Female_ID) %>%
    mutate(eggs_sqrt_est_life_v1 = sum(eggs_sqrt_est_v1),
           eggs_sqrt_est_life_v2 = sum(eggs_sqrt_est_v2)) %>%
  ungroup()

visited_1st_4d_data_tb %>%
  left_join(clutch_egg_num_data) %>%
  mutate(eggs_sqrt_est_v1 = ifelse(mom_at_init,
                                   sqrt(guard_duration*180+400),
                                   ifelse(!mom_at_init,
                                          sqrt(sum_vD*180+400)-20,
                                          NA)),
         eggs_sqrt_est_v2 = ifelse(initL,
                                   sqrt(guard_duration*180+400),
                                   ifelse(!initL,
                                          sqrt(sum_vD_initL*180+400)-20,
                                          NA))) %>%
  group_by(location) %>%
    mutate(eggs_sqrt_est_clutch_allF_v1 = sum(eggs_sqrt_est_v1),
           eggs_sqrt_est_clutch_allF_v2 = sum(eggs_sqrt_est_v2)) %>%
  ungroup() %>%
  group_by(Female_ID) %>%
    mutate(eggs_sqrt_est_life_v1 = sum(eggs_sqrt_est_v1),
           eggs_sqrt_est_life_v2 = sum(eggs_sqrt_est_v2)) %>%
  ungroup() %>%
  filter(clutch_initiated_order==1) %>%
  ggplot(data=., aes(x=guard_duration, y=eggs_sqrt_est_life_v1)) +
  geom_point() +
  geom_smooth()

# can we weight the number of eggs contributed to each clutch using this square root heuristic?
# so scaling the contribution of each female to 
```

```{r}
visited_1st_4d_data_tb %>%
  filter(!is.na(initiation_date)) %>%
  count(Female_ID, mom_at_init)

#### old version of estimating fecundity
# est_fecundity_clutch <- visited_1st_4d_data_tb %>%
#   mutate(desert_rel2h = visit_ends-est_hatch) %>%
#   group_by(Female_ID) %>%
#   mutate(started_by_initiating = 
#            any(clutch_visited_order==1&clutch_initiated_order==1)) %>%
#   ungroup() %>%
#   select(location, Female_ID, clutch_initiated_order, desert_rel2h,
#          females_removed, ants_removed, 
#          `visited in 4 days`, started_by_initiating) %>%
#   left_join(clutch_egg_num_data, by=c("location")) %>%
#   mutate(est_eggs_clutchS_sc2h = n_eggs*(initMb4h_sc2hS/mDb4h_sc2h),
#          est_eggs_clutchL_sc2h = n_eggs*(initMb4h_sc2hL/mDb4h_sc2h),
#          est_eggs_clutchL = ) %>%
#   group_by(Female_ID) %>%
#     mutate(est_eggs_lifeL_sc2h = sum(est_eggs_clutchL_sc2h, na.rm = TRUE),
#            est_eggs_lifeS_sc2h = sum(est_eggs_clutchS_sc2h, na.rm = TRUE),
#            n_clutches_iv = n(),
#            n_initiated = sum(!is.na(clutch_initiated_order)),
#            n_visited = sum(is.na(clutch_initiated_order))) %>%
#   ungroup()
# 
# 
# est_fecundity_clutch %>% distinct(Female_ID)
# 
# est_fecundity_future <- est_fecundity_clutch %>%
#   filter(clutch_initiated_order == 1) %>%
#   mutate(est_eggs_futureL = est_eggs_lifeL - est_eggs_clutchL,
#          est_eggs_futureS = est_eggs_lifeS - est_eggs_clutchS,
#          desert_catL = ifelse(desert_rel2hL <= -16, "desert", 
#                              ifelse(desert_rel2hL > -16 & desert_rel2hL <= 4,
#                                     "eggs","nymphs")),
#          visited_cat = ifelse(visited_early == "visited", "vis", "not"),
#          #ants_cat = ifelse(ants_removed, "none", "ants"),
#          #strat_catL = paste0(desert_catL," ",visited_cat," ",ants_cat),
#          desert_catS = ifelse(desert_rel2hS <= -16, "desert", 
#                              ifelse(desert_rel2hS > -16 & desert_rel2hS <= 4, 
#                                     "eggs","nymphs")))
#          #strat_catS = paste0(desert_catS," ",visited_cat," ",ants_cat))
# 
# est_fecundity_future_all <- est_fecundity_life_all %>%
#   left_join(est_fecundity_future)
# 
# est_fecundity_strat_cats <- est_fecundity_future %>%
#   select(Female_ID, location, mDb4h_sc2h, 
#          initMb4h_sc2hL, desert_rel2hL, 
#          est_eggs_clutchL, est_eggs_lifeL, est_eggs_futureL, desert_catL,
#          initMb4h_sc2hS, desert_rel2hS, 
#          est_eggs_clutchS, est_eggs_lifeS, est_eggs_futureS, desert_catS,
#          females_removed, ants_removed, clutch_initiated_order, 
#          n_clutches_iv, n_initiated, n_visited)
```

# 4 - Final Figures

plot eggs ~ guarding duration 
  A) initL (lone)
  B) initL with visitors
  C) sum_mD

show actual numbers of eggs counted for representative examples
  A) lone female, guarded eggs
  B) lone female, guarded nymphs
  C) visited female, deserted early
  D) many visitors

A) initL (lone)
```{r}
theme_set(theme_publilia())

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(aes(y=med_t5eggs), method=loess, 
              color = "black", fill="black") +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")

## initL only
# fec_model_data %>%
#   left_join(top5eggs_summary) %>%
#   filter(initL,
#          !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
# ggplot(data=., 
#        aes(x=guard_duration, y=med_t5eggs)) +
#   geom_point(aes(y=med_t5eggs), size = 4, alpha = 0.80) +
#   geom_smooth(aes(y=med_t5eggs), method=loess, 
#               color = "black", fill="black") +
#   xlab("Guarding duration of initiating female") +
#   ylab("Clutch size (number of eggs)") +
#   theme(legend.position = "bottom")

## Cutt off at actual hatching, not 20 days
# fec_model_data %>%
#   left_join(top5eggs_summary) %>%
#   filter(mom_at_init,
#          !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
# ggplot(data=., 
#        aes(x=guard_duration, y=med_t5eggs, 
#            color=guard_duration>(est_hatch-initiation_date),
#            fill=guard_duration>(est_hatch-initiation_date))) +
#   geom_point(aes(y=med_t5eggs), size = 4, alpha = 0.80) +
#   geom_smooth(aes(y=med_t5eggs), method=lm) +
#   xlab("Guarding duration of initiating female") +
#   ylab("Clutch size (number of eggs)") +
#   scale_color_manual(labels=c("before hatch", "after hatch"),
#                      values=c("black", "gray")) +
#   scale_fill_manual(labels=c("before hatch", "after hatch"),
#                     values=c("black", "gray")) +
#   theme(legend.position = "bottom")

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=guard_duration>20,
           fill=guard_duration>20)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(aes(y=med_t5eggs), method=lm) +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  scale_color_manual(labels=c("before hatch", "after hatch"),
                     values=c("black", "gray")) +
  scale_fill_manual(labels=c("before hatch", "after hatch"),
                    values=c("black", "gray")) +
  theme(legend.position = "bottom")

## initL only
# fec_model_data %>%
#   left_join(top5eggs_summary) %>%
#   filter(initL,
#          !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
# ggplot(data=., 
#        aes(x=guard_duration, y=med_t5eggs, 
#            color=guard_duration>20,
#            fill=guard_duration>20)) +
#   geom_point(aes(y=med_t5eggs), size = 4, alpha = 0.80) +
#   geom_smooth(aes(y=med_t5eggs), method=lm) +
#   xlab("Guarding duration of initiating female") +
#   ylab("Clutch size (number of eggs)") +
#   scale_color_manual(labels=c("before hatch", "after hatch"),
#                      values=c("black", "gray")) +
#   scale_fill_manual(labels=c("before hatch", "after hatch"),
#                     values=c("black", "gray")) +
#   theme(legend.position = "bottom")

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_l_t5eggs)) +
  geom_point(size = 1, alpha = 0.80) +
  geom_smooth(method=loess, 
              color = "black", fill="black") +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")
```

B) initL with visitors
```{r}
fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !is.na(!(eggs_ever_visited|num_at_init>1))) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs,
           color=!(eggs_ever_visited|num_at_init>1),
           fill=!(eggs_ever_visited|num_at_init>1))) +
  geom_point(size = 1, alpha = 0.80) +
  geom_smooth(method=loess) +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")

# fec_model_data %>%
#   left_join(top5eggs_summary) %>%
#   filter(mom_at_init,
#          !is.na(!(eggs_ever_visited|num_at_init>1))) %>%
# ggplot(data=., 
#        aes(x=guard_duration, y=med_t5eggs,
#            color=interaction(!(eggs_ever_visited|num_at_init>1),
#                              guard_duration>20),
#            fill=interaction(!(eggs_ever_visited|num_at_init>1),
#                             guard_duration>20)))+
#   geom_point(aes(y=med_t5eggs), size = 4, alpha = 0.80) +
#   geom_smooth(aes(y=med_t5eggs), method=lm) +
#   xlab("Guarding duration of initiating female") +
#   ylab("Clutch size (number of eggs)") +
#   scale_color_manual(labels=c("before hatch, visited", 
#                             "after hatch, visited",
#                             "before hatch, not visited", 
#                             "after hatch, not visited"),
#                   values=c("skyblue3","orange3",
#                            "skyblue1","orange1")) +
#   scale_fill_manual(labels=c("before hatch, visited", 
#                             "after hatch, visited",
#                             "before hatch, not visited", 
#                             "after hatch, not visited"),
#                   values=c("skyblue3","orange3",
#                            "skyblue1","orange1"))

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !is.na(!(eggs_ever_visited|num_at_init>1))) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_l_t5eggs)) +
  geom_point(size = 1, alpha = 0.80) +
  geom_smooth(method=loess) +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !is.na(!(eggs_ever_visited|num_at_init>1))) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_l_t5eggs,
           color=!(eggs_ever_visited|num_at_init>1),
           fill=!(eggs_ever_visited|num_at_init>1))) +
  geom_point(size = 1, alpha = 0.80) +
  geom_smooth(method=loess) +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")
```

C) sum_mD
NOTE: I use clutch_egg_num_data here but fec_model_data above. I should decide on one and stick with that.
```{r}
clutch_egg_num_data %>%
  left_join(top5eggs_summary) %>%
ggplot(data=., 
       aes(x=sum_mD, y=med_t5eggs)) +
  geom_point(size = 1, alpha = 0.50) +
  geom_smooth(method=loess, color="black", fill="black") +
  xlab("Sum of guarding durations of initiator and visitors") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")

clutch_egg_num_data %>%
  left_join(top5eggs_summary) %>%
ggplot(data=., 
       aes(x=sum_mD, y=med_l_t5eggs)) +
  geom_point(size = 1, alpha = 0.50) +
  geom_smooth(method=loess, color="black", fill="black") +
  xlab("Sum of guarding durations of initiator and visitors") +
  ylab("Clutch size (length of clutch)") +
  theme(legend.position = "bottom")
```

show actual numbers of eggs counted for representative examples

A) lone female, guarded eggs
```{r}
clutch_status_init_hatch_labels_v1 %>%
  left_join(fec_model_data) %>%
  group_by(location) %>%
  filter(any(!(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)),
         any(mom_at_init&est_rel2h>=-2&est_rel2h<=2),
         !is.na(egg_num)) %>%
  ungroup() %>%
  distinct(location, Date, initiation_date, egg_num) %>%
  ggplot(aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

clutch_status_init_hatch_labels_v1 %>%
  left_join(fec_model_data) %>%
  group_by(location) %>%
  filter(any(!(eggs_ever_visited|num_at_init>1)),
         any(mom_at_init&est_rel2h>=-2&est_rel2h<=2),
         !is.na(egg_num)) %>%
  ungroup() %>%
  distinct(location, Date, initiation_date, egg_num) %>%
  ggplot(aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")
```

B) lone female, guarded nymphs
```{r}
clutch_status_init_hatch_labels_v1 %>%
  left_join(fec_model_data) %>%
  group_by(location) %>%
  filter(any(!(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)),
         any(mom_at_init&est_rel2h>=10),
         !is.na(egg_num)) %>%
  ungroup() %>%
  distinct(location, Date, initiation_date, egg_num) %>%
  ggplot(aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

```

C) visited female, deserted early
```{r}
clutch_status_init_hatch_labels_v1 %>%
  left_join(select(fec_model_data, -initiation_date, -egg_fate, -egg_fate_date)) %>%
  group_by(location) %>%
  filter(any(!(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)),
         any(mom_at_init&guard_duration>=0&guard_duration<=3), 
         !is.na(egg_num)) %>%
  ungroup() %>%
  distinct(location, Date, initiation_date, egg_num,
           eggs_ever_visited,num_at_init,n_clutches_on_plant) %>%
  ggplot(aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

```

D) many visitors
```{r}
clutch_status_init_hatch_labels_v1 %>%
  left_join(fec_model_data) %>%
  group_by(location) %>%
  filter(any(eggs_ever_visited),
         any(mom_at_init&guard_duration<=20)) %>%
  ungroup() %>%
  distinct(location, Date, initiation_date, egg_num) %>%
  ggplot(aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")
```

# Figures for chapter - (all to supplement?)

The final number of eggs in a clutch was highly correlated with the duration that a female guarded them prior to hatching (Figure S2), indicating that Publilia reticulata females continue to lay eggs over time as they guard them. *Figure plus stats*
```{r}
fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(aes(y=med_t5eggs), method=loess, 
              color = "black", fill="black") +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=guard_duration>20,
           fill=guard_duration>20)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(aes(y=med_t5eggs), method=lm) +
  ylim(0,140) +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  scale_color_manual(labels=c("before hatch", "after hatch"),
                     values=c("black", "gray")) +
  scale_fill_manual(labels=c("before hatch", "after hatch"),
                    values=c("black", "gray")) +
  theme(legend.position = "bottom")

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=guard_duration>20,
           fill=guard_duration>20)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(span = 1) +
  ylim(0,140) +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  scale_color_manual(labels=c("before hatch", "after hatch"),
                     values=c("black", "gray")) +
  scale_fill_manual(labels=c("before hatch", "after hatch"),
                    values=c("black", "gray")) +
  theme(legend.position = "bottom")

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(aes(y=med_t5eggs), method="glm", method.args = list(family="poisson"), 
              color = "black", fill="black") +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")

# simple square root model
fec_model_data.v1 <- fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1))

fec_model_data.v1 %>%
  glm(data=., med_t5eggs ~ guard_duration, family="poisson")

fec_mod.m1 <- fec_model_data.v1 %>%
  glm(data=., med_t5eggs ~ guard_duration + I(sqrt(guard_duration)), family="poisson")

fec_model_data.v1.tmp <- fec_model_data.v1 %>%
  add_column(fit = predict(fec_mod.m1, newdata = ., type = 'response'))
## grad the inverse link function
ilink <- family(fec_mod.m1)$linkinv
## add fit and se.fit on the **link** scale
fec_model_data.m1_fit_ci <- fec_model_data.v1.tmp %>%
  add_column(setNames(as_tibble(predict(fec_mod.m1, fec_model_data.v1.tmp, se.fit = TRUE)[1:2]), 
                      c('fit_link','se_link'))) %>%
  ## create the interval and backtransform
  mutate(fit_resp  = ilink(fit_link),
         conf_upr = ilink(fit_link + (2 * se_link)),
         conf_lwr = ilink(fit_link - (2 * se_link)))

ggplot(data = fec_model_data.m1_fit_ci, 
       aes(x = guard_duration, y = fit)) +
    theme_publilia() +
    geom_point(aes(y = med_t5eggs), alpha = 0.1, size = 5) + 
    geom_line(aes(y = fit), size = 1) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.3, color = NA)

# square root model before/after hatch
fec_model_data.v2 <- fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init, !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
  mutate(before_after_hatch = ifelse(guard_duration>=20, "after hatch", "before hatch"))

fec_model_data.v2 %>%
  glm(data=., med_t5eggs ~ guard_duration*before_after_hatch, family="poisson")

fec_mod.m2 <- fec_model_data.v2 %>%
  glm(data=., med_t5eggs ~ I(sqrt(guard_duration))*before_after_hatch, family="poisson")

fec_model_data.v2.tmp <- fec_model_data.v2 %>%
  add_column(fit = predict(fec_mod.m2, newdata = ., type = 'response'))
## grad the inverse link function
ilink <- family(fec_mod.m2)$linkinv
## add fit and se.fit on the **link** scale
fec_model_data.m2_fit_ci <- fec_model_data.v2.tmp %>%
  add_column(setNames(as_tibble(predict(fec_mod.m2, fec_model_data.v2.tmp, se.fit = TRUE)[1:2]), 
                      c('fit_link','se_link'))) %>%
  ## create the interval and backtransform
  mutate(fit_resp  = ilink(fit_link),
         conf_upr = ilink(fit_link + (2 * se_link)),
         conf_lwr = ilink(fit_link - (2 * se_link)))

ggplot(data = fec_model_data.m2_fit_ci, 
       aes(x = guard_duration, y = fit, color=before_after_hatch, fill=before_after_hatch)) +
    theme_publilia() +
    geom_point(aes(y = med_t5eggs), alpha = 0.1, size = 5) + 
    geom_line(aes(y = fit), size = 1) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.3, color = NA)

```

This pattern holds when females were forcibly removed (Figure S2), confirming that females are not depositing a lump sum of eggs at initiation and staying longer with larger clutches as suggested by Olmstead and Wood (198X) for the closely related Entylia carinata (as Entylia bactriana). *Just stats*
```{r}
fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !is.na(!(eggs_ever_visited|num_at_init>1))) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs,
           color=!(eggs_ever_visited|num_at_init>1),
           fill=!(eggs_ever_visited|num_at_init>1))) +
  geom_point(size = 1, alpha = 0.80) +
  geom_smooth(span=0.75) +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")
```

The sum of all females’ egg-guarding durations was more predictive of final clutch size than egg guarding duration of the initiator alone (Table S1 with alternative models and their AICs), showing that females lay eggs while visiting existing clutches. *Figure plus AIC?*
```{r}
clutch_egg_num_data %>%
  left_join(top5eggs_summary) %>%
ggplot(data=., 
       aes(x=sum_mD, y=med_t5eggs)) +
  geom_point(size = 1, alpha = 0.50) +
  geom_smooth(span=0.75, color="black", fill="black") +
  xlab("Sum of guarding durations of initiator and visitors") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")

sum_mD_data <- clutch_egg_num_data %>%
  left_join(top5eggs_summary) %>%
  select(sum_mD, med_t5eggs)
```

Combine plots
```{r}
fec_fig1A <- fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=guard_duration>20,
           fill=guard_duration>20)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(span = 0.75) +
  xlab("Guarding duration of\ninitiating female") +
  ylab("Clutch size (number of eggs)") +
  scale_color_manual(labels=c("before hatch", "after hatch"),
                     values=c("black", "gray")) +
  scale_fill_manual(labels=c("before hatch", "after hatch"),
                    values=c("black", "gray")) +
  theme(legend.position = c(0.8,0.9)) + ylim(0,191) + xlim(0,76.2)

fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init, females_removed,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=guard_duration>20,
           fill=guard_duration>20)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(span = 1) +
  xlab("Guarding duration of\ninitiating female") +
  ylab("Clutch size (number of eggs)") +
  scale_color_manual(labels=c("before hatch", "after hatch"),
                     values=c("black", "gray")) +
  scale_fill_manual(labels=c("before hatch", "after hatch"),
                    values=c("black", "gray")) +
  theme(legend.position = c(0.8,0.8)) + ylim(0,191) + xlim(0,76.2)

fec_fig1B <- fec_model_data %>%
  left_join(top5eggs_summary) %>%
  filter(mom_at_init, !is.na(!(eggs_ever_visited|num_at_init>1))) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs,
           color=(eggs_ever_visited|num_at_init>1),
           fill=(eggs_ever_visited|num_at_init>1))) +
  geom_point(size = 1, alpha = 0.80) +
  geom_smooth(span=0.75) +
  scale_color_brewer(palette="Set2", labels=c("Never visited", "Visited")) +
  scale_fill_brewer(palette="Set2", labels=c("Never visited", "Visited")) +
  xlab("Guarding duration of\ninitiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = c(0.8,0.9)) + ylim(0,191) + xlim(0,76.2)

fec_fig1C <- clutch_egg_num_data %>%
  left_join(top5eggs_summary) %>%
ggplot(data=., 
       aes(x=sum_mD, y=med_t5eggs)) +
  geom_point(size = 1, alpha = 0.50) +
  geom_smooth(span=0.75, color="black", fill="black") +
  xlab("Sum of guarding durations of\ninitiator and visitors") +
  ylab("Clutch size (number of eggs)") + ylim(0,191) + xlim(0,76.2)

fec_fig1 <- egg::ggarrange(fec_fig1A, fec_fig1B, fec_fig1C, 
               labels = c("A","B","C"), nrow=1)

ggsave("oviposition_over_time_loess.png", fec_fig1,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

# Ovary data
```{r}
col_types = c("date", rep("text", 9), rep("numeric", 10), rep("text", 9), "numeric")
ovary_data <- read_xlsx("../Publilia_2019_ovary_data.xlsx", col_types = col_types, na = c(".","?",""))

# revised IDs
females_collected_file <- "../data_in_progress/females_collected_2019.xlsx"
females_collected <- read_xlsx(females_collected_file, sheet = "Tube Labels Ordered",
                                      col_types = c("date", rep("text", 16)), 
                                      na = c("", "NA")) %>%
  mutate(Date = as_date(Date))

ovary_fems_revIDs <- females_collected %>%
  select(Auto_label = `Label stem`, Revised_ID = `Revised ID`, Revision_Notes = `Revision Notes`) %>%
  separate(Auto_label, into = c("DormPlant", "FemID_label"), sep = "_") %>%
  mutate(FemID_label = str_trim(FemID_label, side = "both"),
         `Female ID` = paste0(DormPlant, " ", FemID_label))

ovary_data_w_counts <- ovary_data %>%
  rowwise() %>%
  mutate(n_ovarioles = sum(`O1: ovarioles`, `O2: ovarioles`),
         n_dev_ovar = sum(`O1: dev`, `O2: dev`),
         n_dev_ovid = sum(`O1: oviduct`, `O2: oviduct`),
         n_nr_dev = sum(`O1: near dev`, `O2: near dev`),
         n_dev_total = sum(n_dev_ovar, n_dev_ovid, `dev detached (ovary origin unknown)`),
         n_dev_nr_total = sum(n_dev_total, n_nr_dev, `nr dev detached (ovary origin unknown)`),
         n_ov_reliable = ifelse(`Total ovariole count reliable?` == "y",
                                       TRUE,
                                       FALSE)) %>%
  ungroup() %>%
  full_join(ovary_fems_revIDs, by = "Female ID") %>% 
  arrange(`Female ID`) %>% 
 # filter(is.na(`Tube ID`) | is.na(Revised_ID)) %>%
  filter(!is.na(`Tube ID`) | !is.na(Revised_ID)) %>%
  select(Tube_ID = `Tube ID`, Female_ID = Revised_ID,
       n_ovarioles, n_dev_ovar, n_dev_ovid, n_nr_dev, n_dev_total, n_dev_nr_total,
       n_ov_reliable,  pronotum_len = `Pronotum L (lateral)`)

ovary_data_long <- ovary_data %>%
  mutate(n_ov_reliable = ifelse(
    `Total ovariole count reliable?`=="y",TRUE,FALSE),
    egg_attr_reliable = ifelse(`Egg attribution to ovarioles reliable?`=="y",TRUE,FALSE)) %>%
  select(Tube=`Tube ID`, Female_ID=`Female ID`, 
         O1_ovs=`O1: ovarioles`, O2_ovs=`O2: ovarioles`,
         O1_dev=`O1: dev`, O2_dev=`O2: dev`, 
         Uk_dev=`dev detached (ovary origin unknown)`,
         O1_ovi=`O1: oviduct`, O2_ovi=`O2: oviduct`,
         O1_nrd=`O1: near dev`, O2_nrd=`O2: near dev`, 
         Uk_nrd=`nr dev detached (ovary origin unknown)`,
         n_ov_reliable, egg_attr_reliable,
         pronotum_len = `Pronotum L (lateral)`) %>%
  pivot_longer(cols=c(O1_ovs, O2_ovs, 
                      O1_ovi, O2_ovi, O1_dev, O2_dev, Uk_dev, 
                      O1_nrd, O2_nrd, Uk_nrd), 
               names_pattern = "(^..)(....)",
               names_to=c("site","name")) %>%
  mutate(dev_stage=substr(name,2,4)) %>% select(-name, n=value) %>%
  full_join(ovary_fems_revIDs, by = c("Female_ID"="Female ID")) %>%
  select(Tube, Female_ID=Revised_ID, site, dev_stage, n, n_ov_reliable, egg_attr_reliable, pronotum_len) %>%
  filter(!is.na(Tube))

```

## Within and among female patterns of ovary structure and egg development
*Note that I didn't filter by egg_attr_reliable in the following yet*
- The number of ovarioles per female varied from 13 to 20 (median = 17)
- Each ovary had as many as 10 and as few as 6 ovarioles (median = 9)
- The number of ovarioles per ovary tended to be uneven within females (median=1, mode=1, range=0-4); the majority of females had one ovary with at least one more ovariole than the other.
- Each ovary had as many as 10 developed eggs in the ovarioles and oviduct (median=2), and it was more common to have one or two more developed eggs in one ovary than another than to have same number in each ovary.
- Females had anywhere from 2 to 16 developed eggs total in their ovaries and oviduct (median=6, mode=6).
- Each ovary had as many as 6 nearly developed eggs in the ovarioles and these were never found in the oviduct (median 1), and it was more common to have a difference of one than to have even numbers of nearly developed eggs in the two ovaries.
- So at a given time, an ovary may have anywhere from 0 to 14 developed or nearly developed eggs (median=4, mode=0) and females had a total of anywhere from 4 to 28 developed or nearly developed eggs in their ovaries (median=11, mode=11 and 12).
```{r}
ovary_data_long %>%
  group_by(Female_ID, dev_stage) %>%
  mutate(bigger=rank(ifelse(site %in% c("O1","O2"),n,NA),ties.method="first"),
         Ov_renamed=ifelse(bigger<3, as.character(bigger), "Uk")) %>%
  ungroup()

# The number of ovarioles per female varied from 13 to 20 (median = 17)
(ovary_data_long %>%
  filter(dev_stage=="ovs", n_ov_reliable) %>%
  pivot_wider(names_from=site, values_from=n) %>%
  rowwise() %>%
  mutate(total=sum(O1,O2)))$total %>% quantile(na.rm=T)

(ovary_data_long %>%
  filter(dev_stage=="ovs", n_ov_reliable) %>%
  pivot_wider(names_from=site, values_from=n) %>%
  rowwise() %>%
  mutate(total=sum(O1,O2))) %>%
  ggplot(data=., aes(x=total)) +
  geom_histogram(binwidth=1) + xlab("Total n ovarioles in female")

# Each ovary had as many as 10 and as few as 6 ovarioles (median = 9)
(ovary_data_long %>%
  filter(dev_stage=="ovs", n_ov_reliable))$n %>% quantile(na.rm=T)

# The number of ovarioles per ovary tended to be uneven within females (median=1, mode=1, range=0-4);
# the majority of females had one ovary with at least one more ovariole than the other.
(ovary_data_long %>%
  filter(dev_stage=="ovs", n_ov_reliable) %>%
  pivot_wider(names_from=site, values_from=n) %>%
  mutate(diff=abs(O1-O2)))$diff %>% quantile(na.rm=T)

ovary_data_long %>%
  filter(dev_stage=="ovs", n_ov_reliable) %>%
  pivot_wider(names_from=site, values_from=n) %>%
  mutate(diff=abs(O1-O2)) %>%
  arrange(desc(diff)) %>%
  ggplot(data=., aes(x=diff)) +
  geom_histogram() + xlab("Difference in n ovarioles between ovaries")

# Each ovary had as many as 10 developed eggs in the ovarioles and oviduct (median=2)
(ovary_data_long %>%
  filter(dev_stage=="dev", n_ov_reliable))$n %>% quantile(na.rm=T)

# and it was more common to have one or two more developed eggs in one ovary than another 
# than to have same number in each ovary.
ovary_data_long %>%
  filter(dev_stage=="dev", n_ov_reliable) %>%
  pivot_wider(names_from=site, values_from=n) %>%
  mutate(diff=abs(O1-O2)) %>%
  arrange(desc(diff)) %>%
  ggplot(data=., aes(x=diff)) +
  geom_histogram() + xlab("Difference in n dev eggs between ovaries")

# Females had anywhere from 2 to 16 developed eggs total in their ovaries and oviduct (median=6, mode=6)
(ovary_data_long %>%
  filter(dev_stage=="dev", n_ov_reliable) %>%
  pivot_wider(names_from=site, values_from=n) %>%
  rowwise() %>%
  mutate(total=sum(O1,O2))) %>%
  ggplot(data=., aes(x=total)) +
  geom_histogram(binwidth=1) + xlab("Total n dev eggs in female")

# Each ovary had as many as 6 nearly developed eggs in the ovarioles and these were never found in the oviduct (median 1), and it was more common to have a difference of one than to have even numbers of nearly developed eggs in the two ovaries.
(ovary_data_long %>%
  filter(dev_stage=="nrd", n_ov_reliable))$n %>% quantile(na.rm=T)

ovary_data_long %>%
  filter(dev_stage=="nrd", n_ov_reliable) %>%
  pivot_wider(names_from=site, values_from=n) %>%
  mutate(diff=abs(O1-O2)) %>%
  arrange(desc(diff)) %>%
  ggplot(data=., aes(x=diff)) +
  geom_histogram() + xlab("Difference in n nearly dev eggs between ovaries")

# So at a given time, an ovary may have anywhere from 0 to 14 developed or nearly developed eggs (median=4, mode=0)
(ovary_data_long %>%
  filter(dev_stage %in% c("dev","nrd"), n_ov_reliable) %>%
  group_by(Female_ID, site) %>% 
    summarize(n_dev_nrd = sum(n)) %>% 
  ungroup())$n_dev_nrd %>% quantile(na.rm=T)

# and females had a total of anywhere from 4 to 28 developed or nearly developed eggs in their ovaries (median=11, mode=11 and 12).
(ovary_data_long %>%
  filter(dev_stage %in% c("dev","nrd"), n_ov_reliable) %>%
  group_by(Female_ID, site) %>% 
    summarize(n_dev_nrd = sum(n)) %>% 
  ungroup() %>%
  pivot_wider(names_from=site, values_from=n_dev_nrd) %>%
  rowwise() %>%
  mutate(total=sum(O1,O2)))$total %>% quantile(na.rm=T)

ovary_data_long %>%
  filter(dev_stage %in% c("dev","nrd"), n_ov_reliable) %>%
  group_by(Female_ID, site) %>% 
    summarize(n_dev_nrd = sum(n)) %>% 
  ungroup() %>%
  pivot_wider(names_from=site, values_from=n_dev_nrd) %>%
  rowwise() %>%
  mutate(total=sum(O1,O2)) %>%
  ggplot(data=., aes(x=total)) +
  geom_histogram(binwidth=1) + xlab("Total n dev + nearly dev eggs in female")

ovary_data_long %>%
  filter(dev_stage %in% c("dev","nrd"), n_ov_reliable) %>%
  group_by(Female_ID, site) %>% 
    summarize(n_dev_nrd = sum(n)) %>% 
  ungroup() %>%
  pivot_wider(names_from=site, values_from=n_dev_nrd) %>%
  mutate(diff=abs(O1-O2)) %>%
  arrange(desc(diff)) %>%
  ggplot(data=., aes(x=diff)) +
  geom_histogram() + xlab("Difference in n dev + nearly dev eggs between ovaries")
```

*Note that some female ID names are repeated, so group_by(Female_ID) leads to inflated counts*

Number of ovarioles did not predict number of developed or developing eggs, which doesn't support the hypothesis that variation in ovariole number leads to variation in egg-laying rates among females.
```{r}
ovary_data_long %>%
  filter(dev_stage %in% c("ovs", "dev"), n_ov_reliable) %>%
  pivot_wider(names_from=dev_stage, values_from=n) %>%
  group_by(Female_ID) %>% 
    summarize(n_dev = sum(dev, na.rm=T),
              n_ovs = sum(ovs, na.rm=T)) %>% 
  ungroup() %>%
  ggplot(data=.,aes(x=n_ovs, y=n_dev)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

ovary_data_long %>%
  filter(dev_stage %in% c("ovs", "nrd"), n_ov_reliable) %>%
  pivot_wider(names_from=dev_stage, values_from=n) %>%
  group_by(Female_ID) %>% 
    summarize(n_nrd = sum(nrd, na.rm=T),
              n_ovs = sum(ovs, na.rm=T)) %>% 
  ungroup() %>%
  ggplot(data=.,aes(x=n_ovs, y=n_nrd)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

ovary_data_long %>%
  filter(dev_stage %in% c("ovs", "dev", "nrd"), n_ov_reliable) %>%
  pivot_wider(names_from=dev_stage, values_from=n) %>%
  group_by(Female_ID) %>% 
    summarize(n_nrd_dev = sum(nrd, dev, na.rm=T),
              n_ovs = sum(ovs, na.rm=T)) %>% 
  ungroup() %>%
  ggplot(data=.,aes(x=n_ovs, y=n_nrd_dev)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

ovary_data_long %>%
  filter(dev_stage %in% c("ovs", "dev", "nrd"), n_ov_reliable) %>%
  pivot_wider(names_from=dev_stage, values_from=n) %>%
  group_by(Female_ID) %>% 
    summarize(n_nrd_dev = sum(nrd, dev, na.rm=T),
              n_ovs = sum(ovs, na.rm=T)) %>% 
  ungroup() %>% filter(n_ovs<=20, n_ovs>10) %>% # there are some extreme outliers with >30 ovarioles
  ggplot(data=.,aes(x=n_ovs, y=n_nrd_dev)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

```

Pronotum length did not predict number of ovarioles or number of developed or developing eggs.
```{r}
ovary_data_long %>%
  filter(dev_stage=="ovs", n_ov_reliable, site!="Uk") %>%
  group_by(Female_ID) %>% 
    summarize(n_ovs = sum(n),
              pronotum_len=first(pronotum_len)) %>% 
  ungroup() %>%
  ggplot(data=.,aes(x=pronotum_len, y=n_ovs)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

ovary_data_long %>%
  filter(dev_stage=="dev", n_ov_reliable, site!="Uk") %>%
  group_by(Female_ID) %>% 
    summarize(n_dev = sum(n),
              pronotum_len=first(pronotum_len)) %>% 
  ungroup() %>%
  ggplot(data=.,aes(x=pronotum_len, y=n_dev)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

ovary_data_long %>%
  filter(dev_stage=="nrd", n_ov_reliable, site!="Uk") %>%
  group_by(Female_ID) %>% 
    summarize(n_nrd = sum(n),
              pronotum_len=first(pronotum_len)) %>% 
  ungroup() %>%
  ggplot(data=.,aes(x=pronotum_len, y=n_nrd)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

ovary_data_long %>%
  filter(dev_stage %in% c("dev","nrd"), n_ov_reliable, site!="Uk") %>%
  group_by(Female_ID) %>% 
    summarize(n_dev_nrd = sum(n),
              pronotum_len=first(pronotum_len)) %>% 
  ungroup() %>%
  ggplot(data=.,aes(x=pronotum_len, y=n_dev_nrd)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")
```

Is there any difference in number of ovarioles among females that deserted early vs. stayed?
Or among *early-visited* females that deserted early vs. stayed?
```{r}

```

Is there any difference in number of ovarioles among females that were collected while visiting vs. guarding their own clutch vs. not yet laying any eggs vs. being on a leaf?
```{r}

```

Is there any signal of change in number of developed eggs in ovaries over guarding time?
```{r}

```

# Figures for Chapter
I dissected 133 females collected in the female removal experiment, 77 from the control enclosures and 56 from the ant-exclusion enclosures. There were no significant differences between the metrics of ovary anatomy and development or body size for the two treatments, so the following are the combined figures.
```{r}
library(gtsummary)

clutch_durations_summary_v2 %>%
  distinct(Female_ID, ants_removed) %>%
  right_join(ovary_data_w_counts, by = c("Female_ID")) %>%
  filter(!is.na(Tube_ID)) %>% 
  mutate(Dorm=substr(Female_ID,1,1)) %>%
  count(Dorm, ants_removed)

ovary_data_w_counts %>%
  filter(!is.na(Tube_ID)) %>% 
  mutate(Dorm=substr(Female_ID,1,1),
         ants_removed=ifelse(Dorm %in% c("F","H"), TRUE,
                             ifelse(Dorm %in% c("D","G"), FALSE, NA))) %>%
  count(ants_removed)

ovary_data_w_counts %>%
  filter(!is.na(Tube_ID)) %>% 
  mutate(Dorm=substr(Female_ID,1,1),
         ants_removed=ifelse(Dorm %in% c("F","H"), TRUE,
                             ifelse(Dorm %in% c("D","G"), FALSE, NA))) %>%
  select(ants_removed, n_ov_reliable, n_ovarioles, n_dev_total, n_nr_dev, n_dev_nr_total) %>%
  tbl_summary(by=ants_removed)
```

I was able to count the number of developed and developing eggs in each ovariole for 125 females and the total number of eggs in the ovaries in 127 females.
```{r}
ovary_data_w_counts %>% filter(!is.na(location),!is.na(Tube_ID)) %>% count(n_ov_reliable)
ovary_data_w_counts %>% filter(!is.na(location),!is.na(Tube_ID)) %>% count(!is.na(n_dev_nr_total))
```

There was considerable variation in the number of ovarioles and number of developing or mature eggs among females. The number of ovarioles per ovary ranged from 6 to 10 (median = 9) and the total number of ovarioles per female ranged from from 13 to 20 (median = 17). Asymmetry in the number of ovarioles among the ovaries was common, with more females having a difference of one or more ovarioles between the ovaries (n=73) than having an equal numbers of ovarioles between the ovaries (n=53). 
```{r}
# Each ovary had as many as 10 and as few as 6 ovarioles (median = 9)
(ovary_data_long %>%
  filter(dev_stage=="ovs", n_ov_reliable))$n %>% quantile(na.rm=T)

ovary_data_long %>%
  filter(dev_stage=="ovs", n_ov_reliable) %>%
  pivot_wider(names_from=site, values_from=n) %>%
  mutate(diff=abs(O1-O2)) %>%
  arrange(desc(diff)) %>%
  ggplot(data=., aes(x=diff)) +
  geom_histogram() + xlab("Difference in n ovarioles between ovaries")

(ovary_data_long %>%
  filter(dev_stage=="ovs", n_ov_reliable) %>%
  pivot_wider(names_from=site, values_from=n) %>%
  mutate(diff=abs(O1-O2))) %>% count(diff>0)

# The number of ovarioles per female varied from 13 to 20 (median = 17)
(ovary_data_long %>%
  filter(dev_stage=="ovs", n_ov_reliable) %>%
  pivot_wider(names_from=site, values_from=n) %>%
  rowwise() %>%
  mutate(total=sum(O1,O2)))$total %>% quantile(na.rm=T)

(ovary_data_long %>%
  filter(dev_stage=="ovs", n_ov_reliable) %>%
  pivot_wider(names_from=site, values_from=n) %>%
  rowwise() %>%
  mutate(total=sum(O1,O2))) %>%
  ggplot(data=., aes(x=total)) +
  geom_histogram(binwidth=1) + xlab("Total n ovarioles in female")
```

There was also considerable variation in the number of developed and developing eggs in the ovarioles and oviducts, both within females and across females. The number of developed eggs within an ovariole ranged from 0 to 6 (median = 3), and the number of developing eggs ranged from 0 to 6 (median = 2). The number of eggs in each of the lateral oviducts ranged from 0 to 8 (median = 1). All eggs in the oviducts were fully developed, and I never observed eggs entirely within the common oviduct without some overlap in the lateral oviducts. The total number of developed eggs per female ranged from 2 to 16 (median = 6) and the total number of developed and developing eggs per female ranged from 4 to 28 (median = 11).
```{r}
# The number of developed eggs within an ovariole ranged from 0 to 6 (median = 3),
(ovary_data_long %>% filter(dev_stage=="dev", n_ov_reliable, site %in% c("O1","02")))$n %>%
  quantile(na.rm=T)

# and the number of developing eggs ranged from 0 to 6 (median = 3).
(ovary_data_long %>% filter(dev_stage=="nrd", n_ov_reliable, site %in% c("O1","02")))$n %>%
  quantile(na.rm=T)

# The number of developed eggs within an ovariole ranged from 0 to 8 (median = 1),
(ovary_data_long %>% filter(dev_stage=="ovi", n_ov_reliable, site %in% c("O1","02")))$n %>%
  quantile(na.rm=T)

# Each ovary had as many as 10 developed eggs in the ovarioles and oviduct (median=2)
(ovary_data_long %>%
  filter(dev_stage=="dev", n_ov_reliable))$n %>% quantile(na.rm=T)

(ovary_data_long %>%
  filter(dev_stage %in% c("dev"), n_ov_reliable) %>%
  group_by(Female_ID, site) %>% 
    summarize(n_dev_nrd = sum(n)) %>% 
  ungroup() %>%
  pivot_wider(names_from=site, values_from=n_dev_nrd) %>%
  rowwise() %>%
  mutate(total=sum(O1,O2)))$total %>% quantile(na.rm=T)

(ovary_data_long %>%
  filter(dev_stage %in% c("dev","nrd"), n_ov_reliable) %>%
  group_by(Female_ID, site) %>% 
    summarize(n_dev_nrd = sum(n)) %>% 
  ungroup() %>%
  pivot_wider(names_from=site, values_from=n_dev_nrd) %>%
  rowwise() %>%
  mutate(total=sum(O1,O2)))$total %>% quantile(na.rm=T)

# So at a given time, an ovary may have anywhere from 0 to 14 developed or nearly developed eggs (median=4, mode=0)
(ovary_data_long %>%
  filter(dev_stage %in% c("dev","nrd"), n_ov_reliable) %>%
  group_by(Female_ID, site) %>% 
    summarize(n_dev_nrd = sum(n)) %>% 
  ungroup())$n_dev_nrd %>% quantile(na.rm=T)

# and females had a total of anywhere from 4 to 28 developed or nearly developed eggs in their ovaries (median=11, mode=11 and 12).
(ovary_data_long %>%
  filter(dev_stage %in% c("dev","nrd"), n_ov_reliable) %>%
  group_by(Female_ID, site) %>% 
    summarize(n_dev_nrd = sum(n)) %>% 
  ungroup() %>%
  pivot_wider(names_from=site, values_from=n_dev_nrd) %>%
  rowwise() %>%
  mutate(total=sum(O1,O2)))$total %>% quantile(na.rm=T)

ovary_data_long %>%
  filter(dev_stage %in% c("dev","nrd"), n_ov_reliable) %>%
  group_by(Female_ID, site) %>% 
    summarize(n_dev_nrd = sum(n)) %>% 
  ungroup() %>%
  pivot_wider(names_from=site, values_from=n_dev_nrd) %>%
  rowwise() %>%
  mutate(total=sum(O1,O2)) %>%
  ggplot(data=., aes(x=total)) +
  geom_histogram(binwidth=1) + xlab("Total n dev + nearly dev eggs in female")

ovary_data_long %>%
  filter(dev_stage %in% c("dev","nrd"), n_ov_reliable) %>%
  group_by(Female_ID, site) %>% 
    summarize(n_dev_nrd = sum(n)) %>% 
  ungroup() %>%
  pivot_wider(names_from=site, values_from=n_dev_nrd) %>%
  mutate(diff=abs(O1-O2)) %>%
  arrange(desc(diff)) %>%
  ggplot(data=., aes(x=diff)) +
  geom_histogram() + xlab("Difference in n dev + nearly dev eggs between ovaries")
```

We did not observe a correlation between the number of ovarioles and the total number of developed eggs (Pearson's correlation p-value = 0.9708), but there was a correlation between ovariole count and developing egg count (Pearson's correlation coeficient = 0.252, p-value = 0.004812) eggs. Body size (using pronotum size as a proxy) was also not correlated with the number of ovarioles (p-value = 0.239), the number of developed (p-value = 0.07216) or developing (p-value = 0.3897) eggs in a female. So while the number of ovarioles appears to limit the number of developing eggs present in the ovaries, we don't find strong evidence that this translates to fully developed eggs, and natural variation in body size and ovariole count appear unlikely to cause heterogenety in oviposition rates among females.
```{r}
ovary_data_good_ovs <- ovary_data_w_counts %>%
  filter(n_ov_reliable)

ovary_data_good_ovs %>%
  ggplot(data=., aes(x=n_ovarioles, y=n_dev_total)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

cor.test(ovary_data_good_ovs$n_ovarioles, ovary_data_good_ovs$n_dev_total, 
         method="pearson")

ovary_data_good_ovs %>%
  ggplot(data=., aes(x=n_ovarioles, y=n_nr_dev)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

cor.test(ovary_data_good_ovs$n_ovarioles, ovary_data_good_ovs$n_nr_dev, 
         method="pearson")

ovary_data_good_ovs %>%
  ggplot(data=., aes(x=n_ovarioles, y=n_dev_nr_total)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

cor.test(ovary_data_good_ovs$n_ovarioles, ovary_data_good_ovs$n_dev_nr_total, 
         method="pearson")

ovary_data_good_ovs %>%
  ggplot(data=., aes(x=pronotum_len, y=n_ovarioles)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

cor.test(ovary_data_good_ovs$pronotum_len, ovary_data_good_ovs$n_ovarioles, 
         method="pearson")

ovary_data_good_ovs %>%
  ggplot(data=., aes(x=pronotum_len, y=n_dev_total)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

cor.test(ovary_data_good_ovs$pronotum_len, ovary_data_good_ovs$n_dev_total, 
         method="pearson")

ovary_data_good_ovs %>%
  ggplot(data=., aes(x=pronotum_len, y=n_nr_dev)) +
  geom_count(alpha=0.75) + geom_smooth(method=lm, color="black",fill="black")

cor.test(ovary_data_good_ovs$pronotum_len, ovary_data_good_ovs$n_nr_dev, 
         method="pearson")
```

The total number of fully developed eggs in the ovaries differed among females that in different locations (Kruskall-Wallis test: n = 118, H = 10.6, df = 3, p-value = 0.0143). Females on leaves without eggs had significantly more fully developed eggs in their ovaries (median = 18, Holm-adjusted Dunn's test p-value > 0.05) than females on the stem, guarding a clutch that they initiated or visiting an existing clutch, all of which had equivalent numbers of developed eggs (median = 8, Holm-adjusted Dunn's test p-value > 0.05). The number of undeveloped eggs did not differ among females in different locations (p-value > 0.05).
```{r}
ovary_data_location <- ovary_data_good_ovs %>%
  mutate(Dorm = substr(Tube_ID,1,1),
         date_mom_removed = as_date(ifelse(Dorm %in% c("G", "H"),
                                    as_date("2019-06-07"),
                                    ifelse(Dorm %in% c("F", "D"),
                                           as_date("2019-06-15"),
                                           NA)))) %>%
  left_join(select(All_data_v6, Date:Eggs) %>% filter(!is.na(Female_ID)), 
            by=c("date_mom_removed"="Date", "Female_ID", "Dorm")) %>%
  filter(!is.na(Female_ID)) %>%
  mutate(Fem_loc_at_coll = 
           ifelse(str_sub(Leaf,start=-1) %in% c("A","S","a"),"Stem",
                  ifelse(!is.na(as.numeric(str_sub(Leaf,start=-1))), "Leaf",NA)))

clutch_durations_data_removed <- clutch_durations_summary_v2 %>%
  mutate(date_mom_removed = as_date(ifelse(Dorm %in% c("G", "H"),
                                    as_date("2019-06-07"),
                                    ifelse(Dorm %in% c("F", "D"),
                                           as_date("2019-06-15"),
                                           NA)))) %>%
  filter(date_mom_removed >= visit_starts, date_mom_removed <= visit_ends) %>%
  select(Female_ID:leaf_visit_order, mom_at_init,
         clutch_visited_order:date_mom_removed)

ovary_data_clutch <- ovary_data_location %>%
  left_join(clutch_durations_data_removed) %>%
  mutate(loc_cat = 
           ifelse(Fem_loc_at_coll=="Stem", 
                  "Stem",
                  ifelse((Fem_loc_at_coll=="Leaf")&is.na(clutch_visited_order),
                         "Leaf no eggs",
                         ifelse(!is.na(clutch_visited_order)&!mom_at_init,
                                "Existing clutch",
                                # don't know why this isn't working
                                ifelse(!is.na(clutch_initiated_order),
                                "Initiated clutch",NA)))))

ovary_data_clutch %>%
  select(Fem_loc_at_coll, loc_cat) %>%
  tbl_summary()

ovary_data_clutch %>% filter(!is.na(loc_cat)) %>%
  ggplot(data=., aes(x=loc_cat, y=n_ovarioles, fill=loc_cat)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=3, width=0.35)

ovary_data_clutch %>% filter(!is.na(loc_cat)) %>%
  ggplot(data=., aes(x=loc_cat, y=pronotum_len, fill=loc_cat)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=3, width=0.35)

ovary_data_clutch %>% filter(!is.na(loc_cat)) %>%
  ggplot(data=., aes(x=loc_cat, y=n_dev_total, fill=loc_cat)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=3, width=0.35)

ovary_data_clutch %>% filter(!is.na(loc_cat)) %>%
  ggplot(data=., aes(x=loc_cat, y=n_nr_dev, fill=loc_cat)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=3, width=0.35)

ovary_data_clutch %>% filter(!is.na(loc_cat)) %>%
  ggplot(data=., aes(x=loc_cat, y=n_dev_nr_total, fill=loc_cat)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=3, width=0.35)

# Kruskall-Wallis test followed by Dunn test
KWdata_dev_eggs <- ovary_data_clutch %>% filter(!is.na(loc_cat))
  # run KW test using rstatix::kruskal_test
  KWtest <- KWdata_dev_eggs %>% kruskal_test(n_dev_total ~ loc_cat)
  # get effect size using effectsize::rank_epsilon_squared
  KWepsilon2 <- rank_epsilon_squared(n_dev_total ~ loc_cat, data=KWdata_dev_eggs)
  # run Dunn test using rstatix::dunn_test
  dunn <- KWdata_dev_eggs %>% dunn_test(n_dev_total ~ loc_cat)
  # get multiple comparison groups letters using multcompView::multcompLetters
  dunn.vec <- dunn$p.adj.signif
  names(dunn.vec) <- paste(dunn$group1,dunn$group2,sep="-")
  multcompLetters <- tibble(x=names(multcompLetters(dunn.vec)$Letters),
                            label=unname(multcompLetters(dunn.vec)$Letters))

```

There was no difference in body size or ovariole count among females that had deserted their first clutch early, guarded their first clutch for at least 10 days or started by visiting an existing clutch.
```{r}
desert_cat_ovary_data <- clutch_durations_summary_v2 %>%
  right_join(select(ovary_data_clutch, 
                    Female_ID,Tube_ID:pronotum_len, date_mom_removed), 
             by="Female_ID") %>%
  mutate(est_hatch = as_date(ifelse(is.na(hatch_date),
                                 initiation_date + 20,
                                 hatch_date)),
         desert_rel2h = visit_ends-est_hatch) %>%
  group_by(Female_ID) %>%
  # clutch visited order == 0 means she visited before initiation, so it shouldn't count
  mutate(started_by =
           ifelse(any(clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order==1),
                  "initiating",
                  ifelse(any(clutch_visited_order==1&is.na(clutch_initiated_order)|
                       clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order!=1),
                         "visiting", "other")),
         n_clutches_with_eggs_iv = sum(!is.na(clutch_visited_order)&(clutch_visited_order>0), na.rm=T)) %>%
  ungroup() %>%
  filter(clutch_visited_order==1) %>%
  mutate(desert_cat = 
           ifelse(started_by=="initiating",
                  ifelse(guard_duration <= 10, "desert",
                         ifelse(guard_duration > 10 & desert_rel2h <= 4, "eggs",
                                ifelse(desert_rel2h >= 4,"nymphs", NA))),
                  ifelse(started_by=="visiting", "visit", NA))) %>%
  # select(Female_ID, clutch_visited_order, guard_duration,
  #        desert_cat, visit_ends, date_mom_removed) %>%
  mutate(interupted = date_mom_removed==visit_ends) %>% 
  filter(#!is.na(desert_cat), 
         is.na(desert_cat) | !interupted | (interupted & (desert_cat!="desert")))

desert_cat_ovary_data %>%
  count(desert_cat, interupted)

desert_cat_ovary_data %>%
  distinct(Female_ID, n_ovarioles, desert_cat) %>%
  ggplot(data=., aes(x=desert_cat, y=n_ovarioles)) +
  geom_boxplot() + geom_jitter(pch = 21, size=3, width=0.35)

desert_cat_ovary_data %>%
  distinct(Female_ID, pronotum_len, desert_cat) %>%
  ggplot(data=., aes(x=desert_cat, y=pronotum_len)) +
  geom_boxplot() + geom_jitter(pch = 21, size=3, width=0.35)

```

There was a negative correlation between the number of days a female had been guarding her own clutch when collected and the number of developing eggs in her ovaries (t = -3.2241, df = 66, p-value = 0.001966). There was no relationship between guarding tenure at collection and the number of fully developed eggs, however. Taken together, this suggests that females invest slightly more in oviposition just before initiation, but continue to invest in new eggs for many days after initiation albeit at slowly decreasing rate. Additional experiments will be required to determine whether the costs of initiating a clutch are higher than laying eggs in an existing clutch, which should effect the optimal care strategy in different contexts. 
```{r}
ovary_data_clutch %>%
  ggplot(data=., aes(x=guard_duration, n_dev_total, color=loc_cat, fill=loc_cat)) +
  geom_count() + geom_smooth(method="lm")

ovary_data_clutch_init <- ovary_data_clutch %>% filter(loc_cat=="Initiated clutch")
ovary_data_clutch_exist <- ovary_data_clutch %>% filter(loc_cat=="Existing clutch")

cor.test(ovary_data_clutch_init$guard_duration, ovary_data_clutch_init$n_dev_total, 
         method="pearson")

ovary_data_clutch %>%
  ggplot(data=., aes(x=guard_duration, y=n_nr_dev, color=loc_cat, fill=loc_cat)) +
  geom_count() + geom_smooth(method=lm)

cor.test(ovary_data_clutch_init$guard_duration, ovary_data_clutch_init$n_nr_dev, 
         method="pearson")

cor.test(ovary_data_clutch_exist$guard_duration, ovary_data_clutch_exist$n_nr_dev, 
         method="pearson")

ovary_data_clutch %>%
  mutate(loc_tenure = date_mom_removed - visit_starts) %>%
  ggplot(data=., aes(x=loc_tenure, n_dev_total, color=loc_cat, fill=loc_cat)) +
  geom_count() + geom_smooth()

ovary_data_clutch %>%
  mutate(loc_tenure = date_mom_removed - visit_starts) %>%
  ggplot(data=., aes(x=loc_tenure, n_nr_dev, color=loc_cat, fill=loc_cat)) +
  geom_count() + geom_smooth(se=F)

```

### 2023-08-24 scripts/old/Publilia_2019_CHAPTER-2B-fecundity-estimate.Rmd
added old scripts to `scripts/old/` for reference

---
title: "Publilia_2019_CHAPTER-2B-fecundity-estimate"
author: "micah fletcher"
date: "1/18/2022"
output: html_document
---

# Publilia 2019 Chapter - Script 2B: modeling fecundity
This is meant to consolidate previous scripts and provide a readable and reproducible record of the analyses for the Publilia Chapter.

2) *Fecundity:* No support for trade-off between current care and future fecundity
  - *Dataset B [supp: modeling fecundity ~ guarding]* requirements:
    - Guarding durations of ALL females that visited a clutch are accurate.
      - Cannot exclude any females, including unmarked or ambiguously marked females, because I need them for the sum of guarding time.
    - Maximum number of eggs per clutch is accurate.
    - Can partition 
      - early clutches vs. later clutches
      - single-mother clutches vs. multiple-mother clutches
      - ants vs. no ants
  - *Dataset C [estimating fecundity]* requirements:
    - Guarding durations of ALL females that visited a clutch are accurate.
      - Cannot exclude any females, including unmarked or ambiguously marked females, because I need them for the sum of guarding time.
    - Maximum number of eggs per clutch is accurate.
    - Numbers of clutches per female (and guarding duration and eggs for each) are accurate.
      - Cannot exclude any clutches, including those with ambiguous initiators, or unknown hatch dates
    - Models/heuristics of focal female contribution to clutch are clearly defined and sensible.
      1) simple equal proportion of days
      2) equal proportion of days with "intercept" given to the initiator
      3) unequal proportion of days for initiator(s) vs visitors, with intercept also given to the initiator
      4) Reproducing Zink's fecundity

# 0 - Data import

# 1 - Data prep

iteroparity and the trade-off between initiating and visiting
```{r}
visited_1st_4d_data_tb %>%
  filter(!is.na(initiation_date)) %>%
  count(Female_ID, mom_at_init) %>%
  count(mom_at_init, n)

visited_1st_4d_data_tb %>%
  filter(!is.na(initiation_date)) %>%
  group_by(Female_ID) %>%
    summarize(n_init = sum(mom_at_init),
              n_visit = sum(!mom_at_init)) %>%
  ggplot(data=., aes(x=n_init, y=n_visit)) +
  geom_hex(binwidth=1) + 
    scale_fill_gradientn(colours=rainbow(4))

visited_1st_4d_data_tb %>%
  filter(!is.na(initiation_date)) %>%
  group_by(Female_ID) %>%
    summarize(n_init = sum(mom_at_init),
              n_visit = sum(!mom_at_init),
              ants_removed = first(ants_removed)) %>%
  ungroup() %>%
  ggplot(data=., aes(x=n_init, y=n_visit)) +
  geom_count(aes(size=after_stat(prop), color=after_stat(prop), group = 1)) + 
    scale_size_area(max_size=10) +
  facet_wrap(vars(ants_removed), ncol=1)
```

same but for different strategies on the first clutch
```{r}
clutch_egg_num_data
visited_1st_4d_data_tb %>%
  filter(!is.na(initiation_date))

est_fecundity_clutch <- visited_1st_4d_data_tb %>%
  group_by(Female_ID) %>%
  mutate(started_by_initiating =
           any(clutch_visited_order==1&clutch_initiated_order==1)) %>%
  ungroup() %>%
  select(location, Female_ID, clutch_visited_order, clutch_initiated_order, desert_rel2h = est_rel2h,
         mom_at_init, `visited in 4 days`, started_by_initiating) %>%
  left_join(select(clutch_egg_num_data, -`visited in 4 days`), by=c("location")) %>%
  mutate(est_eggs_clutchS_sc2h = n_eggs*(initMb4h_sc2hS/mDb4h_sc2h),
         est_eggs_clutchL_sc2h = n_eggs*(initMb4h_sc2hL/mDb4h_sc2h)) %>%
  group_by(Female_ID) %>%
    mutate(est_eggs_lifeL_sc2h = sum(est_eggs_clutchL_sc2h, na.rm = TRUE),
           est_eggs_lifeS_sc2h = sum(est_eggs_clutchS_sc2h, na.rm = TRUE),
           n_clutches_iv = n(),
           n_initiated = sum(!is.na(clutch_initiated_order)),
           n_visited = sum(!is.na(initiation_date)&is.na(clutch_initiated_order)),
           n_feed = sum(is.na(initiation_date)),
           init_visit_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "Initiated only"),
                                           ifelse(!any(mom_at_init), "Visited only", NA)),
           one_both_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "One"),
                                           ifelse(!any(mom_at_init), "One", NA))) %>%
  ungroup()

est_fecundity_future <- est_fecundity_clutch %>%
  #filter(clutch_initiated_order == 1) %>% I plotted all the stuff for field day using this instead of first visited
  filter(clutch_visited_order == 1) %>%
  mutate(est_eggs_futureL_sc2h = est_eggs_lifeL_sc2h - est_eggs_clutchL_sc2h,
         est_eggs_futureS_sc2h = est_eggs_lifeS_sc2h - est_eggs_clutchS_sc2h,
         desert_catL = ifelse(desert_rel2hL <= -16, "desert",
                             ifelse(desert_rel2hL > -16 & desert_rel2hL <= 4,
                                    "eggs","nymphs")),
         visited_cat = ifelse(`visited in 4 days` == "Visited", "vis", "not"),
         desert_catS = ifelse(desert_rel2hS <= -16, "desert",
                             ifelse(desert_rel2hS > -16 & desert_rel2hS <= 4,
                                    "eggs","nymphs")))

est_fecundity_strat_cats <- est_fecundity_future %>%
  select(Female_ID, location, mDb4h_sc2h,
         initMb4h_sc2hL, desert_rel2hL,
         est_eggs_clutchL_sc2h, est_eggs_lifeL_sc2h, est_eggs_futureL_sc2h, desert_catL,
         initMb4h_sc2hS, desert_rel2hS,
         est_eggs_clutchS_sc2h, est_eggs_lifeS_sc2h, est_eggs_futureS_sc2h, desert_catS,
         females_removed, ants_removed, clutch_initiated_order,
         n_clutches_iv, n_initiated, n_visited, init_visit_life_tactic, `visited in 4 days`)

est_fecundity_future %>%
  ggplot(data=., aes(x=n_initiated, y=n_visited)) +
  geom_count(aes(size=after_stat(prop), color=after_stat(prop), group = 1)) + 
    scale_size_area(max_size=10) +
  facet_wrap(vars(ants_removed, desert_catL), nrow=1)

strat_fec_geom_count_ants0 <- est_fecundity_future %>%
  filter(!ants_removed, !females_removed) %>%
  ggplot(data=., aes(x=n_initiated, y=n_visited)) +
  geom_count(aes(size=after_stat(prop), color=after_stat(prop), group = 1)) + 
    scale_size_area(max_size=10) +
    ylim(0,3) + xlim(0,6) +
  facet_wrap(vars(desert_catL), nrow=1)

strat_fec_geom_count_ants1 <- est_fecundity_future %>%
  filter(ants_removed, !females_removed) %>%
  ggplot(data=., aes(x=n_initiated, y=n_visited)) +
  geom_count(aes(size=after_stat(prop), color=after_stat(prop), group = 1)) + 
    scale_size_area(max_size=10) +
    ylim(0,3) + xlim(0,6) +
  facet_wrap(vars(desert_catL), nrow=1)

ggpubr::ggarrange(strat_fec_geom_count_ants0, strat_fec_geom_count_ants1, 
          ncol=1)

```

# 2 - Iteroparity
estimating iteroparity: number of clutches (and how long they guarded them)
 - resurrect my old plots and make sure they aren't leaving out any important data
 - recreate Zink's figures/text with my data
  - Fig 4A: number of clutches
  - Fig 4B: mean size (length) of future clutches
  - Fig 4C: duration on remaining clutches
  - from text (not shown): size (length) of the initial egg mass

### Zink Fig 2A:
```{r}
est_fecundity_clutch_zink <- visited_1st_4d_data_tb %>%
  group_by(Female_ID) %>%
  mutate(started_by_initiating =
           any(clutch_visited_order==1&clutch_initiated_order==1)) %>%
  ungroup() %>%
  select(location, Female_ID, clutch_initiated_order, guard_duration, desert_rel2h = est_rel2h,
         mom_at_init, `visited in 4 days`, started_by_initiating) %>%
  left_join(clutch_egg_num_data, by=c("location")) %>%
  mutate(egg_guard_cat_zink = cut(guard_duration, breaks=c(0,4,10,20)),
         len_future_zink = ifelse(clutch_initiated_order>1, mean_l_t5eggs, NA),
         dur_future_zink = ifelse(clutch_initiated_order>1, guard_duration, NA),
         len_first_zink = ifelse(clutch_initiated_order==1, mean_l_t5eggs, NA)) %>%
  group_by(Female_ID) %>%
  summarize(n_broods_future_zink = sum(!is.na(clutch_initiated_order)&clutch_initiated_order>1),
            mean_len_future_zink = ifelse(is.nan(mean(len_future_zink, na.rm=T)),
                                          NA,mean(len_future_zink, na.rm=T)),
            mean_dur_future_zink = ifelse(is.nan(mean(dur_future_zink, na.rm=T)),
                                          NA,mean(dur_future_zink, na.rm=T)),
            mean_len_first_zink = ifelse(is.nan(mean(len_first_zink, na.rm=T)),
                                          NA,mean(len_first_zink, na.rm=T)),
            egg_guard_cat_zink = first(egg_guard_cat_zink),
            n_clutches_iv = n(),
            n_initiated = sum(!is.na(clutch_initiated_order)),
            n_visited = sum(!is.na(initiation_date)&is.na(clutch_initiated_order)),
            n_feed = sum(is.na(initiation_date)),
            started_by_initiating = first(started_by_initiating),
            ants_removed = first(ants_removed),
            females_removed = first(females_removed)) %>%
  ungroup()

zink_4A_data <- est_fecundity_clutch_zink %>%
  filter(!is.na(egg_guard_cat_zink), # remove any females that stayed longer than 20 days after init 
         started_by_initiating, # remove any females that started by visiting
         !ants_removed, !females_removed) %>% # he didn't remove ants or females
  mutate(zink4 = ifelse(egg_guard_cat_zink=="(0,4]","Remain","Abandon"),
         zink10 = ifelse(egg_guard_cat_zink %in% c("(0,4]","(4,10]"),"Remain","Abandon"),
         zink20 = ifelse(egg_guard_cat_zink=="(10,20]","Remain","Abandon"))

std.err <- function(x, na.rm = FALSE) {
 if (na.rm) x <- na.omit(x)
 sqrt(var(x) / length(x))
}

zink_Fig4_data_summary4 <- zink_4A_data %>%
  group_by(zink4) %>%
    summarize(n_broods_future_zink_m = mean(n_broods_future_zink, na.rm=T),
              n_broods_future_zink_se = std.err(n_broods_future_zink, na.rm=T),
              mean_len_future_zink_m = mean(mean_len_future_zink, na.rm=T),
              mean_len_future_zink_se = std.err(mean_len_future_zink, na.rm=T),
              mean_dur_future_zink_m = mean(mean_dur_future_zink, na.rm=T),
              mean_dur_future_zink_se = std.err(mean_dur_future_zink, na.rm=T),
              mean_len_first_zink_m = mean(mean_len_first_zink, na.rm=T),
              mean_len_first_zink_se = std.err(mean_len_first_zink), na.rm=T) %>%
  ungroup()

zink_Fig4_data_summary10 <- zink_4A_data %>%
  group_by(zink10) %>%
    summarize(n_broods_future_zink_m = mean(n_broods_future_zink, na.rm=T),
              n_broods_future_zink_se = std.err(n_broods_future_zink, na.rm=T),
              mean_len_future_zink_m = mean(mean_len_future_zink, na.rm=T),
              mean_len_future_zink_se = std.err(mean_len_future_zink, na.rm=T),
              mean_dur_future_zink_m = mean(mean_dur_future_zink, na.rm=T),
              mean_dur_future_zink_se = std.err(mean_dur_future_zink, na.rm=T),
              mean_len_first_zink_m = mean(mean_len_first_zink, na.rm=T),
              mean_len_first_zink_se = std.err(mean_len_first_zink, na.rm=T)) %>%
  ungroup()

zink_Fig4_data_summary20 <- zink_4A_data %>%
  group_by(zink20) %>%
    summarize(n_broods_future_zink_m = mean(n_broods_future_zink, na.rm=T),
              n_broods_future_zink_se = std.err(n_broods_future_zink, na.rm=T),
              mean_len_future_zink_m = mean(mean_len_future_zink, na.rm=T),
              mean_len_future_zink_se = std.err(mean_len_future_zink, na.rm=T),
              mean_dur_future_zink_m = mean(mean_dur_future_zink, na.rm=T),
              mean_dur_future_zink_se = std.err(mean_dur_future_zink, na.rm=T),
              mean_len_first_zink_m = mean(mean_len_first_zink, na.rm=T),
              mean_len_first_zink_se = std.err(mean_len_first_zink, na.rm=T)) %>%
  ungroup()

# n_broods_future_zink_m
Zink_Fig4A1 <- zink_Fig4_data_summary4 %>% 
ggplot(data=.) +
  geom_bar(aes(y = n_broods_future_zink_m, x =zink4, fill=zink4), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = n_broods_future_zink_m-n_broods_future_zink_se,
                    ymax = n_broods_future_zink_m+n_broods_future_zink_se,
                    x =zink4), width = 0.2, 
               stat = "identity", position="dodge") +
  ylim(0,0.9) + ylab("Number of future broods initiated") +
  xlab("Days 0-4") + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title = element_text(size=10))

Zink_Fig4A2 <- zink_Fig4_data_summary10 %>% 
ggplot(data=.) +
  geom_bar(aes(y = n_broods_future_zink_m, x =zink10, fill=zink10), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = n_broods_future_zink_m-n_broods_future_zink_se,
                    ymax = n_broods_future_zink_m+n_broods_future_zink_se,
                    x =zink10), width = 0.2,
               stat = "identity", position="dodge") +
  ylim(0,0.9)  +
  xlab("Days 5-10") + 
  theme(axis.title.y = element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        axis.line.y=element_blank(),
        axis.title = element_text(size=10))

Zink_Fig4A3 <- zink_Fig4_data_summary20 %>% 
ggplot(data=.) +
  geom_bar(aes(y = n_broods_future_zink_m, x =zink20, fill=zink20), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = n_broods_future_zink_m-n_broods_future_zink_se,
                    ymax = n_broods_future_zink_m+n_broods_future_zink_se,
                    x =zink20), width = 0.2 ,
               stat = "identity", position="dodge") +
  ylim(0,0.9)  +
  xlab("Days 11-20") + 
  theme(axis.title.y = element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        axis.line.y=element_blank(),
        axis.title = element_text(size=10))

# mean_len_future_zink_m
Zink_Fig4B1 <- zink_Fig4_data_summary4 %>% 
ggplot(data=.) +
  geom_bar(aes(y = mean_len_future_zink_m, x =zink4, fill=zink4), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = mean_len_future_zink_m-mean_len_future_zink_se,
                    ymax = mean_len_future_zink_m+mean_len_future_zink_se,
                    x =zink4), width = 0.2,
               stat = "identity", position="dodge") +
  ylim(0,15) + ylab("Mean size of future egg masses (mm)") +
  xlab("Days 0-4") + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title = element_text(size=10))

Zink_Fig4B2 <- zink_Fig4_data_summary10 %>% 
ggplot(data=.) +
  geom_bar(aes(y = mean_len_future_zink_m, x =zink10, fill=zink10), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = mean_len_future_zink_m-mean_len_future_zink_se,
                    ymax = mean_len_future_zink_m+mean_len_future_zink_se,
                    x =zink10), width = 0.2, 
               stat = "identity", position="dodge") +
  ylim(0,15) +
  xlab("Days 5-10") + 
  theme(axis.title.y = element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        axis.line.y=element_blank(),
        axis.title = element_text(size=10))

Zink_Fig4B3 <- zink_Fig4_data_summary20 %>% 
ggplot(data=.) +
  geom_bar(aes(y = mean_len_future_zink_m, x =zink20, fill=zink20), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = mean_len_future_zink_m-mean_len_future_zink_se,
                    ymax = mean_len_future_zink_m+mean_len_future_zink_se,
                    x =zink20), width = 0.2, 
               stat = "identity", position="dodge") +
  ylim(0,15) +
  xlab("Days 11-20") + 
  theme(axis.title.y = element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        axis.line.y=element_blank(),
        axis.title = element_text(size=10))

# mean_dur_future_zink_m
Zink_Fig4C1 <- zink_Fig4_data_summary4 %>% 
ggplot(data=.) +
  geom_bar(aes(y = mean_dur_future_zink_m, x =zink4, fill=zink4), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = mean_dur_future_zink_m-mean_dur_future_zink_se,
                    ymax = mean_dur_future_zink_m+mean_dur_future_zink_se,
                    x =zink4), width = 0.2,
               stat = "identity", position="dodge") +
  ylim(0,30) + ylab("Mean future guarding duration (days)") +
  xlab("Days 0-4") + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title = element_text(size=10))

Zink_Fig4C2 <- zink_Fig4_data_summary10 %>% 
ggplot(data=.) +
  geom_bar(aes(y = mean_dur_future_zink_m, x =zink10, fill=zink10), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = mean_dur_future_zink_m-mean_dur_future_zink_se,
                    ymax = mean_dur_future_zink_m+mean_dur_future_zink_se,
                    x =zink10), width = 0.2, 
               stat = "identity", position="dodge") +
  ylim(0,30) +
  xlab("Days 5-10") + 
  theme(axis.title.y = element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        axis.line.y=element_blank(),
        axis.title = element_text(size=10))

Zink_Fig4C3 <- zink_Fig4_data_summary20 %>% 
ggplot(data=.) +
  geom_bar(aes(y = mean_dur_future_zink_m, x =zink20, fill=zink20), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = mean_dur_future_zink_m-mean_dur_future_zink_se,
                    ymax = mean_dur_future_zink_m+mean_dur_future_zink_se,
                    x =zink20), width = 0.2, 
               stat = "identity", position="dodge") +
  ylim(0,30) +
  xlab("Days 11-20") + 
  theme(axis.title.y = element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        axis.line.y=element_blank(),
        axis.title = element_text(size=10))

ggpubr::ggarrange(Zink_Fig4A1, Zink_Fig4A2, Zink_Fig4A3,
          Zink_Fig4B1, Zink_Fig4B2, Zink_Fig4B3,
          Zink_Fig4C1, Zink_Fig4C2, Zink_Fig4C3,
          common.legend=TRUE)

# mean_len_first_zink_m
Zink_Fig4D1 <- zink_Fig4_data_summary4 %>% 
ggplot(data=.) +
  geom_bar(aes(y = mean_len_first_zink_m, x =zink4, fill=zink4), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = mean_len_first_zink_m-mean_len_first_zink_se,
                    ymax = mean_len_first_zink_m+mean_len_first_zink_se,
                    x =zink4), width = 0.2,
               stat = "identity", position="dodge") +
  ylim(0,20) + ylab("Mean size of first clutch (mm)") +
  xlab("Days 0-4") + 
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title = element_text(size=10))

Zink_Fig4D2 <- zink_Fig4_data_summary10 %>% 
ggplot(data=.) +
  geom_bar(aes(y = mean_len_first_zink_m, x =zink10, fill=zink10), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = mean_len_first_zink_m-mean_len_first_zink_se,
                    ymax = mean_len_first_zink_m+mean_len_first_zink_se,
                    x =zink10), width = 0.2, 
               stat = "identity", position="dodge") +
  ylim(0,20) +
  xlab("Days 5-10") + 
  theme(axis.title.y = element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        axis.line.y=element_blank(),
        axis.title = element_text(size=10))

Zink_Fig4D3 <- zink_Fig4_data_summary20 %>% 
ggplot(data=.) +
  geom_bar(aes(y = mean_len_first_zink_m, x =zink20, fill=zink20), 
               stat = "identity", position="dodge") +
  geom_errorbar(aes(ymin = mean_len_first_zink_m-mean_len_first_zink_se,
                    ymax = mean_len_first_zink_m+mean_len_first_zink_se,
                    x =zink20), width = 0.2, 
               stat = "identity", position="dodge") +
  ylim(0,20) +
  xlab("Days 11-20") + 
  theme(axis.title.y = element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        axis.line.y=element_blank(),
        axis.title = element_text(size=10))

ggpubr::ggarrange(Zink_Fig4A1, Zink_Fig4A2, Zink_Fig4A3,
          Zink_Fig4B1, Zink_Fig4B2, Zink_Fig4B3,
          Zink_Fig4C1, Zink_Fig4C2, Zink_Fig4C3,
          Zink_Fig4D1, Zink_Fig4D2, Zink_Fig4D3,
          ncol=3, nrow=4,
          common.legend=TRUE)
```

I think there is definitely a better way to do what Figure 4A is trying to do. Such as a logistic regression of desertion date vs. number of future broods initiated (or even binary = whether initiated a future clutch or not). Mean number of eggs in future egg masses would be better, although I would prefer to estimate the number of eggs in the lifetime directly.

### Number of clutches laid
```{r}
est_fecundity_future %>%
  filter(!females_removed) %>%
  count(desert_catL, ants_removed)

# Initiated or visited
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = n_initiated+n_visited, x = desert_catL, fill=ants_removed)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
  theme_publilia()

# Initiated only
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = n_initiated, x = desert_catL, fill=ants_removed)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  theme_publilia()

# Visited only
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = n_visited, x = desert_catL, fill=ants_removed)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  theme_publilia()

# Feed only
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = n_feed, x = desert_catL, fill=ants_removed)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  theme_publilia()

```

### Mean size of clutches
```{r}
## tbL
# First clutch
est_fecundity_clutch %>%
  filter(!females_removed, clutch_initiated_order==1) %>%
  left_join(select(est_fecundity_future, location, Female_ID, desert_catL, visited_cat)) %>%
  ggplot(data=., aes(y = mean_t5eggs, x = desert_catL, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Total size of first clutch (number of eggs)")

# Mean for future clutches
est_fecundity_clutch %>%
  filter(!females_removed, clutch_initiated_order>1) %>%
  left_join(select(est_fecundity_future, Female_ID, desert_catL, visited_cat)) %>%
  filter(!is.na(desert_catL)) %>% # not sure why E_Gkgg doesn't have a desert_catL
  group_by(Female_ID) %>%
  mutate(mean_eggs_future_clutches = mean(mean_t5eggs, na.rm=T)) %>%
  ungroup() %>%
  ggplot(data=., aes(y = mean_eggs_future_clutches, x = desert_catL, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Mean size of future clutches (number of eggs)")

## tbS
# First clutch
est_fecundity_clutch %>%
  filter(!females_removed, clutch_initiated_order==1) %>%
  left_join(select(est_fecundity_future, location, Female_ID, desert_catS, visited_cat)) %>%
  ggplot(data=., aes(y = mean_t5eggs, x = desert_catS, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Total size of first clutch (number of eggs)")

# Mean for future clutches
est_fecundity_clutch %>%
  filter(!females_removed, clutch_initiated_order>1) %>%
  left_join(select(est_fecundity_future, Female_ID, desert_catS, visited_cat)) %>%
  filter(!is.na(desert_catS)) %>% # not sure why E_Gkgg doesn't have a desert_catL
  group_by(Female_ID) %>%
  mutate(mean_eggs_future_clutches = mean(mean_t5eggs, na.rm=T)) %>%
  ungroup() %>%
  ggplot(data=., aes(y = mean_eggs_future_clutches, x = desert_catS, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Mean size of future clutches (number of eggs)")
```

### Mean guarding duration
```{r}
## tbL
# Mean for future clutches
est_fecundity_clutch %>%
  filter(!females_removed, clutch_initiated_order>1) %>%
  left_join(select(est_fecundity_future, Female_ID, desert_catL, visited_cat)) %>%
  filter(!is.na(desert_catL)) %>% # not sure why E_Gkgg doesn't have a desert_catL
  group_by(Female_ID) %>%
  mutate(mean_init_durL_future_clutches = mean(init_durL, na.rm=T)) %>%
  ungroup() %>%
  ggplot(data=., aes(y = mean_init_durL_future_clutches, x = desert_catL, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Mean guarding duration on future clutches")

## tbS
# Mean for future clutches
est_fecundity_clutch %>%
  filter(!females_removed, clutch_initiated_order>1) %>%
  left_join(select(est_fecundity_future, Female_ID, desert_catS, visited_cat)) %>%
  filter(!is.na(desert_catS)) %>% # not sure why E_Gkgg doesn't have a desert_catL
  group_by(Female_ID) %>%
  mutate(mean_init_durS_future_clutches = mean(init_durS, na.rm=T)) %>%
  ungroup() %>%
  ggplot(data=., aes(y = mean_init_durS_future_clutches, x = desert_catS, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Mean guarding duration on future clutches")
```

### Estimated lifetime number of eggs laid
Note: I think if I wanted to try a "no tie-breaks" version I would have to calculate est_eggs_future_sc2h and desert_cat from scratch.
```{r}
### Both one-clutch and multi-clutch females.
## tbL
# Estimated future fecundity
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = est_eggs_futureL_sc2h, x = desert_catL, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Estimated future eggs laid") +
  ylim(0,400)

## tbS
# Estimated future fecundity
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = est_eggs_futureS_sc2h, x = desert_catS, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Estimated future eggs laid") +
  ylim(0,400)

## tbL
# Estimated lifetime fecundity
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = est_eggs_lifeL_sc2h, x = desert_catL, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Estimated eggs laid in life") +
  ylim(0,400)

## tbS
# Estimated lifetime fecundity
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = est_eggs_lifeS_sc2h, x = desert_catS, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Estimated eggs laid in life") +
  ylim(0,400)

### Separating one-clutch and multi-clutch females.
## tbL
# Estimated future fecundity
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = est_eggs_futureL_sc2h, x = desert_catL, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Estimated future eggs laid") +
  ylim(0,400) +
  facet_wrap(vars(n_clutches_iv>1),nrow=1)

## tbS
# Estimated future fecundity
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = est_eggs_futureS_sc2h, x = desert_catS, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Estimated future eggs laid") +
  ylim(0,400) +
  facet_wrap(vars(n_clutches_iv>1),nrow=1)

## tbL
# Estimated lifetime fecundity
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = est_eggs_lifeL_sc2h, x = desert_catL, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Estimated eggs laid in life") +
  ylim(0,400) +
  facet_wrap(vars(n_clutches_iv>1),nrow=1)

## tbS
# Estimated lifetime fecundity
est_fecundity_future %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(y = est_eggs_lifeS_sc2h, x = desert_catS, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() +
  ylab("Estimated eggs laid in life") +
  ylim(0,400) +
  facet_wrap(vars(n_clutches_iv>1),nrow=1)
```

## How do the lifetime fecundities of females change with their longevity?
Would one strategy be more advantageous to short-lived females than long-lived females?
```{r}
## tbL
# Estimated lifetime fecundity
est_fecundity_future %>%
  filter(n_clutches_iv==2) %>%
  ggplot(data=., aes(y = est_eggs_lifeL_sc2h, x = desert_catL), fill="white") +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_jitter(pch = 21, size=3, fill="white", width=0.35) +
  theme_publilia() +
  ylab("Estimated eggs laid in life") +
  ylim(0,400) +
  facet_wrap(vars(n_visited),nrow=1)
```

## Zink 2005 Figs 1, 2 and 3

### Fig 1
"The distribution of primary female guarding periods showed that many females leave immediately after egg laying but others remain well through hatching (Fig. 1A). While secondary females arrived at all times after brood initiation, their arrivals were clustered around the early days after brood initiation (Fig. 1B). Regardless of arrival time, secondary females rarely stayed longer than a few days (Fig. 1C), freeing them to lay additional clutches elsewhere on the plant. For the majority of these behaviors (88% of total) a secondary female did not switch plants (groups) between the previous brood and the host brood, confirming that females are primarily searching for hosts within their own group. Many females acted both as primary and second- ary females over the course of their lifetime. There was no greater chance that a female repeated the same tactic versus switched tactics from first to second brood for 1998 (c2=0.02, df=1, P=0.88) and 1999 (c2=1.00, df=1, P=0.32). There was also no pattern between the second and third broods in 1998 (c2=0.16, df=1, P=0.69) and 1999 (c2=0.08, df=1, P=0.78)."

### Fig 2
"Females that exhibited the secondary tactic did not exhibit any reduction in the ability to initiate primary egg masses. Across all females in 1998, there was no relationship between the number of secondary broods a female laid and the total number of primary broods she initiated over her lifetime (r=􏳸0.02, n=478, P=0.63). Taking all females that exhibited the primary tactic and separating them into those that did and did not lay secondary eggs across their lifetimes revealed no difference in the total number of primary egg masses initiated (Z=0.2, n1=231, n2=196,P=0.84). A comparison of the same two groups revealed no difference in the size of primary egg masses (as averaged within females; Z=1.8, n1=231, n2=196, P=0.08)."
```{r}
est_fecundity_clutch %>%
  distinct(location, visited, num_at_init, mean_t5eggs, ants_removed, females_removed) %>%
  #filter(females_removed) %>%
  filter(!is.na(females_removed)) %>% # why is this necessary?
  ggplot(data=., aes(x=visited|num_at_init>1, y=mean_t5eggs, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  scale_x_discrete(labels=c("Not visited","Visited")) +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("white","brown1")) +
  ylab("Total number of eggs laid in clutch") +
  theme_publilia() +
  theme(axis.title.x = element_blank()) +
  facet_wrap(vars(females_removed), nrow=1) +
  ggtitle("Female removal")

est_fecundity_clutch %>%
  distinct(location, visited, num_at_init, mean_t5eggs, ants_removed, females_removed) %>%
  filter(!females_removed) %>%
  filter(!is.na(females_removed)) %>% # why is this necessary?
  ggplot(data=., aes(x=visited|num_at_init>1, y=mean_t5eggs, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.9), outlier.shape=NA, size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  scale_x_discrete(labels=c("Not visited","Visited")) +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("white","brown1")) +
  ylab("Total number of eggs laid in clutch") +
  theme_publilia() +
  theme(axis.title.x = element_blank())

est_fecundity_clutch %>%
  distinct(location, visited, num_at_init, mean_t5eggs, ants_removed, females_removed) %>%
  #filter(females_removed) %>%
  filter(!is.na(females_removed)) %>% # why is this necessary?
  ggplot(data=., aes(x=visited|num_at_init>1, y=mean_t5eggs), fill="white") +
  geom_boxplot(outlier.shape=NA, size = 1.5) +
  geom_jitter(pch = 21, size=3, fill="white", width=0.35) +
  scale_x_discrete(labels=c("Not visited","Visited")) +
  ylab("Total number of eggs laid in clutch") +
  theme_publilia() +
  theme(axis.title.x = element_blank()) +
  facet_wrap(vars(females_removed), nrow=1) +
  ggtitle("Female removal")
```

### Fig 3 - Estimated lifetime fecundity
"Figure 2 reveals that, on average, primary females lay approximately 67% of eggs in a shared egg mass (70 out of 105 eggs). Adjusting for the average number of secondary females per brood, 1.47 (0.06), an individual secondary female is expected to contribute 23% of the eggs in a communal clutch. In unshared egg masses all counted eggs were attributed to the primary female but in shared egg masses the overall number of counted eggs were allocated to primary females and secondary females according to these estimates. Lifetime fecundity was then calculated as the total number of eggs laid by a female across all of her broods (both primary and secondary)."

** Note that I think the "sensu Zink" values are calculated wrong here. I think they double/multi-count the number of eggs for clutches there are more than one female on a given clutch.
```{r}
est_fecundity_clutch %>%
  filter(!is.na(initiation_date), !females_removed) %>%
  mutate(est_fecundity_clutch_z05 = ifelse(mom_at_init, mean_t5eggs*0.67, mean_t5eggs*0.23)) %>%
  group_by(Female_ID) %>%
    summarize(est_fecundity_life_z05 = sum(est_fecundity_clutch_z05, na.rm=T),
              init_visit_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "Initiated only"),
                                           ifelse(!any(mom_at_init), "Visited only", NA)),
              one_or_both_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "One"),
                                           ifelse(!any(mom_at_init), "One", NA)),
              ants_removed = first(ants_removed)) %>%
  ungroup() %>%
  ggplot(data=., aes(x=init_visit_life_tactic, y=est_fecundity_life_z05, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("white","brown1")) +
  scale_x_discrete(limits=c("Initiated only", "Both", "Visited only")) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu Zink 2005")))) +
  theme_publilia() +
  theme(axis.title.x = element_blank())

est_fecundity_clutch %>%
  mutate(est_eggs_futureL_sc2h = est_eggs_lifeL_sc2h - est_eggs_clutchL_sc2h,
         est_eggs_futureS_sc2h = est_eggs_lifeS_sc2h - est_eggs_clutchS_sc2h,
         desert_catL = ifelse(desert_rel2hL <= -16, "desert",
                             ifelse(desert_rel2hL > -16 & desert_rel2hL <= 4,
                                    "eggs","nymphs")),
         visited_cat = ifelse(`visited in 4 days` == "Visited", "vis", "not"),
         desert_catS = ifelse(desert_rel2hS <= -16, "desert",
                             ifelse(desert_rel2hS > -16 & desert_rel2hS <= 4,
                                    "eggs","nymphs"))) %>%
  distinct(Female_ID, init_visit_life_tactic, est_eggs_lifeL_sc2h, ants_removed, females_removed) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=init_visit_life_tactic, y=est_eggs_lifeL_sc2h, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5) +
  #geom_jitter(pch = 21, size=3, fill="white", width=0.35) +
  scale_x_discrete(limits=c("Initiated only", "Both", "Visited only")) +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("white","brown1")) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi")))) +
  theme_publilia() +
  theme(axis.title.x = element_blank())

est_fecundity_clutch %>%
  filter(!is.na(initiation_date)) %>%
  filter(!females_removed) %>%
  #filter(clutch_visited_order>0) %>% # don't include females that were present before init or after hatch
  mutate(est_fecundity_clutch_z05 = ifelse(mom_at_init, mean_t5eggs*0.67, mean_t5eggs*0.23)) %>%
  group_by(Female_ID) %>%
    summarize(est_fecundity_life_z05 = sum(est_fecundity_clutch_z05, na.rm=T),
              init_visit_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "Initiated only"),
                                           ifelse(!any(mom_at_init), "Visited only", NA)),
              ants_removed = first(ants_removed)) %>%
  ungroup() %>%
  ggplot(data=., aes(x=init_visit_life_tactic, y=est_fecundity_life_z05), fill=NA) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, fill="white", width=0.35) +
  scale_x_discrete(limits=c("Initiated only", "Both", "Visited only")) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu Zink 2005")))) +
  ylim(0,200) + # this omits one outlier
  theme_publilia() +
  theme(axis.title.x = element_blank())

est_fecundity_clutch %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Female_ID, init_visit_life_tactic, est_eggs_lifeL_sc2h, ants_removed, females_removed, n_clutches_iv) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=init_visit_life_tactic, y=est_eggs_lifeL_sc2h), fill=NA) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, fill="white", width=0.35) +
  scale_x_discrete(limits=c("Initiated only", "Both", "Visited only")) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi")))) +
  ylim(0,200) + # this omits one outlier
  theme_publilia() +
  theme(axis.title.x = element_blank())

est_fecundity_clutch %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Female_ID, init_visit_life_tactic, est_eggs_lifeL_sc2h, ants_removed, females_removed, n_clutches_iv) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=init_visit_life_tactic, y=est_eggs_lifeL_sc2h), fill=NA) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, fill="white", width=0.35) +
  scale_x_discrete(limits=c("Initiated only", "Both", "Visited only")) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi")))) +
  ylim(0,200) + # this omits one outlier
  theme_publilia() +
  theme(axis.title.x = element_blank()) +
  facet_wrap(vars(n_clutches_iv>1), nrow=1) +
  ggtitle("initiated or visited more than one clutch")

est_fecundity_clutch %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Female_ID, init_visit_life_tactic, est_eggs_lifeL_sc2h, ants_removed, females_removed, n_clutches_iv) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=init_visit_life_tactic, y=est_eggs_lifeL_sc2h, fill=n_clutches_iv>1)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  scale_x_discrete(limits=c("Initiated only", "Both", "Visited only")) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi")))) +
  ylim(0,200) + # this omits one outlier
  theme_publilia() +
  theme(axis.title.x = element_blank()) +
  ggtitle("initiated or visited more than one clutch")

est_fecundity_clutch %>%
  filter(!is.na(initiation_date)) %>%
  filter(!females_removed) %>%
  #filter(clutch_visited_order>0) %>% # don't include females that were present before init or after hatch
  mutate(est_fecundity_clutch_z05 = ifelse(mom_at_init, mean_t5eggs*0.67, mean_t5eggs*0.23)) %>%
  group_by(Female_ID) %>%
    summarize(est_fecundity_life_z05 = sum(est_fecundity_clutch_z05, na.rm=T),
              init_visit_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "Initiated only"),
                                           ifelse(!any(mom_at_init), "Visited only", NA)),
              ants_removed = first(ants_removed),
              n_clutches_iv = first(n_clutches_iv)) %>%
  ungroup() %>%
  ggplot(data=., aes(x=init_visit_life_tactic, y=est_fecundity_life_z05, fill=n_clutches_iv>1)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  scale_x_discrete(limits=c("Initiated only", "Both", "Visited only")) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu Zink 2005")))) +
  ylim(0,200) + # this omits one outlier
  theme_publilia() +
  theme(axis.title.x = element_blank()) +
  ggtitle("initiated or visited more than one clutch")

est_fecundity_clutch %>%
  filter(!is.na(initiation_date)) %>%
  filter(!females_removed) %>%
  filter(clutch_visited_order>0) %>% # don't include females that were present before init or after hatch
  mutate(est_fecundity_clutch_z05 = ifelse(mom_at_init, mean_t5eggs*0.67, mean_t5eggs*0.23)) %>%
  group_by(Female_ID) %>%
    summarize(est_fecundity_life_z05 = sum(est_fecundity_clutch_z05, na.rm=T),
              init_visit_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "Initiated only"),
                                           ifelse(!any(mom_at_init), "Visited only", NA)),
              ants_removed = first(ants_removed),
              n_clutches_iv = first(n_clutches_iv)) %>%
  ungroup() %>%
  ggplot(data=., aes(x=init_visit_life_tactic, y=est_fecundity_life_z05), fill=NA) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, fill="white", width=0.35) +
  scale_x_discrete(limits=c("Initiated only", "Both", "Visited only")) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu Zink 2005")))) +
  ylim(0,200) + # this omits one outlier
  theme_publilia() +
  theme(axis.title.x = element_blank()) +
  facet_wrap(vars(n_clutches_iv>1), nrow=1) +
  ggtitle("initiated or visited more than one clutch")

est_fecundity_clutch %>%
  filter(!is.na(initiation_date)) %>%
  mutate(est_fecundity_clutch_z05 = ifelse(mom_at_init, mean_t5eggs*0.67, mean_t5eggs*0.23)) %>%
  group_by(Female_ID) %>%
    summarize(est_fecundity_life_z05 = sum(est_fecundity_clutch_z05, na.rm=T),
              init_visit_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "Initiated only"),
                                           ifelse(!any(mom_at_init), "Visited only", NA)),
              ants_removed = first(ants_removed),
              n_clutches_iv = first(n_clutches_iv)) %>%
  ungroup() %>%
  ggplot(data=., aes(x=init_visit_life_tactic, y=est_fecundity_life_z05, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("white","brown1")) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu Zink 2005")))) +
  theme_publilia() +
  theme(axis.title.x = element_blank()) +
  facet_wrap(vars(n_clutches_iv>1), nrow=1)

est_fecundity_clutch %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Female_ID, init_visit_life_tactic, est_eggs_lifeL_sc2h, ants_removed, females_removed, n_clutches_iv) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=init_visit_life_tactic, y=est_eggs_lifeL_sc2h, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  scale_x_discrete(limits=c("Initiated only", "Both", "Visited only")) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi")))) +
  theme_publilia() +
  theme(axis.title.x = element_blank()) +
  facet_wrap(vars(n_clutches_iv>1), nrow=1)

```

Same calculations of lifetime fecundity for different desertion strategies
```{r}
est_fecundity_life_strats <- est_fecundity_clutch %>%
  group_by(Female_ID) %>%
  # clutch visited order == 0 means she visited before initiation, so it shouldn't count
  mutate(started_by =
           ifelse(any(clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order==1),
                  "initiating",
                  ifelse(any(clutch_visited_order==1&is.na(clutch_initiated_order)),
                         "visiting", "other")),
         n_clutches_with_eggs_iv = sum(!is.na(clutch_visited_order)&(clutch_visited_order>0), na.rm=T)) %>%
  ungroup() %>%
  filter(clutch_visited_order==1) %>%
  mutate(desert_catL_v2 = ifelse(started_by=="initiating",
                                 ifelse(desert_rel2hL <= -16, "desert",
                                        ifelse(desert_rel2hL > -16 & desert_rel2hL <= 4, "eggs", 
                                               ifelse(desert_rel2hL >= 4,"nymphs",
                                                      NA))),
                                 ifelse(started_by=="visiting", "visit", 
                                        NA)),
         desert_catS_v2 = ifelse(started_by=="initiating",
                                 ifelse(desert_rel2hS <= -16, "desert",
                                        ifelse(desert_rel2hS > -16 & desert_rel2hS <= 4, "eggs", 
                                               ifelse(desert_rel2hS >= 4,"nymphs",
                                                      NA))),
                                 ifelse(started_by=="visiting", "visit", 
                                        NA)),
         desert_catL_v3 = ifelse(started_by=="initiating",
                                 ifelse(desert_rel2hL <= -16, "desert",
                                        ifelse(desert_rel2hL > -16 & desert_rel2hL <= 4, "eggs", 
                                               ifelse(desert_rel2hL >= 4,"nymphs",
                                                      NA))),
                                 init_visit_life_tactic),
         desert_catS_v3 = ifelse(started_by=="initiating",
                                 ifelse(desert_rel2hS <= -16, "desert",
                                        ifelse(desert_rel2hS > -16 & desert_rel2hS <= 4, "eggs", 
                                               ifelse(desert_rel2hS >= 4,"nymphs",
                                                      NA))),
                                 init_visit_life_tactic),
         first_clutch_visited_in4d = ifelse(started_by=="initiating",
                                            ifelse(`visited in 4 days` == "Visited", "vis", "not"),
                                            NA)) %>%
  distinct(Female_ID, ants_removed, females_removed, `visited in 4 days`,
           desert_catL_v2, desert_catL_v3, desert_catS_v2, desert_catS_v3,
           started_by, init_visit_life_tactic, one_both_life_tactic,
           first_clutch_visited_in4d, est_eggs_lifeL_sc2h, est_eggs_lifeS_sc2h,
           n_clutches_with_eggs_iv)

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_catL_v3, y=est_eggs_lifeL_sc2h, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi")))) +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia()

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_catL_v2, y=est_eggs_lifeL_sc2h, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi")))) +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia()

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_catL_v2, y=est_eggs_lifeL_sc2h, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(init_visit_life_tactic))

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_catL_v2, y=est_eggs_lifeS_sc2h, fill=desert_catL_v2)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  ylab("Estimated lifetime fecundity (eggs)")  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1), nrow=1)

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_catS_v2, y=est_eggs_lifeS_sc2h, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1, init_visit_life_tactic))

est_fecundity_life_strats %>%
  filter(!females_removed, # not sure where the NAs come from!
         !is.na(n_clutches_with_eggs_iv), !is.na(init_visit_life_tactic)) %>%
  ggplot(data=., aes(x=desert_catS_v2, y=est_eggs_lifeS_sc2h, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1, init_visit_life_tactic))

est_fecundity_life_strats %>%
  filter(!females_removed, # not sure where the NAs come from!
         !is.na(n_clutches_with_eggs_iv), !is.na(one_both_life_tactic)) %>%
  ggplot(data=., aes(x=desert_catS_v2, y=est_eggs_lifeS_sc2h), fill="white") +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, fill="white", width=0.35) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1, one_both_life_tactic), nrow=1)

est_fecundity_clutch %>%
  mutate(desert_catL = ifelse(desert_rel2hL <= -16, "desert",
                             ifelse(desert_rel2hL > -16 & desert_rel2hL <= 4,
                                    "eggs","nymphs")),
         visited_cat = ifelse(`visited in 4 days` == "Visited", "vis", "not"),
         desert_catS = ifelse(desert_rel2hS <= -16, "desert",
                             ifelse(desert_rel2hS > -16 & desert_rel2hS <= 4,
                                    "eggs","nymphs")),
         desert_catL_v2 = ifelse(!started_by_initiating, "visited first",
                                 ifelse(desert_rel2hL <= -16, "desert",
                                        ifelse(desert_rel2hL > -16 & desert_rel2hL <= 4,
                                               "eggs",
                                               ifelse(desert_rel2hL >= 4,"nymphs",NA))))) %>%
  filter(!females_removed, is.na(desert_catL_v2))
```

on the adaptive value of deserting early:
 - is deserting your first clutch early an adaptive reproductive strategy? 
 - under what circumstances would it be adaptive vs maladaptive?
  - low expected lifespan?
  - large number of available host eggs?
```{r}
est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  #filter(desert_catL_v2 %in% c("desert","eggs")) %>%
  filter(!is.na(init_visit_life_tactic), !is.na(desert_catL_v2)) %>% # need to figure out why this there are NAs
  ggplot(data=., aes(x=desert_catL_v2, y=est_eggs_lifeS_sc2h, 
                     fill=init_visit_life_tactic)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia()

est_fecundity_life_strats %>%
  filter(females_removed) %>%
  #filter(desert_catL_v2 %in% c("desert","eggs")) %>%
  filter(!is.na(init_visit_life_tactic), !is.na(desert_catL_v2)) %>% # need to figure out why this there are NAs
  ggplot(data=., aes(x=desert_catL_v2, y=est_eggs_lifeS_sc2h, 
                     fill=init_visit_life_tactic)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia()

est_fecundity_life_strats %>%
  filter(females_removed, n_clutches_with_eggs_iv==2) %>%
  #filter(desert_catL_v2 %in% c("desert","eggs")) %>%
  filter(!is.na(init_visit_life_tactic), !is.na(desert_catL_v2)) %>% # need to figure out why this there are NAs
  ggplot(data=., aes(x=desert_catL_v2, y=est_eggs_lifeS_sc2h, 
                     fill=init_visit_life_tactic)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia()

est_fecundity_life_strats %>%
  filter(females_removed) %>%
  #filter(desert_catL_v2 %in% c("desert","eggs")) %>%
  filter(!is.na(init_visit_life_tactic), !is.na(desert_catL_v2)) %>% # need to figure out why this there are NAs
  ggplot(data=., aes(x=desert_catL_v2, y=n_clutches_with_eggs_iv, 
                     fill=init_visit_life_tactic)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab("Number of clutches initiated and visited")  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia()

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  #filter(desert_catL_v2 %in% c("desert","eggs")) %>%
  filter(!is.na(init_visit_life_tactic), !is.na(desert_catL_v2)) %>% # need to figure out why this there are NAs
  ggplot(data=., aes(x=desert_catL_v2, y=n_clutches_with_eggs_iv, 
                     fill=init_visit_life_tactic)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab("Number of clutches initiated and visited")  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia()

est_fecundity_life_strats %>%
  filter(!females_removed, n_clutches_with_eggs_iv>1) %>%
  #filter(desert_catL_v2 %in% c("desert","eggs")) %>%
  filter(!is.na(init_visit_life_tactic), !is.na(desert_catL_v2)) %>% # need to figure out why this there are NAs
  ggplot(data=., aes(x=desert_catL_v2, y=est_eggs_lifeS_sc2h, 
                     fill=init_visit_life_tactic)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  xlab("Reproductive strategy for first clutch") +
  ylim(c(0,300)) +
  theme_publilia()

est_fecundity_life_strats %>%
  filter(!females_removed, n_clutches_with_eggs_iv==2) %>%
  #filter(desert_catL_v2 %in% c("desert","eggs")) %>%
  filter(!is.na(init_visit_life_tactic), !is.na(desert_catL_v2)) %>% # need to figure out why this there are NAs
  ggplot(data=., aes(x=desert_catL_v2, y=est_eggs_lifeS_sc2h, 
                     fill=init_visit_life_tactic)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  xlab("Reproductive strategy for first clutch") +
  ylim(c(0,300)) +
  theme_publilia()

```

early-visited clutches: stay vs. go
```{r}
est_fecundity_life_strats %>%
  filter(!females_removed, `visited in 4 days`=="Visited", desert_catL_v2!="visit") %>%
  ggplot(data=., aes(x=desert_catL_v2=="desert", y=est_eggs_lifeL_sc2h, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi")))) +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  ggtitle("early-visited clutches: stay vs. go")

est_fecundity_strat_cats %>%
  filter(!females_removed, `visited in 4 days`=="Visited", desert_catL!="visit") %>%
  ggplot(data=., aes(x=desert_catL=="desert", y=est_eggs_futureL_sc2h, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi")))) +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  ggtitle("early-visited clutches: stay vs. go")

est_fecundity_life_strats %>%
  filter(!females_removed, `visited in 4 days`=="Visited", desert_catS_v2!="visit") %>%
  ggplot(data=., aes(x=desert_catS_v2=="desert", y=est_eggs_lifeS_sc2h, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi")))) +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  ggtitle("early-visited clutches: stay vs. go")

est_fecundity_strat_cats %>%
  filter(!females_removed, `visited in 4 days`=="Visited", desert_catS!="visit") %>%
  ggplot(data=., aes(x=desert_catS=="desert", y=est_eggs_futureS_sc2h, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi")))) +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  ggtitle("early-visited clutches: stay vs. go")

## do early-visited clutches EVER get adopted?
visited_1st_4d_data_tb %>%
  left_join(est_fecundity_strat_cats) %>%
  filter(`visited in 4 days`=="Visited", clutch_visited_order>0,
         !females_removed)

visited_1st_4d_data_tb %>%
  left_join(est_fecundity_strat_cats) %>%
  left_join(first_visit_cuts) %>%
  filter(`visited in 4 days`=="Visited", clutch_visited_order>0,
         !females_removed, num_at_init==1) %>%
  group_by(location) %>%
    mutate(n_moms = n()) %>%
  ungroup() %>%
  filter(n_moms==2) %>%
  ggplot(data=., aes(x=mom_at_init, y=guard_duration)) +
  geom_jitter(aes(color=first_visit_starts)) + 
  theme_publilia() + 
  scale_colour_gradientn(colours=rainbow(4)) +
  xlab("initiator")

visited_1st_4d_data_tb %>%
  left_join(est_fecundity_strat_cats) %>%
  left_join(first_visit_cuts) %>%
  filter(`visited in 4 days`=="Visited", clutch_visited_order>0,
         !females_removed, num_at_init==1) %>%
  group_by(location) %>%
    mutate(n_moms = n()) %>%
  ungroup() %>%
  filter(n_moms==2) %>%
  ggplot(data=., aes(x=mom_at_init, y=guard_duration, group=location)) +
  geom_line(aes(color=first_visit_starts)) + 
  geom_point(size = 2) +
  #geom_text(aes(color=mom_at_init), hjust=0, vjust=0) +
  theme_publilia() + 
  scale_colour_gradientn(colours=rainbow(4)) +
  xlab("initiator")

visited_1st_4d_data_tb %>%
  left_join(est_fecundity_strat_cats) %>%
  left_join(first_visit_cuts) %>%
  filter(`visited in 4 days`=="Visited", clutch_visited_order>0,
         !females_removed) %>%
  group_by(location) %>%
    mutate(n_moms = n()) %>%
  ungroup() %>%
  ggplot(data=., aes(x=mom_at_init, y=guard_duration, group=location)) +
  geom_line(aes(color=n_moms)) + 
  geom_point(size = 2) +
  #geom_text(aes(color=mom_at_init), hjust=0, vjust=0) +
  theme_publilia() + 
  scale_colour_gradientn(colours=rainbow(4)) +
  xlab("initiator")

visited_1st_4d_data_tb %>%
  left_join(est_fecundity_strat_cats) %>%
  left_join(first_visit_cuts) %>%
  filter(`visited in 4 days`=="Visited", clutch_visited_order>0,
         !females_removed) %>%
  group_by(location) %>%
    mutate(n_moms = n()) %>%
  ungroup() %>%
  ggplot(data=., aes(x=mom_at_init, y=guard_duration, group=location)) +
  geom_line(size=4, alpha=0.25) + 
  geom_point(size = 2) +
  #geom_text(aes(color=mom_at_init), hjust=0, vjust=0) +
  theme_publilia() +
  xlab("initiator")

visited_1st_4d_data_tb %>%
  left_join(est_fecundity_strat_cats) %>%
  left_join(first_visit_cuts) %>%
  filter(`visited in 4 days`=="Visited", clutch_visited_order>0,
         !females_removed, num_at_init==1) %>%
  group_by(location) %>%
    mutate(n_moms = n()) %>%
  ungroup() %>%
  filter(n_moms==2) %>%
  ggplot(data=., aes(x=mom_at_init, y=guard_duration, group=location)) +
  geom_line(aes(color=first_visit_starts)) + 
  geom_point(size = 2) +
  #geom_text(aes(color=mom_at_init), hjust=0, vjust=0) +
  theme_publilia() + 
  scale_colour_gradientn(colours=rainbow(4)) +
  xlab("initiator")

# 
visited_1st_4d_data_tb %>%
  left_join(est_fecundity_strat_cats) %>%
  left_join(first_visit_cuts) %>%
  filter(`visited in 4 days`=="Visited") %>%
  filter(!females_removed, ants_removed) %>%
  group_by(location) %>%
    mutate(n_moms = n()) %>%
  ungroup() %>%
  filter(n_moms==2) %>%
ggplot(data=., aes(x=location, y = guard_duration, color=mom_at_init)) +
  geom_point(alpha=0.50)

```

What is the probability that a clutch will be guarded until hatching for clutches that were visited in the first four days vs. not visited? Could it be that there is a significant chance that a visiting female will adopt a clutch she visits?
```{r}
# no tie breaks
visited_1st_4d_data %>%
  filter(!females_removed, !is.na(initiation_date),
         !(visit_ends<initiation_date), # visits that end before initiation are irrelevant
         !(visit_starts>est_hatch+4)) %>% # there are a few cases where clutches are visited long after hatching, which wouldn't affect hatching success
  left_join(first_visit_cuts) %>%
  select(Female_ID:visit_ends, initiation_date, est_hatch, est_rel2h, 
         `visited in 4 days`, mom_at_init, ants_removed, females_removed) %>%
  group_by(location) %>%
  filter(any(mom_at_init)) %>% # remove any clutches where there was no apparent mother at initiation
  summarize(last_des_rel2h = max(ifelse(visit_starts<=initiation_date, est_rel2h, NA), na.rm=T),
            first_des_rel2h_init = min(ifelse(mom_at_init, est_rel2h, NA), na.rm=T),
            last_desert = ifelse(last_des_rel2h>=-2, "after hatch",
                                 ifelse(last_des_rel2h<=0, "before hatch", NA)),
            females_removed = first(females_removed),
            ants_removed = first(ants_removed),
            `visited in 4 days` = first(`visited in 4 days`),
            init_desert_early = ifelse(first(first_des_rel2h_init<=-16), "deserted early", "didn't desert early")) %>%
  ungroup() %>%
  filter(!is.na(`visited in 4 days`)) %>% # E40_9 for some reason didn't get a valid visited in 4 days entry
  filter(location!="A23_8") %>% # A23_8 has two moms at init but for some reason not `visited in 4 days`?
ggplot(data=., aes(x=`visited in 4 days`, y=last_des_rel2h, fill = init_desert_early)) +
  geom_boxplot(size = 1.5) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab("Latest desertion date relative to hatch") +
  theme_publilia() #+
  #facet_wrap(vars(ants_removed), nrow=1)
```

Can I do the same as above but looking at future fecundity or hatching success? This could be a big factor in why females desert when visited.
```{r}
# no tie breaks
life_strats_firstlast_des <- visited_1st_4d_data %>%
  filter(!females_removed, !is.na(initiation_date),
         !(visit_ends<initiation_date), # visits that end before initiation are irrelevant
         !(visit_starts>est_hatch+4)) %>% # there are a few cases where clutches are visited long after hatching, which wouldn't affect hatching success
  left_join(first_visit_cuts) %>%
  select(Female_ID:visit_ends, initiation_date, est_hatch, est_rel2h, 
         `visited in 4 days`, mom_at_init, ants_removed, females_removed) %>%
  group_by(location) %>%
  filter(any(mom_at_init)) %>% # remove any clutches where there was no apparent mother at initiation
  summarize(FemID_last_des_rel2h = # Picks one female if there is a tie, but that's ok
              Female_ID[which.max(ifelse(visit_starts<=initiation_date, est_rel2h, NA))], 
            FemID_first_des_rel2h_init =
              Female_ID[which.min(ifelse(mom_at_init, est_rel2h, NA))],
    last_des_rel2h = max(ifelse(visit_starts<=initiation_date, est_rel2h, NA), na.rm=T),
            first_des_rel2h_init = min(ifelse(mom_at_init, est_rel2h, NA), na.rm=T),
            last_desert = ifelse(last_des_rel2h>=-2, "after hatch",
                                 ifelse(last_des_rel2h<=0, "before hatch", NA)),
            females_removed = first(females_removed),
            ants_removed = first(ants_removed),
            `visited in 4 days` = first(`visited in 4 days`),
            init_desert_early = ifelse(first(first_des_rel2h_init<=-16), "deserted early", "didn't desert early")) %>%
  ungroup() %>%
  filter(!is.na(`visited in 4 days`)) %>% # E40_9 for some reason didn't get a valid visited in 4 days entry
  filter(location!="A23_8") # A23_8 has two moms at init but for some reason not `visited in 4 days`?

life_strats_firstlast_des %>%
ggplot(data=., aes(x=`visited in 4 days`, y=last_des_rel2h, fill = init_desert_early)) +
  geom_boxplot() +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  theme_publilia() #+
  #facet_wrap(vars(ants_removed), nrow=1)

est_fecundity_clutch_life_strats_firstlast_des <- visited_1st_4d_data_tb %>%
  group_by(Female_ID) %>%
  mutate(started_by_initiating =
           any(clutch_visited_order==1&clutch_initiated_order==1)) %>%
  ungroup() %>%
  select(location, Female_ID, clutch_visited_order, clutch_initiated_order, desert_rel2h = est_rel2h,
         mom_at_init, `visited in 4 days`, started_by_initiating) %>%
  left_join(clutch_egg_num_data, by=c("location")) %>%
  right_join(select(life_strats_firstlast_des,
                    location, FemID_first_des_rel2h_init, first_des_rel2h_init,
                    last_des_rel2h, init_desert_early),
             by=c("Female_ID"="FemID_first_des_rel2h_init")) %>%
  mutate(est_eggs_clutchS_sc2h = n_eggs*(initMb4h_sc2hS/mDb4h_sc2h),
         est_eggs_clutchL_sc2h = n_eggs*(initMb4h_sc2hL/mDb4h_sc2h)) %>%
  group_by(Female_ID) %>%
    mutate(est_eggs_lifeL_sc2h = sum(est_eggs_clutchL_sc2h, na.rm = TRUE),
           est_eggs_lifeS_sc2h = sum(est_eggs_clutchS_sc2h, na.rm = TRUE),
           n_clutches_iv = n(),
           n_initiated = sum(!is.na(clutch_initiated_order)),
           n_visited = sum(!is.na(initiation_date)&is.na(clutch_initiated_order)),
           n_feed = sum(is.na(initiation_date)),
           init_visit_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "Initiated only"),
                                           ifelse(!any(mom_at_init), "Visited only", NA)),
           one_both_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "One"),
                                           ifelse(!any(mom_at_init), "One", NA))) %>%
  ungroup()

est_fecundity_life_strats <- est_fecundity_clutch %>%
  group_by(Female_ID) %>%
  # clutch visited order == 0 means she visited before initiation, so it shouldn't count
  mutate(started_by =
           ifelse(any(clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order==1),
                  "initiating",
                  ifelse(any(clutch_visited_order==1&is.na(clutch_initiated_order)),
                         "visiting", "other")),
         n_clutches_with_eggs_iv = sum(!is.na(clutch_visited_order)&(clutch_visited_order>0), na.rm=T)) %>%
  ungroup() %>%
  right_join(select(life_strats_firstlast_des, -c(ants_removed, females_removed, `visited in 4 days`)), 
             by=c("Female_ID"="FemID_first_des_rel2h_init")) %>%
  filter(clutch_visited_order==1) %>%
  mutate(desert_catL_v2 = ifelse(started_by=="initiating",
                                 ifelse(desert_rel2hL <= -16, "desert",
                                        ifelse(desert_rel2hL > -16 & desert_rel2hL <= 4, "eggs", 
                                               ifelse(desert_rel2hL >= 4,"nymphs",
                                                      NA))),
                                 ifelse(started_by=="visiting", "visit", 
                                        NA)),
         desert_catS_v2 = ifelse(started_by=="initiating",
                                 ifelse(desert_rel2hS <= -16, "desert",
                                        ifelse(desert_rel2hS > -16 & desert_rel2hS <= 4, "eggs", 
                                               ifelse(desert_rel2hS >= 4,"nymphs",
                                                      NA))),
                                 ifelse(started_by=="visiting", "visit", 
                                        NA)),
         desert_catL_v3 = ifelse(started_by=="initiating",
                                 ifelse(desert_rel2hL <= -16, "desert",
                                        ifelse(desert_rel2hL > -16 & desert_rel2hL <= 4, "eggs", 
                                               ifelse(desert_rel2hL >= 4,"nymphs",
                                                      NA))),
                                 init_visit_life_tactic),
         desert_catS_v3 = ifelse(started_by=="initiating",
                                 ifelse(desert_rel2hS <= -16, "desert",
                                        ifelse(desert_rel2hS > -16 & desert_rel2hS <= 4, "eggs", 
                                               ifelse(desert_rel2hS >= 4,"nymphs",
                                                      NA))),
                                 init_visit_life_tactic),
         first_clutch_visited_in4d = ifelse(started_by=="initiating",
                                            ifelse(`visited in 4 days` == "Visited", "vis", "not"),
                                            NA)) %>%
  distinct(Female_ID, ants_removed, females_removed, `visited in 4 days`,
           desert_catL_v2, desert_catL_v3, desert_catS_v2, desert_catS_v3,
           started_by, init_visit_life_tactic, one_both_life_tactic,
           first_clutch_visited_in4d, est_eggs_lifeL_sc2h, est_eggs_lifeS_sc2h,
           n_clutches_with_eggs_iv)
```

Also, among females that start by visiting, do the ones that adopt that first clutch have lower lifetime fecundity than those that desert?
```{r}
est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  left_join(select(visited_1st_4d_data, location, Female_ID, 
                   guard_duration, clutch_visited_order)%>%
              filter(clutch_visited_order==1)) %>%
  ggplot(data=., aes(x=desert_catS_v2, y=est_eggs_lifeS_sc2h)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(aes(fill=guard_duration), pch = 21, size=3, width=0.35) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1), nrow=1) + 
    scale_fill_gradientn(colours=rainbow(4))

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  left_join(select(visited_1st_4d_data, location, Female_ID, 
                   guard_duration, clutch_visited_order)%>%
              filter(clutch_visited_order==1)) %>%
  ggplot(data=., aes(x=desert_catL_v2, y=est_eggs_lifeL_sc2h)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(aes(fill=guard_duration), pch = 21, size=3, width=0.35) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1), nrow=1) + 
    scale_fill_gradientn(colours=rainbow(4))

```

I'm not sure what these figures mean. For females with more than one clutch, there may be a trade-off between the guarding duration on the first clutch you initiated (or visited) and your estimated lifetime fecundity, but only among females that stayed with their first nymphs. In other words, if you've stayed with your nymphs, staying longer will come at the cost of future fecundity. These regressions look suggestive, no significant, but I should check.

Maybe there's too little data to tell, but it looks like females that start by visiting show a different pattern. For single-clutch females, staying longer does not increase lifetime fecundity, while for multi-clutch females, staying longer on the first clutch does increase fecundity. ??

But not that there are some inconsistencies in this data, with some "deserters" guarding the first clutch for more than 4 days.
```{r}
est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  left_join(select(visited_1st_4d_data, location, Female_ID, 
                   guard_duration, est_rel2h, clutch_visited_order)%>%
              filter(clutch_visited_order==1)) %>%
  ggplot(data=., aes(x=guard_duration, y=est_eggs_lifeL_sc2h, 
                     color=desert_catL_v2, fill=desert_catL_v2)) +
  geom_point(pch = 21, size=3) +
  geom_smooth(method=lm) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1), nrow=1) +
  ggtitle("tbL")

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  left_join(select(visited_1st_4d_data_tb, location, Female_ID, 
                   guard_duration, est_rel2h, clutch_visited_order, initL)%>%
              filter(clutch_visited_order==1)) %>%
  filter(initL|(desert_catL_v2=="visit")) %>%
  ggplot(data=., aes(x=guard_duration, y=est_eggs_lifeL_sc2h, 
                     color=desert_catL_v2, fill=desert_catL_v2)) +
  geom_point(pch = 21, size=3) +
  geom_smooth(method=lm) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1), nrow=1) +
  ggtitle("tbL")

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  left_join(select(visited_1st_4d_data_tb, location, Female_ID, 
                   guard_duration, clutch_visited_order, initS)%>%
              filter(clutch_visited_order==1, initS)) %>%
  ggplot(data=., aes(x=guard_duration, y=est_eggs_lifeS_sc2h, 
                     color=desert_catS_v2, fill=desert_catS_v2)) +
  geom_point(pch = 21, size=3) +
  geom_smooth(method=lm) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1), nrow=1) +
  ggtitle("tbS")

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  left_join(select(visited_1st_4d_data_tb, location, Female_ID, 
                   guard_duration, est_rel2h, clutch_visited_order, initS)%>%
              filter(clutch_visited_order==1)) %>%
  filter(initS|(desert_catS_v2=="visit")) %>%
  ggplot(data=., aes(x=guard_duration, y=est_eggs_lifeS_sc2h, 
                     color=desert_catS_v2, fill=desert_catS_v2)) +
  geom_point(pch = 21, size=3) +
  geom_smooth(method=lm) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1), nrow=1) +
  ggtitle("tbS")

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  left_join(select(visited_1st_4d_data, location, Female_ID, 
                   guard_duration, clutch_visited_order)%>%
              filter(clutch_visited_order==1)) %>%
  filter(desert_catL_v2!="visit") %>%
  ggplot(data=., aes(x=guard_duration, y=est_eggs_lifeL_sc2h, 
                     color=desert_catL_v2, fill=desert_catL_v2)) +
  geom_point(pch = 21, size=3) +
  geom_smooth(method=lm) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1), nrow=1) +
  ggtitle("tbL")

est_fecundity_life_strats %>%
  filter(!females_removed, ) %>%
  left_join(select(visited_1st_4d_data, location, Female_ID, 
                   guard_duration, clutch_visited_order)%>%
              filter(clutch_visited_order==1)) %>%
  filter(desert_catS_v2!="visit") %>%
  ggplot(data=., aes(x=guard_duration, y=est_eggs_lifeS_sc2h, 
                     color=desert_catS_v2, fill=desert_catS_v2)) +
  geom_point(pch = 21, size=3) +
  geom_smooth(method=lm) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1), nrow=1) +
  ggtitle("tbS")

est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  left_join(select(visited_1st_4d_data, location, Female_ID, 
                   guard_duration, clutch_visited_order)%>%
              filter(clutch_visited_order==1)) %>%
  filter(desert_catL_v2=="visit") %>%
  ggplot(data=., aes(x=guard_duration, y=est_eggs_lifeL_sc2h, 
                     color=desert_catL_v2, fill=desert_catL_v2)) +
  geom_point(pch = 21, size=3) +
  geom_smooth(method=lm) +
  ylab(expression(paste("Estimated lifetime fecundity (eggs) ", italic("sensu moi"))))  +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1), nrow=1)

```

quick stats for qcb talk figure
```{r}
est_fecundity_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_catL_v2, y=est_eggs_lifeS_sc2h, fill=desert_catL_v2)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  ylab("Estimated lifetime fecundity (eggs)")  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1), nrow=1)

est_fecundity_life_strats_semel.data <- est_fecundity_life_strats %>%
  filter(!females_removed, n_clutches_with_eggs_iv==1)

est_fecundity_life_strats_semel.aov <- est_fecundity_life_strats_semel.data %>% anova_test(est_eggs_lifeS_sc2h ~ desert_catL_v2)
est_fecundity_life_strats_semel.aov

est_fecundity_life_strats_semel.tukey <- est_fecundity_life_strats_semel.data %>% tukey_hsd(est_eggs_lifeS_sc2h ~ desert_catL_v2)

est_fecundity_life_strats_itero.data <- est_fecundity_life_strats %>%
  filter(!females_removed, n_clutches_with_eggs_iv>1)

est_fecundity_life_strats_itero.aov <- est_fecundity_life_strats_itero.data %>% anova_test(est_eggs_lifeS_sc2h ~ desert_catL_v2)
est_fecundity_life_strats_itero.aov

est_fecundity_life_strats_itero.tukey <- est_fecundity_life_strats_itero.data %>% tukey_hsd(est_eggs_lifeS_sc2h ~ desert_catL_v2)
```

# 3 - First, future and lifetime fecundity
```{r}

```

### 2023-08-24 scripts/old/Publilia_2019_CHAPTER-2C-fitness.Rmd
added old scripts to `scripts/old/` for reference

---
title: "Publilia_2019_CHAPTER-2C-fitness"
author: "micah fletcher"
date: "2/24/2022"
output: html_document
---

# Publilia 2019 Chapter - Script 2C: estimating fitness
This is meant to consolidate previous scripts and provide a readable and reproducible record of the analyses for the Publilia Chapter.

## Lifetime fitness using regression predictions
Custom functions for using survivorship regression predictions to estimate fitness
```{r}
ci_for_fitness <- function(data_in, survNom, survDen, 
                        tenure, treatment, vis, model){
  data <- eval(substitute(
    data_in %>%
      add_column(fit = predict(model, newdata = ., type = 'response'))
    ))
  ## grad the inverse link function
  ilink <- family(model)$linkinv
  ## add fit and se.fit on the **link** scale
  data_fit_link <- eval(substitute(
    data %>% add_column(
  setNames(as_tibble(predict(model, data, se.fit = TRUE)[1:2]),
           c('fit_link','se_link'))) %>%
## create the interval and backtransform
  mutate(fit_resp  = ilink(fit_link),
         conf_upr = ilink(fit_link + (2 * se_link)),
         conf_lwr = ilink(fit_link - (2 * se_link)))
    ))
  return(data_fit_link)
}
```

# Estimating fitness using different methods
There are several outdated versions that I've since deleted
 - “v2”: (survivorship ~ ant_treatment * desL) * proportion of time on eggs
 - “v3”: (survivorship ~ ants_ever * desL) * proportion of time on eggs
 - “v4”: (survivorship ~ ants_ever * desP) * proportion of time on eggs
 - “v5”: (survivorship ~ ants_ever * I(desP^2)) * proportion of time on eggs

The current versions are:
 - v1: raw offspring count * proportion of time on eggs
 - v6: (survivorship ~ ant_treatment * I(desL^2)) * proportion of time on eggs

Not time for dissertation but I could experiment with using a square root function for egg laying (more eggs in the first few days of guarding/visiting) and see how robust these results are to our assumptions about egg laying behavior.
```{r}
est_fitness_prep <- visited_1st_4d_data %>%
  filter(!is.na(initiation_date)) %>%
  group_by(Female_ID) %>%
  mutate(started_by_initiating =
           any(clutch_visited_order==1&clutch_initiated_order==1)) %>%
  ungroup() %>%
  select(location, Female_ID, clutch_visited_order, clutch_initiated_order, 
         desert_rel2h = est_rel2h, guard_duration,
         mom_at_init, started_by_initiating) %>%
  left_join(select(clutch_survivorship_data, location:last_desert, 
                   n_eggs, med_t5eggs, n_hatched, n_survived, DormPlant), 
            by=c("location")) %>%
  left_join(select(focalMb4h_sc2h, Female_ID, location, focalMb4h_sc2h),
            by=c("Female_ID", "location")) %>%
  mutate(des=last_des_rel2h, 
         ants=ifelse(ants_removed,"Removed","Control"),
         vis=`visited in 4 days`) %>%
  left_join(select(ant_counts, location, ever_antsP)) %>%
  separate(location, into = c("DormPlant", "Leaf"), sep="_", remove=FALSE) %>%
  left_join(dplyr::select(moms_plant_data, DormPlant, last_visit_ends_P), by="DormPlant") %>%
  mutate(last_desP_rel2h = last_visit_ends_P-est_hatch,
         ant_treatment=ifelse(ants_removed,"Removed","Control"))

# v6: (survivorship ~ ant_treatment * I(desL^2)) * proportion of time on eggs
est_fitness_hatch_fit_v6 <- 
  ci_for_fitness(data_in=est_fitness_prep, model=des_hatch.desL.ant_treatment.quad.fits$mai.qb) %>%
  mutate(est_hatch_fit_v6 = fit) %>%
  select(-(fit:conf_lwr))
est_fitness_Esurv_fit_v6 <- 
  ci_for_fitness(data_in=est_fitness_hatch_fit_v6, model=des_Esurv.desL.ant_treatment.quad.fits$mai.qb) %>%
  mutate(est_Esurv_fit_v6 = fit) %>%
  select(-(fit:conf_lwr))

est_fitness_clutch <- est_fitness_Esurv_fit_v6 %>%
  mutate(propD_b4h = focalMb4h_sc2h/mDb4h_sc2h,
         est_eggs_clutch = med_t5eggs*propD_b4h,
         est_hatched_clutch_v1 = n_hatched*propD_b4h,
         est_survived_clutch_v1 = n_survived*propD_b4h,
         est_hatched_clutch_v6 = est_eggs_clutch*est_hatch_fit_v6,
         est_survived_clutch_v6 = est_eggs_clutch*est_Esurv_fit_v6) %>%
  group_by(Female_ID) %>%
    mutate(est_eggs_life = sum(est_eggs_clutch, na.rm = T),
           est_hatched_life_v1 = sum(est_hatched_clutch_v1, na.rm = T),
           est_survived_life_v1 = sum(est_survived_clutch_v1, na.rm = T),
           est_hatched_life_v6 = sum(est_hatched_clutch_v6, na.rm = T),
           est_survived_life_v6 = sum(est_survived_clutch_v6, na.rm = T),
           n_clutches_iv = n(),
           n_initiated = sum(!is.na(clutch_initiated_order)),
           n_visited = sum(!is.na(initiation_date)&is.na(clutch_initiated_order)),
           n_feed = sum(is.na(initiation_date)),
           init_visit_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "Initiated only"),
                                           ifelse(!any(mom_at_init), "Visited only", NA)),
           one_both_life_tactic = ifelse(any(mom_at_init), 
                                           ifelse(any(!mom_at_init), "Both", "One"),
                                           ifelse(!any(mom_at_init), "One", NA))) %>%
  ungroup()

est_fitness_future <- est_fitness_clutch %>%
  filter(clutch_visited_order == 1) %>%
  mutate(est_eggs_future = est_eggs_life - est_eggs_clutch,
         est_hatched_future_v1 = est_hatched_life_v1 - est_hatched_clutch_v1,
         est_hatched_future_v6 = est_hatched_life_v6 - est_hatched_clutch_v6,
         est_survived_future_v1 = est_survived_life_v1 - est_survived_clutch_v1,
         est_survived_future_v6 = est_survived_life_v6 - est_survived_clutch_v6)

est_fitness_strat_cats <- est_fitness_future %>%
  dplyr::select(Female_ID, location, desert_rel2h, last_des_rel2h,
         med_t5eggs, est_eggs_clutch, 
         est_hatched_life_v1, est_hatched_life_v6,
         est_hatched_future_v1, est_hatched_future_v6,
         est_survived_life_v1, est_survived_life_v6,
         est_survived_future_v1, est_survived_future_v6,
         females_removed, ants_removed, clutch_initiated_order,
         n_clutches_iv, n_initiated, n_visited, init_visit_life_tactic, `visited in 4 days`)
```

## Check how I'm calculating fecundity
```{r}
# no need to separate females_removed
est_fitness_clutch %>% 
  filter(!is.na(est_eggs_clutch)) %>%
  ggplot(data=., aes(x=des, y=est_eggs_clutch, color=ants, fill=ants)) +
  geom_point() +
  geom_smooth() + ylim(0,60) +
  facet_wrap(vars(vis))

est_fitness_clutch %>%
  arrange(Female_ID) %>%
  select(Female_ID, location, focalMb4h_sc2h, mDb4h_sc2h, propD_b4h, 
         med_t5eggs, est_eggs_clutch, est_eggs_life) #%>% View()
```

## Check how I'm estimating hatching and survival and how many clutches are recovered
It might be that using the regression model with a continuous desertion date explanatory variable just cannot adequately capture the variation and will always deflate mean and variance in lifetime fitness (# N5). If I want a more accurate representation of the variation, maybe I should use discrete desertion date categories (boxplots) and explicitly include variance in the imputation. But will this lead to strange results when the metric determining eggs contributed is continuous? I don't have time to do this for the dissertation but I could explore it for the paper.
```{r}
# Check how I'm estimating hatching and survival and how many clutches are recovered
est_fitness_clutch %>%
  count(females_removed, !is.na(est_eggs_clutch), !is.na(est_hatched_clutch_v1), !is.na(est_survived_clutch_v1))

est_fitness_clutch %>%
  count(females_removed, !is.na(est_eggs_clutch), !is.na(est_hatched_clutch_v6), !is.na(est_survived_clutch_v6))

# It appears that my modeling is overestimating the number of nymphs hatched for clutches with very low est hatched v1
est_fitness_clutch %>% 
  filter(!is.na(est_hatched_clutch_v1),!is.na(est_hatched_clutch_v6)) %>%
  ggplot(data=., aes(x=est_hatched_clutch_v1, y=est_hatched_clutch_v6, color=sum_vD==0)) +
  geom_abline(slope=1) +
  geom_point()

# v6: Consistency is MUCH worse for survivorship; MANY clutches with no surviving nymphs were predicted to have survived
est_fitness_clutch %>%
  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
  ggplot(data=., aes(x=est_survived_clutch_v1, y=est_survived_clutch_v6, color=vis)) +
  geom_abline(slope=1) +
  geom_point() + facet_wrap(~females_removed)

est_fitness_clutch %>%
  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
  ggplot(data=., aes(x=est_survived_clutch_v1, y=est_survived_clutch_v6, color=interaction(vis,ants))) +
  geom_abline(slope=1) +
  geom_point()  + xlim(0,60) + ylim(0,60)

### how well does this work from the perspective of imputation?
# hatching: ok correspondence, the spread is tighter, but range is preserved
est_fitness_clutch %>% 
  filter(!is.na(est_hatched_clutch_v1),!is.na(est_hatched_clutch_v6)) %>%
  ggplot(data=., aes(x=des, y=est_hatched_clutch_v1, color=ants, fill=ants)) +
  geom_point() +
  geom_smooth() + ylim(0,60) +
  facet_wrap(vars(vis))

est_fitness_clutch %>% 
  filter(!is.na(est_hatched_clutch_v6)) %>%
  ggplot(data=., aes(x=des, y=est_hatched_clutch_v6, color=ants, fill=ants)) +
  geom_point() +
  geom_smooth() + ylim(0,60) +
  facet_wrap(vars(vis))

# survival: ok correspondence, the spread is MUCH tighter and range is more limited; losing many higher values
est_fitness_clutch %>% 
  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
  ggplot(data=., aes(x=des, y=est_survived_clutch_v1, color=ants, fill=ants)) +
  geom_point() +
  geom_smooth() + ylim(0,60) +
  facet_wrap(vars(vis))

est_fitness_clutch %>% 
  filter(!is.na(est_survived_clutch_v6)) %>%
  ggplot(data=., aes(x=des, y=est_survived_clutch_v6, color=ants, fill=ants)) +
  geom_point() +
  geom_smooth() + ylim(0,60) +
  facet_wrap(vars(vis))
```

Only females that laid more than one clutch
```{r}
est_fitness_clutch %>%
  filter(!is.na(est_hatched_clutch_v1),!is.na(est_hatched_clutch_v6)) %>%
  ggplot(data=., aes(x=est_hatched_clutch_v1, y=est_hatched_clutch_v6)) +
  geom_abline(slope=1) +
  geom_point() +
  facet_wrap(~n_initiated>1)

est_fitness_clutch %>%
  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
  ggplot(data=., aes(x=est_survived_clutch_v1, y=est_survived_clutch_v6)) +
  geom_abline(slope=1) +
  geom_point() +
  facet_wrap(~n_initiated>1)
```

### Life strategies: start by deserting early, guarding eggs, guarding nymphs or visited an existing clutch
```{r}
est_fitness_life_strats <- est_fitness_clutch %>%
  group_by(Female_ID) %>%
  # clutch visited order == 0 means she visited before initiation, so it shouldn't count
  mutate(started_by =
           ifelse(any(clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order==1),
                  "initiating",
                  ifelse(any(clutch_visited_order==1&is.na(clutch_initiated_order)|
                             clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order!=1),
                         "visiting", "other")),
         n_clutches_with_eggs_iv = sum(!is.na(clutch_visited_order)&(clutch_visited_order>0), na.rm=T)) %>%
  ungroup() %>%
  filter(clutch_visited_order==1) %>%
  # mutate(desert_cat = ifelse(started_by=="initiating",
  #                                ifelse(desert_rel2h <= -16, "desert",
  #                                       ifelse(desert_rel2h > -16 & desert_rel2h <= 4, "eggs", 
  #                                              ifelse(desert_rel2h >= 4,"nymphs",
  #                                                     NA))),
  #                                ifelse(started_by=="visiting", "visit", 
  #                                       NA)),
  mutate(desert_cat = ifelse(started_by=="initiating",
                                 ifelse(guard_duration <= 10, "desert",
                                        ifelse(guard_duration > 10 & desert_rel2h <= 4, "eggs", 
                                               ifelse(desert_rel2h >= 4,"nymphs",
                                                      NA))),
                                 ifelse(started_by=="visiting", "visit", 
                                        NA)),
         first_clutch_visited_in4d = ifelse(started_by=="initiating",
                                            ifelse(`visited in 4 days` == "Visited", "vis", "not"),
                                            NA),
         est_eggs_future = est_eggs_life - est_eggs_clutch,
         est_hatched_future_v1 = est_hatched_life_v1 - est_hatched_clutch_v1,
         est_hatched_future_v6 = est_hatched_life_v6 - est_hatched_clutch_v6,
         est_survived_future_v1 = est_survived_life_v1 - est_survived_clutch_v1,
         est_survived_future_v6 = est_survived_life_v6 - est_survived_clutch_v6) %>%
  distinct(Female_ID, ants_removed, females_removed, `visited in 4 days`,
           desert_cat, desert_rel2h, guard_duration,
           started_by, init_visit_life_tactic, one_both_life_tactic,
           first_clutch_visited_in4d, n_clutches_with_eggs_iv,
           est_eggs_clutch, est_eggs_life, est_eggs_future, 
           est_hatched_life_v1, est_hatched_life_v6, 
           est_hatched_future_v1, est_hatched_future_v6,
           est_hatched_clutch_v1, est_hatched_clutch_v6,
           est_survived_life_v1, est_survived_life_v6, 
           est_survived_future_v1, est_survived_future_v6,
           est_survived_clutch_v1, est_survived_clutch_v6) %>%
  # remove 4 females that visited clutches with unknown initiation dates
  filter(!is.na(ants_removed)) %>%
  # *** I need to figure out why these are NA!!! ***
  filter(!is.na(est_hatched_clutch_v6))
```

```{r}
est_fitness_life_strats %>%
  filter(!females_removed, !is.na(desert_cat)) %>%
  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  ylab("Estimated lifetime fecundity (eggs)")  +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1)

est_fitness_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v1, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  ylab("Estimated lifetime fitness (eggs hatched)")  + ylim(0,100) +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1)

est_fitness_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  ylab("Estimated lifetime fitness (eggs hatched)")  + ylim(0,100) +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1)

est_fitness_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v1, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  ylab("Estimated lifetime fitness (nymphs survived)")  + ylim(0,60) +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1)

est_fitness_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  ylab("Estimated lifetime fitness (nymphs survived)")  + ylim(0,60) +
  xlab("Reproductive strategy for first clutch") +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1)
```

## Boxplots

with jitter (messy)
```{r}
est_fitness_life_strats_eggs.p <- est_fitness_life_strats %>%
  filter(!females_removed, !is.na(desert_cat)) %>%
  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA, alpha=0) +
  #stat_summary(fun=mean, geom="point", shape=4, size=3) +
  ylab("Lifetime fecundity\n(total eggs laid)")  +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(~ants_removed, nrow=1) +
  theme(strip.background = element_blank(),strip.text.x = element_blank(),
        axis.title.x = element_blank(),axis.text.x=element_blank(),
        legend.position='none')

est_fitness_life_strats_hatched.p <- est_fitness_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA, key_glyph=draw_key_rect) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3, key_glyph=draw_key_rect) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA, alpha=0, key_glyph=draw_key_rect) +
  #stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
  ylab("Lifetime fitness\n(total eggs hatched)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(~ants_removed, nrow=1) +
  theme(strip.background = element_blank(),strip.text.x = element_blank(),
        axis.title.x = element_blank(),axis.text.x=element_blank(),
        legend.position = c(0.7,0.9))

est_fitness_life_strats_survived.p <- est_fitness_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA, alpha=0) +
  #stat_summary(fun=mean, geom="point", shape=4, size=3) +
  ylab("Lifetime fitness\n(total nymphs survived)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(~ants_removed, nrow=1) +
  theme(strip.background = element_blank(),strip.text.x = element_blank(),
        legend.position='none')

#library(egg)
egg::ggarrange(est_fitness_life_strats_eggs.p,
          est_fitness_life_strats_hatched.p,
          est_fitness_life_strats_survived.p,
          ncol=1, nrow=3)
```

with mean (clean)
```{r}
est_fitness_life_strats_eggs.p <- est_fitness_life_strats %>%
  filter(!females_removed, !is.na(desert_cat)) %>%
  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5) +
  stat_summary(fun=mean, geom="point", shape=4, size=3) +
  ylab("Lifetime fecundity\n(total eggs laid)")  +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(~ants_removed, nrow=1) +
  theme(strip.background = element_blank(),strip.text.x = element_blank(),
        axis.title.x = element_blank(),axis.text.x=element_blank(),
        legend.position = "none")

est_fitness_life_strats_hatched.p <- est_fitness_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
  ylab("Lifetime fitness\n(total eggs hatched)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(~ants_removed, nrow=1) +
  theme(strip.background = element_blank(),strip.text.x = element_blank(),
        axis.title.x = element_blank(),axis.text.x=element_blank(),
        legend.position = c(0.7,0.9))

est_fitness_life_strats_survived.p <- est_fitness_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5) +
  stat_summary(fun=mean, geom="point", shape=4, size=3) +
  ylab("Lifetime fitness\n(total nymphs survived)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(~ants_removed, nrow=1) +
  theme(strip.background = element_blank(),strip.text.x = element_blank(),
        legend.position='none')

#library(egg)
egg::ggarrange(est_fitness_life_strats_eggs.p,
          est_fitness_life_strats_hatched.p,
          est_fitness_life_strats_survived.p,
          ncol=1, nrow=3)
```

splitting semelparous and iteroparous females (clean)
```{r}
est_fitness_life_strats_eggs_semel.p <- est_fitness_life_strats %>%
  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv==1) %>%
  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
  ylab("Lifetime fecundity\n(total eggs laid)")  + ylim(0,160) +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(~ants_removed, nrow=1) +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),
        axis.title.x = element_blank(),axis.text.x=element_blank(),
        legend.position="none")

est_fitness_life_strats_eggs_itero.p <- est_fitness_life_strats %>%
  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv>1) %>%
  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
  ylab("Lifetime fecundity\n(total eggs laid)")  + ylim(0,160) +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1) +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),
        axis.title.x = element_blank(),axis.text.x=element_blank(),
        legend.position="none")

est_fitness_life_strats_hatched_semel.p <- est_fitness_life_strats %>%
  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv==1) %>%
  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
  ylab("Lifetime fitness\n(total eggs hatched)") + ylim(0,100) +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(~ants_removed, nrow=1) +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),
        axis.title.x = element_blank(),axis.text.x=element_blank(),
        legend.position=c(0.75,0.9))

est_fitness_life_strats_hatched_itero.p <- est_fitness_life_strats %>%
  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv>1) %>%
  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
   ylab("Lifetime fitness\n(total eggs hatched)") + ylim(0,100) +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1) +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),
        axis.title.x = element_blank(),axis.text.x=element_blank(),
        legend.position=c(0.75,0.9))

est_fitness_life_strats_survived_semel.p <- est_fitness_life_strats %>%
  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv==1) %>%
  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
  ylab("Lifetime fitness\n(total nymphs survived)") + ylim(0,30) +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(~ants_removed, nrow=1) +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),
        legend.position="none",
        axis.text.x=element_text(angle=45, vjust=1, hjust=1))

est_fitness_life_strats_survived_itero.p <- est_fitness_life_strats %>%
  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv>1) %>%
  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
  ylab("Lifetime fitness\n(total nymphs survived)") + ylim(0,30) +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
  theme_publilia() +
  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1) +
  theme(strip.background = element_blank(), strip.text.x = element_blank(),
        legend.position="none",
        axis.text.x=element_text(angle=45, vjust=1, hjust=1))

egg::ggarrange(est_fitness_life_strats_eggs_semel.p,est_fitness_life_strats_eggs_itero.p,
          est_fitness_life_strats_hatched_semel.p,est_fitness_life_strats_hatched_itero.p,
          est_fitness_life_strats_survived_semel.p,est_fitness_life_strats_survived_itero.p,
          ncol=2, nrow=3)
```

Should I include this raw data in the supplement? I think so.
```{r}
est_fitness_life_strats %>%
  filter(!females_removed, !is.na(desert_cat)) %>%
  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab("Estimated lifetime fecundity (eggs)")  +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "white")) +
  theme_publilia() +
  facet_wrap(vars(ants_removed), nrow=1)

est_fitness_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v1, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab("Estimated lifetime fitness (eggs hatched)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "white")) +
  theme_publilia() +
  facet_wrap(vars(ants_removed), nrow=1)

est_fitness_life_strats %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v1, fill=ants_removed)) +
  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  ylab("Estimated lifetime fitness (nymphs survived)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "white")) +
  theme_publilia() +
  facet_wrap(vars(ants_removed), nrow=1)
```

## Split violin plots
geom_split_violin
```{r}
GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
  grp <- data[1, "group"]
  newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
  newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])

  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
      1))
    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
    aesthetics$alpha <- rep(1, nrow(quantiles))
    both <- cbind(quantiles, aesthetics)
    quantile_grob <- GeomPath$draw_panel(both, ...)
    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
  }
  else {
    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
  }
})

geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
                              show.legend = NA, inherit.aes = TRUE) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
}
```

split violin v1
```{r}
est_fitness_life_strats_splitvio_eggs_v1.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=3) +
  ylab("Estimated lifetime fecundity (number of eggs laid)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  theme_publilia()

est_fitness_life_strats_splitvio_hatched_v1.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v1, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=3) +
  ylab("Estimated lifetime fitness (eggs hatched)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  theme_publilia()

est_fitness_life_strats_splitvio_survived_v1.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v1, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=3) +
  ylab("Estimated lifetime fitness (nymphs survived)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  theme_publilia()

egg::ggarrange(est_fitness_life_strats_splitvio_eggs_v1.p,
          est_fitness_life_strats_splitvio_hatched_v1.p,
          est_fitness_life_strats_splitvio_survived_v1.p,
          ncol=1, nrow=3)

est_fitness_life_strats_splitvio_eggs_v1_itero.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=2) +
  ylab("Estimated lifetime fecundity (number of eggs laid)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  theme_publilia() +
  facet_wrap(~n_clutches_with_eggs_iv>1)

est_fitness_life_strats_splitvio_hatched_v1_itero.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v1, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=2) +
  ylab("Estimated lifetime fitness (eggs hatched)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  theme_publilia() +
  facet_wrap(~n_clutches_with_eggs_iv>1)

est_fitness_life_strats_splitvio_survived_v1_itero.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v1, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=2) +
  ylab("Estimated lifetime fitness (nymphs survived)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  theme_publilia() +
  facet_wrap(~n_clutches_with_eggs_iv>1)

egg::ggarrange(est_fitness_life_strats_splitvio_eggs_v1_itero.p,
          est_fitness_life_strats_splitvio_hatched_v1_itero.p,
          est_fitness_life_strats_splitvio_survived_v1_itero.p,
          ncol=1, nrow=3)
```

split violin v6
```{r}
est_fitness_life_strats_splitvio_eggs_v6.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=3) +
  ylab("Estimated lifetime fecundity\n(number of eggs laid)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  theme_publilia()

est_fitness_life_strats_splitvio_hatched_v6.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50, key_glyph=draw_key_rect) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), 
             pch = 16, size=3, key_glyph=draw_key_rect) +
  ylab("Estimated lifetime fitness\n(eggs hatched)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ant exclusion"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ant exclusion"), values=c("brown1", "black")) +
  theme_publilia()

est_fitness_life_strats_splitvio_survived_v6.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=3) +
  ylab("Estimated lifetime fitness\n(nymphs survived)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  theme_publilia()

egg::ggarrange(est_fitness_life_strats_splitvio_eggs_v6.p +
                 theme(legend.position="none"),
          est_fitness_life_strats_splitvio_hatched_v6.p +
                 theme(legend.position=c(0.1,0.9)),
          est_fitness_life_strats_splitvio_survived_v6.p +
                 theme(legend.position="none"),
          ncol=1, nrow=3)

est_fitness_life_strats_splitvio_eggs_v6_itero.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=2) +
  ylab("Estimated lifetime fecundity\n(number of eggs laid)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  theme_publilia() +
  facet_wrap(~n_clutches_with_eggs_iv>1) + theme()

est_fitness_life_strats_splitvio_hatched_v6_itero.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50, key_glyph=draw_key_rect) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), 
             pch = 16, size=3, key_glyph=draw_key_rect) +
  ylab("Estimated lifetime fitness\n(eggs hatched)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  theme_publilia() +
  facet_wrap(~n_clutches_with_eggs_iv>1)

est_fitness_life_strats_splitvio_survived_v6_itero.p <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed, color=ants_removed)) +
  geom_split_violin(color=NA, alpha=0.50) +
  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=2) +
  ylab("Estimated lifetime fitness\n(nymphs survived)") +
  xlab("Reproductive strategy for first clutch") +
  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
  theme_publilia() +
  facet_wrap(~n_clutches_with_eggs_iv>1)

egg::ggarrange(est_fitness_life_strats_splitvio_eggs_v6_itero.p +
                 theme(legend.position="none"),
          est_fitness_life_strats_splitvio_hatched_v6_itero.p +
                 theme(legend.position=c(0.1,0.8)),
          est_fitness_life_strats_splitvio_survived_v6_itero.p +
                 theme(legend.position="none"),
          ncol=1, nrow=3)
```

## Comparing to Zink 2003 method

### 3 Zink 2003 model:
Lifetime fitness (number of eggs that hatched):
w(t_i) = sum(from i=1, to i=N, P_i*g(t_i))
P = number of eggs invested in a clutch (all the eggs go to the initiator?)
t_i = guarding duration in clutch i
N = lifetime number of clutches
g(t) = relationship between guarding duration and hatching success
 (assume g(t) equivalent across all clutches 1 to N)

* I think the main reason Zink found equivalent fitness is that he attributed all the eggs in a clutch to each primary female. Thus an early deserter is given all the eggs from a clutch, even if she leaves within a few days and another female arrives and lays additional eggs. The final nail in the coffin will be to do the exact same "zink" estimates but this time only attributing the egg to each female proportional to the time she spent on the clutch relative to other females.
```{r}
surv_reg_data_zink <- focalMb4h_sc2h %>%
  filter(!is.na(initiation_date), !is.na(guard_duration), !ants_removed) %>%
  filter(mom_at_init) %>% # primary females
  group_by(location) %>%
    summarize(max_primary_dur = max(guard_duration, na.rm=T),
              females_removed = first(females_removed),
              initiation_date = first(initiation_date)) %>%
  ungroup() %>%
  left_join(top5eggs_summary) %>%
  select(location, max_primary_dur,
         females_removed, initiation_date, med_t5eggs) %>%
  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2,
                   -c(ants_removed, females_removed, initiation_date, n_eggs)),
            by=c("location"="NOr_rev_loc")) %>%
  select(location, initiation_date, hatch_date, 
         max_primary_dur, med_t5eggs, n_hatched, n_survived,
         females_removed)

ggplot(data=surv_reg_data_zink, 
       aes(x=max_primary_dur, y=n_hatched/med_t5eggs)) +
  geom_point() +
  geom_smooth(method=lm)

ggplot(data=filter(surv_reg_data_zink, initiation_date<=as_date("2019-06-10")), 
       aes(x=max_primary_dur, y=n_hatched/med_t5eggs)) +
  geom_point() +
  geom_smooth(method=lm)

ggplot(data=filter(surv_reg_data_zink, initiation_date<=as_date("2019-06-10"), !females_removed), 
       aes(x=max_primary_dur, y=n_hatched/med_t5eggs)) +
  geom_point() +
  geom_smooth(method=lm)

zink_hatch.m <- surv_reg_data_zink %>%
  filter(initiation_date<=as_date("2019-06-10"), !is.na(n_hatched/med_t5eggs)) %>%
lm(n_hatched/med_t5eggs ~ max_primary_dur, data=.)

summary(zink_hatch.m) # use this for predicting hatching success

zink_hatch.m.norem <- surv_reg_data_zink %>%
  filter(initiation_date<=as_date("2019-06-10"), !is.na(n_hatched/med_t5eggs), !females_removed) %>%
lm(n_hatched/med_t5eggs ~ max_primary_dur, data=.)

summary(zink_hatch.m.norem)

est_fitness_clutch_zink <- focalMb4h_sc2h %>%
  filter(!is.na(initiation_date), !ants_removed) %>%
  group_by(location) %>%
    mutate(max_primary_dur = max(mom_at_init*guard_duration, na.rm=T)) %>% # non-primary females are not counted
  ungroup() %>%
  left_join(top5eggs_summary) %>%
  left_join(clutch_momDays_b4h) %>%
  select(Female_ID, location, guard_duration, max_primary_dur, desert_rel2h=est_rel2h, focalMb4h_sc2h, mDb4h_sc2h,
         females_removed, initiation_date, med_t5eggs, 
         mom_at_init, clutch_visited_order, clutch_initiated_order) %>%
  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2,
                   -c(ants_removed, females_removed, initiation_date, n_eggs)),
            by=c("location"="NOr_rev_loc")) %>%
  select(Female_ID, location, initiation_date, hatch_date, 
         guard_duration, max_primary_dur, desert_rel2h, focalMb4h_sc2h, mDb4h_sc2h,
         med_t5eggs, n_hatched, n_survived, females_removed,
         mom_at_init, clutch_visited_order, clutch_initiated_order) %>%
  mutate(propD_b4h = focalMb4h_sc2h/mDb4h_sc2h,
         est_eggs_clutch = med_t5eggs*propD_b4h,
         zink_est_hatch_clutch_v1 = med_t5eggs*(coef(zink_hatch.m)[[1]]+guard_duration*coef(zink_hatch.m)[[2]]),
         zink_est_hatch_clutch_v2 = est_eggs_clutch*(coef(zink_hatch.m)[[1]]+guard_duration*coef(zink_hatch.m)[[2]])) %>%
  group_by(Female_ID) %>%
    mutate(zink_est_hatch_life_v1 = sum(zink_est_hatch_clutch_v1, na.rm=T),
           zink_est_hatch_life_v2 = sum(zink_est_hatch_clutch_v2, na.rm=T)) %>%
  ungroup()

est_fitness_life_strats_Zink <- est_fitness_clutch_zink %>%
  group_by(Female_ID) %>%
  # clutch visited order == 0 means she visited before initiation, so it shouldn't count
  mutate(started_by =
           ifelse(any(clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order==1),
                  "initiating",
                  ifelse(any(clutch_visited_order==1&is.na(clutch_initiated_order)|
                             clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order!=1),
                         "visiting", "other")),
         n_clutches_with_eggs_iv = sum(!is.na(clutch_visited_order)&(clutch_visited_order>0), na.rm=T)) %>%
  ungroup() %>%
  filter(clutch_visited_order==1) %>%
  # mutate(desert_cat = ifelse(started_by=="initiating",
  #                                ifelse(desert_rel2h <= -16, "desert",
  #                                       ifelse(desert_rel2h > -16 & desert_rel2h <= 4, "eggs", 
  #                                              ifelse(desert_rel2h >= 4,"nymphs",
  #                                                     NA))),
  #                                ifelse(started_by=="visiting", "visit", 
  #                                       NA)),
  mutate(desert_cat = ifelse(started_by=="initiating",
                                 ifelse(guard_duration <= 10, "desert",
                                        ifelse(guard_duration > 10 & desert_rel2h <= 4, "eggs", 
                                               ifelse(guard_duration >= 4,"nymphs",
                                                      NA))),
                                 ifelse(started_by=="visiting", "visit", 
                                        NA)),
         zink_dur_cat = ifelse(started_by=="initiating",
                               ifelse(guard_duration<12, "desert",
                                      ifelse(guard_duration>=12, "stay", NA)),
                               ifelse(started_by=="visiting", "visit", 
                                        NA))) %>%
  distinct(Female_ID, females_removed,
           guard_duration, max_primary_dur,
           started_by, desert_cat, zink_dur_cat,
           zink_est_hatch_clutch_v1, zink_est_hatch_clutch_v2,
           zink_est_hatch_life_v1, zink_est_hatch_life_v2,
           n_clutches_with_eggs_iv)

# v1: Zink 2003 attributes all egg in a clutch to the primary female, even if they desert early and a visitor laid additional eggs
est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v1, fill=zink_dur_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  ggtitle("v1: all eggs in clutch to primary female")

# v2: all calculations the same, but give eggs to females in proportion to the time they spent at clutch relative to other females
est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v2, fill=zink_dur_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  ggtitle("v2: eggs to female by proportion of time guarding")

# same but separating females that laid one vs. multiple clutches
est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v1, fill=zink_dur_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
  ggtitle("v1: all eggs in clutch to primary female")

est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v2, fill=zink_dur_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
  ggtitle("v2: eggs to female by proportion of time guarding")

est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v1, fill=desert_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  ggtitle("v1: all eggs in clutch to primary female")

# same but using desert_cat instead of Zink 2003 cats
est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v1, fill=desert_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
  ggtitle("v1: all eggs in clutch to primary female")

est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v2, fill=desert_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  ggtitle("v2: eggs to female by proportion of time guarding")

est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v2, fill=desert_cat)) +
  geom_boxplot(size=1.5) +
  geom_jitter(pch = 21, size=3, width=0.35) +
  stat_summary(fun=mean, geom="point", shape=4, size=6) +
  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
  ggtitle("v2: eggs to female by proportion of time guarding")

```

# Other measures of fecundity

### Number of clutches laid
```{r}
# est_fitness_future %>%
#   filter(!females_removed) %>%
#   count(desert_cat, ants_removed)
# 
# # Initiated or visited
# est_fecundity_future %>%
#   filter(!females_removed) %>%
#   ggplot(data=., aes(y = n_initiated+n_visited, x = desert_catL, fill=ants_removed)) +
#   stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
#   stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
#   stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
#   theme_publilia()
# 
# # Initiated only
# est_fecundity_future %>%
#   filter(!females_removed) %>%
#   ggplot(data=., aes(y = n_initiated, x = desert_catL, fill=ants_removed)) +
#   stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
#   stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
#   theme_publilia()
# 
# # Visited only
# est_fecundity_future %>%
#   filter(!females_removed) %>%
#   ggplot(data=., aes(y = n_visited, x = desert_catL, fill=ants_removed)) +
#   stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
#   stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
#   theme_publilia()
# 
# # Feed only
# est_fecundity_future %>%
#   filter(!females_removed) %>%
#   ggplot(data=., aes(y = n_feed, x = desert_catL, fill=ants_removed)) +
#   stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
#   stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
#   theme_publilia()

```

## First clutch vs. future fecundity and fitness
Fecundity
```{r}
fitness_life_strats_data <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs"),
         desert_cat_ants = ifelse(ants_removed, 
                                 paste(desert_cat,"ants removed"),paste(desert_cat,"control")),
         desert_cat_ants = factor(desert_cat_ants,
          levels=c("visit control", "desert control", "eggs control","nymphs control",
                   "visit ants removed", "desert ants removed", "eggs ants removed","nymphs ants removed")))

# First
fitness_first_stats_eggs_v6 <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_clutch, group=desert_cat_ants)
fitness_first_stats_eggs_v6["multcompLetters"]$multcompLetters$x <- 
  factor(rep(c("visit", "desert","eggs", "nymphs"),2), levels=c("visit", "desert","eggs", "nymphs"))
fitness_first_stats_eggs_v6["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_first_stats_eggs_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_first_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_clutch, group=desert_cat, 
                    itero=F, multcompLetters=fitness_first_stats_eggs_v6$multcompLetters,
                    letterSize=letterSize, ymax=160) +
  ylab("First-clutch fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

# Future (all)
fitness_future_stats_eggs_v6 <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_future, group=desert_cat_ants)
fitness_future_stats_eggs_v6["multcompLetters"]$multcompLetters$x <- 
  factor(rep(c("visit", "desert","eggs", "nymphs"),2), levels=c("visit", "desert","eggs", "nymphs"))
fitness_future_stats_eggs_v6["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_future_stats_eggs_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_future_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_future, group=desert_cat, 
                    itero=F, multcompLetters=fitness_future_stats_eggs_v6$multcompLetters,
                    letterSize=letterSize, ymax=160) +
  ylab("Future fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

# Future (iteroparous only)
fitness_life_strats_data.itero <- filter(fitness_life_strats_data, n_clutches_with_eggs_iv>1)
fitness_future_stats_eggs.itero <- 
  fitness_KW_test(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat_ants)
fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_future_stats_eggs_v6.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_eggs.itero$multcompLetters,
                    letterSize=letterSize, ymax=160)$itero +
  ylab("Multi-clutch future\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

# Life
fitness_life_stats_eggs_v6 <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
fitness_life_stats_eggs_v6["multcompLetters"]$multcompLetters$x <- 
  factor(rep(c("visit", "desert","eggs", "nymphs"),2), levels=c("visit", "desert","eggs", "nymphs"))
fitness_life_stats_eggs_v6["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_life_stats_eggs_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_life_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=F, multcompLetters=fitness_life_stats_eggs_v6$multcompLetters,
                    letterSize=letterSize, ymax=160) +
  ylab("Lifetime fecundity\n(eggs laid)") + 
    theme(legend.position="none")

fitness_eggs_future.v6.p <-
  egg::ggarrange(fitness_first_stats_eggs_v6.p, fitness_future_stats_eggs_v6.p, fitness_life_stats_eggs_v6.p,
                 labels=c("A","B","C"), ncol=1, nrow=3)

### trade-off
fitness_life_strats_data.itero %>%
  ggplot(data=., aes(x=desert_rel2h, est_eggs_future, color=ants_removed)) +
  geom_point() + geom_smooth(se=F, span=1)

fitness_life_strats_data.itero %>%
  ggplot(data=., aes(x=desert_rel2h, est_hatched_future_v6, color=ants_removed)) +
  geom_point() + geom_smooth(se=F, span=1)

fitness_life_strats_data.itero %>%
  ggplot(data=., aes(x=desert_rel2h, est_survived_future_v6, color=ants_removed)) +
  geom_point() + geom_smooth(se=F, span=1)

fitness_life_strats_data.itero %>%
  ggplot(data=., aes(x=est_eggs_clutch, est_eggs_future, color=ants_removed)) +
  geom_point() + geom_smooth(method=lm, se=F) +
  xlim(0,160) + ylim(0,160)

fitness_life_strats_data.itero %>%
  ggplot(data=., aes(x=est_hatched_clutch_v6, est_hatched_future_v6, color=ants_removed)) +
  geom_point() + geom_smooth(method=lm, se=F) +
  xlim(0,70) + ylim(0,70) # outlier at est_hatched_clutch_v6=90ish

fitness_life_strats_data.itero %>%
  ggplot(data=., aes(x=est_survived_clutch_v6, est_survived_future_v6, color=ants_removed)) +
  geom_point() + geom_smooth(method=lm, se=F) +
  xlim(0,25) + ylim(0,25)

fitness_life_strats_data.itero %>%
  ggplot(data=., aes(x=guard_duration, est_eggs_future, color=ants_removed)) +
  geom_point() + geom_smooth(method=lm, se=T)

fitness_life_strats_data.itero %>%
  ggplot(data=., aes(x=guard_duration, est_hatched_future_v6, color=ants_removed)) +
  geom_point() + geom_smooth(method=lm, se=F)

fitness_life_strats_data.itero %>%
  ggplot(data=., aes(x=guard_duration, est_survived_future_v6, color=ants_removed)) +
  geom_point() + geom_smooth(method=lm, se=F)

```

Future fecundity/fitness (itero)
```{r}
fitness_life_strats_data.itero <- filter(fitness_life_strats_data, n_clutches_with_eggs_iv>1)

# Eggs
fitness_future_stats_eggs.itero <- 
  fitness_KW_test(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat_ants)
fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_future_stats_eggs_v6.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_eggs.itero$multcompLetters,
                    letterSize=letterSize, ymax=160)$itero +
  ylab("Multi-clutch future\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

# Hatch
fitness_future_stats_hatched.itero <- 
  fitness_KW_test(data=fitness_life_strats_data.itero, y=est_hatched_future_v6, group=desert_cat_ants)
fitness_future_stats_hatched.itero["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_future_stats_hatched.itero["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_future_stats_hatched.itero["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_future_stats_hatched_v6.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_hatched_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_hatched.itero$multcompLetters,
                    letterSize=letterSize, ymax=75)$itero +
  ylab("Multi-clutch future\nfitness (eggs hatch)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

# Survive
fitness_future_stats_survived.itero <- 
  fitness_KW_test(data=fitness_life_strats_data.itero, y=est_survived_future_v6, group=desert_cat_ants)
fitness_future_stats_survived.itero["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_future_stats_survived.itero["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_future_stats_survived.itero["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_future_stats_survived_v6.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_survived_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_survived.itero$multcompLetters,
                    letterSize=letterSize, ymax=22)$itero +
  ylab("Multi-clutch future\nfitness (nymphs survive)") + 
    theme(legend.position=c(0.8,0.8))

fitness_stats_future.v6.itero.p <-
  egg::ggarrange(fitness_future_stats_eggs_v6.itero.p, 
                 fitness_future_stats_hatched_v6.itero.p, 
                 fitness_future_stats_survived_v6.itero.p,
                 labels=c("A","B","C"), ncol=1, nrow=3)
```

Future fecundity/fitness (itero): Is the low sample size for visiting first undermining the power to detect differences among the more interesting groups?
```{r}
fitness_life_strats_data.itero.DEN <- filter(fitness_life_strats_data,
                                         n_clutches_with_eggs_iv>1,
                                         desert_cat != "visit")

# Eggs
fitness_future_stats_eggs.itero.DEN <- 
  fitness_KW_test(data=fitness_life_strats_data.itero.DEN, y=est_eggs_future, group=desert_cat_ants)
fitness_future_stats_eggs.itero.DEN["multcompLetters"]$multcompLetters$x <- 
  rep(c("desert","eggs", "nymphs"),2)
fitness_future_stats_eggs.itero.DEN["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_future_stats_eggs.itero.DEN["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,T,T,T)))

fitness_future_stats_eggs_v6.itero.DEN.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_eggs_future, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_eggs.itero.DEN$multcompLetters,
                    letterSize=letterSize, ymax=160)$itero +
  ylab("Multi-clutch future\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

# Hatch
fitness_future_stats_hatched.itero.DEN <- 
  fitness_KW_test(data=fitness_life_strats_data.itero.DEN, y=est_hatched_future_v6, group=desert_cat_ants)
fitness_future_stats_hatched.itero.DEN["multcompLetters"]$multcompLetters$x <- 
  rep(c("desert","eggs", "nymphs"),2)
fitness_future_stats_hatched.itero.DEN["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_future_stats_hatched.itero.DEN["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,T,T,T)))

fitness_future_stats_hatched_v6.itero.DEN.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_hatched_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_hatched.itero.DEN$multcompLetters,
                    letterSize=letterSize, ymax=75)$itero +
  ylab("Multi-clutch future\nfitness (eggs hatch)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

# Survive
fitness_future_stats_survived.itero.DEN <- 
  fitness_KW_test(data=fitness_life_strats_data.itero.DEN, y=est_survived_future_v6, group=desert_cat_ants)
fitness_future_stats_survived.itero.DEN["multcompLetters"]$multcompLetters$x <- 
  rep(c("desert","eggs", "nymphs"),2)
fitness_future_stats_survived.itero.DEN["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_future_stats_survived.itero.DEN["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,T,T,T)))

fitness_future_stats_survived_v6.itero.DEN.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_survived_future_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_future_stats_survived.itero.DEN$multcompLetters,
                    letterSize=letterSize, ymax=22)$itero +
  ylab("Multi-clutch future\nfitness (nymphs survive)") + 
    theme(legend.position=c(0.8,0.8))

fitness_stats_future.v6.itero.DEN.p <-
  egg::ggarrange(fitness_future_stats_eggs_v6.itero.DEN.p, 
                 fitness_future_stats_hatched_v6.itero.DEN.p, 
                 fitness_future_stats_survived_v6.itero.DEN.p,
                 labels=c("A","B","C"), ncol=1, nrow=3)
```

Future fecundity/fitness (all)
```{r}
# Future
fitness_future_stats_hatched <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_hatched_future_v6, group=desert_cat_ants)
fitness_future_stats_hatched["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_future_stats_hatched["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_future_stats_hatched["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_future_stats_hatched_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_future_v6, group=desert_cat, 
                    multcompLetters=fitness_future_stats_hatched$multcompLetters,
                    letterSize=letterSize, ymax=75) +
  ylab("Future\nfitness (eggs hatch)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

# Future
fitness_future_stats_survived <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_survived_future_v6, group=desert_cat_ants)
fitness_future_stats_survived["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_future_stats_survived["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_future_stats_survived["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_future_stats_survived_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_future_v6, group=desert_cat, 
                    multcompLetters=fitness_future_stats_survived$multcompLetters,
                    letterSize=letterSize, ymax=22) +
  ylab("Future\nfitness (nymphs survive)") + 
    theme(legend.position=c(0.8,0.8))

fitness_stats_future.v6.p <-
  egg::ggarrange(fitness_future_stats_eggs_v6.p, 
                 fitness_future_stats_hatched_v6.p, 
                 fitness_future_stats_survived_v6.p,
                 labels=c("A","B","C"), ncol=1, nrow=3)

ymax <-21
fitness_life_strats_data %>%
      filter(!females_removed, !is.na(desert_cat)) %>%
    ggplot(data = ., aes(x = desert_cat, y=est_survived_future_v6, fill=ants_removed, color=ants_removed)) + 
      ylim(-ymax * 0.05, ymax) + 
      geom_boxplot(alpha = 0.5, key_glyph = draw_key_rect) + 
      geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
                 pch = 16, size = 2, key_glyph = draw_key_rect) + 
      xlab("Guarding strategy for first clutch") + theme_publilia() + 
      scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
      scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
      geom_text(data = fitness_future_stats_survived$multcompLetters, 
                aes(x = x, y = -ymax * 0.05, label = label), 
                fontface = "bold", size = letterSize, position=position_dodge(width=0.5))

fitness_life_strats_data.itero %>%
      filter(!females_removed, !is.na(desert_cat)) %>%
    ggplot(data = ., aes(x = desert_cat, y=est_survived_future_v6, fill=ants_removed, color=ants_removed)) + 
      ylim(-ymax * 0.05, ymax) + 
      geom_boxplot(alpha = 0.5, key_glyph = draw_key_rect) + 
      geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
                 pch = 16, size = 2, key_glyph = draw_key_rect) + 
      xlab("Guarding strategy for first clutch") + theme_publilia() + 
      scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
      scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
      geom_text(data = fitness_future_stats_survived.itero$multcompLetters, 
                aes(x = x, y = -ymax * 0.05, label = label), 
                fontface = "bold", size = letterSize, position=position_dodge(width=0.5))

```

#######################################################################
#######################################################################
#######################################################################

# Final figures and statistics
## Lifetime fecundity and fitness
I want to know whether there is a difference in the lifetime fecundity or fitness yielded by different strategies.
Most importantly, I want to know whether there is a difference within ant-exclusion treatment, but I'm also want to know whether ant exclusion changes the fitness of a given strategy. The data are unpaired and probably no conforming well to a normal distribution.

plotting libraries
```{r}
library(multcompView)
```

geom_split_violin
```{r}
GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
  grp <- data[1, "group"]
  newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
  newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])

  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
      1))
    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
    aesthetics$alpha <- rep(1, nrow(quantiles))
    both <- cbind(quantiles, aesthetics)
    quantile_grob <- GeomPath$draw_panel(both, ...)
    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
  }
  else {
    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
  }
})

geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
                              show.legend = NA, inherit.aes = TRUE) {
  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
}
```

A function to run Kruskall-Wallis test and Dunn tests for each panel
```{r}
fitness_KW_test <- function(data, y, group){
  # non-parametric: Kruskall-Wallis test followed by Dunn test
  # run KW test using rstatix::kruskal_test
  KWtest <- eval(substitute(data %>% kruskal_test(y ~ group)))
  # get effect size using effectsize::rank_epsilon_squared
  KWepsilon2 <- eval(substitute(rank_epsilon_squared(y ~ group, data=data)))
  # run Dunn test using rstatix::dunn_test
  dunn <- eval(substitute(data %>% dunn_test(y ~ group)))
  # get multiple comparison groups letters using multcompView::multcompLetters
  dunn.vec <- dunn$p.adj.signif
  names(dunn.vec) <- paste(dunn$group1,dunn$group2,sep="-")
  multcompLetters <- tibble(x=names(multcompLetters(dunn.vec)$Letters),
                            label=unname(multcompLetters(dunn.vec)$Letters))
  # return
  out <- list(KWtest=KWtest, KWepsilon2=KWepsilon2, dunn=dunn, multcompLetters=multcompLetters)
  return(out)
}

fitness_life_strats_data.itero <- filter(fitness_life_strats_data, n_clutches_with_eggs_iv>1)
fitness_future_stats_eggs.itero <- 
  fitness_KW_test(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat_ants)

KWtest <- fitness_life_strats_data %>% kruskal_test(est_eggs_future ~ desert_cat_ants)

# # test
# fitness_life_strats_data <- est_fitness_life_strats %>% 
#   mutate(desert_cat_ants = ifelse(ants_removed, 
#                                   paste(desert_cat,"ants removed"),paste(desert_cat,"control")))
# fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)

# # Troubleshooting:
# fitness_life_strats_data %>% filter(!females_removed, !is.na(desert_cat)) %>% 
#     ggplot(data = ., aes(x = desert_cat, y = est_eggs_life, fill = ants_removed, 
#         color = ants_removed)) + ylim(-160 * 0.05, 160) + 
#   geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
#   geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
#              pch = 16, size = 2, key_glyph = draw_key_rect) + 
#     xlab("Guarding strategy for first clutch") + theme_publilia() + 
#     scale_fill_manual(labels = c("Control", "Ants removed"), 
#         values = c("brown1", "black")) + scale_color_manual(labels = c("Control", 
#     "Ants removed"), values = c("brown1", "black")) + 
#   geom_text(data = fitness_stats_eggs$multcompLetters, 
#             aes(x = x, y = -160 * 0.05, label = label), 
#             fontface = "bold", size = 4, position = position_dodge(width = 0.5)) + 
#   scale_x_discrete(labels = c("desert", "eggs", "nymphs", "visit"))
# 
# fitness_life_strats_data %>% filter(!females_removed, !is.na(desert_cat)) %>% 
#     ggplot(data = ., aes(x = desert_cat, y=est_eggs_life, fill=ants_removed, color=ants_removed)) + 
#   ylim(-160 * 0.05, 160) + 
#   geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
#   geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
#              pch = 16, size = 2, key_glyph = draw_key_rect) + 
#     xlab("Guarding strategy for first clutch") + theme_publilia() + 
#     scale_fill_manual(labels = c("Control", "Ants removed"), values = c("brown1", "black")) + 
#   scale_color_manual(labels = c("Control", "Ants removed"),  values = c("brown1", "black")) + 
#   geom_text(data = fitness_stats_eggs$multcompLetters, 
#     aes(x = x, y = -160 * 0.05, label = label), 
#     fontface = "bold", size = 4, position=position_dodge(width=0.5)) + 
#   scale_x_discrete(labels = c("desert", "eggs", "nymphs", "visit"))

# plot boxplots, including KWtest letters
fitness_plot_dunn <- function(data, y, group, itero=F, multcompLetters, letterSize, ymax=160){
  if(itero==F){
    (p <- eval(substitute(data %>%
      filter(!females_removed, !is.na(group)) %>%
    ggplot(data = ., aes(x = group, y=y, fill=ants_removed, color=ants_removed)) + 
      ylim(-ymax * 0.05, ymax) + 
      geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
      geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
                 pch = 16, size = 2, key_glyph = draw_key_rect) + 
      xlab("Guarding strategy for first clutch") + theme_publilia() + 
      scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
      scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
      geom_text(data = multcompLetters, 
                aes(x = x, y = -ymax * 0.05, label = label), 
                fontface = "bold", size = letterSize, position=position_dodge(width=0.5)))))
    return(p)
  } else {
    # single-clutch females
    (p_semel <- eval(substitute(data %>%
      filter(!females_removed, !is.na(group),
             (n_clutches_with_eggs_iv==1)) %>%
        ggplot(data = ., aes(x = group, y=y, fill=ants_removed, color=ants_removed)) + 
          ylim(-ymax * 0.05, ymax) + 
          geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
          geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
                     pch = 16, size = 2, key_glyph = draw_key_rect) + 
          xlab("Guarding strategy for first clutch") + theme_publilia() + 
          scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
          scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
          geom_text(data = multcompLetters, 
                    aes(x = x, y = -ymax * 0.05, label = label), 
                    fontface = "bold", size = letterSize, position=position_dodge(width=0.5)))))
    # multi-clutch females
     (p_itero <- eval(substitute(data %>%
      filter(!females_removed, !is.na(group),
             (n_clutches_with_eggs_iv>1)) %>%
        ggplot(data = ., aes(x = group, y=y, fill=ants_removed, color=ants_removed)) + 
          ylim(-ymax * 0.05, ymax) + 
          geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
          geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
                     pch = 16, size = 2, key_glyph = draw_key_rect) + 
          xlab("Guarding strategy for first clutch") + theme_publilia() + 
          scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
          scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
          geom_text(data = multcompLetters, 
                    aes(x = x, y = -ymax * 0.05, label = label), 
                    fontface = "bold", size = letterSize, position=position_dodge(width=0.5)))))
    p_list<-list(semel=p_semel, itero=p_itero)
    return(p_list)
  }
}

# test
# fitness_life_strats_data <- est_fitness_life_strats %>%
#   mutate(desert_cat_ants = ifelse(ants_removed,
#                                   paste(desert_cat,"ants removed"),paste(desert_cat,"control")))
# eggs_fitness_stats <- fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
# 
# fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants,
#                   itero=F, multcompLetters=eggs_fitness_stats$multcompLetters,
#                   letterSize=8)
```

## Not separating single-clutch and multi-clutch females (for main)
```{r}
letterSize<-3

fitness_life_strats_data <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs"),
         desert_cat_ants = ifelse(ants_removed, 
                                 paste(desert_cat,"ants removed"),paste(desert_cat,"control")),
         desert_cat_ants = factor(desert_cat_ants,
          levels=c("visit control", "desert control", "eggs control","nymphs control",
                   "visit ants removed", "desert ants removed", "eggs ants removed","nymphs ants removed")))

fitness_stats_eggs_v6 <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
fitness_stats_eggs_v6["multcompLetters"]$multcompLetters$x <- 
  factor(rep(c("visit", "desert","eggs", "nymphs"),2), levels=c("visit", "desert","eggs", "nymphs"))
fitness_stats_eggs_v6["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_eggs_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_eggs_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_eggs_v6$multcompLetters,
                    letterSize=letterSize, ymax=160) +
  ylab("Lifetime fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

fitness_stats_hatched_v6 <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat_ants)
fitness_stats_hatched_v6["multcompLetters"]$multcompLetters$x <- rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_stats_hatched_v6["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_hatched_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_hatched_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_hatched_v6$multcompLetters,
                    letterSize=letterSize, ymax=100) +
  ylab("Lifetime fitness\n(eggs hatched)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

fitness_stats_survived_v6 <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat_ants)
fitness_stats_survived_v6["multcompLetters"]$multcompLetters$x <- rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_stats_survived_v6["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_survived_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_survived_v6.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_survived_v6$multcompLetters,
                    letterSize=letterSize, ymax=30) +
  ylab("Lifetime fitness\n(nymphs survived)") + 
  theme(legend.position=c(0.3,0.9))

fitness_stats.v6.p.final <-
  egg::ggarrange(fitness_stats_eggs_v6.p, fitness_stats_hatched_v6.p, fitness_stats_survived_v6.p,
                 labels=c("A","B","C"), ncol=1, nrow=3)

ggsave("fitness_stats.violin.final.png",
       fitness_stats.v6.p.final,
       device = "png",
       width = 120, height = 200, units = "mm", dpi = "print")
```

## Just offspring counts (no imputation)
```{r}
letterSize<-3

fitness_life_strats_data <- est_fitness_life_strats %>%
  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs"),
         desert_cat_ants = ifelse(ants_removed, 
                                 paste(desert_cat,"ants removed"),paste(desert_cat,"control")),
         desert_cat_ants = factor(desert_cat_ants,
          levels=c("visit control", "desert control", "eggs control","nymphs control",
                   "visit ants removed", "desert ants removed", "eggs ants removed","nymphs ants removed")))

fitness_stats_eggs_v1 <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
fitness_stats_eggs_v1["multcompLetters"]$multcompLetters$x <- 
  factor(rep(c("visit", "desert","eggs", "nymphs"),2), levels=c("visit", "desert","eggs", "nymphs"))
fitness_stats_eggs_v1["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_eggs_v1["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_eggs_v1.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_eggs_v1$multcompLetters,
                    letterSize=letterSize, ymax=160) +
  ylab("Lifetime fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

fitness_stats_hatched_v1 <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat_ants)
fitness_stats_hatched_v1["multcompLetters"]$multcompLetters$x <- rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_stats_hatched_v1["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_hatched_v1["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_hatched_v1.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_hatched_v1$multcompLetters,
                    letterSize=letterSize, ymax=100) +
  ylab("Lifetime fitness\n(eggs hatched)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank())

fitness_stats_survived_v1 <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat_ants)
fitness_stats_survived_v1["multcompLetters"]$multcompLetters$x <- rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_stats_survived_v1["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_survived_v1["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_survived_v1.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat, 
                    itero=F, multcompLetters=fitness_stats_survived_v1$multcompLetters,
                    letterSize=letterSize, ymax=30) +
  ylab("Lifetime fitness\n(nymphs survived)") + 
  theme(legend.position=c(0.3,0.9))

fitness_stats.v1.p.final <-
  egg::ggarrange(fitness_stats_eggs_v1.p, fitness_stats_hatched_v1.p, fitness_stats_survived_v1.p,
                 labels=c("A","B","C"), ncol=1, nrow=3)

ggsave("fitness_stats.supp_v1.violin.final.png",
       fitness_stats.v1.p.final,
       device = "png",
       width = 120, height = 200, units = "mm", dpi = "print")
```

## Separating single-clutch and multi-clutch females (for main)
```{r}
letterSize<-3

fitness_life_strats_data.semel <- filter(fitness_life_strats_data, n_clutches_with_eggs_iv==1)
fitness_life_strats_data.itero <- filter(fitness_life_strats_data, n_clutches_with_eggs_iv>1)

fitness_stats_eggs.semel <- 
  fitness_KW_test(data=fitness_life_strats_data.semel, 
                  y=est_eggs_life, group=desert_cat_ants)
fitness_stats_eggs.semel["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_stats_eggs.semel["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_eggs.semel["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_eggs.semel.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_eggs.semel$multcompLetters,
                    letterSize=letterSize, ymax=160)$semel +
  ylab("Single-clutch female\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

fitness_stats_eggs.itero <- 
  fitness_KW_test(data=fitness_life_strats_data.itero, 
                  y=est_eggs_life, group=desert_cat_ants)
fitness_stats_eggs.itero["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_stats_eggs.itero["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_eggs.itero["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_eggs.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_eggs.itero$multcompLetters,
                    letterSize=letterSize, ymax=160)$itero +
  ylab("Multi-clutch female\nfecundity (eggs laid)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

fitness_stats_hatched.semel <- 
  fitness_KW_test(data=fitness_life_strats_data.semel, 
                  y=est_hatched_life_v6, group=desert_cat_ants)
fitness_stats_hatched.semel["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_stats_hatched.semel["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_hatched.semel["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_hatched.semel.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_hatched.semel$multcompLetters,
                    letterSize=letterSize, ymax=100)$semel +
  ylab("Single-clutch female\nfitness (eggs hatched)") + 
    theme(legend.position=c(0.3,0.8), axis.title.x = element_blank(),axis.text.x=element_blank())

fitness_stats_hatched.itero <- 
  fitness_KW_test(data=fitness_life_strats_data.itero, 
                  y=est_hatched_life_v6, group=desert_cat_ants)
fitness_stats_hatched.itero["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_stats_hatched.itero["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_hatched.itero["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_hatched.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_hatched.itero$multcompLetters,
                    letterSize=letterSize, ymax=100)$itero +
  ylab("Multi-clutch female\nfitness (eggs hatched)") + 
    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())

fitness_stats_survived.semel <- 
  fitness_KW_test(data=fitness_life_strats_data.semel, 
                  y=est_survived_life_v6, group=desert_cat_ants)
fitness_stats_survived.semel["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_stats_survived.semel["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_survived.semel["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_survived.semel.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_survived.semel$multcompLetters,
                    letterSize=letterSize, ymax=30)$semel +
  ylab("Single-clutch female\nfitness (nymphs survived)") + 
    theme(legend.position="none")

fitness_stats_survived.itero <- 
  fitness_KW_test(data=fitness_life_strats_data.itero, 
                  y=est_survived_life_v6, group=desert_cat_ants)
fitness_stats_survived.itero["multcompLetters"]$multcompLetters$x <- 
  rep(c("visit", "desert","eggs", "nymphs"),2)
fitness_stats_survived.itero["multcompLetters"]$multcompLetters <- 
  bind_cols(fitness_stats_survived.itero["multcompLetters"]$multcompLetters, 
            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))

fitness_stats_survived.itero.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
                    itero=T, multcompLetters=fitness_stats_survived.itero$multcompLetters,
                    letterSize=letterSize, ymax=30)$itero +
  ylab("Multi-clutch female\nfitness (nymphs survived)") + 
    theme(legend.position="none")

fitness_stats.parity.p.final <- egg::ggarrange(
  fitness_stats_eggs.semel.p, fitness_stats_eggs.itero.p,
  fitness_stats_hatched.semel.p, fitness_stats_hatched.itero.p,
  fitness_stats_survived.semel.p, fitness_stats_survived.itero.p,
  labels=c("A","B","C","D","E","F"), ncol=2, nrow=3)

ggsave("fitness_stats.violin.parity.final.png",
       fitness_stats.parity.p.final,
       device = "png",
       width = 200, height = 200, units = "mm", dpi = "print")
```

## Comparing to Zink 2003 fitness measures
Lifetime fitness (number of eggs that hatched):
w(t_i) = sum(from i=1, to i=N, P_i*g(t_i))
P = number of eggs invested in a clutch (all the eggs go to the initiator?)
t_i = guarding duration in clutch i
N = lifetime number of clutches
g(t) = relationship between guarding duration and hatching success
 (assume g(t) equivalent across all clutches 1 to N)

* The main reason Zink found equivalent fitness is that he attributed all the eggs in a clutch to each primary female. Thus an early deserter is given all the eggs from a clutch, even if she leaves within a few days and another female arrives and lays additional eggs.
```{r}
ggplot(data=filter(surv_reg_data_zink, initiation_date<=as_date("2019-06-10")), 
       aes(x=max_primary_dur, y=n_hatched/med_t5eggs)) +
  geom_point() +
  geom_smooth(method=lm)

zink_hatch.m <- surv_reg_data_zink %>%
  filter(initiation_date<=as_date("2019-06-10"), !is.na(n_hatched/med_t5eggs)) %>%
lm(n_hatched/med_t5eggs ~ max_primary_dur, data=.)

summary(zink_hatch.m) # use this for predicting hatching success
```

```{r}
zink_fitness_plot_dunn <- function(data, y, group, multcompLetters, letterSize, ymax=160){
  (p <- eval(substitute(data %>%
    filter(!females_removed, !is.na(desert_cat)) %>%
    ggplot(data=., aes(x=group, y=y)) + ylim(-ymax*0.05,ymax) +
    geom_boxplot(aes(fill=group), 
                 position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
    stat_summary(aes(fill=group), 
                 fun=mean, geom="point", shape=4, size=3, color="black", key_glyph=draw_key_rect) +
    #ylab("Lifetime fecundity\n(eggs laid)")  +
    xlab("Guarding strategy for first clutch") +
    theme_publilia() +
    geom_text(data=multcompLetters, aes(x=x, y=-ymax*0.05, label=label), fontface="bold", size=letterSize))))
  return(p)
}
```

```{r}
# v1: Zink 2003 attributes all egg in a clutch to the primary female, even if they desert early and a visitor laid additional eggs
zink_fitness_stats_v1 <- 
  fitness_KW_test(data=est_fitness_life_strats_Zink, y=zink_est_hatch_life_v1, group=zink_dur_cat)
(Zink_fitness_v1.p <- 
  zink_fitness_plot_dunn(data=est_fitness_life_strats_Zink, y=zink_est_hatch_life_v1, group=zink_dur_cat, 
                    multcompLetters=zink_fitness_stats_v1$multcompLetters,
                    letterSize=4, ymax=150) +
  ylab("Lifetime fitness: Zink 2003\n(all eggs to primary mother,\nlinear model predicts hatching)") +
    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
    theme(legend.position="none",
          axis.text.x=element_text(angle=45, vjust=1, hjust=1)))

est_fitness_life_strats_Zink %>%
  filter(!females_removed, !is.na(desert_cat)) %>%
  group_by(zink_dur_cat) %>% 
    summarize(mean_fitness=mean(zink_est_hatch_life_v1),
              median_fitness=median(zink_est_hatch_life_v1))

# v2: all calculations the same, but give eggs to females in proportion to the time they spent at clutch relative to other females
zink_fitness_stats_v2 <- 
  fitness_KW_test(data=est_fitness_life_strats_Zink, y=zink_est_hatch_life_v2, group=zink_dur_cat)
(Zink_fitness_v2.p <- 
  zink_fitness_plot_dunn(data=est_fitness_life_strats_Zink, y=zink_est_hatch_life_v2, group=zink_dur_cat, 
                    multcompLetters=zink_fitness_stats_v2$multcompLetters,
                    letterSize=4, ymax=150) +
  ylab("Lifetime fitness: modified from Zink 2003\n(eggs proportional to guarding,\nlinear model predicts hatching)") +
    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
    theme(legend.position="none",
          axis.text.x=element_text(angle=45, vjust=1, hjust=1)))

(Zink_fitness.p.final <- egg::ggarrange(
  Zink_fitness_v1.p, Zink_fitness_v2.p, 
  labels=c("A","B"),
  ncol=2, nrow=1))

ggsave("Zink_fitness.final.png",
       Zink_fitness.p.final,
       device = "png",
       width = 200, height = 120, units = "mm", dpi = "print")

# same but separating females that laid one vs. multiple clutches
zink_fitness_data.semel <- est_fitness_life_strats_Zink %>% 
  filter(n_clutches_with_eggs_iv==1)
zink_fitness_stats_v1.semel <- 
  fitness_KW_test(data=zink_fitness_data.semel, y=zink_est_hatch_life_v1, group=zink_dur_cat)
(Zink_fitness_v1.semel.p <- 
  zink_fitness_plot_dunn(data=zink_fitness_data.semel, y=zink_est_hatch_life_v1, group=zink_dur_cat, 
                    multcompLetters=zink_fitness_stats_v1.semel$multcompLetters,
                    letterSize=4, ymax=150) +
  ylab("Lifetime fitness: Zink 2003\n(all eggs to primary mother,\nlinear model predicts hatching)") +
    ggtitle("Single-clutch mothers") +
    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank()))

zink_fitness_data.itero <- est_fitness_life_strats_Zink %>% 
  filter(n_clutches_with_eggs_iv>1)
zink_fitness_stats_v1.itero <- 
  fitness_KW_test(data=zink_fitness_data.itero, y=zink_est_hatch_life_v1, group=zink_dur_cat)
(Zink_fitness_v1.itero.p <- 
  zink_fitness_plot_dunn(data=zink_fitness_data.itero, y=zink_est_hatch_life_v1, group=zink_dur_cat, 
                    multcompLetters=zink_fitness_stats_v1.itero$multcompLetters,
                    letterSize=4, ymax=150) + ggtitle("Multi-clutch mothers") +
    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank(),
          axis.title.y = element_blank(),axis.text.y=element_blank()))

zink_fitness_data.semel <- est_fitness_life_strats_Zink %>% 
  filter(n_clutches_with_eggs_iv==1)
zink_fitness_stats_v2.semel <- 
  fitness_KW_test(data=zink_fitness_data.semel, y=zink_est_hatch_life_v2, group=zink_dur_cat)
(Zink_fitness_v2.semel.p <- 
  zink_fitness_plot_dunn(data=zink_fitness_data.semel, y=zink_est_hatch_life_v2, group=zink_dur_cat, 
                    multcompLetters=zink_fitness_stats_v2.semel$multcompLetters,
                    letterSize=4, ymax=150) +
  ylab("Lifetime fitness: modified from Zink 2003\n(all eggs to primary mother,\nlinear model predicts hatching)") +
    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
    theme(legend.position="none",
          axis.text.x=element_text(angle=45, vjust=1, hjust=1)))

zink_fitness_data.itero <- est_fitness_life_strats_Zink %>% 
  filter(n_clutches_with_eggs_iv>1)
zink_fitness_stats_v2.itero <- 
  fitness_KW_test(data=zink_fitness_data.itero, y=zink_est_hatch_life_v2, group=zink_dur_cat)
(Zink_fitness_v2.itero.p <- 
  zink_fitness_plot_dunn(data=zink_fitness_data.itero, y=zink_est_hatch_life_v2, group=zink_dur_cat, 
                    multcompLetters=zink_fitness_stats_v2.itero$multcompLetters,
                    letterSize=4, ymax=150) +
    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
    theme(legend.position="none",
          axis.text.x=element_text(angle=45, vjust=1, hjust=1),
          axis.title.y = element_blank(),axis.text.y=element_blank()))

(Zink_fitness.parity.p.final <- egg::ggarrange(
  Zink_fitness_v1.semel.p, Zink_fitness_v1.itero.p,
  Zink_fitness_v2.semel.p, Zink_fitness_v2.itero.p,
  labels=c("A","B","C","D"),
  ncol=2, nrow=2))

ggsave("Zink_fitness.parity.final.png",
       Zink_fitness.parity.p.final,
       device = "png",
       width = 200, height = 200, units = "mm", dpi = "print")

```

why such a small first clutch and larger future clutches for early deserters? early deserters lay more or larger clutches?
```{r}
est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  mutate(parity=ifelse(n_clutches_with_eggs_iv==1,"semel","itero")) %>%
  count(parity,zink_dur_cat)

est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  mutate(parity=ifelse(n_clutches_with_eggs_iv==1,"semel","itero")) %>%
  group_by(zink_dur_cat,parity) %>%
  summarize(n=n(),
            mean_n_clutches=mean(n_clutches_with_eggs_iv),
            mean_max_primary_dur=mean(max_primary_dur)) %>%
  ungroup()

est_fitness_life_strats_Zink %>%
  filter(!females_removed) %>%
  mutate(parity=ifelse(n_clutches_with_eggs_iv==1,"semel","itero")) %>%
  group_by(desert_cat,parity) %>%
  summarize(n=n(),
            mean_n_clutches=mean(n_clutches_with_eggs_iv),
            mean_max_primary_dur=mean(max_primary_dur)) %>%
  ungroup()

fitness_life_strats_data %>%
  filter(!females_removed) %>%
  mutate(parity=ifelse(n_clutches_with_eggs_iv==1,"semel","itero")) %>%
  group_by(parity, ants_removed, desert_cat) %>%
  summarize(n=n(),
            mean_n_clutches=mean(n_clutches_with_eggs_iv)) %>%
  ungroup()

```

## Clutch fitness prediction performance for imputation
```{r}
# Consistency is ok worse for hatching; MANY clutches with no surviving nymphs were predicted to have survived
(predicted_clutch_A <- est_fitness_clutch %>% 
  filter(!is.na(est_hatched_clutch_v1),!is.na(est_hatched_clutch_v6)) %>%
  ggplot(data=., aes(x=est_hatched_clutch_v1, y=est_hatched_clutch_v6, color=interaction(vis,ants))) +
  geom_abline(slope=1) +
  geom_point() + xlim(0,80) + ylim(0,80) +
  theme(legend.position="none"))

# Consistency is MUCH worse for survivorship; MANY clutches with no surviving nymphs were predicted to have survived
(predicted_clutch_B <- est_fitness_clutch %>%
  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
  ggplot(data=., aes(x=est_survived_clutch_v1, y=est_survived_clutch_v6, color=interaction(vis,ants))) +
  geom_abline(slope=1) +
  geom_point()  + xlim(0,60) + ylim(0,60) +
  theme(legend.position=c(0.3,0.8)))

(predicted_clutch.p.final <- egg::ggarrange(
  predicted_clutch_A, predicted_clutch_B,
  labels=c("A","B"),
  ncol=2, nrow=1))

ggsave("predicted_clutch.final.png",
       predicted_clutch.p.final,
       device = "png",
       width = 200, height = 100, units = "mm", dpi = "print")
```

### Life fitness prediction performance for imputation
Should I include this in the supplment?
```{r}
# hatching: ok correspondence, the spread is tighter, but range is preserved
(predicted_clutch_A <- est_fitness_clutch %>% 
  filter(!is.na(est_hatched_clutch_v1),!is.na(est_hatched_clutch_v6)) %>%
  ggplot(data=., aes(x=des, y=est_hatched_clutch_v1, color=ants, fill=ants)) +
  geom_point() +
  geom_smooth(span=1) + ylim(0,60) +
   xlab("Desertion date relative to hatch\non first clutch") + 
   ylab("Clutch-level fitness\n(hatched eggs observed)") + 
   scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
   scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
   theme(legend.position="none",
         axis.text.x=element_text(angle=45, vjust=1, hjust=1),
         strip.background = element_blank()) +
  facet_wrap(vars(vis)))

(predicted_clutch_B <-est_fitness_clutch %>% 
  filter(!is.na(est_hatched_clutch_v6)) %>%
  ggplot(data=., aes(x=des, y=est_hatched_clutch_v6, color=ants, fill=ants)) +
  geom_point() +
  geom_smooth(span=1) + ylim(0,60) +
   xlab("Desertion date relative to hatch\non first clutch") + 
   ylab("Clutch-level fitness\n(hatched eggs predicted by model)") + 
   scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
   scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
    theme(legend.position="none",
         axis.text.x=element_text(angle=45, vjust=1, hjust=1),
         strip.background = element_blank()) +
  facet_wrap(vars(vis)))

# survival: ok correspondence, the spread is MUCH tighter and range is more limited; losing many higher values
(predicted_clutch_C <- est_fitness_clutch %>% 
  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
  ggplot(data=., aes(x=des, y=est_survived_clutch_v1, color=ants, fill=ants)) +
  geom_point() +
  geom_smooth(span=1) + ylim(0,60) +
    xlab("Desertion date relative to hatch\non first clutch") + 
   ylab("Clutch-level fitness\n(surviving nymphs observed)") + 
   scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
   scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
    theme(legend.position="none",
         axis.text.x=element_text(angle=45, vjust=1, hjust=1),
         strip.background = element_blank()) +
  facet_wrap(vars(vis)))

(predicted_clutch_D <-est_fitness_clutch %>% 
  filter(!is.na(est_survived_clutch_v6)) %>%
  ggplot(data=., aes(x=des, y=est_survived_clutch_v6, color=ants, fill=ants)) +
  geom_point() +
  geom_smooth(span=1) + ylim(0,60) +
    xlab("Desertion date relative to hatch\non first clutch") + 
   ylab("Clutch-level fitness\n(hatched eggs predicted by model)") + 
   scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
   scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
    theme(legend.position=c(0.75,0.75),
         axis.text.x=element_text(angle=45, vjust=1, hjust=1),
         strip.background = element_blank()) +
  facet_wrap(vars(vis)))

(predicted_clutch.p.final <- egg::ggarrange(
  predicted_clutch_A, predicted_clutch_B,
  predicted_clutch_C, predicted_clutch_D,
  labels=c("A","B","C","D"),
  ncol=2, nrow=2))

ggsave("predicted_clutch.final.png",
       predicted_clutch.p.final,
       device = "png",
       width = 200, height = 200, units = "mm", dpi = "print")
```

### Estimating fitness from counts instead of from survivorship function
```{r}
# fitness_life_strats_data <- fitness_life_strats_data %>%
#   mutate(desert_cat_ants = factor(desert_cat_ants, levels=c("desert control", "eggs control", 
#                                 "nymphs control", "visit control",
#                                 "desert ants removed", "eggs ants removed", 
#                                 "nymphs ants removed", "visit ants removed")))

fitness_stats_eggs_counted <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
(fitness_counted_stats_eggs.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants, 
                    itero=F, multcompLetters=fitness_stats_eggs_counted$multcompLetters,
                    letterSize=4, ymax=160) +
  ylab("Lifetime fecundity\n(eggs laid)") + 
    theme(legend.position="none",
          axis.title.x = element_blank(),axis.text.x=element_blank()))

fitness_stats_hatched_counted <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat_ants)
(fitness_counted_stats_hatched.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat_ants, 
                    itero=F, multcompLetters=fitness_stats_hatched_counted$multcompLetters,
                    letterSize=4, ymax=75) +
  ylab("Lifetime fitness\n(eggs hatched)") + 
    theme(legend.position=c(0.75,0.9),
          axis.title.x = element_blank(),axis.text.x=element_blank()))

fitness_stats_survived_counted <- 
  fitness_KW_test(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat_ants)
(fitness_counted_stats_survived.p <- 
  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat_ants, 
                    itero=F, multcompLetters=fitness_stats_survived_counted$multcompLetters,
                    letterSize=4, ymax=30) +
  ylab("Lifetime fitness\n(nymphs survived)") + 
    theme(legend.position="none",
          axis.text.x=element_text(angle=45, vjust=1, hjust=1)))

(fitness_counted_stats.p.final <- egg::ggarrange(
  fitness_counted_stats_eggs.p,
  fitness_counted_stats_hatched.p,
  fitness_counted_stats_survived.p,
  labels=c("A","B","C"),
  ncol=1, nrow=3))

# ggsave("CHAPTER/fitness_counted_stats.final.png",
#        fitness_counted_stats.p.final,
#        device = "png",
#        width = 120, height = 200, units = "mm", dpi = "print")
```

### 2023-08-24 scripts/old/Publilia_2019_CHAPTER-3A-survivorship-moms.Rmd
added old scripts to `scripts/old/` for reference

---
title: "Publilia_2019_CHAPTER-3A-survivorship-moms"
author: "micah fletcher"
date: "1/18/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Publilia 2019 Chapter - Script 3A: survivorship - clutch-level
This is meant to consolidate previous scripts and provide a readable and reproducible record of the analyses for the Publilia Chapter.

3) *Clutch-level survivorship regressions:* The impact of care on offspring survivorship depends on ants and offspring stage
  - *Dataset D [survivorship ~ guarding duration]* requirements:
    - Guarding durations (relative to [estimated] hatching) are accurate.
    - (Clutch-level) Hatching success is accurate.
    - Number of eggs is accurate.
    - Must exclude clutches where migration to/from other leaves obscured nymph count.
      - This biases the results toward only including clutches alone on a plant, while clearly it is common to have multiple clutches on a plant. One way to address this is to compare to plant-level analysis, so I may reuse parts of this pipeline for the plant-level analysis.
    - (Clutch-level) Nymph survivorship is accurate.
    - Must exclude clutches where migration to/from other leaves obscured nymph count. This biases the results in the same way as above.
    - Main analysis on first clutches laid before June 10. 
    - But also report on [] in the supplement.
      - the full dataset
      - single-female clutches only
      - female-removal included vs. excluded
    - Missing data is clearly represented; Compare the "original" unfiltered data to the final data and report why (and how many) data were excluded.
  - *Dataset E [clutch survivorship ~ ants]* requirements:
    - Same as Dataset B but also need a representative measure of ant attendance intensity/persistence, e.g.:
      - percent days attended before hatch
      - mean/median number of ants before hatch
      - number of days it took for ants to appear at clutch after hatch
      - Note: these would ideally be comparable to plant-level metrics

# 0 - Data import
```{r}
library(gt)
library(gtsummary)
library(flextable)
theme_gtsummary_compact()
```

# 1 - Data prep

## 1.0 - Assigning nymph origins
Nymphs migrate away from their natal leaf. On plants with multiple clutches, it was sometimes possible to determine the origin of nymphs later in the season because sometimes groups of nymph don't travel very far from their natal leaf and mix with other groups. I manually curated examples of this, so that clutch-level stats on hatching success and nymph survivorship could be determined on the plants with multiple clutches. Some clutches (as a rule only on multi-clutch plants) did not have a clear record of nymphs that emigrated from the natal leaf and thus could not be included in future clutch-level analyses of survivorship.

## 1.1 - Adding second gen adult counts per leaf to clutch status stats
```{r}
# counting adults
eA_status_v1 <- All_data_v6 %>%
  group_by(row_number()) %>% # sum of newly exclosed adults
  filter(any(!is.na(c(New_eA, Old_eA)))) %>%
  mutate(n_newA = ifelse(is.na(New_eA),
                         NA,
                         sum(as.numeric(regmatches(New_eA, gregexpr("[0-9]+", New_eA))[[1]]))),
         n_oldA = ifelse(is.na(Old_eA),
                         NA,
                         sum(as.numeric(regmatches(Old_eA, gregexpr("[0-9]+", Old_eA))[[1]]))),
         n_A = sum(n_newA, n_oldA, na.rm = TRUE)) %>%
  ungroup() %>%
  select(Date, location, n_newA, n_oldA, n_A)

All_data_v6_clutch_status_stats_v2 <- All_data_v6 %>%
  # add egg measures, clutch status stats (including initiation dates, hatch dates, egg fate, etc)
  left_join(clutch_status_v2, by = c("location", "Date")) %>%
  left_join(clutch_status_stats_v1, by = c("location")) %>%
  left_join(eA_status_v1, by = c("Date", "location")) %>%
  left_join(select(clutch_status_guarding_summary_v2, location, never_hatched)) %>%
  mutate(N1 = as.numeric(N1),
         N2 = as.numeric(N2),
         N5 = as.numeric(N5))
```

## 1.2 - Manually check nymph origins for revision
First create a table of all entried from clutches that were not flagged in the field as having ambiguous origin (e.g. "leaf 6 or 9") in cases were more than one clutch was on the plant. These were revised manually to specify a leaf of origin for the nymphs, where possible.
```{r}
NOr_status_resolveable_all_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>% 
  select(Date, Dorm, Plant, Leaf, location, 
         egg_num, N1, N2, N5, n_A, nymph_origin, initiation_date, hatch_date,
         any_NOr_ambig_loc, Omit_for_abandon_time, never_hatched,
         n_clutches_on_plant) %>%
  # keep only entries with some nymphs or adults on a leaf
  # OR entries for leaves where clutches have been initiated
  group_by(row_number()) %>%
  filter(!is.na(Leaf) & any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) | 
           Date >= initiation_date) %>% # nrow = 17944
  # flag entries where the nymph origin is text (typically ambiguous, e.g. "8 or 9")
  mutate(NOr_ambig_entry = !is.na(nymph_origin) & is.na(as.numeric(nymph_origin))) %>% 
  ungroup() %>%
  # get rid of duplicate rows from multiple females in the same location
  distinct(Date, location, .keep_all = TRUE) %>% # nrow = 15674
  group_by(Dorm, Plant) %>%
    # filter out any plants with a clutch that was omitted for abandon time
    filter(!any(!is.na(Omit_for_abandon_time))) %>%
    # flag plants with any ambiguous entries (e.g. "8 or 9") skip for checking
    mutate(NOr_ambig_plant = any(NOr_ambig_entry)) %>%
  ungroup()

NOr_status_resolveable_mult_clutches <- NOr_status_resolveable_all_unambig_clutches %>% # nrow = 15674
  group_by(Dorm, Plant) %>%
    # plants with mutliple clutches only
    filter(any(n_clutches_on_plant > 1)) %>%
  ungroup() %>%
  group_by(row_number()) %>%
    # flag for manual checking entries with any nymphs/adults, missing nymph origin, 
    # but not flagged for ambiguous origin in the field.
    # these are the most likely to be easily resolved with minimal work
    mutate(revise_NOr = ifelse(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) &
             !NOr_ambig_plant,
           "MANUAL CHECK",
           NA)) %>% 
  ungroup()

NOr_manual_check_table <- NOr_status_resolveable_mult_clutches %>%
  group_by(Dorm, Plant) %>%
    filter(any(revise_NOr == "MANUAL CHECK")) %>% # nrow = 2830
  ungroup() %>%
    group_by(row_number()) %>%
    filter(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0)) %>%
  ungroup() %>%
  select(Date, Dorm, Plant, Leaf, location, egg_num, N1, N2, N5, n_A, nymph_origin,
         initiation_date, hatch_date,
         revise_NOr) %>%
  arrange(Dorm, as.numeric(Plant), as.numeric(Leaf), Date)
# 83 clutches on 34 plants to check

# write_csv(NOr_manual_check_table %>% filter(revise_NOr == "MANUAL CHECK"), "NOr_manual_check_tmp.csv")

NOr_manual_revisions <- read_xlsx(in_filename, sheet = "NOr_manual_check", col_types = c("date", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "text", "logical", "text")) %>%
  mutate(Date = as_date(Date),
         NOr_rev_loc_manual = paste0(Dorm, Plant, "_", NOr_revised)) %>%
  filter(!cant_resolve) %>%
  select(Date, location, NOr_rev_loc_manual, NOr_revised_manual = NOr_revised)

NOr_manual_revisions %>%
  distinct(NOr_rev_loc_manual) # 43/83 initiated clutches (43/59 hatched) with successfully revised NOr
```

## 1.3 - Implement revisions by creating the new variables NOr_revised and NOr_rev_loc
```{r}
# if nymph origin was clearly resolveable, the revisions were made in NOr_manual_revisions
# updating NOr_status with revisions so that it can be left_joined to other data and
# counts of nymphs and adults on NOr can be calculated
NOr_status_revised_all_unambig_clutches <- NOr_status_resolveable_all_unambig_clutches %>%
  left_join(NOr_manual_revisions, by = c("Date", "location")) %>%
  group_by(Dorm, Plant) %>%
    mutate(lone_hatcher_leaf = ifelse(length(unique(Leaf[!is.na(initiation_date)])) == 1,
                                 unique(Leaf[!is.na(initiation_date)]),
                                 NA),
           NOr_revised = ifelse(!is.na(NOr_revised_manual),
                                       NOr_revised_manual,
                                ifelse(any(!is.na(lone_hatcher_leaf)),
                                       lone_hatcher_leaf,
                                       # if no clutches hatched on the plant, NOr_revised = Leaf
                                       # for leaves with eggs
                                       ifelse(!any(!is.na(hatch_date)) & !is.na(egg_num),
                                              Leaf,
                                              NA)))) %>%
  ungroup() %>%  
  group_by(location) %>%
    mutate(NOr_revised = ifelse(any(NOr_revised == Leaf) & is.na(NOr_revised),
                                Leaf,#unique(NOr_revised[!is.na(NOr_revised)]),
                                NOr_revised)) %>%
  ungroup() %>%
  mutate(NOr_rev_loc = ifelse(is.na(NOr_revised),
                              NA,
                              paste0(Dorm, Plant, "_", NOr_revised))) %>%
  select(Date, location, NOr_revised, NOr_rev_loc) %>%
  filter(!is.na(NOr_rev_loc))

All_data_v6_N_NOr_counts_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>%
  right_join(NOr_status_revised_all_unambig_clutches, by = c("Date", "location")) %>%
  group_by(Date, Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
    summarize(N1_NOr = sum(N1, na.rm= TRUE),
              N2_NOr = sum(N2, na.rm= TRUE),
              N5_NOr = sum(N5, na.rm= TRUE),
              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
              A_NOr = sum(n_A, na.rm= TRUE),
              N5plusA_NOr = sum(N5, n_A, na.rm= TRUE)) %>%
  ungroup() # n = 186

# All_data_v6_N_NOr_counts_unambig_clutches %>% distinct(Dorm, Plant, NOr_rev_loc) # n = 186

All_data_v6_N_NOr_counts_unambig_clutches_summary <- All_data_v6_N_NOr_counts_unambig_clutches %>%
  group_by(Date) %>%
    mutate(mean_N_NOr = mean(N_NOr, na.rm = TRUE),
           mean_N1_NOr = mean(N1_NOr, na.rm = TRUE),
           mean_N2_NOr = mean(N2_NOr, na.rm = TRUE),
           mean_N5_NOr = mean(N5_NOr, na.rm = TRUE),
           mean_A_NOr = mean(A_NOr, na.rm = TRUE),
           mean_N5plusA_NOr = mean(N5plusA_NOr, na.rm = TRUE),
           All_N_NOr = sum(N_NOr),
           All_A_NOr = sum(A_NOr)) %>%
  ungroup() %>%
  group_by(Date, Dorm) %>%
    mutate(All_N_NOr_Dorm = sum(N_NOr),
           All_N1_NOr_Dorm = sum(N1_NOr),
           All_N2_NOr_Dorm = sum(N2_NOr),
           All_N5_NOr_Dorm = sum(N5_NOr),
           All_A_NOr_Dorm = sum(sum(A_NOr))) %>%
  ungroup()

ggplot(data = All_data_v6_N_NOr_counts_unambig_clutches_summary) +
  geom_boxplot(aes(x = Date, y = N_NOr, group = Date)) +
  geom_line(aes(x = Date, y = mean_N_NOr), color = "red")

ggplot(data = All_data_v6_N_NOr_counts_unambig_clutches_summary) +
  geom_line(aes(x = Date, y = mean_N_NOr), color = "black") +
  geom_line(aes(x = Date, y = mean_N1_NOr), color = "green") +  
  geom_line(aes(x = Date, y = mean_N2_NOr), color = "blue") +
  geom_line(aes(x = Date, y = mean_N5_NOr), color = "purple") +
  geom_line(aes(x = Date, y = mean_A_NOr), color = "pink") +
  geom_line(aes(x = Date, y = mean_N5plusA_NOr), color = "red")

ggplot(data = All_data_v6_N_NOr_counts_unambig_clutches_summary) +
  geom_line(aes(x = Date, y = All_N_NOr), color = "black")

ggplot(data = All_data_v6_N_NOr_counts_unambig_clutches_summary) +
  geom_line(aes(x = Date, y = All_N_NOr_Dorm, color = Dorm))

All_data_v6_all_nymphs_unambig_clutches <- All_data_v6_N_NOr_counts_unambig_clutches %>%
  group_by(Date) %>%
    summarize(All_N_NOr = sum(N_NOr)) %>%
  ungroup()

ggplot(data = All_data_v6_all_nymphs_unambig_clutches) +
  geom_line(aes(x = Date, y = All_N_NOr), color = "black")

All_data_v6_max_N_NOr_counts_unambig_clutches <-
  All_data_v6_N_NOr_counts_unambig_clutches %>%
  group_by(Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
    summarize(max_N_NOr = max(N_NOr)) %>%
  ungroup()

clutch_status_stats_v1_unambig_clutches_hatch_success <- clutch_status_stats_v1 %>%
  separate(location, c("DormPlant", "Leaf"), sep = "_", remove = FALSE) %>%
  mutate(Dorm = substr(DormPlant, 1, 1),
         Plant = substring(DormPlant, 2)) %>%
  left_join(distinct(clutch_status_guarding_summary_v2, location, never_hatched)) %>%
  right_join(All_data_v6_max_N_NOr_counts_unambig_clutches, by = c("Dorm", "Plant", "Leaf" = "NOr_revised")) %>%
  # why did I originally say to make hatch_success = NA if never_hatched == TRUE?
  mutate(hatch_success = ifelse(!is.na(initiation_date) & is.na(hatch_date),
                                0,
                                max_N_NOr/max_egg_num))
```

Is 190/ really the best we can do for the sample size of clutches with known hatching success?
```{r}
clutch_status_guarding_summary_v2 %>%
# add number of clutches per plant
  separate(location, c("DormPlant", "Leaf"), "_", remove = FALSE) %>%
  mutate(Dorm = substr(DormPlant, 1,1),
         Plant = substring(DormPlant, 2)) %>%
  distinct(location, n_clutches_on_plant, initiation_date, any_NOr_ambig_loc) %>%
  group_by(n_clutches_on_plant == 1, initiation_date <= as_date("2019-06-10"), any_NOr_ambig_loc) %>%
  summarize(N = n()) %>%
  ungroup()

# there are 319 unique clutches with known inits that have not been flagged for ambig nymph origin in the field
clutch_status_guarding_summary_v2 %>%
# add number of clutches per plant
  separate(location, c("DormPlant", "Leaf"), "_", remove = FALSE) %>%
  mutate(Dorm = substr(DormPlant, 1,1),
         Plant = substring(DormPlant, 2)) %>%
  distinct(location, n_clutches_on_plant, initiation_date, any_NOr_ambig_loc) %>%
  group_by(!is.na(initiation_date), any_NOr_ambig_loc) %>%
  summarize(N = n()) %>%
  ungroup()

NOr_status_resolveable_all_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>% 
  select(Date, Dorm, Plant, Leaf, location, 
         egg_num, N1, N2, N5, n_A, nymph_origin, initiation_date, hatch_date,
         any_NOr_ambig_loc, Omit_for_abandon_time, never_hatched,
         n_clutches_on_plant) %>%
  # keep only entries with some nymphs or adults on a leaf
  # OR entries for leaves where clutches have been initiated
  group_by(row_number()) %>%
  filter(!is.na(Leaf) & any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) | 
           Date >= initiation_date) %>% # nrow = 17944
  # flag entries where the nymph origin is text (typically ambiguous, e.g. "8 or 9")
  mutate(NOr_ambig_entry = !is.na(nymph_origin) & is.na(as.numeric(nymph_origin))) %>% 
  ungroup() %>%
  # get rid of duplicate rows from multiple females in the same location
  distinct(Date, location, .keep_all = TRUE) %>% # nrow = 15674
  group_by(Dorm, Plant) %>%
    # filter out any plants with a clutch that was omitted for abandon time
    filter(!any(!is.na(Omit_for_abandon_time))) %>%
    # flag plants with any ambiguous entries (e.g. "8 or 9") skip for checking
    mutate(NOr_ambig_plant = any(NOr_ambig_entry)) %>%
  ungroup()

NOr_status_resolveable_all_unambig_clutches %>% 
  filter(!is.na(initiation_date)) %>% 
  distinct(location) # 314

NOr_status_resolveable_mult_clutches <- NOr_status_resolveable_all_unambig_clutches %>% # nrow = 15674
  group_by(Dorm, Plant) %>%
    # plants with mutliple clutches only
    filter(any(n_clutches_on_plant > 1)) %>%
  ungroup() %>%
  group_by(row_number()) %>%
    # flag for manual checking entries with any nymphs/adults, missing nymph origin, 
    # but not flagged for ambiguous origin in the field.
    # these are the most likely to be easily resolved with minimal work
    mutate(revise_NOr = ifelse(any(N1 > 0, N2 > 0, N5 > 0, n_A > 0) &
             !NOr_ambig_plant,
           "MANUAL CHECK",
           NA)) %>% 
  ungroup()

NOr_status_resolveable_mult_clutches %>%
  filter(!is.na(initiation_date)) %>%
  distinct(location, revise_NOr) %>%
  group_by(revise_NOr) %>%
  summarize(n())

############## looking at what clutches are NOT included in hatch success data
clutch_status_stats_v1 %>%
  separate(location, c("DormPlant", "Leaf"), sep = "_", remove = FALSE) %>%
  mutate(Dorm = substr(DormPlant, 1, 1),
         Plant = substring(DormPlant, 2)) %>%
  left_join(distinct(clutch_status_guarding_summary, location, never_hatched)) %>%
  full_join(All_data_v6_max_N_NOr_counts_unambig_clutches, by = c("Dorm", "Plant", "Leaf" = "NOr_revised")) %>%
  # why are so many "never_hatched" NA?
  mutate(hatch_success = ifelse(is.na(hatch_date),
                                0,
                                max_N_NOr/max_egg_num)) %>%
  group_by(Dorm, Plant) %>%
  mutate(any_NOr_ambig_loc_Plant = any(any_NOr_ambig_loc)) %>%
  ungroup() %>%
  filter(is.na(hatch_success), !any_NOr_ambig_loc_Plant) %>% View()

hatch_success_tmp1 <- clutch_status_stats_v1 %>%
  separate(location, c("DormPlant", "Leaf"), sep = "_", remove = FALSE) %>%
  mutate(Dorm = substr(DormPlant, 1, 1),
         Plant = substring(DormPlant, 2)) %>%
  left_join(distinct(clutch_status_guarding_summary_v2, location, never_hatched)) %>%
  full_join(All_data_v6_max_N_NOr_counts_unambig_clutches, by = c("Dorm", "Plant", "Leaf" = "NOr_revised")) %>%
  # why are so many "never_hatched" NA?
  mutate(hatch_success = ifelse(!is.na(initiation_date) & is.na(hatch_date),
                                0,
                                max_N_NOr/max_egg_num))

# hatch_success_tmp1 %>%
#   filter(!is.na(hatch_success), initiation_date <= as_date("2019-06-10")) %>% View()

ggplot(data = filter(hatch_success_tmp1, initiation_date <= as_date("2019-06-10"))) +
  geom_histogram(aes(x = hatch_success))

```

```{r}
# Fixing the omission of clutches that never had first instar nymphs
NOr_status_revised_all_unambig_clutches_v2 <- NOr_status_resolveable_all_unambig_clutches %>%
  left_join(NOr_manual_revisions, by = c("Date", "location")) %>%
  group_by(Dorm, Plant) %>%
    mutate(lone_hatcher_leaf = ifelse(length(unique(Leaf[!is.na(initiation_date)])) == 1,
                                 unique(Leaf[!is.na(initiation_date)]),
                                 NA),
           NOr_revised = ifelse(!is.na(NOr_revised_manual), # if I manually annotated a revised location
                                       NOr_revised_manual, # make manual location the new nymph origin
                                ifelse(any(!is.na(lone_hatcher_leaf)), # if only one clutch hatched on the plant
                                       lone_hatcher_leaf, # make that clutch the new nymph origin
                                       # if no clutches hatched on the plant, NOr_revised = Leaf
                                       # for leaves with eggs
                                       ifelse(!any(!is.na(hatch_date)) & !is.na(egg_num), # if no clutches hatched on the plant (but there are eggs)
                                              Leaf, # make the given leaf the new nymph origin
                                              NA)))) %>% # BUT THIS STILL EXCLUDES CLUTCHES THAT DIDN'T HATCH ON A PLANT WITH SOME CLUTCHES THAT DID HATCH
  ungroup() %>%  
  group_by(location) %>%
    mutate(NOr_revised = ifelse(any(NOr_revised == Leaf) & is.na(NOr_revised), # DOES THIS INCLUDE UNHATCHED CLUTCHES? NO
                                Leaf,#unique(NOr_revised[!is.na(NOr_revised)]),
                                NOr_revised),
           NOr_revised = ifelse(any(is.na(NOr_revised)) & # if no revised nymph origin yet
                                                  any(!is.na(egg_num)&egg_num>0 & !any(!is.na(N1)&N1>0)), # and N1 never on clutch (not hatched or spuriously visited by N1)
                                Leaf, # make this leaf the new nymph origin (so we include unhatched clutches)
                                NOr_revised)) %>% 
  ungroup() %>%
  mutate(NOr_rev_loc = ifelse(is.na(NOr_revised),
                              NA,
                              paste0(Dorm, Plant, "_", NOr_revised))) %>%
  select(Date, location, NOr_revised, NOr_rev_loc) %>%
  filter(!is.na(NOr_rev_loc))

All_data_v6_N_NOr_counts_unambig_clutches_v2 <- All_data_v6_clutch_status_stats_v2 %>%
  right_join(NOr_status_revised_all_unambig_clutches_v2, by = c("Date", "location")) %>%
  group_by(Date, Dorm, Plant, NOr_revised, NOr_rev_loc) %>%
    summarize(N1_NOr = sum(N1, na.rm= TRUE),
              N2_NOr = sum(N2, na.rm= TRUE),
              N5_NOr = sum(N5, na.rm= TRUE),
              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
              A_NOr = sum(n_A, na.rm= TRUE),
              N5plusA_NOr = sum(N5, n_A, na.rm= TRUE)) %>%
  ungroup() # n = 186

# All_data_v6_N_NOr_counts_unambig_clutches %>% distinct(Dorm, Plant, NOr_rev_loc) # n = 186

All_data_v6_N_NOr_counts_unambig_clutches_summary_v2 <- All_data_v6_N_NOr_counts_unambig_clutches_v2 %>%
  group_by(Date) %>%
    mutate(mean_N_NOr = mean(N_NOr, na.rm = TRUE),
           mean_N1_NOr = mean(N1_NOr, na.rm = TRUE),
           mean_N2_NOr = mean(N2_NOr, na.rm = TRUE),
           mean_N5_NOr = mean(N5_NOr, na.rm = TRUE),
           mean_A_NOr = mean(A_NOr, na.rm = TRUE),
           mean_N5plusA_NOr = mean(N5plusA_NOr, na.rm = TRUE),
           All_N_NOr = sum(N_NOr),
           All_A_NOr = sum(A_NOr)) %>%
  ungroup() %>%
  group_by(Date, Dorm) %>%
    mutate(All_N_NOr_Dorm = sum(N_NOr),
           All_N1_NOr_Dorm = sum(N1_NOr),
           All_N2_NOr_Dorm = sum(N2_NOr),
           All_N5_NOr_Dorm = sum(N5_NOr),
           All_A_NOr_Dorm = sum(sum(A_NOr))) %>%
  ungroup()

```

Calculate hatch success (strict sense; max N1 / max eggs) and nymph survivorship (max N5+A / max eggs AND/OR max N5+A / max N1)
- Filtered out clutches with outlier numbers of N1 or N5 etc at early or late clutch ages, which were assumed to be cases of immigration that weren't caught during manual nymph origin filtering
```{r}
# Filter to only include curated list of clutches with unambiguous nymph counts after accounting for immigration to non-natal leaves and then sum all nymphs (including emigrants) for each clutch
# I also added clutch_age variables to help identify clutches that were started too close to the end of sampling to be useful
clutch_unambig_NOr_revised_ENAa_summary_v2 <- All_data_v6_clutch_status_stats_v2 %>%
  right_join(NOr_status_revised_all_unambig_clutches_v2, by = c("Date", "location")) %>%
  select(Date, NOr_rev_loc, location, egg_num, N1, N2, N5, n_A, ants_L) %>%
    # remove any duplicates - I need to figure out why there are dups later but for 4th yr talk
  distinct(Date, NOr_rev_loc, location, egg_num, N1, N2, N5, n_A, ants_L, .keep_all = TRUE) %>%
  mutate(egg_num_NOr = ifelse(NOr_rev_loc == location, egg_num, NA)) %>%
  group_by(Date, NOr_rev_loc) %>%
    summarize(eggs_NOr = first(egg_num_NOr[!is.na(egg_num_NOr)]), # only use eggs from origin leaf!
              N1_NOr = sum(N1, na.rm= TRUE),
              N2_NOr = sum(N2, na.rm= TRUE),
              N5_NOr = sum(N5, na.rm= TRUE),
              N_NOr = sum(N1, N2, N5, na.rm = TRUE),
              A_NOr = sum(n_A, na.rm= TRUE),
              N5toA_NOr = sum(N5, n_A, na.rm= TRUE),
              ants_NOr = sum(ants_L, na.rm = TRUE)) %>%
  ungroup() %>%
  left_join(filter(clutch_status_guarding_summary_v2, mom_at_init), by = c("NOr_rev_loc" = "location")) %>%
  mutate(clutch_age1 = Date - initiation_date,
         clutch_age2 = ceiling((Date - initiation_date)/2)*2,
         clutch_age4 = ceiling((Date - initiation_date)/4)*4,
         after_hatch1 = Date - hatch_date,
         after_hatch2 = ceiling((Date - hatch_date)/2)*2,
         after_hatch4 = ceiling((Date - hatch_date)/4)*4) %>%
  select(Date, NOr_rev_loc, clutch_age1, after_hatch1, eggs_NOr, 
         N1_NOr, N2_NOr, N5_NOr, N_NOr, A_NOr, N5toA_NOr, ants_NOr,
         init_fem = Female_ID,
         initiation_date, hatch_date, guard_duration, relative_desert_date,
         clutch_initiated_order, females_removed, ants_removed, 
         clutch_age2, clutch_age4, after_hatch2, after_hatch4) #%>%
  # filter(initiation_date <= as_date("2019-06-10"),
  #        clutch_age4 <= 68)

max_N1_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
  group_by(NOr_rev_loc) %>%
  arrange(NOr_rev_loc, desc(N1_NOr), Date) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(NOr_rev_loc, max_N1_date = Date, max_N1_age = clutch_age1)

max_N5_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
  group_by(NOr_rev_loc) %>%
  arrange(NOr_rev_loc, desc(N5_NOr), Date) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(NOr_rev_loc, max_N5_date = Date, max_N5_age = clutch_age1)

max_A_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
  group_by(NOr_rev_loc) %>%
  arrange(NOr_rev_loc, desc(A_NOr), Date) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(NOr_rev_loc, max_A_date = Date, max_A_age = clutch_age1)

max_N5toA_date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
  group_by(NOr_rev_loc) %>%
  arrange(NOr_rev_loc, desc(N5toA_NOr), Date) %>%
  filter(row_number() == 1) %>%
  ungroup() %>%
  select(NOr_rev_loc, max_N5toA_date = Date, max_N5toA_age = clutch_age1)

max_N5toA_Date_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
  group_by(NOr_rev_loc) %>%
  summarize(max_N1 = max(N1_NOr),
            max_N5toA = max(N5toA_NOr),
            max_clutch_age = max(clutch_age1),
            max_after_hatch = max(after_hatch1),
            max_Date = max(Date),
            hatched = any(!is.na(hatch_date)),
            initiation_date = first(initiation_date)) %>%
  ungroup() %>%
  arrange(desc(max_N5toA)) %>%
  full_join(max_N1_date_v2) %>%
  full_join(max_N5_date_v2) %>%
  full_join(max_A_date_v2) %>%
  full_join(max_N5toA_date_v2)

ggplot(data = max_N5toA_Date_v2) +
  geom_point(aes(x = initiation_date, y = max_N5toA_age))

ggplot(data = max_N5toA_Date_v2) +
  geom_point(aes(x = initiation_date, y = max_N1_age))

ggplot(data = max_N5toA_Date_v2) +
  geom_point(aes(x = initiation_date, y = max_N5_age))

ggplot(data = max_N5toA_Date_v2) +
  geom_point(aes(x = initiation_date, y = max_A_age))

ggplot(data = max_N5toA_Date_v2) +
  geom_point(aes(x = max_clutch_age, y = max_N1, 
                 color = initiation_date >= as_date("2019-06-10")))

ggplot(data = max_N5toA_Date_v2) +
  geom_point(aes(x = initiation_date, y = max_N1))

ggplot(data = max_N5toA_Date_v2) +
  geom_point(aes(x = max_clutch_age, y = max_N5toA, 
                 color = initiation_date >= as_date("2019-06-10")))

ggplot(data = max_N5toA_Date_v2) +
  geom_point(aes(x = initiation_date, y = max_N5toA))

clutch_unambig_NOr_revised_ENAa_summary_imfilt_v2 <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
  mutate(N_imm_likely_d15 = clutch_age1 < 15 & N_NOr > 0,
         N5_imm_likely_d40 = clutch_age1 < 40 & N5_NOr > 0,
         A_imm_likely_d40 = clutch_age1 < 40 & A_NOr > 0) %>%
  group_by(NOr_rev_loc) %>%
    filter(!any(N_imm_likely_d15, N5_imm_likely_d40, A_imm_likely_d40, na.rm = TRUE)) %>% # n = 168
  ungroup()

clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_v2 <-
  clutch_unambig_NOr_revised_ENAa_summary_imfilt_v2 %>%
  group_by(NOr_rev_loc) %>%
    mutate(hatch_success_N1 = max(N1_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
           survival_rate = max(N5toA_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
           prop_E2Ni = max(N1_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
           prop_E2N = max(N_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
           prop_Ni2Nv = max(N5toA_NOr, na.rm = TRUE)/max(N1_NOr, na.rm = TRUE),
           prop_E2Nv = max(N5toA_NOr, na.rm = TRUE)/max(eggs_NOr, na.rm = TRUE),
           n_eggs = max(eggs_NOr, na.rm = TRUE),
           n_hatched = max(N1_NOr, na.rm = TRUE),
           n_N = max(N_NOr, na.rm = TRUE),
           n_survived = max(N5toA_NOr, na.rm = TRUE)) %>%
  ungroup()

clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2 <- clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_v2 %>%
  distinct(NOr_rev_loc, n_eggs, n_hatched, n_survived, n_N,
           prop_E2Ni, prop_Ni2Nv, prop_E2Nv, prop_E2N, hatch_success_N1, survival_rate,
           initiation_date, hatch_date, females_removed, ants_removed) 
```

# Ant counts on clutch; some ants_removed clutches were visited by ants, and vice versa
```{r}
ant_counts <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch) %>%
    summarize(ants_removed=first(ants_removed),
              females_removed=first(females_removed),
              n_antsP=sum(ants_P,na.rm=T),
              ever_antsP=n_antsP>0,
              mean_antsP=mean(ants_P,na.rm=T),
              med_antsP=median(ants_P,na.rm=T),

              n_antsP_b4h=sum(ants_P&b4h),
              ever_antsP_b4h=n_antsP_b4h>0,
              mean_antsP_b4h=mean(ifelse(b4h,ants_P,NA),na.rm=T),
              med_antsP_b4h=median(ifelse(b4h,ants_P,NA),na.rm=T),

              n_antsP_afh=sum(ants_P&afh),
              ever_antsP_afh=n_antsP_afh>0,
              mean_antsP_afh=mean(ifelse(afh,ants_P,NA),na.rm=T),
              med_antsP_afh=median(ifelse(afh,ants_P,NA),na.rm=T)) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ant_treatment=ifelse(ants_removed,"Ants removed","Control"))

ggplot(data=ant_counts,aes(x=Dorm,y=n_antsP, fill=ant_treatment)) +
  geom_boxplot()

ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP, fill=ant_treatment)) +
  geom_boxplot()

ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_b4h, fill=ant_treatment)) +
  geom_boxplot()

ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_afh, fill=ant_treatment)) +
  geom_boxplot()

ant_counts %>%
  count(Dorm,ant_treatment,ever_antsP)

ant_counts %>%
  count(Dorm,ant_treatment,ever_antsP_b4h)

ant_counts %>%
  count(Dorm,ant_treatment,ever_antsP_afh)

# how many clutches ever had ants in each of the dorms?
ant_counts %>%
  ggplot(data=., aes(y=as.numeric(ever_antsP), x=Dorm, fill=ant_treatment)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
  theme_publilia()

ant_counts %>%
  ggplot(data=., aes(y=as.numeric(ever_antsP_b4h), x=Dorm, fill=ant_treatment)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
  theme_publilia()

ant_counts %>%
  ggplot(data=., aes(y=as.numeric(ever_antsP_afh), x=Dorm, fill=ant_treatment)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
  theme_publilia()

# how extreme was the break-through?
ant_counts %>%
  ggplot(data=., aes(x=mean_antsP_b4h, color=ant_treatment, linetype=females_removed, group=Dorm)) +
  geom_freqpoly(bins=100)

ant_counts %>%
  ggplot(data=., aes(x=med_antsP_b4h, color=ant_treatment, linetype=females_removed, group=Dorm)) +
  geom_freqpoly()

ant_counts %>%
  ggplot(data=., aes(x=mean_antsP_afh, color=ant_treatment, linetype=females_removed, group=Dorm)) +
  geom_freqpoly(bins=100)

ant_counts %>%
  ggplot(data=., aes(x=med_antsP_afh, color=ant_treatment, linetype=females_removed, group=Dorm)) +
  geom_freqpoly()

# how many clutches actually ever had ants vs. not?
ant_counts %>%
  ggplot(data=., aes(x=ever_antsP_b4h, fill=ant_treatment)) +
  geom_bar() +
  theme_publilia() + facet_wrap(~females_removed)

ant_counts %>%
  ggplot(data=., aes(x=ever_antsP_afh, fill=ant_treatment)) +
  geom_bar() +
  theme_publilia() + facet_wrap(~females_removed)

ant_counts %>%
  ggplot(data=., aes(x=ever_antsP_b4h|ever_antsP_afh, fill=ant_treatment)) +
  geom_bar() +
  theme_publilia() + facet_wrap(~females_removed)

```

Should I be more lenient with my threshold, so I can have more even sample sizes between "ants" and "no ants"?
- ants_ever = n_days_ants>0: F = 95-12=83, T = 234-91=143
- antsP_gt2d = n_days_ants>2: F = 156-33=123, T = 173-70=103 * most even sample size
- antsP_gt3d = n_days_ants>3: F = 172-39=133, T = 157-64=90
```{r}
ant_n_days <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  mutate(ant_treatment=ifelse(ants_removed,"Ants removed","Control"),
         Dorm=substr(location,1,1)) %>%
  group_by(Date, location) %>%
    summarize(any_antsP_day = any(ants_P>0, na.rm=T),
              females_removed = first(females_removed),
              ant_treatment = first(ant_treatment),
              Dorm = first(Dorm)) %>%
  ungroup() %>%
  group_by(location) %>%
    summarize(n_days_ants = sum(as.numeric(any_antsP_day)),
              females_removed = first(females_removed),
              ant_treatment = first(ant_treatment),
              Dorm = first(Dorm))%>%
  ungroup() %>%
  mutate(antsP_gt2d = !is.na(n_days_ants)&n_days_ants>2,
         antsP_gt3d = !is.na(n_days_ants)&n_days_ants>3,
         ants_everP = is.na(n_days_ants)|n_days_ants>0)

ggplot(ant_n_days, aes(x=Dorm, y=n_days_ants, fill=ant_treatment)) +
  geom_boxplot()

ggplot(ant_n_days, aes(x=Dorm, y=n_days_ants, fill=ant_treatment)) +
  geom_violin() +
  geom_hline(yintercept=2.5)

ant_n_days %>%
  select(-location) %>%
  tbl_summary(by=ants_everP)

ant_n_days %>%
  select(-location) %>%
  tbl_summary(by=antsP_gt2d)

ant_n_days %>%
  select(-location) %>%
  tbl_summary(by=antsP_gt3d)
```

# 2 - egg survivorship ~ guarding duration * ants_removed * `visited in 4 days`

`The sum of all females’ egg-guarding durations was more predictive of final clutch size than egg guarding duration of the initiator alone (Table S1 with alternative models and their AICs), showing that females lay eggs while visiting existing clutches.`
```{r}
visited_1st_4d_data_tb
visited_1st_4d_data_tb %>% filter(!is.na(initiation_date))
visited_1st_4d_data_tb %>% filter(!is.na(initiation_date), !is.na(num_at_init))

##### initiator guarding time: mDb4h
initiator_days_b4hatch <- visited_1st_4d_data_tb %>%
  filter(!is.na(initiation_date),
         # exclude clutches for which the initiators are not known
         !is.na(num_at_init),
         mom_at_init) %>%
  group_by(row_number()) %>%
  # Use median init to hatch interval (20 days) to est hatch date of clutch with no hatch date
  mutate(init_dur = ifelse(min(est_hatch, visit_ends) - 
                                       max(initiation_date, visit_starts) >= 0,
                           visit_ends-initiation_date+1, 
                           NA),
         initMb4hatch = ifelse(min(est_hatch, visit_ends) - 
                                       max(initiation_date, visit_starts) >= 0,
           min(est_hatch, visit_ends) - 
           max(initiation_date, visit_starts) + 1,
           ifelse(visit_starts > est_hatch | visit_ends < initiation_date,
                  NA,
                  NA)),
         initMb4h_sc2h = initMb4hatch/as.numeric((est_hatch-initiation_date+1))) %>%
  ungroup()

initMb4h_tbL <- initiator_days_b4hatch %>%
  filter(initL) %>%
  select(location, desert_rel2hL=est_rel2h, init_durL=init_dur, initMb4h_tbL=initMb4hatch, initMb4h_sc2hL=initMb4h_sc2h,
         females_removed, ants_removed, initiation_date, num_at_init,
         initiator_tbL=Female_ID, n_clutches_on_plant)

initMb4h_tbS <- initiator_days_b4hatch %>%
  filter(initS) %>%
  select(location, desert_rel2hS=est_rel2h, init_durS=init_dur, initMb4h_tbS=initMb4hatch, initMb4h_sc2hS=initMb4h_sc2h,
         females_removed, ants_removed, initiation_date, num_at_init,
         initiator_tbS=Female_ID, n_clutches_on_plant)

##### proportional time: mDb4h
focalMb4h_sc2h <- visited_1st_4d_data_tb  %>%
  # exclude visits to leaves that never had eggs; only interested in clutches
  filter(!is.na(initiation_date),
         # exclude clutches for which the initiators are not known (why?)
         !is.na(num_at_init)) %>%
  group_by(row_number()) %>%
  # Use median init to hatch interval (20 days) to est hatch date of clutch with no hatch date
  mutate(mD = ifelse(min(est_hatch, visit_ends) - 
                                       max(initiation_date, visit_starts) >= 0,
                     visit_ends-initiation_date+1,
                     NA),
         days_guard_b4hatch = ifelse(min(est_hatch, visit_ends) - 
                                       max(initiation_date, visit_starts) >= 0,
           min(est_hatch, visit_ends) - 
           max(initiation_date, visit_starts) + 1,
           ifelse(visit_starts > est_hatch | visit_ends < initiation_date,
                  NA,
                  NA)),
         focalMb4h_sc2h = days_guard_b4hatch/as.numeric((est_hatch-initiation_date+1))) %>%
  ungroup()

clutch_momDays_b4h <- focalMb4h_sc2h %>%
  group_by(location) %>%
    summarize(sum_mD = sum(mD, na.rm=T),
              sum_vD = sum(mD*!mom_at_init, na.rm=T),
              sum_gD = sum(mD*mom_at_init, na.rm=T),
              vDb4h_sc2h = sum(days_guard_b4hatch*!mom_at_init, na.rm = T)/
                # scale to init-hatch interval so clutches with different intervals are comparable 
                as.numeric(first(est_hatch)-first(initiation_date)+1),
              gDb4h_sc2h = sum(days_guard_b4hatch*mom_at_init, na.rm = T)/
                as.numeric((first(est_hatch)-first(initiation_date)+1)),
              mDb4h_sc2h = sum(days_guard_b4hatch, na.rm = T)/
                as.numeric((first(est_hatch)-first(initiation_date)+1))) %>%
  ungroup()

clutch_status_momDays_b4h <- visited_1st_4d_data_tb %>%
  distinct(location, initiation_date, hatch_date, num_at_init,
           females_removed, ants_removed, egg_fate, egg_fate_date,
           max_egg_num, max_egg_len, `visited in 4 days`) %>%
  right_join(clutch_momDays_b4h, by=c("location")) %>%
  left_join(top5eggs_summary)

#### latest desertion
latest_desertions <- visited_1st_4d_data %>%
  filter(!is.na(initiation_date),
         !(visit_ends<initiation_date), # visits that end before initiation are irrelevant
         !(visit_starts>est_hatch+4)) %>% # there are a few cases where clutches are visited long after hatching, which wouldn't affect hatching success
  left_join(first_visit_cuts) %>%
  select(Female_ID:visit_ends, initiation_date, est_hatch, est_rel2h, 
         `visited in 4 days`, mom_at_init, ants_removed, females_removed) %>%
  group_by(location) %>%
  filter(any(mom_at_init)) %>% # remove any clutches where there was no apparent mother at initiation
  summarize(last_des_rel2h = max(ifelse(visit_starts<=initiation_date, est_rel2h, NA), na.rm=T),
            first_des_rel2h_init = min(ifelse(mom_at_init, est_rel2h, NA), na.rm=T),
            last_desert = ifelse(last_des_rel2h>=-2, "after hatch",
                                 ifelse(last_des_rel2h<=0, "before hatch", NA)),
            females_removed = first(females_removed),
            ants_removed = first(ants_removed),
            `visited in 4 days` = first(`visited in 4 days`),
            init_desert_early = ifelse(first(first_des_rel2h_init<=-16), "deserted early", "didn't desert early"),
            est_hatch = first(est_hatch)) %>%
  ungroup() #%>%
  # filter(!is.na(`visited in 4 days`)) %>% # E40_9 for some reason didn't get a valid visited in 4 days entry
  # filter(location!="A23_8") %>% # A23_8 has two moms at init but for some reason not `visited in 4 days`?

#### combine the three (but after getting more comfortable with the "latest_desertions" results I can omit the initL/S for simplicity)
clutch_egg_num_data <- latest_desertions %>%
  left_join(initMb4h_tbL) %>%
  left_join(initMb4h_tbS) %>%
  separate(location, sep = "_", into = c("DormPlant"),  remove = FALSE, extra = "drop") %>%
  left_join(select(clutch_status_momDays_b4h, location, sum_mD, sum_vD, sum_gD,
                   mDb4h_sc2h, gDb4h_sc2h, vDb4h_sc2h, max_egg_num, max_egg_len,
                   `visited in 4 days`)) %>%
  # if tbL and tbS are not the same female, add the female that lost the tie-break to the total sum of visit days
  mutate(sum_vD_initL = ifelse(initiator_tbL!=initiator_tbS,
                           sum_vD+init_durS, sum_vD),
         sum_vD_initS = ifelse(initiator_tbS!=initiator_tbL,
                           sum_vD+init_durL, sum_vD),
         visited = vDb4h_sc2h > 0,
         pmDvD = vDb4h_sc2h/mDb4h_sc2h) %>%
  left_join(top5eggs_summary) %>%
  select(location, last_des_rel2h, first_des_rel2h_init,
         ants_removed, females_removed, initiation_date, est_hatch, `visited in 4 days`,
         sum_mD, sum_vD, sum_gD, mDb4h_sc2h,
         num_at_init, init_desert_early, last_desert,
         n_eggs = max_egg_num, med_t5eggs, mean_t5eggs, max_n_eggs,
         max_egg_len, med_l_t5eggs, mean_l_t5eggs, max_l_eggs,
         init_durL, init_durS, desert_rel2hL, desert_rel2hS,
         sum_vD_initL, sum_vD_initS, initMb4h_sc2hL, initMb4h_sc2hS,
         initiator_tbL, initiator_tbS,
         n_clutches_on_plant, visited, pmDvD, DormPlant)

# add filtered and curated nymph and adult counts
clutch_survivorship_data <- clutch_egg_num_data %>%
  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2,
                   -c(ants_removed, females_removed, initiation_date, n_eggs)),
            by=c("location"="NOr_rev_loc"))

# older version so I can compare
clutch_egg_num_success_data_old <- initMb4h_tbL %>%
  left_join(initMb4h_tbS) %>%
  separate(location, sep = "_", into = c("DormPlant"),  remove = FALSE, extra = "drop") %>%
  left_join(select(clutch_status_momDays_b4h, location, mDb4h_sc2h, gDb4h_sc2h, vDb4h_sc2h, max_egg_num)) %>%
  mutate(visited = vDb4h_sc2h > 0,
         pmDvD = vDb4h_sc2h/mDb4h_sc2h) %>%
  # left_join(select(pDaysb4h_ants_moms, location, anyMb4h)) %>%
  # left_join(select(clutch_status_uDur_b4h, location, uDur_norm)) %>%
  # select(location, initMb4h_sc2hL, initMb4h_sc2hS, desert_rel2hL, desert_rel2hS, mDb4h_sc2h,
  #        anyMb4h, uDur_norm, females_removed, ants_removed, initiation_date, num_at_init, 
  #        n_eggs = max_egg_num, initiator_tbL, initiator_tbS, n_clutches_on_plant, 
  #        visited, visited_early, pmDvD, DormPlant) %>%
  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2, 
                   -females_removed, -ants_removed, -initiation_date, -n_eggs), by=c("location"="NOr_rev_loc"))
  # filter(initiation_date <= as_date("2019-06-10"), n_hatched/n_eggs <= 0.80)

```

## Quick plots before I start modeling
Note that there is a much steeper slope for hatching success for females forcibly removed than for control, suggesting that females are somehow aware of when deserting early is inconsequential.

Note that most of the late-season clutches do not pass the filtering and curation steps for n_hatched/n_eggs, and a few fewer were valid for n_survived/n_hatched
```{r}
clutch_survivorship_data %>%
  ggplot(data=., aes(x=n_hatched/n_eggs)) +
  geom_histogram()

clutch_survivorship_data %>%
  ggplot(data=., aes(x=n_hatched/med_t5eggs)) +
  geom_histogram()

clutch_survivorship_data %>%
  ggplot(data=., aes(x=n_survived/n_hatched)) +
  geom_histogram()

clutch_survivorship_data %>%
  ggplot(data=., aes(x=initiation_date, fill=!is.na(n_hatched/n_eggs))) +
  geom_histogram()

clutch_survivorship_data %>%
  ggplot(data=., aes(x=initiation_date, fill=!is.na(n_survived/n_hatched))) +
  geom_histogram()

clutch_survivorship_data %>%
  ggplot(data=., aes(y=n_hatched/n_eggs, x=last_des_rel2h)) +
  geom_point() +
  geom_smooth(method=lm)

# n_hatched/n_eggs
clutch_survivorship_data %>%
  ggplot(data=., aes(y=n_hatched/n_eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm)

clutch_survivorship_data %>%
  ggplot(data=., aes(y=n_hatched/n_eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(females_removed))

# n_hatched/med_t5eggs
clutch_survivorship_data %>%
  ggplot(data=., aes(y=n_hatched/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm)

clutch_survivorship_data %>%
  ggplot(data=., aes(y=n_hatched/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(females_removed))

# n_hatched/med_t5eggs comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_hatched/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants?")

# n_hatched/med_t5eggs comparing early vs. late season
clutch_survivorship_data %>% filter(!is.na(initiation_date)) %>% # 2 points
  ggplot(data=., aes(y=n_hatched/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(initiation_date > as_date("2019-06-15"))) +
  ggtitle("not really enough valid data in late season for comparison")

# n_survived/n_hatched
clutch_survivorship_data %>%
  ggplot(data=., aes(y=n_survived/n_hatched, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm)

clutch_survivorship_data %>%
  ggplot(data=., aes(y=n_survived/n_hatched, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(females_removed)) +
  ggtitle("intercept higher for clutches with females removed, but only for ants!")

# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_survived/n_hatched, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants!")

# n_hatched/med_t5eggs comparing `visited in 4 days`*females_removed
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_hatched/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`, females_removed)) +
  ggtitle("Intercept of hatching success higher if visited early, but only if females not removed?")

# n_survived/n_hatched comparing `visited in 4 days`*females_removed
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_survived/n_hatched, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`, females_removed)) +
  ggtitle("Survivorship higher for females that were visited before being removed, but only if ants present
          suggests that early-visits lead to larger clutches that can attract ants better.
          Survivorship also higher for early-visited females that were not removed, only if ants present.")

##### Egg-number on survivorship
# n_hatched/med_t5eggs comparing `visited in 4 days`*females_removed
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_hatched/med_t5eggs, x=med_t5eggs, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`, females_removed))

# n_hatched/med_t5eggs comparing `visited in 4 days`*females_removed
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_survived/n_hatched, x=med_t5eggs, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`, females_removed)) +
  ggtitle("Strong effect of clutch size on nymph survivorship for unvisited, removed females with ants;
          but no effect if visited...
          and no effect if female not removed")

# # There appear to be 3 outliers with hatch success > 1 and 1 with slightly higher than 1
# clutch_hatch_success_data_filt <- clutch_egg_num_success_data_filt %>%
#   filter(!is.na(prop_E2Ni)) %>%
#   filter(initiation_date <= as_date("2019-06-10"), n_hatched/n_eggs <= 1)
```

*Focus on recreating these two figures with negative binomial regression.*
The first shows that longer guarding improves hatching success in unvisited females, especially when ants are present, and that when females are visited, hatching success intercept increases and guarding remains helpful for clutches with ants but hatching success does not improve for females without ants.

The second shows that nymph survivorship is improved by guarding only in the absence of ants, but that if females are visited early with ants their intercept of nymph survivorship improves dramatically, allowing them to desert early with the same nymph survivorship as attended or unattended females that stayed long after hatching.
```{r} 
# n_hatched/med_t5eggs comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_hatched/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants?")

# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_survived/n_hatched, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants!")

```

Same thing but filtering out later season clutches, which we can't reliably determine survival to adulthood (because E->A is about 45-75 days, mean=60)
```{r}
date_cutoff <- as_date("2019-06-10")

clutch_survivorship_data %>%
  count(females_removed, ants_removed, !is.na(n_hatched/med_t5eggs)) %>%
  filter(`!is.na(n_hatched/med_t5eggs)`)

clutch_survivorship_data %>%
  filter(initiation_date<=date_cutoff) %>%
  count(females_removed, ants_removed, !is.na(n_hatched/med_t5eggs)) %>%
  filter(`!is.na(n_hatched/med_t5eggs)`)

clutch_survivorship_data %>%
  count(females_removed, ants_removed, !is.na(n_survived/n_hatched)) %>%
  filter(`!is.na(n_survived/n_hatched)`)

clutch_survivorship_data %>%
  filter(initiation_date<=date_cutoff) %>%
  count(females_removed, ants_removed, !is.na(n_survived/n_hatched)) %>%
  filter(`!is.na(n_survived/n_hatched)`)

clutch_survivorship_data %>%
  count(females_removed, ants_removed, !is.na(n_survived/med_t5eggs)) %>%
  filter(`!is.na(n_survived/med_t5eggs)`)

clutch_survivorship_data %>%
  filter(initiation_date<=date_cutoff) %>%
  count(females_removed, ants_removed, !is.na(n_survived/med_t5eggs)) %>%
  filter(`!is.na(n_survived/med_t5eggs)`)

# n_hatched/med_t5eggs comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_hatched/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  #facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("unfilt")

# n_hatched/med_t5eggs comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  filter(initiation_date<=date_cutoff) %>%
  ggplot(data=., aes(y=n_hatched/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  #facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("initiation_date<=date_cutoff")

# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_survived/n_hatched, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  #facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("unfilt")

# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  filter(initiation_date<=date_cutoff) %>%
  ggplot(data=., aes(y=n_survived/n_hatched, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  #facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("initiation_date<=date_cutoff")

# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_survived/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  #facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("unfilt")

# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  filter(initiation_date<=date_cutoff) %>%
  ggplot(data=., aes(y=n_survived/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  #facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("initiation_date<=date_cutoff")

```

Can we account for the high survivorship based on ant arrival times?
```{r}
# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  left_join(ant_data) %>%
  filter(initiation_date<=date_cutoff) %>%
  ggplot(data=., aes(y=n_survived/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(~(antL_arrival_afh<=4)) +
  ggtitle("antL_arrival_afh<=4")

# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  left_join(ant_data) %>%
  filter(initiation_date<=date_cutoff) %>%
  ggplot(data=., aes(y=n_survived/med_t5eggs, x=last_des_rel2h, 
                     color=as.numeric(antL_arrival_afh))) +
  geom_point() +
  geom_smooth(method=lm)
```

And these are important too. They show that early visits increase nymph survivorship, but only in the presence of ants. And importantly, early visits increase the intercept of nymph survivorship, such that laying more eggs doesn't improve survivorship further.

It's hard to decouple the benefit of eggs from continued nymph guarding without focusing on the female removal treatment. If females were removed before hatching, clutch size improved hatching success only if females were not visited, because if they were visited their nymph survivorship intercept increased dramatically and weakly decreased with increasing clutch sizes. So it would be perfectly fine to desert a clutch early if ants are present. All of this is only true when ants are present though, otherwise nymph survivorship is always very low.
```{r}
# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_survived/n_hatched, x=med_t5eggs, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants!")

# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_survived/n_hatched, x=med_t5eggs, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(ifelse(females_removed,"females removed","control"),
             `visited in 4 days`)) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants!")

# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  filter(females_removed, n_survived/n_hatched<=1) %>%
  ggplot(data=., aes(y=n_survived/n_hatched, x=med_t5eggs, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(ifelse(females_removed,"females removed","control"),
             `visited in 4 days`)) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants!")

# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  filter(females_removed, n_survived/n_hatched<=1) %>%
  ggplot(data=., aes(y=n_survived/n_hatched, x=med_t5eggs, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=loess) +
  facet_wrap(vars(ifelse(females_removed,"females removed","control"))) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants!")
```

n_hatched/med_t5eggs ~ des+ants+vis+des:ants+des:vis+ants:vis
```{r}
# n_hatched/med_t5eggs comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_hatched/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants?")

### fit model
hatch.data <- clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, n_hatched, med_t5eggs, 
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`) %>%
  mutate(ants=ifelse(ants, "Removed", "Control"))

hatch.mai.full.qb <- glm(n_hatched/med_t5eggs ~ 
            des*ants*vis,
          data = hatch.data,
          weights = med_t5eggs,
          family = quasibinomial)
summary(hatch.mai.full.qb)

hatch.mai.pw.qb <- glm(n_hatched/med_t5eggs ~ 
            des+ants+vis+des:ants+des:vis+ants:vis,
          data = hatch.data,
          weights = med_t5eggs,
          family = quasibinomial)
summary(hatch.mai.pw.qb)

hatch.mai.pw.b <- glm(n_hatched/med_t5eggs ~ 
            des+ants+vis+des:ants+des:vis+ants:vis,
          data = hatch.data,
          weights = med_t5eggs,
          family = binomial)
summary(hatch.mai.pw.b)
```

n_survived/n_hatched ~ des+ants+vis+des:ants+des:vis+ants:vis
```{r}
# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_survived/n_hatched, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants?")

### fit model
Nsurv.data <- clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, n_hatched, n_survived, 
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`) %>%
  mutate(n_survived = ifelse(n_survived/n_hatched > 1, # if n_survived/n_hatched>1
                             n_hatched, n_survived), # force n_survived/n_hatched=1
         ants=ifelse(ants, "Removed", "Control"))

Nsurv.mai.full.qb <- glm(n_survived/n_hatched ~ 
            des*ants*vis,
          data = Nsurv.data,
          weights = n_hatched,
          family = quasibinomial)
summary(Nsurv.mai.full.qb)

Nsurv.mai.pw.qb <- glm(n_survived/n_hatched ~ 
            des+ants+vis+des:ants+des:vis+ants:vis,
          data = Nsurv.data,
          weights = n_hatched,
          family = quasibinomial)
summary(Nsurv.mai.pw.qb)

Nsurv.mai.pw.b <- glm(n_survived/n_hatched ~ 
            des+ants+vis+des:ants+des:vis+ants:vis,
          data = Nsurv.data,
          weights = n_hatched,
          family = binomial)
summary(Nsurv.mai.pw.b)
```

n_survived/med_t5eggs ~ des+ants+vis+des:ants+des:vis+ants:vis
```{r}
# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  ggplot(data=., aes(y=n_survived/med_t5eggs, x=last_des_rel2h, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(`visited in 4 days`)) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants?")

### fit model
Esurv.data <- clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_survived, 
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`) %>%
  mutate(n_survived = ifelse(n_survived/med_t5eggs > 1,# if n_survived/med_t5eggs>1
                             med_t5eggs, n_survived), # force n_survived/n_hatched=1
         ants=ifelse(ants, "Removed", "Control"))

Esurv.mai.full.qb <- glm(n_survived/med_t5eggs ~ 
            des*ants*vis,
          data = Esurv.data,
          weights = med_t5eggs,
          family = quasibinomial)
summary(Esurv.mai.full.qb)

Esurv.mai.pw.qb <- glm(n_survived/med_t5eggs ~ 
            des+ants+vis+des:ants+des:vis+ants:vis,
          data = Esurv.data,
          weights = med_t5eggs,
          family = quasibinomial)
summary(Esurv.mai.pw.qb)

Esurv.mai.pw.b <- glm(n_survived/med_t5eggs ~ 
            des+ants+vis+des:ants+des:vis+ants:vis,
          data = Esurv.data,
          weights = med_t5eggs,
          family = binomial)
summary(Esurv.mai.pw.b)
```

n_survived/n_hatched ~ med_t5eggs * ants * vis
```{r}
# n_survived/n_hatched comparing `visited in 4 days`
clutch_survivorship_data %>% filter(!is.na(`visited in 4 days`)) %>% # 2 points
  filter(females_removed, n_survived/n_hatched<=1) %>%
  ggplot(data=., aes(y=n_survived/n_hatched, x=med_t5eggs, 
                     color=ants_removed, fill=ants_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  facet_wrap(vars(ifelse(females_removed,"females removed","control"),
             `visited in 4 days`)) +
  ggtitle("intercept higher for clutches that were visited early, but only for ants!")

### fit model
n_eggs.Nsurv.data <- clutch_survivorship_data %>% 
  filter(females_removed) %>%
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_survived, 
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`) %>%
  mutate(n_survived = ifelse(n_survived/med_t5eggs > 1,# if n_survived/med_t5eggs>1
                             med_t5eggs, n_survived), # force n_survived/n_hatched=1
         ants=ifelse(ants, "Removed", "Control"))

n_eggs.Nsurv.mai.full.qb <- glm(n_survived/med_t5eggs ~ 
            med_t5eggs*ants*vis,
          data = n_eggs.Nsurv.data,
          weights = med_t5eggs,
          family = quasibinomial)
summary(n_eggs.Nsurv.mai.full.qb)

n_eggs.Nsurv.mai.full.b <- glm(n_survived/med_t5eggs ~ 
            med_t5eggs*ants*vis,
          data = n_eggs.Nsurv.data,
          weights = med_t5eggs,
          family = binomial)
summary(n_eggs.Nsurv.mai.full.b)

n_eggs.Nsurv.mai.pw.qb <- glm(n_survived/med_t5eggs ~ 
            med_t5eggs+ants+vis+med_t5eggs:ants+med_t5eggs:vis+ants:vis,
          data = n_eggs.Nsurv.data,
          weights = med_t5eggs,
          family = quasibinomial)
summary(Esurv.mai.pw.qb)

n_eggs.Nsurv.mai.pw.b <- glm(n_survived/med_t5eggs ~ 
            med_t5eggs+ants+vis+med_t5eggs:ants+med_t5eggs:vis+ants:vis,
          data = n_eggs.Nsurv.data,
          weights = med_t5eggs,
          family = binomial)
summary(n_eggs.Nsurv.mai.pw.b)
```

## Functions to create plots and run stats using each model
with the visit in first four days parameter
```{r}
### fit survivorship model
fit_surv_vis <- function(data_in, survNom, survDen, tenure, 
                     treatment, vis, interaction=c("full","pw")){
  data <- eval(substitute(data_in %>% filter(!is.na(tenure))))

  if(interaction=="full"){
      mai.b <- eval(substitute(glm(survNom/survDen ~ 
                tenure*treatment*vis,
              data = data, weights = survDen, family = binomial)))
      print("Interaction, Binomial: ")
      print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])

      mai.qb <- eval(substitute(glm(survNom/survDen ~ 
                tenure*treatment*vis,
              data = data, weights = survDen, family = quasibinomial)))
      print("Interaction, Quasibinomial: ")
      print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

      ma.qb <- eval(substitute(glm(survNom/survDen ~ 
                tenure+treatment,
              data = data, weights = survDen, family = quasibinomial)))
      print("No Interaction, Quasibinomial: ")
      print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])
  } else if(interaction=="pw"){
      mai.b <- eval(substitute(glm(survNom/survDen ~ 
                tenure+treatment+vis+tenure:treatment+tenure:vis+treatment:vis,
              data = data, weights = survDen, family = binomial)))
      print("Interaction, Binomial: ")
      print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])

      mai.qb <- eval(substitute(glm(survNom/survDen ~ 
                tenure+treatment+vis+tenure:treatment+tenure:vis+treatment:vis,
              data = data, weights = survDen, family = quasibinomial)))
      print("Interaction, Quasibinomial: ")
      print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

      ma.qb <- eval(substitute(glm(survNom/survDen ~ 
                tenure+treatment+vis,
              data = data, weights = survDen, family = quasibinomial)))
      print("No Interaction, Quasibinomial: ")
      print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])
  } else {print("Must specify interaction=c(\"full\", \"pw\"")
  }
    mai.models <- list(mai.b = mai.b, mai.qb = mai.qb, ma.qb = ma.qb)
  return(mai.models)
}

# Example
# test_fits <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants, vis=vis,
#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)

### Create confidence intervals in the link scale for plotting, and backtransform for plot
# Based on: https://fromthebottomoftheheap.net/2018/12/10/confidence-intervals-for-glms/
ci_for_plot_vis <- function(data_in, survNom, survDen, 
                        tenure, treatment, vis, model){

  data <- eval(substitute(
    data_in %>% filter(!is.na(tenure)) %>%
      select(location, tenure, treatment, vis, survDen, survNom) %>%
      add_column(fit = predict(model, newdata = ., type = 'response'))
    ))

  ## grad the inverse link function
  ilink <- family(model)$linkinv

  ## add fit and se.fit on the **link** scale
  data_fit_link <- eval(substitute(
    data %>% add_column(
  setNames(as_tibble(predict(model, data, se.fit = TRUE)[1:2]),
           c('fit_link','se_link'))) %>%
## create the interval and backtransform
  mutate(fit_resp  = ilink(fit_link),
         conf_upr = ilink(fit_link + (2 * se_link)),
         conf_lwr = ilink(fit_link - (2 * se_link)))
    ))

  return(data_fit_link)
}

# Example
# test_fits.pw <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants, vis=vis,
#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)
# 
# test_ci_data <- ci_for_plot(data_in=hatch.data, tenure=des, treatment=ants, vis=vis,
#                  survNom=n_hatched, survDen=med_t5eggs,
#                  model = test_fits.pw$mai.qb)

### Plot model results with confidence intervals
plot_ci_vis <- function(ci_data, survNom, survDen, treatment, tenure, vis){
  (eval(substitute(plot <- ggplot(data = ci_data, 
       aes(x = tenure, y = fit, 
           color = treatment, fill = treatment)) +
    theme_publilia() +
    geom_point(aes(y = survNom/survDen), alpha = 0.1, size = 5) + 
    geom_line(aes(y = fit), size = 1) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.3, color = NA)))) +
    facet_wrap(vars(vis))
#
}

# Example
test_fits.pw <- fit_surv_vis(data_in=hatch.data, tenure=des, treatment=ants, vis=vis,
                 interaction="pw", survNom=n_hatched, survDen=med_t5eggs)

test_ci_data <- ci_for_plot_vis(data_in=hatch.data, tenure=des, treatment=ants, vis=vis,
                 survNom=n_hatched, survDen=med_t5eggs,
                 model = test_fits.pw$mai.qb)

(p <- plot_ci_vis(ci_data = test_ci_data, tenure = des, treatment=ants, vis=vis,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))
summary(test_fits.pw$mai.qb)
```

without the visit in first four days parameter
```{r}
### fit survivorship model
fit_surv <- function(data_in, survNom, survDen, tenure, 
                     treatment, vis, interaction=c("full","pw")){
  data <- eval(substitute(data_in %>% filter(!is.na(tenure))))

  mai.b <- eval(substitute(glm(survNom/survDen ~ 
            tenure*treatment,
          data = data, weights = survDen, family = binomial)))
  print("Interaction, Binomial: ")
  print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])

  mai.qb <- eval(substitute(glm(survNom/survDen ~ 
            tenure*treatment,
          data = data, weights = survDen, family = quasibinomial)))
  print("Interaction, Quasibinomial: ")
  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

  ma.qb <- eval(substitute(glm(survNom/survDen ~ 
            tenure+treatment,
          data = data, weights = survDen, family = quasibinomial)))
  print("No Interaction, Quasibinomial: ")
  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

  mai.models <- list(mai.b = mai.b, mai.qb = mai.qb, ma.qb = ma.qb)
  return(mai.models)
}

# Example
# test_fits <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants,
#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)

### Create confidence intervals in the link scale for plotting, and backtransform for plot
# Based on: https://fromthebottomoftheheap.net/2018/12/10/confidence-intervals-for-glms/
ci_for_plot <- function(data_in, survNom, survDen, 
                        tenure, treatment, model){

  data <- eval(substitute(
    data_in %>% filter(!is.na(tenure)) %>%
      select(location, tenure, treatment, survDen, survNom) %>%
      add_column(fit = predict(model, newdata = ., type = 'response'))
    ))

  ## grad the inverse link function
  ilink <- family(model)$linkinv

  ## add fit and se.fit on the **link** scale
  data_fit_link <- eval(substitute(
    data %>% add_column(
  setNames(as_tibble(predict(model, data, se.fit = TRUE)[1:2]),
           c('fit_link','se_link'))) %>%
## create the interval and backtransform
  mutate(fit_resp  = ilink(fit_link),
         conf_upr = ilink(fit_link + (2 * se_link)),
         conf_lwr = ilink(fit_link - (2 * se_link)))
    ))

  return(data_fit_link)
}

# Example
# test_fits.pw <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants, 
#                  interaction="pw", survNom=n_hatched, survDen=med_t5eggs)
# 
# test_ci_data <- ci_for_plot(data_in=hatch.data, tenure=des, treatment=ants, 
#                  survNom=n_hatched, survDen=med_t5eggs,
#                  model = test_fits.pw$mai.qb)

### Plot model results with confidence intervals
plot_ci <- function(ci_data, survNom, survDen, treatment, tenure){
  (eval(substitute(plot <- ggplot(data = ci_data, 
       aes(x = tenure, y = fit, 
           color = treatment, fill = treatment)) +
    theme_publilia() +
    geom_point(aes(y = survNom/survDen), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.5, color = NA, key_glyph=draw_key_rect))))
#
}

# Example
test_fits.pw <- fit_surv(data_in=hatch.data, tenure=des, treatment=ants,
                 interaction="pw", survNom=n_hatched, survDen=med_t5eggs)

test_ci_data <- ci_for_plot(data_in=hatch.data, tenure=des, treatment=ants,
                 survNom=n_hatched, survDen=med_t5eggs,
                 model = test_fits.pw$mai.qb)

(p <- plot_ci(ci_data = test_ci_data, tenure = des, treatment=ants,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))
summary(test_fits.pw$mai.qb)
```

# Final figures and stats using functions
Use the same data for each regression
```{r}
# I originally used the ants_removed as the predictor representing ants, but I am now redoing the analysis using whether ants were ever observed at the clutch.
surv_reg_data <- clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_hatched, n_survived,
         des=last_des_rel2h, ants_removed, vis=`visited in 4 days`,
         females_removed, initiation_date, est_hatch) %>%
  mutate(n_survived = ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
                             n_hatched, n_survived), # force n_survived/n_hatched=1
         ant_treatment=ifelse(ants_removed, "Removed", "Control")) %>%
  left_join(select(ant_counts, location, 
                   ever_antsP_b4h, ever_antsP_afh, ever_antsP)) %>%
  mutate(ants_b4h=ifelse(ever_antsP_b4h," ever", " never"),
         ants_afh=ifelse(ever_antsP_afh," ever"," never"),
         ants_ever=ifelse(ever_antsP," ever"," never")) %>%
  left_join(select(ant_n_days, -ants_everP, -ant_treatment, -females_removed)) %>%
  mutate(ants_gt2d=ifelse(antsP_gt2d," ants", " no ants"),
         ants_gt3d=ifelse(antsP_gt3d," ants", " no ants")) %>% 
  separate(location, into = c("DormPlant", "Leaf"), sep="_", remove=FALSE) %>%
  left_join(dplyr::select(moms_plant_data, DormPlant, last_visit_ends_P), by="DormPlant") %>%
  mutate(last_desP_rel2h = last_visit_ends_P-est_hatch,
         desP = last_desP_rel2h) 
```

### n_hatched/med_t5eggs ~ des+ants+vis+des:ants+des:vis+ants:vis
full - no coefs signif; remove three-way interaction
pairwise interaction - des**, des:ants*, vis*, ants:vis. USE THIS for main fig
no vis - des***, ants** (but missing vis* and ants:vis. from above)
```{r}
# vis - full model
des_hatch.vis.full.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment, vis=vis,
                              interaction="full")

des_hatch.vis.full.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=des, treatment=ant_treatment, vis=vis,
                                  model = des_hatch.vis.full.fits$mai.qb)

(des_hatch.vis.full.qb.p <- plot_ci_vis(ci_data=des_hatch.vis.full.qb.ci,
                                        tenure=des, treatment=ant_treatment, vis=vis,
                                        survNom=n_hatched, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.vis.full.fits$mai.qb) # no coefs signif; remove three-way interaction

# vis - pairwise interactions only
des_hatch.vis.pw.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment, vis=vis,
                              interaction="pw")

des_hatch.vis.pw.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=des, treatment=ant_treatment, vis=vis,
                                  model = des_hatch.vis.pw.fits$mai.qb)

(des_hatch.vis.pw.qb.p <- plot_ci_vis(ci_data=des_hatch.vis.pw.qb.ci, 
                                      tenure=des, treatment=ant_treatment, vis=vis,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.vis.pw.fits$mai.qb) # des**, des:ants*, vis*, ants:vis. **USE THIS**

# no vis - pairwise interactions only
des_hatch.pw.fits <- fit_surv(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment,
                              interaction="pw")

des_hatch.pw.qb.ci <- ci_for_plot(data_in=surv_reg_data, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=des, treatment=ant_treatment,
                                  model = des_hatch.pw.fits$mai.qb)

(des_hatch.pw.qb.p <- plot_ci(ci_data=des_hatch.pw.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.pw.fits$mai.qb) # des***, ants** (missing signif vis* and ants:vis.)

## Drop in deviance: none significant, go with second model (vis, pairwise)
anova(des_hatch.vis.full.fits$mai.qb, des_hatch.vis.pw.fits$mai.qb, test = "Chisq") # ns
anova(des_hatch.vis.pw.fits$mai.qb, des_hatch.pw.fits$mai.qb, test = "Chisq") # ns
```

### n_survived/n_hatched ~ des+ants+vis+des:ants+des:vis+ants:vis
full - no coefs signif; remove three-way interaction
pairwise interaction - des:ants*, vis:ants. USE THIS for main fig
no vis - des:ants** (but missing vis:ants. from above)
```{r}
# vis - full interactions
des_Nsurv.vis.full.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ant_treatment, vis=vis,
                              interaction="full")

des_Nsurv.vis.full.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ant_treatment, vis=vis,
                                  model = des_Nsurv.vis.full.fits$mai.qb)

(des_Nsurv.vis.full.qb.p <- plot_ci_vis(ci_data=des_Nsurv.vis.full.qb.ci, 
                              tenure=des, treatment=ant_treatment, vis=vis,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.vis.full.fits$mai.qb) # all coefs ns; drop three-way interaction

# vis - pairwise interactions only
des_Nsurv.vis.pw.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ant_treatment, vis=vis,
                              interaction="pw")

des_Nsurv.vis.pw.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ant_treatment, vis=vis,
                                  model = des_Nsurv.vis.pw.fits$mai.qb)

(des_Nsurv.vis.pw.qb.p <- plot_ci_vis(ci_data=des_Nsurv.vis.pw.qb.ci, 
                              tenure=des, treatment=ant_treatment, vis=vis,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.vis.pw.fits$mai.qb) # des:ants*, vis:ants.

# no vis - pairwise interactions only
des_Nsurv.pw.fits <- fit_surv(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ant_treatment,
                              interaction="pw")

des_Nsurv.pw.qb.ci <- ci_for_plot(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ant_treatment,
                                  model = des_Nsurv.pw.fits$mai.qb)

(des_Nsurv.pw.qb.p <- plot_ci(ci_data=des_Nsurv.pw.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.pw.fits$mai.qb) # des:ants**

## Drop in deviance: none significant, go with second model (vis, pairwise)
anova(des_Nsurv.vis.full.fits$mai.qb, des_Nsurv.vis.pw.fits$mai.qb, test = "Chisq") # ns
anova(des_Nsurv.vis.pw.fits$mai.qb, des_Nsurv.pw.fits$mai.qb, test = "Chisq") # ns
```

### n_survived/med_t5eggs ~ des+ants+vis+des:ants+des:vis+ants:vis
full - no coefs signif;  USE THIS for predicting fitness
pairwise interaction - no signif coefs but ants:vis <0.10
no vis - no signif coefs but ants and des:ants <0.10
```{r}
# vis - full interactions
des_Esurv.vis.full.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment, vis=vis,
                              interaction="full")

des_Esurv.vis.full.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=des, treatment=ant_treatment, vis=vis,
                                  model = des_Esurv.vis.full.fits$mai.qb)

(des_Esurv.vis.full.qb.p <- plot_ci_vis(ci_data=des_Esurv.vis.full.qb.ci, 
                              tenure=des, treatment=ant_treatment, vis=vis,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Esurv.vis.full.fits$mai.qb) # ** use this for predicting fitness

# vis - pairwise interactions only
des_Esurv.vis.pw.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment, vis=vis,
                              interaction="pw")

des_Esurv.vis.pw.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=des, treatment=ant_treatment, vis=vis,
                                  model = des_Esurv.vis.pw.fits$mai.qb)

(des_Esurv.vis.pw.qb.p <- plot_ci_vis(ci_data=des_Esurv.vis.pw.qb.ci, 
                              tenure=des, treatment=ant_treatment, vis=vis,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Esurv.vis.pw.fits$mai.qb) # no signif coefs but ants:vis <0.10

# no vis - pairwise interactions only
des_Esurv.pw.fits <- fit_surv(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment,
                              interaction="pw")

des_Esurv.pw.qb.ci <- ci_for_plot(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=des, treatment=ant_treatment,
                                  model = des_Esurv.pw.fits$mai.qb)

(des_Esurv.pw.qb.p <- plot_ci(ci_data=des_Esurv.pw.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Esurv.pw.fits$mai.qb) # no signif coefs but ants and des:ants <0.10

## Drop in deviance: none significant, go with second model (vis, pairwise)
anova(des_Esurv.vis.full.fits$mai.qb, des_Esurv.vis.pw.fits$mai.qb, test = "Chisq") # ns
anova(des_Esurv.vis.pw.fits$mai.qb, des_Esurv.pw.fits$mai.qb, test = "Chisq") # ns
```

### n_survived/med_t5eggs ~ med_t5eggs * ants * vis
I don't think this is as informative as n_survived/n_hatched, may mention but not show?
full - eggs*, vis* eggs:vis*, eggs:ants.
pairwise interaction - no signif coefs but vis and eggs:vis <0.10
no vis - no signif coefs
```{r}
# vis - full interactions
egg_Esurv.vis.full.fits <- fit_surv_vis(data_in=filter(surv_reg_data, females_removed), 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
                              interaction="full")

egg_Esurv.vis.full.qb.ci <- ci_for_plot_vis(data_in=filter(surv_reg_data, females_removed), 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
                                  model = egg_Esurv.vis.full.fits$mai.qb)

(egg_Esurv.vis.full.qb.p <- plot_ci_vis(ci_data=egg_Esurv.vis.full.qb.ci, 
                              tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Clutch size (number of eggs)") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(egg_Esurv.vis.full.fits$mai.qb) # eggs*, vis* eggs:vis*, eggs:ants.

# vis - pairwise interactions only
egg_Esurv.vis.pw.fits <- fit_surv_vis(data_in=filter(surv_reg_data, females_removed), 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
                              interaction="pw")

egg_Esurv.vis.pw.qb.ci <- ci_for_plot_vis(data_in=filter(surv_reg_data, females_removed), 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
                                  model = egg_Esurv.vis.pw.fits$mai.qb)

(egg_Esurv.vis.pw.qb.p <- plot_ci_vis(ci_data=egg_Esurv.vis.pw.qb.ci, 
                              tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Clutch size (number of eggs)") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(egg_Esurv.vis.pw.fits$mai.qb) # no signif coefs but vis and eggs:vis <0.10

# no vis - pairwise interactions only
egg_Esurv.pw.fits <- fit_surv(data_in=filter(surv_reg_data, females_removed), 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=med_t5eggs, treatment=ant_treatment,
                              interaction="pw")

egg_Esurv.pw.qb.ci <- ci_for_plot(data_in=filter(surv_reg_data, females_removed), 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=med_t5eggs, treatment=ant_treatment,
                                  model = egg_Esurv.pw.fits$mai.qb)

(egg_Esurv.pw.qb.p <- plot_ci(ci_data=egg_Esurv.pw.qb.ci, 
                                  tenure=med_t5eggs, treatment=ant_treatment,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Clutch size (number of eggs)") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(egg_Esurv.pw.fits$mai.qb) # no signif coefs

## Drop in deviance: none significant, go with second model (vis, pairwise)
anova(egg_Esurv.vis.full.fits$mai.qb, egg_Esurv.vis.pw.fits$mai.qb, test = "Chisq") # ns
anova(egg_Esurv.vis.pw.fits$mai.qb, egg_Esurv.pw.fits$mai.qb, test = "Chisq") # ns
```

### n_survived/n_hatched ~ med_t5eggs * ants * vis
full - all but ants * or **
pairwise interaction - vis*, eggs:vis*, eggs. (drop-in-deviance signif)
no vis - no signif coefs (drop-in-deviance <0.10)

Note that this is the only set of models where drop-in-deviance test (full->pairwise) was actually significant, so would it be best to keep the pairwise model? The fit on the intercept for visVisited, AntsRemoved looks really strange on the plot, which makes me think there are just too few data points for this if I'm just using the female removal data. If I include the control data it is hard to decouple egg/nymph guarding from larger clutches, so I think maybe I should skip on this (I wish I had more [both female removal and control] data!!!)
```{r}
# vis - full interactions
egg_Nsurv.vis.full.fits <- fit_surv_vis(data_in=filter(surv_reg_data, females_removed), 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
                              interaction="full")

egg_Nsurv.vis.full.qb.ci <- ci_for_plot_vis(data_in=filter(surv_reg_data, females_removed), 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
                                  model = egg_Nsurv.vis.full.fits$mai.qb)

(egg_Nsurv.vis.full.qb.p <- plot_ci_vis(ci_data=egg_Nsurv.vis.full.qb.ci, 
                              tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
                              survNom=n_survived, survDen=n_hatched) +
    xlab("Clutch size (number of eggs)") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(egg_Nsurv.vis.full.fits$mai.qb) # all but ants * or **

# vis - pairwise interactions only
egg_Nsurv.vis.pw.fits <- fit_surv_vis(data_in=filter(surv_reg_data, females_removed), 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
                              interaction="pw")

egg_Nsurv.vis.pw.qb.ci <- ci_for_plot_vis(data_in=filter(surv_reg_data, females_removed), 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
                                  model = egg_Nsurv.vis.pw.fits$mai.qb)

(egg_Nsurv.vis.pw.qb.p <- plot_ci_vis(ci_data=egg_Nsurv.vis.pw.qb.ci, 
                              tenure=med_t5eggs, treatment=ant_treatment, vis=vis,
                              survNom=n_survived, survDen=n_hatched) +
    xlab("Clutch size (number of eggs)") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(egg_Nsurv.vis.pw.fits$mai.qb) # vis*, eggs:vis*, eggs. (missing three-way interaction)

# no vis - pairwise interactions only
egg_Nsurv.pw.fits <- fit_surv(data_in=filter(surv_reg_data, females_removed), 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=med_t5eggs, treatment=ant_treatment,
                              interaction="pw")

egg_Nsurv.pw.qb.ci <- ci_for_plot(data_in=filter(surv_reg_data, females_removed), 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=med_t5eggs, treatment=ant_treatment,
                                  model = egg_Nsurv.pw.fits$mai.qb)

(egg_Nsurv.pw.qb.p <- plot_ci(ci_data=egg_Nsurv.pw.qb.ci,
                              tenure=med_t5eggs, treatment=ant_treatment,
                              survNom=n_survived, survDen=n_hatched) +
    xlab("Clutch size (number of eggs)") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(egg_Nsurv.pw.fits$mai.qb) # no signif coefs

## Drop in deviance: none significant, go with second model (vis, pairwise)
anova(egg_Nsurv.vis.full.fits$mai.qb, egg_Nsurv.vis.pw.fits$mai.qb, test = "Chisq") # *
anova(egg_Nsurv.vis.pw.fits$mai.qb, egg_Nsurv.pw.fits$mai.qb, test = "Chisq") # .
```

## Changing the ants parameter to reflect which clutches are actually visited
### n_hatched/med_t5eggs ~ des+ants+vis+des:ants+des:vis+ants:vis
*ants=ants_b4h*
full - no coefs signif; remove three-way interaction
pairwise interaction - des**, des:ants*, vis*, ants:vis. USE THIS for main fig
no vis - des***, ants** (but missing vis* and ants:vis. from above)
```{r}
# vis - full model
des_hatch.ants_b4h.vis.full.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_b4h, vis=vis,
                              interaction="full")

des_hatch.ants_b4h.vis.full.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_b4h, vis=vis,
                                  model = des_hatch.ants_b4h.vis.full.fits$mai.qb)

(des_hatch.ants_b4h.vis.full.qb.p <- plot_ci_vis(ci_data=des_hatch.ants_b4h.vis.full.qb.ci,
                                        tenure=des, treatment=ants_b4h, vis=vis,
                                        survNom=n_hatched, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.vis.full.fits$mai.qb) # no coefs signif; remove three-way interaction

# vis - pairwise interactions only
des_hatch.ants_b4h.vis.pw.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_b4h, vis=vis,
                              interaction="pw")

des_hatch.ants_b4h.vis.pw.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_b4h, vis=vis,
                                  model = des_hatch.ants_b4h.vis.pw.fits$mai.qb)

(des_hatch.ants_b4h.vis.pw.qb.p <- plot_ci_vis(ci_data=des_hatch.ants_b4h.vis.pw.qb.ci, 
                                      tenure=des, treatment=ants_b4h, vis=vis,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.vis.pw.fits$mai.qb) # des**, des:ants*, vis*, ants:vis. **USE THIS**

# no vis - pairwise interactions only
des_hatch.ants_b4h.pw.fits <- fit_surv(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_b4h,
                              interaction="pw")

des_hatch.ants_b4h.pw.qb.ci <- ci_for_plot(data_in=surv_reg_data, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_b4h,
                                  model = des_hatch.ants_b4h.pw.fits$mai.qb)

(des_hatch.ants_b4h.pw.qb.p <- plot_ci(ci_data=des_hatch.ants_b4h.pw.qb.ci, 
                                  tenure=des, treatment=ants_b4h,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.ants_b4h.pw.fits$mai.qb) # des***, ants** (missing signif vis* and ants:vis.)

## Drop in deviance: none significant, go with second model (vis, pairwise)
anova(des_hatch.ants_b4h.vis.full.fits$mai.qb, des_hatch.ants_b4h.vis.pw.fits$mai.qb, test = "Chisq") # ns
anova(des_hatch.ants_b4h.vis.pw.fits$mai.qb, des_hatch.ants_b4h.pw.fits$mai.qb, test = "Chisq") # ns
```

### n_hatched/med_t5eggs ~ des+ants+vis+des:ants+des:vis+ants:vis
*ants=ants_ever*
full - no coefs signif; remove three-way interaction
pairwise interaction - des**, des:ants*, vis*, ants:vis. USE THIS for main fig
no vis - des***, ants** (but missing vis* and ants:vis. from above)
```{r}
# vis - full model
des_hatch.ants_ever.vis.full.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever, vis=vis,
                              interaction="full")

des_hatch.ants_ever.vis.full.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_ever, vis=vis,
                                  model = des_hatch.ants_ever.vis.full.fits$mai.qb)

(des_hatch.ants_ever.vis.full.qb.p <- plot_ci_vis(ci_data=des_hatch.ants_ever.vis.full.qb.ci,
                                        tenure=des, treatment=ants_ever, vis=vis,
                                        survNom=n_hatched, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.ants_ever.vis.full.fits$mai.qb) # no coefs signif; remove three-way interaction

# vis - pairwise interactions only
des_hatch.ants_ever.vis.pw.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever, vis=vis,
                              interaction="pw")

des_hatch.ants_ever.vis.pw.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_ever, vis=vis,
                                  model = des_hatch.ants_ever.vis.pw.fits$mai.qb)

(des_hatch.ants_ever.vis.pw.qb.p <- plot_ci_vis(ci_data=des_hatch.ants_ever.vis.pw.qb.ci, 
                                      tenure=des, treatment=ants_ever, vis=vis,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.ants_ever.vis.pw.fits$mai.qb) # des**, des:ants*, vis*, ants:vis. **USE THIS**

# no vis - pairwise interactions only
des_hatch.ants_ever.pw.fits <- fit_surv(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever,
                              interaction="pw")

des_hatch.ants_ever.pw.qb.ci <- ci_for_plot(data_in=surv_reg_data, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_ever,
                                  model = des_hatch.ants_ever.pw.fits$mai.qb)

(des_hatch.ants_ever.pw.qb.p <- plot_ci(ci_data=des_hatch.ants_ever.pw.qb.ci, 
                                  tenure=des, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.ants_ever.pw.fits$mai.qb) # des***, ants** (missing signif vis* and ants:vis.)

## Drop in deviance: none significant, go with second model (vis, pairwise)
anova(des_hatch.ants_ever.vis.full.fits$mai.qb, des_hatch.ants_ever.vis.pw.fits$mai.qb, test = "Chisq") # ns
anova(des_hatch.ants_ever.vis.pw.fits$mai.qb, des_hatch.ants_ever.pw.fits$mai.qb, test = "Chisq") # ns
```

### n_survived/n_hatched ~ des+ants+vis+des:ants+des:vis+ants:vis
*ants=ants_b4h*
full - no coefs signif; remove three-way interaction
pairwise interaction - des:ants*, vis:ants. USE THIS for main fig
no vis - des:ants** (but missing vis:ants. from above)
```{r}
# vis - full interactions
des_Nsurv.ants_b4h.vis.full.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_b4h, vis=vis,
                              interaction="full")

des_Nsurv.ants_b4h.vis.full.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ants_b4h, vis=vis,
                                  model = des_Nsurv.ants_b4h.vis.full.fits$mai.qb)

(des_Nsurv.ants_b4h.full.qb.p <- plot_ci_vis(ci_data=des_Nsurv.ants_b4h.vis.full.qb.ci, 
                              tenure=des, treatment=ants_b4h, vis=vis,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_b4h.vis.full.fits$mai.qb) # all coefs ns; drop three-way interaction

# vis - pairwise interactions only
des_Nsurv.ants_b4h.vis.pw.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_b4h, vis=vis,
                              interaction="pw")

des_Nsurv.ants_b4h.vis.pw.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ants_b4h, vis=vis,
                                  model = des_Nsurv.ants_b4h.vis.pw.fits$mai.qb)

(des_Nsurv.ants_b4h.pw.qb.p <- plot_ci_vis(ci_data=des_Nsurv.ants_b4h.vis.pw.qb.ci, 
                              tenure=des, treatment=ants_b4h, vis=vis,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_b4h.vis.pw.fits$mai.qb) # des:ants*, vis:ants.

# no vis - pairwise interactions only
des_Nsurv.ants_b4h.pw.fits <- fit_surv(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_b4h,
                              interaction="pw")

des_Nsurv.ants_b4h.pw.qb.ci <- ci_for_plot(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ants_b4h,
                                  model = des_Nsurv.ants_b4h.pw.fits$mai.qb)

(des_Nsurv.ants_b4h.pw.qb.p <- plot_ci(ci_data=des_Nsurv.ants_b4h.pw.qb.ci, 
                                  tenure=des, treatment=ants_b4h,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_b4h.pw.fits$mai.qb) # des:ants**

## Drop in deviance: none significant, go with second model (vis, pairwise)
anova(des_Nsurv.ants_b4h.vis.full.fits$mai.qb, des_Nsurv.ants_b4h.vis.pw.fits$mai.qb, test = "Chisq") # ns
anova(des_Nsurv.ants_b4h.vis.pw.fits$mai.qb, des_Nsurv.ants_b4h.pw.fits$mai.qb, test = "Chisq") # ns
```

### n_survived/n_hatched ~ des+ants+vis+des:ants+des:vis+ants:vis
*ants=ants_afh*
full - no coefs signif; remove three-way interaction
pairwise interaction - des:ants*, vis:ants. USE THIS for main fig
no vis - des:ants** (but missing vis:ants. from above)
```{r}
# vis - full interactions
des_Nsurv.ants_afh.vis.full.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_afh, vis=vis,
                              interaction="full")

des_Nsurv.ants_afh.vis.full.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ants_afh, vis=vis,
                                  model = des_Nsurv.ants_afh.vis.full.fits$mai.qb)

(des_Nsurv.ants_afh.full.qb.p <- plot_ci_vis(ci_data=des_Nsurv.ants_afh.vis.full.qb.ci, 
                              tenure=des, treatment=ants_afh, vis=vis,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_afh.vis.full.fits$mai.qb) # all coefs ns; drop three-way interaction

# vis - pairwise interactions only
des_Nsurv.ants_afh.vis.pw.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_afh, vis=vis,
                              interaction="pw")

des_Nsurv.ants_afh.vis.pw.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ants_afh, vis=vis,
                                  model = des_Nsurv.ants_afh.vis.pw.fits$mai.qb)

(des_Nsurv.ants_afh.pw.qb.p <- plot_ci_vis(ci_data=des_Nsurv.ants_afh.vis.pw.qb.ci, 
                              tenure=des, treatment=ants_afh, vis=vis,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_afh.vis.pw.fits$mai.qb) # des:ants*, vis:ants.

# no vis - pairwise interactions only
des_Nsurv.ants_afh.pw.fits <- fit_surv(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_afh,
                              interaction="pw")

des_Nsurv.ants_afh.pw.qb.ci <- ci_for_plot(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ants_afh,
                                  model = des_Nsurv.ants_afh.pw.fits$mai.qb)

(des_Nsurv.ants_afh.pw.qb.p <- plot_ci(ci_data=des_Nsurv.ants_afh.pw.qb.ci, 
                                  tenure=des, treatment=ants_afh,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_afh.pw.fits$mai.qb) # des:ants**

## Drop in deviance: none significant, go with second model (vis, pairwise)
anova(des_Nsurv.ants_afh.vis.full.fits$mai.qb, des_Nsurv.ants_afh.vis.pw.fits$mai.qb, test = "Chisq") # ns
anova(des_Nsurv.ants_afh.vis.pw.fits$mai.qb, des_Nsurv.ants_afh.pw.fits$mai.qb, test = "Chisq") # ns
```

### n_survived/n_hatched ~ des+ants+vis+des:ants+des:vis+ants:vis
*ants=ants_ever*
full - no coefs signif; remove three-way interaction
pairwise interaction - des:ants*, vis:ants. USE THIS for main fig
no vis - des:ants** (but missing vis:ants. from above)
```{r}
# vis - full interactions
des_Nsurv.ants_ever.vis.full.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_ever, vis=vis,
                              interaction="full")

des_Nsurv.ants_ever.vis.full.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ants_ever, vis=vis,
                                  model = des_Nsurv.ants_ever.vis.full.fits$mai.qb)

(des_Nsurv.ants_ever.vis.full.qb.p <- plot_ci_vis(ci_data=des_Nsurv.ants_ever.vis.full.qb.ci, 
                              tenure=des, treatment=ants_ever, vis=vis,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_ever.vis.full.fits$mai.qb) # all coefs ns; drop three-way interaction

# vis - pairwise interactions only
des_Nsurv.ants_ever.vis.pw.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_ever, vis=vis,
                              interaction="pw")

des_Nsurv.ants_ever.vis.pw.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ants_ever, vis=vis,
                                  model = des_Nsurv.ants_ever.vis.pw.fits$mai.qb)

(des_Nsurv.ants_ever.vis.pw.qb.p <- plot_ci_vis(ci_data=des_Nsurv.ants_ever.vis.pw.qb.ci, 
                              tenure=des, treatment=ants_ever, vis=vis,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_ever.vis.pw.fits$mai.qb) # des:ants*, vis:ants.

# no vis - pairwise interactions only
des_Nsurv.ants_ever.pw.fits <- fit_surv(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_ever,
                              interaction="pw")

des_Nsurv.ants_ever.pw.qb.ci <- ci_for_plot(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ants_ever,
                                  model = des_Nsurv.ants_ever.pw.fits$mai.qb)

(des_Nsurv.ants_ever.pw.qb.p <- plot_ci(ci_data=des_Nsurv.ants_ever.pw.qb.ci, 
                                  tenure=des, treatment=ants_ever,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_ever.pw.fits$mai.qb) # des:ants**

## Drop in deviance: none significant, go with second model (vis, pairwise)
anova(des_Nsurv.ants_ever.vis.full.fits$mai.qb, des_Nsurv.ants_ever.vis.pw.fits$mai.qb, test = "Chisq") # ns
anova(des_Nsurv.ants_ever.vis.pw.fits$mai.qb, des_Nsurv.ants_ever.pw.fits$mai.qb, test = "Chisq") # ns
```

### n_survived/med_t5eggs ~ des+ants+vis+des:ants+des:vis+ants:vis
*ants=ants_ever*
full - no coefs signif;  USE THIS for predicting fitness
pairwise interaction - no signif coefs but ants:vis <0.10
no vis - no signif coefs but ants and des:ants <0.10
```{r}
# vis - full interactions
des_Esurv.ants_ever.vis.full.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever, vis=vis,
                              interaction="full")

des_Esurv.ants_ever.vis.full.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_ever, vis=vis,
                                  model = des_Esurv.ants_ever.vis.full.fits$mai.qb)

(des_Esurv.ants_ever.vis.full.qb.p <- plot_ci_vis(ci_data=des_Esurv.ants_ever.vis.full.qb.ci, 
                              tenure=des, treatment=ants_ever, vis=vis,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Esurv.ants_ever.vis.full.fits$mai.qb) # ** use this for predicting fitness

# vis - pairwise interactions only
des_Esurv.ants_ever.vis.pw.fits <- fit_surv_vis(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever, vis=vis,
                              interaction="pw")

des_Esurv.ants_ever.vis.pw.qb.ci <- ci_for_plot_vis(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_ever, vis=vis,
                                  model = des_Esurv.ants_ever.vis.pw.fits$mai.qb)

(des_Esurv.ants_ever.vis.pw.qb.p <- plot_ci_vis(ci_data=des_Esurv.ants_ever.vis.pw.qb.ci, 
                              tenure=des, treatment=ants_ever, vis=vis,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Esurv.ants_ever.vis.pw.fits$mai.qb) # no signif coefs but ants_ever:vis <0.10

# no vis - pairwise interactions only
des_Esurv.ants_ever.pw.fits <- fit_surv(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever,
                              interaction="pw")

des_Esurv.ants_ever.pw.qb.ci <- ci_for_plot(data_in=surv_reg_data, 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_ever,
                                  model = des_Esurv.ants_ever.pw.fits$mai.qb)

(des_Esurv.ants_ever.pw.qb.p <- plot_ci(ci_data=des_Esurv.ants_ever.pw.qb.ci, 
                                  tenure=des, treatment=ants_ever,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Esurv.ants_ever.pw.fits$mai.qb) # no signif coefs but ants_ever and des:ants_ever <0.10

## Drop in deviance: none significant, go with second model (vis, pairwise)
anova(des_Esurv.ants_ever.vis.full.fits$mai.qb, des_Esurv.ants_ever.vis.pw.fits$mai.qb, test = "Chisq") # ns
anova(des_Esurv.ants_ever.vis.pw.fits$mai.qb, des_Esurv.ants_ever.pw.fits$mai.qb, test = "Chisq") # ns
```

### n_survived/med_t5eggs ~ med_t5eggs * ants * vis
*ants=ants_ever*
This is just impossible. There's too little data for ants never. Plus clutch size is confounded by guarding duration, and ants ever is also confounded by guarding duration.
*Is that a problem for other comparison?*

### n_survived/n_hatched ~ med_t5eggs * ants * vis
*ants=ants_ever*
Same problem with too few data as for n_hatched/med_t5eggs

#### Does removing late season clutches that likely didn't reach max n_N5 change the results?
```{r}
cutoff_date<-as_date("2019-06-10")
surv_reg_data_filt <- filter(surv_reg_data, initiation_date<=cutoff_date)

# hatching
des_hatch.ants_ever.pw.fits.filt <- fit_surv(data_in=surv_reg_data_filt, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever,
                              interaction="pw")

des_hatch.ants_ever.pw.qb.ci.filt <- ci_for_plot(data_in=surv_reg_data_filt, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_ever,
                                  model = des_hatch.ants_ever.pw.fits.filt$mai.qb)

(des_hatch.ants_ever.pw.qb.p.filt <- plot_ci(ci_data=des_hatch.ants_ever.pw.qb.ci.filt, 
                                  tenure=des, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.ants_ever.pw.fits.filt$mai.qb)

# Nsurv
des_Nsurv.ants_ever.pw.fits.filt <- fit_surv(data_in=surv_reg_data_filt, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_ever,
                              interaction="pw")

des_Nsurv.ants_ever.pw.qb.ci.filt <- ci_for_plot(data_in=surv_reg_data_filt, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ants_ever,
                                  model = des_Nsurv.ants_ever.pw.fits.filt$mai.qb)

(des_Nsurv.ants_ever.pw.qb.p.filt <- plot_ci(ci_data=des_Nsurv.ants_ever.pw.qb.ci.filt, 
                                  tenure=des, treatment=ants_ever,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_ever.pw.fits.filt$mai.qb) # des:ants**

# Esurv
des_Esurv.ants_ever.pw.fits.filt <- fit_surv(data_in=surv_reg_data_filt, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever,
                              interaction="pw")

des_Esurv.ants_ever.pw.qb.ci.filt <- ci_for_plot(data_in=surv_reg_data_filt, 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_ever,
                                  model = des_Esurv.ants_ever.pw.fits.filt$mai.qb)

(des_Esurv.ants_ever.pw.qb.p.filt <- plot_ci(ci_data=des_Esurv.ants_ever.pw.qb.ci.filt, 
                                  tenure=des, treatment=ants_ever,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Esurv.ants_ever.pw.fits.filt$mai.qb)

egg::ggarrange(des_hatch.ants_ever.pw.qb.p.filt+
                 theme(legend.position="none"),
               des_Nsurv.ants_ever.pw.qb.p.filt+
                 theme(legend.position="none"),
               des_Esurv.ants_ever.pw.qb.p.filt+
                 theme(legend.position="none")+ylim(0,1),
               labels=c("A","B","C"),
               nrow=3)
```

#### Does focusing only on the clutches where females were not removed change anything?
```{r}
surv_reg_data_filtFemRem <- filter(surv_reg_data, !females_removed)

# hatching
des_hatch.ants_ever.pw.fits.filtFemRem <- fit_surv(data_in=surv_reg_data_filtFemRem, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever,
                              interaction="pw")

des_hatch.ants_ever.pw.qb.ci.filtFemRem <- ci_for_plot(data_in=surv_reg_data_filtFemRem, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_ever,
                                  model = des_hatch.ants_ever.pw.fits.filtFemRem$mai.qb)

(des_hatch.ants_ever.pw.qb.p.filtFemRem <- plot_ci(ci_data=des_hatch.ants_ever.pw.qb.ci.filtFemRem, 
                                  tenure=des, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.ants_ever.pw.fits.filtFemRem$mai.qb)

# Nsurv
des_Nsurv.ants_ever.pw.fits.filtFemRem <- fit_surv(data_in=surv_reg_data_filtFemRem, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_ever,
                              interaction="pw")

des_Nsurv.ants_ever.pw.qb.ci.filtFemRem <- ci_for_plot(data_in=surv_reg_data_filtFemRem, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=des, treatment=ants_ever,
                                  model = des_Nsurv.ants_ever.pw.fits.filtFemRem$mai.qb)

(des_Nsurv.ants_ever.pw.qb.p.filtFemRem <- plot_ci(ci_data=des_Nsurv.ants_ever.pw.qb.ci.filtFemRem, 
                                  tenure=des, treatment=ants_ever,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_ever.pw.fits.filtFemRem$mai.qb) # des:ants**

# Esurv
des_Esurv.ants_ever.pw.fits.filtFemRem <- fit_surv(data_in=surv_reg_data_filtFemRem, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever,
                              interaction="pw")

des_Esurv.ants_ever.pw.qb.ci.filtFemRem <- ci_for_plot(data_in=surv_reg_data_filtFemRem, 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=des, treatment=ants_ever,
                                  model = des_Esurv.ants_ever.pw.fits.filtFemRem$mai.qb)

(des_Esurv.ants_ever.pw.qb.p.filtFemRem <- plot_ci(ci_data=des_Esurv.ants_ever.pw.qb.ci.filtFemRem, 
                                  tenure=des, treatment=ants_ever,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Esurv.ants_ever.pw.fits.filtFemRem$mai.qb)

egg::ggarrange(des_hatch.ants_ever.pw.qb.p.filtFemRem+
                 theme(legend.position="none"),
               des_Nsurv.ants_ever.pw.qb.p.filtFemRem+
                 theme(legend.position="none"),
               des_Esurv.ants_ever.pw.qb.p.filtFemRem+
                 theme(legend.position="none")+ylim(0,1),
               labels=c("A","B","C"),
               nrow=3)
```

```{r}
# Compare ants_treatment to ants_ever and unfilt to filt
(survivorship.ants_treatment.final.p <- 
    egg::ggarrange(des_hatch.pw.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.pw.qb.p+
                 theme(legend.position="none"),
               des_Esurv.pw.qb.p+
                 theme(legend.position="none")+ylim(0,1),
               labels=c("A","B","C"),
               nrow=1))

(survivorship.ants_ever.final.p <- 
    egg::ggarrange(des_hatch.ants_ever.pw.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.ants_ever.pw.qb.p+
                 theme(legend.position="none"),
               des_Esurv.ants_ever.pw.qb.p+
                 theme(legend.position="none")+ylim(0,1),
               labels=c("A","B","C"),
               nrow=1))

# ggsave("CHAPTER/survivorship.ants_treatment.final.png",
#        survivorship.ants_treatment.final.p,
#        device="png", width = 300, height = 110, units = "mm", dpi = "print")

# ggsave("CHAPTER/survivorship.ants_ever.final.png",
#        survivorship.ants_ever.final.p,
#        device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

### Compare qaicc values from various models in a table
Method taken from: https://cran.r-project.org/web/packages/bbmle/vignettes/quasi.pdf

Fit the model twice, once with a regular likelihood model (family=binomial,
poisson, etc.) and once with the quasi- variant — extract the log-
likelihood from the former and the dispersion parameter from the latter.
```{r}
# Calculate qAICc
library(bbmle)

get_qaicc <- function(model.fits) {
  model.qaicc <- qAICc(model.fits$mai.b,
        dispersion=summary(model.fits$mai.qb)$dispersion,
        nobs = nrow(model.fits$mai.qb$data))
  return(model.qaicc)
}

des_hatch.vis.full.qaicc <- get_qaicc(des_hatch.vis.full.fits)
des_hatch.vis.pw.qaicc <- get_qaicc(des_hatch.vis.pw.fits)
des_hatch.pw.qaicc <- get_qaicc(des_hatch.pw.fits)
des_hatch.ants_ever.vis.full.qaicc <- get_qaicc(des_hatch.ants_ever.vis.full.fits)
des_hatch.ants_ever.vis.pw.qaicc <- get_qaicc(des_hatch.ants_ever.vis.pw.fits)
des_hatch.ants_ever.pw.qaicc <- get_qaicc(des_hatch.ants_ever.pw.fits)

des_hatch.qaicc <- data.frame(model = c("vis.full", "vis.pw", "pw",
                     "ants_ever.vis.full", "ants_ever.vis.pw", "ants_ever.pw"), 
       qaicc = c(des_hatch.vis.full.qaicc,
                 des_hatch.vis.pw.qaicc,
                 des_hatch.pw.qaicc,
                 des_hatch.ants_ever.vis.full.qaicc, 
                 des_hatch.ants_ever.vis.pw.qaicc, 
                 des_hatch.ants_ever.pw.qaicc))

des_Nsurv.vis.full.qaicc <- get_qaicc(des_Nsurv.vis.full.fits)
des_Nsurv.vis.pw.qaicc <- get_qaicc(des_Nsurv.vis.pw.fits)
des_Nsurv.pw.qaicc <- get_qaicc(des_Nsurv.pw.fits)
des_Nsurv.ants_ever.vis.full.qaicc <- get_qaicc(des_Nsurv.ants_ever.vis.full.fits)
des_Nsurv.ants_ever.vis.pw.qaicc <- get_qaicc(des_Nsurv.ants_ever.vis.pw.fits)
des_Nsurv.ants_ever.pw.qaicc <- get_qaicc(des_Nsurv.ants_ever.pw.fits)

des_Nsurv.qaicc <- data.frame(model = c("vis.full", "vis.pw", "pw",
                     "ants_ever.vis.full", "ants_ever.vis.pw", "ants_ever.pw"), 
       qaicc = c(des_Nsurv.vis.full.qaicc,
                 des_Nsurv.vis.pw.qaicc,
                 des_Nsurv.pw.qaicc,
                 des_Nsurv.ants_ever.vis.full.qaicc, 
                 des_Nsurv.ants_ever.vis.pw.qaicc, 
                 des_Nsurv.ants_ever.pw.qaicc))

des_Esurv.vis.full.qaicc <- get_qaicc(des_Esurv.vis.full.fits)
des_Esurv.vis.pw.qaicc <- get_qaicc(des_Esurv.vis.pw.fits)
des_Esurv.pw.qaicc <- get_qaicc(des_Esurv.pw.fits)
des_Esurv.ants_ever.vis.full.qaicc <- get_qaicc(des_Esurv.ants_ever.vis.full.fits)
des_Esurv.ants_ever.vis.pw.qaicc <- get_qaicc(des_Esurv.ants_ever.vis.pw.fits)
des_Esurv.ants_ever.pw.qaicc <- get_qaicc(des_Esurv.ants_ever.pw.fits)

des_Esurv.qaicc <- data.frame(model = c("vis.full", "vis.pw", "pw",
                     "ants_ever.vis.full", "ants_ever.vis.pw", "ants_ever.pw"), 
       qaicc = c(des_Esurv.vis.full.qaicc,
                 des_Esurv.vis.pw.qaicc,
                 des_Esurv.pw.qaicc,
                 des_Esurv.ants_ever.vis.full.qaicc, 
                 des_Esurv.ants_ever.vis.pw.qaicc, 
                 des_Esurv.ants_ever.pw.qaicc))
```

### Combining plots for paper
*ants=ants_ever* for all
n_hatched/med_t5eggs ~ des+ants+vis+des:ants+des:vis+ants:vis

```{r}
# n_hatched/med_t5eggs ~ des+ants+vis+des:ants+des:vis+ants:vis
des_hatch.qaicc
des_hatch.ants_ever.vis.full.qb.p # qaicc=254.8996
summary(des_hatch.ants_ever.vis.full.fits$mai.qb)
des_hatch.ants_ever.vis.pw.qb.p # qaicc=253.4002
summary(des_hatch.ants_ever.vis.pw.fits$mai.qb)
des_hatch.ants_ever.pw.qb.p # qaicc=251.2537 **>2
summary(des_hatch.ants_ever.pw.fits$mai.qb)

# n_survived/n_hatched ~ des+ants+vis+des:ants+des:vis+ants:vis
des_Nsurv.qaicc
des_Nsurv.ants_ever.vis.full.qb.p # qaicc=223.9026
summary(des_Nsurv.ants_ever.vis.full.fits$mai.qb)
des_Nsurv.ants_ever.vis.pw.qb.p # qaicc=223.0314
summary(des_Nsurv.ants_ever.vis.pw.fits$mai.qb)
des_Nsurv.ants_ever.pw.qb.p # qaicc=220.4654 **>2
summary(des_Nsurv.ants_ever.pw.fits$mai.qb)

# n_survived/med_t5eggs ~ des+ants+vis+des:ants+des:vis+ants:vis
summary(des_Esurv.ants_ever.vis.full.fits$mai.qb)
des_Esurv.ants_ever.vis.full.qb.p # qaicc=201.6597
summary(des_Esurv.ants_ever.vis.pw.fits$mai.qb)
des_Esurv.ants_ever.vis.pw.qb.p # qaicc=200.9795
summary(des_Esurv.ants_ever.pw.fits$mai.qb)
des_Esurv.ants_ever.pw.qb.p # qaicc=197.3052 **>2

# So the three best qaicc models to show in tables/plots of main all don't have vis:
des_hatch.ants_ever.pw.qb.p
summary(des_hatch.ants_ever.pw.fits$mai.qb)
des_Nsurv.ants_ever.pw.qb.p
summary(des_Nsurv.ants_ever.pw.fits$mai.qb)
des_Esurv.ants_ever.pw.qb.p
summary(des_Esurv.ants_ever.pw.fits$mai.qb)

(des_hatch.ants_ever.pw.qb.p <- plot_ci(ci_data=des_hatch.ants_ever.pw.qb.ci, 
                                  tenure=des, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

(des_Nsurv.ants_ever.pw.qb.p <- plot_ci(ci_data=des_Nsurv.ants_ever.pw.qb.ci, 
                                  tenure=des, treatment=ants_ever,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

(des_Esurv.ants_ever.pw.qb.p <- plot_ci(ci_data=des_Esurv.ants_ever.pw.qb.ci, 
                                  tenure=des, treatment=ants_ever,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

egg::ggarrange(des_hatch.ants_ever.pw.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.ants_ever.pw.qb.p+
                 theme(legend.position="none"),
               des_Esurv.ants_ever.pw.qb.p+ylim(0,1)+
                 theme(legend.position=c(0.8,0.9)),
               labels=c("A","B","C"),
               nrow=3)

# But should I show vis.pw in the supplement? Nothing interesting to see really. All the plots look the same.
egg::ggarrange(des_hatch.ants_ever.vis.pw.qb.p,
               des_Nsurv.ants_ever.vis.pw.qb.p,
               des_Esurv.ants_ever.vis.pw.qb.p+ylim(0,1),
               labels=c("A","B","C"),
               nrow=3)
```

### number of clutches on plant
The model performs well for hatching but overfits/underestimates survivorship. Would adding number of clutches help?
```{r}
clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_hatched, n_survived,
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`,
         females_removed, n_clutches_on_plant) %>%
  mutate(n_survived=ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
                           n_hatched, n_survived), # force n_survived/n_hatched=1
         ants=ifelse(ants, "Removed", "Control"),
         Nclutches=cut(n_clutches_on_plant, breaks=c(0,1,2,7), labels=c("1","2",">2"))) %>%
  count(Nclutches, ants, vis)

clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_hatched, n_survived,
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`,
         females_removed, n_clutches_on_plant) %>%
  mutate(n_survived=ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
                           n_hatched, n_survived), # force n_survived/n_hatched=1
         ants=ifelse(ants, "Removed", "Control"),
         Nclutches=cut(n_clutches_on_plant, breaks=c(0,1,2,7), labels=c("1","2",">2"))) %>%
  ggplot(data=.,aes(x=des, y=n_hatched, shape=ants, color=Nclutches)) +
    geom_point() +
    geom_smooth(method=lm, se=F) +
  facet_wrap(~vis)

clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_hatched, n_survived,
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`,
         females_removed, n_clutches_on_plant) %>%
  mutate(n_survived=ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
                           n_hatched, n_survived), # force n_survived/n_hatched=1
         ants=ifelse(ants, "Removed", "Control"),
         Nclutches=cut(n_clutches_on_plant, breaks=c(0,1,2,7), labels=c("1","2",">2"))) %>%
  ggplot(data=.,aes(x=des, y=n_survived, shape=ants, color=Nclutches)) +
    geom_point() +
    geom_smooth(method=lm, se=F) +
  facet_wrap(~vis)

clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_hatched, n_survived,
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`,
         females_removed, n_clutches_on_plant) %>%
  mutate(n_survived=ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
                           n_hatched, n_survived), # force n_survived/n_hatched=1
         ants=ifelse(ants, "Removed", "Control")) %>%
  count(n_clutches_on_plant)

```

Number of clutches per plants doesn't explain the high n_survived counts!
```{r}
clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_hatched, n_survived,
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`,
         females_removed, n_clutches_on_plant) %>%
  mutate(n_survived=ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
                           n_hatched, n_survived), # force n_survived/n_hatched=1
         ants=ifelse(ants, "Removed", "Control"),
         Nclutches=cut(n_clutches_on_plant, breaks=c(0,1,2,7), labels=c("1","2",">2"))) %>%
  ggplot(data=.,aes(x=des, y=n_survived/n_hatched, linetype=ants, color=Nclutches)) +
    geom_point() +
    geom_smooth(method=lm, se=F) +
  facet_wrap(~vis)

clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`),
         n_survived>0) %>%
  select(location, med_t5eggs, n_hatched, n_survived,
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`,
         females_removed, n_clutches_on_plant) %>%
  mutate(n_survived=ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
                           n_hatched, n_survived), # force n_survived/n_hatched=1
         ants=ifelse(ants, "Removed", "Control"),
         Nclutches=cut(n_clutches_on_plant, breaks=c(0,1,2,7), labels=c("1","2",">2"))) %>%
  ggplot(data=.,aes(x=des, y=n_survived/n_hatched, linetype=ants, color=Nclutches)) +
    geom_point() +
    geom_smooth(method=lm, se=F) +
  facet_wrap(~vis)
```

Dorms?
It does look like there is some variation in the 
```{r}
clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_hatched, n_survived,
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`,
         females_removed, n_clutches_on_plant) %>%
  mutate(n_survived=ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
                           n_hatched, n_survived), # force n_survived/n_hatched=1
         ants=ifelse(ants, "Removed", "Control"),
         Nclutches=cut(n_clutches_on_plant, breaks=c(0,1,2,7), labels=c("1","2",">2")),
         Dorm=substr(location,1,1)) %>%
  ggplot(data=.,aes(x=des, y=n_survived/n_hatched, color=Dorm, shape=ants, linetype=ants)) +
    geom_point() +
    geom_smooth(method=lm, se=F) +
  facet_wrap(~vis)

clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_hatched, n_survived,
         des=last_des_rel2h, ants=ants_removed, vis=`visited in 4 days`,
         females_removed, n_clutches_on_plant) %>%
  mutate(n_survived=ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
                           n_hatched, n_survived), # force n_survived/n_hatched=1
         ants=ifelse(ants, "Removed", "Control"),
         Nclutches=cut(n_clutches_on_plant, breaks=c(0,1,2,7), labels=c("1","2",">2")),
         Dorm=substr(location,1,1)) %>%
  ggplot(data=.,aes(x=des, y=n_hatched/med_t5eggs, color=Dorm, shape=ants, linetype=ants)) +
    geom_point() +
    geom_smooth(method=lm, se=F)+
  facet_wrap(~vis)
```

### A very quick exploration of plant-level nymph survivorship
Note that I shouldn't include clutches that were laid so late that nymphs (or adults) had not all hatched/survived, depending on the metric of interest.
```{r}
N_plant_max_data <- All_data_v6_clutch_status_stats_v2 %>%
  mutate(DormPlant = paste0(Dorm, Plant)) %>%
  group_by(Date, DormPlant) %>%
    filter(any(!is.na(initiation_date))) %>%
    distinct(Date, DormPlant, Eggs, N1, N2, N5, n_A, n_clutches_on_plant) %>%
    summarize(N1_P = sum(N1, na.rm=T),
              N2_P = sum(N2, na.rm=T),
              N5_P = sum(N5, na.rm=T),
              N_P = sum(N1, N2, N5, na.rm=T),
              N5toA_P = sum(N5, n_A, na.rm=T),
              A_P = sum(n_A, na.rm=T)) %>%
  ungroup() %>%
  group_by(DormPlant) %>%
    summarize(N1_P_max = max(N1_P),
              N2_P_max = max(N2_P),
              N5_P_max = max(N5_P),
              N_P_max = max(N_P),
              N5toA_P_max = max(N5toA_P),
              A_P_max = max(A_P)) %>%
  ungroup()

moms_plant_data <- visited_1st_4d_data %>%
  filter(!is.na(initiation_date)) %>%
  separate(location, "_", into=c("DormPlant","Leaf")) %>%
  group_by(DormPlant) %>%
  summarize(n_moms_alltime = n(),
            n_moms_leaf_H = sum(est_rel2h>=0, na.rm=T),
            any_moms_leaf_H = any(est_rel2h>=0, na.rm=T),
            last_visit_ends_P = max(visit_ends, na.rm=T),
            n_moms_P_H = sum((last_visit_ends_P-est_hatch)>=0, na.rm=T),
            any_moms_P_H = any((last_visit_ends_P-est_hatch)>=0, na.rm=T),
            n_moms_P_8afterH = sum((last_visit_ends_P-est_hatch+8)>=0, na.rm=T),
            any_moms_P_8afterH = sum((last_visit_ends_P-est_hatch+8)>=0, na.rm=T),
            n_clutches_on_plant = first(n_clutches_on_plant)) %>%
  ungroup()

ant_counts_DormPlant <- ant_counts %>%
  separate(location, "_", into=c("DormPlant","Leaf")) %>%
  group_by(DormPlant) %>%
    summarize(any_antsP = ifelse(any(ever_antsP, na.rm=T), "some ants", "never ants")) %>%
  ungroup %>%
  distinct(DormPlant, any_antsP)

top5eggs_DormPlant <- top5eggs_summary %>%
  separate(location, "_", into=c("DormPlant","Leaf")) %>%
  group_by(DormPlant) %>%
    summarize(sum_medt5eggsP = sum(med_t5eggs, na.rm=T)) %>%
  ungroup()

# when is the maximum number of nymphs reached?
maxN_plant_date_data <- All_data_v6_clutch_status_stats_v2 %>%
  mutate(DormPlant = paste0(Dorm, Plant)) %>%
  group_by(Date, DormPlant) %>%
    filter(any(!is.na(initiation_date))) %>%
    distinct(Date, DormPlant, Eggs, N1, N2, N5, n_A, n_clutches_on_plant) %>%
    summarize(N_plant = sum(N1, N2, N5, na.rm=T)) %>%
  ungroup() %>%
  group_by(DormPlant) %>% dplyr::slice_max(N_plant, with_ties=F) %>% ungroup() %>%
  select(DormPlant, maxN_plant_date = Date)

# when is the maximum number of adults reached?
maxN5toA_plant_date_data <- All_data_v6_clutch_status_stats_v2 %>%
  mutate(DormPlant = paste0(Dorm, Plant)) %>%
  group_by(Date, DormPlant) %>%
    filter(any(!is.na(initiation_date))) %>%
    distinct(Date, DormPlant, Eggs, N1, N2, N5, n_A, n_clutches_on_plant) %>%
    summarize(N5toA_plant = sum(n_A, N5, na.rm=T)) %>%
  ungroup() %>%
  group_by(DormPlant) %>% dplyr::slice_max(N5toA_plant, with_ties=F) %>% ungroup() %>%
  select(DormPlant, maxN5toA_plant_date = Date)

last_obs_date <- All_data_v6_clutch_status_stats_v2 %>%
  mutate(DormPlant = paste0(Dorm, Plant)) %>%
  group_by(DormPlant) %>% dplyr::slice_max(Date, with_ties=F) %>% ungroup() %>%
  select(DormPlant, last_obs_date = Date)

survival_plant_data <- N_plant_max_data %>%
  left_join(moms_plant_data) %>%
  left_join(ant_counts_DormPlant) %>%
  left_join(top5eggs_DormPlant) %>%
  left_join(maxN_plant_date_data) %>%
  left_join(maxN5toA_plant_date_data) %>%
  left_join(last_obs_date)

survival_plant_data %>%
  filter(maxN_plant_date>=(last_obs_date-4))

survival_plant_data %>%
  filter(maxN5toA_plant_date>=(last_obs_date-4))

survival_plant_data %>%
  filter(maxN5toA_plant_date==last_obs_date)

survival_plant_data %>%
  filter(!is.na(any_antsP)) %>% # why does these exist?
  #filter(!(maxN_plant_date==last_obs_date)) %>%
  ggplot(data=., aes(x=any_moms_P_H, y=N_P_max/sum_medt5eggsP, 
                     fill=any_antsP)) +
  geom_boxplot() +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  facet_wrap(~n_clutches_on_plant>1)

survival_plant_data %>%
  filter(!is.na(any_antsP)) %>% # why does these exist?
  #filter(!(maxN5toA_plant_date==last_obs_date)) %>%
  ggplot(data=., aes(x=any_moms_P_H, y=N5toA_P_max/N_P_max, 
                     fill=any_antsP)) +
  geom_boxplot() +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  facet_wrap(~n_clutches_on_plant>1)

survival_plant_data %>%
  filter(!is.na(any_antsP)) %>% # why does these exist?
  filter(!(maxN5toA_plant_date==last_obs_date)) %>%
  ggplot(data=., aes(x=any_moms_P_H, y=N5toA_P_max/N_P_max, 
                     fill=any_antsP)) +
  geom_boxplot() +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  facet_wrap(~n_clutches_on_plant>1)

survival_plant_data %>%
  filter(!(maxN5toA_plant_date>=(last_obs_date-8))) %>%
  ggplot(data=., aes(x=any_moms_P_H, y=N5toA_P_max/sum_medt5eggsP, 
                     fill=any_antsP)) +
  geom_boxplot() +
  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
  facet_wrap(~n_clutches_on_plant>1)

survival_plant_data %>%
  filter(!(maxN5toA_plant_date>=(last_obs_date-8))) %>%
  ggplot(data=., aes(x=any_moms_P_H, y=N5toA_P_max/N_P_max, 
                     fill=any_antsP)) +
  geom_boxplot()

# Next step: what is the expected interval from laying eggs to new adults, and from hatching to new adults?
# Here, I didn't add N5 plus A, but I did for previous iterations of the analysis.

# first nymphs/adults
N1_first_date <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
  filter(N1_NOr>0) %>% group_by(NOr_rev_loc) %>% dplyr::slice_head(n=1) %>% ungroup() %>%
  select(NOr_rev_loc, N1_first_date=Date)

N2_first_date <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
  filter(N2_NOr>0) %>% group_by(NOr_rev_loc) %>% dplyr::slice_head(n=1) %>% ungroup() %>%
  select(NOr_rev_loc, N2_first_date=Date)

N5_first_date <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
  filter(N5_NOr>0) %>% group_by(NOr_rev_loc) %>% dplyr::slice_head(n=1) %>% ungroup() %>%
  select(NOr_rev_loc, N5_first_date=Date)

A_first_date <- clutch_unambig_NOr_revised_ENAa_summary_v2 %>%
  filter(A_NOr>0) %>% group_by(NOr_rev_loc) %>% dplyr::slice_head(n=1) %>% ungroup() %>%
  select(NOr_rev_loc, A_first_date=Date)

clutch_first_dates_data <- clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2 %>%
  select(NOr_rev_loc, initiation_date, females_removed, ants_removed) %>%
  left_join(N1_first_date) %>%
  left_join(N2_first_date) %>%
  left_join(N5_first_date) %>%
  left_join(A_first_date) %>%
  mutate(E2N_int = N1_first_date-initiation_date,
         N2N5_int = N5_first_date-N1_first_date,
         E2N5_int = N5_first_date-initiation_date,
         E2A_int = A_first_date-initiation_date,
         N52A_int = A_first_date-N5_first_date,
         N12N2_int = N2_first_date-N1_first_date)

clutch_first_dates_data %>%
  ggplot(data=.) +
  geom_boxplot(aes(x="E2N", y=E2N_int)) +
  geom_jitter(aes(x="E2N", y=E2N_int)) +
  geom_boxplot(aes(x="N2N5", y=N2N5_int)) + 
  geom_jitter(aes(x="N2N5", y=N2N5_int)) +
  geom_boxplot(aes(x="E2N5", y=E2N5_int)) +
  geom_jitter(aes(x="E2N5", y=E2N5_int)) +
  geom_boxplot(aes(x="E2A", y=E2A_int)) +
  geom_jitter(aes(x="E2A", y=E2A_int)) +
  geom_boxplot(aes(x="N52A", y=N52A_int)) +
  geom_jitter(aes(x="N52A", y=N52A_int)) +
  geom_boxplot(aes(x="N12N2", y=N12N2_int)) +
  geom_jitter(aes(x="N12N2", y=N12N2_int))

# most clutches have begun to yield N5 by 60 days after initiation (median ~ 50 days)

surv_reg_data_plant <- clutch_survivorship_data %>% 
  filter(!is.na(`visited in 4 days`)) %>%
  select(location, med_t5eggs, n_hatched, n_survived,
         des=last_des_rel2h, ants_removed, vis=`visited in 4 days`,
         females_removed) %>%
  mutate(n_survived = ifelse(n_survived/n_hatched > 1,# if n_survived/n_hatched>1
                             n_hatched, n_survived), # force n_survived/n_hatched=1
         ant_treatment=ifelse(ants_removed, "Removed", "Control")) %>%
  left_join(select(ant_counts, location, 
                   ever_antsP_b4h, ever_antsP_afh, ever_antsP)) %>%
  mutate(ants_b4h=ifelse(ever_antsP_b4h," ever", " never"),
         ants_afh=ifelse(ever_antsP_afh," ever"," never"),
         ants_ever=ifelse(ever_antsP," ever"," never"))
```

Does latest desert date on *plant* explain the high hatching success for early latest desertion date on clutch?
```{r}
surv_reg_data_LastDesPlant <- surv_reg_data #%>% 
  #separate(location, into = c("DormPlant", "Leaf"), sep="_", remove=FALSE) %>%
  #left_join(dplyr::select(moms_plant_data, DormPlant, last_visit_ends_P), by="DormPlant") %>%
  #mutate(last_desP_rel2h = last_visit_ends_P-est_hatch)

ggplot(data = surv_reg_data_LastDesPlant, aes(x=des, y = last_desP_rel2h)) +
  geom_count(aes(color=vis), alpha=0.50) +
  geom_abline(slope=1,intercept=0, color="red")

ggplot(data = filter(surv_reg_data_LastDesPlant, !females_removed), aes(x=des, y = last_desP_rel2h)) +
  geom_count(aes(color=vis), alpha=0.50) +
  geom_abline(slope=1,intercept=0, color="red")

# hatching
des_hatch.ants_ever.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ants_ever,
                              interaction="pw")

des_hatch.ants_ever.pw.qb.ci.LastDesPlant <- ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=last_desP_rel2h, treatment=ants_ever,
                                  model = des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb)

(des_hatch.ants_ever.pw.qb.p.LastDesPlant <- plot_ci(ci_data=des_hatch.ants_ever.pw.qb.ci.LastDesPlant, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion from the plant relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb)

# Nsurv
des_Nsurv.ants_ever.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=last_desP_rel2h, treatment=ants_ever,
                              interaction="pw")

des_Nsurv.ants_ever.pw.qb.ci.LastDesPlant <- ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=last_desP_rel2h, treatment=ants_ever,
                                  model = des_Nsurv.ants_ever.pw.fits.LastDesPlant$mai.qb)

(des_Nsurv.ants_ever.pw.qb.p.LastDesPlant <- plot_ci(ci_data=des_Nsurv.ants_ever.pw.qb.ci.LastDesPlant, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion from the plant relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.ants_ever.pw.fits.LastDesPlant$mai.qb) # des:ants**

# Esurv
des_Esurv.ants_ever.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ants_ever,
                              interaction="pw")

des_Esurv.ants_ever.pw.qb.ci.LastDesPlant <- ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=last_desP_rel2h, treatment=ants_ever,
                                  model = des_Esurv.ants_ever.pw.fits.LastDesPlant$mai.qb)

(des_Esurv.ants_ever.pw.qb.p.LastDesPlant <- plot_ci(ci_data=des_Esurv.ants_ever.pw.qb.ci.LastDesPlant, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion from the plant relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Esurv.ants_ever.pw.fits.LastDesPlant$mai.qb)

egg::ggarrange(des_hatch.ants_ever.pw.qb.p.LastDesPlant+
                 theme(legend.position="none"),
               des_Nsurv.ants_ever.pw.qb.p.LastDesPlant+
                 theme(legend.position="none"),
               des_Esurv.ants_ever.pw.qb.p.LastDesPlant+
                 theme(legend.position="none")+ylim(0,1),
               labels=c("A","B","C"),
               nrow=3)

des_hatch.ants_ever.LastDesPlant.tbl <- 
  tbl_regression(des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()
des_Nsurv.ants_ever.LastDesPlant.tbl <- 
  tbl_regression(des_Nsurv.ants_ever.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()
des_Esurv.ants_ever.LastDesPlant.tbl <- 
  tbl_regression(des_Esurv.ants_ever.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()

(ants_ever.LastDesPlant.tbl_merge <- 
  tbl_merge(
    tbls = list(des_hatch.ants_ever.LastDesPlant.tbl, 
                des_Nsurv.ants_ever.LastDesPlant.tbl, 
                des_Esurv.ants_ever.LastDesPlant.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

```

ants treatment
```{r}
# hatching
des_hatch.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ant_treatment,
                              interaction="pw")

des_hatch.pw.qb.ci.LastDesPlant <- ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
                                  survNom=n_hatched, survDen=med_t5eggs,
                                  tenure=last_desP_rel2h, treatment=ant_treatment,
                                  model = des_hatch.pw.fits.LastDesPlant$mai.qb)

(des_hatch.pw.qb.p.LastDesPlant <- plot_ci(ci_data=des_hatch.pw.qb.ci.LastDesPlant, 
                                  tenure=last_desP_rel2h, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion from the plant relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_hatch.pw.fits.LastDesPlant$mai.qb)

# Nsurv
des_Nsurv.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=last_desP_rel2h, treatment=ant_treatment,
                              interaction="pw")

des_Nsurv.pw.qb.ci.LastDesPlant <- ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
                                  survNom=n_survived, survDen=n_hatched,
                                  tenure=last_desP_rel2h, treatment=ant_treatment,
                                  model = des_Nsurv.pw.fits.LastDesPlant$mai.qb)

(des_Nsurv.pw.qb.p.LastDesPlant <- plot_ci(ci_data=des_Nsurv.pw.qb.ci.LastDesPlant, 
                                  tenure=last_desP_rel2h, treatment=ant_treatment,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion from the plant relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Nsurv.pw.fits.LastDesPlant$mai.qb) # des:ants**

# Esurv
des_Esurv.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ant_treatment,
                              interaction="pw")

des_Esurv.pw.qb.ci.LastDesPlant <- ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
                                  survNom=n_survived, survDen=med_t5eggs,
                                  tenure=last_desP_rel2h, treatment=ant_treatment,
                                  model = des_Esurv.pw.fits.LastDesPlant$mai.qb)

(des_Esurv.pw.qb.p.LastDesPlant <- plot_ci(ci_data=des_Esurv.pw.qb.ci.LastDesPlant, 
                                  tenure=last_desP_rel2h, treatment=ant_treatment,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion from the plant relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

summary(des_Esurv.pw.fits.LastDesPlant$mai.qb)

egg::ggarrange(des_hatch.pw.qb.p.LastDesPlant+
                 theme(legend.position="none"),
               des_Nsurv.pw.qb.p.LastDesPlant+
                 theme(legend.position="none"),
               des_Esurv.pw.qb.p.LastDesPlant+
                 theme(legend.position="none")+ylim(0,1),
               labels=c("A","B","C"),
               nrow=3)

des_hatch.LastDesPlant.tbl <- 
  tbl_regression(des_hatch.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ant_treatment ~ "Ants")) %>% bold_p()
des_Nsurv.LastDesPlant.tbl <- 
  tbl_regression(des_Nsurv.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ant_treatment ~ "Ants")) %>% bold_p()
des_Esurv.LastDesPlant.tbl <- 
  tbl_regression(des_Esurv.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ant_treatment ~ "Ants")) %>% bold_p()

(treatment.LastDesPlant.tbl_merge <- 
  tbl_merge(
    tbls = list(des_hatch.LastDesPlant.tbl, 
                des_Nsurv.LastDesPlant.tbl, 
                des_Esurv.LastDesPlant.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

# qaicc
des_hatch.qaicc
get_qaicc(des_hatch.pw.fits.LastDesPlant)
des_Nsurv.qaicc
get_qaicc(des_Nsurv.pw.fits.LastDesPlant)
des_Esurv.qaicc
get_qaicc(des_Esurv.pw.fits.LastDesPlant)
```

# Final stats, plots for paper
main = ants_removed vs. control
supplement = ever ants vs. never any ants

## dataset summary table
### main
last_desL*ants_ever
```{r}

(surv_reg_data.tbl_summary.ants_ever <- surv_reg_data %>%
  mutate(ants = ifelse(ever_antsP, "Ever ants", "Never ants"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `desertion date rel. to hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `desertion date rel. to hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n() %>% add_p() %>% bold_p())

surv_reg_data.tbl_summary.ants_ever %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.data_summary.desL.ants_ever.docx")
```

### supp
last_desL*ant_treatment
```{r}
(surv_reg_data.tbl_summary.ants_treatment <- surv_reg_data %>%
  mutate(ants = ifelse(ants_removed, "Ant exclusion", "Control"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `desertion date rel. to hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `desertion date rel. to hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n() %>% add_p() %>% bold_p())

surv_reg_data.tbl_summary.ants_treatment %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.data_summary.desL.ants_treatment.docx")
```

last_desP*ants_ever
```{r}
(surv_reg_data.tbl_summary.ants_ever.LastDesPlant <- surv_reg_data_LastDesPlant %>%
  mutate(ants = ifelse(ever_antsP, "Ever ants", "Never ants"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `desertion of clutch rel. to hatch` = des,
         `desertion of plant rel. to hatch` = last_desP_rel2h,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `desertion of clutch rel. to hatch`, `desertion of plant rel. to hatch`,
         `n eggs`, `n hatched`, `n survived`) %>%
  tbl_strata(
    strata = females,
    ~.x %>%
      tbl_summary(by = ants) %>% bold_labels() %>% italicize_levels() %>% add_n()))

surv_reg_data.tbl_summary.ants_ever.LastDesPlant %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.data_summary.desP.ants_ever.docx")
```

## stats
### main
last_desL*ants_ever
```{r}
des_hatch.ants_ever.tbl <- 
  tbl_regression(des_hatch.ants_ever.pw.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Desertion rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()
des_Nsurv.ants_ever.tbl <- 
  tbl_regression(des_Nsurv.ants_ever.pw.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Desertion rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()
des_Esurv.ants_ever.tbl <- 
  tbl_regression(des_Esurv.ants_ever.pw.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Desertion rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()

(ants_ever.tbl_merge <- 
  tbl_merge(
    tbls = list(des_hatch.ants_ever.tbl, 
                des_Nsurv.ants_ever.tbl, 
                des_Esurv.ants_ever.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

ants_ever.tbl_merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desL.ants_ever.docx")
```

### supp
last_desL*ant_treatment
```{r}
# qaicc
des_hatch.qaicc
des_Nsurv.qaicc
des_Esurv.qaicc

# So the three best qaicc models to show in tables/plots of main all don't have vis:
summary(des_hatch.pw.fits$mai.qb)
summary(des_Nsurv.pw.fits$mai.qb)
summary(des_Esurv.pw.fits$mai.qb)

des_hatch.ants_trt.tbl <- 
  tbl_regression(des_hatch.pw.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Desertion rel. hatch",
                          ant_treatment ~ "Ants")) %>% bold_p()
des_Nsurv.ants_trt.tbl <- tbl_regression(des_Nsurv.pw.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Desertion rel. hatch",
                          ant_treatment ~ "Ants")) %>% bold_p()
des_Esurv.ants_trt.tbl <- tbl_regression(des_Esurv.pw.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Desertion rel. hatch",
                          ant_treatment ~ "Ants")) %>% bold_p()

(ants_trt.tbl_merge <- 
  tbl_merge(
    tbls = list(des_hatch.ants_trt.tbl, 
                des_Nsurv.ants_trt.tbl, 
                des_Esurv.ants_trt.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

ants_trt.tbl_merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desL.ants_treatment.docx")
```

last_desP*ants_ever
```{r}
# qaicc
des_hatch.qaicc
get_qaicc(des_hatch.ants_ever.pw.fits.LastDesPlant)
des_Nsurv.qaicc
get_qaicc(des_Nsurv.ants_ever.pw.fits.LastDesPlant)
des_Esurv.qaicc
get_qaicc(des_Esurv.ants_ever.pw.fits.LastDesPlant)

# So the three best qaicc models to show in tables/plots of main all don't have vis:
summary(des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb)
summary(des_Nsurv.ants_ever.pw.fits.LastDesPlant$mai.qb)
summary(des_Esurv.ants_ever.pw.fits.LastDesPlant$mai.qb)

des_hatch.ants_ever.LastDesPlant.tbl <- 
  tbl_regression(des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()
des_Nsurv.ants_ever.LastDesPlant.tbl <- 
  tbl_regression(des_Nsurv.ants_ever.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()
des_Esurv.ants_ever.LastDesPlant.tbl <- 
  tbl_regression(des_Esurv.ants_ever.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()

(ants_ever.LastDesPlant.tbl_merge <- 
  tbl_merge(
    tbls = list(des_hatch.ants_ever.LastDesPlant.tbl, 
                des_Nsurv.ants_ever.LastDesPlant.tbl, 
                des_Esurv.ants_ever.LastDesPlant.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

ants_ever.LastDesPlant.tbl_merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desP.ants_ever.docx")
```

## figures
### main
```{r}
des_hatch.ants_ever.pw.qb.p <- plot_ci(ci_data=des_hatch.ants_ever.pw.qb.ci, 
                                  tenure=des, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Nsurv.ants_ever.pw.qb.p <- plot_ci(ci_data=des_Nsurv.ants_ever.pw.qb.ci, 
                                  tenure=des, treatment=ants_ever,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Esurv.ants_ever.pw.qb.p <- plot_ci(ci_data=des_Esurv.ants_ever.pw.qb.ci, 
                                  tenure=des, treatment=ants_ever,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants")) +
    scale_fill_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants"))

(survivorship.ants_ever.final.p <- 
    egg::ggarrange(des_hatch.ants_ever.pw.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.ants_ever.pw.qb.p+
                 theme(legend.position="none"),
               des_Esurv.ants_ever.pw.qb.p+
                 theme(legend.position=c(0.5,0.9))+ylim(0,1),
               labels=c("A","B","C"),
               nrow=1))

ggsave("survivorship.desL.ants_ever.final.png",
       survivorship.ants_ever.final.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

### supp
last_desL*ant_treatment
```{r}
des_hatch.pw.qb.p <- plot_ci(ci_data=des_hatch.pw.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Nsurv.pw.qb.p <- plot_ci(ci_data=des_Nsurv.pw.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Esurv.pw.qb.p <- plot_ci(ci_data=des_Esurv.pw.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion date relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants")) +
    scale_fill_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants"))

(survivorship.ants_treatment.final.p <- 
    egg::ggarrange(des_hatch.pw.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.pw.qb.p+
                 theme(legend.position="none"),
               des_Esurv.pw.qb.p+
                 theme(legend.position=c(0.5,0.9))+ylim(0,1),
               labels=c("A","B","C"),
               nrow=1))

ggsave("survivorship.desL.ants_treatment.final.png",
       survivorship.ants_treatment.final.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

last_desP*ants_ever
```{r}
des_hatch.desP.ants_ever.pw.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb)

des_Nsurv.desP.ants_ever.pw.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.ants_ever.pw.fits.LastDesPlant$mai.qb)

des_Esurv.desP.ants_ever.pw.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.ants_ever.pw.fits.LastDesPlant$mai.qb)

des_hatch.ants_ever.LastDesPlant.tbl <- 
  tbl_regression(des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()

des_hatch.desP.ants_ever.pw.qb.p <- plot_ci(ci_data=des_hatch.desP.ants_ever.pw.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Nsurv.desP.ants_ever.pw.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ants_ever.pw.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Esurv.desP.ants_ever.pw.qb.p <- plot_ci(ci_data=des_Esurv.desP.ants_ever.pw.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants")) +
    scale_fill_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants"))

(survivorship.desP.ants_ever.final.p <- 
    egg::ggarrange(des_hatch.desP.ants_ever.pw.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_ever.pw.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desP.ants_ever.pw.qb.p+
                 theme(legend.position=c(0.5,0.9))+ylim(0,1),
               labels=c("A","B","C"),
               nrow=1))

ggsave("survivorship.desP.ants_ever.final.png",
       survivorship.desP.ants_ever.final.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

last_desP*ants_ever female removal control only
```{r}
surv_reg_data_LastDesPlant_filtFemRem <- filter(surv_reg_data_LastDesPlant, !females_removed)

des_hatch.ants_ever.filtFemRem.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ants_ever,
                              interaction="pw")

des_Nsurv.ants_ever.filtFemRem.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=n_hatched,
                              interaction="pw")

des_Esurv.ants_ever.filtFemRem.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=med_t5eggs,
                              interaction="pw")

des_hatch.desP.ants_ever.filtFemRem.pw.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb)

des_Nsurv.desP.ants_ever.filtFemRem.pw.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.ants_ever.pw.fits.LastDesPlant$mai.qb)

des_Esurv.desP.ants_ever.filtFemRem.pw.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.ants_ever.pw.fits.LastDesPlant$mai.qb)

des_hatch.ants_ever.filtFemRem.LastDesPlant.tbl <- 
  tbl_regression(des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()

des_hatch.desP.ants_ever.filtFemRem.pw.qb.p <- plot_ci(ci_data=des_hatch.desP.ants_ever.filtFemRem.pw.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Nsurv.desP.ants_ever.filtFemRem.pw.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ants_ever.filtFemRem.pw.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Esurv.desP.ants_ever.filtFemRem.pw.qb.p <- plot_ci(ci_data=des_Esurv.desP.ants_ever.filtFemRem.pw.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants")) +
    scale_fill_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants"))

(survivorship.desP.ants_ever.filtFemRem.final.p <- 
    egg::ggarrange(des_hatch.desP.ants_ever.filtFemRem.pw.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_ever.filtFemRem.pw.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desP.ants_ever.filtFemRem.pw.qb.p+
                 theme(legend.position=c(0.5,0.9))+ylim(0,1),
               labels=c("A","B","C"),
               nrow=1))

ggsave("survivorship.desP.ants_ever.filtFemRem.final.png",
       survivorship.desP.ants_ever.filtFemRem.final.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

last_desP*ants_ever filtFemRem regression table
```{r}
des_hatch.ants_ever.filtFemRem.LastDesPlant.tbl <- 
  tbl_regression(des_hatch.ants_ever.filtFemRem.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()
des_Nsurv.ants_ever.filtFemRem.LastDesPlant.tbl <- 
  tbl_regression(des_Nsurv.ants_ever.filtFemRem.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()
des_Esurv.ants_ever.filtFemRem.LastDesPlant.tbl <- 
  tbl_regression(des_Esurv.ants_ever.filtFemRem.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()

(ants_ever.filtFemRem.LastDesPlant.tbl_merge <- 
  tbl_merge(
    tbls = list(des_hatch.ants_ever.LastDesPlant.tbl, 
                des_Nsurv.ants_ever.LastDesPlant.tbl, 
                des_Esurv.ants_ever.LastDesPlant.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

ants_ever.filtFemRem.LastDesPlant.tbl_merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desP.ants_ever.filtFemRem.docx")
```

last_desP*ants_ever female removal control only
```{r}
des_hatch.ants_ever.filtFemRem.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ants_ever,
                              interaction="pw")

des_Nsurv.ants_ever.filtFemRem.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=n_hatched,
                              interaction="pw")

des_Esurv.ants_ever.filtFemRem.pw.fits.LastDesPlant <- fit_surv(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=med_t5eggs,
                              interaction="pw")

des_hatch.desP.ants_ever.filtFemRem.pw.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb)

des_Nsurv.desP.ants_ever.filtFemRem.pw.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.ants_ever.pw.fits.LastDesPlant$mai.qb)

des_Esurv.desP.ants_ever.filtFemRem.pw.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant_filtFemRem, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.ants_ever.pw.fits.LastDesPlant$mai.qb)

des_hatch.ants_ever.filtFemRem.LastDesPlant.tbl <- 
  tbl_regression(des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()

des_hatch.desP.ants_ever.filtFemRem.pw.qb.p <- plot_ci(ci_data=des_hatch.desP.ants_ever.filtFemRem.pw.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Nsurv.desP.ants_ever.filtFemRem.pw.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ants_ever.filtFemRem.pw.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Esurv.desP.ants_ever.filtFemRem.pw.qb.p <- plot_ci(ci_data=des_Esurv.desP.ants_ever.filtFemRem.pw.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants")) +
    scale_fill_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants"))

(survivorship.desP.ants_ever.filtFemRem.final.p <- 
    egg::ggarrange(des_hatch.desP.ants_ever.filtFemRem.pw.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_ever.filtFemRem.pw.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desP.ants_ever.filtFemRem.pw.qb.p+
                 theme(legend.position=c(0.5,0.9))+ylim(0,1),
               labels=c("A","B","C"),
               nrow=1))

ggsave("survivorship.desP.ants_ever.filtFemRem.final.png",
       survivorship.desP.ants_ever.filtFemRem.final.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

does adding a quadratic term improve model fit and performance?
```{r}
### fit survivorship model
fit_surv_quad <- function(data_in, survNom, survDen, tenure, 
                     treatment){
  data <- eval(substitute(data_in %>% filter(!is.na(tenure))))

  mai.b <- eval(substitute(glm(survNom/survDen ~
            tenure*treatment + (I(as.numeric(tenure)^2))*treatment,
          data = data, weights = survDen, family = binomial)))
  print("Interaction, Binomial: ")
  print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])

  mai.qb <- eval(substitute(glm(survNom/survDen ~
            tenure*treatment + (I(as.numeric(tenure)^2))*treatment,
          data = data, weights = survDen, family = quasibinomial)))
  print("Interaction, Quasibinomial: ")
  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

  ma.qb <- eval(substitute(glm(survNom/survDen ~
            tenure+treatment + (I(as.numeric(tenure)^2))*treatment,
          data = data, weights = survDen, family = quasibinomial)))
  print("No Interaction, Quasibinomial: ")
  print(capture.output(summary(ma.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(ma.qb))))-1)])

    mai.models <- list(mai.b = mai.b, mai.qb = mai.qb, ma.qb = ma.qb)
  return(mai.models)
}

## DesP  
# ants_ever, desP
des_hatch.ants_ever.LastDesPlant.quad.fits <- fit_surv_quad(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ants_ever)

des_hatch.ants_ever.LastDesPlant.quad.ci <- ci_for_plot(data_in=surv_reg_data_LastDesPlant,
            model=des_hatch.ants_ever.LastDesPlant.quad.fits$mai.qb,
            survNom=n_hatched, survDen=med_t5eggs, tenure=last_desP_rel2h, treatment=ants_ever)

plot_ci(ci_data = des_hatch.ants_ever.LastDesPlant.quad.ci, 
                  tenure = last_desP_rel2h, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion of plant date relative to hatch") +
    ylab("Hatching success") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))
summary(des_hatch.ants_ever.LastDesPlant.quad.fits$mai.qb)

get_qaicc(des_hatch.ants_ever.pw.fits.LastDesPlant)
get_qaicc(des_hatch.ants_ever.LastDesPlant.quad.fits)

des_Nsurv.ants_ever.LastDesPlant.quad.fits <- fit_surv_quad(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=last_desP_rel2h, treatment=ants_ever)

des_Nsurv.ants_ever.LastDesPlant.quad.ci <- ci_for_plot(data_in=surv_reg_data_LastDesPlant,
            model=des_Nsurv.ants_ever.LastDesPlant.quad.fits$mai.qb,
            survNom=n_survived, survDen=n_hatched, tenure=last_desP_rel2h, treatment=ants_ever)

plot_ci(ci_data = des_Nsurv.ants_ever.LastDesPlant.quad.ci, 
                  tenure = last_desP_rel2h, treatment=ants_ever,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion of plant date relative to hatch") +
    ylab("Survivorship of nymphs") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))
summary(des_Nsurv.ants_ever.LastDesPlant.quad.fits$mai.qb)

get_qaicc(des_Nsurv.ants_ever.pw.fits.LastDesPlant)
get_qaicc(des_Nsurv.ants_ever.LastDesPlant.quad.fits)

des_Esurv.ants_ever.LastDesPlant.quad.fits <- fit_surv_quad(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ants_ever)

des_Esurv.ants_ever.LastDesPlant.quad.ci <- ci_for_plot(data_in=surv_reg_data_LastDesPlant,
            model=des_Esurv.ants_ever.LastDesPlant.quad.fits$mai.qb,
            survNom=n_survived, survDen=med_t5eggs, tenure=last_desP_rel2h, treatment=ants_ever)

plot_ci(ci_data = des_Esurv.ants_ever.LastDesPlant.quad.ci, 
                  tenure = last_desP_rel2h, treatment=ants_ever,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion of plant date relative to hatch") +
    ylab("Survivorship of eggs") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))
summary(des_Esurv.ants_ever.LastDesPlant.quad.fits$mai.qb)

get_qaicc(des_Esurv.ants_ever.pw.fits.LastDesPlant)
get_qaicc(des_Esurv.ants_ever.LastDesPlant.quad.fits)

# ant_treatment, desP
des_hatch.ant_treatment.LastDesPlant.quad.fits <- fit_surv_quad(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ant_treatment)

des_hatch.ant_treatment.LastDesPlant.quad.ci <- ci_for_plot(data_in=surv_reg_data_LastDesPlant,
            model=des_hatch.ant_treatment.LastDesPlant.quad.fits$mai.qb,
            survNom=n_hatched, survDen=med_t5eggs, tenure=last_desP_rel2h, treatment=ant_treatment)

plot_ci(ci_data = des_hatch.ant_treatment.LastDesPlant.quad.ci, 
                  tenure = last_desP_rel2h, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion of plant date relative to hatch") +
    ylab("Hatching success") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))
summary(des_hatch.ant_treatment.LastDesPlant.quad.fits$mai.qb)

#get_qaicc(des_hatch.ant_treatment.pw.fits.LastDesPlant)
get_qaicc(des_hatch.ant_treatment.LastDesPlant.quad.fits)

des_Nsurv.ant_treatment.LastDesPlant.quad.fits <- fit_surv_quad(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=last_desP_rel2h, treatment=ant_treatment)

des_Nsurv.ant_treatment.LastDesPlant.quad.ci <- ci_for_plot(data_in=surv_reg_data_LastDesPlant,
            model=des_Nsurv.ant_treatment.LastDesPlant.quad.fits$mai.qb,
            survNom=n_survived, survDen=n_hatched, tenure=last_desP_rel2h, treatment=ant_treatment)

plot_ci(ci_data = des_Nsurv.ant_treatment.LastDesPlant.quad.ci, 
                  tenure = last_desP_rel2h, treatment=ant_treatment,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion of plant date relative to hatch") +
    ylab("Survivorship of nymphs") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))
summary(des_Nsurv.ant_treatment.LastDesPlant.quad.fits$mai.qb)

#get_qaicc(des_Nsurv.ant_treatment.pw.fits.LastDesPlant)
get_qaicc(des_Nsurv.ant_treatment.LastDesPlant.quad.fits)

des_Esurv.ant_treatment.LastDesPlant.quad.fits <- fit_surv_quad(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ant_treatment)

des_Esurv.ant_treatment.LastDesPlant.quad.ci <- ci_for_plot(data_in=surv_reg_data_LastDesPlant,
            model=des_Esurv.ant_treatment.LastDesPlant.quad.fits$mai.qb,
            survNom=n_survived, survDen=med_t5eggs, tenure=last_desP_rel2h, treatment=ant_treatment)

plot_ci(ci_data = des_Esurv.ant_treatment.LastDesPlant.quad.ci, 
                  tenure = last_desP_rel2h, treatment=ant_treatment,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion of plant date relative to hatch") +
    ylab("Survivorship of eggs") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))
summary(des_Esurv.ant_treatment.LastDesPlant.quad.fits$mai.qb)

#get_qaicc(des_Esurv.ant_treatment.pw.fits.LastDesPlant)
get_qaicc(des_Esurv.ant_treatment.LastDesPlant.quad.fits)

## DesL
# ants_ever, desL
des_hatch.ants_ever.desL.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever)

des_hatch.ants_ever.desL.quad.ci <- ci_for_plot(data_in=surv_reg_data,
            model=des_hatch.ants_ever.desL.quad.fits$mai.qb,
            survNom=n_hatched, survDen=med_t5eggs, tenure=des, treatment=ants_ever)

(des_hatch.desL.ants_ever.quad.qb.p <- plot_ci(ci_data = des_hatch.ants_ever.desL.quad.ci, 
                  tenure = des, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion of leaf date relative to hatch") +
    ylab("Hatching success") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))
summary(des_hatch.ants_ever.desL.quad.fits$mai.qb)

#get_qaicc(des_hatch.ants_ever.pw.fits.desL)
get_qaicc(des_hatch.ants_ever.desL.quad.fits)

des_Nsurv.ants_ever.desL.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_ever)

des_Nsurv.ants_ever.desL.quad.ci <- ci_for_plot(data_in=surv_reg_data,
            model=des_Nsurv.ants_ever.desL.quad.fits$mai.qb,
            survNom=n_survived, survDen=n_hatched, tenure=des, treatment=ants_ever)

(des_Nsurv.desL.ants_ever.quad.qb.p <- plot_ci(ci_data = des_Nsurv.ants_ever.desL.quad.ci, 
                  tenure = des, treatment=ants_ever,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion of leaf date relative to hatch") +
    ylab("Survivorship of nymphs") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))
summary(des_Nsurv.ants_ever.desL.quad.fits$mai.qb)

#get_qaicc(des_Nsurv.ants_ever.pw.fits.desL)
get_qaicc(des_Nsurv.ants_ever.desL.quad.fits)

des_Esurv.ants_ever.desL.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ants_ever)

des_Esurv.ants_ever.desL.quad.ci <- ci_for_plot(data_in=surv_reg_data,
            model=des_Esurv.ants_ever.desL.quad.fits$mai.qb,
            survNom=n_survived, survDen=med_t5eggs, tenure=des, treatment=ants_ever)

(des_Esurv.desL.ants_ever.quad.qb.p <- plot_ci(ci_data = des_Esurv.ants_ever.desL.quad.ci, 
                  tenure = des, treatment=ants_ever,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion of leaf date relative to hatch") +
    ylab("Survivorship of eggs") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))
summary(des_Esurv.ants_ever.desL.quad.fits$mai.qb)

#get_qaicc(des_Esurv.ants_ever.pw.fits.desL)
get_qaicc(des_Esurv.ants_ever.desL.quad.fits)

# ant_treatment, desL
des_hatch.ant_treatment.desL.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment)

des_hatch.ant_treatment.desL.quad.ci <- ci_for_plot(data_in=surv_reg_data,
            model=des_hatch.ant_treatment.desL.quad.fits$mai.qb,
            survNom=n_hatched, survDen=med_t5eggs, tenure=des, treatment=ant_treatment)

plot_ci(ci_data = des_hatch.ant_treatment.desL.quad.ci, 
                  tenure = des, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion of plant date relative to hatch") +
    ylab("Hatching success") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))
summary(des_hatch.ant_treatment.desL.quad.fits$mai.qb)

#get_qaicc(des_hatch.ant_treatment.pw.fits.desL)
get_qaicc(des_hatch.ant_treatment.desL.quad.fits)

des_Nsurv.ant_treatment.desL.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ant_treatment)

des_Nsurv.ant_treatment.desL.quad.ci <- ci_for_plot(data_in=surv_reg_data,
            model=des_Nsurv.ant_treatment.desL.quad.fits$mai.qb,
            survNom=n_survived, survDen=n_hatched, tenure=des, treatment=ant_treatment)

plot_ci(ci_data = des_Nsurv.ant_treatment.desL.quad.ci, 
                  tenure = des, treatment=ant_treatment,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion of plant date relative to hatch") +
    ylab("Survivorship of nymphs") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))
summary(des_Nsurv.ant_treatment.desL.quad.fits$mai.qb)

#get_qaicc(des_Nsurv.ant_treatment.pw.fits.desL)
get_qaicc(des_Nsurv.ant_treatment.desL.quad.fits)

des_Esurv.ant_treatment.desL.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment)

des_Esurv.ant_treatment.desL.quad.ci <- ci_for_plot(data_in=surv_reg_data,
            model=des_Esurv.ant_treatment.desL.quad.fits$mai.qb,
            survNom=n_survived, survDen=med_t5eggs, tenure=des, treatment=ant_treatment)

plot_ci(ci_data = des_Esurv.ant_treatment.desL.quad.ci, 
                  tenure = des, treatment=ant_treatment,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion of plant date relative to hatch") +
    ylab("Survivorship of eggs") +
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))
summary(des_Esurv.ant_treatment.desL.quad.fits$mai.qb)

#get_qaicc(des_Esurv.ant_treatment.pw.fits.desL)
get_qaicc(des_Esurv.ant_treatment.desL.quad.fits)
```

last_desP * ants_ever + last_desP^2 * ants_ever
```{r}
des_hatch.desP.ants_ever.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.ants_ever.LastDesPlant.quad.fits$mai.qb)

des_Nsurv.desP.ants_ever.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.ants_ever.LastDesPlant.quad.fits$mai.qb)

des_Esurv.desP.ants_ever.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=last_desP_rel2h, treatment=ants_ever,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.ants_ever.LastDesPlant.quad.fits$mai.qb)

des_hatch.ants_ever.LastDesPlant.tbl <- 
  tbl_regression(des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()

des_hatch.desP.ants_ever.quad.qb.p <- plot_ci(ci_data=des_hatch.desP.ants_ever.quad.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Nsurv.desP.ants_ever.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ants_ever.quad.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom=n_survived, survDen=n_hatched) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

des_Esurv.desP.ants_ever.quad.qb.p <- plot_ci(ci_data=des_Esurv.desP.ants_ever.quad.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_ever,
             survNom=n_survived, survDen=med_t5eggs) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Survivorship of eggs (eggs/adults)") + 
    scale_color_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants")) +
    scale_fill_manual(values = c("brown1", "black"), labels=c("Ever ants", "Never ants"))

(survivorship.desP.ants_ever.quad.final.p <- 
    egg::ggarrange(des_hatch.desP.ants_ever.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_ever.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desP.ants_ever.quad.qb.p+
                 theme(legend.position=c(0.5,0.9))+ylim(0,1),
               labels=c("A","B","C"),
               nrow=1))

ggsave("survivorship.desP.ants_ever.quad.final.png",
       survivorship.desP.ants_ever.quad.final.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

quadratic regression table
```{r}
desP_hatch.ants_ever.quad.tbl <- 
  tbl_regression(des_hatch.ants_ever.LastDesPlant.quad.fits$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()
desP_Nsurv.ants_ever.quad.tbl <- 
  tbl_regression(des_Nsurv.ants_ever.LastDesPlant.quad.fits$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()
desP_Esurv.ants_ever.quad.tbl <- 
  tbl_regression(des_Esurv.ants_ever.LastDesPlant.quad.fits$mai.qb, exponentiate=T,
                 label=list(last_desP_rel2h ~ "Desertion of plant rel. hatch",
                          ants_ever ~ "Ants")) %>% bold_p()

(desP.ants_ever.quad.tbl_merge <- 
  tbl_merge(
    tbls = list(desP_hatch.ants_ever.quad.tbl, 
                desP_Nsurv.ants_ever.quad.tbl, 
                desP_Esurv.ants_ever.quad.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desP.ants_ever.quad.tbl_merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desP.ants_ever.quad.docx")
```

model comparison table
```{r}
des_hatch.ants_ever.pw.fits.LastDesPlant.null <- 
  glm(data=surv_reg_data_LastDesPlant,
      n_hatched/med_t5eggs ~ 1, family=quasibinomial, weights=med_t5eggs)

with(anova(des_hatch.ants_ever.pw.fits.LastDesPlant.null,
           des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb),
     pchisq(Deviance,Df,lower.tail=FALSE)[2])

des_hatch.pw.fits.null <- 
  glm(data=surv_reg_data,
      n_hatched/med_t5eggs ~ 1, family=quasibinomial, weights=med_t5eggs)

with(anova(des_hatch.pw.fits.null,
           des_hatch.pw.fits$mai.qb),
     pchisq(Deviance,Df,lower.tail=FALSE)[2])

# qaicc
(qAICc_gt_tbl <- tibble(
  Model = rep(c("last desert clutch, ant treatment","last desert clutch, ever ants", 
                "last desert plant, ant treatment", "last desert plant, ever ants"),3),
  Response = c(rep("Hatching success",4), rep("Survivorship of nymphs",4), rep("Survivorship of eggs",4)),
  qAICc = c(
    get_qaicc(des_hatch.pw.fits),
    get_qaicc(des_hatch.ants_ever.pw.fits),
    get_qaicc(des_hatch.pw.fits.LastDesPlant),
    get_qaicc(des_hatch.ants_ever.pw.fits.LastDesPlant),
    get_qaicc(des_Nsurv.pw.fits),
    get_qaicc(des_Nsurv.ants_ever.pw.fits),
    get_qaicc(des_Nsurv.pw.fits.LastDesPlant),
    get_qaicc(des_Nsurv.ants_ever.pw.fits.LastDesPlant),
    get_qaicc(des_Esurv.pw.fits),
    get_qaicc(des_Esurv.ants_ever.pw.fits),
    get_qaicc(des_Esurv.pw.fits.LastDesPlant),
    get_qaicc(des_Esurv.ants_ever.pw.fits.LastDesPlant))
  ) %>% 
  group_by(Response) %>%
    arrange(qAICc) %>%
    mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))

qAICc_gt_tbl %>%
  gt::gtsave(filename="survivorsip_models.qAICc_comparison.rtf")

# qAICc into separate tables
# qaicc
(qAICc_gt_tbl_hatch <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment",
            "desert leaf + ants ever + desert leaf*ants ever",
            "desert plant + ant treatment + desert plant*ant treatment",
            "desert plant + ants ever + desert plant*ants ever",
            "desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert leaf + ants ever + desert leaf*ants ever + 
            desert leaf^2 + desert leaf^2*ants ever",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert plant + ants ever + desert plant*ants ever + 
            desert plant^2 + desert plant^2*ants ever"),
  Response = c(rep("Hatching success",8)),
  qAICc = c(
    get_qaicc(des_hatch.pw.fits),
    get_qaicc(des_hatch.ants_ever.pw.fits),
    get_qaicc(des_hatch.pw.fits.LastDesPlant),
    get_qaicc(des_hatch.ants_ever.pw.fits.LastDesPlant),
    get_qaicc(des_hatch.ant_treatment.desL.quad.fits),
    get_qaicc(des_hatch.ants_ever.desL.quad.fits),
    get_qaicc(des_hatch.ant_treatment.LastDesPlant.quad.fits),
    get_qaicc(des_hatch.ants_ever.LastDesPlant.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))

(qAICc_gt_tbl_Nsurv <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment",
            "desert leaf + ants ever + desert leaf*ants ever",
            "desert plant + ant treatment + desert plant*ant treatment",
            "desert plant + ants ever + desert plant*ants ever",
            "desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert leaf + ants ever + desert leaf*ants ever + 
            desert leaf^2 + desert leaf^2*ants ever",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert plant + ants ever + desert plant*ants ever + 
            desert plant^2 + desert plant^2*ants ever"),
  Response = c(rep("Survivorship of nymphs",8)),
  qAICc = c(
    get_qaicc(des_Nsurv.pw.fits),
    get_qaicc(des_Nsurv.ants_ever.pw.fits),
    get_qaicc(des_Nsurv.pw.fits.LastDesPlant),
    get_qaicc(des_Nsurv.ants_ever.pw.fits.LastDesPlant),
    get_qaicc(des_Nsurv.ant_treatment.desL.quad.fits),
    get_qaicc(des_Nsurv.ants_ever.desL.quad.fits),
    get_qaicc(des_Nsurv.ant_treatment.LastDesPlant.quad.fits),
    get_qaicc(des_Nsurv.ants_ever.LastDesPlant.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))

(qAICc_gt_tbl_Esurv <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment",
            "desert leaf + ants ever + desert leaf*ants ever",
            "desert plant + ant treatment + desert plant*ant treatment",
            "desert plant + ants ever + desert plant*ants ever",
            "desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert leaf + ants ever + desert leaf*ants ever + 
            desert leaf^2 + desert leaf^2*ants ever",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert plant + ants ever + desert plant*ants ever + 
            desert plant^2 + desert plant^2*ants ever"),
  Response = c(rep("Survivorship of eggs",8)),
  qAICc = c(
    get_qaicc(des_Esurv.pw.fits),
    get_qaicc(des_Esurv.ants_ever.pw.fits),
    get_qaicc(des_Esurv.pw.fits.LastDesPlant),
    get_qaicc(des_Esurv.ants_ever.pw.fits.LastDesPlant),
    get_qaicc(des_Esurv.ant_treatment.desL.quad.fits),
    get_qaicc(des_Esurv.ants_ever.desL.quad.fits),
    get_qaicc(des_Esurv.ant_treatment.LastDesPlant.quad.fits),
    get_qaicc(des_Esurv.ants_ever.LastDesPlant.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))
```

### Plot only the best model (based on qAICc) for each response variable.
#### Hatching success
`desert_leaf * ants_ever`, `desert_plant * ants_ever`, `desert_plant * ants_treatment`, and `desert_plant * ants_ever + desert_plant^2 * ants_ever` are all equivalent (delta-qAICc < 2) and all models tested were within 4 qAICc of the best model, probably reflecting poor fit and small effect of desertion time and ants on hatching across all models.

Showing the top 4 models:
```{r}
qAICc_gt_tbl_hatch

tbl_regression(des_hatch.ants_ever.pw.fits$mai.qb, exponentiate=T) %>% bold_p()
des_hatch.ants_ever.pw.qb.p

tbl_regression(des_hatch.ants_ever.pw.fits.LastDesPlant$mai.qb, exponentiate=T) %>% bold_p()
des_hatch.ants_ever.pw.qb.p.LastDesPlant

tbl_regression(des_hatch.pw.fits.LastDesPlant$mai.qb, exponentiate=T) %>% bold_p()
des_hatch.pw.qb.p.LastDesPlant

tbl_regression(des_hatch.ants_ever.LastDesPlant.quad.fits$mai.qb, exponentiate=T) %>% bold_p()
des_hatch.desP.ants_ever.quad.qb.p
```

#### Nymph survivorship
The clear winner here is `desert_plant * ants_ever + desert_plant^2 * ants_ever` (second best, quadratic leaf_desertion, is qAICc=28.28 higher).

Showing just the best model: `desert_plant * ants_ever + desert_plant^2 * ants_ever`
```{r}
qAICc_gt_tbl_Nsurv

tbl_regression(des_Nsurv.ants_ever.LastDesPlant.quad.fits$mai.qb, exponentiate=T) %>% bold_p()
des_Nsurv.desP.ants_ever.quad.qb.p

# Compare to model I was showing in the main text before:
tbl_regression(des_Nsurv.ants_ever.pw.fits$mai.qb, exponentiate=T) %>% bold_p()
des_Nsurv.ants_ever.pw.qb.p
```

#### Egg to adult survivorship
The clear winner here is `desert_plant * ants_ever + desert_plant^2 * ants_ever` (second best, quadratic leaf_desertion, is qAICc=28.28 higher).

The problem is that the 95% conf int in the plot looks really awful at the earliest desertion dates.
I guess because there's not enough data to resolve whether there truly is a drop in survivorship after a certain late desertion date (concave down), and since the quadratic term is still significant and there are fewer values at lower desertion dates, it forces a concave-up curve. This is probably why the models that include a quadratic term have generally wider (and uglier) confidence intervals.

Showing just the best model: `desert_plant * ants_ever + desert_plant^2 * ants_ever`
```{r}
qAICc_gt_tbl_Esurv

tbl_regression(des_Esurv.ants_ever.desL.quad.fits$mai.qb, exponentiate=T) %>% bold_p()
des_Esurv.desL.ants_ever.quad.qb.p

tbl_regression(des_Esurv.ants_ever.LastDesPlant.quad.fits$mai.qb, exponentiate=T) %>% bold_p()

# Compare to model I was showing in the main text before:
tbl_regression(des_Esurv.ants_ever.pw.fits$mai.qb, exponentiate=T) %>% bold_p()
des_Esurv.ants_ever.pw.qb.p
```

#### Putting the best (quad) models together
```{r}
egg::ggarrange(des_hatch.desP.ants_ever.quad.qb.p+ # desP was lowest qAICc
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_ever.quad.qb.p+ # desP was lowest qAICc
                 theme(legend.position="none"),
               des_Esurv.desP.ants_ever.quad.qb.p+ # desP was lowest qAICc
                 theme(legend.position=c(0.8,0.8))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3)

egg::ggarrange(des_hatch.desL.ants_ever.quad.qb.p+ # desL was lowest qAICc
                 theme(legend.position="none"),
               des_Nsurv.desL.ants_ever.quad.qb.p+ # desL was lowest qAICc
                 theme(legend.position="none"),
               des_Esurv.desL.ants_ever.quad.qb.p+ # desL was lowest qAICc
                 theme(legend.position=c(0.8,0.8))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3)

# Compare to old main figure
egg::ggarrange(des_hatch.ants_ever.pw.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.ants_ever.pw.qb.p+
                 theme(legend.position="none"),
               des_Esurv.ants_ever.pw.qb.p+
                 theme(legend.position=c(0.8,0.8))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3)
```

### ants_gt2d
desP.ants_gt2d.quad.qb.p
```{r}
# hatching success
des_hatch.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ants_gt2d)

des_hatch.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=last_desP_rel2h, treatment=ants_gt2d,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desP.ants_gt2d.quad.fits$mai.qb)

(des_hatch.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_gt2d,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

# nymph survivorship
des_Nsurv.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=last_desP_rel2h, treatment=ants_gt2d)

des_Nsurv.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=last_desP_rel2h, treatment=ants_gt2d,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desP.ants_gt2d.quad.fits$mai.qb)

(des_Nsurv.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_gt2d,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

# egg survivorship
des_Esurv.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data_LastDesPlant, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=last_desP_rel2h, treatment=ants_gt2d)

des_Esurv.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=last_desP_rel2h, treatment=ants_gt2d,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desP.ants_gt2d.quad.fits$mai.qb)

(des_Esurv.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=last_desP_rel2h, treatment=ants_gt2d,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion from plant relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))

egg::ggarrange(des_hatch.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position=c(0.8,0.8))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3)

```

desL.ants_gt2d.quad.qb.p
```{r}
# hatching success
des_hatch.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_gt2d)

des_hatch.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ants_gt2d.quad.fits$mai.qb)

(des_hatch.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion from leaf relative to hatch") +
    ylab("Hatching success (eggs/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))
summary(des_hatch.desL.ants_gt2d.quad.fits$mai.qb)

# nymph survivorship
des_Nsurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_gt2d)

des_Nsurv.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb)

(des_Nsurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion from leaf relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))
summary(des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb)

# egg survivorship
des_Esurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ants_gt2d)

des_Esurv.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desL.ants_gt2d.quad.fits$mai.qb)

(des_Esurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion from leaf relative to hatch") +
    ylab("Survivorship of nymphs (nymphs/adults)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black")))
summary(des_Esurv.desL.ants_gt2d.quad.fits$mai.qb)

egg::ggarrange(des_hatch.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position=c(0.8,0.8))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3)

hatch.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Desertion of leaf rel. hatch",
                            `I(as.numeric(des)^2)` ~ "(Desertion of leaf rel. hatch)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Desertion of leaf rel. hatch",
                            `I(as.numeric(des)^2)` ~ "(Desertion of leaf rel. hatch)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Desertion of leaf rel. hatch",
                            `I(as.numeric(des)^2)` ~ "(Desertion of leaf rel. hatch)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

(desP.ants_gt2d.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desL.ants_gt2d.quad.qb.tbl, 
                Nsurv.desL.ants_gt2d.quad.qb.tbl, 
                Esurv.desL.ants_gt2d.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())
```

qaicc
```{r}
# qAICc into separate tables
# qaicc
(qAICc_gt_tbl_hatch_gt2d <- tibble(
  Model = c("desert leaf + ants ever + desert leaf*ants ever",
            "desert plant + ants ever + desert plant*ants ever",
            "desert leaf + ants ever + desert leaf*ants ever + 
            desert leaf^2 + desert leaf^2*ants ever",
            "desert plant + ants ever + desert plant*ants ever + 
            desert plant^2 + desert plant^2*ants ever",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Hatching success",6)),
  qAICc = c(
    get_qaicc(des_hatch.ants_ever.pw.fits),
    get_qaicc(des_hatch.ants_ever.pw.fits.LastDesPlant),
    get_qaicc(des_hatch.ants_ever.desL.quad.fits),
    get_qaicc(des_hatch.ants_ever.LastDesPlant.quad.fits),
    get_qaicc(des_hatch.desL.ants_gt2d.quad.fits),
    get_qaicc(des_hatch.desP.ants_gt2d.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))

(qAICc_gt_tbl_Nsurv_gt2d <- tibble(
  Model = c("desert leaf + ants ever + desert leaf*ants ever",
            "desert plant + ants ever + desert plant*ants ever",
            "desert leaf + ants ever + desert leaf*ants ever + 
            desert leaf^2 + desert leaf^2*ants ever",
            "desert plant + ants ever + desert plant*ants ever + 
            desert plant^2 + desert plant^2*ants ever",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Survivorship of nymphs",6)),
  qAICc = c(
    get_qaicc(des_Nsurv.ants_ever.pw.fits),
    get_qaicc(des_Nsurv.ants_ever.pw.fits.LastDesPlant),
    get_qaicc(des_Nsurv.ants_ever.desL.quad.fits),
    get_qaicc(des_Nsurv.ants_ever.LastDesPlant.quad.fits),
    get_qaicc(des_Nsurv.desL.ants_gt2d.quad.fits),
    get_qaicc(des_Nsurv.desP.ants_gt2d.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))

(qAICc_gt_tbl_Esurv_gt2d <- tibble(
  Model = c("desert leaf + ants ever + desert leaf*ants ever",
            "desert plant + ants ever + desert plant*ants ever",
            "desert leaf + ants ever + desert leaf*ants ever + 
            desert leaf^2 + desert leaf^2*ants ever",
            "desert plant + ants ever + desert plant*ants ever + 
            desert plant^2 + desert plant^2*ants ever",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Survivorship of eggs",6)),
  qAICc = c(
    get_qaicc(des_Esurv.ants_ever.pw.fits),
    get_qaicc(des_Esurv.ants_ever.pw.fits.LastDesPlant),
    get_qaicc(des_Esurv.ants_ever.desL.quad.fits),
    get_qaicc(des_Esurv.ants_ever.LastDesPlant.quad.fits),
    get_qaicc(des_Esurv.desL.ants_gt2d.quad.fits),
    get_qaicc(des_Esurv.desP.ants_gt2d.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))
```

# Final (really this time) figures for the dissertation
Choosing the models strictly based on qAICc leads to some odd results that make biological interpretation too complciated.

Hatching success: All model types are within ~2 qAICc of each other, so pick whichever shows the biology best and is most consistent with Nsurv and Esurv.

Nymph survivorship: desP * ants_ever * desP^2 has the best qAICc, and the desL version has the second best. The desL version (which, for biological interpretation's sake, should be in the main figure) has very wide 95% CI on the left side, which sends off alarm bells that model fit may be a less robust to addition or subtraction of samples than the AIC suggests.

Egg survivorship: desL * ants_ever * desL^2  has best qAICc, by far. Again the left side 95% CI is huge and it just looks terrible, suggesting to me that there may be too few influential points on the right side to conclusively support the convex up shape.

One problem with the ants_ever method is that the `never ants` level has a much smaller sample size than the `ever ants` level. I'm worried that this could make conclusive inference on the difference among these treatments or even just slope and shape could be shaky. Breaking the groups into `ants >2 days` vs `ants <=2 days` solves the unequal sample sizes problem and makes the desL figure more straightforward to interpret. The qAICc is considerably worse, but I'm concerned that it is only because ants ever was overfitting with too little data.

So, I'm making `desL * ants_gt2 * desL^2` the main figure and `desP * ants_gt2 * desP^2` the supplemental figure. I will report the qAICc of these two models, but not in a table. The data summary table, regression table and results text will need to change too.

*******

After running all these new regressions, I realize that the desL * ant treatment quadratic model has the lowest qAICc and the most interpretable plot and summary stats. I will use this instead.

And since the desP models perform poorly (both in terms of AICc and a convex up Nsurv fit), I just won't even include them in the supplement. I can include the desL `ants >2 days` in the supplement, but honestly it might not even be necessary since it looks so similar to the treatment-based model. I can just mention they are similar?

# Main - `desL * ants_gt2 * desL^2`

## Tables
```{r}
(surv_reg_data.tbl_summary.desL.ants_gt2d <- surv_reg_data %>%
  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `leaf desert date rel. hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desL.ants_gt2d %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desL.ants_gt2d.docx")
```

```{r}
hatch.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

(desL.ants_gt2d.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desL.ants_gt2d.quad.qb.tbl, 
                Nsurv.desL.ants_gt2d.quad.qb.tbl, 
                Esurv.desL.ants_gt2d.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desL.ants_gt2d.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desL.ants_gt2d.quad.docx")
```

## Figures
```{r}
# hatching success
des_hatch.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_gt2d)

des_hatch.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ants_gt2d.quad.fits$mai.qb)

des_hatch.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_gt2d)

des_Nsurv.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb)

des_Nsurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# egg survivorship
des_Esurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ants_gt2d)

des_Esurv.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desL.ants_gt2d.quad.fits$mai.qb)

des_Esurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
    scale_color_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days")) +
    scale_fill_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days"))

(desL.ants_gt2d.quad.qb.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desL.ants_gt2d.quad.qb.p+
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desL.ants_gt2d.quad.final.png",
       desL.ants_gt2d.quad.qb.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

# Supp 1 -`desL * ants_treatment * desL^2`
## Figures
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment)

des_hatch.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ant_treatment,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ant_treatment.quad.fits$mai.qb)

des_hatch.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ant_treatment)

des_Nsurv.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ant_treatment,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)

des_Nsurv.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# egg survivorship
des_Esurv.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment)

des_Esurv.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ant_treatment,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desL.ant_treatment.quad.fits$mai.qb)

des_Esurv.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Esurv.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
    scale_color_manual(values = c("brown1", "black"), labels = c("Control", "Ant Exclusion")) +
    scale_fill_manual(values = c("brown1", "black"), labels = c("Control", "Ant Exclusion"))

(desL.ant_treatment.quad.qb.p <- egg::ggarrange(des_hatch.desL.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desL.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desL.ant_treatment.quad.qb.p+
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desL.ant_treatment.quad.final.png",
       desL.ant_treatment.quad.qb.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

## Tables
```{r}
(surv_reg_data.tbl_summary.desL.ant_treatment <- surv_reg_data %>%
  mutate(ants = ant_treatment,
         females = ifelse(females_removed, "Females removed", "Control"),
         `leaf desert date rel. hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desL.ant_treatment %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desL.ant_treatment.docx")
```

```{r}
hatch.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

(desL.ant_treatment.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desL.ant_treatment.quad.qb.tbl, 
                Nsurv.desL.ant_treatment.quad.qb.tbl, 
                Esurv.desL.ant_treatment.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desL.ant_treatment.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desL.ants_treatment.quad.docx")
```

# Supp 2 -`desP * ants_gt2 * desP^2`
## Figures
```{r}
# hatching success
des_hatch.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=desP, treatment=ants_gt2d)

des_hatch.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ants_gt2d,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desP.ants_gt2d.quad.fits$mai.qb)

des_hatch.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=desP, treatment=ants_gt2d,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=desP, treatment=ants_gt2d)

des_Nsurv.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ants_gt2d,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desP.ants_gt2d.quad.fits$mai.qb)

des_Nsurv.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=desP, treatment=ants_gt2d,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# egg survivorship
des_Esurv.desP.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=desP, treatment=ants_gt2d)

des_Esurv.desP.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ants_gt2d,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desP.ants_gt2d.quad.fits$mai.qb)

des_Esurv.desP.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Esurv.desP.ants_gt2d.quad.qb.ci, 
                                  tenure=desP, treatment=ants_gt2d,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
    scale_color_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days")) +
    scale_fill_manual(values = c("brown1", "black"), labels = c("ants > 2 days", "ants ≤ 2 days"))

(desP.ants_gt2d.quad.qb.p <- egg::ggarrange(des_hatch.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desP.ants_gt2d.quad.qb.p+
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desP.ants_gt2d.quad.final.png",
       desP.ants_gt2d.quad.qb.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

## Tables
don't need to include the data summary in supp, since the only thing that changes is the median (IQR) for desertion
```{r}
(surv_reg_data.tbl_summary.desP.ants_gt2d <- surv_reg_data %>%
  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `plant desert date rel. hatch` = desP,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `plant desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desP.ants_gt2d %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desP.ants_gt2d.docx")
```

```{r}
hatch.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ants_gt2d.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

(desP.ants_gt2d.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desP.ants_gt2d.quad.qb.tbl, 
                Nsurv.desP.ants_gt2d.quad.qb.tbl, 
                Esurv.desP.ants_gt2d.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desP.ants_gt2d.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desP.ants_gt2d.quad.docx")
```

# Supp 3 -`desP * ant_s_gt2_treatment * desP^2`
## Figures
```{r}
# hatching success
des_hatch.desP.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=desP, treatment=ant_treatment)

des_hatch.desP.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ant_treatment,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desP.ant_treatment.quad.fits$mai.qb)

des_hatch.desP.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_hatch.desP.ant_treatment.quad.qb.ci, 
                                  tenure=desP, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desP.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=desP, treatment=ant_treatment)

des_Nsurv.desP.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ant_treatment,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desP.ant_treatment.quad.fits$mai.qb)

des_Nsurv.desP.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desP.ant_treatment.quad.qb.ci, 
                                  tenure=desP, treatment=ant_treatment,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# egg survivorship
des_Esurv.desP.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=med_t5eggs,
                              tenure=desP, treatment=ant_treatment)

des_Esurv.desP.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=desP, treatment=ant_treatment,
              survNom=n_survived, survDen=med_t5eggs,
              model = des_Esurv.desP.ant_treatment.quad.fits$mai.qb)

des_Esurv.desP.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Esurv.desP.ant_treatment.quad.qb.ci, 
                                  tenure=desP, treatment=ant_treatment,
             survNom = n_survived, survDen = med_t5eggs) +
    xlab("Latest desertion date from plant\nrelative to hatch") +
    ylab("Survivorship of eggs\n(5th instars/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

(desP.ant_treatment.quad.qb.p <- egg::ggarrange(des_hatch.desP.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desP.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Esurv.desP.ant_treatment.quad.qb.p+
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

ggsave("desP.ant_treatment.quad.final.png",
       desP.ant_treatment.quad.qb.p,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

## Tables
don't need to include the data summary in supp, since the only thing that changes is the median (IQR) for desertion
```{r}
(surv_reg_data.tbl_summary.desP.ant_treatment <- surv_reg_data %>%
  mutate(ants = ifelse(ant_treatment==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `plant desert date rel. hatch` = desP,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `plant desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

surv_reg_data.tbl_summary.desP.ant_treatment %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv_reg_data.tbl_summary.desP.ant_treatment.docx")
```

```{r}
hatch.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ant_treatment.quad.fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

(desP.ant_treatment.quad.qb.tbl.merge <- 
  tbl_merge(
    tbls = list(hatch.desP.ant_treatment.quad.qb.tbl, 
                Nsurv.desP.ant_treatment.quad.qb.tbl, 
                Esurv.desP.ant_treatment.quad.qb.tbl),
    tab_spanner = c("**Hatching success**", 
                    "**Survivorship of nymphs**", 
                    "**Survivorship of eggs**")
  ) %>%
  modify_header(label = "**Variable**") %>%
  bold_labels() %>% italicize_levels())

desP.ant_treatment.quad.qb.tbl.merge %>%
  as_flex_table() %>%
  flextable::save_as_docx(path="surv.reg_summary.desP.ant_treatment.quad.docx")
```

# qAICc
```{r}
# qAICc into separate tables
# qaicc
(qAICc_gt_tbl_hatch_quad <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Hatching success",4)),
  qAICc = c(
    get_qaicc(des_hatch.desL.ant_treatment.quad.fits),
    get_qaicc(des_hatch.desP.ant_treatment.quad.fits),
    get_qaicc(des_hatch.desL.ants_gt2d.quad.fits),
    get_qaicc(des_hatch.desP.ants_gt2d.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))

(qAICc_gt_tbl_Nsurv_quad <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Nymph survivorship",4)),
  qAICc = c(
    get_qaicc(des_Nsurv.desL.ant_treatment.quad.fits),
    get_qaicc(des_Nsurv.desP.ant_treatment.quad.fits),
    get_qaicc(des_Nsurv.desL.ants_gt2d.quad.fits),
    get_qaicc(des_Nsurv.desP.ants_gt2d.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))

(qAICc_gt_tbl_hatch_quad <- tibble(
  Model = c("desert leaf + ant treatment + desert leaf*ant treatment + 
            desert leaf^2 + desert leaf^2*ant treatment",
            "desert plant + ant treatment + desert plant*ant treatment + 
            desert plant^2 + desert plant^2*ant treatment",
            "desert leaf + ants >2days + desert leaf*ants >2days + 
            desert leaf^2 + desert leaf^2*ants >2days",
            "desert plant + ants >2days + desert plant*ants >2days + 
            desert plant^2 + desert plant^2*ants >2days"),
  Response = c(rep("Egg survivorship",4)),
  qAICc = c(
    get_qaicc(des_Esurv.desL.ant_treatment.quad.fits),
    get_qaicc(des_Esurv.desP.ant_treatment.quad.fits),
    get_qaicc(des_Esurv.desL.ants_gt2d.quad.fits),
    get_qaicc(des_Esurv.desP.ants_gt2d.quad.fits))
  ) %>% 
  arrange(qAICc) %>%
  mutate('delta-qAICc' = qAICc - first(qAICc)) %>%
  gt() %>%
  fmt_number(columns=c(`qAICc`, `delta-qAICc`), decimals=2))
```

## Stats interpretation
```{r}
# function to get fits and confint
ci_for_stats <- function(data_in, model){

  data <- eval(substitute(
    data_in %>%
      add_column(fit = predict(model, newdata = ., type = 'response'))
    ))

  ## grad the inverse link function
  ilink <- family(model)$linkinv

  ## add fit and se.fit on the **link** scale
  data_fit_link <- eval(substitute(
    data %>% add_column(
  setNames(as_tibble(predict(model, data, se.fit = TRUE)[1:2]),
           c('fit_link','se_link'))) %>%
## create the interval and backtransform
  mutate(fit_resp  = ilink(fit_link),
         conf_upr = ilink(fit_link + (2 * se_link)),
         conf_lwr = ilink(fit_link - (2 * se_link)))
    ))

  return(data_fit_link)
}

# function to get max fit, plus upper and lower ci
get_max_fit <- function(data_in, model){

  max_fit <- eval(substitute(ci_for_stats(data_in=data_in, 
             model) %>%
  group_by(ant_treatment) %>%
  mutate(max = max(fit)) %>% filter(fit==max) %>% 
    select(ant_treatment, des, max)))

  max_upr <- eval(substitute(ci_for_stats(data_in=data_in, 
             model) %>%
  group_by(ant_treatment) %>%
  mutate(max_upr = max(conf_upr)) %>% filter(conf_upr==max_upr) %>% 
    select(ant_treatment, des_upr=des, max_upr)))

  max_lwr <- eval(substitute(ci_for_stats(data_in=data_in, 
             model) %>%
  group_by(ant_treatment) %>%
  mutate(max_lwr = max(conf_lwr)) %>% filter(conf_lwr==max_lwr) %>% 
    select(ant_treatment, des_lwr=des, max_lwr)))

  data_out <- max_fit %>% left_join(max_upr) %>% left_join(max_lwr)
  return(data_out)
}

## Hatch
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_hatch.desL.ant_treatment.quad.fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_hatch.desL.ant_treatment.quad.fits$mai.qb)

# Nsurv
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)

# Esurv
# at -20,0,10 etc.
ci_for_stats(data_in=
               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
                      des=rep(c(-20,10,0,10,20),2)), 
             des_Esurv.desL.ant_treatment.quad.fits$mai.qb)

# where is the maximum?
get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
                           des=rep(seq(-20,20,length.out=10000),2)),
            model=des_Esurv.desL.ant_treatment.quad.fits$mai.qb)
```

# Figures for FPO

## Figures
### Both colors
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment)

des_hatch.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ant_treatment,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ant_treatment.quad.fits$mai.qb)

des_hatch.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ant_treatment)

des_Nsurv.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ant_treatment,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ant_treatment.quad.fits$mai.qb)

des_Nsurv.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

(FPO_desL.ant_treatment_allCols <- egg::ggarrange(des_hatch.desL.ant_treatment.quad.qb.p+
                 theme(legend.position="none"),
               des_Nsurv.desL.ant_treatment.quad.qb.p+
                 theme(legend.position="none")))

ggsave("FPO_desL.ant_treatment_allCols.png",
       FPO_desL.ant_treatment_allCols,
       device="png", width = 150, height = 200, units = "mm", dpi = "print")
```

### Black only
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad.qb.p_blackOnly <- 
  ggplot(data = filter(des_hatch.desL.ant_treatment.quad.qb.ci,
                       ant_treatment=="Removed"), 
       aes(x = des, y = fit), 
           color = "black", fill = "black") +
    theme_publilia() +
    geom_point(aes(y = n_hatched/med_t5eggs), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.5, color = NA, key_glyph=draw_key_rect) +
      xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)")

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad.qb.p_blackOnly <- 
  ggplot(data = filter(des_Nsurv.desL.ant_treatment.quad.qb.ci,
                       ant_treatment=="Removed"), 
       aes(x = des, y = fit), 
           color = "black", fill = "black") +
    theme_publilia() +
    geom_point(aes(y = n_survived/n_hatched), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.5, color = NA, key_glyph=draw_key_rect) +
  xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)")

(FPO_desL.ant_treatment_blackOnly <- egg::ggarrange(des_hatch.desL.ant_treatment.quad.qb.p_blackOnly+
                 theme(legend.position="none"),
               des_Nsurv.desL.ant_treatment.quad.qb.p_blackOnly+
                 theme(legend.position="none")))

ggsave("FPO_desL.ant_treatment_blackOnly.png",
       FPO_desL.ant_treatment_blackOnly,
       device="png", width = 150, height = 200, units = "mm", dpi = "print")
```

hatching success
```{r}
# hatching success
des_hatch.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ants_gt2d)

des_hatch.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ants_gt2d.quad.fits$mai.qb)

des_hatch.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

plot_ci(ci_data=filter(des_hatch.desL.ants_gt2d.quad.qb.ci, 
                       ants_gt2d ), 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

```

nymph survivorship
```{r}
# nymph survivorship
des_Nsurv.desL.ants_gt2d.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ants_gt2d)

des_Nsurv.desL.ants_gt2d.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data_LastDesPlant, 
              tenure=des, treatment=ants_gt2d,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ants_gt2d.quad.fits$mai.qb)

des_Nsurv.desL.ants_gt2d.quad.qb.p <- plot_ci(ci_data=des_Nsurv.desL.ants_gt2d.quad.qb.ci, 
                                  tenure=des, treatment=ants_gt2d,
             survNom = n_survived, survDen = n_hatched) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Survivorship of nymphs\n(5th instars/nymphs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))
```

### 2023-08-24 scripts/old/Publilia_2019_CHAPTER-4-ants.Rmd
added old scripts to `scripts/old/` for reference

---
title: "Publilia_2019_CHAPTER-4-ants"
author: "micah fletcher"
date: "3/2/2022"
output: html_document
---

# Ant counts on plant; some ants_removed clutches were visited by ants, and vice versa
```{r}
ant_counts <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch) %>%
    summarize(ants_removed=first(ants_removed),
              females_removed=first(females_removed),
              n_antsP=sum(ants_P,na.rm=T),
              mean_antsP=mean(ants_P,na.rm=T),
              med_antsP=median(ants_P,na.rm=T),
              ever_antsP=n_antsP>0,
              n_days_antsP=sum(ants_P>0,na.rm=T),

              n_antsP_b4h=sum(ants_P&b4h),
              ever_antsP_b4h=n_antsP_b4h>0,
              mean_antsP_b4h=mean(ifelse(b4h,ants_P,NA),na.rm=T),
              med_antsP_b4h=median(ifelse(b4h,ants_P,NA),na.rm=T),

              n_antsP_afh=sum(ants_P&afh),
              ever_antsP_afh=n_antsP_afh>0,
              mean_antsP_afh=mean(ifelse(afh,ants_P,NA),na.rm=T),
              med_antsP_afh=median(ifelse(afh,ants_P,NA),na.rm=T)) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

ggplot(data=ant_counts,aes(x=Dorm,y=n_antsP, fill=ants_treatment)) +
  geom_boxplot()

ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP, fill=ants_treatment)) +
  geom_boxplot()

ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_b4h, fill=ants_treatment)) +
  geom_boxplot()

ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_afh, fill=ants_treatment)) +
  geom_boxplot()

ant_counts %>%
  count(Dorm,ants_treatment,ever_antsP)

ant_counts %>%
  count(Dorm,ants_treatment,ever_antsP_b4h)

ant_counts %>%
  count(Dorm,ants_treatment,ever_antsP_afh)

# how many clutches ever had ants in each of the dorms?
ant_counts %>%
  ggplot(data=., aes(y=as.numeric(ever_antsP), x=Dorm, fill=ants_treatment)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
  theme_publilia()

ant_counts %>%
  ggplot(data=., aes(y=as.numeric(ever_antsP_b4h), x=Dorm, fill=ants_treatment)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
  theme_publilia()

ant_counts %>%
  ggplot(data=., aes(y=as.numeric(ever_antsP_afh), x=Dorm, fill=ants_treatment)) +
  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
  theme_publilia()

# how long/extensive was the break-through?
ant_counts %>%
  ggplot(data=., aes(x=n_days_antsP)) +
  geom_histogram() +
  theme_publilia() + facet_wrap(~ants_treatment, nrow=2)
```

ant arrival times
```{r}
antP_arrival_afh_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&(Date<est_hatch),
           afh=Date>=est_hatch,
           is_antsP_afh=(ants_P>0)&afh) %>%
    filter(is_antsP_afh) %>%
    slice_head(n=1) %>% 
  mutate(antP_arrival_afh=Date-est_hatch) %>%
  select(location, antP_arrival_afh, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antP_last_b4h_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&(Date<est_hatch),
           afh=Date>=est_hatch,
           is_antsP_bfh=(ants_P>0)&b4h) %>%
    filter(is_antsP_bfh) %>%
    slice_tail(n=1) %>% 
  mutate(antP_last_b4h=Date-est_hatch) %>%
  select(location, antP_last_b4h, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antL_arrival_afh_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&(Date<est_hatch),
           afh=Date>=est_hatch,
           is_antsL_afh=(ants_L>0)&afh) %>%
    filter(is_antsL_afh) %>%
    slice_head(n=1) %>% 
  mutate(antL_arrival_afh=Date-est_hatch) %>%
  select(location, antL_arrival_afh, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antL_last_b4h_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&(Date<est_hatch),
           afh=Date>=est_hatch,
           is_antsL_bfh=(ants_L>0)&b4h) %>%
    filter(is_antsL_bfh) %>%
    slice_tail(n=1) %>% 
  mutate(antL_last_b4h=Date-est_hatch) %>%
  select(location, antL_last_b4h, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

ant_data <- ant_counts %>%
  left_join(antP_last_b4h_data) %>%
  left_join(antP_arrival_afh_data) %>%
  left_join(antL_last_b4h_data) %>%
  left_join(antL_arrival_afh_data)

ant_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  select(location, ants_removed, females_removed, antL_arrival_afh)

ant_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  ggplot(data=., aes(x=antL_arrival_afh)) +
  geom_histogram()

```

There is no relationship between when ants arrive and hatching success or nymph survivial
```{r}
## No relationship between when ants arrive and hatching success or nymph survivial
ant_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  ggplot(data=., aes(x=antL_arrival_afh, y=n_hatched/med_t5eggs)) +
  geom_point()

ant_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  ggplot(data=., aes(x=antL_arrival_afh, y=n_survived/n_hatched)) +
  geom_point()
```

# plotting all ant counts over time
- Was ant exclusion effective in eliminating ants? Reducing ants?
- Are there any criteria for changing which clutches should be considered as "with ants" vs. "without ants"?
- How can I demonstrate a causal arrow from moms -> ants rather than the other way?
- Is there any way to predict maternal behavior based on ant attendance?
- Can I decouple ant attendance and maternal care to predict survivorship?
```{r}
# when were the break-through events?
ants_days_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(n_antsP=sum(ants_P,na.rm=T),
           mean_antsP=mean(ants_P,na.rm=T),
           med_antsP=median(ants_P,na.rm=T),
           ever_antsP=n_antsP>0,
           n_days_antsP=sum(ants_P>0,na.rm=T)) %>% ungroup() %>%
  arrange(desc(n_antsP))
```

```{r}
##### Ants on plant
# date-est_hatch, ordered by last_desertion date rel to hatch
(ant_days_p1 <- ants_days_data %>% # ants control, females control
  right_join(latest_desertions) %>%
  filter(!ants_removed, !females_removed) %>%
  mutate(ants_P=ifelse(ants_P==0,NA,ants_P)) %>%
ggplot(data=, aes(y=reorder(location,desc(last_des_rel2h)),x=Date-est_hatch, color=ants_P)) +
  geom_point(size=0.25) +
  geom_point(aes(y=reorder(location,desc(last_des_rel2h)), x=last_des_rel2h+1), shape=4, size=0.75, color="black") +
  scale_colour_distiller(name = "n ants on plant", na.value="grey95", 
                         breaks=c(1,2,4,8,16,32,64), limits=c(1,64),
                         palette="Oranges", direction=+1, trans="log") +
  theme_classic() +
  theme(axis.line.y = element_blank(),
        axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank()) +
  xlim(-40,60) +
  xlab("Date relative to hatch"))

# *** this one demonstrates how removing mothers leads to fewer ants on the plant
# but how can I show this statistically?
(ant_days_p2 <- ants_days_data %>%  # ants control, females removed
  right_join(latest_desertions) %>%
  filter(!ants_removed, females_removed) %>%
  mutate(ants_P=ifelse(ants_P==0,NA,ants_P)) %>%
ggplot(data=, aes(y=reorder(location,desc(last_des_rel2h)),x=Date-est_hatch, color=ants_P)) +
  geom_point(size=0.25) +
  geom_point(aes(y=reorder(location,desc(last_des_rel2h)), x=last_des_rel2h+1), shape=4, size=0.75, color="black") +
  scale_colour_distiller(name = "n ants on plant", na.value="grey95", 
                         breaks=c(1,2,4,8,16,32,64), limits=c(1,64),
                         palette="Oranges", direction=+1, trans="log") +
  theme_classic() +
  theme(axis.line.y = element_blank(),
        axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank()) +
  xlim(-40,60) +
  xlab("Date relative to hatch"))

(ant_days_p3 <- ants_days_data %>% # ants removed, females control
  right_join(latest_desertions) %>%
  filter(ants_removed, !females_removed) %>%
  mutate(ants_P=ifelse(ants_P==0,NA,ants_P)) %>%
ggplot(data=, aes(y=reorder(location,desc(last_des_rel2h)),x=Date-est_hatch, color=ants_P)) +
  geom_point(size=0.25) +
  geom_point(aes(y=reorder(location,desc(last_des_rel2h)), x=last_des_rel2h+1), shape=4, size=0.75, color="black") +
  scale_colour_distiller(name = "n ants on plant", na.value="grey95", 
                         breaks=c(1,2,4,8,16,32,64), limits=c(1,64),
                         palette="Oranges", direction=+1, trans="log") +
  theme_classic() +
  theme(axis.line.y = element_blank(),
        axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank()) +
  xlim(-40,60) +
  xlab("Date relative to hatch"))

(ant_days_p4 <- ants_days_data %>% # ants removed, females removed
  right_join(latest_desertions) %>%
  filter(ants_removed, females_removed) %>%
  mutate(ants_P=ifelse(ants_P==0,NA,ants_P)) %>%
ggplot(data=, aes(y=reorder(location,desc(last_des_rel2h)),x=Date-est_hatch, color=ants_P)) +
  geom_point(size=0.25) +
  geom_point(aes(y=reorder(location,desc(last_des_rel2h)), x=last_des_rel2h+1), shape=4, size=0.75, color="black") +
  scale_colour_distiller(name = "n ants on plant", na.value="grey95", 
                         breaks=c(1,2,4,8,16,32,64), limits=c(1,64),
                         palette="Oranges", direction=+1, trans="log") +
  theme_classic() +
  theme(axis.line.y = element_blank(),
        axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank()) +
  xlim(-40,60) +
  xlab("Date relative to hatch"))

(ant_days_plant.p.final <- ggpubr::ggarrange(labels=c("A","B","C","D"),
                  ant_days_p1, ant_days_p2, ant_days_p3, ant_days_p4,
                  ncol=2, nrow=2, common.legend=T, legend="bottom"))

# ggsave("CHAPTER/ant_days_plant.final.png",
#        ant_days_plant.p.final,
#        device = "png",
#        width = 200, height = 200, units = "mm", dpi = "print")

```

I shouldn't use ants on leaf because nymphs emigrate from the natal leaf.

These plots make me think that including females_removed in the regressions might not be appropriate, since for some reason (sampling bias?) clutches were attended more consistently in the females removal dorms than in the control dorms. You can see this from how consistently females were attended in their first several days of guarding and after hatching.

Does ant attendance in the first few days predict ant attendance after hatching better than desertion date?

Does removing females reduce the number of ants at the clutch?
```{r}
ants_before_after_p1.data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  mutate(last_des_date = est_hatch+last_des_rel2h) %>%
  filter((Date<=(last_des_date+4))&(Date>=(last_des_date-4))) %>%
  filter(Date!=(last_des_date-3), Date!=(last_des_date-1)) %>% #fix higher sampling rate before removal
  group_by(location) %>%
  filter(any((Date==(last_des_date-4)))&any(Date==(last_des_date-2))) %>% # remove any clutches where there are missing data before des
  mutate(before_after=cut(as.numeric(Date-last_des_date), 
                          breaks=c(-5,-3,-1,0,2,4), labels=c("-4","-2","0","2","4"))) %>%
  ungroup()

(ants_before_after_p1.p <- ants_before_after_p1.data  %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"unattended","attended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after female removal") +
  ylab("Proportion of clutches") +
  xlab("Days since female removal"))

table(mutate(ants_before_after_p1.data, ants=ants_L>0)$ants,
        ants_before_after_p1.data$before_after)

table(mutate(ants_before_after_p1.data, ants=ants_L>0)$ants,
        ants_before_after_p1.data$before_after) %>%
  chisq.test()
```

Do ants come back at hatch after removing females?
```{r}
ants_before_after_p2.data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  filter((Date<=(est_hatch+4))&(Date>=(est_hatch-4))) %>%
  filter(Date!=(est_hatch-3), Date!=(est_hatch-1)) %>% #fix higher sampling rate before removal
  group_by(location) %>%
  filter(any((Date==(est_hatch-4)))&any(Date==(est_hatch-2))) %>% # remove any clutches where there are missing data before des
  mutate(before_after=cut(as.numeric(Date-est_hatch), 
                          breaks=c(-5,-3,-1,0,2,4), labels=c("-4","-2","0","2","4"))) %>%
  ungroup()

(ants_before_after_p2.p <- ants_before_after_p2.data %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"unattended","attended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after hatching (females removed)") +
  ylab("Proportion of clutches") +
  xlab("Days since hatch"))

table(mutate(ants_before_after_p2.data, ants=ants_L>0)$ants,
        ants_before_after_p2.data$before_after)

table(mutate(ants_before_after_p2.data, ants=ants_L>0)$ants,
        ants_before_after_p2.data$before_after) %>%
  chisq.test()
```

How do different relative desertion times affect how likely a clutch is to be attended in the days before and after hatch?
```{r}
# desert, eggs, nymphs
ants_before_after_p3.data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed, last_des_rel2h<=-4) %>%
  filter((Date<=(est_hatch+4))&(Date>=(est_hatch-4))) %>%
  group_by(location) %>%
  filter(any((Date==(est_hatch-4)))&any(Date==(est_hatch-2))) %>% # remove any clutches where there are missing data before des
  mutate(before_after=cut(as.numeric(Date-est_hatch), 
                          breaks=c(-5,-3,-1,0,2,4), labels=c("-4","-2","0","2","4"))) %>%
  ungroup()

(ants_before_after_p3.p <- ants_before_after_p3.data %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"unattended","attended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after hatching (last desert early)") +
  ylab("Proportion of clutches") +
  xlab("Days since hatch"))

table(mutate(ants_before_after_p3.data, ants=ants_L>0)$ants,
        ants_before_after_p3.data$before_after)

table(mutate(ants_before_after_p3.data, ants=ants_L>0)$ants,
        ants_before_after_p3.data$before_after) %>%
  chisq.test()

(ants_before_after_p4 <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed, last_des_rel2h>-4, last_des_rel2h<=4) %>%
  group_by(location) %>%
  filter((Date<=(est_hatch+4))&(Date>=(est_hatch-4))) %>%
  mutate(last_des_date = est_hatch+last_des_rel2h,
         before_after=cut(as.numeric(Date-last_des_date), 
                          breaks=c(-5,-3,-1,0,2,4), labels=c("-4","-2","0","2","4"))) %>%
  ungroup() %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"unattended","attended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after hatching (last desert eggs)") +
  ylab("Proportion of clutches") +
  xlab("Days since hatch"))

(ants_before_after_p5 <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed, last_des_rel2h>4) %>%
  group_by(location) %>%
  filter((Date<=(est_hatch+4))&(Date>=(est_hatch-4))) %>%
  mutate(last_des_date = est_hatch+last_des_rel2h,
         before_after=cut(as.numeric(Date-last_des_date), 
                          breaks=c(-5,-3,-1,0,2,4), labels=c("-4","-2","0","2","4"))) %>%
  ungroup() %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"unattended","attended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after hatching (last desert nymphs)") +
  ylab("Proportion of clutches") +
  xlab("Days since hatch"))
```
FUUUUUUUUCKKKKK!!!!!!!!!!!!
Removing a mother results in a decrease in the probability of the clutch being attended by ants in the four days following removal ().
```{r}
ants_before_after_p1.data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  mutate(last_des_date = est_hatch+last_des_rel2h) %>%
  filter((Date<=(last_des_date+4))&(Date>=(last_des_date-2))) %>%
  filter(Date!=(last_des_date-3), Date!=(last_des_date-1)) %>% #fix higher sampling rate before removal
  group_by(location) %>%
  filter(any(Date==(last_des_date-2))) %>% # remove any clutches where there are missing data before des
  mutate(before_after=cut(as.numeric(Date-last_des_date), 
                          breaks=c(-3,0,4), labels=c("4 days before removal", "4 days after removal"))) %>%
  ungroup() %>%
  select(location,Date, last_des_date, before_after, ants_L)

(ants_before_after_p1.p <- ants_before_after_p1.data  %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"attended","unattended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after female removal") +
  ylab("Proportion of clutches"))

table(mutate(ants_before_after_p1.data, ants=ants_L>0)$ants,
        ants_before_after_p1.data$before_after)

table(mutate(ants_before_after_p1.data, ants=ants_L>0)$ants,
        ants_before_after_p1.data$before_after) %>%
  fisher.test()
```

But hatching leads to a relative increase in the likelihood of being attended by ants (although not all clutches are attended).
```{r}
ants_before_after_p2.data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  filter((Date<=(est_hatch+2))&(Date>=(est_hatch-4))) %>%
  filter(Date!=(est_hatch-3), Date!=(est_hatch-1)) %>% #fix higher sampling rate before removal
  group_by(location) %>%
  filter(any((Date==(est_hatch-4)))&any(Date==(est_hatch-2))) %>% # remove any clutches where there are missing data before des
  mutate(before_after=cut(as.numeric(Date-est_hatch), 
                          breaks=c(-5,0,2), labels=c("4 days before hatch", "4 days after hatch"))) %>%
  ungroup() %>%
  select(location,Date, est_hatch, before_after, ants_L)

(ants_before_after_p2.p <- ants_before_after_p2.data  %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"attended","unattended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after hatching (females removed)") +
  ylab("Proportion of clutches"))

table(mutate(ants_before_after_p2.data, ants=ants_L>0)$ants,
        ants_before_after_p2.data$before_after)

table(mutate(ants_before_after_p2.data, ants=ants_L>0)$ants,
        ants_before_after_p2.data$before_after) %>%
  fisher.test()
```

early deserter have low chance of being visited by ants in the 4 days before and after hatching (25% across the board)
```{r}
# desert, eggs, nymphs
ants_before_after_p3.data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed, last_des_rel2h<=-4) %>%
  filter((Date<=(est_hatch+2))&(Date>=(est_hatch-4))) %>%
  filter(Date!=(est_hatch-3), Date!=(est_hatch-1)) %>% #fix higher sampling rate before removal
  group_by(location) %>%
  filter(any((Date==(est_hatch-4)))&any(Date==(est_hatch-2))) %>% # remove any clutches where there are missing data before des
  mutate(before_after=cut(as.numeric(Date-est_hatch), 
                          breaks=c(-5,0,2), labels=c("4 days before hatch", "4 days after hatch"))) %>%
  ungroup() %>%
  select(location,Date, est_hatch, before_after, ants_L)

(ants_before_after_p3.p <- ants_before_after_p3.data %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"attended","unattended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after hatching (last desert early)") +
  ylab("Proportion of clutches") +
  xlab("Days since hatch"))

table(mutate(ants_before_after_p3.data, ants=ants_L>0)$ants,
        ants_before_after_p3.data$before_after)

table(mutate(ants_before_after_p3.data, ants=ants_L>0)$ants,
        ants_before_after_p3.data$before_after) %>%
  chisq.test()
```

egg guarders have high chance of being visited by ants (about 60% across the board)
```{r}
ants_before_after_p4.data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed, last_des_rel2h>-4, last_des_rel2h<=4) %>%
  filter((Date<=(est_hatch+2))&(Date>=(est_hatch-4))) %>%
  filter(Date!=(est_hatch-3), Date!=(est_hatch-1)) %>% #fix higher sampling rate before removal
  group_by(location) %>%
  filter(any((Date==(est_hatch-4)))&any(Date==(est_hatch-2))) %>% # remove any clutches where there are missing data before des
  mutate(before_after=cut(as.numeric(Date-est_hatch), 
                          breaks=c(-5,0,2), labels=c("4 days before hatch", "4 days after hatch"))) %>%
  ungroup() %>%
  select(location,Date, est_hatch, before_after, ants_L)

(ants_before_after_p4.p <- ants_before_after_p4.data %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"attended","unattended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after hatching (last desert early)") +
  ylab("Proportion of clutches") +
  xlab("Days since hatch"))

table(mutate(ants_before_after_p4.data, ants=ants_L>0)$ants,
        ants_before_after_p4.data$before_after)

table(mutate(ants_before_after_p4.data, ants=ants_L>0)$ants,
        ants_before_after_p4.data$before_after) %>%
  chisq.test()
```

nymph guarders have low chance of being visited by ants at or after hatching (20%), but not worse on the 4th day before hatching (50%)
```{r}
ants_before_after_p5.data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed, last_des_rel2h>4) %>%
  filter((Date<=(est_hatch+2))&(Date>=(est_hatch-4))) %>%
  filter(Date!=(est_hatch-3), Date!=(est_hatch-1)) %>% #fix higher sampling rate before removal
  group_by(location) %>%
  filter(any((Date==(est_hatch-4)))&any(Date==(est_hatch-2))) %>% # remove any clutches where there are missing data before des
  mutate(before_after=cut(as.numeric(Date-est_hatch), 
                          breaks=c(-5,0,2), labels=c("4 days before hatch", "4 days after hatch"))) %>%
  ungroup() %>%
  select(location,Date, est_hatch, before_after, ants_L)

(ants_before_after_p5.p <- ants_before_after_p5.data %>%
  count(before_after, ants_L>0) %>%
  ggplot(data=., aes(x=before_after, y=n, fill=ifelse(`ants_L > 0`,"attended","unattended"))) +
  geom_col(position="fill") +
  ggtitle("Ants before and after hatching (last desert early)") +
  ylab("Proportion of clutches") +
  xlab("Days since hatch"))

table(mutate(ants_before_after_p5.data, ants=ants_L>0)$ants,
        ants_before_after_p5.data$before_after)

table(mutate(ants_before_after_p5.data, ants=ants_L>0)$ants,
        ants_before_after_p5.data$before_after) %>%
  chisq.test()
```

Clutches guarded until hatching were more likely to be attended by ants within the first 4 days after hatching than those deserted early (Fisher's Exact Test p = 0.008, odds ratio = 3.988299).
```{r}
ants_before_after.data.eggs.afterH <- ants_before_after_p3.data %>%
  filter(before_after == "4 days after hatch") %>%
  mutate(ants=ifelse(ants_L>0, "attended","unattended"), desert="eggs")

ants_before_after.data.early.afterH <- ants_before_after_p4.data %>%
  filter(before_after == "4 days after hatch") %>%
  mutate(ants=ifelse(ants_L>0, "attended","unattended"), desert="early")

ants_before_after.data.eggsVSearly <- rbind(ants_before_after.data.eggs.afterH,ants_before_after.data.early.afterH)

(ants_before_after.eggsVSearly.p <- ants_before_after.data.eggsVSearly %>%
  count(desert, ants) %>%
  ggplot(data=., aes(x=desert, y=n, fill=ants)) +
  geom_col(position="fill") +
  ggtitle("Ants before and after hatching (last desert early)") +
  ylab("Proportion of clutches") +
  xlab("Days since hatch"))

table(ants_before_after.data.eggsVSearly$desert, ants_before_after.data.eggsVSearly$ants)

table(ants_before_after.data.eggsVSearly$desert, ants_before_after.data.eggsVSearly$ants) %>%
  fisher.test()
```

Using beta regression to do the same as above: How does the probability of being attended by ants change from the 4 days before the females is removed to the 4 days after?
```{r}
library(effects)

B4orAF_fem_data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  select(location, Date, est_hatch, last_des_rel2h, ants_P) %>%
  mutate(last_des_date=est_hatch+last_des_rel2h,
         B4orAF_fem=ifelse((Date<=(last_des_date+4))&(Date>last_des_date), "4 after",
                             ifelse((Date>=(last_des_date-2))&(Date<=last_des_date), "4 before",
                                    NA))) %>%
  filter(!is.na(B4orAF_fem)) %>%
  #fix higher sampling rate before removal
  filter(Date!=(last_des_date-3), Date!=(last_des_date-1)) %>%
  group_by(location, B4orAF_fem) %>%
    summarize(any_antsP = as.numeric(any(ants_P)),
              n = n()) %>%
  ungroup()# %>% 
  #filter(n==2) # 4 clutches had too few/many obs bc females deserted before I removed them

table(B4orAF_fem_data$B4orAF_fem, B4orAF_fem_data$any_antsP)

B4orAF_fem.m <- glm(any_antsP ~ B4orAF_fem, data=B4orAF_fem_data, family="binomial")
summary(B4orAF_fem.m)
coef(B4orAF_fem.m) # log-odds ratio
confint(B4orAF_fem.m) # log-odds ratio 95% confint
exp(coef(B4orAF_fem.m)) # odds ratio, i.e. "the odds of being visited by ants 23 times higher after female removal than before"
exp(confint(B4orAF_fem.m)) # odds ratio 95% confint: 8.4071654 75.7673129

B4orAF_fem.predict <- predict(B4orAF_fem.m, 
                              data.frame(any_antsP=c(TRUE,FALSE),B4orAF_fem=c("4 before", "4 after")),
                              type="response", se.fit=TRUE)
# prob of ants visiting before mother removed
B4orAF_fem.predict$fit[1] # 88%
B4orAF_fem.predict$fit[1]+B4orAF_fem.predict$se.fit[1]*1.96 # 95% confint upper: 97%
B4orAF_fem.predict$fit[1]-B4orAF_fem.predict$se.fit[1]*1.96 # 95% confint lower: 79%
# prob of ants visiting after mother removed
B4orAF_fem.predict$fit[2] # 23%
B4orAF_fem.predict$fit[2]+B4orAF_fem.predict$se.fit[2]*1.96 # 95% confint upper: 36%
B4orAF_fem.predict$fit[2]-B4orAF_fem.predict$se.fit[2]*1.96 # 95% confint lower: 11%

# png("CHAPTER/FigS1_B4orAF_fem.m.e.p.png", width=250, height=300)
# plot(allEffects(B4orAF_fem.m, residuals=T))
# dev.off()

## same dataset (ants control, female removal) but testing effect of hatching on prob of ant attendance
B4orAF_hatch_data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed, !is.na(hatch_date)) %>% # only interested in clutch that truly hatched
  select(location, Date, hatch_date, last_des_rel2h, ants_P) %>%
  mutate(B4orAF_hatch=ifelse((Date<=(hatch_date+3))&(Date>=hatch_date), "4 days after hatch",
                             ifelse((Date>=(hatch_date-4))&(Date<hatch_date), "4 days before hatch",
                                    NA))) %>%
  filter(!is.na(B4orAF_hatch)) %>%
  group_by(location, B4orAF_hatch) %>%
    summarize(any_antsP = as.numeric(any(ants_P)),
              n = n()) %>%
  ungroup()

table(B4orAF_hatch_data$any_antsP, B4orAF_hatch_data$B4orAF_hatch)

B4orAF_hatch.m <- glm(any_antsP ~ B4orAF_hatch, data=B4orAF_hatch_data, family="binomial")
summary(B4orAF_hatch.m)
coef(B4orAF_hatch.m) # log-odds ratio
confint(B4orAF_hatch.m) # log-odds ratio 95% confint
exp(coef(B4orAF_hatch.m)) # odds ratio, i.e. "the odds of being visited by ants was 11% higher after hatching than before"
exp(confint(B4orAF_hatch.m)) # odds ratio 95% confint: 8.4071654 75.7673129

B4orAF_hatch.predict <- predict(B4orAF_hatch.m, 
                              data.frame(B4orAF_hatch=c("4 days before hatch", "4 days after hatch")),
                              type="response", se.fit=TRUE)
# prob of ants visiting before hatch
B4orAF_hatch.predict$fit[1] # 8.1%
B4orAF_hatch.predict$fit[1]+B4orAF_hatch.predict$se.fit[1]*1.96 # 95% confint upper: 17%
B4orAF_hatch.predict$fit[1]-B4orAF_hatch.predict$se.fit[1]*1.96 # 95% confint lower: -0.7% = 0%
# prob of ants visiting after hatch
B4orAF_hatch.predict$fit[2] # 48.6%
B4orAF_hatch.predict$fit[2]+B4orAF_hatch.predict$se.fit[2]*1.96 # 95% confint upper: 65%
B4orAF_hatch.predict$fit[2]-B4orAF_hatch.predict$se.fit[2]*1.96 # 95% confint lower: 33%

# png("CHAPTER/FigS2_B4orAF_hatch.m.e.png", width=250, height=300)
# plot(allEffects(B4orAF_hatch.m, residuals=T))
# dev.off()
```

I've been doing binomial regression for this, but is that necessary/appropriate?
Is there a significant drop in the probability of ants visiting a clutch after female removal?
Before and after data are not independent! They should be paired.
"Exact McNemar's Test (with central confidence intervals)", report odds ratio as effect size
```{r}
library(exact2x2)

B4orAF_fem_paired <- B4orAF_fem_data %>%
  pivot_wider(id_cols = location,
              names_from = B4orAF_fem,
              values_from = any_antsP) %>%
  select(location, before=`4 before`, after=`4 after`)

B4orAF_fem_paired %>%
  count(before, after)

B4orAF_fem_paired %>%
  count(before, after) %>%
  pivot_wider(names_from = after,
              names_prefix = "after_",
              values_from = n,
              values_fill = 0) # fill empty cells with '0'

mcnemar.exact(B4orAF_fem_paired$before, B4orAF_fem_paired$after) 
# p-value = 1.164e-10; odds ratio = 0

### after hatch
B4orAF_hatch_paired <- B4orAF_hatch_data %>%
  pivot_wider(id_cols = location,
              names_from = B4orAF_hatch,
              values_from = any_antsP) %>%
  select(location, before=`4 days before hatch`, after=`4 days after hatch`)

B4orAF_hatch_paired %>%
  count(before, after)

B4orAF_hatch_paired %>%
  count(before, after) %>%
  pivot_wider(names_from = after,
              names_prefix = "after_",
              values_from = n,
              values_fill = 0) # fill empty cells with '0'

mcnemar.exact(B4orAF_hatch_paired$before, B4orAF_hatch_paired$after) 
# p-value = 6.104e-05; odds ratio = Inf
```

In the control trial, all females that visited a clutch deserted before hatching but ants were sometimes nonetheless observed on the plant before the deserted clutch hatched. If freely moving females can make desertion decisions that minimize the chances of their eggs going unattended – for example, deserting only when other females are present on the plant and likely to remain after the deserting mother has left, or only deserting early if laying additional clutches on the same plant – then we would expect the drop in the probability of ants being attending before and after desertion to be lower in free-moving females that deserted on their own fruition than females that were forcibly removed. In X/X cases when the final , at least one female was present on the plant after desertion of the focal clutch and in X/X cases at least one female was present on the plant up until the focal clutch hatched.

To test this prediction, we performed another binomial regression using only the data from control trial where females deserted at least four days before hatching to estimate the probability of ants visiting in the four days leading up to desertion vs. the four days following plus an additional explanatory variable representing whether a female was present elsewhere on the plant in the four days following the desertion of the focal clutch. 
```{r}
B4orAF_fem_des_data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed, last_des_rel2h<=est_hatch-4) %>%
  select(location, Date, est_hatch, last_des_rel2h, ants_P, DormPlant) %>%
  mutate(last_des_date=est_hatch+last_des_rel2h,
         B4orAF_fem=ifelse((Date<=(last_des_date+4))&(Date>last_des_date), "4 after",
                             ifelse((Date>=(last_des_date-2))&(Date<=last_des_date), "4 before",
                                    NA))) %>%
  filter(!is.na(B4orAF_fem)) %>%
  group_by(DormPlant) %>%
    mutate(last_des_date_plant=max(last_des_date)) %>%
  ungroup() %>%
  group_by(location, B4orAF_fem) %>%
    summarize(any_momsP = first((last_des_date_plant>last_des_date)),
              any_momsP_4d = first((last_des_date_plant>last_des_date) &
                                     (last_des_date_plant>=last_des_date+4)),
              any_momsP_hatch = first((last_des_date_plant>last_des_date) &
                                        (last_des_date_plant>=est_hatch)),
              any_antsP = as.numeric(any(ants_P)),
              n = n()) %>%
  ungroup()

B4orAF_fem_des_data %>% count(B4orAF_fem, any_antsP, any_momsP)
B4orAF_fem_des_data %>% count(B4orAF_fem, any_antsP, any_momsP_4d)
B4orAF_fem_des_data %>% count(B4orAF_fem, any_antsP, any_momsP_hatch)

ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed) %>%
  distinct(DormPlant, location, est_hatch, last_des_rel2h) %>%
  mutate(last_des_date=est_hatch+last_des_rel2h) %>%
  group_by(DormPlant) %>% mutate(last_des_date_plant=max(last_des_date)) %>% ungroup() %>%
  group_by(location) %>%
    summarize(deserted_4b4h = last_des_rel2h<=-4,
              any_momsP = last_des_date_plant>last_des_date,
              any_momsP_hatch = (last_des_date_plant>last_des_date) & (last_des_date_plant>=est_hatch),
              n = n()) %>%
  ungroup() %>%
  count(deserted_4b4h, any_momsP_hatch)

# any_antsP ~ B4orAF_fem*any_momsP_4d
B4orAF_fem_des.m1 <- glm(any_antsP ~ B4orAF_fem*any_momsP_4d, data=B4orAF_fem_des_data, family="binomial")
summary(B4orAF_fem_des.m1) # ns
plot(allEffects(B4orAF_fem_des.m1, residuals=T))

# any_antsP ~ B4orAF_fem*any_momsP_hatch
B4orAF_fem_des.m2 <- glm(any_antsP ~ B4orAF_fem*any_momsP_hatch, data=B4orAF_fem_des_data, family="binomial")
summary(B4orAF_fem_des.m2) # ns
plot(allEffects(B4orAF_fem_des.m2, residuals=T))

```

```{r}
## interaction with female guarding strategy in the double control dataset?
B4orAF_hatch_data <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed) %>%
  select(location, Date, est_hatch, last_des_rel2h, ants_P) %>%
  mutate(strat=ifelse(last_des_rel2h<=-16, "desert",
                      ifelse(last_des_rel2h>-16 & last_des_rel2h<=4, "eggs",
                             ifelse(last_des_rel2h>4, "nymphs", NA))),
         B4orAF_hatch=ifelse((Date<=(est_hatch+3))&(Date>=est_hatch), "4 days after hatch",
                             ifelse((Date>=(est_hatch-4))&(Date<est_hatch), "4 days before hatch",
                                    NA))) %>%
  filter(!is.na(B4orAF_hatch)) %>%
  group_by(location, B4orAF_hatch) %>%
    summarize(strat=first(strat),
              any_antsP = as.numeric(any(ants_P)),
              n = n()) %>%
  ungroup() %>% 
  # why do two clutches have n=1?
  filter(n==2, !is.na(strat))

table(B4orAF_hatch_data$any_antsP, B4orAF_hatch_data$B4orAF_hatch, B4orAF_hatch_data$strat)

# interaction term not significant; AIC=267.8
B4orAF_hatch.mai <- glm(any_antsP ~ B4orAF_hatch*strat, data=B4orAF_hatch_data,
                      family=binomial)
summary(B4orAF_hatch.mai)
plot(allEffects(B4orAF_hatch.mai))

# without interaction term, strat=eggs becomes significant; AIC=264.73
B4orAF_hatch.ma <- glm(any_antsP ~ B4orAF_hatch+strat, data=B4orAF_hatch_data,
                      family=binomial)
summary(B4orAF_hatch.ma)
plot(allEffects(B4orAF_hatch.ma))

B4orAF_hatch.ma.e <- allEffects(B4orAF_hatch.ma)
B4orAF_hatch.ma.e$strat$model.matrix

# using predict with new data to check figure
ndata <- data.frame(B4orAF_hatch=factor(c(rep("4 days before hatch",3),rep("4 days after hatch",3))),
                    strat=factor(c("desert","eggs","nymphs")))
predict(object = B4orAF_hatch.ma, newdata = ndata, type = "response")

# drop in deviance
anova(B4orAF_hatch.mai, B4orAF_hatch.ma, test = "Chisq") # ns

# make the effect plot look better (can't figure this out, use default, try later)
# plot(allEffects(B4orAF_hatch.ma))
# #library(ggeffects)
# B4orAF_hatch.ma.pred <- ggpredict(B4orAF_hatch.ma)
# plot(B4orAF_hatch.ma.pred)
# B4orAF_hatch.ma.e.p <- plot(allEffects(B4orAF_hatch.ma))

# png("CHAPTER/B4orAF_hatch.ma.e.p.png", width=500, height=300)
# plot(allEffects(B4orAF_hatch.mai))
# dev.off()
```

## How does the presence of ants before/after hatching effect hatching success and nymph survivorship?
female removal:
hatch success ~ any ants 4 days before hatch*any ants 4 days after hatch
```{r}
B4orAF_hatch_surv_data_femrem <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, females_removed) %>%
  select(location, Date, est_hatch, last_des_rel2h, ants_L, 
         med_t5eggs, n_hatched, n_survived) %>%
  mutate(strat=ifelse(last_des_rel2h<=-16, "desert",
                      ifelse(last_des_rel2h>-16 & last_des_rel2h<=4, "eggs",
                             ifelse(last_des_rel2h>4, "nymphs", NA))),
         B4orAF_hatch=ifelse((Date<=(est_hatch+9))&(Date>=est_hatch), "10 days after hatch",
                             ifelse((Date>=(est_hatch-10))&(Date<est_hatch), "10 days before hatch",
                                    NA))) %>%
  filter(!is.na(B4orAF_hatch)) %>%
  group_by(location) %>%
    summarize(strat=first(strat),
              any_antsL_B4H=as.numeric(any(ants_L&(B4orAF_hatch=="10 days before hatch"))),
              any_antsL_AFH=as.numeric(any(ants_L&(B4orAF_hatch=="10 days after hatch"))),
              n=n(),
              med_t5eggs=first(med_t5eggs), 
              n_hatched=first(n_hatched), 
              n_survived=ifelse(first(n_survived)/first(n_hatched)>1,
                                1, first(n_survived))) %>%
  ungroup() %>% 
  # note that there are slight uneven sample sizes across clutches
  filter(!is.na(strat), !is.na(n_hatched))

ggplot(B4orAF_hatch_surv_data_femrem, 
       aes(y=n_hatched/med_t5eggs, x=interaction(any_antsL_B4H,any_antsL_AFH),
           color=interaction(any_antsL_B4H,any_antsL_AFH))) +
  geom_violin() +
  geom_jitter()

B4orAF_hatch_surv_femrem.eggs.mai <- glm(n_hatched/med_t5eggs ~ any_antsL_B4H*any_antsL_AFH,
                        data=B4orAF_hatch_surv_data_femrem,
                        family=binomial, weight=med_t5eggs)
summary(B4orAF_hatch_surv_femrem.eggs.mai)
plot(allEffects(B4orAF_hatch_surv_femrem.eggs.mai))

ggplot(B4orAF_hatch_surv_data_femrem, 
       aes(y=n_survived/n_hatched, x=interaction(any_antsL_B4H,any_antsL_AFH),
           color=interaction(any_antsL_B4H,any_antsL_AFH))) +
  geom_violin() +
  geom_jitter()

B4orAF_hatch_surv_femrem.nymphs.mai <- glm(n_survived/n_hatched ~ any_antsL_AFH*any_antsL_B4H,
                        data=B4orAF_hatch_surv_data_femrem,
                        family=binomial, weight=n_hatched)
summary(B4orAF_hatch_surv_femrem.nymphs.mai)
plot(allEffects(B4orAF_hatch_surv_femrem.nymphs.mai))

B4orAF_hatch_surv_femrem.nymphs.ma <- glm(n_survived/n_hatched ~ any_antsL_AFH+any_antsL_B4H,
                        data=B4orAF_hatch_surv_data_femrem,
                        family=binomial, weight=n_hatched)
summary(B4orAF_hatch_surv_femrem.nymphs.ma)
plot(allEffects(B4orAF_hatch_surv_femrem.nymphs.ma))
```

all data:
hatch success ~ any ants 10 days before hatch * any ants 10 days after hatch * strat
```{r}
B4orAF_hatch_surv_data_all <- ants_days_data %>% # ants removed, females removed
  left_join(clutch_survivorship_data) %>%
  select(location, Date, est_hatch, last_des_rel2h, ants_L, ants_P,
         med_t5eggs, n_hatched, n_survived) %>%
  mutate(strat=ifelse(last_des_rel2h<=-16, "desert",
                      ifelse(last_des_rel2h>-16 & last_des_rel2h<=4, "eggs",
                             ifelse(last_des_rel2h>4, "nymphs", NA))),
         B4orAF_hatch=ifelse((Date<=(est_hatch+9))&(Date>=est_hatch), "10 days after hatch",
                             ifelse((Date>=(est_hatch-10))&(Date<est_hatch), "10 days before hatch",
                                    NA))) %>%
  filter(!is.na(B4orAF_hatch)) %>%
  group_by(location) %>%
    summarize(strat=first(strat),
              any_antsP_B4H=factor(any(ants_P&(B4orAF_hatch=="10 days before hatch"))),
              any_antsP_AFH=factor(any(ants_P&(B4orAF_hatch=="10 days after hatch"))),
              n=n(),
              med_t5eggs=first(med_t5eggs), 
              n_hatched=first(n_hatched), 
              n_survived=ifelse(first(n_survived)/first(n_hatched)>1,
                                1, first(n_survived))) %>%
  ungroup() %>% 
  # note that there are slight uneven sample sizes across clutches
  filter(!is.na(strat), !is.na(n_hatched))

ggplot(B4orAF_hatch_surv_data_all, 
       aes(y=n_hatched/med_t5eggs, x=interaction(any_antsP_B4H,any_antsP_AFH),
           color=interaction(any_antsP_B4H,any_antsP_AFH))) +
  geom_boxplot() +
  geom_jitter() +
  facet_wrap(~strat)

B4orAF_hatch_surv_all.eggs.mai <- glm(n_hatched/med_t5eggs ~
                                        any_antsP_B4H*any_antsP_AFH*strat,
                        data=B4orAF_hatch_surv_data_all,
                        family=quasibinomial, weight=med_t5eggs)
summary(B4orAF_hatch_surv_all.eggs.mai)
plot(Effect(focal.predictors=c("any_antsP_B4H","any_antsP_AFH", "strat"), residuals=T,
            mod=B4orAF_hatch_surv_all.eggs.mai))
plot(Effect(focal.predictors=c("strat"), residuals=T,
            mod=B4orAF_hatch_surv_all.eggs.mai))
```

all data:
nymph survivorship ~ any ants 4 days before hatch*any ants 4 days after hatch*strat
```{r}
ggplot(B4orAF_hatch_surv_data_all, 
       aes(y=n_survived/n_hatched, x=interaction(any_antsP_B4H,any_antsP_AFH),
           color=interaction(any_antsP_B4H,any_antsP_AFH))) +
  geom_boxplot() +
  geom_jitter() +
  facet_wrap(~strat)

B4orAF_hatch_surv_all.nymphs.mai <- glm(n_survived/n_hatched ~
                                        any_antsP_B4H*any_antsP_AFH*strat,
                        data=B4orAF_hatch_surv_data_all,
                        family=quasibinomial, weight=n_hatched)
summary(B4orAF_hatch_surv_all.nymphs.mai)
plot(Effect(focal.predictors=c("any_antsP_AFH"),
            mod=B4orAF_hatch_surv_all.nymphs.mai, residuals=TRUE))
plot(Effect(focal.predictors=c("any_antsP_AFH", "strat"),
            mod=B4orAF_hatch_surv_all.nymphs.mai, residuals=TRUE))
plot(Effect(focal.predictors=c("any_antsP_B4H", "strat"),
            mod=B4orAF_hatch_surv_all.nymphs.mai, residuals=TRUE))
plot(Effect(focal.predictors=c("any_antsP_AFH", "any_antsP_B4H"),
            mod=B4orAF_hatch_surv_all.nymphs.mai, residuals=TRUE))
```

all data:
egg survivorship ~ any ants 4 days before hatch*any ants 4 days after hatch*strat
```{r}
ggplot(B4orAF_hatch_surv_data_all, 
       aes(y=n_survived/med_t5eggs, x=interaction(any_antsP_B4H,any_antsP_AFH),
           color=interaction(any_antsP_B4H,any_antsP_AFH))) +
  geom_boxplot() +
  geom_jitter() +
  facet_wrap(~strat)

B4orAF_hatch_surv_all.Esurv.mai <- glm(n_survived/med_t5eggs ~
                                        any_antsP_B4H*any_antsP_AFH*strat,
                        data=B4orAF_hatch_surv_data_all,
                        family=quasibinomial, weight=med_t5eggs)
summary(B4orAF_hatch_surv_all.Esurv.mai)
plot(Effect(focal.predictors=c("any_antsP_AFH"),
            mod=B4orAF_hatch_surv_all.Esurv.mai, residuals=TRUE))
plot(Effect(focal.predictors=c("any_antsP_AFH", "strat"),
            mod=B4orAF_hatch_surv_all.Esurv.mai, residuals=TRUE))
plot(Effect(focal.predictors=c("any_antsP_AFH", "any_antsP_B4H"),
            mod=B4orAF_hatch_surv_all.Esurv.mai, residuals=TRUE))
```

### quickly seeing whether adding proportion of days ants attended is helpful
```{r}
B4orAF_hatch_propAnts_data_all_unfilt <- ants_days_data %>%
  left_join(clutch_survivorship_data) %>%
  select(location, Date, est_hatch, last_des_rel2h, `visited in 4 days`, ants_L, ants_P,
         med_t5eggs, n_hatched, n_survived) %>%
  mutate(strat=ifelse(last_des_rel2h<=-16, "desert",
                      ifelse(last_des_rel2h>-16 & last_des_rel2h<=4, "eggs",
                             ifelse(last_des_rel2h>4, "nymphs", NA))),
         B4orAF_hatch=ifelse((Date<=(est_hatch+9))&(Date>=est_hatch), "10 days after hatch",
                             ifelse((Date>=(est_hatch-10))&(Date<est_hatch), "10 days before hatch",
                                    NA))) %>%
  filter(!is.na(B4orAF_hatch)) %>%
  group_by(location) %>%
    summarize(last_des_rel2h=first(last_des_rel2h),
              vis=first(factor(`visited in 4 days`)),
              strat=first(strat),
              any_antsP_B4H=factor(any(ants_P&(B4orAF_hatch=="10 days before hatch"))),
              any_antsP_AFH=factor(any(ants_P&(B4orAF_hatch=="10 days after hatch"))),
              prop_ants_B4H=ifelse(any_antsP_B4H=="TRUE",
                                   sum(ants_P&(B4orAF_hatch=="10 days before hatch"))/
                                     sum(B4orAF_hatch=="10 days before hatch"),
                                   0),
              prop_ants_AFH=ifelse(any_antsP_AFH=="TRUE",
                                   sum(ants_P&(B4orAF_hatch=="10 days after hatch"))/
                                     sum(B4orAF_hatch=="10 days after hatch"),
                                   0),
              n=n(),
              med_t5eggs=first(med_t5eggs), 
              n_hatched=first(n_hatched), 
              n_survived=ifelse(first(n_survived)/first(n_hatched)>1,
                                1, first(n_survived))) %>%
  ungroup()

B4orAF_hatch_propAnts_data_all <- B4orAF_hatch_propAnts_data_all_unfilt %>% 
  # note that there are slight uneven sample sizes across clutches
  filter(!is.na(strat), !is.na(n_hatched), n>=8, n<=13)

ggplot(B4orAF_hatch_propAnts_data_all) +
  geom_point(aes(y=n_hatched/med_t5eggs, x=prop_ants_B4H)) +
  geom_smooth(aes(y=n_hatched/med_t5eggs, x=prop_ants_B4H), method=lm) +
  facet_wrap(~strat)

ggplot(B4orAF_hatch_propAnts_data_all) +
  geom_point(aes(y=n_hatched/med_t5eggs, x=prop_ants_AFH)) +
  geom_smooth(aes(y=n_hatched/med_t5eggs, x=prop_ants_AFH), method=lm) +
  facet_wrap(~strat)

B4orAF_hatch_propAnts_all.eggs.mai <- glm(n_hatched/med_t5eggs ~
                                          strat*prop_ants_B4H*prop_ants_AFH,
                        data=B4orAF_hatch_propAnts_data_all,
                        family=quasibinomial, weight=med_t5eggs)
summary(B4orAF_hatch_propAnts_all.eggs.mai)
plot(Effect(focal.predictors=c("strat"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.eggs.mai))

B4orAF_hatch_propAnts_all.nymphs.mai <- glm(n_survived/n_hatched ~
                                          strat*prop_ants_B4H*prop_ants_AFH,
                        data=B4orAF_hatch_propAnts_data_all,
                        family=quasibinomial, weight=n_hatched)
summary(B4orAF_hatch_propAnts_all.nymphs.mai)
plot(Effect(focal.predictors=c("strat"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.mai))
plot(Effect(focal.predictors=c("prop_ants_AFH"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.mai))
plot(Effect(focal.predictors=c("strat", "prop_ants_AFH"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.mai))

B4orAF_hatch_propAnts_all.Esurv.mai <- glm(n_survived/med_t5eggs ~
                                          strat*prop_ants_B4H*prop_ants_AFH,
                        data=B4orAF_hatch_propAnts_data_all,
                        family=quasibinomial, weight=med_t5eggs)
summary(B4orAF_hatch_propAnts_all.Esurv.mai)
plot(Effect(c("strat"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.Esurv.mai))
plot(Effect(c("strat", "prop_ants_AFH"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.Esurv.mai))

```

#### using three continuous predictors
Plotting with residuals reveals poor model fit, plus AIC is much higher than binned. I think there are too many colinearities/confounding trends to make this work.
```{r}
xlevels_props<-list(last_des_rel2h=c(-20,0,20),
                             prop_ants_B4H=c(0,0.5,1),
                             prop_ants_AFH=c(0,0.5,1))

B4orAF_hatch_propAnts_all.eggs.lastdes.mai <- glm(n_hatched/med_t5eggs ~
                                          last_des_rel2h*prop_ants_B4H*prop_ants_AFH,
                        data=B4orAF_hatch_propAnts_data_all,
                        family=quasibinomial, weight=med_t5eggs)
summary(B4orAF_hatch_propAnts_all.eggs.lastdes.mai)
plot(Effect(focal.predictors=c("last_des_rel2h"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.eggs.lastdes.mai, xlevels=xlevels_props))

B4orAF_hatch_propAnts_all.nymphs.lastdes.mai <- glm(n_survived/n_hatched ~ last_des_rel2h*prop_ants_B4H*prop_ants_AFH,
                        data=B4orAF_hatch_propAnts_data_all,
                        family=quasibinomial, weight=n_hatched)
summary(B4orAF_hatch_propAnts_all.nymphs.lastdes.mai)
plot(Effect(focal.predictors=c("last_des_rel2h"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.mai, xlevels=xlevels_props))

B4orAF_hatch_propAnts_all.Esurv.lastdes.mai <- glm(n_survived/med_t5eggs ~
                                          last_des_rel2h*prop_ants_B4H*prop_ants_AFH,
                        data=B4orAF_hatch_propAnts_data_all,
                        family=quasibinomial, weight=med_t5eggs)
summary(B4orAF_hatch_propAnts_all.Esurv.lastdes.mai)
plot(Effect(c("last_des_rel2h"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.Esurv.lastdes.mai, xlevels=xlevels_props))
plot(Effect(c("prop_ants_AFH"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.Esurv.lastdes.mai, xlevels=xlevels_props))
plot(Effect(c("last_des_rel2h", "prop_ants_AFH"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.Esurv.lastdes.mai, xlevels=xlevels_props))

```

last des but any ants
```{r}
B4orAF_hatch_all.eggs.lastdes.mai <- glm(n_hatched/med_t5eggs ~
                                          last_des_rel2h*any_antsP_B4H*any_antsP_AFH,
                        data=B4orAF_hatch_propAnts_data_all,
                        family=quasibinomial, weight=med_t5eggs)
plot(Effect(focal.predictors=c("any_antsP_AFH"), residuals=T,
            mod=B4orAF_hatch_all.eggs.lastdes.mai, xlevels=xlevels_props))

B4orAF_hatch_all.nymphs.lastdes.mai <- glm(n_survived/n_hatched ~
                                          last_des_rel2h*any_antsP_B4H*any_antsP_AFH,
                        data=B4orAF_hatch_propAnts_data_all,
                        family=quasibinomial, weight=n_hatched)
summary(B4orAF_hatch_all.nymphs.lastdes.mai)
plot(Effect(focal.predictors=c("any_antsP_AFH"), residuals=T,
            mod=B4orAF_hatch_all.nymphs.lastdes.mai, xlevels=xlevels_props))

B4orAF_hatch_all.Esurv.lastdes.mai <- glm(n_survived/med_t5eggs ~
                                          last_des_rel2h*any_antsP_B4H*any_antsP_AFH,
                        data=B4orAF_hatch_propAnts_data_all,
                        family=quasibinomial, weight=med_t5eggs)
summary(B4orAF_hatch_all.Esurv.lastdes.mai)
plot(Effect(focal.predictors=c("any_antsP_AFH"), residuals=T,
            mod=B4orAF_hatch_all.Esurv.lastdes.mai, xlevels=xlevels_props))
```

### trying again with visited in 4 days

```{r}
ggplot(B4orAF_hatch_propAnts_data_all) +
  geom_point(aes(y=n_hatched/med_t5eggs, x=prop_ants_B4H)) +
  geom_smooth(aes(y=n_hatched/med_t5eggs, x=prop_ants_B4H), method=lm) +
  facet_wrap(vars(strat,vis))

ggplot(B4orAF_hatch_propAnts_data_all) +
  geom_point(aes(y=n_hatched/med_t5eggs, x=prop_ants_AFH)) +
  geom_smooth(aes(y=n_hatched/med_t5eggs, x=prop_ants_AFH), method=lm) +
  facet_wrap(vars(strat,vis))

B4orAF_hatch_propAnts_all.eggs.lastdes.vis.mai <- 
  glm(n_hatched/med_t5eggs ~ last_des_rel2h + prop_ants_B4H + prop_ants_AFH +
        prop_ants_B4H:last_des_rel2h + prop_ants_AFH:last_des_rel2h +
        prop_ants_B4H:prop_ants_AFH +
        vis + vis:last_des_rel2h + 
        vis:last_des_rel2h:prop_ants_B4H + vis:last_des_rel2h:prop_ants_AFH +
        vis:prop_ants_B4H + vis:prop_ants_AFH,
      data=B4orAF_hatch_propAnts_data_all,
      family=quasibinomial, weight=med_t5eggs)
summary(B4orAF_hatch_propAnts_all.eggs.lastdes.vis.mai)
xlevels_props<-list(last_des_rel2h=c(-20,0,20),
                    prop_ants_B4H=c(0,0.5,1),
                    prop_ants_AFH=c(0,0.5,1))
plot(allEffects(B4orAF_hatch_propAnts_all.eggs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("prop_ants_AFH"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.eggs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("prop_ants_AFH","vis"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.eggs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("last_des_rel2h", "prop_ants_B4H"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.eggs.lastdes.vis.mai, xlevels=xlevels_props))

B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai <- 
  glm(n_survived/n_hatched ~ last_des_rel2h + prop_ants_B4H + prop_ants_AFH +
        prop_ants_B4H:last_des_rel2h + prop_ants_AFH:last_des_rel2h +
        prop_ants_B4H:prop_ants_AFH +
        vis + vis:last_des_rel2h +
        vis:prop_ants_B4H + vis:prop_ants_AFH,
      data=B4orAF_hatch_propAnts_data_all,
      family=binomial, weight=n_hatched)
summary(B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai)
xlevels_props<-list(last_des_rel2h=c(-20,0,20),
                    prop_ants_B4H=c(0,0.5,1),
                    prop_ants_AFH=c(0,0.5,1))

plot(Effect(focal.predictors=c("prop_ants_B4H"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("prop_ants_AFH"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("vis"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai, xlevels=xlevels_props))

plot(Effect(focal.predictors=c("last_des_rel2h", "prop_ants_B4H"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("last_des_rel2h", "prop_ants_AFH"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("last_des_rel2h"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("vis"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("vis", "last_des_rel2h"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("vis","last_des_rel2h", "prop_ants_B4H"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("vis","last_des_rel2h", "prop_ants_AFH"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai, xlevels=xlevels_props))
plot(Effect(focal.predictors=c("prop_ants_B4H", "prop_ants_AFH"), residuals=T,
            mod=B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai, xlevels=xlevels_props))
```

### comparing all these models
Including the proportion of days in the 10 days before hatching ants visited the plant and the proportion of days in the 10 days after hatching ants visited the plant yields only one significant term in the model, the latest date desertion relative to hatching for hatching success, nymph survival and survival of eggs. However, this model performs as well as or better than the model representing ant attendance simply by ant exclusion treatment at the task of predicting the actual survivorship measures ("imputation" figures).
```{r}
summary(B4orAF_hatch_surv_all.eggs.mai) # all ns >0.05
summary(B4orAF_hatch_propAnts_all.eggs.lastdes.mai) # last_des_rel2h*
summary(B4orAF_hatch_all.nymphs.lastdes.mai) # all ns >0.05
#summary(B4orAF_hatch_propAnts_all.eggs.lastdes.vis.mai)

summary(B4orAF_hatch_surv_all.nymphs.mai) # any_antsP_AFH*, stratnymphs:any_antsP_AFH*
summary(B4orAF_hatch_propAnts_all.nymphs.lastdes.mai) # last_des_rel2h*
summary(B4orAF_hatch_all.nymphs.lastdes.mai) # all ns >0.05
#summary(B4orAF_hatch_propAnts_all.nymphs.lastdes.vis.mai)

summary(B4orAF_hatch_surv_all.Esurv.mai) # any_antsP_AFH*, stratnymphs:any_antsP_AFH*
summary(B4orAF_hatch_propAnts_all.Esurv.lastdes.mai) # last_des_rel2h*
summary(B4orAF_hatch_all.Esurv.lastdes.mai) # any_antsP_AFH*
#summary(B4orAF_hatch_propAnts_all.Esurv.lastdes.vis.mai)
```

```{r}

# multi-clutch plants vs single-clutch plants
ants_days_data %>%
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed, n_clutches_on_plant>1) %>%
  mutate(ants_P=ifelse(ants_P==0,NA,ants_P)) %>%
ggplot(data=, aes(y=reorder(location,desc(last_des_rel2h)),x=Date-est_hatch, color=log(ants_P))) +
  geom_point() +
  geom_point(aes(y=reorder(location,desc(last_des_rel2h)), x=last_des_rel2h+1), shape=8, color="black") +
  theme_publilia() +
  scale_colour_gradientn(colours=rainbow(6)) +
  theme(axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank())

ants_days_data %>%
  left_join(clutch_survivorship_data) %>%
  filter(!ants_removed, !females_removed, n_clutches_on_plant==1) %>%
  mutate(ants_P=ifelse(ants_P==0,NA,ants_P)) %>%
ggplot(data=, aes(y=reorder(location,desc(last_des_rel2h)),x=Date-est_hatch, color=log(ants_P))) +
  geom_point() +
  geom_point(aes(y=reorder(location,desc(last_des_rel2h)), x=last_des_rel2h+1), shape=8, color="black") +
  theme_publilia() +
  scale_colour_gradientn(colours=rainbow(6)) +
  theme(axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank())

ants_days_data %>%
  filter(ants_removed) %>%
  mutate(ants_P=ifelse(ants_P==0,NA,ants_P)) %>%
ggplot(data=, aes(y=reorder(location,n_days_antsP),x=Date-est_hatch, color=log(ants_P))) +
  geom_point() +
  theme_publilia() +
    scale_colour_gradientn(colours=rainbow(6))

# how many clutches actually ever had ants vs. not?
ant_counts %>%
  ggplot(data=., aes(x=ants_treatment, fill=ifelse(ever_antsP,"ever ants", "never ants"))) +
  geom_bar() +
  theme_publilia() + facet_wrap(~ifelse(females_removed, "Females removed", "Control"))

```

ant arrival times
```{r}
antP_arrival_afh_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsP_afh=ants_P&afh) %>%
    filter(is_antsP_afh) %>%
    slice_head(n=1) %>% 
  mutate(antP_arrival_afh=Date-est_hatch) %>%
  select(location, antP_arrival_afh, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antP_last_b4h_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsP_bfh=ants_P&b4h) %>%
    filter(is_antsP_bfh) %>%
    slice_tail(n=1) %>% 
  mutate(antP_last_b4h=Date-est_hatch) %>%
  select(location, antP_last_b4h, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antL_arrival_afh_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsL_afh=ants_L&afh) %>%
    filter(is_antsL_afh) %>%
    slice_head(n=1) %>% 
  mutate(antL_arrival_afh=Date-est_hatch) %>%
  select(location, antL_arrival_afh, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

antL_last_b4h_data <- All_data_v6 %>%
  left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
  filter(!is.na(initiation_date)) %>%
  distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
  group_by(location) %>%
    mutate(b4h=Date>=initiation_date&Date<est_hatch,
           afh=Date>=est_hatch,
           is_antsL_bfh=ants_L&b4h) %>%
    filter(is_antsL_bfh) %>%
    slice_tail(n=1) %>% 
  mutate(antL_last_b4h=Date-est_hatch) %>%
  select(location, antL_last_b4h, ants_removed, females_removed,
         initiation_date, est_hatch) %>%
  ungroup() %>%
  mutate(Dorm=substr(location,1,1),
         ants_treatment=ifelse(ants_removed,"Ants removed","Control"))

ant_data <- ant_counts %>%
  left_join(antP_last_b4h_data) %>%
  left_join(antP_arrival_afh_data) %>%
  left_join(antL_last_b4h_data) %>%
  left_join(antL_arrival_afh_data)

visited_1st_4d_data_ants <- visited_1st_4d_data %>%
  left_join(ant_data)

visited_1st_4d_data_ants %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h, y=antL_last_b4h, color=females_removed)) +
  geom_point() +
  geom_abline(slope=1)

visited_1st_4d_data_ants %>%
  filter(ants_treatment=="Control", females_removed) %>%
  ggplot(data=., aes(x=est_rel2h, y=antL_last_b4h)) +
  geom_point() +
  geom_abline(slope=1)

visited_1st_4d_data_ants %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h, y=antL_arrival_afh, color=females_removed)) +
  geom_point() +
  geom_smooth(method=lm) +
  geom_abline(slope=1)

visited_1st_4d_data_ants %>%
  filter(ever_antsP) %>%
  ggplot(data=., aes(x=est_rel2h>=0, y=antL_last_b4h)) +
  geom_boxplot()

visited_1st_4d_data_ants %>%
  filter(ants=="Control") %>%
  ggplot(data=., aes(x=est_rel2h>=0, y=antL_arrival_afh)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=1, width=0.35, height=0) +
  stat_summary(fun=mean, geom="point", shape=4, size=3)

visited_1st_4d_data_ants %>%
  filter(est_rel2h<=4) %>%
  filter(ants=="Control", !females_removed) %>%
  ggplot(data=., aes(x=est_rel2h>=-4, y=antL_arrival_afh)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=1, width=0.35, height=0) +
  stat_summary(fun=mean, geom="point", shape=4, size=3)

visited_1st_4d_data_ants %>%
  filter(ants=="Control") %>%
  ggplot(data=., aes(x=females_removed, y=antL_arrival_afh)) +
  geom_boxplot() +
  geom_jitter(pch = 21, size=1, width=0.35, height=0) +
  stat_summary(fun=mean, geom="point", shape=4, size=3)
```

```{r}
## Not visited early
# ever ants b4h
ggplot(data = filter(visited_1st_4d_data_ants, 
                                 `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends<last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color = ever_antsP_b4h, fill = ever_antsP_b4h), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

# ever ants afh
ggplot(data = filter(visited_1st_4d_data_ants, 
                                 `visited in 4 days` == "Not visited",
                                 !grepl("U", Female_ID), !females_removed, mom_at_init,
                                 clutch_initiated_order == 1, visit_ends < last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color=ever_antsP_afh, fill=ever_antsP_afh), 
            alpha = 0.75, stat='bin', binwidth=4, size=0, position="identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

## Visited early
# ever ants b4h
ggplot(data = filter(visited_1st_4d_data_ants,
                     `visited in 4 days` == "Visited",
                     !grepl("U", Female_ID), !females_removed, mom_at_init,
                     clutch_initiated_order == 1, visit_ends<last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color = ever_antsP_b4h, fill = ever_antsP_b4h), 
            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)

# ever ants afh
ggplot(data = filter(visited_1st_4d_data_ants,
                     `visited in 4 days` == "Visited",
                     !grepl("U", Female_ID), !females_removed, mom_at_init,
                     clutch_initiated_order == 1, visit_ends < last_day_fID)) +
  geom_area(aes(x = est_rel2h, y=..density.., 
                color=ever_antsP_afh, fill=ever_antsP_afh), 
            alpha = 0.75, stat='bin', binwidth=4, size=0, position="identity") + 
  theme_publilia() +
  xlab("Desert date relative to hatching") +
  ylab("Proportion of females") +
  scale_color_manual(values = c("black", "brown1")) +
 scale_fill_manual(values = c("black", "brown1")) +
  geom_vline(xintercept = -20, linetype="dotted", 
                color = "gray", size=1) +
  geom_vline(xintercept = 0, linetype="dashed", 
                color = "gray", size=1)
```

### 2023-08-25 scripts/Publilia-01-qc.Rmd
minor edits to ensure scripts 01-03 run after overhaul of strats_data

@@
 ---
-title: '01 - TreehopperFitness: Quality control'
+title: '01 - TreehopperFitness - Quality control and data prep'
 author: "Micah Fletcher"
@@
 ## 7.1 - Adding second gen adult counts per leaf to clutch status stats
-```{r}
+```{r, warning=FALSE}
 # counting adults
@@
 These were revised manually to specify a leaf of origin for the nymphs, where possible.
-```{r}
+```{r, warning=FALSE}
 NOr_status_resolveable_all_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>% 
@@
 ## 7.3 - Implement revisions by creating the new variables NOr_revised and NOr_rev_loc
-```{r}
+```{r, warning=FALSE}
 # if nymph origin was clearly resolveable, the revisions were made in NOr_manual_revisions
@@
 
-```{r}
+```{r, warning=FALSE}
 NOr_status_resolveable_all_unambig_clutches <- All_data_v6_clutch_status_stats_v2 %>% 
@@
 - Filtered out clutches with outlier numbers of N1 or N5 etc at early or late clutch ages, which were assumed to be cases of immigration that weren't caught during manual nymph origin filtering
-```{r}
+```{r, warning=FALSE}
 # Filter to only include curated list of clutches with unambiguous nymph counts after accounting for immigration to non-natal leaves and then sum all nymphs (including emigrants) for each clutch
@@
 Taking the median (or mean) of the top 5 egg_num counts yields an estimate of max egg num that is more robust to outliers/miscounts
-```{r}
+```{r, warning=FALSE}
 tmp_t5eggs_data <- clutch_status_init_hatch_labels_v1 %>%

### 2023-08-25 scripts/Publilia-02-strats.Rmd
minor edits to ensure scripts 01-03 run after overhaul of strats_data

@@
 ---
-title: '01 - TreehopperFitness: Defining strategies and calculating frequencies'
+title: '02 - PubliliaFitness - Defining strategies and calculating frequencies'
 author: "Micah Fletcher"
@@
 library(multcompView)
+library(scales)
+library(ggupset)
 library(here)
@@
 
-clutch_status_guarding_summary_v2
+All_data_v6 and strats_data should be all we need
 ```{r}
 All_data_v6 <- read_rds(here("saved_rds/All_data_v6.rds"))
-# clutch_status_guarding_summary_v2 <- read_rds(here("saved_rds/clutch_status_guarding_summary_v2.rds"))
-# last_day_fID <- read_rds(here("saved_rds/last_day_fID.rds"))
-
 strats_data <- read_rds(here("saved_rds/strats_data.rds"))
@@
 
-# 3 - Defining exposure to ants
-
-## 3.1 - Ant counts on plant; some ants_removed clutches were visited by ants, and vice versa
-```{r}
-## Moved to Publilia-01-qc.Rmd
-# ant_counts <- All_data_v6 %>%
-#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-#   filter(!is.na(initiation_date)) %>%
-#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-#   group_by(location) %>%
-#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
-#            afh=Date>=est_hatch) %>%
-#     summarize(ants_removed=first(ants_removed),
-#               females_removed=first(females_removed),
-#               n_antsP=sum(ants_P,na.rm=T),
-#               ever_antsP=n_antsP>0,
-#               mean_antsP=mean(ants_P,na.rm=T),
-#               med_antsP=median(ants_P,na.rm=T),
-#               
-#               n_antsP_b4h=sum(ants_P&b4h),
-#               ever_antsP_b4h=n_antsP_b4h>0,
-#               mean_antsP_b4h=mean(ifelse(b4h,ants_P,NA),na.rm=T),
-#               med_antsP_b4h=median(ifelse(b4h,ants_P,NA),na.rm=T),
-#               
-#               n_antsP_afh=sum(ants_P&afh),
-#               ever_antsP_afh=n_antsP_afh>0,
-#               mean_antsP_afh=mean(ifelse(afh,ants_P,NA),na.rm=T),
-#               med_antsP_afh=median(ifelse(afh,ants_P,NA),na.rm=T)) %>%
-#   ungroup() %>%
-#   mutate(Dorm=substr(location,1,1),
-#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
-
-ggplot(data=ant_counts,aes(x=Dorm,y=n_antsP, fill=ants_treatment)) +
-  geom_boxplot()
-
-ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP, fill=ants_treatment)) +
-  geom_boxplot()
-
-ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_b4h, fill=ants_treatment)) +
-  geom_boxplot()
-
-ggplot(data=ant_counts,aes(x=Dorm,y=mean_antsP_afh, fill=ants_treatment)) +
-  geom_boxplot()
-
-ant_counts %>%
-  count(Dorm,ants_treatment,ever_antsP)
-
-ant_counts %>%
-  count(Dorm,ants_treatment,ever_antsP_b4h)
-
-ant_counts %>%
-  count(Dorm,ants_treatment,ever_antsP_afh)
-
-# how many clutches ever had ants in each of the dorms?
-ant_counts %>%
-  ggplot(data=., aes(y=as.numeric(ever_antsP), x=Dorm, fill=ants_treatment)) +
-  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
-  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
-  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
-  theme_publilia()
-
-ant_counts %>%
-  ggplot(data=., aes(y=as.numeric(ever_antsP_b4h), x=Dorm, fill=ants_treatment)) +
-  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
-  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
-  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
-  theme_publilia()
-
-ant_counts %>%
-  ggplot(data=., aes(y=as.numeric(ever_antsP_afh), x=Dorm, fill=ants_treatment)) +
-  stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
-  stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
-  stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
-  theme_publilia()
-
-# how extreme was the break-through?
-ant_counts %>%
-  ggplot(data=., aes(x=mean_antsP_b4h, color=ants_treatment, linetype=females_removed, group=Dorm)) +
-  geom_freqpoly(bins=100)
-
-ant_counts %>%
-  ggplot(data=., aes(x=med_antsP_b4h, color=ants_treatment, linetype=females_removed, group=Dorm)) +
-  geom_freqpoly()
-
-ant_counts %>%
-  ggplot(data=., aes(x=mean_antsP_afh, color=ants_treatment, linetype=females_removed, group=Dorm)) +
-  geom_freqpoly(bins=100)
-
-ant_counts %>%
-  ggplot(data=., aes(x=med_antsP_afh, color=ants_treatment, linetype=females_removed, group=Dorm)) +
-  geom_freqpoly()
-
-# how many clutches actually ever had ants vs. not?
-ant_counts %>%
-  ggplot(data=., aes(x=ever_antsP_b4h, fill=ants_treatment)) +
-  geom_bar() +
-  theme_publilia() + facet_wrap(~females_removed)
-
-ant_counts %>%
-  ggplot(data=., aes(x=ever_antsP_afh, fill=ants_treatment)) +
-  geom_bar() +
-  theme_publilia() + facet_wrap(~females_removed)
-
-ant_counts %>%
-  ggplot(data=., aes(x=ever_antsP_b4h|ever_antsP_afh, fill=ants_treatment)) +
-  geom_bar() +
-  theme_publilia() + facet_wrap(~females_removed)
-
-```
-
-## 3.2 - Ant arrival times
-```{r}
-## Moved to Publilia-01-qc.Rmd
-# antP_arrival_afh_data <- All_data_v6 %>%
-#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-#   filter(!is.na(initiation_date)) %>%
-#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-#   group_by(location) %>%
-#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
-#            afh=Date>=est_hatch,
-#            is_antsP_afh=ants_P&afh) %>%
-#     filter(is_antsP_afh) %>%
-#     slice_head(n=1) %>% 
-#   mutate(antP_arrival_afh=Date-est_hatch) %>%
-#   select(location, antP_arrival_afh, ants_removed, females_removed,
-#          initiation_date, est_hatch) %>%
-#   ungroup() %>%
-#   mutate(Dorm=substr(location,1,1),
-#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
-# 
-# antP_last_b4h_data <- All_data_v6 %>%
-#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-#   filter(!is.na(initiation_date)) %>%
-#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-#   group_by(location) %>%
-#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
-#            afh=Date>=est_hatch,
-#            is_antsP_bfh=ants_P&b4h) %>%
-#     filter(is_antsP_bfh) %>%
-#     slice_tail(n=1) %>% 
-#   mutate(antP_last_b4h=Date-est_hatch) %>%
-#   select(location, antP_last_b4h, ants_removed, females_removed,
-#          initiation_date, est_hatch) %>%
-#   ungroup() %>%
-#   mutate(Dorm=substr(location,1,1),
-#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
-# 
-# antL_arrival_afh_data <- All_data_v6 %>%
-#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-#   filter(!is.na(initiation_date)) %>%
-#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-#   group_by(location) %>%
-#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
-#            afh=Date>=est_hatch,
-#            is_antsL_afh=ants_L&afh) %>%
-#     filter(is_antsL_afh) %>%
-#     slice_head(n=1) %>% 
-#   mutate(antL_arrival_afh=Date-est_hatch) %>%
-#   select(location, antL_arrival_afh, ants_removed, females_removed,
-#          initiation_date, est_hatch) %>%
-#   ungroup() %>%
-#   mutate(Dorm=substr(location,1,1),
-#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
-# 
-# antL_last_b4h_data <- All_data_v6 %>%
-#   left_join(select(visited_1st_4d_data, location, initiation_date, est_hatch, ants_removed, females_removed)) %>%
-#   filter(!is.na(initiation_date)) %>%
-#   distinct(Date,location,ants_removed,females_removed,initiation_date,est_hatch,ants_L,ants_P) %>%
-#   group_by(location) %>%
-#     mutate(b4h=Date>=initiation_date&Date<est_hatch,
-#            afh=Date>=est_hatch,
-#            is_antsL_bfh=ants_L&b4h) %>%
-#     filter(is_antsL_bfh) %>%
-#     slice_tail(n=1) %>% 
-#   mutate(antL_last_b4h=Date-est_hatch) %>%
-#   select(location, antL_last_b4h, ants_removed, females_removed,
-#          initiation_date, est_hatch) %>%
-#   ungroup() %>%
-#   mutate(Dorm=substr(location,1,1),
-#          ants_treatment=ifelse(ants_removed,"Ants removed","Control"))
-# 
-# ant_data <- ant_counts %>%
-#   left_join(antP_last_b4h_data) %>%
-#   left_join(antP_arrival_afh_data) %>%
-#   left_join(antL_last_b4h_data) %>%
-#   left_join(antL_arrival_afh_data)
-# 
-# visited_1st_4d_data_ants <- visited_1st_4d_data %>%
-#   left_join(ant_data)
-
-strats_data %>%
-  filter(ever_antsP) %>%
-  ggplot(data=., aes(x=est_rel2h, y=antL_last_b4h, color=females_removed)) +
-  geom_point() +
-  geom_abline(slope=1)
-
-strats_data %>%
-  filter(ever_antsP) %>%
-  ggplot(data=., aes(x=est_rel2h, y=antL_arrival_afh, color=females_removed)) +
-  geom_point() +
-  geom_smooth(method=lm) +
-  geom_abline(slope=1)
-
-strats_data %>%
-  filter(ever_antsP) %>%
-  ggplot(data=., aes(x=est_rel2h>=0, y=antL_last_b4h)) +
-  geom_boxplot()
-
-strats_data %>%
-  filter(ants=="Control") %>%
-  ggplot(data=., aes(x=est_rel2h>=0, y=antL_arrival_afh)) +
-  geom_boxplot() +
-  geom_jitter(pch = 21, size=1, width=0.35, height=0) +
-  stat_summary(fun=mean, geom="point", shape=4, size=3)
-
-strats_data %>%
-  filter(ants=="Control", !females_removed) %>%
-  ggplot(data=., aes(x=est_rel2h>=0, y=antL_arrival_afh)) +
-  geom_boxplot() +
-  geom_jitter(pch = 21, size=1, width=0.35, height=0) +
-  stat_summary(fun=mean, geom="point", shape=4, size=3)
-```
-
 # 4 - Figure 1: Histograms of guarding tenure
@@
 ```{r}
-Fig1_v1_data <- visited_1st_4d_data %>%
+Fig1_v1_data <- strats_data %>%
   filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-strat_data_table1 <- visited_1st_4d_data %>%
+strat_data_table1 <- strats_data %>%
   mutate(`Ant exclusion` = ifelse(ants_removed, "Ants excluded", "Control"),
@@
 
-strat_data_table2 <- visited_1st_4d_data %>%
+strat_data_table2 <- strats_data %>%
   filter(!is.na(initiation_date), !females_removed) %>%
@@
 
-Fig1_v1C.gd <- ggplot(data = filter(visited_1st_4d_data,
+Fig1_v1C.gd <- ggplot(data = filter(strats_data,
                                  !females_removed, !mom_at_init,
@@
 
-filter(clutch_status_guarding_summary_v2, location == "A18_8", mom_at_init) %>%
+filter(strats_data, location == "A18_8", mom_at_init) %>%
   select(Female_ID:hatch_date, first_visitor_initiator, init_dur_rank:init_first_dur_shortest)
@@
 # non-parametric: Kruskall-Wallis test followed by Dunn test or pairwise wilcox tests
-vis_cat_v1.data <- visited_1st_4d_data %>%
+vis_cat_v1.data <- strats_data %>%
   left_join(first_visit_cuts) %>%
@@
 # non-parametric: Kruskall-Wallis test followed by Dunn test or pairwise wilcox tests
-vis_cat_v2.data <- visited_1st_4d_data %>%
+vis_cat_v2.data <- strats_data %>%
   left_join(first_visit_cuts) %>%
@@
 # vis_cat_v2.data %>% filter(is.na(vis_cat))
-# visited_1st_4d_data %>% filter(location=='C41_6')
+# strats_data %>% filter(location=='C41_6')
 # # C41_6 was deserted immediately, then visited long after hatch
-# visited_1st_4d_data %>% filter(location=='E148_6')
+# strats_data %>% filter(location=='E148_6')
 # # E148_6 was also visited long after hatch
-# visited_1st_4d_data %>% filter(location=='E40_9')
+# strats_data %>% filter(location=='E40_9')
 # # There was one female (E_Gkgg: E40_9) on the eggs before and after but not ON the init date.
@@
 ```{r}
-visit_data.desL.desP <- visited_1st_4d_data %>%
-  left_join(first_visit_cuts) %>%
+visit_data.desL.desP <- strats_data %>%
   group_by(location) %>% mutate(last_visit_ends_L = max(visit_ends, na.rm=T)) %>% ungroup() %>%
@@
 ```{r, fig.width=3, fig.height=3}
-Fig1_v1_data <- visited_1st_4d_data %>%
+Fig1_v1_data <- strats_data %>%
   filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-visited_1st_4d_data %>%
+strats_data %>%
   filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-(guarding_durations_plot_2023 <- visited_1st_4d_data %>%
+(guarding_durations_plot_2023 <- strats_data %>%
   filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
@@
 
-## The data used for the figures
-```{r}
-## Unfiltered data
-strats_data <- left_join(clutch_status_guarding_summary_v2, last_day_fID)
-
-## Data for histogram
-visited_1st_4d_data <- strats_data %>%
-  group_by(location) %>%
-    mutate(visited_1st_4d = any(!mom_at_init & as.numeric(visit_starts-initiation_date)<=4)) %>%
-  ungroup() %>%
-  mutate(`visited in 4 days` = ifelse(visited_1st_4d | num_at_init>1,
-                                      "Visited", "Not visited"),
-         ants = ifelse(ants_removed, "Ants removed", "Control"),
-         est_hatch = as_date(ifelse(is.na(hatch_date),
-                                 initiation_date + 20,
-                                 hatch_date)),
-         est_rel2h = visit_ends-est_hatch)
-
-visited_1st_4d_data %>%
-  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
-         clutch_initiated_order == 1, visit_ends < last_day_fID) %>% 
-  filter(!is.na(`visited in 4 days`)) %>%
-  mutate(`visited in 4 days` = 
-           ifelse(`visited in 4 days` == "Visited", 
-                  "Visited\nwithin first 4 days", 
-                  "Not visited\nwithin first 4 days"))
-
-## Data for visit vs init
-vis_cat_v1.data <- visited_1st_4d_data %>%
-  left_join(first_visit_cuts) %>%
-  mutate(vis_cat = ifelse(num_at_init > 1,
-                          "0",
-                          ifelse(is.na(first_visit_starts),
-                                 "never visited",
-                                 ifelse(first_visit_cut=="(0,4]", "1 to 4", "5+"))),
-         vis_cat = factor(vis_cat, levels = c("0","1 to 4",
-                                              "5+","never visited"))) %>%
-  filter(!females_removed, mom_at_init, 
-         clutch_initiated_order == 1, 
-         !grepl("U", Female_ID),
-         visit_ends < last_day_fID,
-         # ** There was one female (E_Gkgg) which was on the eggs before and after but not ON the initiation date.
-         # I suspect I missed her in the field or she may have left and come back. In any case she was never visited
-         # and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
-         !is.na(vis_cat))
-```
-
 ## Upset plot
 ```{r, fig.width=6, fig.height=2}
-library(ggupset)
-
 sample_size_upset_data <- strats_data %>%
@@
          `first clutch she initiated`,
-         `first clutch she initiated or visited`,
+         `her first clutch`,
          `female marked`, `female disappeared`, `unknown whether visited`, 

### 2023-08-25 scripts/old/Publilia_2019_CHAPTER-4-ants.Rmd
minor edits to ensure scripts 01-03 run after overhaul of strats_data

@@
 ```
-FUUUUUUUUCKKKKK!!!!!!!!!!!!
+
 Removing a mother results in a decrease in the probability of the clutch being attended by ants in the four days following removal ().

### 2023-08-25 scripts/Publilia-01-qc.Rmd
init `Publilia-04-within_clutch_iteroparity.Rmd`

@@
 
-## 10.1 - Generate data for fecundity modeling
-
-```{r}
-fec_model_data <- visited_1st_4d_data_tb %>%
-  filter(!is.na(guard_duration)) %>%
-  group_by(location) %>%
-  mutate(eggs_ever_visited = any(!mom_at_init & visit_ends <= est_hatch)) %>%
-  ungroup() %>%
-  select(Female_ID, location, guard_duration, est_rel2h, initiation_date, est_hatch,
-         mom_at_init, clutch_initiated_order, initL, initS,
-         visit_starts, visit_ends, last_day_fID,
-         num_at_init, n_clutches_on_plant, `visited in 4 days`, eggs_ever_visited, ants,
-         females_removed, ants_removed, 
-         max_egg_num, egg_fate, egg_fate_date)
-```
-
-## 10.2 - Calculate median of top 5 egg counts in lieu of max egg counts
+## 10.1 - Calculate median of top 5 egg counts in lieu of max egg counts
 Taking the median (or mean) of the top 5 egg_num counts yields an estimate of max egg num that is more robust to outliers/miscounts
 ```{r, warning=FALSE}
-tmp_t5eggs_data <- clutch_status_init_hatch_labels_v1 %>%
+t5eggs_data <- clutch_status_init_hatch_labels_v1 %>%
   mutate(est_hatch = as_date(ifelse(is.na(hatch_date),
@@
 
-top5eggs_summary <- tmp_t5eggs_data %>%
+top5eggs_summary <- t5eggs_data %>%
   group_by(location) %>%
@@
   ungroup()
+```
+
+## 10.2 - Generate data for fecundity modeling
+
+```{r}
+fec_model_data <- visited_1st_4d_data_tb %>%
+  filter(!is.na(guard_duration)) %>%
+  group_by(location) %>%
+  mutate(eggs_ever_visited = any(!mom_at_init & visit_ends <= est_hatch)) %>%
+  ungroup() %>%
+  select(Female_ID, location, guard_duration, est_rel2h, initiation_date, est_hatch,
+         mom_at_init, clutch_initiated_order, initL, initS,
+         visit_starts, visit_ends, last_day_fID,
+         num_at_init, n_clutches_on_plant, `visited in 4 days`, eggs_ever_visited, ants,
+         females_removed, ants_removed, 
+         max_egg_num, egg_fate, egg_fate_date) %>%
+  left_join(top5eggs_summary)
 ```
@@
 ```
+
+# 13 - Write data for `Publilia-04-within_clutch_iteroparity.Rmd` to `.rds`
+
+## `Publilia-04-within_clutch_iteroparity.Rmd`
+```{r}
+write_rds(clutch_egg_num_data, here("saved_rds/clutch_egg_num_data"))
+write_rds(t5eggs_data, here("saved_rds/t5eggs_data"))
+write_rds(fec_model_data, here("saved_rds/fec_model_data.rds"))
+write_rds(clutch_status_init_hatch_labels_v1, here("saved_rds/clutch_status_init_hatch_labels_v1.rds"))
+```

### 2023-08-25 scripts/Publilia-04-within_clutch_iteroparity.Rmd
init `Publilia-04-within_clutch_iteroparity.Rmd`

---
title: '04 - PubliliaFitness - Modeling within-clutch iteroparity'
author: "Micah Fletcher"
date: '`r Sys.Date()`'
output: 
  rmdformats::robobook:
  fig_width: 9
toc_depth: 3
---

# Required libraries and functions

```{r}
library(here)
library(MASS)
library(tidyverse)
library(mgcv)
select <- dplyr::select
```

# 0 - Data import

```{r}
clutch_egg_num_data <- read_rds(here("saved_rds/clutch_egg_num_data"))
clutch_status_init_hatch_labels_v1 <- read_rds(here("saved_rds/clutch_status_init_hatch_labels_v1.rds"))
t5eggs_data <- read_rds(here("saved_rds/t5eggs_data"))
fec_model_data <- read_rds(here("saved_rds/fec_model_data.rds"))
```

# 1 - Using the max number of eggs for clutch size is prone to overestimation

```{r}
# plotting the actual number of eggs over time to look for outliers
fec_model_data %>% filter(females_removed, mom_at_init, visit_ends==last_day_fID,
                   !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
         filter(guard_duration<7, max_egg_num>60)

clutch_status_init_hatch_labels_v1 %>% filter(location == "D77_11") %>% print(n=Inf) # this is definitely an outlier!
ggplot(clutch_status_init_hatch_labels_v1 %>% filter(location == "D77_11", !is.na(egg_num)),
       aes(x=Date,y=egg_num)) +
  geom_point() +
  geom_smooth()

clutch_status_init_hatch_labels_v1 %>% filter(location == "G32_8") %>% print(n=Inf) # this is definitely an outlier!
ggplot(clutch_status_init_hatch_labels_v1 %>% filter(location == "G32_8", !is.na(egg_num)),
       aes(x=Date,y=egg_num)) +
  geom_point() +
  geom_smooth()

clutch_status_init_hatch_labels_v1 %>% filter(location == "G55_9") %>% print(n=Inf) # this is definitely an outlier!
ggplot(clutch_status_init_hatch_labels_v1 %>% filter(location == "G55_9", !is.na(egg_num)),
       aes(x=Date,y=egg_num)) +
  geom_point() +
  geom_smooth()

clutch_status_init_hatch_labels_v1 %>% filter(location == "G67_10") %>% print(n=Inf) # this is definitely an outlier!
ggplot(clutch_status_init_hatch_labels_v1 %>% filter(location == "G67_10", !is.na(egg_num)),
       aes(x=Date,y=egg_num)) +
  geom_point() +
  geom_smooth()

clutch_status_init_hatch_labels_v1 %>% filter(location == "H19_8") %>% print(n=Inf) # this is definitely an outlier!
ggplot(clutch_status_init_hatch_labels_v1 %>% filter(location == "H19_8", !is.na(egg_num)),
       aes(x=Date,y=egg_num)) +
  geom_point() +
  geom_smooth()

```

# 2 - Counts are too uncertain to directly measure day-to-day oviposition for each female

Can I take the slope of each 2-day segment of a loess regression of the egg counts and assign those to the females that were present at the time? that would be more faithful to the estimating I'm trying to do.

It feels elegant, but it also puts too much faith in the individual counts of eggs, especially when you consider the fact that many counts increase even after all females have been removed. how would you account for that? I think that is too presumptuous to pursue with this data full of measurement error
```{r}
t5eggs_data_loess <- t5eggs_data %>% 
  filter(grepl("G",location)|grepl("F",location), !is.na(egg_num)) %>%
  #filter(location=="G5_6", !is.na(egg_num)) %>%
  mutate(clutch_age = as.numeric(Date-initiation_date)) %>%
  group_by(location) %>%
  filter(n()>1) %>% # loess cannot be run on a single value of x
  #do(model=loess(egg_num ~ clutch_age, data=.)) %>%
  do(modelr::add_predictions(model=loess(egg_num ~ clutch_age, data=.),
                             data=.)) %>%
  arrange(location,clutch_age) %>%
  mutate(loess_step = pred - lag(pred, order_by=clutch_age))

ggplot(data=t5eggs_data %>% filter(location=="G69_10", !is.na(egg_num)), 
       aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  geom_hline(aes(yintercept = max_n_eggs), color = "blue") +
  geom_hline(aes(yintercept = med_t5eggs), color = "green") +
  geom_hline(aes(yintercept = mean_t5eggs), color = "red") +
  geom_vline(aes(xintercept = est_hatch-initiation_date), color = "gray", linetype="dotted") +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

ggplot(data=t5eggs_data_loess %>% filter(location=="G69_10", !is.na(egg_num)), 
       aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  geom_line(aes(x = clutch_age, y = pred), color = "blue") +
  geom_hline(aes(yintercept = med_t5eggs), color = "green") +
  geom_hline(aes(yintercept = mean_t5eggs), color = "red") +
  geom_vline(aes(xintercept = est_hatch-initiation_date), color = "gray", linetype="dotted") +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")
```

# 3 - Actual numbers of eggs counted for representative examples

# 3.1 - lone female, guarded eggs
```{r}
clutch_status_init_hatch_labels_v1 %>%
  left_join(fec_model_data) %>%
  group_by(location) %>%
  filter(any(!(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)),
         any(mom_at_init&est_rel2h>=-2&est_rel2h<=2),
         !is.na(egg_num)) %>%
  ungroup() %>%
  distinct(location, Date, initiation_date, egg_num) %>%
  ggplot(aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

clutch_status_init_hatch_labels_v1 %>%
  left_join(fec_model_data) %>%
  group_by(location) %>%
  filter(any(!(eggs_ever_visited|num_at_init>1)),
         any(mom_at_init&est_rel2h>=-2&est_rel2h<=2),
         !is.na(egg_num)) %>%
  ungroup() %>%
  distinct(location, Date, initiation_date, egg_num) %>%
  ggplot(aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")
```

## 3.2 - lone female, guarded nymphs
```{r}
clutch_status_init_hatch_labels_v1 %>%
  left_join(fec_model_data) %>%
  group_by(location) %>%
  filter(any(!(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)),
         any(mom_at_init&est_rel2h>=10),
         !is.na(egg_num)) %>%
  ungroup() %>%
  distinct(location, Date, initiation_date, egg_num) %>%
  ggplot(aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

```

## 3.3 - visited female, deserted early
```{r}
clutch_status_init_hatch_labels_v1 %>%
  left_join(select(fec_model_data, -initiation_date, -egg_fate, -egg_fate_date)) %>%
  group_by(location) %>%
  filter(any(!(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)),
         any(mom_at_init&guard_duration>=0&guard_duration<=3), 
         !is.na(egg_num)) %>%
  ungroup() %>%
  distinct(location, Date, initiation_date, egg_num,
           eggs_ever_visited,num_at_init,n_clutches_on_plant) %>%
  ggplot(aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

```

## 3.4 - many visitors
```{r, fig.width = 6, fig.height=6}
clutch_status_init_hatch_labels_v1 %>%
  left_join(fec_model_data) %>%
  group_by(location) %>%
  filter(any(eggs_ever_visited),
         any(mom_at_init&guard_duration<=20)) %>%
  ungroup() %>%
  distinct(location, Date, initiation_date, egg_num) %>%
  ggplot(aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")
```

# 4 - It's not feasible to estimate per-female-clutch average oviposition rates either

Can I faithfully estimate the egg laying rate of lone females with `mean_t5eggs / visit_ends-initiation_date` and a y-intercept of 0 and initiation_date-1? [No]
```{r}
est_ov_rates <- fec_model_data %>% 
  filter(females_removed, mom_at_init, visit_ends==last_day_fID,
         !(eggs_ever_visited|num_at_init>1)) %>%
  filter(grepl("G",location)|grepl("F",location)) %>%
  left_join(t5eggs_data_loess) %>%
  distinct(Female_ID, location, mean_t5eggs, visit_ends, initiation_date) %>%
  group_by(location) %>%
  # +1 because this is the number of days the female was present, not the interval
  mutate(est_ov_rate = mean_t5eggs/as.numeric(visit_ends-initiation_date))

fec_model_data %>% 
  filter(females_removed, mom_at_init, visit_ends==last_day_fID,
         !(eggs_ever_visited|num_at_init>1)) %>%
  filter(grepl("G",location)|grepl("F",location)) %>%
  left_join(t5eggs_data_loess) %>%
ggplot(data=., aes(x=Date-initiation_date,y=egg_num)) +
  geom_point() +
  geom_smooth(color="purple",se=F) +
  geom_line(aes(x = clutch_age, y = pred), color = "blue") +
  geom_hline(aes(yintercept = med_t5eggs), color = "green") +
  geom_hline(aes(yintercept = mean_t5eggs), color = "red") +
  geom_vline(aes(xintercept = est_hatch-initiation_date), color = "gray", linetype="dotted") +
  geom_abline(data=est_ov_rates, aes(slope=est_ov_rate,intercept=-1)) +
  facet_wrap(vars(location)) +
  theme(legend.position="bottom")

fec_model_data %>% 
  filter(females_removed, mom_at_init, visit_ends==last_day_fID) %>%
  left_join(t5eggs_data) %>%
  distinct(Female_ID, location, mean_t5eggs, visit_ends, initiation_date, .keep_all=T) %>%
  group_by(location) %>%
  # +1 because this is the number of days the female was present, not the interval
  mutate(est_ov_rate = mean_t5eggs/as.numeric(visit_ends-initiation_date)) %>%
  ggplot() +
  geom_jitter(aes(y=est_ov_rate, x=eggs_ever_visited|num_at_init>1, group=eggs_ever_visited|num_at_init>1,
    color=eggs_ever_visited|num_at_init>1)) +
  theme(legend.position = "bottom")

```

# 5 - The final number of eggs in a clutch is correlated with guarding duration

`The final number of eggs in a clutch was highly correlated with the duration a female guarded them prior to hatching (Figure S2), indicating that females continue to lay eggs over time as they guard them.`

For this I want a model and R^2 value, plus a supplemental figure showing the data with the fitted model. 
 - I want to look at single females with no other visitors interfering or adding eggs of their own. Thus, I use only the females on clutches that were (1) never observed being visited (including multiple initiators), and (2) were alone on the plant (reducing the chance of including undetected visitors). 
 - Clutches from both the control and female removal treatments are included so that we can include more intermediate durations that are rare under control conditions. 
```{r}
fec_model_data %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=n_clutches_on_plant>1,fill=n_clutches_on_plant>1)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=loess) +
  theme(legend.position = "bottom")

fec_model_data %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=loess) +
  theme(legend.position = "bottom")

t5eggs_gdur_loneFs.data <- fec_model_data %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1))

ggplot(data=t5eggs_gdur_loneFs.data, 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(size = 4, alpha = 0.50) +
  theme(legend.position = "bottom")

t5eggs_gdur_loneFs.lm <- gam(med_t5eggs ~ guard_duration,
                             data = t5eggs_gdur_loneFs.data)
summary(t5eggs_gdur_loneFs.lm)
#visreg(t5eggs_gdur_loneFs.lm, "guard_duration", gg=TRUE)

t5eggs_gdur_loneFs.glm_pois <- glm(med_t5eggs ~ guard_duration, family = poisson,
                             data = t5eggs_gdur_loneFs.data)
summary(t5eggs_gdur_loneFs.glm_pois)
#visreg(t5eggs_gdur_loneFs.glm_pois, "guard_duration", gg=TRUE)

t5eggs_gdur_loneFs.gam_pois <- gam(med_t5eggs ~ s(guard_duration, bs="cr"), family = poisson,
                             data = t5eggs_gdur_loneFs.data)
summary(t5eggs_gdur_loneFs.gam_pois)
plot(t5eggs_gdur_loneFs.gam_pois)
#visreg(t5eggs_gdur_loneFs.gam_pois, "guard_duration", gg=TRUE)
```

`This pattern holds when including only females that were forcibly removed from their clutches (Figure S2), confirming that females are not depositing a lump sum of eggs at initiation and staying longer with larger clutches as suggested in other treehoppers (Olmstead and Wood 198X).`
I'm not certain this is necessary. If I want to demonstrate convincingly that they are depositing eggs over time, I could simply show the plots of different lone females on clutches with egg numbers growing over time?
```{r}
fec_model_data %>%
  filter(mom_at_init, females_removed, visit_ends==last_day_fID,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=lm) +
  theme(legend.position = "bottom")

# without the potential outliers potentially representing undetected visits
fec_model_data %>%
  filter(mom_at_init, females_removed, visit_ends==last_day_fID,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1),
         !(guard_duration<7&med_t5eggs>50)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(size = 4, alpha = 0.50) +
  geom_smooth(method=lm) +
  theme(legend.position = "bottom")
```

# 6 - Preliminary figures

The final number of eggs in a clutch was highly correlated with the duration that a female guarded them prior to hatching (Figure S2), indicating that Publilia reticulata females continue to lay eggs over time as they guard them. *Figure plus stats*
```{r}
fec_model_data %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(aes(y=med_t5eggs), method=loess, 
              color = "black", fill="black") +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")

fec_model_data %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=guard_duration>20,
           fill=guard_duration>20)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(aes(y=med_t5eggs), method=lm) +
  ylim(0,140) +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  scale_color_manual(labels=c("before hatch", "after hatch"),
                     values=c("black", "gray")) +
  scale_fill_manual(labels=c("before hatch", "after hatch"),
                    values=c("black", "gray")) +
  theme(legend.position = "bottom")

fec_model_data %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=guard_duration>20,
           fill=guard_duration>20)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(span = 1) +
  ylim(0,140) +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  scale_color_manual(labels=c("before hatch", "after hatch"),
                     values=c("black", "gray")) +
  scale_fill_manual(labels=c("before hatch", "after hatch"),
                    values=c("black", "gray")) +
  theme(legend.position = "bottom")

fec_model_data %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(aes(y=med_t5eggs), method="glm", method.args = list(family="poisson"), 
              color = "black", fill="black") +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")

# simple square root model
fec_model_data.v1 <- fec_model_data %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1))

fec_model_data.v1 %>%
  glm(data=., med_t5eggs ~ guard_duration, family="poisson")

fec_mod.m1 <- fec_model_data.v1 %>%
  glm(data=., med_t5eggs ~ guard_duration + I(sqrt(guard_duration)), family="poisson")

fec_model_data.v1.tmp <- fec_model_data.v1 %>%
  add_column(fit = predict(fec_mod.m1, newdata = ., type = 'response'))
## grad the inverse link function
ilink <- family(fec_mod.m1)$linkinv
## add fit and se.fit on the **link** scale
fec_model_data.m1_fit_ci <- fec_model_data.v1.tmp %>%
  add_column(setNames(as_tibble(predict(fec_mod.m1, fec_model_data.v1.tmp, se.fit = TRUE)[1:2]), 
                      c('fit_link','se_link'))) %>%
  ## create the interval and backtransform
  mutate(fit_resp  = ilink(fit_link),
         conf_upr = ilink(fit_link + (2 * se_link)),
         conf_lwr = ilink(fit_link - (2 * se_link)))

ggplot(data = fec_model_data.m1_fit_ci, 
       aes(x = guard_duration, y = fit)) +
    theme_publilia() +
    geom_point(aes(y = med_t5eggs), alpha = 0.1, size = 5) + 
    geom_line(aes(y = fit), size = 1) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.3, color = NA)

# square root model before/after hatch
fec_model_data.v2 <- fec_model_data %>%
  filter(mom_at_init, !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
  mutate(before_after_hatch = ifelse(guard_duration>=20, "after hatch", "before hatch"))

fec_model_data.v2 %>%
  glm(data=., med_t5eggs ~ guard_duration*before_after_hatch, family="poisson")

fec_mod.m2 <- fec_model_data.v2 %>%
  glm(data=., med_t5eggs ~ I(sqrt(guard_duration))*before_after_hatch, family="poisson")

fec_model_data.v2.tmp <- fec_model_data.v2 %>%
  add_column(fit = predict(fec_mod.m2, newdata = ., type = 'response'))
## grad the inverse link function
ilink <- family(fec_mod.m2)$linkinv
## add fit and se.fit on the **link** scale
fec_model_data.m2_fit_ci <- fec_model_data.v2.tmp %>%
  add_column(setNames(as_tibble(predict(fec_mod.m2, fec_model_data.v2.tmp, se.fit = TRUE)[1:2]), 
                      c('fit_link','se_link'))) %>%
  ## create the interval and backtransform
  mutate(fit_resp  = ilink(fit_link),
         conf_upr = ilink(fit_link + (2 * se_link)),
         conf_lwr = ilink(fit_link - (2 * se_link)))

ggplot(data = fec_model_data.m2_fit_ci, 
       aes(x = guard_duration, y = fit, color=before_after_hatch, fill=before_after_hatch)) +
    theme_publilia() +
    geom_point(aes(y = med_t5eggs), alpha = 0.1, size = 5) + 
    geom_line(aes(y = fit), size = 1) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.3, color = NA)

```

This pattern holds when females were forcibly removed (Figure S2), confirming that females are not depositing a lump sum of eggs at initiation and staying longer with larger clutches as suggested by Olmstead and Wood (198X) for the closely related Entylia carinata (as Entylia bactriana). *Just stats*
```{r}
fec_model_data %>%
  filter(mom_at_init,
         !is.na(!(eggs_ever_visited|num_at_init>1))) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs,
           color=!(eggs_ever_visited|num_at_init>1),
           fill=!(eggs_ever_visited|num_at_init>1))) +
  geom_point(size = 1, alpha = 0.80) +
  geom_smooth(span=0.75) +
  xlab("Guarding duration of initiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")
```

The sum of all females’ egg-guarding durations was more predictive of final clutch size than egg guarding duration of the initiator alone (Table S1 with alternative models and their AICs), showing that females lay eggs while visiting existing clutches. *Figure plus AIC?*
```{r}
clutch_egg_num_data %>%
ggplot(data=., 
       aes(x=sum_mD, y=med_t5eggs)) +
  geom_point(size = 1, alpha = 0.50) +
  geom_smooth(span=0.75, color="black", fill="black") +
  xlab("Sum of guarding durations of initiator and visitors") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = "bottom")

sum_mD_data <- clutch_egg_num_data %>%
  select(sum_mD, med_t5eggs)
```

Combine plots
```{r}
fec_fig1A <- fec_model_data %>%
  filter(mom_at_init,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=guard_duration>20,
           fill=guard_duration>20)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(span = 0.75) +
  xlab("Guarding duration of\ninitiating female") +
  ylab("Clutch size (number of eggs)") +
  scale_color_manual(labels=c("before hatch", "after hatch"),
                     values=c("black", "gray")) +
  scale_fill_manual(labels=c("before hatch", "after hatch"),
                    values=c("black", "gray")) +
  theme(legend.position = c(0.8,0.9)) + ylim(0,191) + xlim(0,76.2)

fec_model_data %>%
  filter(mom_at_init, females_removed,
         !(eggs_ever_visited|num_at_init>1|n_clutches_on_plant>1)) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs, 
           color=guard_duration>20,
           fill=guard_duration>20)) +
  geom_point(aes(y=med_t5eggs), size = 1, alpha = 0.80) +
  geom_smooth(span = 1) +
  xlab("Guarding duration of\ninitiating female") +
  ylab("Clutch size (number of eggs)") +
  scale_color_manual(labels=c("before hatch", "after hatch"),
                     values=c("black", "gray")) +
  scale_fill_manual(labels=c("before hatch", "after hatch"),
                    values=c("black", "gray")) +
  theme(legend.position = c(0.8,0.8)) + ylim(0,191) + xlim(0,76.2)

fec_fig1B <- fec_model_data %>%
  filter(mom_at_init, !is.na(!(eggs_ever_visited|num_at_init>1))) %>%
ggplot(data=., 
       aes(x=guard_duration, y=med_t5eggs,
           color=(eggs_ever_visited|num_at_init>1),
           fill=(eggs_ever_visited|num_at_init>1))) +
  geom_point(size = 1, alpha = 0.80) +
  geom_smooth(span=0.75) +
  scale_color_brewer(palette="Set2", labels=c("Never visited", "Visited")) +
  scale_fill_brewer(palette="Set2", labels=c("Never visited", "Visited")) +
  xlab("Guarding duration of\ninitiating female") +
  ylab("Clutch size (number of eggs)") +
  theme(legend.position = c(0.8,0.9)) + ylim(0,191) + xlim(0,76.2)

fec_fig1C <- clutch_egg_num_data %>%
ggplot(data=., 
       aes(x=sum_mD, y=med_t5eggs)) +
  geom_point(size = 1, alpha = 0.50) +
  geom_smooth(span=0.75, color="black", fill="black") +
  xlab("Sum of guarding durations of\ninitiator and visitors") +
  ylab("Clutch size (number of eggs)") + ylim(0,191) + xlim(0,76.2)

fec_fig1 <- egg::ggarrange(fec_fig1A, fec_fig1B, fec_fig1C, 
               labels = c("A","B","C"), nrow=1)

ggsave(here("prelim_figs/oviposition_over_time_loess.png"), fec_fig1,
       device="png", width = 300, height = 110, units = "mm", dpi = "print")
```

### 2023-08-26 scripts/Publilia-03-survivorship.Rmd
minor edits to ensure scripts 01-03 run after overhaul of strats_data
moving custom functions to separate files for each script

@@
 ---
-title: "Publilia-03-survivorship.Rmd"
-author: "micah fletcher"
-date: "8/4/2023"
-output: html_document
+title: '03 - PubliliaFitness - Modeling offspring surivorship'
+author: "Micah Fletcher"
+date: '`r Sys.Date()`'
+output: 
+  rmdformats::robobook:
+  fig_width: 9
+toc_depth: 3
 ---
@@
 
-source(here("R/custom_functions.R"))
+source(here("R/utils.R"))
+source(here("R/Publilia-03-survivorship-functions.R"))
 ```

### 2023-08-26 R/Publilia-03-survivorship-functions.R

@@ -1,0 +1,201 @@
+## Publilia-03-survivorship: regression functions
+
+### fit survivorship model
+fit_surv <- function(data_in, survNom, survDen, tenure, treatment, quad){
+  data <- data_in %>% filter(!is.na(.data[[tenure]]))
+  
+  if (!quad) {
+    formula.mai <- paste0(survNom,"/",survDen,"~",tenure,"*",treatment) %>% as.formula()
+    formula.ma <- paste0(survNom,"/",survDen,"~",tenure,"+",treatment) %>% as.formula()
+  } else if (quad) {
+    formula.mai <- paste0(
+      survNom,"/",survDen,"~",
+      tenure,"*",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
+    ) %>% as.formula()
+    formula.ma <- paste0(
+      survNom,"/",survDen,"~",
+      tenure,"+",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
+    ) %>% as.formula()
+  }
+  
+  mai.b <- glm(formula = formula.mai, data = data, weights = data[[survDen]], family = binomial)
+  mai.qb <- glm(formula = formula.mai, data = data, weights = data[[survDen]], family = quasibinomial)
+  ma.qb <- glm(formula = formula.ma, data = data, weights = data[[survDen]], family = binomial)
+  models <- list(mai.b = mai.b, mai.qb = mai.qb, ma.qb = ma.qb)
+  return(models)
+}
+
+capture_glm_stats <- function(model) {
+  capture.output(summary(model))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(model))))-1)]
+}
+
+print_glm_stats <- function(models) {
+  cat("Interaction, Binomial: \n")
+  print(capture_glm_stats(models$mai.b))
+  cat("\nInteraction, Quasibinomial: \n")
+  print(capture_glm_stats(models$mai.b))
+  cat("\nNo Interaction, Quasibinomial: \n")
+  print(capture_glm_stats(models$mai.b))
+}
+
+
+### Create confidence intervals in the link scale for plotting, and backtransform for plot
+# Based on: https://fromthebottomoftheheap.net/2018/12/10/confidence-intervals-for-glms/
+ci_for_plot <- function(data_in, survNom, survDen, 
+                        tenure, treatment, model){
+  
+  data <- data_in %>%
[…]

### 2023-08-26 R/Publilia-05-fitness-functions.R

@@ -1,0 +1,148 @@
+## Publilia-05-fitness custom functions
+
+# Confidence interval for estimating fitness
+ci_for_fitness <- function(data_in, survNom, survDen, 
+                           tenure, treatment, vis, model){
+  data <- eval(substitute(
+    data_in %>%
+      add_column(fit = predict(model, newdata = ., type = 'response'))
+  ))
+  ## grad the inverse link function
+  ilink <- family(model)$linkinv
+  ## add fit and se.fit on the **link** scale
+  data_fit_link <- eval(substitute(
+    data %>% add_column(
+      setNames(as_tibble(predict(model, data, se.fit = TRUE)[1:2]),
+               c('fit_link','se_link'))) %>%
+      ## create the interval and backtransform
+      mutate(fit_resp  = ilink(fit_link),
+             conf_upr = ilink(fit_link + (2 * se_link)),
+             conf_lwr = ilink(fit_link - (2 * se_link)))
+  ))
+  return(data_fit_link)
+}
+
+## Split violin plot
+# Based on jan-glx answer on https://stackoverflow.com/questions/35717353/split-violin-plot-with-ggplot2
+GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
+                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
+                             data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
+                             grp <- data[1, "group"]
+                             newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
+                             newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
+                             newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
+                             
+                             if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
+                               stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
+                                                                         1))
+                               quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
+                               aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
+                               aesthetics$alpha <- rep(1, nrow(quantiles))
+                               both <- cbind(quantiles, aesthetics)
[…]

### 2023-08-26 scripts/Publilia-05-fitness.Rmd
init `Publilia-05-fitness.Rmd`

--- 2023-08-24 scripts/old/Publilia_2019_CHAPTER-2C-fitness.Rmd
@@
 ---
-title: "Publilia_2019_CHAPTER-2C-fitness"
-author: "micah fletcher"
-date: "2/24/2022"
-output: html_document
+title: '05 - PubliliaFitness - Estimating lifetime fecundity and fitness'
+author: "Micah Fletcher"
+date: '`r Sys.Date()`'
+output: 
+  rmdformats::robobook:
+  fig_width: 9
+toc_depth: 3
 ---
 
-# Publilia 2019 Chapter - Script 2C: estimating fitness
-This is meant to consolidate previous scripts and provide a readable and reproducible record of the analyses for the Publilia Chapter.
-
-## Lifetime fitness using regression predictions
-Custom functions for using survivorship regression predictions to estimate fitness
-```{r}
-ci_for_fitness <- function(data_in, survNom, survDen, 
-                        tenure, treatment, vis, model){
-  data <- eval(substitute(
-    data_in %>%
-      add_column(fit = predict(model, newdata = ., type = 'response'))
-    ))
-  ## grad the inverse link function
-  ilink <- family(model)$linkinv
-  ## add fit and se.fit on the **link** scale
-  data_fit_link <- eval(substitute(
-    data %>% add_column(
-  setNames(as_tibble(predict(model, data, se.fit = TRUE)[1:2]),
-           c('fit_link','se_link'))) %>%
-## create the interval and backtransform
-  mutate(fit_resp  = ilink(fit_link),
-         conf_upr = ilink(fit_link + (2 * se_link)),
-         conf_lwr = ilink(fit_link - (2 * se_link)))
-    ))
-  return(data_fit_link)
-}
+# Load libraries
+
+```{r}
+library(multcompView)
+source(here("R/Publilia-05-fitness-functions.R"))
+```
+
+# 0 - Data import
+
+```{r}
+surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
 ```
@@
 
-Not time for dissertation but I could experiment with using a square root function for egg laying (more eggs in the first few days of guarding/visiting) and see how robust these results are to our assumptions about egg laying behavior.
 ```{r}
@@
 
-## Split violin plots
-geom_split_violin
-```{r}
-GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
-                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
-  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
-  grp <- data[1, "group"]
-  newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
-  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
-  newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
-
-  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
-    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
-      1))
-    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
-    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
-    aesthetics$alpha <- rep(1, nrow(quantiles))
-    both <- cbind(quantiles, aesthetics)
-    quantile_grob <- GeomPath$draw_panel(both, ...)
-    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
-  }
-  else {
-    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
-  }
-})
-
-geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
-                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
-                              show.legend = NA, inherit.aes = TRUE) {
-  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
-        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
-        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
-}
-```
-
 split violin v1
@@
 
-plotting libraries
-```{r}
-library(multcompView)
-```
-
-geom_split_violin
-```{r}
-GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
-                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
-  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
-  grp <- data[1, "group"]
-  newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
-  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
-  newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
-
-  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
-    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
-      1))
-    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
-    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
-    aesthetics$alpha <- rep(1, nrow(quantiles))
-    both <- cbind(quantiles, aesthetics)
-    quantile_grob <- GeomPath$draw_panel(both, ...)
-    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
-  }
-  else {
-    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
-  }
-})
-
-geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
-                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
-                              show.legend = NA, inherit.aes = TRUE) {
-  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
-        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
-        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
-}
-```
-
-A function to run Kruskall-Wallis test and Dunn tests for each panel
-```{r}
-fitness_KW_test <- function(data, y, group){
-  # non-parametric: Kruskall-Wallis test followed by Dunn test
-  # run KW test using rstatix::kruskal_test
-  KWtest <- eval(substitute(data %>% kruskal_test(y ~ group)))
-  # get effect size using effectsize::rank_epsilon_squared
-  KWepsilon2 <- eval(substitute(rank_epsilon_squared(y ~ group, data=data)))
-  # run Dunn test using rstatix::dunn_test
-  dunn <- eval(substitute(data %>% dunn_test(y ~ group)))
-  # get multiple comparison groups letters using multcompView::multcompLetters
-  dunn.vec <- dunn$p.adj.signif
-  names(dunn.vec) <- paste(dunn$group1,dunn$group2,sep="-")
-  multcompLetters <- tibble(x=names(multcompLetters(dunn.vec)$Letters),
-                            label=unname(multcompLetters(dunn.vec)$Letters))
-  # return
-  out <- list(KWtest=KWtest, KWepsilon2=KWepsilon2, dunn=dunn, multcompLetters=multcompLetters)
-  return(out)
-}
-
-fitness_life_strats_data.itero <- filter(fitness_life_strats_data, n_clutches_with_eggs_iv>1)
-fitness_future_stats_eggs.itero <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat_ants)
-
-KWtest <- fitness_life_strats_data %>% kruskal_test(est_eggs_future ~ desert_cat_ants)
-
-# # test
-# fitness_life_strats_data <- est_fitness_life_strats %>% 
-#   mutate(desert_cat_ants = ifelse(ants_removed, 
-#                                   paste(desert_cat,"ants removed"),paste(desert_cat,"control")))
-# fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
-
-# # Troubleshooting:
-# fitness_life_strats_data %>% filter(!females_removed, !is.na(desert_cat)) %>% 
-#     ggplot(data = ., aes(x = desert_cat, y = est_eggs_life, fill = ants_removed, 
-#         color = ants_removed)) + ylim(-160 * 0.05, 160) + 
-#   geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
-#   geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-#              pch = 16, size = 2, key_glyph = draw_key_rect) + 
-#     xlab("Guarding strategy for first clutch") + theme_publilia() + 
-#     scale_fill_manual(labels = c("Control", "Ants removed"), 
-#         values = c("brown1", "black")) + scale_color_manual(labels = c("Control", 
-#     "Ants removed"), values = c("brown1", "black")) + 
-#   geom_text(data = fitness_stats_eggs$multcompLetters, 
-#             aes(x = x, y = -160 * 0.05, label = label), 
-#             fontface = "bold", size = 4, position = position_dodge(width = 0.5)) + 
-#   scale_x_discrete(labels = c("desert", "eggs", "nymphs", "visit"))
-# 
-# fitness_life_strats_data %>% filter(!females_removed, !is.na(desert_cat)) %>% 
-#     ggplot(data = ., aes(x = desert_cat, y=est_eggs_life, fill=ants_removed, color=ants_removed)) + 
-#   ylim(-160 * 0.05, 160) + 
-#   geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
-#   geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-#              pch = 16, size = 2, key_glyph = draw_key_rect) + 
-#     xlab("Guarding strategy for first clutch") + theme_publilia() + 
-#     scale_fill_manual(labels = c("Control", "Ants removed"), values = c("brown1", "black")) + 
-#   scale_color_manual(labels = c("Control", "Ants removed"),  values = c("brown1", "black")) + 
-#   geom_text(data = fitness_stats_eggs$multcompLetters, 
-#     aes(x = x, y = -160 * 0.05, label = label), 
-#     fontface = "bold", size = 4, position=position_dodge(width=0.5)) + 
-#   scale_x_discrete(labels = c("desert", "eggs", "nymphs", "visit"))
-
-# plot boxplots, including KWtest letters
-fitness_plot_dunn <- function(data, y, group, itero=F, multcompLetters, letterSize, ymax=160){
-  if(itero==F){
-    (p <- eval(substitute(data %>%
-      filter(!females_removed, !is.na(group)) %>%
-    ggplot(data = ., aes(x = group, y=y, fill=ants_removed, color=ants_removed)) + 
-      ylim(-ymax * 0.05, ymax) + 
-      geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
-      geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-                 pch = 16, size = 2, key_glyph = draw_key_rect) + 
-      xlab("Guarding strategy for first clutch") + theme_publilia() + 
-      scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
-      scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
-      geom_text(data = multcompLetters, 
-                aes(x = x, y = -ymax * 0.05, label = label), 
-                fontface = "bold", size = letterSize, position=position_dodge(width=0.5)))))
-    return(p)
-  } else {
-    # single-clutch females
-    (p_semel <- eval(substitute(data %>%
-      filter(!females_removed, !is.na(group),
-             (n_clutches_with_eggs_iv==1)) %>%
-        ggplot(data = ., aes(x = group, y=y, fill=ants_removed, color=ants_removed)) + 
-          ylim(-ymax * 0.05, ymax) + 
-          geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
-          geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-                     pch = 16, size = 2, key_glyph = draw_key_rect) + 
-          xlab("Guarding strategy for first clutch") + theme_publilia() + 
-          scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
-          scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
-          geom_text(data = multcompLetters, 
-                    aes(x = x, y = -ymax * 0.05, label = label), 
-                    fontface = "bold", size = letterSize, position=position_dodge(width=0.5)))))
-    # multi-clutch females
-     (p_itero <- eval(substitute(data %>%
-      filter(!females_removed, !is.na(group),
-             (n_clutches_with_eggs_iv>1)) %>%
-        ggplot(data = ., aes(x = group, y=y, fill=ants_removed, color=ants_removed)) + 
-          ylim(-ymax * 0.05, ymax) + 
-          geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
-          geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-                     pch = 16, size = 2, key_glyph = draw_key_rect) + 
-          xlab("Guarding strategy for first clutch") + theme_publilia() + 
-          scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
-          scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
-          geom_text(data = multcompLetters, 
-                    aes(x = x, y = -ymax * 0.05, label = label), 
-                    fontface = "bold", size = letterSize, position=position_dodge(width=0.5)))))
-    p_list<-list(semel=p_semel, itero=p_itero)
-    return(p_list)
-  }
-}
-
-# test
-# fitness_life_strats_data <- est_fitness_life_strats %>%
-#   mutate(desert_cat_ants = ifelse(ants_removed,
-#                                   paste(desert_cat,"ants removed"),paste(desert_cat,"control")))
-# eggs_fitness_stats <- fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
-# 
-# fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants,
-#                   itero=F, multcompLetters=eggs_fitness_stats$multcompLetters,
-#                   letterSize=8)
-```
-
 ## Not separating single-clutch and multi-clutch females (for main)

### 2023-08-26 scripts/Publilia-03-survivorship.Rmd
Moved Zink fitness analysis to it's own script + saved survorship model fits from script 03 to use in 05 + other minor edits to script 05 to run without error

@@
 
-models_output <- list(
+surv_model_fits <- list(
   hatch = des_hatch.desL.ant_treatment.quad$fits,
@@
 ```{r}
-print_glm_stats(models_output$hatch)
+print_glm_stats(surv_model_fits$hatch)
 ```
@@
 ```{r}
-print_glm_stats(models_output$Nsurv)
+print_glm_stats(surv_model_fits$Nsurv)
 ```
@@
 ```{r}
-print_glm_stats(models_output$Esurv)
+print_glm_stats(surv_model_fits$Esurv)
 ```
@@
                                     "surv.reg_summary.desL.ants_treatment.quad.docx"))
+```
+
+## Save Main model fits for estimating fitness
+
+```{r}
+write_rds(surv_model_fits, here("saved_rds/surv_model_fits.rds"))
 ```

### 2023-08-26 scripts/Publilia-05-fitness.Rmd
Moved Zink fitness analysis to it's own script + saved survorship model fits from script 03 to use in 05 + other minor edits to script 05 to run without error

@@
 surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
+surv_model_fits <- read_rds(here("saved_rds/surv_model_fits.rds"))
 ```
@@
 est_fitness_hatch_fit_v6 <- 
-  ci_for_fitness(data_in=est_fitness_prep, model=des_hatch.desL.ant_treatment.quad.fits$mai.qb) %>%
+  ci_for_fitness(data_in=est_fitness_prep, model=surv_model_fits$hatch$mai.qb) %>%
   mutate(est_hatch_fit_v6 = fit) %>%
@@
 est_fitness_Esurv_fit_v6 <- 
-  ci_for_fitness(data_in=est_fitness_hatch_fit_v6, model=des_Esurv.desL.ant_treatment.quad.fits$mai.qb) %>%
+  ci_for_fitness(data_in=est_fitness_hatch_fit_v6, model=surv_model_fits$Esurv$mai.qb) %>%
   mutate(est_Esurv_fit_v6 = fit) %>%
@@
 
-## Comparing to Zink 2003 method
-
-### 3 Zink 2003 model:
-Lifetime fitness (number of eggs that hatched):
-w(t_i) = sum(from i=1, to i=N, P_i*g(t_i))
-P = number of eggs invested in a clutch (all the eggs go to the initiator?)
-t_i = guarding duration in clutch i
-N = lifetime number of clutches
-g(t) = relationship between guarding duration and hatching success
- (assume g(t) equivalent across all clutches 1 to N)
-
-* I think the main reason Zink found equivalent fitness is that he attributed all the eggs in a clutch to each primary female.
-Thus an early deserter is given all the eggs from a clutch, even if she leaves within a few days and another female arrives and lays additional eggs.
-The final nail in the coffin will be to do the exact same "zink" estimates but this time only attributing the egg to each female proportional to the time she spent on the clutch relative to other females.
-```{r}
-surv_reg_data_zink <- focalMb4h_sc2h %>%
-  filter(!is.na(initiation_date), !is.na(guard_duration), !ants_removed) %>%
-  filter(mom_at_init) %>% # primary females
-  group_by(location) %>%
-    summarize(max_primary_dur = max(guard_duration, na.rm=T),
-              females_removed = first(females_removed),
-              initiation_date = first(initiation_date)) %>%
-  ungroup() %>%
-  left_join(top5eggs_summary) %>%
-  select(location, max_primary_dur,
-         females_removed, initiation_date, med_t5eggs) %>%
-  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2,
-                   -c(ants_removed, females_removed, initiation_date, n_eggs)),
-            by=c("location"="NOr_rev_loc")) %>%
-  select(location, initiation_date, hatch_date, 
-         max_primary_dur, med_t5eggs, n_hatched, n_survived,
-         females_removed)
-
-ggplot(data=surv_reg_data_zink, 
-       aes(x=max_primary_dur, y=n_hatched/med_t5eggs)) +
-  geom_point() +
-  geom_smooth(method=lm)
-
-ggplot(data=filter(surv_reg_data_zink, initiation_date<=as_date("2019-06-10")), 
-       aes(x=max_primary_dur, y=n_hatched/med_t5eggs)) +
-  geom_point() +
-  geom_smooth(method=lm)
-
-ggplot(data=filter(surv_reg_data_zink, initiation_date<=as_date("2019-06-10"), !females_removed), 
-       aes(x=max_primary_dur, y=n_hatched/med_t5eggs)) +
-  geom_point() +
-  geom_smooth(method=lm)
-
-zink_hatch.m <- surv_reg_data_zink %>%
-  filter(initiation_date<=as_date("2019-06-10"), !is.na(n_hatched/med_t5eggs)) %>%
-lm(n_hatched/med_t5eggs ~ max_primary_dur, data=.)
-
-summary(zink_hatch.m) # use this for predicting hatching success
-
-zink_hatch.m.norem <- surv_reg_data_zink %>%
-  filter(initiation_date<=as_date("2019-06-10"), !is.na(n_hatched/med_t5eggs), !females_removed) %>%
-lm(n_hatched/med_t5eggs ~ max_primary_dur, data=.)
-
-summary(zink_hatch.m.norem)
-
-est_fitness_clutch_zink <- focalMb4h_sc2h %>%
-  filter(!is.na(initiation_date), !ants_removed) %>%
-  group_by(location) %>%
-    mutate(max_primary_dur = max(mom_at_init*guard_duration, na.rm=T)) %>% # non-primary females are not counted
-  ungroup() %>%
-  left_join(top5eggs_summary) %>%
-  left_join(clutch_momDays_b4h) %>%
-  select(Female_ID, location, guard_duration, max_primary_dur, desert_rel2h=est_rel2h, focalMb4h_sc2h, mDb4h_sc2h,
-         females_removed, initiation_date, med_t5eggs, 
-         mom_at_init, clutch_visited_order, clutch_initiated_order) %>%
-  left_join(select(clutch_unambig_NOr_revised_ENAa_summary_imfilt_success_summary_v2,
-                   -c(ants_removed, females_removed, initiation_date, n_eggs)),
-            by=c("location"="NOr_rev_loc")) %>%
-  select(Female_ID, location, initiation_date, hatch_date, 
-         guard_duration, max_primary_dur, desert_rel2h, focalMb4h_sc2h, mDb4h_sc2h,
-         med_t5eggs, n_hatched, n_survived, females_removed,
-         mom_at_init, clutch_visited_order, clutch_initiated_order) %>%
-  mutate(propD_b4h = focalMb4h_sc2h/mDb4h_sc2h,
-         est_eggs_clutch = med_t5eggs*propD_b4h,
-         zink_est_hatch_clutch_v1 = med_t5eggs*(coef(zink_hatch.m)[[1]]+guard_duration*coef(zink_hatch.m)[[2]]),
-         zink_est_hatch_clutch_v2 = est_eggs_clutch*(coef(zink_hatch.m)[[1]]+guard_duration*coef(zink_hatch.m)[[2]])) %>%
-  group_by(Female_ID) %>%
-    mutate(zink_est_hatch_life_v1 = sum(zink_est_hatch_clutch_v1, na.rm=T),
-           zink_est_hatch_life_v2 = sum(zink_est_hatch_clutch_v2, na.rm=T)) %>%
-  ungroup()
-
-est_fitness_life_strats_Zink <- est_fitness_clutch_zink %>%
-  group_by(Female_ID) %>%
-  # clutch visited order == 0 means she visited before initiation, so it shouldn't count
-  mutate(started_by =
-           ifelse(any(clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order==1),
-                  "initiating",
-                  ifelse(any(clutch_visited_order==1&is.na(clutch_initiated_order)|
-                             clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order!=1),
-                         "visiting", "other")),
-         n_clutches_with_eggs_iv = sum(!is.na(clutch_visited_order)&(clutch_visited_order>0), na.rm=T)) %>%
-  ungroup() %>%
-  filter(clutch_visited_order==1) %>%
-  # mutate(desert_cat = ifelse(started_by=="initiating",
-  #                                ifelse(desert_rel2h <= -16, "desert",
-  #                                       ifelse(desert_rel2h > -16 & desert_rel2h <= 4, "eggs", 
-  #                                              ifelse(desert_rel2h >= 4,"nymphs",
-  #                                                     NA))),
-  #                                ifelse(started_by=="visiting", "visit", 
-  #                                       NA)),
-  mutate(desert_cat = ifelse(started_by=="initiating",
-                                 ifelse(guard_duration <= 10, "desert",
-                                        ifelse(guard_duration > 10 & desert_rel2h <= 4, "eggs", 
-                                               ifelse(guard_duration >= 4,"nymphs",
-                                                      NA))),
-                                 ifelse(started_by=="visiting", "visit", 
-                                        NA)),
-         zink_dur_cat = ifelse(started_by=="initiating",
-                               ifelse(guard_duration<12, "desert",
-                                      ifelse(guard_duration>=12, "stay", NA)),
-                               ifelse(started_by=="visiting", "visit", 
-                                        NA))) %>%
-  distinct(Female_ID, females_removed,
-           guard_duration, max_primary_dur,
-           started_by, desert_cat, zink_dur_cat,
-           zink_est_hatch_clutch_v1, zink_est_hatch_clutch_v2,
-           zink_est_hatch_life_v1, zink_est_hatch_life_v2,
-           n_clutches_with_eggs_iv)
-
-# v1: Zink 2003 attributes all egg in a clutch to the primary female, even if they desert early and a visitor laid additional eggs
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v1, fill=zink_dur_cat)) +
-  geom_boxplot(size=1.5) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  stat_summary(fun=mean, geom="point", shape=4, size=6) +
-  ggtitle("v1: all eggs in clutch to primary female")
-
-# v2: all calculations the same, but give eggs to females in proportion to the time they spent at clutch relative to other females
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v2, fill=zink_dur_cat)) +
-  geom_boxplot(size=1.5) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  stat_summary(fun=mean, geom="point", shape=4, size=6) +
-  ggtitle("v2: eggs to female by proportion of time guarding")
-
-# same but separating females that laid one vs. multiple clutches
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v1, fill=zink_dur_cat)) +
-  geom_boxplot(size=1.5) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  stat_summary(fun=mean, geom="point", shape=4, size=6) +
-  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
-  ggtitle("v1: all eggs in clutch to primary female")
-
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=zink_dur_cat, y=zink_est_hatch_life_v2, fill=zink_dur_cat)) +
-  geom_boxplot(size=1.5) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  stat_summary(fun=mean, geom="point", shape=4, size=6) +
-  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
-  ggtitle("v2: eggs to female by proportion of time guarding")
-
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v1, fill=desert_cat)) +
-  geom_boxplot(size=1.5) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  stat_summary(fun=mean, geom="point", shape=4, size=6) +
-  ggtitle("v1: all eggs in clutch to primary female")
-
-# same but using desert_cat instead of Zink 2003 cats
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v1, fill=desert_cat)) +
-  geom_boxplot(size=1.5) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  stat_summary(fun=mean, geom="point", shape=4, size=6) +
-  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
-  ggtitle("v1: all eggs in clutch to primary female")
-
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v2, fill=desert_cat)) +
-  geom_boxplot(size=1.5) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  stat_summary(fun=mean, geom="point", shape=4, size=6) +
-  ggtitle("v2: eggs to female by proportion of time guarding")
-
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=zink_est_hatch_life_v2, fill=desert_cat)) +
-  geom_boxplot(size=1.5) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  stat_summary(fun=mean, geom="point", shape=4, size=6) +
-  facet_wrap(vars(n_clutches_with_eggs_iv!=1)) +
-  ggtitle("v2: eggs to female by proportion of time guarding")
-
-```
-
 # Other measures of fecundity
@@
 ## First clutch vs. future fecundity and fitness
+
+```{r}
+letterSize <- 3
+```
+
 Fecundity
@@
   fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_clutch, group=desert_cat, 
-                    itero=F, multcompLetters=fitness_first_stats_eggs_v6$multcompLetters,
-                    letterSize=letterSize, ymax=160) +
+                    itero=F, multcompLetters=fitness_first_stats_eggs_v6$multcompLetters,ymax=160) +
   ylab("First-clutch fecundity\n(eggs laid)") + 
@@
                     itero=F, multcompLetters=fitness_future_stats_eggs_v6$multcompLetters,
-                    letterSize=letterSize, ymax=160) +
+                    ymax=160) +
   ylab("Future fecundity\n(eggs laid)") + 
@@
                     itero=T, multcompLetters=fitness_future_stats_eggs.itero$multcompLetters,
-                    letterSize=letterSize, ymax=160)$itero +
+                    ymax=160)$itero +
   ylab("Multi-clutch future\nfecundity (eggs laid)") + 
@@
                     itero=F, multcompLetters=fitness_life_stats_eggs_v6$multcompLetters,
-                    letterSize=letterSize, ymax=160) +
+                    ymax=160) +
   ylab("Lifetime fecundity\n(eggs laid)") + 
@@
                     itero=T, multcompLetters=fitness_future_stats_hatched.itero$multcompLetters,
-                    letterSize=letterSize, ymax=75)$itero +
+                    ymax=75)$itero +
   ylab("Multi-clutch future\nfitness (eggs hatch)") + 
@@
                     itero=T, multcompLetters=fitness_future_stats_survived.itero$multcompLetters,
-                    letterSize=letterSize, ymax=22)$itero +
+                    ymax=22)$itero +
   ylab("Multi-clutch future\nfitness (nymphs survive)") + 
@@
                     itero=T, multcompLetters=fitness_future_stats_eggs.itero.DEN$multcompLetters,
-                    letterSize=letterSize, ymax=160)$itero +
+                    ymax=160)$itero +
   ylab("Multi-clutch future\nfecundity (eggs laid)") + 
@@
                     itero=T, multcompLetters=fitness_future_stats_hatched.itero.DEN$multcompLetters,
-                    letterSize=letterSize, ymax=75)$itero +
+                    ymax=75)$itero +
   ylab("Multi-clutch future\nfitness (eggs hatch)") + 
@@
                     itero=T, multcompLetters=fitness_future_stats_survived.itero.DEN$multcompLetters,
-                    letterSize=letterSize, ymax=22)$itero +
+                    ymax=22)$itero +
   ylab("Multi-clutch future\nfitness (nymphs survive)") + 
@@
                     multcompLetters=fitness_future_stats_hatched$multcompLetters,
-                    letterSize=letterSize, ymax=75) +
+                    ymax=75) +
   ylab("Future\nfitness (eggs hatch)") + 
@@
                     multcompLetters=fitness_future_stats_survived$multcompLetters,
-                    letterSize=letterSize, ymax=22) +
+                    ymax=22) +
   ylab("Future\nfitness (nymphs survive)") + 
@@
                     itero=F, multcompLetters=fitness_stats_eggs_v6$multcompLetters,
-                    letterSize=letterSize, ymax=160) +
+                    ymax=160) +
   ylab("Lifetime fecundity\n(eggs laid)") + 
@@
                     itero=F, multcompLetters=fitness_stats_hatched_v6$multcompLetters,
-                    letterSize=letterSize, ymax=100) +
+                    ymax=100) +
   ylab("Lifetime fitness\n(eggs hatched)") + 
@@
                     itero=F, multcompLetters=fitness_stats_survived_v6$multcompLetters,
-                    letterSize=letterSize, ymax=30) +
+                    ymax=30) +
   ylab("Lifetime fitness\n(nymphs survived)") + 
@@
 
-ggsave("fitness_stats.violin.final.png",
+ggsave(here("prelim_figs/Publilia-05-fitness/fitness_stats.violin.final.png"),
        fitness_stats.v6.p.final,
@@
                     itero=F, multcompLetters=fitness_stats_eggs_v1$multcompLetters,
-                    letterSize=letterSize, ymax=160) +
+                    ymax=160) +
   ylab("Lifetime fecundity\n(eggs laid)") + 
@@
                     itero=F, multcompLetters=fitness_stats_hatched_v1$multcompLetters,
-                    letterSize=letterSize, ymax=100) +
+                    ymax=100) +
   ylab("Lifetime fitness\n(eggs hatched)") + 
@@
                     itero=F, multcompLetters=fitness_stats_survived_v1$multcompLetters,
-                    letterSize=letterSize, ymax=30) +
+                    ymax=30) +
   ylab("Lifetime fitness\n(nymphs survived)") + 
@@
 
-ggsave("fitness_stats.supp_v1.violin.final.png",
+ggsave(here("prelim_figs/Publilia-05-fitness/fitness_stats.supp_v1.violin.final.png"),
        fitness_stats.v1.p.final,
@@
                     itero=T, multcompLetters=fitness_stats_eggs.semel$multcompLetters,
-                    letterSize=letterSize, ymax=160)$semel +
+                    ymax=160)$semel +
   ylab("Single-clutch female\nfecundity (eggs laid)") + 
@@
                     itero=T, multcompLetters=fitness_stats_eggs.itero$multcompLetters,
-                    letterSize=letterSize, ymax=160)$itero +
+                    ymax=160)$itero +
   ylab("Multi-clutch female\nfecundity (eggs laid)") + 
@@
                     itero=T, multcompLetters=fitness_stats_hatched.semel$multcompLetters,
-                    letterSize=letterSize, ymax=100)$semel +
+                    ymax=100)$semel +
   ylab("Single-clutch female\nfitness (eggs hatched)") + 
@@
                     itero=T, multcompLetters=fitness_stats_hatched.itero$multcompLetters,
-                    letterSize=letterSize, ymax=100)$itero +
+                    ymax=100)$itero +
   ylab("Multi-clutch female\nfitness (eggs hatched)") + 
@@
                     itero=T, multcompLetters=fitness_stats_survived.semel$multcompLetters,
-                    letterSize=letterSize, ymax=30)$semel +
+                    ymax=30)$semel +
   ylab("Single-clutch female\nfitness (nymphs survived)") + 
@@
                     itero=T, multcompLetters=fitness_stats_survived.itero$multcompLetters,
-                    letterSize=letterSize, ymax=30)$itero +
+                    ymax=30)$itero +
   ylab("Multi-clutch female\nfitness (nymphs survived)") + 
@@
 
-ggsave("fitness_stats.violin.parity.final.png",
+ggsave(here("prelim_figs/Publilia-05-fitness/fitness_stats.violin.parity.final.png"),
        fitness_stats.parity.p.final,
@@
        width = 200, height = 200, units = "mm", dpi = "print")
-```
-
-## Comparing to Zink 2003 fitness measures
-Lifetime fitness (number of eggs that hatched):
-w(t_i) = sum(from i=1, to i=N, P_i*g(t_i))
-P = number of eggs invested in a clutch (all the eggs go to the initiator?)
-t_i = guarding duration in clutch i
-N = lifetime number of clutches
-g(t) = relationship between guarding duration and hatching success
- (assume g(t) equivalent across all clutches 1 to N)
-
-* The main reason Zink found equivalent fitness is that he attributed all the eggs in a clutch to each primary female.
-Thus an early deserter is given all the eggs from a clutch, even if she leaves within a few days and another female arrives and lays additional eggs.
-```{r}
-ggplot(data=filter(surv_reg_data_zink, initiation_date<=as_date("2019-06-10")), 
-       aes(x=max_primary_dur, y=n_hatched/med_t5eggs)) +
-  geom_point() +
-  geom_smooth(method=lm)
-
-zink_hatch.m <- surv_reg_data_zink %>%
-  filter(initiation_date<=as_date("2019-06-10"), !is.na(n_hatched/med_t5eggs)) %>%
-lm(n_hatched/med_t5eggs ~ max_primary_dur, data=.)
-
-summary(zink_hatch.m) # use this for predicting hatching success
-```
-
-```{r}
-zink_fitness_plot_dunn <- function(data, y, group, multcompLetters, letterSize, ymax=160){
-  (p <- eval(substitute(data %>%
-    filter(!females_removed, !is.na(desert_cat)) %>%
-    ggplot(data=., aes(x=group, y=y)) + ylim(-ymax*0.05,ymax) +
-    geom_boxplot(aes(fill=group), 
-                 position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
-    stat_summary(aes(fill=group), 
-                 fun=mean, geom="point", shape=4, size=3, color="black", key_glyph=draw_key_rect) +
-    #ylab("Lifetime fecundity\n(eggs laid)")  +
-    xlab("Guarding strategy for first clutch") +
-    theme_publilia() +
-    geom_text(data=multcompLetters, aes(x=x, y=-ymax*0.05, label=label), fontface="bold", size=letterSize))))
-  return(p)
-}
-```
-
-```{r}
-# v1: Zink 2003 attributes all egg in a clutch to the primary female, even if they desert early and a visitor laid additional eggs
-zink_fitness_stats_v1 <- 
-  fitness_KW_test(data=est_fitness_life_strats_Zink, y=zink_est_hatch_life_v1, group=zink_dur_cat)
-(Zink_fitness_v1.p <- 
-  zink_fitness_plot_dunn(data=est_fitness_life_strats_Zink, y=zink_est_hatch_life_v1, group=zink_dur_cat, 
-                    multcompLetters=zink_fitness_stats_v1$multcompLetters,
-                    letterSize=4, ymax=150) +
-  ylab("Lifetime fitness: Zink 2003\n(all eggs to primary mother,\nlinear model predicts hatching)") +
-    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
-    theme(legend.position="none",
-          axis.text.x=element_text(angle=45, vjust=1, hjust=1)))
-
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed, !is.na(desert_cat)) %>%
-  group_by(zink_dur_cat) %>% 
-    summarize(mean_fitness=mean(zink_est_hatch_life_v1),
-              median_fitness=median(zink_est_hatch_life_v1))
-
-# v2: all calculations the same, but give eggs to females in proportion to the time they spent at clutch relative to other females
-zink_fitness_stats_v2 <- 
-  fitness_KW_test(data=est_fitness_life_strats_Zink, y=zink_est_hatch_life_v2, group=zink_dur_cat)
-(Zink_fitness_v2.p <- 
-  zink_fitness_plot_dunn(data=est_fitness_life_strats_Zink, y=zink_est_hatch_life_v2, group=zink_dur_cat, 
-                    multcompLetters=zink_fitness_stats_v2$multcompLetters,
-                    letterSize=4, ymax=150) +
-  ylab("Lifetime fitness: modified from Zink 2003\n(eggs proportional to guarding,\nlinear model predicts hatching)") +
-    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
-    theme(legend.position="none",
-          axis.text.x=element_text(angle=45, vjust=1, hjust=1)))
-
-(Zink_fitness.p.final <- egg::ggarrange(
-  Zink_fitness_v1.p, Zink_fitness_v2.p, 
-  labels=c("A","B"),
-  ncol=2, nrow=1))
-
-ggsave("Zink_fitness.final.png",
-       Zink_fitness.p.final,
-       device = "png",
-       width = 200, height = 120, units = "mm", dpi = "print")
-
-# same but separating females that laid one vs. multiple clutches
-zink_fitness_data.semel <- est_fitness_life_strats_Zink %>% 
-  filter(n_clutches_with_eggs_iv==1)
-zink_fitness_stats_v1.semel <- 
-  fitness_KW_test(data=zink_fitness_data.semel, y=zink_est_hatch_life_v1, group=zink_dur_cat)
-(Zink_fitness_v1.semel.p <- 
-  zink_fitness_plot_dunn(data=zink_fitness_data.semel, y=zink_est_hatch_life_v1, group=zink_dur_cat, 
-                    multcompLetters=zink_fitness_stats_v1.semel$multcompLetters,
-                    letterSize=4, ymax=150) +
-  ylab("Lifetime fitness: Zink 2003\n(all eggs to primary mother,\nlinear model predicts hatching)") +
-    ggtitle("Single-clutch mothers") +
-    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
-    theme(legend.position="none",
-          axis.title.x = element_blank(),axis.text.x=element_blank()))
-
-zink_fitness_data.itero <- est_fitness_life_strats_Zink %>% 
-  filter(n_clutches_with_eggs_iv>1)
-zink_fitness_stats_v1.itero <- 
-  fitness_KW_test(data=zink_fitness_data.itero, y=zink_est_hatch_life_v1, group=zink_dur_cat)
-(Zink_fitness_v1.itero.p <- 
-  zink_fitness_plot_dunn(data=zink_fitness_data.itero, y=zink_est_hatch_life_v1, group=zink_dur_cat, 
-                    multcompLetters=zink_fitness_stats_v1.itero$multcompLetters,
-                    letterSize=4, ymax=150) + ggtitle("Multi-clutch mothers") +
-    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
-    theme(legend.position="none",
-          axis.title.x = element_blank(),axis.text.x=element_blank(),
-          axis.title.y = element_blank(),axis.text.y=element_blank()))
-
-zink_fitness_data.semel <- est_fitness_life_strats_Zink %>% 
-  filter(n_clutches_with_eggs_iv==1)
-zink_fitness_stats_v2.semel <- 
-  fitness_KW_test(data=zink_fitness_data.semel, y=zink_est_hatch_life_v2, group=zink_dur_cat)
-(Zink_fitness_v2.semel.p <- 
-  zink_fitness_plot_dunn(data=zink_fitness_data.semel, y=zink_est_hatch_life_v2, group=zink_dur_cat, 
-                    multcompLetters=zink_fitness_stats_v2.semel$multcompLetters,
-                    letterSize=4, ymax=150) +
-  ylab("Lifetime fitness: modified from Zink 2003\n(all eggs to primary mother,\nlinear model predicts hatching)") +
-    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
-    theme(legend.position="none",
-          axis.text.x=element_text(angle=45, vjust=1, hjust=1)))
-
-zink_fitness_data.itero <- est_fitness_life_strats_Zink %>% 
-  filter(n_clutches_with_eggs_iv>1)
-zink_fitness_stats_v2.itero <- 
-  fitness_KW_test(data=zink_fitness_data.itero, y=zink_est_hatch_life_v2, group=zink_dur_cat)
-(Zink_fitness_v2.itero.p <- 
-  zink_fitness_plot_dunn(data=zink_fitness_data.itero, y=zink_est_hatch_life_v2, group=zink_dur_cat, 
-                    multcompLetters=zink_fitness_stats_v2.itero$multcompLetters,
-                    letterSize=4, ymax=150) +
-    # geom_jitter(aes(fill=ants_removed), pch = 21, size=3, width=0.35) + 
-    theme(legend.position="none",
-          axis.text.x=element_text(angle=45, vjust=1, hjust=1),
-          axis.title.y = element_blank(),axis.text.y=element_blank()))
-
-(Zink_fitness.parity.p.final <- egg::ggarrange(
-  Zink_fitness_v1.semel.p, Zink_fitness_v1.itero.p,
-  Zink_fitness_v2.semel.p, Zink_fitness_v2.itero.p,
-  labels=c("A","B","C","D"),
-  ncol=2, nrow=2))
-
-ggsave("Zink_fitness.parity.final.png",
-       Zink_fitness.parity.p.final,
-       device = "png",
-       width = 200, height = 200, units = "mm", dpi = "print")
-
-```
-
-why such a small first clutch and larger future clutches for early deserters? early deserters lay more or larger clutches?
-```{r}
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed) %>%
-  mutate(parity=ifelse(n_clutches_with_eggs_iv==1,"semel","itero")) %>%
-  count(parity,zink_dur_cat)
-
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed) %>%
-  mutate(parity=ifelse(n_clutches_with_eggs_iv==1,"semel","itero")) %>%
-  group_by(zink_dur_cat,parity) %>%
-  summarize(n=n(),
-            mean_n_clutches=mean(n_clutches_with_eggs_iv),
-            mean_max_primary_dur=mean(max_primary_dur)) %>%
-  ungroup()
-
-est_fitness_life_strats_Zink %>%
-  filter(!females_removed) %>%
-  mutate(parity=ifelse(n_clutches_with_eggs_iv==1,"semel","itero")) %>%
-  group_by(desert_cat,parity) %>%
-  summarize(n=n(),
-            mean_n_clutches=mean(n_clutches_with_eggs_iv),
-            mean_max_primary_dur=mean(max_primary_dur)) %>%
-  ungroup()
-
-fitness_life_strats_data %>%
-  filter(!females_removed) %>%
-  mutate(parity=ifelse(n_clutches_with_eggs_iv==1,"semel","itero")) %>%
-  group_by(parity, ants_removed, desert_cat) %>%
-  summarize(n=n(),
-            mean_n_clutches=mean(n_clutches_with_eggs_iv)) %>%
-  ungroup()
-
 ```
@@
 
-ggsave("predicted_clutch.final.png",
+ggsave(here("prelim_figs/Publilia-05-fitness/predicted_clutch.final.png"),
        predicted_clutch.p.final,
@@
 ### Estimating fitness from counts instead of from survivorship function
+2023.08.26 - `fitness_plot_dunn()` with `group=desert_cat_ants` caused error so changed to `group=desert_cat`, as for iterations above
 ```{r}
@@
   fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
+fitness_stats_eggs_counted["multcompLetters"]$multcompLetters$x <- 
+  rep(c("visit", "desert","eggs", "nymphs"),2)
+fitness_stats_eggs_counted["multcompLetters"]$multcompLetters <- 
+  bind_cols(fitness_stats_eggs_counted["multcompLetters"]$multcompLetters, 
+            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
+
 (fitness_counted_stats_eggs.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants, 
+  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
                     itero=F, multcompLetters=fitness_stats_eggs_counted$multcompLetters,
@@
   fitness_KW_test(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat_ants)
+fitness_stats_hatched_counted["multcompLetters"]$multcompLetters$x <- 
+  rep(c("visit", "desert","eggs", "nymphs"),2)
+fitness_stats_hatched_counted["multcompLetters"]$multcompLetters <- 
+  bind_cols(fitness_stats_hatched_counted["multcompLetters"]$multcompLetters, 
+            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
+
 (fitness_counted_stats_hatched.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat_ants, 
+  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat, 
                     itero=F, multcompLetters=fitness_stats_hatched_counted$multcompLetters,
@@
   fitness_KW_test(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat_ants)
+
+fitness_stats_survived_counted <- 
+  fitness_KW_test(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat_ants)
+fitness_stats_survived_counted["multcompLetters"]$multcompLetters$x <- 
+  rep(c("visit", "desert","eggs", "nymphs"),2)
+fitness_stats_survived_counted["multcompLetters"]$multcompLetters <- 
+  bind_cols(fitness_stats_survived_counted["multcompLetters"]$multcompLetters, 
+            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
+
 (fitness_counted_stats_survived.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat_ants, 
+  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat, 
                     itero=F, multcompLetters=fitness_stats_survived_counted$multcompLetters,
@@
 
-# ggsave("CHAPTER/fitness_counted_stats.final.png",
-#        fitness_counted_stats.p.final,
-#        device = "png",
-#        width = 120, height = 200, units = "mm", dpi = "print")
-```
+ggsave(here("prelim_figs/Publilia-05-fitness/fitness_counted_stats.final.png"),
+       fitness_counted_stats.p.final,
+       device = "png",
+       width = 120, height = 200, units = "mm", dpi = "print")
+```

### 2023-08-26 scripts/Publilia-06-fitness_sensu_Zink.Rmd
Moved Zink fitness analysis to it's own script + saved survorship model fits from script 03 to use in 05 + other minor edits to script 05 to run without error

--- 2023-08-24 scripts/old/Publilia_2019_CHAPTER-2C-fitness.Rmd
@@
 ---
-title: "Publilia_2019_CHAPTER-2C-fitness"
-author: "micah fletcher"
-date: "2/24/2022"
-output: html_document
+title: '06 - PubliliaFitness - Estimating lifetime fecundity and fitness using formulas from Zink 2003'
+author: "Micah Fletcher"
+date: '`r Sys.Date()`'
+output: 
+  rmdformats::robobook:
+  fig_width: 9
+toc_depth: 3
 ---
 
-# Publilia 2019 Chapter - Script 2C: estimating fitness
-This is meant to consolidate previous scripts and provide a readable and reproducible record of the analyses for the Publilia Chapter.
+# Load libraries
 
-## Lifetime fitness using regression predictions
-Custom functions for using survivorship regression predictions to estimate fitness
 ```{r}
-ci_for_fitness <- function(data_in, survNom, survDen, 
-                        tenure, treatment, vis, model){
-  data <- eval(substitute(
-    data_in %>%
-      add_column(fit = predict(model, newdata = ., type = 'response'))
-    ))
-  ## grad the inverse link function
-  ilink <- family(model)$linkinv
-  ## add fit and se.fit on the **link** scale
-  data_fit_link <- eval(substitute(
-    data %>% add_column(
-  setNames(as_tibble(predict(model, data, se.fit = TRUE)[1:2]),
-           c('fit_link','se_link'))) %>%
-## create the interval and backtransform
-  mutate(fit_resp  = ilink(fit_link),
-         conf_upr = ilink(fit_link + (2 * se_link)),
-         conf_lwr = ilink(fit_link - (2 * se_link)))
-    ))
-  return(data_fit_link)
-}
+library(multcompView)
+source(here("R/Publilia-05-fitness-functions.R"))
 ```
 
-# Estimating fitness using different methods
-There are several outdated versions that I've since deleted
- - “v2”: (survivorship ~ ant_treatment * desL) * proportion of time on eggs
- - “v3”: (survivorship ~ ants_ever * desL) * proportion of time on eggs
- - “v4”: (survivorship ~ ants_ever * desP) * proportion of time on eggs
- - “v5”: (survivorship ~ ants_ever * I(desP^2)) * proportion of time on eggs
-
-The current versions are:
- - v1: raw offspring count * proportion of time on eggs
- - v6: (survivorship ~ ant_treatment * I(desL^2)) * proportion of time on eggs
-
-Not time for dissertation but I could experiment with using a square root function for egg laying (more eggs in the first few days of guarding/visiting) and see how robust these results are to our assumptions about egg laying behavior.
-```{r}
-est_fitness_prep <- visited_1st_4d_data %>%
-  filter(!is.na(initiation_date)) %>%
-  group_by(Female_ID) %>%
-  mutate(started_by_initiating =
-           any(clutch_visited_order==1&clutch_initiated_order==1)) %>%
-  ungroup() %>%
-  select(location, Female_ID, clutch_visited_order, clutch_initiated_order, 
-         desert_rel2h = est_rel2h, guard_duration,
-         mom_at_init, started_by_initiating) %>%
-  left_join(select(clutch_survivorship_data, location:last_desert, 
-                   n_eggs, med_t5eggs, n_hatched, n_survived, DormPlant), 
-            by=c("location")) %>%
-  left_join(select(focalMb4h_sc2h, Female_ID, location, focalMb4h_sc2h),
-            by=c("Female_ID", "location")) %>%
-  mutate(des=last_des_rel2h, 
-         ants=ifelse(ants_removed,"Removed","Control"),
-         vis=`visited in 4 days`) %>%
-  left_join(select(ant_counts, location, ever_antsP)) %>%
-  separate(location, into = c("DormPlant", "Leaf"), sep="_", remove=FALSE) %>%
-  left_join(dplyr::select(moms_plant_data, DormPlant, last_visit_ends_P), by="DormPlant") %>%
-  mutate(last_desP_rel2h = last_visit_ends_P-est_hatch,
-         ant_treatment=ifelse(ants_removed,"Removed","Control"))
-
-# v6: (survivorship ~ ant_treatment * I(desL^2)) * proportion of time on eggs
-est_fitness_hatch_fit_v6 <- 
-  ci_for_fitness(data_in=est_fitness_prep, model=des_hatch.desL.ant_treatment.quad.fits$mai.qb) %>%
-  mutate(est_hatch_fit_v6 = fit) %>%
-  select(-(fit:conf_lwr))
-est_fitness_Esurv_fit_v6 <- 
-  ci_for_fitness(data_in=est_fitness_hatch_fit_v6, model=des_Esurv.desL.ant_treatment.quad.fits$mai.qb) %>%
-  mutate(est_Esurv_fit_v6 = fit) %>%
-  select(-(fit:conf_lwr))
-
-est_fitness_clutch <- est_fitness_Esurv_fit_v6 %>%
-  mutate(propD_b4h = focalMb4h_sc2h/mDb4h_sc2h,
-         est_eggs_clutch = med_t5eggs*propD_b4h,
-         est_hatched_clutch_v1 = n_hatched*propD_b4h,
-         est_survived_clutch_v1 = n_survived*propD_b4h,
-         est_hatched_clutch_v6 = est_eggs_clutch*est_hatch_fit_v6,
-         est_survived_clutch_v6 = est_eggs_clutch*est_Esurv_fit_v6) %>%
-  group_by(Female_ID) %>%
-    mutate(est_eggs_life = sum(est_eggs_clutch, na.rm = T),
-           est_hatched_life_v1 = sum(est_hatched_clutch_v1, na.rm = T),
-           est_survived_life_v1 = sum(est_survived_clutch_v1, na.rm = T),
-           est_hatched_life_v6 = sum(est_hatched_clutch_v6, na.rm = T),
-           est_survived_life_v6 = sum(est_survived_clutch_v6, na.rm = T),
-           n_clutches_iv = n(),
-           n_initiated = sum(!is.na(clutch_initiated_order)),
-           n_visited = sum(!is.na(initiation_date)&is.na(clutch_initiated_order)),
-           n_feed = sum(is.na(initiation_date)),
-           init_visit_life_tactic = ifelse(any(mom_at_init), 
-                                           ifelse(any(!mom_at_init), "Both", "Initiated only"),
-                                           ifelse(!any(mom_at_init), "Visited only", NA)),
-           one_both_life_tactic = ifelse(any(mom_at_init), 
-                                           ifelse(any(!mom_at_init), "Both", "One"),
-                                           ifelse(!any(mom_at_init), "One", NA))) %>%
-  ungroup()
-
-est_fitness_future <- est_fitness_clutch %>%
-  filter(clutch_visited_order == 1) %>%
-  mutate(est_eggs_future = est_eggs_life - est_eggs_clutch,
-         est_hatched_future_v1 = est_hatched_life_v1 - est_hatched_clutch_v1,
-         est_hatched_future_v6 = est_hatched_life_v6 - est_hatched_clutch_v6,
-         est_survived_future_v1 = est_survived_life_v1 - est_survived_clutch_v1,
-         est_survived_future_v6 = est_survived_life_v6 - est_survived_clutch_v6)
-
-est_fitness_strat_cats <- est_fitness_future %>%
-  dplyr::select(Female_ID, location, desert_rel2h, last_des_rel2h,
-         med_t5eggs, est_eggs_clutch, 
-         est_hatched_life_v1, est_hatched_life_v6,
-         est_hatched_future_v1, est_hatched_future_v6,
-         est_survived_life_v1, est_survived_life_v6,
-         est_survived_future_v1, est_survived_future_v6,
-         females_removed, ants_removed, clutch_initiated_order,
-         n_clutches_iv, n_initiated, n_visited, init_visit_life_tactic, `visited in 4 days`)
-```
-
-## Check how I'm calculating fecundity
-```{r}
-# no need to separate females_removed
-est_fitness_clutch %>% 
-  filter(!is.na(est_eggs_clutch)) %>%
-  ggplot(data=., aes(x=des, y=est_eggs_clutch, color=ants, fill=ants)) +
-  geom_point() +
-  geom_smooth() + ylim(0,60) +
-  facet_wrap(vars(vis))
-
-est_fitness_clutch %>%
-  arrange(Female_ID) %>%
-  select(Female_ID, location, focalMb4h_sc2h, mDb4h_sc2h, propD_b4h, 
-         med_t5eggs, est_eggs_clutch, est_eggs_life) #%>% View()
-```
-
-## Check how I'm estimating hatching and survival and how many clutches are recovered
-It might be that using the regression model with a continuous desertion date explanatory variable just cannot adequately capture the variation and will always deflate mean and variance in lifetime fitness (# N5).
-If I want a more accurate representation of the variation, maybe I should use discrete desertion date categories (boxplots) and explicitly include variance in the imputation.
-But will this lead to strange results when the metric determining eggs contributed is continuous?
-I don't have time to do this for the dissertation but I could explore it for the paper.
-```{r}
-# Check how I'm estimating hatching and survival and how many clutches are recovered
-est_fitness_clutch %>%
-  count(females_removed, !is.na(est_eggs_clutch), !is.na(est_hatched_clutch_v1), !is.na(est_survived_clutch_v1))
-
-est_fitness_clutch %>%
-  count(females_removed, !is.na(est_eggs_clutch), !is.na(est_hatched_clutch_v6), !is.na(est_survived_clutch_v6))
-
-# It appears that my modeling is overestimating the number of nymphs hatched for clutches with very low est hatched v1
-est_fitness_clutch %>% 
-  filter(!is.na(est_hatched_clutch_v1),!is.na(est_hatched_clutch_v6)) %>%
-  ggplot(data=., aes(x=est_hatched_clutch_v1, y=est_hatched_clutch_v6, color=sum_vD==0)) +
-  geom_abline(slope=1) +
-  geom_point()
-
-# v6: Consistency is MUCH worse for survivorship; MANY clutches with no surviving nymphs were predicted to have survived
-est_fitness_clutch %>%
-  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
-  ggplot(data=., aes(x=est_survived_clutch_v1, y=est_survived_clutch_v6, color=vis)) +
-  geom_abline(slope=1) +
-  geom_point() + facet_wrap(~females_removed)
-
-est_fitness_clutch %>%
-  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
-  ggplot(data=., aes(x=est_survived_clutch_v1, y=est_survived_clutch_v6, color=interaction(vis,ants))) +
-  geom_abline(slope=1) +
-  geom_point()  + xlim(0,60) + ylim(0,60)
-
-### how well does this work from the perspective of imputation?
-# hatching: ok correspondence, the spread is tighter, but range is preserved
-est_fitness_clutch %>% 
-  filter(!is.na(est_hatched_clutch_v1),!is.na(est_hatched_clutch_v6)) %>%
-  ggplot(data=., aes(x=des, y=est_hatched_clutch_v1, color=ants, fill=ants)) +
-  geom_point() +
-  geom_smooth() + ylim(0,60) +
-  facet_wrap(vars(vis))
-
-est_fitness_clutch %>% 
-  filter(!is.na(est_hatched_clutch_v6)) %>%
-  ggplot(data=., aes(x=des, y=est_hatched_clutch_v6, color=ants, fill=ants)) +
-  geom_point() +
-  geom_smooth() + ylim(0,60) +
-  facet_wrap(vars(vis))
-
-# survival: ok correspondence, the spread is MUCH tighter and range is more limited; losing many higher values
-est_fitness_clutch %>% 
-  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
-  ggplot(data=., aes(x=des, y=est_survived_clutch_v1, color=ants, fill=ants)) +
-  geom_point() +
-  geom_smooth() + ylim(0,60) +
-  facet_wrap(vars(vis))
-
-est_fitness_clutch %>% 
-  filter(!is.na(est_survived_clutch_v6)) %>%
-  ggplot(data=., aes(x=des, y=est_survived_clutch_v6, color=ants, fill=ants)) +
-  geom_point() +
-  geom_smooth() + ylim(0,60) +
-  facet_wrap(vars(vis))
-```
-
-Only females that laid more than one clutch
-```{r}
-est_fitness_clutch %>%
-  filter(!is.na(est_hatched_clutch_v1),!is.na(est_hatched_clutch_v6)) %>%
-  ggplot(data=., aes(x=est_hatched_clutch_v1, y=est_hatched_clutch_v6)) +
-  geom_abline(slope=1) +
-  geom_point() +
-  facet_wrap(~n_initiated>1)
-
-est_fitness_clutch %>%
-  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
-  ggplot(data=., aes(x=est_survived_clutch_v1, y=est_survived_clutch_v6)) +
-  geom_abline(slope=1) +
-  geom_point() +
-  facet_wrap(~n_initiated>1)
-```
-
-### Life strategies: start by deserting early, guarding eggs, guarding nymphs or visited an existing clutch
-```{r}
-est_fitness_life_strats <- est_fitness_clutch %>%
-  group_by(Female_ID) %>%
-  # clutch visited order == 0 means she visited before initiation, so it shouldn't count
-  mutate(started_by =
-           ifelse(any(clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order==1),
-                  "initiating",
-                  ifelse(any(clutch_visited_order==1&is.na(clutch_initiated_order)|
-                             clutch_visited_order==1&!is.na(clutch_initiated_order)&clutch_initiated_order!=1),
-                         "visiting", "other")),
-         n_clutches_with_eggs_iv = sum(!is.na(clutch_visited_order)&(clutch_visited_order>0), na.rm=T)) %>%
-  ungroup() %>%
-  filter(clutch_visited_order==1) %>%
-  # mutate(desert_cat = ifelse(started_by=="initiating",
-  #                                ifelse(desert_rel2h <= -16, "desert",
-  #                                       ifelse(desert_rel2h > -16 & desert_rel2h <= 4, "eggs", 
-  #                                              ifelse(desert_rel2h >= 4,"nymphs",
-  #                                                     NA))),
-  #                                ifelse(started_by=="visiting", "visit", 
-  #                                       NA)),
-  mutate(desert_cat = ifelse(started_by=="initiating",
-                                 ifelse(guard_duration <= 10, "desert",
-                                        ifelse(guard_duration > 10 & desert_rel2h <= 4, "eggs", 
-                                               ifelse(desert_rel2h >= 4,"nymphs",
-                                                      NA))),
-                                 ifelse(started_by=="visiting", "visit", 
-                                        NA)),
-         first_clutch_visited_in4d = ifelse(started_by=="initiating",
-                                            ifelse(`visited in 4 days` == "Visited", "vis", "not"),
-                                            NA),
-         est_eggs_future = est_eggs_life - est_eggs_clutch,
-         est_hatched_future_v1 = est_hatched_life_v1 - est_hatched_clutch_v1,
-         est_hatched_future_v6 = est_hatched_life_v6 - est_hatched_clutch_v6,
-         est_survived_future_v1 = est_survived_life_v1 - est_survived_clutch_v1,
-         est_survived_future_v6 = est_survived_life_v6 - est_survived_clutch_v6) %>%
-  distinct(Female_ID, ants_removed, females_removed, `visited in 4 days`,
-           desert_cat, desert_rel2h, guard_duration,
-           started_by, init_visit_life_tactic, one_both_life_tactic,
-           first_clutch_visited_in4d, n_clutches_with_eggs_iv,
-           est_eggs_clutch, est_eggs_life, est_eggs_future, 
-           est_hatched_life_v1, est_hatched_life_v6, 
-           est_hatched_future_v1, est_hatched_future_v6,
-           est_hatched_clutch_v1, est_hatched_clutch_v6,
-           est_survived_life_v1, est_survived_life_v6, 
-           est_survived_future_v1, est_survived_future_v6,
-           est_survived_clutch_v1, est_survived_clutch_v6) %>%
-  # remove 4 females that visited clutches with unknown initiation dates
-  filter(!is.na(ants_removed)) %>%
-  # *** I need to figure out why these are NA!!! ***
-  filter(!is.na(est_hatched_clutch_v6))
-```
+# 0 - Data import
 
 ```{r}
-est_fitness_life_strats %>%
-  filter(!females_removed, !is.na(desert_cat)) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  ylab("Estimated lifetime fecundity (eggs)")  +
-  xlab("Reproductive strategy for first clutch") +
-  theme_publilia() +
-  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1)
-
-est_fitness_life_strats %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v1, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  ylab("Estimated lifetime fitness (eggs hatched)")  + ylim(0,100) +
-  xlab("Reproductive strategy for first clutch") +
-  theme_publilia() +
-  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1)
-
-est_fitness_life_strats %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  ylab("Estimated lifetime fitness (eggs hatched)")  + ylim(0,100) +
-  xlab("Reproductive strategy for first clutch") +
-  theme_publilia() +
-  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1)
-
-est_fitness_life_strats %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v1, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  ylab("Estimated lifetime fitness (nymphs survived)")  + ylim(0,60) +
-  xlab("Reproductive strategy for first clutch") +
-  theme_publilia() +
-  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1)
-
-est_fitness_life_strats %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
-  geom_jitter(pch = 21, size=3, width=0.35) +
-  ylab("Estimated lifetime fitness (nymphs survived)")  + ylim(0,60) +
-  xlab("Reproductive strategy for first clutch") +
-  theme_publilia() +
-  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1)
-```
-
-## Boxplots
-
-with jitter (messy)
-```{r}
-est_fitness_life_strats_eggs.p <- est_fitness_life_strats %>%
-  filter(!females_removed, !is.na(desert_cat)) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
-  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA, alpha=0) +
-  #stat_summary(fun=mean, geom="point", shape=4, size=3) +
-  ylab("Lifetime fecundity\n(total eggs laid)")  +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(~ants_removed, nrow=1) +
-  theme(strip.background = element_blank(),strip.text.x = element_blank(),
-        axis.title.x = element_blank(),axis.text.x=element_blank(),
-        legend.position='none')
-
-est_fitness_life_strats_hatched.p <- est_fitness_life_strats %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA, key_glyph=draw_key_rect) +
-  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3, key_glyph=draw_key_rect) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA, alpha=0, key_glyph=draw_key_rect) +
-  #stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
-  ylab("Lifetime fitness\n(total eggs hatched)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(~ants_removed, nrow=1) +
-  theme(strip.background = element_blank(),strip.text.x = element_blank(),
-        axis.title.x = element_blank(),axis.text.x=element_blank(),
-        legend.position = c(0.7,0.9))
-
-est_fitness_life_strats_survived.p <- est_fitness_life_strats %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
-  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA, alpha=0) +
-  #stat_summary(fun=mean, geom="point", shape=4, size=3) +
-  ylab("Lifetime fitness\n(total nymphs survived)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(~ants_removed, nrow=1) +
-  theme(strip.background = element_blank(),strip.text.x = element_blank(),
-        legend.position='none')
-
-#library(egg)
-egg::ggarrange(est_fitness_life_strats_eggs.p,
-          est_fitness_life_strats_hatched.p,
-          est_fitness_life_strats_survived.p,
-          ncol=1, nrow=3)
-```
-
-with mean (clean)
-```{r}
-est_fitness_life_strats_eggs.p <- est_fitness_life_strats %>%
-  filter(!females_removed, !is.na(desert_cat)) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5) +
-  stat_summary(fun=mean, geom="point", shape=4, size=3) +
-  ylab("Lifetime fecundity\n(total eggs laid)")  +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(~ants_removed, nrow=1) +
-  theme(strip.background = element_blank(),strip.text.x = element_blank(),
-        axis.title.x = element_blank(),axis.text.x=element_blank(),
-        legend.position = "none")
-
-est_fitness_life_strats_hatched.p <- est_fitness_life_strats %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
-  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
-  ylab("Lifetime fitness\n(total eggs hatched)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(~ants_removed, nrow=1) +
-  theme(strip.background = element_blank(),strip.text.x = element_blank(),
-        axis.title.x = element_blank(),axis.text.x=element_blank(),
-        legend.position = c(0.7,0.9))
-
-est_fitness_life_strats_survived.p <- est_fitness_life_strats %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5) +
-  stat_summary(fun=mean, geom="point", shape=4, size=3) +
-  ylab("Lifetime fitness\n(total nymphs survived)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(~ants_removed, nrow=1) +
-  theme(strip.background = element_blank(),strip.text.x = element_blank(),
-        legend.position='none')
-
-#library(egg)
-egg::ggarrange(est_fitness_life_strats_eggs.p,
-          est_fitness_life_strats_hatched.p,
-          est_fitness_life_strats_survived.p,
-          ncol=1, nrow=3)
-```
-
-splitting semelparous and iteroparous females (clean)
-```{r}
-est_fitness_life_strats_eggs_semel.p <- est_fitness_life_strats %>%
-  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv==1) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
-  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
-  ylab("Lifetime fecundity\n(total eggs laid)")  + ylim(0,160) +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(~ants_removed, nrow=1) +
-  theme(strip.background = element_blank(), strip.text.x = element_blank(),
-        axis.title.x = element_blank(),axis.text.x=element_blank(),
-        legend.position="none")
-
-est_fitness_life_strats_eggs_itero.p <- est_fitness_life_strats %>%
-  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv>1) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
-  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
-  ylab("Lifetime fecundity\n(total eggs laid)")  + ylim(0,160) +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1) +
-  theme(strip.background = element_blank(), strip.text.x = element_blank(),
-        axis.title.x = element_blank(),axis.text.x=element_blank(),
-        legend.position="none")
-
-est_fitness_life_strats_hatched_semel.p <- est_fitness_life_strats %>%
-  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv==1) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
-  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
-  ylab("Lifetime fitness\n(total eggs hatched)") + ylim(0,100) +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(~ants_removed, nrow=1) +
-  theme(strip.background = element_blank(), strip.text.x = element_blank(),
-        axis.title.x = element_blank(),axis.text.x=element_blank(),
-        legend.position=c(0.75,0.9))
-
-est_fitness_life_strats_hatched_itero.p <- est_fitness_life_strats %>%
-  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv>1) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
-  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
-   ylab("Lifetime fitness\n(total eggs hatched)") + ylim(0,100) +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1) +
-  theme(strip.background = element_blank(), strip.text.x = element_blank(),
-        axis.title.x = element_blank(),axis.text.x=element_blank(),
-        legend.position=c(0.75,0.9))
-
-est_fitness_life_strats_survived_semel.p <- est_fitness_life_strats %>%
-  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv==1) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
-  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
-  ylab("Lifetime fitness\n(total nymphs survived)") + ylim(0,30) +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(~ants_removed, nrow=1) +
-  theme(strip.background = element_blank(), strip.text.x = element_blank(),
-        legend.position="none",
-        axis.text.x=element_text(angle=45, vjust=1, hjust=1))
-
-est_fitness_life_strats_survived_itero.p <- est_fitness_life_strats %>%
-  filter(!females_removed, !is.na(desert_cat), n_clutches_with_eggs_iv>1) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, key_glyph=draw_key_rect) +
-  stat_summary(fun=mean, geom="point", shape=4, size=3,  key_glyph=draw_key_rect) +
-  ylab("Lifetime fitness\n(total nymphs survived)") + ylim(0,30) +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray80")) +
-  theme_publilia() +
-  facet_wrap(vars(n_clutches_with_eggs_iv>1, ants_removed), nrow=1) +
-  theme(strip.background = element_blank(), strip.text.x = element_blank(),
-        legend.position="none",
-        axis.text.x=element_text(angle=45, vjust=1, hjust=1))
-
-egg::ggarrange(est_fitness_life_strats_eggs_semel.p,est_fitness_life_strats_eggs_itero.p,
-          est_fitness_life_strats_hatched_semel.p,est_fitness_life_strats_hatched_itero.p,
-          est_fitness_life_strats_survived_semel.p,est_fitness_life_strats_survived_itero.p,
-          ncol=2, nrow=3)
-```
-
-Should I include this raw data in the supplement? I think so.
-```{r}
-est_fitness_life_strats %>%
-  filter(!females_removed, !is.na(desert_cat)) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
-  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
-  ylab("Estimated lifetime fecundity (eggs)")  +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "white")) +
-  theme_publilia() +
-  facet_wrap(vars(ants_removed), nrow=1)
-
-est_fitness_life_strats %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v1, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
-  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
-  ylab("Estimated lifetime fitness (eggs hatched)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "white")) +
-  theme_publilia() +
-  facet_wrap(vars(ants_removed), nrow=1)
-
-est_fitness_life_strats %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v1, fill=ants_removed)) +
-  geom_boxplot(position = position_dodge(0.75), size = 1.5, outlier.shape=NA) +
-  geom_point(pch = 21, position=position_jitterdodge(jitter.width=0.25), size=3) +
-  ylab("Estimated lifetime fitness (nymphs survived)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "white")) +
-  theme_publilia() +
-  facet_wrap(vars(ants_removed), nrow=1)
-```
-
-## Split violin plots
-geom_split_violin
-```{r}
-GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
-                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
-  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
-  grp <- data[1, "group"]
-  newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
-  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
-  newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
-
-  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
-    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
-      1))
-    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
-    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
-    aesthetics$alpha <- rep(1, nrow(quantiles))
-    both <- cbind(quantiles, aesthetics)
-    quantile_grob <- GeomPath$draw_panel(both, ...)
-    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
-  }
-  else {
-    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
-  }
-})
-
-geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
-                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
-                              show.legend = NA, inherit.aes = TRUE) {
-  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
-        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
-        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
-}
-```
-
-split violin v1
-```{r}
-est_fitness_life_strats_splitvio_eggs_v1.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=3) +
-  ylab("Estimated lifetime fecundity (number of eggs laid)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  theme_publilia()
-
-est_fitness_life_strats_splitvio_hatched_v1.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v1, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=3) +
-  ylab("Estimated lifetime fitness (eggs hatched)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  theme_publilia()
-
-est_fitness_life_strats_splitvio_survived_v1.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v1, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=3) +
-  ylab("Estimated lifetime fitness (nymphs survived)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  theme_publilia()
-
-egg::ggarrange(est_fitness_life_strats_splitvio_eggs_v1.p,
-          est_fitness_life_strats_splitvio_hatched_v1.p,
-          est_fitness_life_strats_splitvio_survived_v1.p,
-          ncol=1, nrow=3)
-
-est_fitness_life_strats_splitvio_eggs_v1_itero.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=2) +
-  ylab("Estimated lifetime fecundity (number of eggs laid)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  theme_publilia() +
-  facet_wrap(~n_clutches_with_eggs_iv>1)
-
-est_fitness_life_strats_splitvio_hatched_v1_itero.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v1, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=2) +
-  ylab("Estimated lifetime fitness (eggs hatched)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  theme_publilia() +
-  facet_wrap(~n_clutches_with_eggs_iv>1)
-
-est_fitness_life_strats_splitvio_survived_v1_itero.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v1, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=2) +
-  ylab("Estimated lifetime fitness (nymphs survived)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  theme_publilia() +
-  facet_wrap(~n_clutches_with_eggs_iv>1)
-
-egg::ggarrange(est_fitness_life_strats_splitvio_eggs_v1_itero.p,
-          est_fitness_life_strats_splitvio_hatched_v1_itero.p,
-          est_fitness_life_strats_splitvio_survived_v1_itero.p,
-          ncol=1, nrow=3)
-```
-
-split violin v6
-```{r}
-est_fitness_life_strats_splitvio_eggs_v6.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=3) +
-  ylab("Estimated lifetime fecundity\n(number of eggs laid)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  theme_publilia()
-
-est_fitness_life_strats_splitvio_hatched_v6.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50, key_glyph=draw_key_rect) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), 
-             pch = 16, size=3, key_glyph=draw_key_rect) +
-  ylab("Estimated lifetime fitness\n(eggs hatched)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ant exclusion"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ant exclusion"), values=c("brown1", "black")) +
-  theme_publilia()
-
-est_fitness_life_strats_splitvio_survived_v6.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=3) +
-  ylab("Estimated lifetime fitness\n(nymphs survived)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  theme_publilia()
-
-egg::ggarrange(est_fitness_life_strats_splitvio_eggs_v6.p +
-                 theme(legend.position="none"),
-          est_fitness_life_strats_splitvio_hatched_v6.p +
-                 theme(legend.position=c(0.1,0.9)),
-          est_fitness_life_strats_splitvio_survived_v6.p +
-                 theme(legend.position="none"),
-          ncol=1, nrow=3)
-
-est_fitness_life_strats_splitvio_eggs_v6_itero.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_eggs_life, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=2) +
-  ylab("Estimated lifetime fecundity\n(number of eggs laid)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  theme_publilia() +
-  facet_wrap(~n_clutches_with_eggs_iv>1) + theme()
-
-est_fitness_life_strats_splitvio_hatched_v6_itero.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_hatched_life_v6, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50, key_glyph=draw_key_rect) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), 
-             pch = 16, size=3, key_glyph=draw_key_rect) +
-  ylab("Estimated lifetime fitness\n(eggs hatched)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  theme_publilia() +
-  facet_wrap(~n_clutches_with_eggs_iv>1)
-
-est_fitness_life_strats_splitvio_survived_v6_itero.p <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs")) %>%
-  filter(!females_removed) %>%
-  ggplot(data=., aes(x=desert_cat, y=est_survived_life_v6, fill=ants_removed, color=ants_removed)) +
-  geom_split_violin(color=NA, alpha=0.50) +
-  geom_point(position=position_jitterdodge(jitter.width=0.08, dodge.width=0.3), pch = 16, size=2) +
-  ylab("Estimated lifetime fitness\n(nymphs survived)") +
-  xlab("Reproductive strategy for first clutch") +
-  scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "black")) +
-  theme_publilia() +
-  facet_wrap(~n_clutches_with_eggs_iv>1)
-
-egg::ggarrange(est_fitness_life_strats_splitvio_eggs_v6_itero.p +
-                 theme(legend.position="none"),
-          est_fitness_life_strats_splitvio_hatched_v6_itero.p +
-                 theme(legend.position=c(0.1,0.8)),
-          est_fitness_life_strats_splitvio_survived_v6_itero.p +
-                 theme(legend.position="none"),
-          ncol=1, nrow=3)
+surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
 ```
@@
 
-# Other measures of fecundity
-
-### Number of clutches laid
-```{r}
-# est_fitness_future %>%
-#   filter(!females_removed) %>%
-#   count(desert_cat, ants_removed)
-# 
-# # Initiated or visited
-# est_fecundity_future %>%
-#   filter(!females_removed) %>%
-#   ggplot(data=., aes(y = n_initiated+n_visited, x = desert_catL, fill=ants_removed)) +
-#   stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
-#   stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
-#   stat_summary(fun.data="n", geom = "text", position = position_dodge(0.9)) +
-#   theme_publilia()
-# 
-# # Initiated only
-# est_fecundity_future %>%
-#   filter(!females_removed) %>%
-#   ggplot(data=., aes(y = n_initiated, x = desert_catL, fill=ants_removed)) +
-#   stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
-#   stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
-#   theme_publilia()
-# 
-# # Visited only
-# est_fecundity_future %>%
-#   filter(!females_removed) %>%
-#   ggplot(data=., aes(y = n_visited, x = desert_catL, fill=ants_removed)) +
-#   stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
-#   stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
-#   theme_publilia()
-# 
-# # Feed only
-# est_fecundity_future %>%
-#   filter(!females_removed) %>%
-#   ggplot(data=., aes(y = n_feed, x = desert_catL, fill=ants_removed)) +
-#   stat_summary(fun="mean", geom = "bar", position = position_dodge(0.9)) +
-#   stat_summary(fun.data="mean_se", geom = "errorbar",position = position_dodge(0.9), width = 0.2) +
-#   theme_publilia()
-
-```
-
-## First clutch vs. future fecundity and fitness
-Fecundity
-```{r}
-fitness_life_strats_data <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs"),
-         desert_cat_ants = ifelse(ants_removed, 
-                                 paste(desert_cat,"ants removed"),paste(desert_cat,"control")),
-         desert_cat_ants = factor(desert_cat_ants,
-          levels=c("visit control", "desert control", "eggs control","nymphs control",
-                   "visit ants removed", "desert ants removed", "eggs ants removed","nymphs ants removed")))
-
-# First
-fitness_first_stats_eggs_v6 <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_clutch, group=desert_cat_ants)
-fitness_first_stats_eggs_v6["multcompLetters"]$multcompLetters$x <- 
-  factor(rep(c("visit", "desert","eggs", "nymphs"),2), levels=c("visit", "desert","eggs", "nymphs"))
-fitness_first_stats_eggs_v6["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_first_stats_eggs_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_first_stats_eggs_v6.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_clutch, group=desert_cat, 
-                    itero=F, multcompLetters=fitness_first_stats_eggs_v6$multcompLetters,
-                    letterSize=letterSize, ymax=160) +
-  ylab("First-clutch fecundity\n(eggs laid)") + 
-    theme(legend.position="none",
-          axis.title.x = element_blank(),axis.text.x=element_blank())
-
-# Future (all)
-fitness_future_stats_eggs_v6 <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_future, group=desert_cat_ants)
-fitness_future_stats_eggs_v6["multcompLetters"]$multcompLetters$x <- 
-  factor(rep(c("visit", "desert","eggs", "nymphs"),2), levels=c("visit", "desert","eggs", "nymphs"))
-fitness_future_stats_eggs_v6["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_future_stats_eggs_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_future_stats_eggs_v6.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_future, group=desert_cat, 
-                    itero=F, multcompLetters=fitness_future_stats_eggs_v6$multcompLetters,
-                    letterSize=letterSize, ymax=160) +
-  ylab("Future fecundity\n(eggs laid)") + 
-    theme(legend.position="none",
-          axis.title.x = element_blank(),axis.text.x=element_blank())
-
-# Future (iteroparous only)
-fitness_life_strats_data.itero <- filter(fitness_life_strats_data, n_clutches_with_eggs_iv>1)
-fitness_future_stats_eggs.itero <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat_ants)
-fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_future_stats_eggs_v6.itero.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_future_stats_eggs.itero$multcompLetters,
-                    letterSize=letterSize, ymax=160)$itero +
-  ylab("Multi-clutch future\nfecundity (eggs laid)") + 
-    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())
-
-# Life
-fitness_life_stats_eggs_v6 <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
-fitness_life_stats_eggs_v6["multcompLetters"]$multcompLetters$x <- 
-  factor(rep(c("visit", "desert","eggs", "nymphs"),2), levels=c("visit", "desert","eggs", "nymphs"))
-fitness_life_stats_eggs_v6["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_life_stats_eggs_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_life_stats_eggs_v6.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
-                    itero=F, multcompLetters=fitness_life_stats_eggs_v6$multcompLetters,
-                    letterSize=letterSize, ymax=160) +
-  ylab("Lifetime fecundity\n(eggs laid)") + 
-    theme(legend.position="none")
-
-fitness_eggs_future.v6.p <-
-  egg::ggarrange(fitness_first_stats_eggs_v6.p, fitness_future_stats_eggs_v6.p, fitness_life_stats_eggs_v6.p,
-                 labels=c("A","B","C"), ncol=1, nrow=3)
-
-### trade-off
-fitness_life_strats_data.itero %>%
-  ggplot(data=., aes(x=desert_rel2h, est_eggs_future, color=ants_removed)) +
-  geom_point() + geom_smooth(se=F, span=1)
-
-fitness_life_strats_data.itero %>%
-  ggplot(data=., aes(x=desert_rel2h, est_hatched_future_v6, color=ants_removed)) +
-  geom_point() + geom_smooth(se=F, span=1)
-
-fitness_life_strats_data.itero %>%
-  ggplot(data=., aes(x=desert_rel2h, est_survived_future_v6, color=ants_removed)) +
-  geom_point() + geom_smooth(se=F, span=1)
-
-fitness_life_strats_data.itero %>%
-  ggplot(data=., aes(x=est_eggs_clutch, est_eggs_future, color=ants_removed)) +
-  geom_point() + geom_smooth(method=lm, se=F) +
-  xlim(0,160) + ylim(0,160)
-
-fitness_life_strats_data.itero %>%
-  ggplot(data=., aes(x=est_hatched_clutch_v6, est_hatched_future_v6, color=ants_removed)) +
-  geom_point() + geom_smooth(method=lm, se=F) +
-  xlim(0,70) + ylim(0,70) # outlier at est_hatched_clutch_v6=90ish
-
-fitness_life_strats_data.itero %>%
-  ggplot(data=., aes(x=est_survived_clutch_v6, est_survived_future_v6, color=ants_removed)) +
-  geom_point() + geom_smooth(method=lm, se=F) +
-  xlim(0,25) + ylim(0,25)
-
-fitness_life_strats_data.itero %>%
-  ggplot(data=., aes(x=guard_duration, est_eggs_future, color=ants_removed)) +
-  geom_point() + geom_smooth(method=lm, se=T)
-
-fitness_life_strats_data.itero %>%
-  ggplot(data=., aes(x=guard_duration, est_hatched_future_v6, color=ants_removed)) +
-  geom_point() + geom_smooth(method=lm, se=F)
-
-fitness_life_strats_data.itero %>%
-  ggplot(data=., aes(x=guard_duration, est_survived_future_v6, color=ants_removed)) +
-  geom_point() + geom_smooth(method=lm, se=F)
-
-```
-
-Future fecundity/fitness (itero)
-```{r}
-fitness_life_strats_data.itero <- filter(fitness_life_strats_data, n_clutches_with_eggs_iv>1)
-
-# Eggs
-fitness_future_stats_eggs.itero <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat_ants)
-fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_future_stats_eggs.itero["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_future_stats_eggs_v6.itero.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_future_stats_eggs.itero$multcompLetters,
-                    letterSize=letterSize, ymax=160)$itero +
-  ylab("Multi-clutch future\nfecundity (eggs laid)") + 
-    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())
-
-# Hatch
-fitness_future_stats_hatched.itero <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero, y=est_hatched_future_v6, group=desert_cat_ants)
-fitness_future_stats_hatched.itero["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_future_stats_hatched.itero["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_future_stats_hatched.itero["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_future_stats_hatched_v6.itero.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_hatched_future_v6, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_future_stats_hatched.itero$multcompLetters,
-                    letterSize=letterSize, ymax=75)$itero +
-  ylab("Multi-clutch future\nfitness (eggs hatch)") + 
-    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())
-
-# Survive
-fitness_future_stats_survived.itero <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero, y=est_survived_future_v6, group=desert_cat_ants)
-fitness_future_stats_survived.itero["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_future_stats_survived.itero["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_future_stats_survived.itero["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_future_stats_survived_v6.itero.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data.itero, y=est_survived_future_v6, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_future_stats_survived.itero$multcompLetters,
-                    letterSize=letterSize, ymax=22)$itero +
-  ylab("Multi-clutch future\nfitness (nymphs survive)") + 
-    theme(legend.position=c(0.8,0.8))
-
-fitness_stats_future.v6.itero.p <-
-  egg::ggarrange(fitness_future_stats_eggs_v6.itero.p, 
-                 fitness_future_stats_hatched_v6.itero.p, 
-                 fitness_future_stats_survived_v6.itero.p,
-                 labels=c("A","B","C"), ncol=1, nrow=3)
-```
-
-Future fecundity/fitness (itero): Is the low sample size for visiting first undermining the power to detect differences among the more interesting groups?
-```{r}
-fitness_life_strats_data.itero.DEN <- filter(fitness_life_strats_data,
-                                         n_clutches_with_eggs_iv>1,
-                                         desert_cat != "visit")
-
-# Eggs
-fitness_future_stats_eggs.itero.DEN <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero.DEN, y=est_eggs_future, group=desert_cat_ants)
-fitness_future_stats_eggs.itero.DEN["multcompLetters"]$multcompLetters$x <- 
-  rep(c("desert","eggs", "nymphs"),2)
-fitness_future_stats_eggs.itero.DEN["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_future_stats_eggs.itero.DEN["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,T,T,T)))
-
-fitness_future_stats_eggs_v6.itero.DEN.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_eggs_future, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_future_stats_eggs.itero.DEN$multcompLetters,
-                    letterSize=letterSize, ymax=160)$itero +
-  ylab("Multi-clutch future\nfecundity (eggs laid)") + 
-    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())
-
-# Hatch
-fitness_future_stats_hatched.itero.DEN <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero.DEN, y=est_hatched_future_v6, group=desert_cat_ants)
-fitness_future_stats_hatched.itero.DEN["multcompLetters"]$multcompLetters$x <- 
-  rep(c("desert","eggs", "nymphs"),2)
-fitness_future_stats_hatched.itero.DEN["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_future_stats_hatched.itero.DEN["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,T,T,T)))
-
-fitness_future_stats_hatched_v6.itero.DEN.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_hatched_future_v6, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_future_stats_hatched.itero.DEN$multcompLetters,
-                    letterSize=letterSize, ymax=75)$itero +
-  ylab("Multi-clutch future\nfitness (eggs hatch)") + 
-    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())
-
-# Survive
-fitness_future_stats_survived.itero.DEN <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero.DEN, y=est_survived_future_v6, group=desert_cat_ants)
-fitness_future_stats_survived.itero.DEN["multcompLetters"]$multcompLetters$x <- 
-  rep(c("desert","eggs", "nymphs"),2)
-fitness_future_stats_survived.itero.DEN["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_future_stats_survived.itero.DEN["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,T,T,T)))
-
-fitness_future_stats_survived_v6.itero.DEN.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data.itero.DEN, y=est_survived_future_v6, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_future_stats_survived.itero.DEN$multcompLetters,
-                    letterSize=letterSize, ymax=22)$itero +
-  ylab("Multi-clutch future\nfitness (nymphs survive)") + 
-    theme(legend.position=c(0.8,0.8))
-
-fitness_stats_future.v6.itero.DEN.p <-
-  egg::ggarrange(fitness_future_stats_eggs_v6.itero.DEN.p, 
-                 fitness_future_stats_hatched_v6.itero.DEN.p, 
-                 fitness_future_stats_survived_v6.itero.DEN.p,
-                 labels=c("A","B","C"), ncol=1, nrow=3)
-```
-
-Future fecundity/fitness (all)
-```{r}
-# Future
-fitness_future_stats_hatched <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_hatched_future_v6, group=desert_cat_ants)
-fitness_future_stats_hatched["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_future_stats_hatched["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_future_stats_hatched["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_future_stats_hatched_v6.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_future_v6, group=desert_cat, 
-                    multcompLetters=fitness_future_stats_hatched$multcompLetters,
-                    letterSize=letterSize, ymax=75) +
-  ylab("Future\nfitness (eggs hatch)") + 
-    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())
-
-# Future
-fitness_future_stats_survived <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_survived_future_v6, group=desert_cat_ants)
-fitness_future_stats_survived["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_future_stats_survived["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_future_stats_survived["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_future_stats_survived_v6.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_future_v6, group=desert_cat, 
-                    multcompLetters=fitness_future_stats_survived$multcompLetters,
-                    letterSize=letterSize, ymax=22) +
-  ylab("Future\nfitness (nymphs survive)") + 
-    theme(legend.position=c(0.8,0.8))
-
-fitness_stats_future.v6.p <-
-  egg::ggarrange(fitness_future_stats_eggs_v6.p, 
-                 fitness_future_stats_hatched_v6.p, 
-                 fitness_future_stats_survived_v6.p,
-                 labels=c("A","B","C"), ncol=1, nrow=3)
-
-ymax <-21
-fitness_life_strats_data %>%
-      filter(!females_removed, !is.na(desert_cat)) %>%
-    ggplot(data = ., aes(x = desert_cat, y=est_survived_future_v6, fill=ants_removed, color=ants_removed)) + 
-      ylim(-ymax * 0.05, ymax) + 
-      geom_boxplot(alpha = 0.5, key_glyph = draw_key_rect) + 
-      geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-                 pch = 16, size = 2, key_glyph = draw_key_rect) + 
-      xlab("Guarding strategy for first clutch") + theme_publilia() + 
-      scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
-      scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
-      geom_text(data = fitness_future_stats_survived$multcompLetters, 
-                aes(x = x, y = -ymax * 0.05, label = label), 
-                fontface = "bold", size = letterSize, position=position_dodge(width=0.5))
-
-fitness_life_strats_data.itero %>%
-      filter(!females_removed, !is.na(desert_cat)) %>%
-    ggplot(data = ., aes(x = desert_cat, y=est_survived_future_v6, fill=ants_removed, color=ants_removed)) + 
-      ylim(-ymax * 0.05, ymax) + 
-      geom_boxplot(alpha = 0.5, key_glyph = draw_key_rect) + 
-      geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-                 pch = 16, size = 2, key_glyph = draw_key_rect) + 
-      xlab("Guarding strategy for first clutch") + theme_publilia() + 
-      scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
-      scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
-      geom_text(data = fitness_future_stats_survived.itero$multcompLetters, 
-                aes(x = x, y = -ymax * 0.05, label = label), 
-                fontface = "bold", size = letterSize, position=position_dodge(width=0.5))
-
-```
-
-#######################################################################
-#######################################################################
-#######################################################################
-
-# Final figures and statistics
-## Lifetime fecundity and fitness
-I want to know whether there is a difference in the lifetime fecundity or fitness yielded by different strategies.
-Most importantly, I want to know whether there is a difference within ant-exclusion treatment, but I'm also want to know whether ant exclusion changes the fitness of a given strategy.
-The data are unpaired and probably no conforming well to a normal distribution.
-
-plotting libraries
-```{r}
-library(multcompView)
-```
-
-geom_split_violin
-```{r}
-GeomSplitViolin <- ggproto("GeomSplitViolin", GeomViolin, 
-                           draw_group = function(self, data, ..., draw_quantiles = NULL) {
-  data <- transform(data, xminv = x - violinwidth * (x - xmin), xmaxv = x + violinwidth * (xmax - x))
-  grp <- data[1, "group"]
-  newdata <- plyr::arrange(transform(data, x = if (grp %% 2 == 1) xminv else xmaxv), if (grp %% 2 == 1) y else -y)
-  newdata <- rbind(newdata[1, ], newdata, newdata[nrow(newdata), ], newdata[1, ])
-  newdata[c(1, nrow(newdata) - 1, nrow(newdata)), "x"] <- round(newdata[1, "x"])
-
-  if (length(draw_quantiles) > 0 & !scales::zero_range(range(data$y))) {
-    stopifnot(all(draw_quantiles >= 0), all(draw_quantiles <=
-      1))
-    quantiles <- ggplot2:::create_quantile_segment_frame(data, draw_quantiles)
-    aesthetics <- data[rep(1, nrow(quantiles)), setdiff(names(data), c("x", "y")), drop = FALSE]
-    aesthetics$alpha <- rep(1, nrow(quantiles))
-    both <- cbind(quantiles, aesthetics)
-    quantile_grob <- GeomPath$draw_panel(both, ...)
-    ggplot2:::ggname("geom_split_violin", grid::grobTree(GeomPolygon$draw_panel(newdata, ...), quantile_grob))
-  }
-  else {
-    ggplot2:::ggname("geom_split_violin", GeomPolygon$draw_panel(newdata, ...))
-  }
-})
-
-geom_split_violin <- function(mapping = NULL, data = NULL, stat = "ydensity", position = "identity", ..., 
-                              draw_quantiles = NULL, trim = TRUE, scale = "area", na.rm = FALSE, 
-                              show.legend = NA, inherit.aes = TRUE) {
-  layer(data = data, mapping = mapping, stat = stat, geom = GeomSplitViolin, 
-        position = position, show.legend = show.legend, inherit.aes = inherit.aes, 
-        params = list(trim = trim, scale = scale, draw_quantiles = draw_quantiles, na.rm = na.rm, ...))
-}
-```
-
-A function to run Kruskall-Wallis test and Dunn tests for each panel
-```{r}
-fitness_KW_test <- function(data, y, group){
-  # non-parametric: Kruskall-Wallis test followed by Dunn test
-  # run KW test using rstatix::kruskal_test
-  KWtest <- eval(substitute(data %>% kruskal_test(y ~ group)))
-  # get effect size using effectsize::rank_epsilon_squared
-  KWepsilon2 <- eval(substitute(rank_epsilon_squared(y ~ group, data=data)))
-  # run Dunn test using rstatix::dunn_test
-  dunn <- eval(substitute(data %>% dunn_test(y ~ group)))
-  # get multiple comparison groups letters using multcompView::multcompLetters
-  dunn.vec <- dunn$p.adj.signif
-  names(dunn.vec) <- paste(dunn$group1,dunn$group2,sep="-")
-  multcompLetters <- tibble(x=names(multcompLetters(dunn.vec)$Letters),
-                            label=unname(multcompLetters(dunn.vec)$Letters))
-  # return
-  out <- list(KWtest=KWtest, KWepsilon2=KWepsilon2, dunn=dunn, multcompLetters=multcompLetters)
-  return(out)
-}
-
-fitness_life_strats_data.itero <- filter(fitness_life_strats_data, n_clutches_with_eggs_iv>1)
-fitness_future_stats_eggs.itero <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero, y=est_eggs_future, group=desert_cat_ants)
-
-KWtest <- fitness_life_strats_data %>% kruskal_test(est_eggs_future ~ desert_cat_ants)
-
-# # test
-# fitness_life_strats_data <- est_fitness_life_strats %>% 
-#   mutate(desert_cat_ants = ifelse(ants_removed, 
-#                                   paste(desert_cat,"ants removed"),paste(desert_cat,"control")))
-# fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
-
-# # Troubleshooting:
-# fitness_life_strats_data %>% filter(!females_removed, !is.na(desert_cat)) %>% 
-#     ggplot(data = ., aes(x = desert_cat, y = est_eggs_life, fill = ants_removed, 
-#         color = ants_removed)) + ylim(-160 * 0.05, 160) + 
-#   geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
-#   geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-#              pch = 16, size = 2, key_glyph = draw_key_rect) + 
-#     xlab("Guarding strategy for first clutch") + theme_publilia() + 
-#     scale_fill_manual(labels = c("Control", "Ants removed"), 
-#         values = c("brown1", "black")) + scale_color_manual(labels = c("Control", 
-#     "Ants removed"), values = c("brown1", "black")) + 
-#   geom_text(data = fitness_stats_eggs$multcompLetters, 
-#             aes(x = x, y = -160 * 0.05, label = label), 
-#             fontface = "bold", size = 4, position = position_dodge(width = 0.5)) + 
-#   scale_x_discrete(labels = c("desert", "eggs", "nymphs", "visit"))
-# 
-# fitness_life_strats_data %>% filter(!females_removed, !is.na(desert_cat)) %>% 
-#     ggplot(data = ., aes(x = desert_cat, y=est_eggs_life, fill=ants_removed, color=ants_removed)) + 
-#   ylim(-160 * 0.05, 160) + 
-#   geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
-#   geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-#              pch = 16, size = 2, key_glyph = draw_key_rect) + 
-#     xlab("Guarding strategy for first clutch") + theme_publilia() + 
-#     scale_fill_manual(labels = c("Control", "Ants removed"), values = c("brown1", "black")) + 
-#   scale_color_manual(labels = c("Control", "Ants removed"),  values = c("brown1", "black")) + 
-#   geom_text(data = fitness_stats_eggs$multcompLetters, 
-#     aes(x = x, y = -160 * 0.05, label = label), 
-#     fontface = "bold", size = 4, position=position_dodge(width=0.5)) + 
-#   scale_x_discrete(labels = c("desert", "eggs", "nymphs", "visit"))
-
-# plot boxplots, including KWtest letters
-fitness_plot_dunn <- function(data, y, group, itero=F, multcompLetters, letterSize, ymax=160){
-  if(itero==F){
-    (p <- eval(substitute(data %>%
-      filter(!females_removed, !is.na(group)) %>%
-    ggplot(data = ., aes(x = group, y=y, fill=ants_removed, color=ants_removed)) + 
-      ylim(-ymax * 0.05, ymax) + 
-      geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
-      geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-                 pch = 16, size = 2, key_glyph = draw_key_rect) + 
-      xlab("Guarding strategy for first clutch") + theme_publilia() + 
-      scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
-      scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
-      geom_text(data = multcompLetters, 
-                aes(x = x, y = -ymax * 0.05, label = label), 
-                fontface = "bold", size = letterSize, position=position_dodge(width=0.5)))))
-    return(p)
-  } else {
-    # single-clutch females
-    (p_semel <- eval(substitute(data %>%
-      filter(!females_removed, !is.na(group),
-             (n_clutches_with_eggs_iv==1)) %>%
-        ggplot(data = ., aes(x = group, y=y, fill=ants_removed, color=ants_removed)) + 
-          ylim(-ymax * 0.05, ymax) + 
-          geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
-          geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-                     pch = 16, size = 2, key_glyph = draw_key_rect) + 
-          xlab("Guarding strategy for first clutch") + theme_publilia() + 
-          scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
-          scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
-          geom_text(data = multcompLetters, 
-                    aes(x = x, y = -ymax * 0.05, label = label), 
-                    fontface = "bold", size = letterSize, position=position_dodge(width=0.5)))))
-    # multi-clutch females
-     (p_itero <- eval(substitute(data %>%
-      filter(!females_removed, !is.na(group),
-             (n_clutches_with_eggs_iv>1)) %>%
-        ggplot(data = ., aes(x = group, y=y, fill=ants_removed, color=ants_removed)) + 
-          ylim(-ymax * 0.05, ymax) + 
-          geom_split_violin(color = NA, alpha = 0.5, key_glyph = draw_key_rect) + 
-          geom_point(position = position_jitterdodge(jitter.width = 0.08, dodge.width = 0.3), 
-                     pch = 16, size = 2, key_glyph = draw_key_rect) + 
-          xlab("Guarding strategy for first clutch") + theme_publilia() + 
-          scale_fill_manual(labels = c("Control", "Ant exclusion"), values = c("brown1", "black")) + 
-          scale_color_manual(labels = c("Control", "Ant exclusion"),  values = c("brown1", "black")) +
-          geom_text(data = multcompLetters, 
-                    aes(x = x, y = -ymax * 0.05, label = label), 
-                    fontface = "bold", size = letterSize, position=position_dodge(width=0.5)))))
-    p_list<-list(semel=p_semel, itero=p_itero)
-    return(p_list)
-  }
-}
-
-# test
-# fitness_life_strats_data <- est_fitness_life_strats %>%
-#   mutate(desert_cat_ants = ifelse(ants_removed,
-#                                   paste(desert_cat,"ants removed"),paste(desert_cat,"control")))
-# eggs_fitness_stats <- fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
-# 
-# fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants,
-#                   itero=F, multcompLetters=eggs_fitness_stats$multcompLetters,
-#                   letterSize=8)
-```
-
-## Not separating single-clutch and multi-clutch females (for main)
-```{r}
-letterSize<-3
-
-fitness_life_strats_data <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs"),
-         desert_cat_ants = ifelse(ants_removed, 
-                                 paste(desert_cat,"ants removed"),paste(desert_cat,"control")),
-         desert_cat_ants = factor(desert_cat_ants,
-          levels=c("visit control", "desert control", "eggs control","nymphs control",
-                   "visit ants removed", "desert ants removed", "eggs ants removed","nymphs ants removed")))
-
-fitness_stats_eggs_v6 <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
-fitness_stats_eggs_v6["multcompLetters"]$multcompLetters$x <- 
-  factor(rep(c("visit", "desert","eggs", "nymphs"),2), levels=c("visit", "desert","eggs", "nymphs"))
-fitness_stats_eggs_v6["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_eggs_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_eggs_v6.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
-                    itero=F, multcompLetters=fitness_stats_eggs_v6$multcompLetters,
-                    letterSize=letterSize, ymax=160) +
-  ylab("Lifetime fecundity\n(eggs laid)") + 
-    theme(legend.position="none",
-          axis.title.x = element_blank(),axis.text.x=element_blank())
-
-fitness_stats_hatched_v6 <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat_ants)
-fitness_stats_hatched_v6["multcompLetters"]$multcompLetters$x <- rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_stats_hatched_v6["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_hatched_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_hatched_v6.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
-                    itero=F, multcompLetters=fitness_stats_hatched_v6$multcompLetters,
-                    letterSize=letterSize, ymax=100) +
-  ylab("Lifetime fitness\n(eggs hatched)") + 
-    theme(legend.position="none",
-          axis.title.x = element_blank(),axis.text.x=element_blank())
-
-fitness_stats_survived_v6 <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat_ants)
-fitness_stats_survived_v6["multcompLetters"]$multcompLetters$x <- rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_stats_survived_v6["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_survived_v6["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_survived_v6.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
-                    itero=F, multcompLetters=fitness_stats_survived_v6$multcompLetters,
-                    letterSize=letterSize, ymax=30) +
-  ylab("Lifetime fitness\n(nymphs survived)") + 
-  theme(legend.position=c(0.3,0.9))
-
-fitness_stats.v6.p.final <-
-  egg::ggarrange(fitness_stats_eggs_v6.p, fitness_stats_hatched_v6.p, fitness_stats_survived_v6.p,
-                 labels=c("A","B","C"), ncol=1, nrow=3)
-
-ggsave("fitness_stats.violin.final.png",
-       fitness_stats.v6.p.final,
-       device = "png",
-       width = 120, height = 200, units = "mm", dpi = "print")
-```
-
-## Just offspring counts (no imputation)
-```{r}
-letterSize<-3
-
-fitness_life_strats_data <- est_fitness_life_strats %>%
-  mutate(desert_cat = fct_relevel(desert_cat, "visit", "desert", "eggs", "nymphs"),
-         desert_cat_ants = ifelse(ants_removed, 
-                                 paste(desert_cat,"ants removed"),paste(desert_cat,"control")),
-         desert_cat_ants = factor(desert_cat_ants,
-          levels=c("visit control", "desert control", "eggs control","nymphs control",
-                   "visit ants removed", "desert ants removed", "eggs ants removed","nymphs ants removed")))
-
-fitness_stats_eggs_v1 <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
-fitness_stats_eggs_v1["multcompLetters"]$multcompLetters$x <- 
-  factor(rep(c("visit", "desert","eggs", "nymphs"),2), levels=c("visit", "desert","eggs", "nymphs"))
-fitness_stats_eggs_v1["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_eggs_v1["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_eggs_v1.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
-                    itero=F, multcompLetters=fitness_stats_eggs_v1$multcompLetters,
-                    letterSize=letterSize, ymax=160) +
-  ylab("Lifetime fecundity\n(eggs laid)") + 
-    theme(legend.position="none",
-          axis.title.x = element_blank(),axis.text.x=element_blank())
-
-fitness_stats_hatched_v1 <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat_ants)
-fitness_stats_hatched_v1["multcompLetters"]$multcompLetters$x <- rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_stats_hatched_v1["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_hatched_v1["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_hatched_v1.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat, 
-                    itero=F, multcompLetters=fitness_stats_hatched_v1$multcompLetters,
-                    letterSize=letterSize, ymax=100) +
-  ylab("Lifetime fitness\n(eggs hatched)") + 
-    theme(legend.position="none",
-          axis.title.x = element_blank(),axis.text.x=element_blank())
-
-fitness_stats_survived_v1 <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat_ants)
-fitness_stats_survived_v1["multcompLetters"]$multcompLetters$x <- rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_stats_survived_v1["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_survived_v1["multcompLetters"]$multcompLetters, tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_survived_v1.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat, 
-                    itero=F, multcompLetters=fitness_stats_survived_v1$multcompLetters,
-                    letterSize=letterSize, ymax=30) +
-  ylab("Lifetime fitness\n(nymphs survived)") + 
-  theme(legend.position=c(0.3,0.9))
-
-fitness_stats.v1.p.final <-
-  egg::ggarrange(fitness_stats_eggs_v1.p, fitness_stats_hatched_v1.p, fitness_stats_survived_v1.p,
-                 labels=c("A","B","C"), ncol=1, nrow=3)
-
-ggsave("fitness_stats.supp_v1.violin.final.png",
-       fitness_stats.v1.p.final,
-       device = "png",
-       width = 120, height = 200, units = "mm", dpi = "print")
-```
-
-## Separating single-clutch and multi-clutch females (for main)
-```{r}
-letterSize<-3
-
-fitness_life_strats_data.semel <- filter(fitness_life_strats_data, n_clutches_with_eggs_iv==1)
-fitness_life_strats_data.itero <- filter(fitness_life_strats_data, n_clutches_with_eggs_iv>1)
-
-fitness_stats_eggs.semel <- 
-  fitness_KW_test(data=fitness_life_strats_data.semel, 
-                  y=est_eggs_life, group=desert_cat_ants)
-fitness_stats_eggs.semel["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_stats_eggs.semel["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_eggs.semel["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_eggs.semel.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_stats_eggs.semel$multcompLetters,
-                    letterSize=letterSize, ymax=160)$semel +
-  ylab("Single-clutch female\nfecundity (eggs laid)") + 
-    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())
-
-fitness_stats_eggs.itero <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero, 
-                  y=est_eggs_life, group=desert_cat_ants)
-fitness_stats_eggs.itero["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_stats_eggs.itero["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_eggs.itero["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_eggs.itero.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_stats_eggs.itero$multcompLetters,
-                    letterSize=letterSize, ymax=160)$itero +
-  ylab("Multi-clutch female\nfecundity (eggs laid)") + 
-    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())
-
-fitness_stats_hatched.semel <- 
-  fitness_KW_test(data=fitness_life_strats_data.semel, 
-                  y=est_hatched_life_v6, group=desert_cat_ants)
-fitness_stats_hatched.semel["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_stats_hatched.semel["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_hatched.semel["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_hatched.semel.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_stats_hatched.semel$multcompLetters,
-                    letterSize=letterSize, ymax=100)$semel +
-  ylab("Single-clutch female\nfitness (eggs hatched)") + 
-    theme(legend.position=c(0.3,0.8), axis.title.x = element_blank(),axis.text.x=element_blank())
-
-fitness_stats_hatched.itero <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero, 
-                  y=est_hatched_life_v6, group=desert_cat_ants)
-fitness_stats_hatched.itero["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_stats_hatched.itero["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_hatched.itero["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_hatched.itero.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v6, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_stats_hatched.itero$multcompLetters,
-                    letterSize=letterSize, ymax=100)$itero +
-  ylab("Multi-clutch female\nfitness (eggs hatched)") + 
-    theme(legend.position="none", axis.title.x = element_blank(),axis.text.x=element_blank())
-
-fitness_stats_survived.semel <- 
-  fitness_KW_test(data=fitness_life_strats_data.semel, 
-                  y=est_survived_life_v6, group=desert_cat_ants)
-fitness_stats_survived.semel["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_stats_survived.semel["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_survived.semel["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_survived.semel.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_stats_survived.semel$multcompLetters,
-                    letterSize=letterSize, ymax=30)$semel +
-  ylab("Single-clutch female\nfitness (nymphs survived)") + 
-    theme(legend.position="none")
-
-fitness_stats_survived.itero <- 
-  fitness_KW_test(data=fitness_life_strats_data.itero, 
-                  y=est_survived_life_v6, group=desert_cat_ants)
-fitness_stats_survived.itero["multcompLetters"]$multcompLetters$x <- 
-  rep(c("visit", "desert","eggs", "nymphs"),2)
-fitness_stats_survived.itero["multcompLetters"]$multcompLetters <- 
-  bind_cols(fitness_stats_survived.itero["multcompLetters"]$multcompLetters, 
-            tibble(ants_removed = c(F,F,F,F,T,T,T,T)))
-
-fitness_stats_survived.itero.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v6, group=desert_cat, 
-                    itero=T, multcompLetters=fitness_stats_survived.itero$multcompLetters,
-                    letterSize=letterSize, ymax=30)$itero +
-  ylab("Multi-clutch female\nfitness (nymphs survived)") + 
-    theme(legend.position="none")
-
-fitness_stats.parity.p.final <- egg::ggarrange(
-  fitness_stats_eggs.semel.p, fitness_stats_eggs.itero.p,
-  fitness_stats_hatched.semel.p, fitness_stats_hatched.itero.p,
-  fitness_stats_survived.semel.p, fitness_stats_survived.itero.p,
-  labels=c("A","B","C","D","E","F"), ncol=2, nrow=3)
-
-ggsave("fitness_stats.violin.parity.final.png",
-       fitness_stats.parity.p.final,
-       device = "png",
-       width = 200, height = 200, units = "mm", dpi = "print")
-```
-
 ## Comparing to Zink 2003 fitness measures
@@
 ```
-
-## Clutch fitness prediction performance for imputation
-```{r}
-# Consistency is ok worse for hatching; MANY clutches with no surviving nymphs were predicted to have survived
-(predicted_clutch_A <- est_fitness_clutch %>% 
-  filter(!is.na(est_hatched_clutch_v1),!is.na(est_hatched_clutch_v6)) %>%
-  ggplot(data=., aes(x=est_hatched_clutch_v1, y=est_hatched_clutch_v6, color=interaction(vis,ants))) +
-  geom_abline(slope=1) +
-  geom_point() + xlim(0,80) + ylim(0,80) +
-  theme(legend.position="none"))
-
-# Consistency is MUCH worse for survivorship; MANY clutches with no surviving nymphs were predicted to have survived
-(predicted_clutch_B <- est_fitness_clutch %>%
-  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
-  ggplot(data=., aes(x=est_survived_clutch_v1, y=est_survived_clutch_v6, color=interaction(vis,ants))) +
-  geom_abline(slope=1) +
-  geom_point()  + xlim(0,60) + ylim(0,60) +
-  theme(legend.position=c(0.3,0.8)))
-
-(predicted_clutch.p.final <- egg::ggarrange(
-  predicted_clutch_A, predicted_clutch_B,
-  labels=c("A","B"),
-  ncol=2, nrow=1))
-
-ggsave("predicted_clutch.final.png",
-       predicted_clutch.p.final,
-       device = "png",
-       width = 200, height = 100, units = "mm", dpi = "print")
-```
-
-### Life fitness prediction performance for imputation
-Should I include this in the supplment?
-```{r}
-# hatching: ok correspondence, the spread is tighter, but range is preserved
-(predicted_clutch_A <- est_fitness_clutch %>% 
-  filter(!is.na(est_hatched_clutch_v1),!is.na(est_hatched_clutch_v6)) %>%
-  ggplot(data=., aes(x=des, y=est_hatched_clutch_v1, color=ants, fill=ants)) +
-  geom_point() +
-  geom_smooth(span=1) + ylim(0,60) +
-   xlab("Desertion date relative to hatch\non first clutch") + 
-   ylab("Clutch-level fitness\n(hatched eggs observed)") + 
-   scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
-   scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
-   theme(legend.position="none",
-         axis.text.x=element_text(angle=45, vjust=1, hjust=1),
-         strip.background = element_blank()) +
-  facet_wrap(vars(vis)))
-
-(predicted_clutch_B <-est_fitness_clutch %>% 
-  filter(!is.na(est_hatched_clutch_v6)) %>%
-  ggplot(data=., aes(x=des, y=est_hatched_clutch_v6, color=ants, fill=ants)) +
-  geom_point() +
-  geom_smooth(span=1) + ylim(0,60) +
-   xlab("Desertion date relative to hatch\non first clutch") + 
-   ylab("Clutch-level fitness\n(hatched eggs predicted by model)") + 
-   scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
-   scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
-    theme(legend.position="none",
-         axis.text.x=element_text(angle=45, vjust=1, hjust=1),
-         strip.background = element_blank()) +
-  facet_wrap(vars(vis)))
-
-# survival: ok correspondence, the spread is MUCH tighter and range is more limited; losing many higher values
-(predicted_clutch_C <- est_fitness_clutch %>% 
-  filter(!is.na(est_survived_clutch_v1),!is.na(est_survived_clutch_v6)) %>%
-  ggplot(data=., aes(x=des, y=est_survived_clutch_v1, color=ants, fill=ants)) +
-  geom_point() +
-  geom_smooth(span=1) + ylim(0,60) +
-    xlab("Desertion date relative to hatch\non first clutch") + 
-   ylab("Clutch-level fitness\n(surviving nymphs observed)") + 
-   scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
-   scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
-    theme(legend.position="none",
-         axis.text.x=element_text(angle=45, vjust=1, hjust=1),
-         strip.background = element_blank()) +
-  facet_wrap(vars(vis)))
-
-(predicted_clutch_D <-est_fitness_clutch %>% 
-  filter(!is.na(est_survived_clutch_v6)) %>%
-  ggplot(data=., aes(x=des, y=est_survived_clutch_v6, color=ants, fill=ants)) +
-  geom_point() +
-  geom_smooth(span=1) + ylim(0,60) +
-    xlab("Desertion date relative to hatch\non first clutch") + 
-   ylab("Clutch-level fitness\n(hatched eggs predicted by model)") + 
-   scale_fill_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
-   scale_color_manual(labels=c("Control","Ants removed"), values=c("brown1", "gray50")) +
-    theme(legend.position=c(0.75,0.75),
-         axis.text.x=element_text(angle=45, vjust=1, hjust=1),
-         strip.background = element_blank()) +
-  facet_wrap(vars(vis)))
-
-(predicted_clutch.p.final <- egg::ggarrange(
-  predicted_clutch_A, predicted_clutch_B,
-  predicted_clutch_C, predicted_clutch_D,
-  labels=c("A","B","C","D"),
-  ncol=2, nrow=2))
-
-ggsave("predicted_clutch.final.png",
-       predicted_clutch.p.final,
-       device = "png",
-       width = 200, height = 200, units = "mm", dpi = "print")
-```
-
-### Estimating fitness from counts instead of from survivorship function
-```{r}
-# fitness_life_strats_data <- fitness_life_strats_data %>%
-#   mutate(desert_cat_ants = factor(desert_cat_ants, levels=c("desert control", "eggs control", 
-#                                 "nymphs control", "visit control",
-#                                 "desert ants removed", "eggs ants removed", 
-#                                 "nymphs ants removed", "visit ants removed")))
-
-fitness_stats_eggs_counted <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants)
-(fitness_counted_stats_eggs.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_eggs_life, group=desert_cat_ants, 
-                    itero=F, multcompLetters=fitness_stats_eggs_counted$multcompLetters,
-                    letterSize=4, ymax=160) +
-  ylab("Lifetime fecundity\n(eggs laid)") + 
-    theme(legend.position="none",
-          axis.title.x = element_blank(),axis.text.x=element_blank()))
-
-fitness_stats_hatched_counted <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat_ants)
-(fitness_counted_stats_hatched.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_hatched_life_v1, group=desert_cat_ants, 
-                    itero=F, multcompLetters=fitness_stats_hatched_counted$multcompLetters,
-                    letterSize=4, ymax=75) +
-  ylab("Lifetime fitness\n(eggs hatched)") + 
-    theme(legend.position=c(0.75,0.9),
-          axis.title.x = element_blank(),axis.text.x=element_blank()))
-
-fitness_stats_survived_counted <- 
-  fitness_KW_test(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat_ants)
-(fitness_counted_stats_survived.p <- 
-  fitness_plot_dunn(data=fitness_life_strats_data, y=est_survived_life_v1, group=desert_cat_ants, 
-                    itero=F, multcompLetters=fitness_stats_survived_counted$multcompLetters,
-                    letterSize=4, ymax=30) +
-  ylab("Lifetime fitness\n(nymphs survived)") + 
-    theme(legend.position="none",
-          axis.text.x=element_text(angle=45, vjust=1, hjust=1)))
-
-(fitness_counted_stats.p.final <- egg::ggarrange(
-  fitness_counted_stats_eggs.p,
-  fitness_counted_stats_hatched.p,
-  fitness_counted_stats_survived.p,
-  labels=c("A","B","C"),
-  ncol=1, nrow=3))
-
-# ggsave("CHAPTER/fitness_counted_stats.final.png",
-#        fitness_counted_stats.p.final,
-#        device = "png",
-#        width = 120, height = 200, units = "mm", dpi = "print")
-```

### 2023-08-26 R/Publilia-05-fitness-functions.R

@@ -82,7 +82,7 @@ fitness_KW_test <- function(data, y, group){
 
 
 ## plot boxplots, including KWtest letters
-fitness_plot_dunn <- function(data, y, group, itero=F, multcompLetters, letterSize, ymax=160){
+fitness_plot_dunn <- function(data, y, group, itero=F, multcompLetters, letterSize=3, ymax=160){
   if(itero==F){
     (p <- eval(substitute(data %>%
                             filter(!females_removed, !is.na(group)) %>%

### 2023-08-27 scripts/Publilia-01-qc.Rmd
Starting script 05 from `strats_data` instead of `visited_1st_4d_data`

@@
 ```{r}
-write_rds(clutch_egg_num_data, here("saved_rds/clutch_egg_num_data"))
+write_rds(clutch_egg_num_data, here("saved_rds/clutch_egg_num_data.rds"))
 write_rds(t5eggs_data, here("saved_rds/t5eggs_data"))
@@
 ```
+
+# 14 - Write data for
+
+```{r}
+write_rds(moms_plant_data, here("saved_rds/moms_plant_data.rds"))
+write_rds(focalMb4h_sc2h, here("saved_rds/focalMb4h_sc2h.rds"))
+write_rds(clutch_survivorship_data, here("saved_rds/clutch_survivorship_data.rds"))
+```

### 2023-08-27 scripts/Publilia-05-fitness.Rmd
Starting script 05 from `strats_data` instead of `visited_1st_4d_data`

@@
 ```{r}
+library(here)
+library(tidyverse)
+library(rstatix)
+library(effectsize)
 library(multcompView)
+source(here("R/utils.R"))
 source(here("R/Publilia-05-fitness-functions.R"))
@@
 ```{r}
-surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
+strats_data <- read_rds(here("saved_rds/strats_data.rds"))
+clutch_survivorship_data <- read_rds(here("saved_rds/clutch_survivorship_data.rds"))
+focalMb4h_sc2h <- read_rds(here("saved_rds/focalMb4h_sc2h.rds"))
+moms_plant_data <- read_rds(here("saved_rds/moms_plant_data.rds"))
 surv_model_fits <- read_rds(here("saved_rds/surv_model_fits.rds"))
@@
 ```{r}
-est_fitness_prep <- visited_1st_4d_data %>%
+est_fitness_prep <- strats_data %>%
   filter(!is.na(initiation_date)) %>%
@@
          desert_rel2h = est_rel2h, guard_duration,
-         mom_at_init, started_by_initiating) %>%
+         mom_at_init, started_by_initiating, ever_antsP) %>%
   left_join(select(clutch_survivorship_data, location:last_desert,
@@
          vis=`visited in 4 days`) %>%
-  left_join(select(ant_counts, location, ever_antsP)) %>%
   separate(location, into = c("DormPlant", "Leaf"), sep="_", remove=FALSE) %>%
@@
          ant_treatment=ifelse(ants_removed,"Removed","Control"))
+
+# beware that clutch_status_momDays_b4h was create by right-joining clutch_momDays_b4h; possible that some hidden filtering occurred there
 
@@
   filter(!is.na(est_hatched_clutch_v1),!is.na(est_hatched_clutch_v6)) %>%
-  ggplot(data=., aes(x=est_hatched_clutch_v1, y=est_hatched_clutch_v6, color=sum_vD==0)) +
+  ggplot(data=., aes(x=est_hatched_clutch_v1, y=est_hatched_clutch_v6, color=vis)) +
   geom_abline(slope=1) +
@@
 split violin v6
-```{r}
+```{r, fig.width = 6, fig.height = 4}
 est_fitness_life_strats_splitvio_eggs_v6.p <- est_fitness_life_strats %>%

### 2023-08-30 manuscript/Manuscript_runfile.Rmd
Section 1 of manuscript runfile

@@
 
-# 0 - Data import
+**Setup**
 
@@
 ```
+
+# 1 - Maternal egg guarding increases offspring survivorship, and ants enhance this effect
+
+## Prep
+
+```{r}
+## Load data
+surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
+```
+
+```{r}
+## Fit models
+# hatching success
+des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
+                           tenure="des", treatment="ant_treatment")
+
+# nymph survivorship
+des_Nsurv.desL.ant_treatment.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
+                           tenure="des", treatment="ant_treatment")
+
+# egg survivorship
+des_Esurv.desL.ant_treatment.quad <- surv_reg_data %>%
+  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
+                           tenure="des", treatment="ant_treatment")
+
+surv_model_fits <- list(
+  hatch = des_hatch.desL.ant_treatment.quad$fits,
+  Nsurv = des_Nsurv.desL.ant_treatment.quad$fits,
+  Esurv = des_Esurv.desL.ant_treatment.quad$fits
+)
+```
+
+## Figure 5
+
+```{r}
+(desL.ant_treatment.quad.p <- egg::ggarrange(
+  des_hatch.desL.ant_treatment.quad$p +
+    ylab("Hatching success") +
+    theme(legend.position="none"),
+  des_Nsurv.desL.ant_treatment.quad$p +
+    ylab("Nymph survivorship") +
+    theme(legend.position="none"),
+  des_Esurv.desL.ant_treatment.quad$p +
+    theme(legend.position = c(0.8,0.95)) + 
+    ylab("Egg survivorship") +
+    ylim(0,1),
+  labels=c("A","B","C"),
+  ncol=3))
+
+ggsave(here("manuscript/",
+            "Figure5.png"),
+       desL.ant_treatment.quad.p,
+       device="png", width = 300, height = 110, units = "mm", dpi = "print")
+```
+
+## Table 1
+
+```{r}
+hatch.desL.ant_treatment.quad.qb.tbl <- 
+  tbl_regression(des_hatch.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
+                 label=list(des ~ "Leaf desert date",
+                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
+                            ant_treatment ~ "Ants")) %>% bold_p()
+Nsurv.desL.ant_treatment.quad.qb.tbl <- 
+  tbl_regression(des_Nsurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
+                 label=list(des ~ "Leaf desert date",
+                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
+                            ant_treatment ~ "Ants")) %>% bold_p()
+Esurv.desL.ant_treatment.quad.qb.tbl <- 
+  tbl_regression(des_Esurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
+                 label=list(des ~ "Leaf desert date",
+                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
+                            ant_treatment ~ "Ants")) %>% bold_p()
+
+(desL.ant_treatment.quad.qb.tbl.merge <- 
+  tbl_merge(
+    tbls = list(hatch.desL.ant_treatment.quad.qb.tbl, 
+                Nsurv.desL.ant_treatment.quad.qb.tbl, 
+                Esurv.desL.ant_treatment.quad.qb.tbl),
+    tab_spanner = c("**Hatching success**", 
+                    "**Survivorship of nymphs**", 
+                    "**Survivorship of eggs**")
+  ) %>%
+  modify_header(label = "**Variable**") %>%
+  bold_labels() %>% italicize_levels())
+
+desL.ant_treatment.quad.qb.tbl.merge %>%
+  as_flex_table() %>%
+  flextable::save_as_docx(path=here("manuscript",
+                                    "Table1.docx"))
+
+```
+
+## [Text] Hatching success
+
+```{r}
+## Sample size table
+(surv_reg_data.tbl_summary.desL.ant_treatment <- surv_reg_data %>%
+  mutate(ants = ant_treatment,
+         females = ifelse(females_removed, "Females removed", "Control"),
+         `leaf desert date rel. hatch` = des,
+         `visited early` = vis,
+         `n eggs` = med_t5eggs,
+         `n hatched` = n_hatched,
+         `n survived` = n_survived) %>%
+  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
+         `n eggs`, `n hatched`, `n survived`) %>%
+  group_by(females, ants) %>%
+  tbl_summary(by = ants) %>%
+  bold_labels() %>% italicize_levels() %>%
+  add_n())
+```
+
+```{r}
+## Hatch
+# at -20,0,10 etc.
+ci_for_stats(data_in=
+               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
+                      des=rep(c(-20,10,0,10,20),2)), 
+             des_hatch.desL.ant_treatment.quad$fits$mai.qb)
+
+# where is the maximum?
+get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
+                           des=rep(seq(-20,20,length.out=10000),2)),
+            model=des_hatch.desL.ant_treatment.quad$fits$mai.qb)
+```
+
+# 2 - Offspring survivorship is equivalent when either mothers or ants guard nymphs
+
+## [Text] Nymph survivorship
+
+```{r}
+# Nsurv
+# at -20,0,10 etc.
+ci_for_stats(data_in=
+               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
+                      des=rep(c(-20,10,0,10,20),2)), 
+             des_Nsurv.desL.ant_treatment.quad$fits$mai.qb)
+
+# where is the maximum?
+get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
+                           des=rep(seq(-20,20,length.out=10000),2)),
+            model=des_Nsurv.desL.ant_treatment.quad$fits$mai.qb)
+```
+
+## [Text] Egg survivorship
+
+```{r}
+# Esurv
+# at -20,0,10 etc.
+ci_for_stats(data_in=
+               tibble(ant_treatment=c(rep("Control",5), rep("Removed",5)),
+                      des=rep(c(-20,10,0,10,20),2)), 
+             des_Esurv.desL.ant_treatment.quad$fits$mai.qb)
+
+# where is the maximum?
+get_max_fit(data_in=tibble(ant_treatment=c(rep("Control",10000), rep("Removed",10000)),
+                           des=rep(seq(-20,20,length.out=10000),2)),
+            model=des_Esurv.desL.ant_treatment.quad$fits$mai.qb)
+```
+
+# 3 - Mothers dynamically adjust care depending on the presence of ants and conspecific females
+
+## Figure Figure S3
+
+## Figure 3
+
+## [Text]
+
+# 4 - Early visits by other females lead to early desertion of clutches
+
+## Appendix A (?)
+
+## Figure 4
+
+## [Text]
+
+# 5 - Ant mutualists reliably enhance lifetime fitness, but offloading care to peers is risky
+
+## Figure 6
+
+## Figure S4
+
+## [Text]
+
+# Old:
 

### 2023-09-01 scripts/Publilia-02-strats.Rmd
fixed figures 2, 3, and s4

@@
 base_text <- expand.grid(ants = c("Ants removed", "Control"),
-            `visited in 4 days` = c("Not visited\nwithin first 4 days", 
-                                    "Visited\nwithin first 4 days")) %>%
+            `visited in 4 days` = c("Not visited", 
+                                    "Visited")) %>%
   tibble()
@@
 hatch_text <- base_text %>%
-  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited\nwithin first 4 days", 
+  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited", 
          "Hatch date", 
@@
            ifelse(`visited in 4 days` == "Visited", 
-                  "Visited\nwithin first 4 days", 
-                  "Not visited\nwithin first 4 days")) %>%
+                  "Visited", 
+                  "Not visited")) %>%
   ggplot(aes(x=guard_duration, fill=ants)) +
@@
   ylab("Number of females") +
-  scale_y_continuous(breaks = c(0,4,8),
-                     labels = label_number(accuracy = 1)) +
+  scale_y_continuous(labels = label_number(accuracy = 1)) +
   scale_color_manual(values = c("black", "brown1")) +
@@
 
+# 2023.09.31 Figure S4
+
+## Original
+```{r}
+
+Fig1_v1A.gd <- Fig1_v1_data %>%
+  filter(`visited in 4 days` == "Not visited") %>%
+  ggplot(data = .) +
+  geom_area(aes(x = guard_duration, y=..density.., color = ants, fill = ants), 
+            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
+  theme_publilia() +
+  xlab("Guarding duration") +
+  ylab("Proportion\nof initiating females") +
+  scale_color_manual(values = c("black", "brown1")) +
+ scale_fill_manual(values = c("black", "brown1")) +
+  geom_vline(xintercept = 20, linetype="dashed", 
+                color = "gray", size=1)
+
+Fig1_v1B.gd <- Fig1_v1_data %>%
+  filter(`visited in 4 days` == "Visited") %>%
+  ggplot(data = .) +
+  geom_area(aes(x = guard_duration, y=..density.., color = ants, fill = ants), 
+            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
+  theme_publilia() +
+  xlab("Guarding duration") +
+  ylab("Proportion\nof initiating females") +
+  scale_color_manual(values = c("black", "brown1")) +
+  scale_fill_manual(values = c("black", "brown1")) +
+  geom_vline(xintercept = 20, linetype="dashed", 
+                color = "gray", size=1)
+
+Fig1_v1C.gd <- strats_data %>%
+  filter(!females_removed, !mom_at_init,
+         visit_ends >= initiation_date,
+         visit_ends < last_day_fID) %>%
+  ggplot(data = .) +
+  geom_area(aes(x = guard_duration, y=..density.., color = ants, fill = ants), 
+            alpha = 0.75, stat='bin', binwidth = 4, size = 0, position = "identity") + 
+  theme_publilia() +
+  xlab("Guarding duration") +
+  ylab("Proportion\nof secondary visitors") +
+  scale_color_manual(values = c("black", "brown1")) +
+  scale_fill_manual(values = c("black", "brown1")) +
+  geom_vline(xintercept = 20, linetype="dashed", 
+                color = "gray", size=1)
+
+(Fig1_v1ABC.gd <- ggpubr::ggarrange(Fig1_v1A.gd +
+            theme(legend.justification = c(1,1),
+                  legend.position = "none") +
+            xlim(-4,52),
+         Fig1_v1B.gd + 
+           theme(legend.justification = c(1,1),
+                 legend.position = "none") +
+            xlim(-4,52),
+         Fig1_v1C.gd + 
+           theme(legend.justification = c(1,1),
+                 legend.position = c(0.95,0.95)) +
+            xlim(-4,52),
+         align = "v",
+         labels = c("A", "B", "C"),
+         ncol = 1, nrow = 3))
+```
+
+## Histogram
+```{r, fig.width=3, fig.height=4.5}
+visit_colors <- rev(unique(ggplot_build(Fig1_v1D)$data[[1]]$fill))
+
+hist_strips <- strip_nested(
+     # Horizontal strips
+     background_y = list(
+       element_rect(fill = visit_colors[1]), 
+       element_rect(fill = visit_colors[2]),
+       element_rect(fill = "cornflowerblue"),
+       element_blank(), element_blank(), 
+       element_blank(), element_blank(),
+       element_blank(), element_blank()),
+     text_y = list(
+       element_text(color = c("black")), 
+       element_text(color = c("black")), 
+       element_text(color = c("black")),
+       element_blank(), element_blank(),
+       element_blank(), element_blank(), 
+       element_blank(), element_blank()),
+     by_layer_y = FALSE
+)
+
+base_text <- expand.grid(ants = c("Ants removed", "Control"),
+            cat4facet = c("Not visited", "Visited", "Visitor")) %>%
+  tibble()
+
+hatch_text <- base_text %>%
+  mutate(label = ifelse(ants=="Ants removed" & cat4facet=="Not visited", 
+         "Hatch date", 
+         ""))
+
+Figure_S4_data <- strats_data %>%
+  mutate(is_not_visited = !grepl("U", Female_ID) &
+           !females_removed &
+           mom_at_init & 
+           clutch_initiated_order == 1 &
+           visit_ends < last_day_fID &
+           `visited in 4 days` == "Not visited",
+         is_visited = !grepl("U", Female_ID) &
+           !females_removed &
+           mom_at_init & 
+           clutch_initiated_order == 1 &
+           visit_ends < last_day_fID &
+           `visited in 4 days` == "Visited",
+         is_visitor = !females_removed &
+           !mom_at_init &
+           visit_ends >= initiation_date &
+           visit_ends < last_day_fID,
+         cat4facet = ifelse(is_visited, "Visited",
+                            ifelse(is_not_visited, "Not visited",
+                                   ifelse(is_visitor, "Visitor", NA))),
+         cat4facet = factor(cat4facet, levels = c("Not visited", "Visited", "Visitor"))) %>%
+  filter(!is.na(cat4facet))
+
+(Figure_S4 <- Figure_S4_data %>%
+  ggplot(aes(x=guard_duration, fill=ants)) +
+  geom_histogram(binwidth = 4) +
+  theme_publilia() +
+  xlab("Guarding duration") +
+  ylab("Number of females") +
+  scale_y_continuous(labels = label_number(accuracy = 1)) +
+  scale_color_manual(values = c("black", "brown1")) +
+  scale_fill_manual(values = c("black", "brown1")) +
+  geom_vline(xintercept = 20, linetype="dashed", 
+                color = "gray", size=1) +
+  ggh4x::facet_grid2(vars(cat4facet, ants), 
+                     strip = hist_strips) +
+  theme(strip.background = element_rect(color = NA),
+        strip.text = element_text(size = 12),
+        legend.justification = c(1,1),
+        legend.position = c(1,0.2),
+        legend.text = element_text(size = 12)) +
+  geom_text(data = hatch_text,
+            aes(x = 20, y = Inf, label = label),
+            hjust = -0.1, vjust = 0, color = "gray", fontface = "bold") +
+  coord_cartesian(clip = "off"))
+```
+
 # 2023.07.22 - Using geom_ridgeline instead of freq_poly with alpha
@@
               fontface="bold", size=6) +
-  xlab("Day first visited (Days since initiation)") +
+  xlab("Clutch age (days) when first visited") +
   ylab("Guard duration of initiating female") +

### 2023-12-27 manuscript/Manuscript_runfile.Rmd
Added fig 2 and 4 to `Manuscript_runfile.Rmd`

@@
 ## Load data
-surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds"))
+surv_reg_data <- read_rds(here("saved_rds/surv_reg_data.rds")) %>%
+    mutate(ant_treatment = ifelse(ant_treatment == "Removed", 
+                                  "Ant exclusion", ant_treatment))
 ```
@@
 des_Nsurv.desL.ant_treatment.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
+  runTenureXOffspringModel(., survNom="n_survived", survDen="n_hatched", 
                            tenure="des", treatment="ant_treatment")
@@
 des_Esurv.desL.ant_treatment.quad <- surv_reg_data %>%
-  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
+  runTenureXOffspringModel(., survNom="n_survived", survDen="med_t5eggs", 
                            tenure="des", treatment="ant_treatment")
@@
 
-## Figure 5
+## Figure 2
 
-```{r}
+```{r, fig.height = 2, fig.width = 6}
 (desL.ant_treatment.quad.p <- egg::ggarrange(
   des_hatch.desL.ant_treatment.quad$p +
+    xlab("Desertion date relative to hatch") +
     ylab("Hatching success") +
@@
   des_Nsurv.desL.ant_treatment.quad$p +
+    xlab("Desertion date relative to hatch") +
     ylab("Nymph survivorship") +
@@
     theme(legend.position = c(0.8,0.95)) + 
+    xlab("Desertion date relative to hatch") +
     ylab("Egg survivorship") +
@@
   ncol=3))
-
-ggsave(here("manuscript/",
-            "Figure5.png"),
-       desL.ant_treatment.quad.p,
-       device="png", width = 300, height = 110, units = "mm", dpi = "print")
 ```
@@
 
+```{r, fig.width=3, fig.height=3}
+visit_colors <- rev(unique(ggplot_build(Fig1_v1D)$data[[1]]$fill))
+
+hist_strips <- strip_nested(
+     # Horizontal strips
+     background_y = list(
+       element_rect(fill = visit_colors[1]), 
+       element_rect(fill = visit_colors[2]), 
+       element_blank(), element_blank(), 
+       element_blank(), element_blank()),
+     text_y = list(
+       element_text(color = c("black")), 
+       element_text(color = c("black")), 
+       element_blank(), element_blank(), 
+       element_blank(), element_blank()),
+     by_layer_y = FALSE
+)
+
+base_text <- expand.grid(ants = c("Ants removed", "Control"),
+            `visited in 4 days` = c("Not visited\nwithin first 4 days", 
+                                    "Visited\nwithin first 4 days")) %>%
+  tibble()
+
+hatch_text <- base_text %>%
+  mutate(label = ifelse(ants=="Ants removed" & `visited in 4 days`=="Not visited\nwithin first 4 days", 
+         "Hatch date", 
+         ""))
+
+(guarding_durations_plot_2023 <- strats_data %>%
+  filter(!grepl("U", Female_ID), !females_removed, mom_at_init,
+         clutch_initiated_order == 1, visit_ends < last_day_fID) %>% 
+  filter(!is.na(`visited in 4 days`)) %>%
+  mutate(`visited in 4 days` = 
+           ifelse(`visited in 4 days` == "Visited", 
+                  "Visited\nwithin first 4 days", 
+                  "Not visited\nwithin first 4 days")) %>%
+  ggplot(aes(x=guard_duration, fill=ants)) +
+  geom_histogram(binwidth = 4) +
+  theme_publilia() +
+  xlab("Guarding duration") +
+  ylab("Number of females") +
+  scale_y_continuous(breaks = c(0,4,8),
+                     labels = label_number(accuracy = 1)) +
+  scale_color_manual(values = c("black", "brown1")) +
+  scale_fill_manual(values = c("black", "brown1")) +
+  geom_vline(xintercept = 20, linetype="dashed", 
+                color = "gray", size=1) +
+  ggh4x::facet_grid2(vars(`visited in 4 days`, ants), 
+                     strip = hist_strips) +
+  theme(strip.background = element_rect(color = NA),
+        strip.text = element_text(size = 12),
+        legend.justification = c(1,1),
+        legend.position = c(1,0.2),
+        legend.text = element_text(size = 12)) +
+  geom_text(data = hatch_text,
+            aes(x = 20, y = Inf, label = label),
+            hjust = -0.1, vjust = 0, color = "gray", fontface = "bold") +
+  coord_cartesian(clip = "off"))
+```
+
 ## [Text]
@@
 ## Figure 4
+
+```{r, fig.width=3, fig.height=2}
+
+# non-parametric: Kruskall-Wallis test followed by Dunn test or pairwise wilcox tests
+vis_cat_v1.data <- strats_data %>%
+  left_join(first_visit_cuts) %>%
+  mutate(vis_cat = ifelse(num_at_init > 1,
+                          "0",
+                          ifelse(is.na(first_visit_starts),
+                                 "never visited",
+                                 ifelse(first_visit_cut=="(0,4]", "1 to 4", "5+"))),
+         vis_cat = factor(vis_cat, levels = c("0","1 to 4",
+                                              "5+","never visited"))) %>%
+  filter(!females_removed, mom_at_init, 
+         clutch_initiated_order == 1, 
+         !grepl("U", Female_ID),
+         visit_ends < last_day_fID,
+         # ** There was one female (E_Gkgg) which was on the eggs before and after but not ON the initiation date.
+         # I suspect I missed her in the field or she may have left and come back. In any case she was never visited
+         # and deserted 20 days after initiation and we have plenty such data points, so I think it's safe to ignore.
+         !is.na(vis_cat))
+
+(Fig1_v1D <- ggplot(data = vis_cat_v1.data, 
+       aes(y = guard_duration, x = vis_cat, group = vis_cat)) +
+  #geom_boxplot(outlier.shape = NA) +
+  geom_violin(aes(fill=vis_cat%in%c("0","1 to 4")), color = NA, trim=T, size=2, alpha=0.50) +
+  geom_jitter(aes(color=vis_cat%in%c("0","1 to 4")), width=0.1, size=3) +
+  theme_publilia() +
+  scale_color_brewer(palette="Set2") + scale_fill_brewer(palette="Set2") +
+  xlab("First day clutch was visited (Days since clutch initiated)") +
+  ylab("Guarding duration of initiating female (days)") +
+  theme(legend.position = "none"))
+
+# Visualization: box plots with p-values
+Fig1_v1D +
+    geom_text(data=strats_cuts_v1.multcompLetters, 
+              aes(x=vis_cat, y=-4, label=label, 
+                  color=vis_cat%in%c("0","1 to 4")), 
+              fontface="bold", size=6) +
+  xlab("Day first visited (Days since initiation)") +
+  ylab("Guard duration of initiating female") +
+  theme(legend.position = "none")
+```
 

### 2023-12-27 R/Publilia-03-survivorship-functions.R

@@ -76,7 +76,7 @@ ci_for_plot <- function(data_in, survNom, survDen,
 
 ### Plot model results with confidence intervals
 plot_ci <- function(ci_data, survNom, survDen, treatment, tenure){
-  plot <- ggplot(data = ci_data, 
+  p <- ggplot(data = ci_data, 
                  aes(x = .data[[tenure]], y = fit, 
                      color = .data[[treatment]], fill = .data[[treatment]])) +
     theme_publilia() +
@@ -84,6 +84,8 @@ plot_ci <- function(ci_data, survNom, survDen, treatment, tenure){
     geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
     geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                 alpha = 0.5, color = NA, key_glyph=draw_key_rect)
+  
+  return(p)
 }
 
 # Example
@@ -121,10 +123,9 @@ runTenureXOffspringModel <- function(surv_reg_data, survNom, survDen, tenure, tr
   
   p <- plot_ci(ci_data = test_ci_data, tenure = tenure, treatment=treatment,
                survNom = survNom, survDen = survDen) +
-    xlab("Latest desertion date relative to hatch") +
-    ylab("Hatching success") +
-    scale_color_manual(values = c("brown1", "black")) +
-    scale_fill_manual(values = c("brown1", "black"))
+    scale_color_manual(values = c("black", "brown1")) +
+    scale_fill_manual(values = c("black", "brown1"))
+  
   stat_summary <- summary(test_fits$mai.qb)
   
   obj_out <- list(
